### 2015-05-27 abstract.tex
First version

\begin{abstract}
The term Approximate Dynamic Programming (ADP) refers to a gamut of approximate solution methods for MDPs with large number of states. Though various ADP algorithms are known till date, very few of them successfully address both the prediction and the control problems. Approximate Linear Programming (ALP) is an ADP method that offers sound theoretical guarantees and solves both the prediction and the control problems. Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead. Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.\\
In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP. Central to our framework are two $\max$-norm contraction operators. Our result also theoretically justifies linear approximation of constraints. We discuss the implication of our results in the contexts of ADP and reinforcement learning.
\end{abstract}
\begin{keywords}{
Approximate Dynamic Programming (ADP), Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), Generalized Reduced Linear Program (GRLP), Constraint Sampling, Reinforcement Learning.}
\end{keywords}

### 2015-05-27 adp.tex
First version

\section{Approximate Dynamic Programming}
\emph{Curse-of-Dimensionality} is a term used to denote the fact that the number of states grows exponentially in the number of state variables. Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. In order to tackle the curse, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy. Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.
\subsection{Value-Function based ADP}
In the value-function based ADP schemes a parameterized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parameterized class.
Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$.
\begin{lemma}\label{subopt}
Let $\tilde{J}$ be the approximate value function and $\tilde{u}$ be as in \eqref{subpol}, then 
\begin{align}
||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty.
\end{align}
\end{lemma}
The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm. The term  $||J^*-\tilde{J}||$ denotes the error in prediction and $||J^*-J_{\tu}||$ denotes the loss in performance resulting from the sub-optimal policy $\tu$ with respect to the optimal policy $u^*$. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy. In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.\\
\subsection{Linear Function Approximation}
The most widely used parameterized class to approximate the value-function is the linear function approximator (LFA). Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.\\
There are two important approaches to value function approximation. Both the approaches start out with a basic solution method and appropriately introduce function approximation in it. The two approaches are:
\begin{enumerate}
\item The Projected Bellman Equation (PBE) which combines the BE and the linear least squares projection operator to project high dimensional quantities onto the subspace of the LFA.
\item The approximate linear programming formulation which introduces the LFA in the linear programming formulation. 
\end{enumerate}
A host of ADP methods are based on the PBE and have been found to be useful in practice. The main application of the PBE is for approximate policy evaluation, i.e., to compute $\tilde{J}_u$, an approximation to the value function $J_u$ of policy $u$. Due to the mismatch in the norms, i.e, the linear least squares projection operator based on the $L_2$-norm and the $L_\infty$-norm of the Bellman operator $T$, one cannot use the PBE to obtain a direct approximation to $J^*$. Thus in order to solve the problem of control, $\tilde{J}_u$ is used to compute a one-step greedy policy. However, again due to the mismatch in the norms, i.e., $L_2$-norm of the linear least squares projection and the $L_\infty$ norm required for policy improvement (Lemma~\ref{subopt}), the one-step greedy policy need not necessarily be an improvement. This leads to a phenomenon called \emph{policy-chattering} \cite{dpchapter} where looping within of bad policies can occur. Further, such policy-chattering can be demonstrated in simple examples as well \cite{dpchapter}. Thus, though the approximate value function obtained by solving the PBE offers guarantees for prediction it does not offer any guarantees for the control problem, a significant shortcoming of the PBE based methods.\\
The ALP formulation \cite{ALP} on the other hand does not suffer from issues such as policy-chattering, for the simple reason that it computes $\tilde{J}$ which is an approximation to $J^*$ and a one-step greedy policy $\tilde{u}$ obtained using $\tilde{J}$. In short, since there is only one policy that the ALP outputs there is no question of policy-chattering. Further, the ALP offers performance guarantees for both the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$. Though the ALP is a complete method addressing both the control and prediction problems, it nevertheless suffers from an important limitation in the form of large number of constraints (as large as the size of the state space). This limitation has been addressed in literature by sampling only a fewer tractable constraints to formulate a reduced linear program (RLP). The RLP has been shown to perform well in practice \cite{ALP,CS,CST}, but theoretical performance guarantees \cite{CS} are available for a specific RLP obtained under idealized assumptions. In this paper, by providing a sound theoretical analysis of the RLP, we aim to show that RLP is a complete method that addresses both the prediction and the control problems.
We achieve this by developing and presenting a comprehensive theoretical framework to understand the constraint reduction/approximation procedure.\\
In the next section, we discuss the approximate linear programming (ALP) formulation, the basic results and present prior results in literature as well as motivate the problem that we address in this paper.

### 2015-05-27 alubp.tex
First version

\section{Approximate Least Upper Bound Projection}\label{sec:alubp}
We define an approximate least upper bound (ALUB) projection operator which has a structure similar to the GRLP and is an approximation to the LUB operator.
\begin{definition}\label{alubpop}
Given $J\in \R^n$, its approximate least upper bound (ALUB) projection is denoted by $\hg J$ and is defined as 
\begin{align}\label{tgamdef}
(\hg J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb \forall i=1,\ldots,n,
\end{align}
where $r_{e_j}$ is a solution to the linear program in \eqref{alubplp} for $c=e_j$, and $e_j$ is the same as in Definition~\ref{lubpop}.
\begin{align}\label{alubplp}
r_c\stackrel{\Delta}{=}\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb &W^\top E \Phi r\geq W^\top HJ, W \in \R^{nd\times m}_+ .
\end{align}
\end{definition}
Note that $W$ in \eqref{alubplp} is the same matrix that is used in \eqref{grlp} and satisfies Assumption~\ref{wassump}.
\begin{lemma}\label{tgmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\geq J_2$, we have $\hg J_1\geq \hg J_2$.
\end{lemma}
\begin{proof}
The proof follows from Assumptions~\ref{wassump} and ~\ref{one} using arguments along the lines of Lemma~\ref{gmonotone}.
\end{proof}
\begin{lemma}\label{tgshift}
Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+t\one$, then $\hg J_2=\hg J_1+\alpha t\one$.
\end{lemma}
\begin{proof}
The proof follows from Assumption~\ref{wassump} and ~\ref{one}, as well as Lemma~\ref{lpsol} using arguments along the lines of Lemma~\ref{gshift}. In particular, consider the $i^{th}$ linear program corresponding to $\hg J_1$ and $\hg J_2$. Now, the result follows by letting $A=W^\top E \Phi$, $b=W^\top H J$, $c=e_i$, $b_0=\alpha t \mathbf{1}$, $x_0=\alpha t e_i$.
\end{proof}
\begin{theorem}\label{tgmaxcontra}
The operator $\hg \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$ and the following iterative scheme based on the ALUB projection operator $\hg$, see \eqref{apvi}, converges to a unique fixed point $\hv$.
\begin{align}\label{apvi}
V_{n+1}&=\hg V_n,\mb\forall n\geq 0.
\end{align}
\end{theorem}
\begin{proof}
Follows along similar lines as the proof of Theorem~\ref{gmaxcontra}.
\end{proof}
\begin{lemma}\label{relation2}
The unique fixed point $\hv$ of the iteration in \eqref{apvi} and the solution $\hj$ of the GRLP obey $\hj\geq\hv$.
\end{lemma}
\begin{proof}
Follows in a similar manner as the proof of Lemma~\ref{relation1}. To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\hj(i)\geq\Phi r_i(i)\geq V_0(i), \mb \forall i=1,\ldots,n$. Also from the monotone property of $T$ we have 
\begin{align}
\Phi r_i&\geq V_0,\nn\\
H\Phi r_i&\geq H V_0,\mbox{we also have}\nn\\
E\Phi r_i\geq H\Phi r_i&\geq HV_0,\mb\text{by taking component-wise minimum},\nn\\
E V_0\geq H V_0.
\end{align}
Since $V_1=\hg V_0$, from the definition of $\hg$ in \eqref{gamdef} and the construction of $V_0$, we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb\forall n\geq 0$. So it follows that $\hj\geq V_0\geq V_1\ldots\geq \hv$.
\end{proof}
\begin{theorem}\label{mt1}
Let $\hv$ be the fixed point of the iterative scheme in \eqref{apvi} and let $\bj$ be the best possible approximation of $J^*$ as in Definition~\ref{bestproj}, then
\begin{align}
||J^*-\hv||_\infty\leq \frac{||J^*-\bj||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{theorem}
\begin{proof}
Let $\epsilon=||J^*-\bj||_\infty$, and $\{V_n\},n\geq 0$ be the iterates of the scheme in \eqref{apvi} with $V_0=\hg J^*$, then
\begin{align}
||J^*-\hg J^*||_\infty&\leq||J^*-\Gamma J^*||_\infty+||\Gamma J^*-\hg J^*||_\infty\nn\\\vspace{10pt}
&= \epsilon+\beta,
\end{align}
where $\beta=||\Gamma J^*-\hg J^*||_\infty$. Now
\begin{align}
||J^*-\hv||_\infty&\leq ||J^*-V_0+V_0-V_1+V_1\ldots-\hv||_\infty\nn\\
&\leq ||J^*-V_0||_\infty+||V_0-V_1||_\infty+||V_1-V_2||_\infty+\ldots\nn\\
&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\\vspace{10pt}
&\leq (\epsilon+\beta)+\alpha(\epsilon+\beta)+\ldots\nn\\
&=\frac{\epsilon+\beta}{1-\alpha}.
\end{align}
\end{proof}

\begin{corollary}\label{cmt1}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_\infty$, then
\begin{align}
||J^*-\hv||_\infty\leq \frac{2||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{corollary}
\begin{proof}
The result is obtained by using Lemma~\ref{bestbnd} to replace the term $||J^*-\bj||_\infty$ in Theorem~\ref{mt1}.
\end{proof}

### 2015-05-27 basic.tex
First version

\small
\begin{align}\label{mdplp}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall s\in S, a \in A,
\end{align}
\normalsize
where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 
Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.\\
While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.\\

### 2015-05-27 cartoon.tex
First version

\begin{figure}[h!]
\centering
%\resizebox{columnwidth}{2cm}{
\begin{tikzpicture}[domain=-10:7.7,scale=0.6,font=\small,axis/.style={very thick, ->, >=stealth'}]
%\draw[line,thick,->] (-1,-0.625)--(4,-0.625);
%\draw[line,thick,->] (0,-1)--(0,4);
%\draw[line,thick,-](-0.2,-0.6)--(1,3);
\draw[line,thick,-](0.5,3.5)--(1,1);
\draw[line,thick,-](1,1)--(3,1.5);
\draw[line,thick,-](3,1.5)--(4,2.1);
\node[](one) at (2,2.3){\text{$J\geq TJ$}};
\node[rotate=-45](seven) at (-0.5,2.3){\text{\tiny $W^\top J\geq W^\top TJ$}};
\node[](two) at (-0.3,-0.5){\text{$\Phi r$}};
\node[](three) at (0.7,0.7){\text{$J^*$}};
%\draw[line,thick,-](0,0)--(4,2.5);
 \draw [ultra thick, draw=white, fill=gray, opacity=0.5]
       (0.5,3.5)--(1,1)--(3,1.5)--(4,2.1) -- cycle;
\draw[line,thick,-](-1,-0.625)--(3,1.8750);
 \fill (1,1)  circle[radius=2pt];
 \fill (2,1.25)  circle[radius=2pt];
 \fill (0.5,0.3125)  circle[radius=2pt];
\draw[line,dashed,-](-1,0.1)--(6,1);
\draw[line,dashed,-](-1,0.1)--(-2,5);
 \draw [ultra thick, draw=white, fill=gray, opacity=0.2]
       (-1,0.1)--(6,1)--(-2,5) -- cycle;
\node[] (four) at (2,0.8){\text{$\tilde{J}_c$}};
\node[] (six) at (0.5,-0.1){\text{$\hat{J}_c$}};
\end{tikzpicture}
%}
\caption{The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints. The main contribution of the paper is to bound $||J^*-\hat{J}_c||$.}
\label{cartoon}
\end{figure}

### 2015-05-27 concl.tex
First version

\section{Conclusion}
The approximate linear programming (ALP) is an approximate dynamic programming method that addresses the prediction and control problems successfully. However, an important shortcoming of the ALP is that it has large number of constraints, which is tackled in practice by sampling a tractable number of constraints from the ALP to formulate and solve a reduced linear program (RLP). Though RLP has been found to work well empirically in various domains ranging from queues to Tetris games, performance guarantees are available only in the case of a specific RLP formulated under idealized assumptions. Thus there has been a gap in the theory of constraint reduction.\\
In this paper, we introduced a novel framework based on the generalized reduced linear program formulation to study constraint reduction. The constraints of the GRLP were obtained as positive linear combinations of the original ALP. We provided an error bound that relates the optimal value function to the solution of the GRLP. Our error bound contained two terms, one inherent to the ALP formulation and the other due to constraint reduction. We also made qualitative and quantitative observations about the nature of the error term that arose due to constraint reduction. Our analysis also revealed the fact that it is not always necessary to sample according to the stationary distribution of the optimal policy and, in fact, potentially several different constraint sampling/approximation strategies might work. In particular, we also theoretically justified linear function approximation of the constraints. We also discussed the results and provided a numerical example in the domain of controlled queues. To conclude, we observe that by providing a novel theoretical framework to study constraint approximation, this paper provides important results that add to the theory of ALP.

### 2015-05-27 constsamp.tex
First version

\section{Constraint sampling}
The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP. While the objective function of the RLP is the same as that of the ALP, the RLP has only $m<<nd$ constraints sampled from the original ALP according to a given probability distribution. The reduced linear program is then given by
\small
\begin{align}\label{rlp}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall (s,a) \in \I,
\end{align}
\normalsize
where $\I$ is the index set containing the $m$ sampled state-action pairs. Using the index set $\I$ we define an $nd\times m$ matrix $\M$, called the constraint sampling matrix as below.
\begin{definition}\label{csampmat}
Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i\stackrel{\Delta}{=}s_i+(a_i-1)\times n,\forall i=1,\ldots,m$. Then the constraint sampling matrix associated with the index set $\I$ is given by
\begin{align}
\M(i,j)&=1, \mb\text{if}\mb q_i=j\nn\\
&=0, \mb\text{otherwise}.
\end{align}
\end{definition}
The RLP can then be represented in short as
\begin{align}\label{rlpshort}
\min_{r\in \N} &c^\top \Phi r\nn\\
\text{s.t}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r,
\end{align}
where $\M$ is a constraint sampling matrix as in Definition~\ref{csampmat} and $\N\subset \R^k$ is a bounded set such that $\tr \in \N$. Note that the feasible set of the RLP is a superset of the feasible set of the ALP.\\
The RLP based on constraint sampling has been found to perform well empirically in application domains ranging from controlled queuing networks (see section $6.2$ of \cite{ALP} and section $7$ of \cite{SALP}) to Tetris (see \cite{CST} and section $6$ of \cite{SALP}). However, the theoretical guarantees for the RLP are available only under a restricted setting \cite{CS}. We present the main result of \cite{CS} on constraint sampling, and to that end define the following:
\begin{definition}\label{sampdist}
Given a policy $u$ and Lyapunov function $\psi$ in the column span of $\Phi$, we define probability distributions $\mu_u$, $\mu_{u,\psi}$ and constant $\theta$ as 
\begin{align}
\mu^\top&\stackrel{\Delta}{=}(1-\alpha)c^\top (I-\alpha P_u)^{-1},\nn\\
\mu_{u,\psi}(s,a)&\stackrel{\Delta}{=}\frac{\mu_{u}(s) \psi(s)}{\mu_u^\top \psi d},\nn\\
\theta&\stackrel{\Delta}{=}\frac{(1+\beta_{\psi})}{2}\frac{\mu_{u^*}^\top \psi}{c^\top J^*}\sup_{r\in \N}||J^*-\Phi r||_{\mn}.
\end{align}
\end{definition}
We now recall Theorem~$3.1$ of \cite{CS} below.
\begin{theorem}\label{csresult}
Let $\epsilon$ and $\delta$ be scalars in $(0,1)$. Let $u^*$ be the optimal policy and $\I$ an index set containing the $m$ state-action pairs sampled independently according to the distribution $\psi_{u^*,\psi}$, for some Lyapunov function $\psi$, where
\begin{align}
m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\big).
\end{align}
Let $\tilde{r}$ be an optimal	solution of the ALP and let $\hat{r}$ be the solution of the corresponding RLP, then with probability at least $1-\delta$, we have
\begin{align}
||J^*-\Phi \hat{r}||_{1,c}\leq ||J^*-\Phi \tilde{r}||_{1,c}+\epsilon||J^*||_{1,c}.
\end{align}
\end{theorem}
\textbf{Motivation for our work:}\\
The result in Theorem~\ref{csresult} has a significant limitation in that the sampling distribution $\mu_{u^*,\psi}$ requires the knowledge of $u^*$. The optimal policy $u^*$ might not be available in practice and hence it would not be possible to even formulate the specific RLP for which the bound in Theorem~\ref{csresult} applies. However, as mentioned before, the RLP has performed reasonably well even when the sampling distribution is not $\mu_{u^*,\psi}$. Thus there is a gap between the theoretical understanding of the RLP and its practical efficacy which merits our attention. The gap also indicates that the RLP might be a special case of a generalized constraint reduction scheme with provable performance guarantees. Understanding such a generalized method would result in an ALP based ADP techinque that would have theoretical performance guarantees while being practically useful. In particular, we wish to answer the following open questions.
\begin{itemize}
\item  As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?
\item Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
\end{itemize}
In this paper, we address both of the questions above.

### 2015-05-27 grlp.tex
First version

\section{Generalized Reduced Linear Program}
In this section we present the generalized reduced linear program (GRLP) which is obtained by appropriately extending the definition of the RLP. An important property that should carry over from the RLP is that the feasible set of the GRLP should also be a superset of the feasible set of the ALP. A natural way to achieve this is to replace the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP. Formally, we define the generalized reduced linear program (GRLP) as below:
\begin{align}\label{grlp}
\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
\end{align}
where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$. Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP. Constraint reduction is achieved by choosing $m<<nd$. The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone. Also note that an RLP is trivially a GRLP as well. Unless specified otherwise we use $\hr$ to denote the solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column). Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive. Also, normalizing columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP. Keeping these in mind we also assume the following throughout the rest of the paper:
\begin{assumption}\label{wassump}
$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m<<nd$) and each of its column sums equals $1$.
\end{assumption}
The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
\input{cartoon}
The rest of the paper develops analytically various performance bounds and our main results provide the following:
\begin{enumerate}
\item A bound for $||J^*-\hj||$, the error between the approximate value function $\hj$ as computed by the GRLP and the optimal value function $J^*$;
\item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
\item an important result on constraint sampling.
\end{enumerate}
We achieve the above via two novel $\max$-norm contraction operators namely the least upper bound (LUB) projection operator (denoted by $\Gamma$) and the approximate least upper bound (ALUB) projection operator (denoted by $\hat{\Gamma}$). We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$. We first establish our results in the $L_\infty$-norm and then extend the same in a modified $L_\infty$-norm. The schematic in Fig. ~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
\FloatBarrier
\input{schematic}

### 2015-05-27 improv.tex
First version

\section{Improved Bounds}\label{sec:improv}
In this section, we present improved error bounds by making use of Lyapunov functions. 
\begin{lemma}\label{bestbndmn}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
\begin{align}
||J^*-\bj||_{\infty,1/\psi}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\infty,1/\psi} \psi\geq TJ^*$.
\end{proof}

Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the modified $L_\infty$ norm.
\begin{lemma}\label{gshiftmn}
Let $J_1\in \R^n$ and $k\in \R$ be a constant. If $J_2=J_1+k\psi$, then $\Gamma J_2\leq \Gamma J_1+\beta_{\psi} k\psi$.
\end{lemma}
\begin{proof}
The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
\end{proof}
\begin{theorem}\label{gmaxcontramn}
The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in modified $L_\infty$ with factor $\beta_{\psi}$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n$ let $\epsilon=||J_1-J_2||_{\infty,1/\psi}$. Thus
\begin{align}\label{ineq}
J_2-\epsilon\psi\leq J_1\leq J_2+\epsilon \psi.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshiftmn}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\beta_{\psi} \epsilon\psi\leq \Gamma J_1\leq \Gamma J_2+\beta_{\psi} \epsilon\psi.
\end{align}
Thus
\begin{align}
||\Gamma J_1-\Gamma J_2||_{\infty,1/\psi}\leq \beta_{\psi} ||J_1-J_2||_{\infty,1/\psi}.
\end{align}
\end{proof}
\begin{corollary}\label{hgmaxcontramn}
$\hg$ is also a contraction map in the modified $L_\infty$ norm.
\end{corollary}
\begin{proof}
Follows from arguments similar to Theorem~\ref{gmaxcontramn}.
\end{proof}
\begin{lemma}\label{cmt1mn}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
\begin{align}
||J^*-\hv||_{\infty,1/\psi}\leq \frac{2||J^*-\Phi r^*||_{\infty,1/\psi}+||\Gamma J^*-\hg J^*||_{\infty,1/\psi}}{1-\beta_{\psi}}.
\end{align}
\end{lemma}
\begin{proof}
The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\infty,1/\psi}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
\end{proof}\\
We now recall Lemma~$4.3$ of \cite{ALP}.
\begin{lemma}\label{restate}
Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ , $r \in \R^k$ be an arbitrary vector and let $r'$ be such that
\begin{align}
\Phi r'=\Phi r+||J^*-\Phi r||_{\mn}(\frac{1+\beta_{\psi}}{1-\beta_{\psi}})\psi.
\end{align}
Then $r'$ is feasible for the ALP in \eqref{alp}.
\end{lemma}
\begin{theorem}\label{mt2mn}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\stackrel{\Delta}{=}\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then
\begin{align}
||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}
%\nn\\&
+||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_{\infty,1/\psi}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
\begin{align}
||\Phi r'-J^*||_{\mn}&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.\nn
\end{align}
Since $r'$ is also feasible for the GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\
&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
&\leq c^\top \psi ||\Phi r'-\hv||_{\infty,1/\psi}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\infty,1/\psi}+||J^*-\hv||_{\infty,1/\psi}).
\end{align}
The result follows from Corollary~\ref{cmt1}.\\
\textbf{Main Result~$1$: Prediction Error bound in modified $L_\infty$-norm}
\end{proof}
\begin{theorem}\label{cmt2mn}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{finalbndmn}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
\end{align}
The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
\end{proof}\\

### 2015-05-27 intro.tex
First version

%!TEX root =  autocontgrlp.tex
\section{Introduction}\label{intro}
Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs). A policy $u$, is a mapping from state space to action space and it specifies the action selection mechanism. The problem of \emph{control} requires coming up with good policies and for which one needs to \emph{predict} the behavior of individual policies. The problem of \emph{prediction} deals with computing the value-function $J_u$\footnote{Also known as reward/cost-to-go function.} (a mapping from state space to reals) which specifies the value of each state under a given policy $u$. In order to solve an MDP it is necessary to solve the problem of prediction as well as the problem of control.\\
Given an MDP, ideally, we would be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$. The Bellman equation (BE) relates these quantities. Conventional solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming can compute exact values of $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation. By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems. However, in most practical problems the size of the state space grows exponentially in the number of state variables, making the computation of $u^*$ and $J^*$ intractable using the exact methods.\\
Approximate Dynamic Programming (ADP) \cite{dpchapter,powell} refers to a gamut of approximate solution methods to MDPs with large number of states. In order to reduce the computational effort, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy and restricting their search space to the chosen parameterized class. Thus, instead of computing exact values of $u^*$ and $J^*$, ADP methods only compute an approximate value function $\tilde{J}$ and a sub-optimal policy $\tilde{u}$. The quality of the ADP method is measured by the error $||J^*-\tilde{J}||$, in approximating the value function and the loss in performance due to the sub-optimal policy $||J^*-J_{\tilde{u}}||$, measured with respect to the optimal policy. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in the problem of finding a useful policy. In the context of ADP, the prediction and control problems are said to be addressed when the errors $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$ can be bounded so that the loss in performance due to the approximation can be quantified.\\
Value-function-only\footnote{Since this paper is concerned with results related to the Approximate Linear Programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods approximate the value function and use it to obtain a one-step look ahead policy by making use of the Bellman equation. Most widely used parameterization to approximate the value function is the linear function approximator (LFA). Methods employing LFA approximate the value function as $J_u\approx\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learnt. Dimensionality reduction is achieved by choosing fewer number of basis functions compared to the number of states.\\
A host of value-function-based ADP methods solve the Projected Bellman equation (PBE) which is obtained by including the least squares projection operator in the BE so as to project quantities onto the lower dimensional subspace. A limitation of using the least squares projection operator is that it reduces the prediction error $L_2$-norm and cannot ensure policy improvement which requires prediction error to be minimum in the $L_\infty$-norm. Due to this norm mismatch, policy improvement cannot be guaranteed and \emph{policy-chattering} (policy-oscillations) can occur in practice \cite{dpchapter}. 
As a result, the performance loss is difficult to control and existing result that control this loss are proven under restrictive conditions \cite[e.g.,][]{anszemu:mlj07,FaMuSz10}.\\
The approximate linear programming (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy. Since ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, there is no issue of policy-chattering. The ALP formulation also provides theoretical performance guarantees, i.e., both error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$ can be bounded. This makes ALP an attractive method since it addresses both the prediction and control problems. However, an important shortcoming of ALP is that the number of constraints are of the order of the state space, making the vanilla version of ALP intractable.\\
One proposal in the literature to overcome this hurdle is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a reduced linear program (RLP). The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} in various domains such as Tetris and in network of queues. However, the theoretical results \cite{CS} are available only for a specific RLP formulated under idealized conditions. Thus, there is a gap in the theoretical understanding of RLP and constraint reduction/approximation. Our aim in this paper is to provide theoretical guarantees which will make the RLP a complete ADP method that addresses both the prediction and the control problems.\\
In this paper, we develop a novel theoretical framework to study a generalized constraint reduction technique namely generalized reduced linear program (GRLP) and present its error analysis. The salient aspects of our contribution are listed below:
\begin{enumerate}
\item \textbf{Framework:}\\ We generalize the RLP to define GRLPs. A GRLP has a small number of constraints which are obtained as positive linear combinations of the original constraints of the ALP. The GRLP serves as a framework to analyze error due to constraint reduction and linear constraint approximation.
\item \textbf{Error Analysis:}
	\begin{itemize}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$. 
		\item We show that $||J^*-\hat{J}||\leq (c_1+c_2)$, where $c_1>0$, $c_2>0$ are constants. While the term $c_1$ is error inherent to the ALP formulation itself, the term $c_2$ is the additional error introduced due to constraint approximation.  
		\item We derive a greedy policy $\hu$ by making use of $\hj$ and bound the term $||J^*-J_{\hu}||$. 
		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a modified $L_\infty$-norm.
		\item Our analysis is based on two novel $\max$-norm contraction operators called the least upper bound (LUB) projection operator and the approximate least upper bound projection operator (ALUB). This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
\end{itemize}
\item \textbf{Significant Results:}
	\begin{itemize}
		\item We provide error bounds for both prediction and control errors, i.e., bound the terms $||J^*-\hj||$ and $||J^*-J_{\hu}||$ in a modified $L_\infty$-norm. Thus, the GRLP is a complete ADP method with performance guarantees for both the prediction as well as control problems. The modified $L_\infty$-norm allows us to choose the quality of approximation across various states. This makes our result an important addition to the theory of ALP \cite{ALP,CS,CST,SALP}.
		\item The structure of the error terms also reveals an important result that it is not always necessary to sample using the stationary distribution of the optimal policy. This throws additional light on constraint sampling by providing a better explanation for its empirical success even in those cases when sampling distributions other than the stationary distribution of the optimal policy was used. 
		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints. This means that constraint reduction is not only limited to sampling but also can be extended to include linear combinations of constraints.
	\end{itemize}
\item We also discuss the implication of our results in the context of reinforcement learning and also present a numerical example illustrating the theory developed. A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.
\end{enumerate}

### 2015-05-27 lp.tex
First version

\section{Approximate Linear Programming}
The LP formulation in \eqref{mdplp} can be represented in short as,
\begin{align}\label{mdplpshort}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J\geq T J,\\
\textbf{or}\nn\\
\label{shortalter}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &EJ\geq H J,\\
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $E$ is an $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other. Note that \eqref{mdplpshort} and \eqref{shortalter} are identical programs and differ only in notation. We use notation of type \eqref{mdplpshort} whenever we prefer brevity and we use notation \eqref{shortalter} in some definitions and proof for the sake of clarity.
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by letting $J=\Phi r$ in \eqref{mdplpshort} and is given as
\begin{align}\label{alp}
\min_{r\in \R^k} &c^\top \Phi r\nn\\
\text{s.t}\mb &\Phi r\geq T \Phi r.
\end{align}
Unless specified otherwise we use $\tr$ to denote the solution to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. We now state the assumptions and definitions used for the rest of the paper.
\begin{assumption}\label{one}
The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. In other words, the constant function is part of the basis.
\end{assumption}
\begin{assumption}\label{probdist}
$c=(c(i),i=1,\ldots,n)\in \R^n$ is a probability distribution, i.e., $c(i)\geq 0$ and $\sum_{i=1}^n c(i)=1$.
\end{assumption}
\begin{definition}
Given a function $\chi\colon S\ra \R^+$ we define the quantity $\beta_{\chi}$ as
\begin{align}
\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}.
\end{align}
\end{definition}
\begin{definition}
The function $\chi$ is then said to be a \emph{Lyapunov} function if $\beta_{\chi}<1$.
\end{definition}
\begin{assumption}\label{lyap}
$\psi\colon S \ra \R^+$ is a Lyapunov function and is present in the column span of the feature matrix $\Phi$.
\end{assumption}
It is straightforward to check that the function $\one$ is a Lyapunov function and trivially is present in the column span of $\Phi$. 
\begin{definition}\label{modlone}
The modified $L_1$-norm is defined as
\begin{align}
||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|,
\end{align}
where $c$ obeys Assumption~\ref{probdist}.
\end{definition}
\begin{definition}\label{modnorm}
The modified $L_\infty$-norm is defined as follows:
\begin{align}
||J||_{\infty,\rho}=\max_{s \in S} \rho(s) |J(s)|,
\end{align}
where $\rho \colon \S \ra \R^+$, $J\in \R^n$.
\end{definition}
In Definition~\ref{modnorm}, the use of the weighting function $\rho$ allows us to measure the error taking into account the relative importance of the various states. A lower value of $\rho(s)$ means that the state $s$ is less important and vice-versa.\\
We recall below Theorem~$4.2$ of \cite{ALP} which bounds the error in the approximate value function.
\begin{theorem}\label{restateval}
Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be a Lyapunov function and $c$ be a distribution as in \eqref{probdist}, then 
\begin{align}
||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}.
\end{align}
\end{theorem}
We now recall Theorem~$3.1$ of \cite{ALP} that characterizes the loss in performance of the greedy policy.
\begin{theorem}\label{restatepol}
Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP, then 
\begin{align}
||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'},
\end{align}
where $c'=(1-\alpha)c^\top(I-\alpha P_{\tu})^{-1}$.
\end{theorem}
Theorems~\ref{restateval} and ~\ref{restatepol} together imply that the ALP addresses both the control and prediction problems. Please refer to \cite{ALP} for a more detailed treatment of the ALP.\\
Note that the ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplpshort} which has $n$ variables. Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

### 2015-05-27 lubp.tex
First version

\section{Least Upper Bound Projection}\label{sec:lubp}
The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
\begin{definition}\label{lubpop}
Given $J\in \R^n$, its least upper bound projection is denoted by $\Gamma J$ and is defined as 
\begin{align}\label{gamdef}
(\Gamma J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb \forall i=1,\ldots,n,
\end{align}
where $V(i)$ denotes the $i^{th}$ component of the vector $V\in \R^n$. Also in \eqref{gamdef}, $e_j$ is the vector with $1$ in the $j^{th}$ place and zeros elsewhere, and $r_{e_j}$ is a solution to the linear program in \eqref{lubplp} for $c=e_j$.
\begin{align}\label{lubplp}
r_c\stackrel{\Delta}{=}\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb &\Phi r\geq  TJ.
\end{align}
\end{definition}
\vspace{-10pt}
\begin{remark}
\mb\\
\vspace{-10pt}
\begin{enumerate}
\item The definition of LUB operator $\Gamma \colon \R^n \ra \R^n$ involves $n$ associated linear programs.
\item Observe that $\Gamma J\geq TJ$ (follows from the fact that if $a\geq c$ and $b\geq c$, then $\min(a,b)\geq c$, where $a, b, c \in \R$).
\item Given $\Phi$ and $J\in \R^n$, define $\F\stackrel{\Delta}{=}\{\Phi r|\Phi r\geq TJ\}$. Thus $\F$ is the set of all vectors in the span of $\Phi$ that upper bound $TJ$. By fixing $c$ in the linear program in \eqref{lubplp} we select a unique vector $\Phi r_c \in \F$. The LUB projection operator $\Gamma$ picks $n$ vectors $\Phi r_{e_i},i=1,\ldots,n$ from the set $\F$ and $\Gamma J$ is obtained by computing their component-wise minimum.
\item Even though $\Gamma J$ does not belong to the span of $\Phi$, $\Gamma J$ collates the various best upper bounds that can be obtained via the linear program in \eqref{lubplp}.
\item The LUB operator $\Gamma$ in \eqref{gamdef} bears close similarity to the ALP in \eqref{alp}.
\end{enumerate}
\end{remark}
\begin{definition}\label{bestproj}
The LUB projection of $J^*$ is denoted by $\bj=\Gamma J^*$.
\end{definition}
We now characterize the LUB projection operator $\Gamma$ in the following lemmas (all the proofs are presented in the Appendix). As mentioned earlier, the error analysis depends on two $\max$-norm contraction operators the first of which is $\Gamma$. The important result of this section is Theorem~\ref{fxpres} and it relates the fixed point $\tilde{V}$ of $\Gamma$ to $J^*$.
\begin{lemma}\label{bestbnd}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_\infty$, then 
\begin{align}
||J^*-\bj||_\infty\leq 2||J^*-\Phi r^*||_\infty.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef} and the construction of $V_0$, Assumption~\ref{one}, and the fact that $\Phi r^*+||J^*-\Phi r^*||_\infty \one\geq TJ^*$. To see this, note that
\begin{align}
&\Gamma J^*=\hj \geq J^*,\nn\\
&\Phi r^* +||J^*-\Phi r^*||_\infty\geq TJ^*= J^*.\nn\\
&\text{Thus,}\nn\\
&\Phi r^* +||J^*-\Phi r^*||_\infty\geq \Gamma J^*\geq TJ^*.
\end{align}
\end{proof}

\begin{lemma}\label{gmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\geq J_2$, we have $\Gamma J_1\geq \Gamma J_2$.
\end{lemma}
\begin{proof}
Choose any $i\in \{1,\ldots,n\}$ and let $r^1_{e_i}$ and $r^2_{e_i}$ be solutions to the linear program in \eqref{lubplp} for $c=e_i$ with $J=J_1$ and $J=J_2$ respectively. Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$ and $e_i^\top \Phi r^1_{e_i} \geq e_i^\top \Phi r^2_{e_i}$, i.e., $(\Phi r^1_{e_i})(i)\geq (\Phi r^2_{e_i})(i)$. The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i})(i),\mb\forall J\in \R^n$, and our choice of $i$ was arbitrary.
\end{proof}
\begin{lemma}\label{lpsol}
Let $A\in \R^{u\times v}$, $b,c\in R^u$, $x_0 \in R^v$ and $b_0=Ax_0$. Then
\begin{align}
\min\{c^\top Ax:Ax\geq b+b_0\} =\min\{c^\top Ax:Ax\geq b\}+c^\top b_0.
\end{align}
\end{lemma}
\begin{proof}
The claim can be shown by a simple change of variables.
\end{proof}
\begin{lemma}\label{gshift}
Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+k\one$, then $\Gamma J_2=\Gamma J_1+\alpha t\one$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear programs associated with $\Gamma J_1$ and $\Gamma J_2$. The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ and $x_0=\alpha t e_i$.
\end{proof}
\begin{theorem}\label{gmaxcontra}
The operator $\Gamma  \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n,$ let $\epsilon=||J_1-J_2||_\infty$. Thus,
\begin{align}\label{ineq}
J_2-\epsilon\one\leq J_1\leq J_2+\epsilon \one.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshift}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\alpha \epsilon\one\leq \Gamma J_1\leq \Gamma J_2+\alpha \epsilon\one.
\end{align}
\end{proof}
\begin{corollary}
The iterative scheme in \eqref{pvi} based on the LUB projection operator $\Gamma$ in \eqref{gamdef} converges to a unique fixed point $\tv$.
\begin{align}\label{pvi}
V_{n+1}&=\Gamma V_n,\mb \forall n\geq 0.
\end{align}
\end{corollary}
\begin{lemma}\label{gfp}
 $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, obeys $\tv\geq T\tv$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear program associated with $\Gamma \tv$. We know that $\Phi r_{e_i}\geq T \tv,\mb \forall i=1,\ldots, n$. The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_{e_j})(i)$.
\end{proof}
\begin{lemma}\label{relation1}
 $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey the relation $\tj\geq\tv\geq J^*$.
\end{lemma}
\begin{proof}
Since $\tv\geq T\tv$ it follows that $\tv\geq J^*$. Let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{pvi} with $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\tj(i)\geq\Phi r_i(i)\geq V_0(i),\mb \forall i=1,\ldots,n$. Also from the monotone property of $T$, we have 
\begin{align}\label{lineq}
\Phi r_i&\geq V_0,\nn\\
T\Phi r_i&\geq T V_0,\mbox{we also have}\nn\\
\Phi r_i\geq T\Phi r_i&\geq T V_0,\mb\text{by taking component-wise minimum},\nn\\
V_0&\geq T V_0.
\end{align}
From the first three inequalitites in \eqref{lineq}, $\Phi r_i\geq T \Phi r_i\geq T V_0, \mb\forall i=1\to n$ and hence $V_0\geq TV_0$. Since $V_1=\Gamma V_0$, from the definition of $\Gamma$ in \eqref{gamdef} we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb\forall n\geq 0$. So it follows that $\tj\geq V_0\geq V_1\ldots\geq \tv$.
\end{proof}
\input{perfbnds}

### 2015-05-27 mdp.tex
First version

\section{Markov Decision Processes (MDPs)}
In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
An MDP is a $4$-tuple $<S,A,P,g>$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function. We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\\
A policy $\mu$ specifies the action selection mechanism, and is described by the sequence $\mu=\{u_1,u_2,\ldots,u_n,\ldots\}$, where $u_n\colon S \ra A, \mbox{ }\forall n \geq 0$. A stationary deterministic policy (SDP) is one where $u_n\equiv u, \mbox{ }\forall n\geq 0$ for some $u\colon S \ra A$. By abuse of notation we denote the SDP by $u$ itself instead of $\mu$. In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}. In this paper, we restrict our focus to the class $U$ of SDPs.  Under an SDP $u$, the MDP is a Markov chain with probability transition kernel $P_u$.\\
Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
\begin{align}
J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n)\mbox{ }\forall n\geq 0],\nn
\end{align}
where $\alpha \in (0,1)$ is a given discount factor. Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s), \forall s\in S)^\top\in R^n$ is called the value-function corresponding to the SDP $u$.\\
The optimal policy $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}. The optimal value-function $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$. Given an MDP, our aim is to find the optimal value function $J^*$ and the optimal policy $u^*$. The optimal policy and value function obey the Bellman equation (BE) as under: $\forall s \in S$,
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
\label{bellpol}u^*(s)&=\arg\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big).
\end{align}
\end{subequations}
Typically $J^*$ is computed first and $u^*$ is obtained by substituting $J^*$ in \eqref{bellpol}. The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
\begin{definition}
\begin{align}
(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big), 
\end{align}
where $J\in \R^n$. Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
\begin{align}
(T_uJ)(s)=\big(g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\big).
\end{align}
\end{definition}
Given $J \in \R^n$, $TJ$ is the `one-step' greedy value function. It is also useful to define the notion of a one-step greedy policy as below:
\begin{definition}
A policy $\tilde{u}$ is said to be greedy with respect to $\tilde{J}$ if
\begin{align}\label{subpol}
\tilde{u}(s)=\underset{a \in A}{\arg\max}(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')).
\end{align}
\end{definition}
\begin{definition}
We also define the $Q$-Bellman operator \cite{BertB} $H$. Given any $J\in \R^n$ we have,

\begin{align}
HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd},\mbox{where}\nn\\
(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \forall s\in S, a\in A,
\end{align}
\end{definition}
 We now state without proof the important properties related to the Bellman operator. Though in these results, we make use of the Bellman operator $T$, the results also trivially hold for $T_u$ as well.
\subsection{Properties of $T$}
\begin{lemma}\label{maxnorm}
$T$ is a $\max$-norm contraction operator, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
\begin{align}
||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
\end{align}
\end{lemma}
\begin{corollary}\label{uniquesol}
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{corollary}
The Bellman operator $T$ exhibits two more important properties presented in the following lemmas (see \cite{BertB} for proofs):
\begin{lemma}\label{monotone}
$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_2\geq J_1$, we have $T J_2\geq T J_1$. Further, if $J\in \R^n$ is such that $J\geq TJ$, it follows that $J\geq J^*$.
\end{lemma}
\begin{lemma}\label{shift}
Given $J\in \R^n$, $t \in \R$ and $\mathbf{1} \in \R^n$, a vector with all entries $1$, we have
\begin{align}
T(J+t\mathbf{1})=TJ+\alpha t\mathbf{1}.
\end{align}
\end{lemma}
Note that Lemmas~\ref{maxnorm}-\ref{shift} also hold for the $Q$-Bellman operator $H$.
Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}. The problem of \emph{control} deals with coming up with a good (and if possible the optimal) policy. Often, in order to solve the problem of \emph{control}, one needs to solve the problem of \emph{prediction}, which deals with computing the value function $J_u$ of the policy $u$. The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain the optimal policy $u^*$. Thus, the Bellman equation is at the heart of the solution methods to MDPs. Any solution method to MDP is said to be complete only if it satisfactorily (with provable performance guarantees) addresses both the prediction and the control problems. \\
The basic solution methods namely value iteration, policy iteration and linear programming (LP) formulation \cite{BertB} solve both the control and prediction problems. Of the three basic methods, in this paper, we are interested in the LP formulation given by
\small
\begin{align}\label{mdplp}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall s\in S, a \in A,
\end{align}
\normalsize
where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 
Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.\\
While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.\\

### 2015-05-27 polbnd.tex
First version

\textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\
We now bound the performance of the greedy policy $\hu$.
\begin{theorem}\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function. Let $r^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{polthebnd}
||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}\big).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}\label{polderv}
||J_{\hu}-\hj||_{1,c}&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
&\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
&\leq c^\top (I-\alpha P_{\hu})^{-1} \psi ||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})||J^*- \hj||_{\mn},
\end{align}
where in the second inequality, for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. Now
\begin{align}
||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
&=\frac{2c^\top \psi}{1-\beta_{\psi}}||J^*- \hj||_{\mn}.
\end{align}
The result now follows by substituting the value of $||J^*- \hj||_{\mn}$ from Corollary~\ref{cmt2mn}.
\end{proof}
\begin{note}
By letting $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}+||J^*-\hg J^*||_{\mn}$ (inequality follows from Lemma~\ref{bestbndmn}), we can also modifiy the bounds in \eqref{finalbnd} and \eqref{polthe} as
\begin{align}
\label{loose1}||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||J^*-\hg J^*||_{\mn}).\\
\label{loose2}||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(10 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||J^*-\hg J^*||_{\mn}\big).
\end{align}
Here the term $||J^*-\hg J^*||$ in \eqref{loose1} and \eqref{loose2} captures the error due to the use of both $\Phi$ and $W$. Though, \eqref{loose1} and \eqref{loose2} might be loser bounds than \eqref{finalbndmn} and \eqref{polthebnd} respectively, the aim here is to capture the error due to function approximation as well as constraint reduction in a single term.
\end{note}

### 2015-05-27 propT.tex
First version

--- 2015-05-27 mdp.tex
@@
-\section{Markov Decision Processes (MDPs)}
-In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
-An MDP is a $4$-tuple $<S,A,P,g>$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function.
-We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$.
-For simplicity, we assume that all actions are feasible in all states.
-The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$.
-We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\\
-A policy $\mu$ specifies the action selection mechanism, and is described by the sequence $\mu=\{u_1,u_2,\ldots,u_n,\ldots\}$, where $u_n\colon S \ra A, \mbox{ }\forall n \geq 0$.
-A stationary deterministic policy (SDP) is one where $u_n\equiv u, \mbox{ }\forall n\geq 0$ for some $u\colon S \ra A$.
-By abuse of notation we denote the SDP by $u$ itself instead of $\mu$.
-In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}.
-In this paper, we restrict our focus to the class $U$ of SDPs.
-Under an SDP $u$, the MDP is a Markov chain with probability transition kernel $P_u$.\\
-Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
-\begin{align}
-J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n)\mbox{ }\forall n\geq 0],\nn
-\end{align}
-where $\alpha \in (0,1)$ is a given discount factor.
-Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s), \forall s\in S)^\top\in R^n$ is called the value-function corresponding to the SDP $u$.\\
-The optimal policy $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}.
-The optimal value-function $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.
-Given an MDP, our aim is to find the optimal value function $J^*$ and the optimal policy $u^*$.
-The optimal policy and value function obey the Bellman equation (BE) as under: $\forall s \in S$,
-\begin{subequations}\label{bell}
-\begin{align}
-\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
-\label{bellpol}u^*(s)&=\arg\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big).
-\end{align}
-\end{subequations}
-Typically $J^*$ is computed first and $u^*$ is obtained by substituting $J^*$ in \eqref{bellpol}. The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
-\begin{definition}
-\begin{align}
-(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big), 
-\end{align}
-where $J\in \R^n$. Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
-\begin{align}
-(T_uJ)(s)=\big(g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\big).
-\end{align}
-\end{definition}
-Given $J \in \R^n$, $TJ$ is the `one-step' greedy value function. It is also useful to define the notion of a one-step greedy policy as below:
-\begin{definition}
-A policy $\tilde{u}$ is said to be greedy with respect to $\tilde{J}$ if
-\begin{align}\label{subpol}
-\tilde{u}(s)=\underset{a \in A}{\arg\max}(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')).
-\end{align}
-\end{definition}
-\begin{definition}
-We also define the $Q$-Bellman operator \cite{BertB} $H$. Given any $J\in \R^n$ we have,
-
-\begin{align}
-HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd},\mbox{where}\nn\\
-(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \forall s\in S, a\in A,
-\end{align}
-\end{definition}
- We now state without proof the important properties related to the Bellman operator.
-Though in these results, we make use of the Bellman operator $T$, the results also trivially hold for $T_u$ as well.
 \subsection{Properties of $T$}
@@
 Note that Lemmas~\ref{maxnorm}-\ref{shift} also hold for the $Q$-Bellman operator $H$.
-Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}.
-The problem of \emph{control} deals with coming up with a good (and if possible the optimal) policy.
-Often, in order to solve the problem of \emph{control}, one needs to solve the problem of \emph{prediction}, which deals with computing the value function $J_u$ of the policy $u$.
-The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain the optimal policy $u^*$.
-Thus, the Bellman equation is at the heart of the solution methods to MDPs.
-Any solution method to MDP is said to be complete only if it satisfactorily (with provable performance guarantees) addresses both the prediction and the control problems.
-\\
-The basic solution methods namely value iteration, policy iteration and linear programming (LP) formulation \cite{BertB} solve both the control and prediction problems.
-Of the three basic methods, in this paper, we are interested in the LP formulation given by
-\small
-\begin{align}\label{mdplp}
-\min_{J\in \R^n} &c^\top J\nn\\
-\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall s\in S, a \in A,
-\end{align}
-\normalsize
-where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 
-Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.\\
-While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.\\

### 2015-05-27 resdisc.tex
First version

%!TEX root =  autocontgrlp.tex
\section{Discussion}
In this section we discuss the implications and insights provided by the results presented in Theorems~\ref{cmt2mn} and ~\ref{polthe}.
\subsection{On Error Terms}
\begin{itemize}
\item The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
\begin{enumerate}
\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$,
\item $||\Gamma J^*-\hg J^*||_{\mn}$.
\end{enumerate}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\\
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.
\item Unlike the result in \cite{CS} which holds only for a specific RLP formulated under ideal assumptions, our bounds hold for any GRLP and as a result for any given RLP. Another interesting feature of our result is that it holds with probability $1$. 
\item A salient feature of the ALP formulation is the use of Lyapunov functions to control/shape the error across the states based on their relative importance. Since the error bounds are in a modified $L_\infty$-norm, the GRLP framework retains this salient feature of the ALP.
\end{itemize}
The fact that both the prediction and control problems can be addressed by the GRLP makes it a complete ADP method, and by addressing the constraint approximation, the GRLP framework is an important addition to the theory of ALP.
\subsection{On Constraint Reduction and Approximation}
We claim the following based on the error bounds that we derived for the GRLP.\\
{Claim $1$)} It is not always necessary to sample constraints according to the stationary distribution of the optimal policy.\\
{Claim $2$)} Constraint approximation is not only restricted to constraint sampling but also can be extended to include linear approximation of the constraints.\\
The following result (Theorem~\ref{st}) supports Claim~$1$ in the above.\\
\textbf{Main Result~$3$: On Constraint Sampling}\\
The error term $\etmn$ gives new insights into constraint sampling. 
\begin{theorem}\label{st}
Let $s\in S$ be a state whose constraint was sampled. Then
\begin{align}\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align}
\end{theorem}
\begin{proof}
Let $r_{e_s}$ and $\hat{r}_{e_s}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s})(s)\geq (\Phi \hat{r}_{e_s})(s)$. However, since all the constraints with respect to state $s$ have been sampled we know that $(\Phi \hat{r}_{e_s})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.
\end{proof}\\
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbnd} comes to our rescue to control the error due to those states that are not sampled. Thus the sampling distribution need not be the stationary distribution of the optimal policy as long as it samples the \emph{important} states, an observation that might theoretically explain the empirical successes of the RLP \cite{ALP,CST,SALP}.\\
To understand the implication of Claim~$2$ we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
\begin{align}\label{lag}
\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
\end{align}
The insight that the GRLP is a linear function approximation of the constraints (i.e., the Lagrangian multipliers) can be obtained by noting that $ Wq\approx \lambda$ in \eqref{lag2}. Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$). Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under the optimal policy $u^*$, i.e., 
\begin{align}
\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
			\lambda^*(s,a)&=0, \forall a \neq u^*(s),\nn
\end{align}
where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.\\
\subsection{Numerical Illustration}
We take up an example in the domain of controlled queues from \cite{ALP} for which the ALP has been known to work well. For this domain, we make use of our results and observations to select various useful $W$ matrices and present their performance.\\
The queuing system consists of $n=10^4$ states and $d=4$ actions. We chose $n=10^4$ because it was possible to solve both the GRLP and the exact LP (the latter with significant effort) so as to enumerate the approximation errors. We hasten to mention that while we could run the GRLP for queuing systems with $n>10^4$ without much computational overhead, solving the exact LP was not possible for $n>10^4$ as a result of which the approximation error could not be computed.\\
\textbf{Queuing Model:}
The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$.
The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$.\\
\textbf{Choice of $\Phi:$} We make use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}. This takes care of the term $||J^*-\Phi r^*||_\infty$ in \eqref{finalbnd}. \\
\textbf{Selection of $W$:} For our experiments, we choose two contenders for the $W$-matrix and compare them with the ideal sampling matrix $W_i$ (\cite{CS}) and random positive matrix $W_r$. Our choices of the $W$ matrix are as below.\\
{$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$. This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states.\\
{$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$. Our choice of the $W_a$ matrix to correspond to aggregation of near by states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
The aggregation matrix $W_a$ is defined as below: $\forall i=1,\ldots,m$,
\begin{align}\label{wdes}
W_a(i,j)&=1, \mb\forall j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
&=0,\mb\text{otherwise}.
\end{align}
We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$. We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$. We set $c(s)=(1-\zeta) \zeta^s, \mb\forall s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$. Also note that a better performance of $W_a$ and $W_c$ in the larger system $Q_L$ tallies with a lower value of $\et$ in the smaller system $Q_S$.
\FloatBarrier
\begin{table}[H]
\begin{center}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|}\hline
Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
$||J^*-\hj||_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
$||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
\end{tabular}
\end{center}
%}
\caption{Shows values of Error Terms for $Q_L$.}
\label{pref}
\end{table}

\FloatBarrier
\begin{table}[H]
%\resizebox{\columnwidth}{!}{
\begin{center}
\begin{tabular}{|c|c|c|c|}\hline
Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
\end{tabular}
\end{center}
%}
\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
$.}
\label{pref}
\end{table}
Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
\subsection{Reinforcement Learning}
Reinforcement Learning (RL) algorithms are useful in scenarios where the system is available in the form of a simulator or only samples can be obtained via direct interaction. In particular, in the RL setting, the model parameters $g$ and $P$ are not known explicitly and the underlying MDP needs to be solved by using sample trajectories. In short, RL algorithms are sample trajectory based solution schemes for solving MDPs whose model information is not known. RL methods learn by filtering out the noisy sample via stochastic approximation and they also employ function approximation in order to handle MDPs with large number of states. Most RL algorithms are sample trajectory based extensions of ADP methods.\\
The RL extension of the ALP formulation has been applied to the optimal stopping problem in \cite{ALP-Bor}. Function approximation is employed to approximate the square root of the Lagrange multipliers. However, since the approximation is not linear, convergence of the resulting RL algorithm cannot be guaranteed. Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.

### 2015-05-27 strel.tex
First version

\section{A simple bound}
The following lemmas relate the fixed point $\hv$ of $\hg$ to the solution $\hj$ of the GRLP in \eqref{grlp}.
\begin{lemma}\label{srw}
$\hat{r} \in \R^k$ is a solution to GRLP in \eqref{grlp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\min_{r\in \chi} &||\Phi r-\hv||_{1,c}\nn\\
\text{s.t}\mb & W^\top \Phi r\geq W^\top T \Phi r.
\end{align}
\end{lemma}
\begin{proof}
We know from Lemma~\ref{relation2} that $\hj\geq\hv$, and thus minimizing $||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv$, is the same as minimizing $c^\top \Phi r$.
\end{proof}
\begin{theorem}\label{mt2}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\stackrel{\Delta}{=}\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
\begin{align}
||\hj-\hv||_{1,c}\leq\frac{4||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_\infty$, then  it is easy to see that
\begin{align}
||J^*-T\Phi r^*||_\infty&=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma,\mb\text{and}\nn\\\vspace{10pt}
||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma.
\end{align}
From Assumption~\ref{one} there exists $r'\in \R^k$ such that $\Phi r'=\Phi r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP. Now
\begin{align}
||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty\nn\\&\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
\end{align}
Since $r'$ is also feasible for GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\\vspace{10pt}
&\leq||\Phi r'-\hv||_\infty\mb\text{(Since $c$ is a distribution)}\nn\\
&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty.\nn
\end{align}
The result follows from Corollary~\ref{cmt1}.
\end{proof}\\
\textbf{Prediction Error bound in the $L_\infty$-norm}\\
\begin{corollary}\label{cmt2}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then
\begin{align}\label{finalbnd}
||J^*-\hj||_{1,c}\leq\frac{6 ||J^*-\Phi r^*||_\infty+2||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{corollary}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\\vspace{10pt}
&\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}\nn
\end{align}
The result now follows from Corollary~\ref{cmt1} and Theorem~\ref{mt2}.
\end{proof}
The results presented in Corollary~\ref{cmt2} is in the $L_\infty$-norm. In the next section, we use of Lyapunov functions to provide an improved bound in a modified $L_\infty$-norm.

### 2015-05-28 resdisc.tex
changed resdisc.tex

@@
 The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.
-Also note that a better performance of $W_a$ and $W_c$ in the larger system $Q_L$ tallies with a lower value of $\et$ in the smaller system $Q_S$.
 \FloatBarrier
@@
 Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
+\subsection{Computational Complexity}
+It is known that the complexity of the linear program \cite{kar} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables.
+In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states.
+Thus, the complexity of obtaining the exact solution grows at a rate which is at least quadratic in the number of states.
+The entries of the GRLP on the other hand are of the order of $m\time k$, where the constants $m$ and $k$ are chosen to be much smaller than the number of states.
+We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$) take a time of only about $0.03$ seconds or lesser while computing the exact solution took about $21$ minutes.
+Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the orginial constraints of the ALP without additional computational overhead.
 \subsection{Reinforcement Learning}

### 2015-06-01 alubp.tex
small edits, mostly typography + some comments

@@
+%!TEX root =  autocontgrlp.tex
 \section{Approximate Least Upper Bound Projection}\label{sec:alubp}
@@
 \begin{align}\label{tgamdef}
-(\hg J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb \forall i=1,\ldots,n,
+(\hg J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb i=1,\ldots,n,
 \end{align}
@@
 \begin{align}\label{apvi}
-V_{n+1}&=\hg V_n,\mb\forall n\geq 0.
+V_{n+1}&=\hg V_n,\mb n\geq 0.
 \end{align}
@@
 Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$.
-It is clear from the definition of $V_0$ that $\hj(i)\geq\Phi r_i(i)\geq V_0(i), \mb \forall i=1,\ldots,n$.
+It is clear from the definition of $V_0$ that $\hj(i)\geq\Phi r_i(i)\geq V_0(i)$, $i=1,\ldots,n$.
 Also from the monotone property of $T$ we have
@@
 \end{align}
-Since $V_1=\hg V_0$, from the definition of $\hg$ in \eqref{gamdef} and the construction of $V_0$, we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb\forall n\geq 0$.
+Since $V_1=\hg V_0$, from the definition of $\hg$ in \eqref{gamdef} and the construction of $V_0$, we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb n\geq 0$.
 So it follows that $\hj\geq V_0\geq V_1\ldots\geq \hv$.
@@
 \begin{theorem}\label{mt1}
-Let $\hv$ be the fixed point of the iterative scheme in \eqref{apvi} and let $\bj$ be the best possible approximation of $J^*$ as in Definition~\ref{bestproj}, then
+Let $\hv$ be the fixed point of the iterative scheme in \eqref{apvi} and let $\bj$ be the best possible LUB approximation of $J^*$ as in Definition~\ref{bestproj}. Then,
 \begin{align}
@@
 Let $\epsilon=||J^*-\bj||_\infty$, and $\{V_n\},n\geq 0$ be the iterates of the scheme in \eqref{apvi} with $V_0=\hg J^*$, then
+\todoc{Can the proof be simplified similarly to that of Theorem~\ref{fxpres}? Not a high priority.}
 \begin{align}

### 2015-06-01 cartoon.tex
small edits, mostly typography + some comments

@@
+%!TEX root =  autocontgrlp.tex
 \begin{figure}[h!]
@@
 %\resizebox{columnwidth}{2cm}{
-\begin{tikzpicture}[domain=-10:7.7,scale=0.6,font=\small,axis/.style={very thick, ->, >=stealth'}]
+%\begin{tikzpicture}[domain=-10:7.7,scale=0.6,font=\small,axis/.style={very thick, ->, >=stealth'}]
+\begin{tikzpicture}[domain=-10:7.7,scale=1.2,font=\normalsize,axis/.style={very thick, ->, >=stealth'}]
 %\draw[line,thick,->] (-1,-0.625)--(4,-0.625);
@@
 %}
-\caption{The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints.
+\caption{
+%\normalsize 
+The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints.
 The main contribution of the paper is to bound $||J^*-\hat{J}_c||$.}

### 2015-06-01 lubp.tex
small edits, mostly typography + some comments

@@
+%!TEX root =  autocontgrlp.tex
 \section{Least Upper Bound Projection}\label{sec:lubp}
@@
 \begin{align}\label{gamdef}
-(\Gamma J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb \forall i=1,\ldots,n,
+(\Gamma J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i),\quad i=1,\ldots,n,
 \end{align}
 where $V(i)$ denotes the $i^{th}$ component of the vector $V\in \R^n$.
-Also in \eqref{gamdef}, $e_j$ is the vector with $1$ in the $j^{th}$ place and zeros elsewhere, and $r_{e_j}$ is a solution to the linear program in \eqref{lubplp} for $c=e_j$.
+Also in \eqref{gamdef}, $e_j$ is the vector with $1$ in the $j^{th}$ place and zeros elsewhere, and $r_{e_j}$ is a solution to the linear program in \eqref{lubplp} for $c=e_j$:
 \begin{align}\label{lubplp}
-r_c\stackrel{\Delta}{=}\min_{r\in \chi} &c^\top \Phi r,\nn\\
-\text{s.t}\mb &\Phi r\geq  TJ.
+ r_c   \stackrel{\Delta}{=}& \argmin_{r\in \chi} c^\top \Phi r,\nn\\
+ \text{s.t}& \mb \Phi r\geq  TJ.
 \end{align}
 \end{definition}
+Note that $r_{e_j}$ depends on $J$, but this dependence is suppressed to reduce clutter. 
 \vspace{-10pt}
@@
 \item The LUB operator $\Gamma$ in \eqref{gamdef} bears close similarity to the ALP in \eqref{alp}.
+In fact, it is not hard to observe that $(\Gamma J)(i) = (\Phi r_{e_i})(i)$ for any $1\le i \le n$; the reason $\Gamma$ is defined the way it is so that this resembles to \eqref{alp} will be clear.
+\todoc{In fact, I would prefer the simpler definition without the $\min$ and then changing this remark.}
 \end{enumerate}
@@
 \end{definition}
-We now characterize the LUB projection operator $\Gamma$ in the following lemmas (all the proofs are presented in the Appendix).
+We now characterize the LUB projection operator $\Gamma$ in the following lemmas. 
 As mentioned earlier, the error analysis depends on two $\max$-norm contraction operators the first of which is $\Gamma$.
 The important result of this section is Theorem~\ref{fxpres} and it relates the fixed point $\tilde{V}$ of $\Gamma$ to $J^*$.
+\todoc{Poor choice of symbols: $\tilde{V}$ is the fixed point of $\Gamma$ and $\hat{V}$ will be the fixed point of $\tilde{\Gamma}$? Hmm.. Not a high priority to change it, but still..}
 \begin{lemma}\label{bestbnd}
@@
 \begin{align}
-&\Gamma J^*=\hj \geq J^*,\nn\\
-&\Phi r^* +||J^*-\Phi r^*||_\infty\geq TJ^*= J^*.\nn\\
-&\text{Thus,}\nn\\
-&\Phi r^* +||J^*-\Phi r^*||_\infty\geq \Gamma J^*\geq TJ^*.
+\Gamma J^*=\hj \geq J^*,\nn \text{ and }
+\Phi r^* +||J^*-\Phi r^*||_\infty\geq TJ^*= J^*.\nn
+\end{align}
+Thus,
+\begin{align}
+\Phi r^* +||J^*-\Phi r^*||_\infty\geq \Gamma J^*\geq TJ^*.
 \end{align}
@@
 Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$ and $e_i^\top \Phi r^1_{e_i} \geq e_i^\top \Phi r^2_{e_i}$, i.e., $(\Phi r^1_{e_i})(i)\geq (\Phi r^2_{e_i})(i)$.
-The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i})(i),\mb\forall J\in \R^n$, and our choice of $i$ was arbitrary.
+The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i})(i)$, $J\in \R^n$, and our choice of $i$ was arbitrary.
 \end{proof}
@@
 \begin{lemma}\label{gshift}
-Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+k\one$, then $\Gamma J_2=\Gamma J_1+\alpha t\one$.
+Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+t\one$, then $\Gamma J_2=\Gamma J_1+\alpha t\one$.
 \end{lemma}
@@
 \begin{corollary}
-The iterative scheme in \eqref{pvi} based on the LUB projection operator $\Gamma$ in \eqref{gamdef} converges to a unique fixed point $\tv$.
+Let $V_0$ be arbitrary and $(V_n)$ be defined recursively by
 \begin{align}\label{pvi}
-V_{n+1}&=\Gamma V_n,\mb \forall n\geq 0.
+V_{n+1}&=\Gamma V_n, \quad n\geq 0\,.
 \end{align}
+Then, $V_n$ converges to the the unique fixed point $\tv$ of $\Gamma$.
 \end{corollary}
@@
 Consider the $i^{th}$ linear program associated with $\Gamma \tv$.
-We know that $\Phi r_{e_i}\geq T \tv,\mb \forall i=1,\ldots, n$.
+We know that $\Phi r_{e_i}\geq T \tv$, for all $i=1,\ldots, n$.
 The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_{e_j})(i)$.
@@
 Now consider the iterative scheme in \eqref{pvi} with $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$.
-It is clear from the definition of $V_0$ that $\tj(i)\geq\Phi r_i(i)\geq V_0(i),\mb \forall i=1,\ldots,n$.
+It is clear from the definition of $V_0$ that $\tj(i)\geq\Phi r_i(i)\geq V_0(i)$, $i=1,\ldots,n$.
 Also from the monotone property of $T$, we have
@@
 \Phi r_i&\geq V_0,\nn\\
-T\Phi r_i&\geq T V_0,\mbox{we also have}\nn\\
-\Phi r_i\geq T\Phi r_i&\geq T V_0,\mb\text{by taking component-wise minimum},\nn\\
-V_0&\geq T V_0.
+T\Phi r_i&\geq T V_0,\nn
 \end{align}
-From the first three inequalitites in \eqref{lineq}, $\Phi r_i\geq T \Phi r_i\geq T V_0, \mb\forall i=1\to n$ and hence $V_0\geq TV_0$.
-Since $V_1=\Gamma V_0$, from the definition of $\Gamma$ in \eqref{gamdef} we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb\forall n\geq 0$.
+hence we also have,
+$\Phi r_i\geq T\Phi r_i \geq T V_0$, 
+and so by taking component-wise minimum,
+$V_0 \geq T V_0$.
+
+From the first three inequalities in \eqref{lineq}, $\Phi r_i\geq T \Phi r_i\geq T V_0$, $i=1,\dots, n$ and hence $V_0\geq TV_0$.
+Since $V_1=\Gamma V_0$, from the definition of $\Gamma$ in \eqref{gamdef} we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}$, $n\geq 0$.
 So it follows that $\tj\geq V_0\geq V_1\ldots\geq \tv$.

### 2015-06-01 resdisc.tex
small edits, mostly typography + some comments

--- 2015-05-27 resdisc.tex
@@
 				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
-			\lambda^*(s,a)&=0, \forall a \neq u^*(s),\nn
+			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
 \end{align}
@@
 Our choice of the $W_a$ matrix to correspond to aggregation of near by states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
-The aggregation matrix $W_a$ is defined as below: $\forall i=1,\ldots,m$,
+The aggregation matrix $W_a$ is defined as below: for all $ i=1,\ldots,m$,
 \begin{align}\label{wdes}
-W_a(i,j)&=1, \mb\forall j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
+W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
 &=0,\mb\text{otherwise}.
@@
 We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$.
-We set $c(s)=(1-\zeta) \zeta^s, \mb\forall s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively.
+We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively.
 The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.
-Also note that a better performance of $W_a$ and $W_c$ in the larger system $Q_L$ tallies with a lower value of $\et$ in the smaller system $Q_S$.
 \FloatBarrier
@@
 Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
+\subsection{Computational Complexity}
+It is known that the complexity of the linear program \cite{karmarkar} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables.
+In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states.
+Thus, the complexity of obtaining the exact solution grows at a rate which is at least quadratic in the number of states.
+The entries of the GRLP on the other hand are of the order of $m\times k$, \todoc{$\times d$?} where the constants $m$ and $k$ are chosen to be much smaller than the number of states.
+We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, while computing the exact solution took about $20$ minutes.
+\todoc{Sorry for the many questions, but did you also run ALP ($k=4$) with no constraint aggregation?}
+ Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the original constraints of the ALP without additional computational overhead.
 \subsection{Reinforcement Learning}

### 2015-06-01 strel.tex
small edits, mostly typography + some comments

@@
+%!TEX root =  autocontgrlp.tex
 \section{A simple bound}
@@
 \begin{proof}
-We know from Lemma~\ref{relation2} that $\hj\geq\hv$, and thus minimizing $||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv$, is the same as minimizing $c^\top \Phi r$.
+We know from Lemma~\ref{relation2} that $\hj\geq\hv$, and thus minimizing 
+\begin{align*}
+||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv
+\end{align*} 
+is the same as minimizing $c^\top \Phi r$.
 \end{proof}
@@
 \end{align}
-From Assumption~\ref{one} there exists $r'\in \R^k$ such that $\Phi r'=\Phi r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP. Now
+From Assumption~\ref{one} there exists $r'\in \R^k$ such that $\Phi r'=\Phi r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP.
+\todoc{Why not just state that let $r' = r^* + \frac{(1+\alpha)\gamma}{1-\alpha} e_1$?}
+Now
 \begin{align}
 ||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty\nn\\&\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
+\label{mt2eq1}
 \end{align}
@@
 \begin{align}
-||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\\vspace{10pt}
-&\leq||\Phi r'-\hv||_\infty\mb\text{(Since $c$ is a distribution)}\nn\\
-&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty.\nn
+||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn &(\text{thanks to Lemma~\ref{srw}}) \\ %\vspace{10pt}
+&\leq||\Phi r'-\hv||_\infty\mb & \text{(since $c$ is a distribution)}\nn\\
+&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,,\nn
 \end{align}
-The result follows from Corollary~\ref{cmt1}.
+The result follows from \eqref{mt2eq1} and Corollary~\ref{cmt1}.
 \end{proof}\\
@@
 \begin{corollary}\label{cmt2}
-Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then
+Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then \todoc{Where is the effect of $\chi$?}
 \begin{align}\label{finalbnd}

### 2015-06-01 alubp.tex
removed vspaces

--- 2015-05-27 alubp.tex
@@
 \begin{align}
-||J^*-\hg J^*||_\infty&\leq||J^*-\Gamma J^*||_\infty+||\Gamma J^*-\hg J^*||_\infty\nn\\\vspace{10pt}
+||J^*-\hg J^*||_\infty&\leq||J^*-\Gamma J^*||_\infty+||\Gamma J^*-\hg J^*||_\infty\nn\\
 &= \epsilon+\beta,
@@
 &\leq ||J^*-V_0||_\infty+||V_0-V_1||_\infty+||V_1-V_2||_\infty+\ldots\nn\\
-&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\\vspace{10pt}
+&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\
 &\leq (\epsilon+\beta)+\alpha(\epsilon+\beta)+\ldots\nn\\
@@
 \end{proof}
-
 \begin{corollary}\label{cmt1}

### 2015-06-01 grlp.tex

@@
+%!TEX root =  autocontgrlp.tex
 \section{Generalized Reduced Linear Program}
@@
 where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$.
+\todoc{I don't think that $\chi$ is used in a consistent fashion.
+On the first reading though, I noticed this.
+Also, the role of $\chi$ is never explained.
+Or did I just miss this?
+Do we want to keep $\chi$ or maybe we should just remove it?}
 Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP.

### 2015-06-01 lp.tex

@@
+%!TEX root =  autocontgrlp.tex
 \section{Approximate Linear Programming}
@@
 \begin{definition}\label{modlone}
-The modified $L_1$-norm is defined as
+The modified $L_1$-norm is defined as \todoc{modified $\Rightarrow$ weighted?}
 \begin{align}
@@
 \begin{definition}\label{modnorm}
-The modified $L_\infty$-norm is defined as follows:
+The modified $L_\infty$-norm is defined as follows:  \todoc{modified $\Rightarrow$ weighted?
+Also, the convention in math is to divide in the case of the $L_{\infty}$ norm.
+Not a high priority to change this, but maybe it would be good to do this in the longer term.}
 \begin{align}

### 2015-06-01 mdp.tex

@@
+%!TEX root =  autocontgrlp.tex
 \section{Markov Decision Processes (MDPs)}
 In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
-An MDP is a $4$-tuple $<S,A,P,g>$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function.
+An MDP is a $4$-tuple $\langle S,A,P,g\rangle$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function.
 We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$.
@@
 We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\\
-A policy $\mu$ specifies the action selection mechanism, and is described by the sequence $\mu=\{u_1,u_2,\ldots,u_n,\ldots\}$, where $u_n\colon S \ra A, \mbox{ }\forall n \geq 0$.
-A stationary deterministic policy (SDP) is one where $u_n\equiv u, \mbox{ }\forall n\geq 0$ for some $u\colon S \ra A$.
+A policy $\mu$ specifies the action selection mechanism, and is described by the sequence $\mu=(u_1,u_2,\ldots,u_n,\ldots)$, where $u_n\colon S \ra A$ for all $n \geq 0$.
+A stationary deterministic policy (SDP) is one where $u_n\equiv u$ for all $n\geq 0$ for some $u\colon S \ra A$.
 By abuse of notation we denote the SDP by $u$ itself instead of $\mu$.
@@
 \begin{align}
-J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n)\mbox{ }\forall n\geq 0],\nn
+J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n), n= 0,1,\dots],\nn
 \end{align}
 where $\alpha \in (0,1)$ is a given discount factor.
-Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s), \forall s\in S)^\top\in R^n$ is called the value-function corresponding to the SDP $u$.\\
+Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s))_{s\in S}\in R^n$ is called the value-function corresponding to the SDP $u$.\\
 The optimal policy $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}.
@@
 Given an MDP, our aim is to find the optimal value function $J^*$ and the optimal policy $u^*$.
-The optimal policy and value function obey the Bellman equation (BE) as under: $\forall s \in S$,
+The optimal policy and value function obey the Bellman equation (BE) as under: for all $ s \in S$,
 \begin{subequations}\label{bell}
@@
 HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd},\mbox{where}\nn\\
-(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \forall s\in S, a\in A,
+(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A,
 \end{align}
@@
 Of the three basic methods, in this paper, we are interested in the LP formulation given by
-\small
 \begin{align}\label{mdplp}
 \min_{J\in \R^n} &c^\top J\nn\\
-\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall s\in S, a \in A,
+\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \qquad s\in S, a \in A,
 \end{align}
-\normalsize
 where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 

### 2015-06-01 resdisc.tex
Resolving conflict marks (<<<HEAD)

@@
 \subsection{Computational Complexity}
-It is known that the complexity of the linear program \cite{karmarkar} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables.
+It is known that the complexity of the linear program \cite{karmarkar,adler} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables.
 In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states.

### 2015-06-01 strel.tex
removed vspaces
Resolving conflict marks (<<<HEAD)

@@
 \begin{align}
-||J^*-T\Phi r^*||_\infty&=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma,\mb\text{and}\nn\\\vspace{10pt}
+||J^*-T\Phi r^*||_\infty&=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma,\mb\text{and}\nn\\
 ||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma.
@@
 ||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn &(\text{thanks to Lemma~\ref{srw}}) \\ %\vspace{10pt}
-&\leq||\Phi r'-\hv||_\infty\mb & \text{(since $c$ is a distribution)}\nn\\
-&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,,\nn
+&\leq||\Phi r'-\hv||_\infty\mb & (\text{since $c$ is a distribution})\nn\\
+&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,.\nn
 \end{align}
@@
 \begin{align}
-||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\\vspace{10pt}
+||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
 &\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}\nn

### 2015-06-02 intro.tex
Cleaning the beginning

@@
 The problem of \emph{control} requires coming up with good policies and for which one needs to \emph{predict} the behavior of individual policies.
-The problem of \emph{prediction} deals with computing the value-function $J_u$\footnote{Also known as reward/cost-to-go function.} (a mapping from state space to reals) which specifies the value of each state under a given policy $u$.
-In order to solve an MDP it is necessary to solve the problem of prediction as well as the problem of control.\\
-Given an MDP, ideally, we would be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$.
+The problem of \emph{prediction} deals with computing the value-function $J_u$(a mapping from state space to reals\footnote{Also known as reward/cost-to-go function.}) which specifies the value of each state under a given policy $u$.
+In order to solve an MDP it is necessary to solve the problem of prediction as well as the problem of control.\todoc{Do we have a source to cite here?
+What does it mean to solve an MDP anyways?
+Find an optimal policy?
+Find a near-optimal policy?
+I think the story is that knowing the optimal value function helps, but I have not seen any claim that it is \emph{necessary} to compute it to find.}
+
+Given an MDP,\todoc{How is the MDP given? If it is given as a list of values, just reading the values may take too much time.
+Or we assume sparsity?
+Or we assume that one can query the next state distribution at any state-action?
+These yield to different models.
+We should specify which one we work with (presumably the sparse is the easiest).
+} ideally, we would be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$.
 The Bellman equation (BE) relates these quantities.
@@
 By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems.
-However, in most practical problems the size of the state space grows exponentially in the number of state variables, making the computation of $u^*$ and $J^*$ intractable using the exact methods.\\
-Approximate Dynamic Programming (ADP) \cite{dpchapter,powell} refers to a gamut of approximate solution methods to MDPs with large number of states.
+However, in most practical problems the size of the state space grows exponentially in the number of state variables, making the computation of $u^*$ and $J^*$ intractable using the exact methods.
+
+\emph{Approximate dynamic programming} (ADP) \cite{dpchapter,powell} refers to a gamut of approximate solution methods to MDPs with large number of states.
 In order to reduce the computational effort, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy and restricting their search space to the chosen parameterized class.
@@
 The quality of the ADP method is measured by the error $||J^*-\tilde{J}||$, in approximating the value function and the loss in performance due to the sub-optimal policy $||J^*-J_{\tilde{u}}||$, measured with respect to the optimal policy.
-Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in the problem of finding a useful policy.
-In the context of ADP, the prediction and control problems are said to be addressed when the errors $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$ can be bounded so that the loss in performance due to the approximation can be quantified.\\
-Value-function-only\footnote{Since this paper is concerned with results related to the Approximate Linear Programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods approximate the value function and use it to obtain a one-step look ahead policy by making use of the Bellman equation.
-Most widely used parameterization to approximate the value function is the linear function approximator (LFA).
+Of the two error terms, $||J^*-J_{\tu}||$ is more important if we are interested in the problem of finding a useful policy.
+In the context of ADP, the prediction and control problems are said to be addressed when the errors $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$ can be bounded so that the loss in performance due to the approximation can be quantified.
+\todoc{I don't understand why one should care about  approximating $J^*$ at all.}
+
+Value-function-only\footnote{Since this paper is concerned with results related to the approximate linear programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods approximate the value function and use it to obtain a one-step look ahead policy by making use of the Bellman equation.
+Most widely used parameterization to approximate the value function is the \emph{linear function approximator} (LFA).
 Methods employing LFA approximate the value function as $J_u\approx\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learnt.
-Dimensionality reduction is achieved by choosing fewer number of basis functions compared to the number of states.\\
-A host of value-function-based ADP methods solve the Projected Bellman equation (PBE) which is obtained by including the least squares projection operator in the BE so as to project quantities onto the lower dimensional subspace.
+Dimensionality reduction (in terms of the number of unknowns) is achieved by choosing fewer number of basis functions compared to the number of states.
+
+A host of value-function-based ADP methods solve the \emph{projected Bellman equation} (PBE) which is obtained by including the least squares projection operator in the BE so as to project quantities onto the lower dimensional subspace.
 A limitation of using the least squares projection operator is that it reduces the prediction error $L_2$-norm and cannot ensure policy improvement which requires prediction error to be minimum in the $L_\infty$-norm.
 Due to this norm mismatch, policy improvement cannot be guaranteed and \emph{policy-chattering} (policy-oscillations) can occur in practice \cite{dpchapter}.
-As a result, the performance loss is difficult to control and existing result that control this loss are proven under restrictive conditions \cite[e.g.,][]{anszemu:mlj07,FaMuSz10}.\\
-The approximate linear programming (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy.
+As a result, the performance loss is difficult to control and existing result that control this loss are proven under restrictive conditions \cite[e.g.,][]{anszemu:mlj07,FaMuSz10}.
+
+The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy.
 Since ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, there is no issue of policy-chattering.
@@
 This makes ALP an attractive method since it addresses both the prediction and control problems.
-However, an important shortcoming of ALP is that the number of constraints are of the order of the state space, making the vanilla version of ALP intractable.\\
-One proposal in the literature to overcome this hurdle is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a reduced linear program (RLP).
+However, an important shortcoming of ALP is that the number of constraints are of the order of the state space, making the vanilla version of ALP intractable.
+
+One proposal in the literature to overcome this hurdle is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP).
 The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} in various domains such as Tetris and in network of queues.
-However, the theoretical results \cite{CS} are available only for a specific RLP formulated under idealized conditions.
+However, the theoretical results are available only for a specific RLP formulated under idealized conditions \cite{CS}.
 Thus, there is a gap in the theoretical understanding of RLP and constraint reduction/approximation.
-Our aim in this paper is to provide theoretical guarantees which will make the RLP a complete ADP method that addresses both the prediction and the control problems.\\
-In this paper, we develop a novel theoretical framework to study a generalized constraint reduction technique namely generalized reduced linear program (GRLP) and present its error analysis.
+Our aim in this paper is to fill this gap by providing theoretical guarantees which will make the RLP a complete ADP method that addresses both the prediction and the control problems.
+
+In particular, in this paper we develop a novel theoretical framework to study a generalized constraint reduction technique namely \emph{generalized reduced linear program} (GRLP) and present its error analysis.
 The salient aspects of our contribution are listed below:
 \begin{enumerate}
-\item \textbf{Framework:}\\ We generalize the RLP to define GRLPs.
-A GRLP has a small number of constraints which are obtained as positive linear combinations of the original constraints of the ALP.
+\item \textbf{Framework:}
+
+We generalize RLPs to define GRLPs. A GRLP has a small number of constraints which are obtained as positive linear combinations of the original constraints of the ALP. 
 The GRLP serves as a framework to analyze error due to constraint reduction and linear constraint approximation.
@@
 		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$. 
-		\item We show that $||J^*-\hat{J}||\leq (c_1+c_2)$, where $c_1>0$, $c_2>0$ are constants.
-While the term $c_1$ is error inherent to the ALP formulation itself, the term $c_2$ is the additional error introduced due to constraint approximation.
-		\item We derive a greedy policy $\hu$ by making use of $\hj$ and bound the term $||J^*-J_{\hu}||$. 
+		\item We show a bound of the form $||J^*-\hat{J}||\leq c_1+c_2$, 
+		where the term $c_1$ is the error inherent to the ALP formulation itself, 
+		while the term $c_2$ is the additional error introduced due to the constraint approximation.  
+		\item We derive a greedy policy $\hu$ by making use of $\hj$ and bound the loss $||J^*-J_{\hu}||$. 
 		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a modified $L_\infty$-norm.

### 2015-06-02 mdp.tex
Cleaning the beginning

@@
 An MDP is a $4$-tuple $\langle S,A,P,g\rangle$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function.
-We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$.
+We consider MDPs with large but finite number of states.
+We also assume that the number of actions is finite.
+Without the loss of generality, we set  $S=\{1,2,\ldots,n\}$  and the action set is given by $A=\{1,2,\ldots,d\}$.
 For simplicity, we assume that all actions are feasible in all states.
 The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$.
-We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\\
+We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
+
 A policy $\mu$ specifies the action selection mechanism, and is described by the sequence $\mu=(u_1,u_2,\ldots,u_n,\ldots)$, where $u_n\colon S \ra A$ for all $n \geq 0$.
+\todoc{This is somewhat limited; normally we should allow history dependent,
+and also stochastic policies.} 
 A stationary deterministic policy (SDP) is one where $u_n\equiv u$ for all $n\geq 0$ for some $u\colon S \ra A$.
@@
 In this paper, we restrict our focus to the class $U$ of SDPs.
-Under an SDP $u$, the MDP is a Markov chain with probability transition kernel $P_u$.\\
+Under an SDP $u$, the MDP is a Markov chain with probability transition kernel $P_u$.
+
 Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
@@
 Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s))_{s\in S}\in R^n$ is called the value-function corresponding to the SDP $u$.\\
-The optimal policy $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}.
+The optimal policy $u^*$ is any policy whose value is the largest possible under any policy: 
+$J_{u^*}(s) = \max_{u\in U} J_u(s)$ for all $s\in S$. Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP \cite{Puter}.
+\todoc{A stronger definition allows any policy, including history dependent and yet the statement will hold true.}
  The optimal value-function $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.
+\todoc{Probably better to define first $J^*$ as the pointwise max and then the optimal policy's definition could use $J^*$.}
 Given an MDP, our aim is to find the optimal value function $J^*$ and the optimal policy $u^*$.
-The optimal policy and value function obey the Bellman equation (BE) as under: for all $ s \in S$,
+The optimal policy and value function obey the Bellman equation (BE): for all $ s \in S$, \todoc{Non-unique maximizers in the policy def?}
 \begin{subequations}\label{bell}
@@
 \end{subequations}
-Typically $J^*$ is computed first and $u^*$ is obtained by substituting $J^*$ in \eqref{bellpol}. The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
+If $J^*$ is computed first, then $u^*$ can be obtained by substituting $J^*$ in \eqref{bellpol}. The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
 \begin{definition}
+The Bellman operator $T: \R^n \to \R^n$ is defined by 
 \begin{align}
-(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big), 
+(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big)\,, 
 \end{align}
-where $J\in \R^n$. Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
+where $J\in \R^n$ and $J_s = J(s)$, $s\in S = \{1,\dots,n\}$.  
+Similarly one can define the Bellman operator $T_u:\R^n \to \R^n$ restricted to an SDP $u$ as follows:
 \begin{align}
-(T_uJ)(s)=\big(g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\big).
+(T_uJ)(s)=g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\,.
 \end{align}

### 2015-06-02 adp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4

@@
+%!TEX root =  autocontgrlp.tex
 \section{Approximate Dynamic Programming}
-\emph{Curse-of-Dimensionality} is a term used to denote the fact that the number of states grows exponentially in the number of state variables.
+\emph{Curse-of-dimensionality} is a term used to denote the fact that the number of states grows exponentially in the number of state variables.
+\todoc{This itself won't be a curse, would it be?
+The problem is that the computation cost also grows exponentially.
+Note that we never defined what we mean by state variables.}
 Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios.
@@
 Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.
+
 \subsection{Value-Function based ADP}
@@
 \begin{align}
-||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty.
+||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty\,.
 \end{align}
@@
 Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy.
-In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.\\
+In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.
+
 \subsection{Linear Function Approximation}
 The most widely used parameterized class to approximate the value-function is the linear function approximator (LFA).
-Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.\\
+Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.
+
 There are two important approaches to value function approximation.
@@
 Further, such policy-chattering can be demonstrated in simple examples as well \cite{dpchapter}.
-Thus, though the approximate value function obtained by solving the PBE offers guarantees for prediction it does not offer any guarantees for the control problem, a significant shortcoming of the PBE based methods.\\
+Thus, though the approximate value function obtained by solving the PBE offers guarantees for prediction it does not offer any guarantees for the control problem, a significant shortcoming of the PBE based methods.
+
 The ALP formulation \cite{ALP} on the other hand does not suffer from issues such as policy-chattering, for the simple reason that it computes $\tilde{J}$ which is an approximation to $J^*$ and a one-step greedy policy $\tilde{u}$ obtained using $\tilde{J}$.
@@
 In this paper, by providing a sound theoretical analysis of the RLP, we aim to show that RLP is a complete method that addresses both the prediction and the control problems.
-We achieve this by developing and presenting a comprehensive theoretical framework to understand the constraint reduction/approximation procedure.\\
+We achieve this by developing and presenting a comprehensive theoretical framework to understand the constraint reduction/approximation procedure.
+
 In the next section, we discuss the approximate linear programming (ALP) formulation, the basic results and present prior results in literature as well as motivate the problem that we address in this paper.

### 2015-06-02 alubp.tex
Resolving conflict marks (<<<HEAD)
Cosmetics and some comments, especially on the proof of Lemma 8.4

@@
 \begin{align}\label{alubplp}
-r_c\stackrel{\Delta}{=}\min_{r\in \chi} &c^\top \Phi r,\nn\\
-\text{s.t}\mb &W^\top E \Phi r\geq W^\top HJ, W \in \R^{nd\times m}_+ .
+r_c\stackrel{\Delta}{=} & \argmin_{r\in \chi} c^\top \Phi r,\nn\\
+& \text{s.t.}\,\,\, W^\top E \Phi r\geq W^\top HJ,\,\, W \in \R^{nd\times m}_+ .
 \end{align}
@@
 \begin{lemma}\label{relation2}
-The unique fixed point $\hv$ of the iteration in \eqref{apvi} and the solution $\hj$ of the GRLP obey $\hj\geq\hv$.
+The unique fixed point $\hv$ of the iteration in \eqref{apvi} and the solution $\hj$ of the GRLP \eqref{grlp} obey $\hj\geq\hv$.
 \end{lemma}
 \begin{proof}
-Follows in a similar manner as the proof of Lemma~\ref{relation1}.
+The proof follows in a similar manner as the proof of Lemma~\ref{relation1}.
 To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively.
+Fix some other $c\in [0,1]^n$, $\sum_i c(i)=1$.
 Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. 
-It is clear from the definition of $V_0$ that $\hj(i)\geq\Phi r_i(i)\geq V_0(i)$, $i=1,\ldots,n$.
-Also from the monotone property of $T$ we have
-\begin{align}
-\Phi r_i&\geq V_0,\nn\\
-H\Phi r_i&\geq H V_0,\mbox{we also have}\nn\\
-E\Phi r_i\geq H\Phi r_i&\geq HV_0,\mb\text{by taking component-wise minimum},\nn\\
-E V_0\geq H V_0.
-\end{align}
+It is clear from the definition of $V_0$ that $\hj(i),(\Phi r_j)(i)\geq(\Phi r_i)(i)$, $i=1,\ldots,n$.
+In particular, it follows that $V_0(i) =( \Phi r_i)(i)$ and so
+$\Phi r_i \geq V_0$.
+From the monotone property of $T$ (viz. $H$) we have 
+$H\Phi r_i\geq H V_0$ and also, by minimizing component-wise
+$E\Phi r_i\geq H\Phi r_i\geq HV_0$. Thus,
+$E V_0\geq H V_0$. 
+\todoc[inline]{I lost why this was needed.
+I think the proof would be much easier to understand if we introduced $r_{c,J} = \argmin_{r} \{ c^\top \Phi r \,|\, W^\top E \Phi r \ge W^\top H J\}$.
+We could start by saying we need $V_1\le V_0 \le \hj$ because then Lemma~\ref{tgmonotone} will give the desired result.
+Next, $V_0\le \hj$ holds because on the one hand, $\hj(i) \ge (\Phi r_i)(i)$ for any $i$, while on the other hand,
+$(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $i,j$, hence $V_0(i)  = (\Phi r_i)(i)$. 
+Now, for showing that $V_1 \le V_0$ holds, fix any $i$.
+We need to show that $(\hg V_0)(i) = \min_j (\Phi r_{e_j,V_0})(i) = (\Phi r_{e_i,V_0})(i)$ is less than $V_0(i)$.
+By the definition of $r_{e_j,V_0}$ we know that $(\Phi r_{e_i,V_0})(i) \le (\Phi r)(i)$
+holds for any $r$ such that $W^\top E \Phi r \ge W^\top H V_0$. Thus, it suffices to show that $r_i$ satisfies this latter inequality,
+i.e., $W^\top E \Phi r_i \ge W^\top H V_0$. For this, it clearly sufficient if $\Phi r_i \ge V_0$. This however directly follows 
+from the definition of $V_0$.
+}
 Since $V_1=\hg V_0$, from the definition of $\hg$ in \eqref{gamdef} and the construction of $V_0$, we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb n\geq 0$.
@@
 \begin{corollary}\label{cmt1}
-Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_\infty$, then
+Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\argmin_{r\in \R^k}||J^*-\Phi r||_\infty$, then
 \begin{align}

### 2015-06-02 basic.tex
small edits, mostly typography + some comments
Cosmetics and some comments, especially on the proof of Lemma 8.4

@@
-\small
 \begin{align}\label{mdplp}
-\min_{J\in \R^n} &c^\top J\nn\\
-\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall s\in S, a \in A,
+\begin{split}
+\min_{J\in \R^n} \,&c^\top J\\
+\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb s\in S, a \in A,
+\end{split}
 \end{align}
-\normalsize
 where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 
-Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.\\
-While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.\\
+Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.
+
+While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.

### 2015-06-02 grlp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4

--- 2015-05-27 grlp.tex
@@
 \begin{align}\label{grlp}
-\min_{r\in \chi} &c^\top \Phi r,\nn\\
+\begin{split}
+\min_{r\in \chi}\, &c^\top \Phi r,\\
 \text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
+\end{split}
 \end{align}
-where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$.
+where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$. \todoc{Is not $\hj\in \R^n$?
+Moreover, later often $\chi$ is not taken into account. 
+Also, the role of $\chi$ is never explained. Do we want to keep $\chi$ or maybe we should just remove it?
+Further, $\hj$ is not really well defined. We need to defined $r_c$ and then set $\hj = \Phi r_c$.
+}
 Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP.

### 2015-06-02 improv.tex
small edits, mostly typography + some comments
Cosmetics and some comments, especially on the proof of Lemma 8.4

@@
+%!TEX root =  autocontgrlp.tex
 \section{Improved Bounds}\label{sec:improv}
@@
 \begin{lemma}\label{bestbndmn}
-Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
+Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\argmin_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
 \begin{align}
@@
 \begin{lemma}\label{cmt1mn}
-Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
+Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
 \begin{align}
@@
 \end{proof}\\
-We now recall Lemma~$4.3$ of \cite{ALP}.
+We now recall Lemma~$4.5$ of \cite{ALP}. \todoc{You had 4.3 here, but in the official journal version this seems to be Lemma 5 in Section 4.}
 \begin{lemma}\label{restate}
@@
 \begin{align}
-\Phi r'=\Phi r+||J^*-\Phi r||_{\mn}(\frac{1+\beta_{\psi}}{1-\beta_{\psi}})\psi.
+\Phi r'=\Phi r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, \psi.
 \end{align}

### 2015-06-02 mdp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4

@@
 \begin{align}\label{subpol}
-\tilde{u}(s)=\underset{a \in A}{\arg\max}(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')).
+\tilde{u}(s)=\underset{a \in A}{\argmax} \, \big(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')\big)\,.
 \end{align}
 \end{definition}
+We also define the Bellman operator $H$ for action values  \cite{BertB}: \todoc{$Q$-Bellman is a bad name.}
 \begin{definition}
-We also define the $Q$-Bellman operator \cite{BertB} $H$. Given any $J\in \R^n$ we have,
-
+Let $H: \R^n \to \R^{nd}$ be defined as follows: For $J\in \R^n$,
 \begin{align}
 HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd},\mbox{where}\nn\\
-(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A,
+(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A.
 \end{align}
@@
 \begin{align}\label{mdplp}
-\min_{J\in \R^n} &c^\top J\nn\\
+\begin{split}
+\min_{J\in \R^n}\, &c^\top J\\
 \text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \qquad s\in S, a \in A,
+\end{split}
 \end{align}

### 2015-06-05 intro.tex
modified the introduction

@@
 The problem of \emph{prediction} deals with computing the value-function $J_u$(a mapping from state space to reals\footnote{Also known as reward/cost-to-go function.}) which specifies the value of each state under a given policy $u$.
-In order to solve an MDP it is necessary to solve the problem of prediction as well as the problem of control.\todoc{Do we have a source to cite here?
+\todoc{How is the MDP given?
+If it is given as a list of values, just reading the values may take too much time.
+Or we assume sparsity?
+Or we assume that one can query the next state distribution at any state-action?
+These yield to different models.
+We should specify which one we work with (presumably the sparse is the easiest).
+}Ideally, we are be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$.
+The Bellman equation (BE) relates these quantities and in particular $u^*$ can be obtained as a `greedy/one-step look ahead' policy by substituting $J^*$ in the BE.
+Conventional solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming can compute exact values of $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation.
+By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems.
+However, in the case of MDPs with large number of states, computing $u^*$ and $J^*$ using the exact methods is infeasible.
+\todoc{Do we have a source to cite here?
 What does it mean to solve an MDP anyways?
@@
 
-Given an MDP,\todoc{How is the MDP given? If it is given as a list of values, just reading the values may take too much time.
-Or we assume sparsity?
-Or we assume that one can query the next state distribution at any state-action?
-These yield to different models.
-We should specify which one we work with (presumably the sparse is the easiest).
-} ideally, we would be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$.
-The Bellman equation (BE) relates these quantities.
-Conventional solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming can compute exact values of $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation.
-By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems.
-However, in most practical problems the size of the state space grows exponentially in the number of state variables, making the computation of $u^*$ and $J^*$ intractable using the exact methods.
-
 \emph{Approximate dynamic programming} (ADP) \cite{dpchapter,powell} refers to a gamut of approximate solution methods to MDPs with large number of states.
-In order to reduce the computational effort, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy and restricting their search space to the chosen parameterized class.
-Thus, instead of computing exact values of $u^*$ and $J^*$, ADP methods only compute an approximate value function $\tilde{J}$ and a sub-optimal policy $\tilde{u}$.
-The quality of the ADP method is measured by the error $||J^*-\tilde{J}||$, in approximating the value function and the loss in performance due to the sub-optimal policy $||J^*-J_{\tilde{u}}||$, measured with respect to the optimal policy.
-Of the two error terms, $||J^*-J_{\tu}||$ is more important if we are interested in the problem of finding a useful policy.
-In the context of ADP, the prediction and control problems are said to be addressed when the errors $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$ can be bounded so that the loss in performance due to the approximation can be quantified.
-\todoc{I don't understand why one should care about  approximating $J^*$ at all.}
-
-Value-function-only\footnote{Since this paper is concerned with results related to the approximate linear programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods approximate the value function and use it to obtain a one-step look ahead policy by making use of the Bellman equation.
-Most widely used parameterization to approximate the value function is the \emph{linear function approximator} (LFA).
-Methods employing LFA approximate the value function as $J_u\approx\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learnt.
-Dimensionality reduction (in terms of the number of unknowns) is achieved by choosing fewer number of basis functions compared to the number of states.
+Value-function-only\footnote{Since this paper is concerned with results related to the approximate linear programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods compute an approximate value function and use it to obtain a one-step look ahead policy by making use of BE.
+In order to reduce the computational effort, the approximate value function is restricted to a chosen parametrized class of functions.
+The most widely used parametrization to approximate the value function is the \emph{linear function approximator} (LFA).
+Methods employing LFA approximate the value function as $\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learned.
+Computational advantage (in terms of the number of unknowns) is achieved by choosing fewer number of basis functions compared to the number of states.
+Once the set of basis function is chosen, the way to compute $r^*$ varies across the different ADP methods.\todoc{I don't understand why one should care about  approximating $J^*$ at all.}
 
@@
 Due to this norm mismatch, policy improvement cannot be guaranteed and \emph{policy-chattering} (policy-oscillations) can occur in practice \cite{dpchapter}.
-As a result, the performance loss is difficult to control and existing result that control this loss are proven under restrictive conditions \cite[e.g.,][]{anszemu:mlj07,FaMuSz10}.
+As a result, the performance loss is difficult to control and existing result that control this loss are proven under restrictive conditions \cite{anszemu:mlj07,FaMuSz10}.
 
-The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy.
+The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy $\tilde{u}$.
 Since ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, there is no issue of policy-chattering.
-The ALP formulation also provides theoretical performance guarantees, i.e., both error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$ can be bounded.
-This makes ALP an attractive method since it addresses both the prediction and control problems.
+The ALP formulation also provides theoretical performance guarantees, i.e., the prediction error $||J^*-\tilde{J}||$ and the control error\footnote{loss in performance due to the sub-optimal policy} $||J^*-J_{\tilde{u}}||$ can be bounded.
+This makes ALP an attractive method since it addresses both the prediction and control problems by providing the error bounds.
 However, an important shortcoming of ALP is that the number of constraints are of the order of the state space, making the vanilla version of ALP intractable.

### 2015-06-05 mdp.tex
modified mdp.tex

@@
 We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
-
-A policy $\mu$ specifies the action selection mechanism, and is described by the sequence $\mu=(u_1,u_2,\ldots,u_n,\ldots)$, where $u_n\colon S \ra A$ for all $n \geq 0$.
 \todoc{This is somewhat limited; normally we should allow history dependent,
 and also stochastic policies.} 
-A stationary deterministic policy (SDP) is one where $u_n\equiv u$ for all $n\geq 0$ for some $u\colon S \ra A$.
-By abuse of notation we denote the SDP by $u$ itself instead of $\mu$.
-In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}.
-In this paper, we restrict our focus to the class $U$ of SDPs.
-Under an SDP $u$, the MDP is a Markov chain with probability transition kernel $P_u$.
-
-Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
+By a policy, we mean a sequence $\pi=\{\pi_0,\ldots,\pi_n,\ldots\}$ of functions $\pi_i, i\geq 0$ that describe the manner in which an action is picked in a given state at time $i$.
+The most general class of policies is the class of \emph{history-dependent randomized policies} denoted by $\pi$ and is defined below.
+\begin{definition}
+Let $h_n=\{s_0,\ldots,s_n, \pi_0, \ldots, \pi_{n-1}\}$ denote the \emph{history}.
+A policy $\pi$ is said to be a \emph{history-dependent randomized} policy if $\pi_n,n\geq 0$ is such that for every $s\in S$, $\pi_n(s,\cdot|h_n)$ is a probability distribution over the set of actions.
+\end{definition}
+We denote the class of policies by $\Pi$. The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$ is denoted by $J_\pi(s)$ and is defined by
 \begin{align}
-J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n), n= 0,1,\dots],\nn
+J_\pi(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|\pi],\nn
 \end{align}
-where $\alpha \in (0,1)$ is a given discount factor.
-Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s))_{s\in S}\in R^n$ is called the value-function corresponding to the SDP $u$.\\
-The optimal policy $u^*$ is any policy whose value is the largest possible under any policy: 
-$J_{u^*}(s) = \max_{u\in U} J_u(s)$ for all $s\in S$. Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP \cite{Puter}.
+where $a_{n} \sim \pi_n(s,\cdot)$ and $\alpha \in (0,1)$ is a given discount factor.
+Here $J_\pi(s)$ is known as the value of the state $s$ under the policy $\pi$, and the vector quantity $J_\pi\stackrel{\Delta}{=}(J_\pi(s))_{s\in S}\in R^n$ is called the value-function corresponding to the policy $\pi$.
+The optimal value function $J^*$ is defined as $J^*(s)\stackrel{def}{=}\underset{\pi \in \Pi}{\max} J_\pi(s)$.\par
+A stationary deterministic policy (SDP) is one where $\pi_n\equiv u$ for all $n\geq 0$ for some $u\colon S \ra A$.
+By abuse of notation we denote the SDP by $u$ itself instead of $\pi$.
+In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}, i.e., there exists an SDP $u^*$ such that $J_{u^*}(s)=J^*(s),\forall s\in S$.
+In this paper, we restrict our focus to the class $U$ of SDPs and without loss of generality we assume that there exists a unique SDP $u^*$ that is optimal.
+Under a stationary policy $u$ (or $\pi$), the MDP is a Markov chain and we denote its probability transition kernel by $P_u=(p_{u(i)}(i,j),i,j=1,\ldots,n)$ (or $P_\pi=(p_{\pi(i)}(i,j),i,j=1,\ldots,n)$, where $p_{\pi(i)}(i,j)=\sum_{a\in A}\pi(i,a)p_a(i,j)$ and $\pi(i)=(\pi(i,a), a\in A)$).\par
 \todoc{A stronger definition allows any policy, including history dependent and yet the statement will hold true.}
- The optimal value-function $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.
+%The optimal value-function $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$. 
 \todoc{Probably better to define first $J^*$ as the pointwise max and then the optimal policy's definition could use $J^*$.}
-Given an MDP, our aim is to find the optimal value function $J^*$ and the optimal policy $u^*$.
+Given an MDP, our aim is to find the optimal value function $J^*$ and the optimal policy SDP $u^*$.
 The optimal policy and value function obey the Bellman equation (BE): for all $ s \in S$, \todoc{Non-unique maximizers in the policy def?}
@@
 We also define the Bellman operator $H$ for action values  \cite{BertB}: \todoc{$Q$-Bellman is a bad name.}
-\begin{definition}
+\begin{definition}\label{bellactval}
 Let $H: \R^n \to \R^{nd}$ be defined as follows: For $J\in \R^n$,
@@
 \end{lemma}
-Note that Lemmas~\ref{maxnorm}-\ref{shift} also hold for the $Q$-Bellman operator $H$.
+Note that Lemmas~\ref{maxnorm}-\ref{shift} also hold for the Bellman operator $H$ defined for the action values in Definition~\ref{bellactval}.\par
 Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}.

### 2015-06-05 adp.tex
address some comments

@@
 \section{Approximate Dynamic Programming}
-\emph{Curse-of-dimensionality} is a term used to denote the fact that the number of states grows exponentially in the number of state variables.
+\emph{Curse-of-dimensionality} is a term used to denote the fact that the number of states and computational costs grow exponentially in the dimensions of the state space.
 \todoc{This itself won't be a curse, would it be?
@@
 Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$.
-In order to tackle the curse, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy.
+In order to tackle the curse, ADP methods resort to dimensionality reduction by parametrizing the value function and/or the policy.
 Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.
@@
 \subsection{Value-Function based ADP}
-In the value-function based ADP schemes a parameterized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parameterized class.
+In the value-function based ADP schemes a parametrized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parametrized class.
 Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
@@
 \subsection{Linear Function Approximation}
-The most widely used parameterized class to approximate the value-function is the linear function approximator (LFA).
+The most widely used parametrized class to approximate the value-function is the linear function approximator (LFA).
 Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.

### 2015-06-05 alubp.tex
address some comments

@@
 \begin{align}\label{tgamdef}
-(\hg J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb i=1,\ldots,n,
+(\hg J)(i)\stackrel{\Delta}{=}(\Phi r_{e_i,J})(i), \mb i=1,\ldots,n,
 \end{align}
@@
 \begin{align}\label{alubplp}
-r_c\stackrel{\Delta}{=} & \argmin_{r\in \chi} c^\top \Phi r,\nn\\
+r_{c,J}\stackrel{\Delta}{=} & \underset{r\in \N}{\argmin}\mb c^\top \Phi r,\nn\\
 & \text{s.t.}\,\,\, W^\top E \Phi r\geq W^\top HJ,\,\, W \in \R^{nd\times m}_+ .
@@
 Fix some other $c\in [0,1]^n$, $\sum_i c(i)=1$.
-Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. 
+Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$.\par
+We need to show $V_1\le V_0 \le \hj$ and then the desired result follows from Lemma~\ref{tgmonotone}.
+Since $(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $1\leq i,j\leq n$ we have $V_0(i)  = (\Phi r_i)(i)$.
+Also, since $\hj(i) \ge (\Phi r_i)(i),1\leq i \leq n$ it follows that $\hj\geq V_0$.
+Now, for showing that $V_1 \le V_0$ holds, fix any $i$.
+We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi r_{e_i,V_0})(i) \leq V_0(i)$.
+By the definition of $r_{e_i,V_0}$ we know that $(\Phi r_{e_i,V_0})(i) \le (\Phi r)(i)$
+holds for any $r$ such that $W^\top E \Phi r \ge W^\top H V_0$.
+Thus, it suffices to show that $r_i$ satisfies this latter inequality, i.e., $W^\top E \Phi r_i \ge W^\top H V_0$.
+For this, it clearly sufficient if $\Phi r_i \ge V_0$.
+This however directly follows from the definition of $V_0$.
+\begin{comment}
 It is clear from the definition of $V_0$ that $\hj(i),(\Phi r_j)(i)\geq(\Phi r_i)(i)$, $i=1,\ldots,n$.
@@
 So it follows that $\hj\geq V_0\geq V_1\ldots\geq \hv$.
+\end{comment}
 \end{proof}
@@
 \begin{align}
-||J^*-\hv||_\infty&\leq ||J^*-V_0+V_0-V_1+V_1\ldots-\hv||_\infty\nn\\
-&\leq ||J^*-V_0||_\infty+||V_0-V_1||_\infty+||V_1-V_2||_\infty+\ldots\nn\\
-&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\
-&\leq (\epsilon+\beta)+\alpha(\epsilon+\beta)+\ldots\nn\\
-&=\frac{\epsilon+\beta}{1-\alpha}.
+||J^*-\hv||\leq ||J^*-\hg J^*||+||\hg J^*-\hg \hv||\leq ||J^*-\hg J^*||+\alpha || J^*- \hv||
+%||J^*-\hv||_\infty&\leq ||J^*-V_0+V_0-V_1+V_1\ldots-\hv||_\infty\nn\\
+%&\leq ||J^*-V_0||_\infty+||V_0-V_1||_\infty+||V_1-V_2||_\infty+\ldots\nn\\
+%&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\
+%&\leq (\epsilon+\beta)+\alpha(\epsilon+\beta)+\ldots\nn\\
+%&=\frac{\epsilon+\beta}{1-\alpha}.
 \end{align}

### 2015-06-05 constsamp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4
address some comments

@@
+%!TEX root =  autocontgrlp.tex
 \section{Constraint sampling}
@@
 The reduced linear program is then given by
-\small
 \begin{align}\label{rlp}
-\min_{J\in \R^n} &c^\top J\nn\\
-\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall (s,a) \in \I,
+\begin{split}
+\min_{J\in \R^n}\, &c^\top J\\
+\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb (s,a) \in \I,
+\end{split}
 \end{align}
-\normalsize
 where $\I$ is the index set containing the $m$ sampled state-action pairs. Using the index set $\I$ we define an $nd\times m$ matrix $\M$, called the constraint sampling matrix as below.
 \begin{definition}\label{csampmat}
-Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i\stackrel{\Delta}{=}s_i+(a_i-1)\times n,\forall i=1,\ldots,m$.
+Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i\stackrel{\Delta}{=}s_i+(a_i-1)\times n$, $i=1,\ldots,m$.
 Then the constraint sampling matrix associated with the index set $\I$ is given by
 \begin{align}
-\M(i,j)&=1, \mb\text{if}\mb q_i=j\nn\\
-&=0, \mb\text{otherwise}.
+\M(i,j)
+=
+\begin{cases}
+1, & \text{ if } q_i = j;\\
+0, & \text{ otherwise }.
+\end{cases}
 \end{align}
@@
 \begin{align}\label{rlpshort}
-\min_{r\in \N} &c^\top \Phi r\nn\\
+\begin{split}
+\min_{r\in \N}\, &c^\top \Phi r\\
 \text{s.t}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r,
+\end{split}
 \end{align}
 where $\M$ is a constraint sampling matrix as in Definition~\ref{csampmat} and $\N\subset \R^k$ is a bounded set such that $\tr \in \N$.
+The purpose of $\N$ is to ensure that the solution to the RLP is always bounded\todoc{explained the role of $\N$ and used the same in the definitions of LUB and ALUB operators}.
 Note that the feasible set of the RLP is a superset of the feasible set of the ALP.\\
@@
 \begin{align}
-m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\big).
+m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\left(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\right).
 \end{align}

### 2015-06-05 grlp.tex
address some comments

@@
 \begin{split}
-\min_{r\in \chi}\, &c^\top \Phi r,\\
+\underset{r\in \N}{\min}\, &c^\top \Phi r,\\
 \text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
@@
 \end{align}
-where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$. \todoc{Is not $\hj\in \R^n$?
+where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\N \subset \R^k$ is any bounded set such that $\tilde{r}_c \in \N$. \todoc{Is not $\hj\in \R^n$?
 Moreover, later often $\chi$ is not taken into account. 
@@
 }
+\todoc{Changed the definition and using $\N$ that was used in the definition of RLP.}
 Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP.
@@
 Also note that an RLP is trivially a GRLP as well.
-Unless specified otherwise we use $\hr$ to denote the solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
+Unless specified otherwise we use $\hr$ to denote any solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
 Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column).
@@
 \end{assumption}
+\begin{comment}
 The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
+\end{comment}
 \input{cartoon}

### 2015-06-05 lp.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4
address some comments

@@
 The LP formulation in \eqref{mdplp} can be represented in short as,
-\begin{align}\label{mdplpshort}
-\min_{J\in \R^n} &c^\top J\nn\\
-\text{s.t}\mb &J\geq T J,\\
-\textbf{or}\nn\\
+\begin{align}
+\begin{split}
+\label{mdplpshort}
+\min_{J\in \R^n}\, &c^\top J\\
+\text{s.t}\mb &J\geq T J,
+\end{split}
+\end{align}
+or 
+%\text{ or }\nn\\
+\begin{align}
+\begin{split}
 \label{shortalter}
-\min_{J\in \R^n} &c^\top J\nn\\
-\text{s.t}\mb &EJ\geq H J,\\
+\min_{J\in \R^n} \,&c^\top J\\
+\text{s.t}\mb &EJ\geq H J,
+\end{split}
 \end{align}
@@
 \begin{align}\label{alp}
-\min_{r\in \R^k} &c^\top \Phi r\nn\\
+\begin{split}
+\min_{r\in \R^k}\, &c^\top \Phi r\\
 \text{s.t}\mb &\Phi r\geq T \Phi r.
+\end{split}
 \end{align}
-Unless specified otherwise we use $\tr$ to denote the solution to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function.
+Unless specified otherwise we use $\tr$ to denote any solution\todoc{instead of saying the solution} to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function.
 We now state the assumptions and definitions used for the rest of the paper.
@@
 Given a function $\chi\colon S\ra \R^+$ we define the quantity $\beta_{\chi}$ as
-\begin{align}
-\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}.
-\end{align}
+\begin{align*}
+\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}\,.
+\end{align*}
 \end{definition}
@@
 \begin{definition}\label{modlone}
-The modified $L_1$-norm is defined as \todoc{modified $\Rightarrow$ weighted?}
-\begin{align}
+The weighted $L_1$-norm is defined as \todoc{modified $\Rightarrow$ weighted?}
+\begin{align*}
 ||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|,
-\end{align}
+\end{align*}
 where $c$ obeys Assumption~\ref{probdist}.
@@
 \begin{definition}\label{modnorm}
-The modified $L_\infty$-norm is defined as follows:  \todoc{modified $\Rightarrow$ weighted?
+The weighted $L_\infty$-norm is defined as follows:  \todoc{modified $\Rightarrow$ weighted?
 Also, the convention in math is to divide in the case of the $L_{\infty}$ norm.
 Not a high priority to change this, but maybe it would be good to do this in the longer term.}
-\begin{align}
-||J||_{\infty,\rho}=\max_{s \in S} \rho(s) |J(s)|,
-\end{align}
-where $\rho \colon \S \ra \R^+$, $J\in \R^n$.
+\begin{align*}
+||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)},
+\end{align*}
+where $\rho \colon \S \ra \R^+$ is the weighing function and $J\in \R^n$.
 \end{definition}
@@
 Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be a Lyapunov function and $c$ be a distribution as in \eqref{probdist}, then 
-\begin{align}
+\begin{align*}
 ||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}.
-\end{align}
+\end{align*}
 \end{theorem}
@@
 Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP, then 
-\begin{align}
+\begin{align*}
 ||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'},
-\end{align}
+\end{align*}
 where $c'=(1-\alpha)c^\top(I-\alpha P_{\tu})^{-1}$.

### 2015-06-05 lubp.tex
removed vspaces
Resolving conflict marks (<<<HEAD)
Cosmetics and some comments, especially on the proof of Lemma 8.4
address some comments

@@
 \begin{align}\label{gamdef}
-(\Gamma J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i),\quad i=1,\ldots,n,
+(\Gamma J)(i)\stackrel{\Delta}{=}(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n,
 \end{align}
@@
 \begin{align}\label{lubplp}
- r_c   \stackrel{\Delta}{=}& \argmin_{r\in \chi} c^\top \Phi r,\nn\\
+ r_{c,J}   \stackrel{\Delta}{=}& \underset{r\in \N}{\argmin} \mbox{ } c^\top \Phi r,\nn\\
  \text{s.t}& \mb \Phi r\geq  TJ.
@@
 \end{definition}
-Note that $r_{e_j}$ depends on $J$, but this dependence is suppressed to reduce clutter. 
-\vspace{-10pt}
+%Note that $r_{e_j}$ depends on $J$, but this dependence is suppressed to reduce clutter. 
 \begin{remark}
-\mb\\
-\vspace{-10pt}
 \begin{enumerate}
@@
 \item Even though $\Gamma J$ does not belong to the span of $\Phi$, $\Gamma J$ collates the various best upper bounds that can be obtained via the linear program in \eqref{lubplp}.
+\begin{comment}
 \item The LUB operator $\Gamma$ in \eqref{gamdef} bears close similarity to the ALP in \eqref{alp}.
 In fact, it is not hard to observe that $(\Gamma J)(i) = (\Phi r_{e_i})(i)$ for any $1\le i \le n$; the reason $\Gamma$ is defined the way it is so that this resembles to \eqref{alp} will be clear. 
+\end{comment}
 \todoc{In fact, I would prefer the simpler definition without the $\min$ and then changing this remark.}
@@
 As mentioned earlier, the error analysis depends on two $\max$-norm contraction operators the first of which is $\Gamma$.
-The important result of this section is Theorem~\ref{fxpres} and it relates the fixed point $\tilde{V}$ of $\Gamma$ to $J^*$.
-\todoc{Poor choice of symbols: $\tilde{V}$ is the fixed point of $\Gamma$ and $\hat{V}$ will be the fixed point of $\tilde{\Gamma}$? Hmm.. Not a high priority to change it, but still..}
+The important result of this section is Theorem~\ref{fxpres} and it relates the fixed point $\tv$ of $\Gamma$ to $J^*$.
+\todoc{Poor choice of symbols: $\tv$ is the fixed point of $\Gamma$ and $\hat{V}$ will be the fixed point of $\tilde{\Gamma}$? Hmm.. Not a high priority to change it, but still..}
 \begin{lemma}\label{bestbnd}
-Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_\infty$, then 
+Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\argmin_{r\in R^k}||J^*-\Phi r||_\infty$, then 
 \begin{align}
@@
 \begin{proof}
-Choose any $i\in \{1,\ldots,n\}$ and let $r^1_{e_i}$ and $r^2_{e_i}$ be solutions to the linear program in \eqref{lubplp} for $c=e_i$ with $J=J_1$ and $J=J_2$ respectively.
-Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$ and $e_i^\top \Phi r^1_{e_i} \geq e_i^\top \Phi r^2_{e_i}$, i.e., $(\Phi r^1_{e_i})(i)\geq (\Phi r^2_{e_i})(i)$.
-The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i})(i)$, $J\in \R^n$, and our choice of $i$ was arbitrary.
+Choose any $i\in \{1,\ldots,n\}$ and let $r_{e_i,J_1}$ and $r_{e_i,J_2}$ be solutions to the linear program in \eqref{lubplp} for $c=e_i$ with $J=J_1$ and $J=J_2$ respectively.
+Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$ and $e_i^\top \Phi r_{e_i,J_1} \geq e_i^\top \Phi r_{e_i,J_2}$, i.e., $(\Phi r_{e_i,J_1})(i)\geq (\Phi r_{e_i,J_2})(i)$.
+The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i,J})(i)$, $J\in \R^n$, and our choice of $i$ was arbitrary.
 \end{proof}
@@
 We know that $\Phi r_{e_i}\geq T \tv$, for all $i=1,\ldots, n$.
-The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_{e_j})(i)$.
+The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=(\Phi r_{e_i,V})(i)$.
 \end{proof}

### 2015-06-05 resdisc.tex
address some comments

@@
 The entries of the GRLP on the other hand are of the order of $m\times k$, \todoc{$\times d$?} where the constants $m$ and $k$ are chosen to be much smaller than the number of states.
-We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, while computing the exact solution took about $20$ minutes.
+We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, the ALP with took about $0.7$ seconds, while computing the exact solution took about $20$ minutes.
 \todoc{Sorry for the many questions, but did you also run ALP ($k=4$) with no constraint aggregation?}

### 2015-06-09 intro.tex
Text tuning

@@
 \section{Introduction}\label{intro}
-Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs).
-A policy $u$, is a mapping from state space to action space and it specifies the action selection mechanism.
-The problem of \emph{control} requires coming up with good policies and for which one needs to \emph{predict} the behavior of individual policies.
-The problem of \emph{prediction} deals with computing the value-function $J_u$(a mapping from state space to reals\footnote{Also known as reward/cost-to-go function.}) which specifies the value of each state under a given policy $u$.
-\todoc{How is the MDP given?
-If it is given as a list of values, just reading the values may take too much time.
+Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs), where the problem is to find a policy $u$, mapping states to actions, so as to maximize long term expected cumulated discounted reward.
+The problem of \emph{control} requires coming up with good policies.
+% and for which one needs to \emph{predict} the behavior of individual policies. 
+	\todoc{I removed the second part of the sentence; it seemed that it was not adding anything.}
+The problem of \emph{prediction} deals with computing the value-function $J_u$ 
+	(a mapping from the state space to the set of reals%
+	\footnote{Also known as reward/cost-to-go function.}), 
+	which gives the value of each state under a given policy $u$. 
+\todoc{How is the MDP given? If it is given as a list of values, just reading the values may take too much time.
 Or we assume sparsity?
@@
 We should specify which one we work with (presumably the sparse is the easiest).
-}Ideally, we are be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$.
-The Bellman equation (BE) relates these quantities and in particular $u^*$ can be obtained as a `greedy/one-step look ahead' policy by substituting $J^*$ in the BE.
-Conventional solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming can compute exact values of $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation.
+}
+\todoc{Why do we discuss control and prediction?}
+The optimal value function $J^*$ collects the highest values achievable in each state.
+A policy $u^*$ is optimal if it achieves the optimal value in each state, i.e., if $J^* = J_{u^*}$.
+``Exact'' solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming 
+compute $J^*$, the optimal value function, 
+which can then be plugged in the Bellman equation (BE) to get the optimal policy $u^*$.
+%Ideally, we would be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$. 
+%Under reasonable conditions, the optimal value function is known to be the fixed point of the (so-called) Bellman equation (BE),
+%in which case $u^*$ can be obtained as a `greedy/one-step look ahead' policy by substituting $J^*$ in the BE. 
+%``Exact'' solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming 
+%compute $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation. 
 By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems. 
+\todoc{So is the prediction problem to predict $J_{u^*}$?}
 However, in the case of MDPs with large number of states, computing $u^*$ and $J^*$ using the exact methods is infeasible.
@@
 
-\emph{Approximate dynamic programming} (ADP) \cite{dpchapter,powell} refers to a gamut of approximate solution methods to MDPs with large number of states.
-Value-function-only\footnote{Since this paper is concerned with results related to the approximate linear programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods compute an approximate value function and use it to obtain a one-step look ahead policy by making use of BE.
-In order to reduce the computational effort, the approximate value function is restricted to a chosen parametrized class of functions.
-The most widely used parametrization to approximate the value function is the \emph{linear function approximator} (LFA).
-Methods employing LFA approximate the value function as $\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learned.
-Computational advantage (in terms of the number of unknowns) is achieved by choosing fewer number of basis functions compared to the number of states.
-Once the set of basis function is chosen, the way to compute $r^*$ varies across the different ADP methods.\todoc{I don't understand why one should care about  approximating $J^*$ at all.}
+\emph{Approximate dynamic programming} (ADP) \cite{dpchapter,powell} 
+	refers to a gamut of approximate solution methods to MDPs with large number of states
+	that build on dynamic programming.
+The key idea in value-function-only%
+\footnote{
+		Since this paper is concerned with results related to the approximate linear programming formulation we do not 
+		discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} 
+	(or \emph{critic-only}) ADP methods is to employ a parametrized class of functions
+	to approximate the value functions that occur in the iterations of dynamic programming.
+The most widely used parametrization is linear.
+Methods employing such a \emph{linear function approximator} (LFA) 
+	approximate the value function as $\Phi r^*$, 
+	where $\Phi$ is a feature matrix whose columns are the basis functions 
+	and $r^*$ is a weight vector to be learned. 
+Computational advantage (in terms of the number of unknowns) 
+	is achieved by choosing fewer number of basis functions compared to the number of states. 
+Once the set of basis function is chosen, 
+	the way to compute $r^*$ varies across the different ADP methods.
 
-A host of value-function-based ADP methods solve the \emph{projected Bellman equation} (PBE) which is obtained by including the least squares projection operator in the BE so as to project quantities onto the lower dimensional subspace.
-A limitation of using the least squares projection operator is that it reduces the prediction error $L_2$-norm and cannot ensure policy improvement which requires prediction error to be minimum in the $L_\infty$-norm.
-Due to this norm mismatch, policy improvement cannot be guaranteed and \emph{policy-chattering} (policy-oscillations) can occur in practice \cite{dpchapter}.
-As a result, the performance loss is difficult to control and existing result that control this loss are proven under restrictive conditions \cite{anszemu:mlj07,FaMuSz10}.
+A host of value-function-based ADP methods solve 
+	the \emph{projected Bellman equation} (PBE), 
+	which is obtained by including the least squares projection operator in the BE 
+	so as to project quantities onto the lower dimensional subspace. 
+A limitation of using the least squares projection operator is that 
+	it reduces the prediction error $L_2$-norm and cannot in general ensure monotonous policy improvement 
+	which requires the prediction error to be minimum in the $L_\infty$-norm. 
+Due to this norm mismatch, monotonous policy improvement cannot be guaranteed 
+	and \emph{policy-chattering} (policy-oscillations) can occur in practice \cite{dpchapter}. 
+As a result, the performance loss is difficult to control unless 
+	one is willing to assume some extra technical conditions which may be difficult to guarantee in practice 
+	\cite{anszemu:mlj07,FaMuSz10}.
 
-The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy $\tilde{u}$.
-Since ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, there is no issue of policy-chattering.
-The ALP formulation also provides theoretical performance guarantees, i.e., the prediction error $||J^*-\tilde{J}||$ and the control error\footnote{loss in performance due to the sub-optimal policy} $||J^*-J_{\tilde{u}}||$ can be bounded.
-This makes ALP an attractive method since it addresses both the prediction and control problems by providing the error bounds.
-However, an important shortcoming of ALP is that the number of constraints are of the order of the state space, making the vanilla version of ALP intractable.
+The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} host of methods 
+	also employs LFA. 
+However, ALP solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, 
+	and computes a one-step greedy policy $\tilde{u}$. 
+Since ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, 
+	there is no issue of policy-chattering. 
+The ALP formulation also provides theoretical performance guarantees, 
+	i.e., the prediction error $||J^*-\tilde{J}||$ and the control error%
+	\footnote{That is, the loss in performance due to the sub-optimal policy} 
+	$||J^*-J_{\tilde{u}}||$ can be bounded. 
+This makes ALP an attractive method since it addresses both the prediction 
+	and control problems by providing the error bounds. 
+However, a critical shortcoming of ALP is 
+	that the number of constraints are of the order of the state space, 
+	making, in the lack of extra structure, 
+	\todoc{I added this as sometimes one can solve linear programs with exponentially many constraints in polynomial time.}
+	the vanilla version of ALP intractable.
 
-One proposal in the literature to overcome this hurdle is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP).
-The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} in various domains such as Tetris and in network of queues.
-However, the theoretical results are available only for a specific RLP formulated under idealized conditions \cite{CS}.
-Thus, there is a gap in the theoretical understanding of RLP and constraint reduction/approximation.
-Our aim in this paper is to fill this gap by providing theoretical guarantees which will make the RLP a complete ADP method that addresses both the prediction and the control problems.
+One proposal in the literature to overcome this hurdle is 
+	to employ a procedure known as constraint sampling, 
+	wherein a subset of the original constraints of the ALP 
+	are sampled to formulate a \emph{reduced linear program} (RLP). 
+The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} 
+	in various domains such as Tetris and in network of queues. 
+However, theoretical results are available only for a specific RLP 
+	formulated under idealized conditions \cite{CS}. 
+Thus, there is a gap in the theoretical understanding of RLP 
+	and constraint reduction/approximation. 
+Our aim in this paper is to fill this gap by providing theoretical guarantees 
+	which will make the RLP a complete ADP method that addresses 
+	both the prediction and the control problems. \todoc{Why is ALP and ADP method? Where is the dynamic programming?}
 
-In particular, in this paper we develop a novel theoretical framework to study a generalized constraint reduction technique namely \emph{generalized reduced linear program} (GRLP) and present its error analysis.
+In particular, in this paper we develop a novel theoretical framework 
+	to study a generalized constraint reduction technique 
+	namely \emph{generalized reduced linear program} (GRLP) and present its error analysis. 
 	The salient aspects of our contribution are listed below:
+%
 \begin{enumerate}
@@
 The GRLP serves as a framework to analyze error due to constraint reduction and linear constraint approximation.
+\todoc{Give theorem numbers?}
 \item \textbf{Error Analysis:}
@@
 		while the term $c_2$ is the additional error introduced due to the constraint approximation.  
-		\item We derive a greedy policy $\hu$ by making use of $\hj$ and bound the loss $||J^*-J_{\hu}||$. 
-		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a modified $L_\infty$-norm.
+		\item We also bound the loss $||J^*-J_{\hu}||$ of the one-step greedy policy $\hu$ based on $\hj$.
+		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a weighted $L_\infty$-norm.
 		\item Our analysis is based on two novel $\max$-norm contraction operators called the least upper bound (LUB) projection operator and the approximate least upper bound projection operator (ALUB).
@@
 	\begin{itemize}
-		\item We provide error bounds for both prediction and control errors, i.e., bound the terms $||J^*-\hj||$ and $||J^*-J_{\hu}||$ in a modified $L_\infty$-norm.
+		\item We provide error bounds for both prediction and control errors, i.e., bound the terms $||J^*-\hj||$ and $||J^*-J_{\hu}||$ in a weighted $L_\infty$-norm.
 Thus, the GRLP is a complete ADP method with performance guarantees for both the prediction as well as control problems.
-The modified $L_\infty$-norm allows us to choose the quality of approximation across various states.
+The weighted $L_\infty$-norm allows us to choose the quality of approximation across various states.
 This makes our result an important addition to the theory of ALP \cite{ALP,CS,CST,SALP}.
-		\item The structure of the error terms also reveals an important result that it is not always necessary to sample using the stationary distribution of the optimal policy.
-This throws additional light on constraint sampling by providing a better explanation for its empirical success even in those cases when sampling distributions other than the stationary distribution of the optimal policy was used.
+		\item The structure of the error terms also reveals that it is not always necessary to sample using the stationary distribution of the optimal policy.
+This throws additional light on constraint sampling by providing a better explanation for its empirical success in the more practical situations when sampling distributions other than the stationary distribution of the optimal policy was used.
 		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints.

### 2015-06-09 mdp.tex
streamlining the text
no uniqueness, def of policies updated, etc.

--- 2015-06-02 mdp.tex
@@
 We also assume that the number of actions is finite.
-Without the loss of generality, we set  $S=\{1,2,\ldots,n\}$  and the action set is given by $A=\{1,2,\ldots,d\}$.
-For simplicity, we assume that all actions are feasible in all states.
-The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$.
+Without the loss of generality, we set  $S=\{1,2,\ldots,n\}$  and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. 
+The probability transition kernel $P= (p_a)_{a\in A}$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$.
 We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
+By a policy, we mean a sequence $\pi=\{\pi_0,\ldots,\pi_n,\ldots\}$ of functions $\pi_n, n\geq 0$ 
+	that describe the manner in which an action is picked in a given state at time $n$. 
+In the most general case, $\pi_n$ maps $(S \times A)^n \times S$, i.e., 
+	histories $h_n =(s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$ 
+	of state-action sequences of length $2n+1$, to a distribution over the actions. 
+We denote the class of policies by $\Pi$. 
+The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$ is denoted by $J_\pi(s)$ and is defined by
+\begin{align}
+J_\pi(s)\stackrel{\Delta}{=}\E\left[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)\,\Large|\,\pi\right]\,,\nn
+\end{align}
+	where $a_{n} \sim \pi_n(\,\cdot\,|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$, $s_{n+1} \sim p_{a_n}(s_n,\cdot)$ 
+	and $\alpha \in (0,1)$ is a given discount factor. 
+Here $J_\pi(s)$ is known as the value of the state $s$ under the policy $\pi$, and $J_\pi:S\to \R$ is 
+ %the vector quantity $J_\pi\stackrel{\Delta}{=}(J_\pi(s))_{s\in S}\in R^n$ is 
+ called the value-function corresponding to the policy $\pi$. 
+ The optimal value function $J^*:S\to \R$ is defined as $J^*(s)\stackrel{def}{=}\underset{\pi \in \Pi}{\max} J_\pi(s)$, $s\in S$.
 
-A policy $\mu$ specifies the action selection mechanism, and is described by the sequence $\mu=(u_1,u_2,\ldots,u_n,\ldots)$, where $u_n\colon S \ra A$ for all $n \geq 0$.
-\todoc{This is somewhat limited; normally we should allow history dependent,
-and also stochastic policies.} 
-A stationary deterministic policy (SDP) is one where $u_n\equiv u$ for all $n\geq 0$ for some $u\colon S \ra A$.
-By abuse of notation we denote the SDP by $u$ itself instead of $\mu$.
-In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}.
+A stationary deterministic policy (SDP) is one where $\pi_n\equiv u$ for all $n\geq 0$ for some $u\colon S \ra A$
+in the sense that $\pi_n(a|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$ is one for $a = u(s_n)$ and is zero elsewhere.
+By abuse of notation we denote such an SDP by $u$ itself instead of $\pi$. 
+In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}, i.e., there exists an SDP $u^*$ such that $J_{u^*}(s)=J^*(s),\forall s\in S$. 
 In this paper, we restrict our focus to the class $U$ of SDPs. 
-Under an SDP $u$, the MDP is a Markov chain with probability transition kernel $P_u$.
+%	and without loss of generality 
+%	we assume that there exists a unique SDP $u^*$ that is optimal.  
+	\todoc{Do we need uniqueness? I got rid of it.}
+%Under a stationary policy $u$ (or $\pi$), 
+%	the MDP is a Markov chain and we denote its probability transition kernel 
+%	by $P_u=(p_{u(s)}(s,s'),s,s'=1,\ldots,n)$ (or $P_\pi=(p_{\pi(s)}(s,s'),s,s'=1,\ldots,n)$, 
+%	where $p_{\pi(s)}(s,s')=\sum_{a\in A}\pi(s,a)p_a(s,s')$ and $\pi(s)=(\pi(s,a), a\in A)$).
+Under a stationary deterministic policy $u$, 
+	the MDP gives rise to a Markov chain with state space $S$,
+whose  transition probability kernel we will denote
+	by $P_u=(p_{u(s)}(s,s'),s,s'=1,\ldots,n)$.  \todoc{I don't think we need stationary \emph{stochastic} policies anywhere.}
 
-Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
-\begin{align}
-J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n), n= 0,1,\dots],\nn
-\end{align}
-where $\alpha \in (0,1)$ is a given discount factor.
-Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s))_{s\in S}\in R^n$ is called the value-function corresponding to the SDP $u$.\\
-The optimal policy $u^*$ is any policy whose value is the largest possible under any policy: 
-$J_{u^*}(s) = \max_{u\in U} J_u(s)$ for all $s\in S$. Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP \cite{Puter}.
-\todoc{A stronger definition allows any policy, including history dependent and yet the statement will hold true.}
- The optimal value-function $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.
-\todoc{Probably better to define first $J^*$ as the pointwise max and then the optimal policy's definition could use $J^*$.}
-Given an MDP, our aim is to find the optimal value function $J^*$ and the optimal policy $u^*$.
-The optimal policy and value function obey the Bellman equation (BE): for all $ s \in S$, \todoc{Non-unique maximizers in the policy def?}
+Given an MDP, our aim is to find the optimal value function $J^*$ and an optimal policy SDP $u^*$. 
+Any optimal policy $u^*$ and the value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
 \begin{subequations}\label{bell}
@@
 \label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
-\label{bellpol}u^*(s)&=\arg\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big).
+\label{bellpol}u^*(s)&\in \argmax_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
 \end{align}
 \end{subequations}
-If $J^*$ is computed first, then $u^*$ can be obtained by substituting $J^*$ in \eqref{bellpol}. The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
+If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}. 
+For convenience, in what follows we identify $\R^n$ with $\R^{S}$:
+Any vector $J\in \R^n$ is viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
+The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
 \begin{definition}
@@
 \begin{align}
-(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big)\,, 
+(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big)\,,  \qquad s\in S\,,J\in \R^n\,.
 \end{align}
-where $J\in \R^n$ and $J_s = J(s)$, $s\in S = \{1,\dots,n\}$.  
-Similarly one can define the Bellman operator $T_u:\R^n \to \R^n$ restricted to an SDP $u$ as follows:
+\end{definition}
+Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
+\begin{definition}
+The Bellman operator $T_u:\R^n \to \R^n$  restricted to an SDP $u$ is defined by
 \begin{align}
-(T_uJ)(s)=g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\,.
+(T_uJ)(s)=g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\,,  \qquad s\in S\,,J\in \R^n\,.
 \end{align}
@@
 \begin{align}\label{subpol}
-\tilde{u}(s)=\underset{a \in A}{\arg\max}(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')).
+\tilde{u}(s)\in \underset{a \in A}{\argmax} \, \big(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')\big)\,.
 \end{align}
 \end{definition}
-\begin{definition}
-We also define the $Q$-Bellman operator \cite{BertB} $H$. Given any $J\in \R^n$ we have,
-
+We also define the Bellman operator $H$ for action values  \cite{BertB}: 
+\begin{definition}\label{bellactval}
+Let $H: \R^n \to \R^{nd}$ be defined as follows: For $J\in \R^n$,
 \begin{align}
-HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd},\mbox{where}\nn\\
-(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A,
+HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd}, \text{ where}\nn\\
+(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A.
 \end{align}
 \end{definition}
- We now state without proof the important properties related to the Bellman operator.
+We now state without proof the most important properties of the Bellman operator. 
 Though in these results, we make use of the Bellman operator $T$, the results also trivially hold for $T_u$ as well.
-\subsection{Properties of $T$}
+
+%\subsection{Properties of $T$}
 \begin{lemma}\label{maxnorm}
-$T$ is a $\max$-norm contraction operator, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
+$T$ is a $\max$-norm contraction operator with contraction factor $\alpha$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
 \begin{align}
@@
 \end{lemma}
-\begin{corollary}\label{uniquesol}
+\begin{lemma}\label{uniquesol} 
 $J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
-\end{corollary}
+\end{lemma}
+For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
 The Bellman operator $T$ exhibits two more important properties presented in the following lemmas (see \cite{BertB} for proofs):
 \begin{lemma}\label{monotone}
-$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_2\geq J_1$, we have $T J_2\geq T J_1$. Further, if $J\in \R^n$ is such that $J\geq TJ$, it follows that $J\geq J^*$.
+$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
+Further, if $J\in \R^n$ is such that $J\geq TJ$ then $J\geq J^*$.
 \end{lemma}
@@
 \end{lemma}
-Note that Lemmas~\ref{maxnorm}-\ref{shift} also hold for the $Q$-Bellman operator $H$.
+Note that Lemmas~\ref{maxnorm}--\ref{shift} also hold for the Bellman operator $H$ defined for the action values in Definition~\ref{bellactval}.\par
 Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}.
-The problem of \emph{control} deals with coming up with a good (and if possible the optimal) policy.
+The problem of \emph{control} deals with coming up with a good (and if possible an optimal) policy.
 Often, in order to solve the problem of \emph{control}, one needs to solve the problem of \emph{prediction}, which deals with computing the value function $J_u$ of the policy $u$.
-The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain the optimal policy $u^*$.
+The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain an optimal policy $u^*$.
 Thus, the Bellman equation is at the heart of the solution methods to MDPs.
 Any solution method to MDP is said to be complete only if it satisfactorily (with provable performance guarantees) addresses both the prediction and the control problems.
-\\
-The basic solution methods namely value iteration, policy iteration and linear programming (LP) formulation \cite{BertB} solve both the control and prediction problems.
-Of the three basic methods, in this paper, we are interested in the LP formulation given by
+\todoc{Why insist on prediction?}
+
+The basic solution methods namely value iteration, policy iteration and linear programming (LP) \cite{BertB} solve both the control and prediction problems.
+Of the three basic methods, in this paper, we focus on the LP formulation given by
 \begin{align}\label{mdplp}
-\min_{J\in \R^n} &c^\top J\nn\\
-\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \qquad s\in S, a \in A,
+\begin{split}
+\min_{J\in \R^n}\, &c^\top J\\
+\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \qquad s\in S, a \in A,
+\end{split}
 \end{align}
-where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 
-Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.\\
-While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.\\
+where $c\in \R^n_+$ is any vector whose components are all non-negative (we denote the set of non-negative reals by $\R_+$).
+One can show that $J^*$ is the solution to the linear program given by \eqref{mdplp} \cite{BertB}.
+Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.
+
+While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are intractable in the case of MDPs with a large number of states.

### 2015-06-10 adp.tex
Refining the meaning of DP, making the intro more precise

@@
 \section{Approximate Dynamic Programming}
-\emph{Curse-of-dimensionality} is a term used to denote the fact that the number of states and computational costs grow exponentially in the dimensions of the state space.
-\todoc{This itself won't be a curse, would it be?
-The problem is that the computation cost also grows exponentially.
-Note that we never defined what we mean by state variables.}
-Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios.
+In practical problems, often the states are best described as multi-dimensional tuples.
+In this context, the term \emph{curse-of-dimensionality} refers to the fact that the number of states
+	grows exponentially as a function of the number of dimensions
+	and thus solution methods whose computation cost grows at least linearly with the size of the state space
+	quickly become intractable.
+%Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. 
 Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. 
@@
 Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
-The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$.
+The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$. \todoc{Add citation.}
 \begin{lemma}\label{subopt}

### 2015-06-10 adp.tex
Increasing precision

@@
 Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
-The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$. \todoc{Add citation.}
+The following lemma,
+	bounds the degree of sub-optimality of the greedy policy $\tilde{u}$: 
+	\todoc{Is this tight? Add a note.}
 \begin{lemma}\label{subopt}
@@
 \end{lemma}
+This lemma is easy to prove and has appeared multiple times in the literature (e.g., \cite{SinghYee94}).
+
 The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm.
@@
 Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy.
-In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.
+In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are both bounded by ``small'' constants.
 
 \subsection{Linear Function Approximation}
-The most widely used parametrized class to approximate the value-function is the linear function approximator (LFA).
-Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.
+The most widely used parametrization is linear. 
+When such linear function approximators (LFAs) are employed,  
+	the value-function is approximated as $\tilde{J}=\Phi r^*$, 
+	with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is a
+	parameter to be computed.
 
-There are two important approaches to value function approximation.
+There are two widely used approaches to value function approximation. 
 Both the approaches start out with a basic solution method and appropriately introduce function approximation in it. 
@@
 A host of ADP methods are based on the PBE and have been found to be useful in practice. 
-The main application of the PBE is for approximate policy evaluation, i.e., to compute $\tilde{J}_u$, an approximation to the value function $J_u$ of policy $u$.
-Due to the mismatch in the norms, i.e, the linear least squares projection operator based on the $L_2$-norm and the $L_\infty$-norm of the Bellman operator $T$, one cannot use the PBE to obtain a direct approximation to $J^*$.
+The main application of the PBE is for approximate policy evaluation, 
+i.e., to compute $\tilde{J}_u$, an approximation to the value function $J_u$ of policy $u$. 
+Due to the mismatch in the norms, 
+	i.e, the linear least squares projection operator based on the $L_2$-norm 
+	and the $L_\infty$-norm of the Bellman operator $T$, 
+	one cannot use the PBE to obtain a direct approximation to $J^*$. 
 Thus in order to solve the problem of control, $\tilde{J}_u$ is used to compute a one-step greedy policy. 
-However, again due to the mismatch in the norms, i.e., $L_2$-norm of the linear least squares projection and the $L_\infty$ norm required for policy improvement (Lemma~\ref{subopt}), the one-step greedy policy need not necessarily be an improvement.
-This leads to a phenomenon called \emph{policy-chattering} \cite{dpchapter} where looping within of bad policies can occur.
+However, again due to the mismatch in the norms, 
+	i.e., $L_2$-norm of the linear least squares projection 
+	and the $L_\infty$ norm required for policy improvement (Lemma~\ref{subopt}), 
+	the one-step greedy policy need not necessarily be an improvement. 
+	This leads to a phenomenon called \emph{policy-chattering} \cite{dpchapter} 
+	where looping within of bad policies can occur. 
 	Further, such policy-chattering can be demonstrated in simple examples as well \cite{dpchapter}. 
-Thus, though the approximate value function obtained by solving the PBE offers guarantees for prediction it does not offer any guarantees for the control problem, a significant shortcoming of the PBE based methods.
+	Thus, though the approximate value function obtained by solving the PBE offers guarantees 
+	for prediction it does not offer any guarantees for the control problem, 
+	a significant shortcoming of the PBE based methods. 
+	\todoc{Again, this needs to be changed as there are guarantees as mentioned in the intro.}
 
-The ALP formulation \cite{ALP} on the other hand does not suffer from issues such as policy-chattering, for the simple reason that it computes $\tilde{J}$ which is an approximation to $J^*$ and a one-step greedy policy $\tilde{u}$ obtained using $\tilde{J}$.
+The ALP formulation \cite{ALP} on the other hand 
+	does not suffer from issues such as policy-chattering, 
+	for the simple reason that it computes $\tilde{J}$ 
+	which is an approximation to $J^*$ 
+	and a one-step greedy policy $\tilde{u}$ obtained using $\tilde{J}$. 
 In short, since there is only one policy that the ALP outputs there is no question of policy-chattering. 
-Further, the ALP offers performance guarantees for both the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$.
-Though the ALP is a complete method addressing both the control and prediction problems, it nevertheless suffers from an important limitation in the form of large number of constraints (as large as the size of the state space).
-This limitation has been addressed in literature by sampling only a fewer tractable constraints to formulate a reduced linear program (RLP).
-The RLP has been shown to perform well in practice \cite{ALP,CS,CST}, but theoretical performance guarantees \cite{CS} are available for a specific RLP obtained under idealized assumptions.
-In this paper, by providing a sound theoretical analysis of the RLP, we aim to show that RLP is a complete method that addresses both the prediction and the control problems.
-We achieve this by developing and presenting a comprehensive theoretical framework to understand the constraint reduction/approximation procedure.
+	\todoc{Policy chattering is annoying but the real problem is not policy chattering.
+	If all policies in the long run would be pretty good, no one would care or should care about the lack of convergence.
+	The problem is that to guarantee good performance one needs extra assumptions on the MDP,
+	which may or may not hold in a given application.
+	}
+Further, ALP offers performance guarantees 
+	for both the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$. 
+	\todoc{This is confusing. On one hand, bounding $||J^*-\tilde{J}||$ is enough based on Lemma~\ref{subopt}.
+	On the other hand, alone I don't get why anyone would care about $\norm{J^* - \tilde{J}}$?
+	Maybe to get a certificate of how well the policy will do (lower bound)? This should be explained at minimum.
+	}
+	Though the ALP is a complete method addressing 
+		both the control and prediction problems, 
+		it nevertheless suffers from an important limitation in the form of large number of constraints 
+		(as large as the size of the state space). 
+This limitation has been addressed in literature 
+	by sampling only a fewer tractable constraints to formulate a reduced linear program (RLP). 
+The RLP has been shown to perform well in practice \cite{ALP,CS,CST}, 
+	but theoretical performance guarantees \cite{CS} are available for a specific RLP obtained under idealized assumptions. 
+In this paper, by providing a sound theoretical analysis of the RLP, 
+	we aim to show that RLP is a complete method that addresses both the prediction and the control problems.
+We achieve this by developing and presenting 
+	a comprehensive theoretical framework to understand the constraint reduction/approximation procedure. 
+\todoc{We probably will need to discuss at some point other related work, such as
+the ``Smoothed Linear Program'' due to Desai et al (which aims at the problem when the number of next states
+is high and sampling is used instead of the Bellman operator in the definition of the LP),
+Petrik and Pazis and Parr's approach to the dilemma of what features to use (L1 regularization,
+non-parametric approximate LP's),
+dual dynamic programming due to Wang et al.,
+partitioned linear programming due to Kveton and Hauskrecht,
+Wang and Bertsekas'  incremental constraint projection methods for variational inference,
+Bertsimas and Caramanis' ``adaptability via sampling'',
+Guestrin and Hauskrecht's ``Solving factored MDPs with continuous and discrete variables'' amongst others.}
 

### 2015-06-10 improv.tex
eqdef and other minor fixes

@@
 \begin{lemma}\label{bestbndmn}
-Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\argmin_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
+Let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
 \begin{align}
@@
 
-Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the modified $L_\infty$ norm.
+Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.
 \begin{lemma}\label{gshiftmn}
@@
 \begin{theorem}\label{gmaxcontramn}
-The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in modified $L_\infty$ with factor $\beta_{\psi}$.
+The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in weighted $L_\infty$ with factor $\beta_{\psi}$.
 \end{theorem}
@@
 \begin{corollary}\label{hgmaxcontramn}
-$\hg$ is also a contraction map in the modified $L_\infty$ norm.
+$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
 \end{corollary}
@@
 \begin{lemma}\label{cmt1mn}
-Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
+Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
 \begin{align}
@@
 Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP.
-Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\stackrel{\Delta}{=}\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then
+Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then
 \begin{align}
@@
 The result follows from Corollary~\ref{cmt1}.\\
-\textbf{Main Result~$1$: Prediction Error bound in modified $L_\infty$-norm}
+\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
 \end{proof}

### 2015-06-10 mdp.tex
eqdef and other minor fixes

@@
 We denote the class of policies by $\Pi$. 
-The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$ is denoted by $J_\pi(s)$ and is defined by
+The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$ is denoted by $J_\pi(s)$ and is defined by \todoc{Explain the meaning of $\eqdef$.}
 \begin{align}
-J_\pi(s)\stackrel{\Delta}{=}\E\left[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)\,\Large|\,\pi\right]\,,\nn
+J_\pi(s) \eqdef
+	\E\left[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)\,\Large|\,\pi\right]\,,\nn
 \end{align}
@@
 Here $J_\pi(s)$ is known as the value of the state $s$ under the policy $\pi$, and $J_\pi:S\to \R$ is 
- %the vector quantity $J_\pi\stackrel{\Delta}{=}(J_\pi(s))_{s\in S}\in R^n$ is 
+ %the vector quantity $J_\pi\eqdef(J_\pi(s))_{s\in S}\in R^n$ is 
  called the value-function corresponding to the policy $\pi$. 
- The optimal value function $J^*:S\to \R$ is defined as $J^*(s)\stackrel{def}{=}\underset{\pi \in \Pi}{\max} J_\pi(s)$, $s\in S$.
+ The optimal value function $J^*:S\to \R$ is defined as $J^*(s) \eqdef
+ \sup_{\pi\in\Pi} J_\pi(s)$, $s\in S$.
+ %\underset{\pi \in \Pi}{\sup}\, J_\pi(s)$, $s\in S$.
 
@@
 If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}.
+
 For convenience, in what follows we identify $\R^n$ with $\R^{S}$:
 Any vector $J\in \R^n$ is viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
+We now define some operators acting on $\R^n$ (equivalently, on $\R^S$) that will be useful later.
 The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
@@
 $T$ is a $\max$-norm contraction operator with contraction factor $\alpha$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
+\todoc{Introduce $\norm{\cdot}_{\infty}$. Should we have a notation/symbols section?}
 \begin{align}

### 2015-06-10 strel.tex
Cosmetics and some comments, especially on the proof of Lemma 8.4
address some comments
eqdef and other minor fixes

@@
 \begin{align}\label{grlpeqprog}
-\min_{r\in \chi} &||\Phi r-\hv||_{1,c}\nn\\
+\begin{split}
+\min_{r\in \chi}\, &||\Phi r-\hv||_{1,c}\\
 \text{s.t}\mb & W^\top \Phi r\geq W^\top T \Phi r.
+\end{split}
 \end{align}
@@
 Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP.
-Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\stackrel{\Delta}{=}\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
+Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
 \begin{align}
@@
 \end{align}
-From Assumption~\ref{one} there exists $r'\in \R^k$ such that $\Phi r'=\Phi r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP.
+From Assumption~\ref{one} there exists $r'= r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP.
 \todoc{Why not just state that let $r' = r^* + \frac{(1+\alpha)\gamma}{1-\alpha} e_1$?}

### 2015-06-13 improv.tex
Mostly streamlining the text in the alp section

@@
 The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\infty,1/\psi}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
-\end{proof}\\
+\end{proof}
+
 We now recall Lemma~$4.5$ of \cite{ALP}. \todoc{You had 4.3 here, but in the official journal version this seems to be Lemma 5 in Section 4.}
@@
 The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
-\end{proof}\\
+\end{proof}

### 2015-06-13 lp.tex
eqdef and other minor fixes
Mostly streamlining the text in the alp section

@@
 \min_{J\in \R^n}\, &c^\top J\\
-\text{s.t}\mb &J\geq T J,
+\text{s.t.}\mb &J\geq T J,
 \end{split}
@@
 \min_{J\in \R^n} \,&c^\top J\\
-\text{s.t}\mb &EJ\geq H J,
+\text{s.t.}\mb &EJ\geq H J,
 \end{split}
@@
 Note that \eqref{mdplpshort} and \eqref{shortalter} are identical programs and differ only in notation.
-We use notation of type \eqref{mdplpshort} whenever we prefer brevity and we use notation \eqref{shortalter} in some definitions and proof for the sake of clarity.
-The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by letting $J=\Phi r$ in \eqref{mdplpshort} and is given as
+We use notation of type \eqref{mdplpshort} whenever we prefer brevity and we use notation \eqref{shortalter} in some definitions and proofs for the sake of clarity.
+Recall that the vector $c\in \R^n$ must have positive entries to guarantee that the unique solution to the above LP is the optimal value function.
+By convention, we will also assume that $c$ is also normalized:
+\begin{assumption}\label{probdist}
+$c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0$ and $\sum_{i=1}^n c(i)=1$.
+\todoc{I am pretty sure the positivity is needed.}
+\end{assumption}
+
+The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplpshort} with $\Phi \in \R^{n\times k}$ and the new variables $r\in \R^k$.
+By substitution, this leads to
 \begin{align}\label{alp}
@@
 \min_{r\in \R^k}\, &c^\top \Phi r\\
-\text{s.t}\mb &\Phi r\geq T \Phi r.
+\text{s.t.}\mb &\Phi r\geq T \Phi r.
 \end{split}
@@
 Unless specified otherwise we use $\tr$ to denote any solution\todoc{instead of saying the solution} to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. 
-We now state the assumptions and definitions used for the rest of the paper.
+The extra constraint added that $J$ lies in the (column) span of $\Phi$ could lead to an infeasible LP.
+An easy way to prevent this is if the vector $\one$ whose components are all equal to one is in the span of $\Phi$.
+Indeed, by \cref{shift}, for any $t\in \R$, $T (t\one ) =  \alpha t \one+T \zero \le \alpha t \one + \max_{s,a} g_a(s)$, hence $t\one \ge \alpha t \one+T\zero $ happens as soon as
+$t\ge \frac{1}{1-\alpha}\max_{s,a} g_a(s)$. 
+This leads to the following assumption:
 \begin{assumption}\label{one}
-The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. In other words, the constant function is part of the basis.
+The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
+In other words, the constant function is part of the basis.
 \end{assumption}
-\begin{assumption}\label{probdist}
-$c=(c(i),i=1,\ldots,n)\in \R^n$ is a probability distribution, i.e., $c(i)\geq 0$ and $\sum_{i=1}^n c(i)=1$.
-\end{assumption}
-\begin{definition}
-Given a function $\chi\colon S\ra \R^+$ we define the quantity $\beta_{\chi}$ as
+
+We will now recall two results due to de Farias and Van Roy 
+	that bound the error due to the introduction of the extra constraint in the ALP.
+For this, we will need the definition of weighted $L_1$ and $L_\infty$ norms.
+For any $c,\rho:S \to \R$ positive valued functions
+the weighted $L_1$-norms $\norm{\cdot}_{1,c}$ 
+and 
+the weighted $L_\infty$-norms  $\norm{\cdot}_{\infty,\rho}$ are defined as
+\begin{align*}
+||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|\,, \qquad
+||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}\,, \qquad J:S\to \R\,.
+\end{align*}
+
+We let $\R_+$ denote the set of nonnegative reals. \todoc{Move up?}
+For any function $\chi\colon S\ra \R_+$, define the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as
 \begin{align*}
@@
 \end{align*}
+\begin{definition}
+A function $\chi:S\to\R_+$ is said to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ 
+	if $\beta_{\chi}<1$.
 \end{definition}
-\begin{definition}
-The function $\chi$ is then said to be a \emph{Lyapunov} function if $\beta_{\chi}<1$.
-\end{definition}
+The error bound will be given in terms of a Lyapunov function $\psi$ for $P$ that is in the column span of $\Phi$:
 \begin{assumption}\label{lyap}
-$\psi\colon S \ra \R^+$ is a Lyapunov function and is present in the column span of the feature matrix $\Phi$.
+$\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
+and is present in the column span of the feature matrix $\Phi$.
 \end{assumption}
-It is straightforward to check that the function $\one$ is a Lyapunov function and trivially is present in the column span of $\Phi$. 
-\begin{definition}\label{modlone}
-The weighted $L_1$-norm is defined as \todoc{modified $\Rightarrow$ weighted?}
+It is straightforward to check that the vector $\one$ when viewed as a $S \to \R_+$ function 
+is a Lyapunov function. 
+Further, by \cref{one}, $\one$ is trivially present in the column span of $\Phi$, 
+hence, \cref{lyap} is not limiting.
+
+%In Definition~\ref{modnorm}, the use of the weighting function $\rho$ allows us to measure the error taking into account the relative importance of the various states.
+A higher value of $\rho(s)$ means that the state $s$ is less important and vice-versa.\\
+With this, we can recall the said result.  %below  which bounds the error in the approximate value function.
+\begin{theorem}[Theorem~$4.2$ of \cite{ALP}]
+\label{restateval}
+Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be as in \cref{lyap} 
+and $c$ be a distribution as in \eqref{probdist}. Then, it holds that
 \begin{align*}
-||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|,
-\end{align*}
-where $c$ obeys Assumption~\ref{probdist}.
-\end{definition}
-\begin{definition}\label{modnorm}
-The weighted $L_\infty$-norm is defined as follows:  \todoc{modified $\Rightarrow$ weighted?
-Also, the convention in math is to divide in the case of the $L_{\infty}$ norm.
-Not a high priority to change this, but maybe it would be good to do this in the longer term.}
-\begin{align*}
-||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)},
-\end{align*}
-where $\rho \colon \S \ra \R^+$ is the weighing function and $J\in \R^n$.
-\end{definition}
-In Definition~\ref{modnorm}, the use of the weighting function $\rho$ allows us to measure the error taking into account the relative importance of the various states.
-A lower value of $\rho(s)$ means that the state $s$ is less important and vice-versa.\\
-We recall below Theorem~$4.2$ of \cite{ALP} which bounds the error in the approximate value function.
-\begin{theorem}\label{restateval}
-Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be a Lyapunov function and $c$ be a distribution as in \eqref{probdist}, then 
-\begin{align*}
-||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}.
+||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}\,.
 \end{align*}
 \end{theorem}
-We now recall Theorem~$3.1$ of \cite{ALP} that characterizes the loss in performance of the greedy policy.
-\begin{theorem}\label{restatepol}
+The next result  the loss in performance of a policy that is greedy w.r.t. $J_{\tu}$:
+\begin{theorem}[Theorem~$3.1$ of \cite{ALP}]
+\label{restatepol}
 Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP, then 
 \begin{align*}
-||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'},
+||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'}\,,
 \end{align*}
@@
 Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
+\todoc{Column generation, Dantzig-Wolf decomposition?}

### 2015-06-13 mdp.tex
Mostly streamlining the text in the alp section

@@
 \end{align}
-where $c\in \R^n_+$ is any vector whose components are all non-negative (we denote the set of non-negative reals by $\R_+$).
+where $c\in \R^n$ is any vector whose components are all positive.
+\todoc{I changed this from nonnegative to positive.} 
 One can show that $J^*$ is the solution to the linear program given by \eqref{mdplp} \cite{BertB}. 

### 2015-06-13 resdisc.tex
Mostly streamlining the text in the alp section

@@
 The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.
-\end{proof}\\
+\end{proof}
+
 The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
@@
 The modified $L_\infty$ norm in \eqref{finalbnd} comes to our rescue to control the error due to those states that are not sampled.
-Thus the sampling distribution need not be the stationary distribution of the optimal policy as long as it samples the \emph{important} states, an observation that might theoretically explain the empirical successes of the RLP \cite{ALP,CST,SALP}.\\
+Thus the sampling distribution need not be the stationary distribution of the optimal policy as long as it samples the \emph{important} states, an observation that might theoretically explain the empirical successes of the RLP \cite{ALP,CST,SALP}.
+
 To understand the implication of Claim~$2$ we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
@@
 \subsection{Computational Complexity}
-It is known that the complexity of the linear program \cite{karmarkar,adler} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables.
+It is known that the complexity of the linear program is polynomial in the length of its entries, i.e., the number of constraints times the number of variables \cite{karmarkar,adler}. 
 In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states.

### 2015-06-13 constsamp.tex
eqdef and other minor fixes
RLP polishing

--- 2015-05-27 constsamp.tex
@@
+%!TEX root =  autocontgrlp.tex
 \section{Constraint sampling}
-The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP.
-While the objective function of the RLP is the same as that of the ALP, the RLP has only $m<<nd$ constraints sampled from the original ALP according to a given probability distribution.
-The reduced linear program is then given by
-\small
+One way to reduce the number of constraints is to randomly choose a subset of them \cite{CS},
+leading to the so-called reduced linear program (RLP). \todoc{How about the results of Calafiore and Campi (2005, Math. Prog.) and others reviewed in \cite{CS}? Any follow-up we missed?}
+While the objective function of the RLP is the same as that of the ALP, 
+the RLP has only $m \ll nd$ constraints sampled from the original ALP according to a given probability distribution:
 \begin{align}\label{rlp}
-\min_{J\in \R^n} &c^\top J\nn\\
-\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall (s,a) \in \I,
+\begin{split}
+\min_{r\in \N}\, &c^\top \Phi r\\
+\text{s.t}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \mb (s,a) \in \I\,,
+\end{split}
 \end{align}
-\normalsize
-where $\I$ is the index set containing the $m$ sampled state-action pairs. Using the index set $\I$ we define an $nd\times m$ matrix $\M$, called the constraint sampling matrix as below.
+where $\I$ is the index set containing $m$ sampled state-action pairs and
+the extra constraint set $\N\subset \R^k$ is introduced to guarantee a bounded feasible set (hence, bounded solution).
+It is assumed that $\N$ is compact and $\tr\in \N$. \todoc{How can one arrange for this in general?}
+The index set $\I$ naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
 \begin{definition}\label{csampmat}
-Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i\stackrel{\Delta}{=}s_i+(a_i-1)\times n,\forall i=1,\ldots,m$.
-Then the constraint sampling matrix associated with the index set $\I$ is given by
+Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i \eqdef s_i+(a_i-1)\times n$, $i=1,\ldots,m$.
+Define the constraint sampling matrix $\M \in \R^{nd\times m}$ associated with the index set $\I$ by
 \begin{align}
-\M(i,j)&=1, \mb\text{if}\mb q_i=j\nn\\
-&=0, \mb\text{otherwise}.
+\M(i,j)
+=
+\begin{cases}
+1, & \text{ if } q_i = j\,;\\
+0, & \text{ otherwise}.
+\end{cases}
 \end{align}
@@
 \begin{align}\label{rlpshort}
-\min_{r\in \N} &c^\top \Phi r\nn\\
-\text{s.t}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r,
+\begin{split}
+\min_{r\in \N}\, &c^\top \Phi r\\
+\text{s.t}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
+\end{split}
 \end{align}
-where $\M$ is a constraint sampling matrix as in Definition~\ref{csampmat} and $\N\subset \R^k$ is a bounded set such that $\tr \in \N$.
-Note that the feasible set of the RLP is a superset of the feasible set of the ALP.\\
+Note that apart from $r\in \N$ the feasible set of the RLP is a superset of the feasible set of the ALP.
+
 The RLP based on constraint sampling has been found to perform well empirically in application domains ranging from controlled queuing networks (see section $6.2$ of \cite{ALP} and section $7$ of \cite{SALP}) to Tetris (see \cite{CST} and section $6$ of \cite{SALP}).
 However, the theoretical guarantees for the RLP are available only under a restricted setting \cite{CS}.
-We present the main result of \cite{CS} on constraint sampling, and to that end define the following:
-\begin{definition}\label{sampdist}
-Given a policy $u$ and Lyapunov function $\psi$ in the column span of $\Phi$, we define probability distributions $\mu_u$, $\mu_{u,\psi}$ and constant $\theta$ as 
+We present the main result of \cite{CS} on constraint sampling, and to that end define the following quantities:
+%\begin{definition}\label{sampdist}
+Given a policy $u$, a Lyapunov function $\psi$ in the column span of $\Phi$
+and a probability distribution $c$ over the states
+we define probability distributions $\mu_{u,c}$, $\mu_{u,\c,\psi}$ and constant $\theta_{u,c,\psi}$ as 
 \begin{align}
-\mu^\top&\stackrel{\Delta}{=}(1-\alpha)c^\top (I-\alpha P_u)^{-1},\nn\\
-\mu_{u,\psi}(s,a)&\stackrel{\Delta}{=}\frac{\mu_{u}(s) \psi(s)}{\mu_u^\top \psi d},\nn\\
-\theta&\stackrel{\Delta}{=}\frac{(1+\beta_{\psi})}{2}\frac{\mu_{u^*}^\top \psi}{c^\top J^*}\sup_{r\in \N}||J^*-\Phi r||_{\mn}.
+\mu_{u,c}^\top& \eqdef (1-\alpha)c^\top (I-\alpha P_u)^{-1},\nn\\
+\mu_{u,c,\psi}(s,a)&\eqdef (d \, \mu_u^\top \psi)^{-1} \, \mu_{u}(s) \psi(s),\nn\qquad s\in \S,a\in  \A\,,\\
+\theta_{u,c,\psi} &\eqdef\mfrac{(1+\beta_{\psi})}{2} \, \mfrac{\mu_{u,c}^\top \,\psi}{c^\top J^*}\, \sup_{r\in \N}||J^*-\Phi r||_{\mn}.
 \end{align}
-\end{definition}
-We now recall Theorem~$3.1$ of \cite{CS} below.
+%\end{definition}
+We now recall Theorem~$3.1$ of \cite{CS} below. \todoc{Assumptions? }
 \begin{theorem}\label{csresult}
-Let $\epsilon$ and $\delta$ be scalars in $(0,1)$.
-Let $u^*$ be the optimal policy and $\I$ an index set containing the $m$ state-action pairs sampled independently according to the distribution $\psi_{u^*,\psi}$, for some Lyapunov function $\psi$, where
+Let $\epsilon$ and $\delta$ be scalars in $(0,1)$,
+$\theta = \theta_{u^*,c,\psi}$ where $u^*$ is an optimal policy.
+Let $\I$ be an index set obtained by sampling $m$ state-action pairs 
+	independently according to the distribution $\mu_{u^*,c,\psi}$,
+	\todoc{Their Lyapunov function definition is slightly different. Which one is the real one needed by this result?}
+	where%
+	\footnote{Note that the cardinality of $\I$ might be smaller than $m$.}
 \begin{align}
-m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\big).
+m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\left(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\right).
 \end{align}
-Let $\tilde{r}$ be an optimal	solution of the ALP and let $\hat{r}$ be the solution of the corresponding RLP, then with probability at least $1-\delta$, we have
+Let $\tilde{r}$ be an optimal	solution of the ALP and let $\hat{r}$ be the solution of the corresponding RLP. 
+Then, with probability at least $1-\delta$, we have
 \begin{align}
@@
 \end{theorem}
-\textbf{Motivation for our work:}\\
-The result in Theorem~\ref{csresult} has a significant limitation in that the sampling distribution $\mu_{u^*,\psi}$ requires the knowledge of $u^*$.
-The optimal policy $u^*$ might not be available in practice and hence it would not be possible to even formulate the specific RLP for which the bound in Theorem~\ref{csresult} applies.
-However, as mentioned before, the RLP has performed reasonably well even when the sampling distribution is not $\mu_{u^*,\psi}$.
-Thus there is a gap between the theoretical understanding of the RLP and its practical efficacy which merits our attention.
-The gap also indicates that the RLP might be a special case of a generalized constraint reduction scheme with provable performance guarantees.
-Understanding such a generalized method would result in an ALP based ADP techinque that would have theoretical performance guarantees while being practically useful.
+\noindent \textbf{Motivation for our work:}
+As noted by the authors of \cite{CS}, this result is best viewed as a
+	theoretical illustration of the potential of constraint sampling:
+	sampling from $\mu_{u^*,c,\psi}$ will more often than not be infeasible in practice
+	as this distribution is dependent on the optimal policy $u^*$.
+However, as mentioned before, the RLP has performed reasonably well 
+	even when the sampling distribution is not $\mu_{u^*,\psi}$. 
+Thus there is a gap between the theoretical understanding of the RLP 
+	and its practical efficacy which merits our attention. 
+The gap also indicates that the RLP might be a special case 
+	of a generalized constraint reduction scheme with provable performance guarantees. 
+Understanding such a generalized method would result in an ALP based ADP technique 
+	that would have theoretical performance guarantees while being practically useful. 
 In particular, we wish to answer the following open questions.

### 2015-06-13 grlp.tex
RLP polishing

@@
 Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP.
-Constraint reduction is achieved by choosing $m<<nd$.
+Constraint reduction is achieved by choosing $m\ll nd$.
 The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone.
@@
 \begin{assumption}\label{wassump}
-$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m<<nd$) and each of its column sums equals $1$.
+$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m\ll nd$) and each of its column sums equals $1$.
 \end{assumption}

### 2015-06-13 improv.tex
1/psi replacement

@@
 \begin{lemma}\label{bestbndmn}
-Let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
+Let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}$, then 
 \begin{align}
-||J^*-\bj||_{\infty,1/\psi}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}.
+||J^*-\bj||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.
 \end{align}
@@
 \begin{proof}
-The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\infty,1/\psi} \psi\geq TJ^*$.
+The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\mn} \psi\geq TJ^*$.
 \end{proof}
@@
 \begin{proof}
-Given $J_1,J_2\in \R^n$ let $\epsilon=||J_1-J_2||_{\infty,1/\psi}$. Thus
+Given $J_1,J_2\in \R^n$ let $\epsilon=||J_1-J_2||_{\mn}$. Thus
 \begin{align}\label{ineq}
@@
 \begin{align}
-||\Gamma J_1-\Gamma J_2||_{\infty,1/\psi}\leq \beta_{\psi} ||J_1-J_2||_{\infty,1/\psi}.
+||\Gamma J_1-\Gamma J_2||_{\mn}\leq \beta_{\psi} ||J_1-J_2||_{\mn}.
 \end{align}
@@
 \begin{lemma}\label{cmt1mn}
-Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
+Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_{\mn}$ then
 \begin{align}
-||J^*-\hv||_{\infty,1/\psi}\leq \frac{2||J^*-\Phi r^*||_{\infty,1/\psi}+||\Gamma J^*-\hg J^*||_{\infty,1/\psi}}{1-\beta_{\psi}}.
+||J^*-\hv||_{\mn}\leq \frac{2||J^*-\Phi r^*||_{\mn}+||\Gamma J^*-\hg J^*||_{\mn}}{1-\beta_{\psi}}.
 \end{align}
@@
 \begin{proof}
-The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\infty,1/\psi}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
+The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\mn}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
 \end{proof}
@@
 Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP.
-Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then
+Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\mn}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\mn}$, then
 \begin{align}
@@
 \begin{proof}
-Let $\gamma=||J^*-\Phi r^*||_{\infty,1/\psi}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
+Let $\gamma=||J^*-\Phi r^*||_{\mn}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
 \begin{align}
@@
 &=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
-&\leq c^\top \psi ||\Phi r'-\hv||_{\infty,1/\psi}\nn\\
-&\leq c^\top \psi (||\Phi r'-J^*||_{\infty,1/\psi}+||J^*-\hv||_{\infty,1/\psi}).
+&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
+&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).
 \end{align}

### 2015-06-13 lp.tex
1/psi replacement

@@
 \end{assumption}
-It is straightforward to check that the vector $\one$ when viewed as a $S \to \R_+$ function 
+It is straightforward to check that the vector $\one$ when viewed as an $S \to \R_+$ function 
 is a Lyapunov function. 
@@
 hence, \cref{lyap} is not limiting.
+In what follows we will always assume that Assumptions \ref{probdist}--\ref{lyap} hold.
 
@@
 \label{restateval}
-Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be as in \cref{lyap} 
-and $c$ be a distribution as in \eqref{probdist}. Then, it holds that
+Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$.
+% $\psi$ be as in \cref{lyap} 
+%and $c$ be a distribution as in \eqref{probdist}. 
+Then, it holds that
 \begin{align*}
@@
 \label{restatepol}
-Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP, then 
+Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP. Then,
 \begin{align*}
@@
 Theorems~\ref{restateval} and ~\ref{restatepol} together imply that the ALP addresses both the control and prediction problems. Please refer to \cite{ALP} for a more detailed treatment of the ALP.\\
-Note that the ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplpshort} which has $n$ variables.
+Note that the ALP is a linear program in $k$ ($\ll n$) variables as opposed to the LP in \eqref{mdplpshort} which has $n$ variables.
 Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

### 2015-06-13 polbnd.tex
1/psi replacement

@@
+%!TEX root =  autocontgrlp.tex
 \textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\
@@
 \begin{note}
-By letting $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}+||J^*-\hg J^*||_{\mn}$ (inequality follows from Lemma~\ref{bestbndmn}), we can also modifiy the bounds in \eqref{finalbnd} and \eqref{polthe} as
+By letting $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}+||J^*-\hg J^*||_{\mn}$ (inequality follows from Lemma~\ref{bestbndmn}), we can also modifiy the bounds in \eqref{finalbnd} and \eqref{polthe} as
 \begin{align}

### 2015-06-14 mdp.tex
Streamlining

@@
 In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
-An MDP is a $4$-tuple $\langle S,A,P,g\rangle$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function.
+An MDP is a $4$-tuple $\langle S,A,P,g\rangle$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g:S\times A \to \R$ is the reward function.
 We consider MDPs with large but finite number of states.
@@
 The probability transition kernel $P= (p_a)_{a\in A}$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. 
-We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
+We also denote the reward $g(s,a)$ obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
 By a policy, we mean a sequence $\pi=\{\pi_0,\ldots,\pi_n,\ldots\}$ of functions $\pi_n, n\geq 0$ 
-	that describe the manner in which an action is picked in a given state at time $n$. 
+	that describe which action is to be picked in a given state at time $n$. 
 In the most general case, $\pi_n$ maps $(S \times A)^n \times S$, i.e., 
@@
 	of state-action sequences of length $2n+1$, to a distribution over the actions. 
-We denote the class of policies by $\Pi$. 
-The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$ is denoted by $J_\pi(s)$ and is defined by \todoc{Explain the meaning of $\eqdef$.}
+Let $\Pi$ stand for the set of policies. 
+The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$,
+	or, in short, the value of $\pi$ in state $s$
+	is denoted by $J_\pi(s)$ and is defined by \todoc{Explain the meaning of $\eqdef$.}
 \begin{align}
@@
 	where $a_{n} \sim \pi_n(\,\cdot\,|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$, $s_{n+1} \sim p_{a_n}(s_n,\cdot)$ 
-	and $\alpha \in (0,1)$ is a given discount factor. 
-Here $J_\pi(s)$ is known as the value of the state $s$ under the policy $\pi$, and $J_\pi:S\to \R$ is 
- %the vector quantity $J_\pi\eqdef(J_\pi(s))_{s\in S}\in R^n$ is 
- called the value-function corresponding to the policy $\pi$. 
+	and $\alpha \in (0,1)$ is the so-called discount factor. 
+The resulting function $J_\pi:S\to \R$ is called the value function of policy $\pi$.	
  The optimal value function $J^*:S\to \R$ is defined as $J^*(s) \eqdef
@@
 We now state without proof the most important properties of the Bellman operator.
-Though in these results, we make use of the Bellman operator $T$, the results also trivially hold for $T_u$ as well.
+The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
 
 %\subsection{Properties of $T$}
+First, we introduce some extra notation:
+For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
+We use $\one \in \R^n$ to denote a vector with all entries $1$.
+The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
+\begin{lemma}\label{monotone}
+$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
+Further, if $J\in \R^n$ is such that $J\geq TJ$ then $J\geq J^*$. \todoc{Should we move this second part out?}
+\end{lemma}
+\begin{lemma}\label{shift}
+Given $J\in \R^n$ and $t \in \R$, we have
+\begin{align}\label{eq:shift}
+T(J+t\one)=TJ+\alpha t\one.
+\end{align}
+\end{lemma}
+From these result, it immediately follows that $T$ is a contraction in the $L_\infty$-norm through the following lemma:
 \begin{lemma}\label{maxnorm}
+If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{eq:shift} then 
 $T$ is a $\max$-norm contraction operator with contraction factor $\alpha$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
-\todoc{Introduce $\norm{\cdot}_{\infty}$. Should we have a notation/symbols section?}
 \begin{align}
@@
 \end{lemma}
+\begin{proof}
+The proof is given as we will need this lemma later.
+Let $\eps = \norm{J_1 - J_2}_\infty$. Then $J_2 - \eps \one \le J_1 \le J_2 + \eps \one$. By the monotonicity of $T$,
+$T(J_2 - \eps \one) \le T J_1 \le T(J_2 + \eps \one)$. Using~\eqref{eq:shift}, we get 
+$TJ_2 - \alpha \eps \one \le T J_1 \le TJ_2 + \alpha \eps \one$, i.e., $-\alpha \eps \one \le T J_1 - T J_2 \le \alpha \eps \one$, from which the result follows.
+\end{proof}
+Through Banach's fixed point theorem, from \cref{maxnorm} we get the following lemma:
 \begin{lemma}\label{uniquesol} 
@@
 \end{lemma}
-For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
-The Bellman operator $T$ exhibits two more important properties presented in the following lemmas (see \cite{BertB} for proofs):
-\begin{lemma}\label{monotone}
-$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
-Further, if $J\in \R^n$ is such that $J\geq TJ$ then $J\geq J^*$.
-\end{lemma}
-\begin{lemma}\label{shift}
-Given $J\in \R^n$, $t \in \R$ and $\mathbf{1} \in \R^n$, a vector with all entries $1$, we have
-\begin{align}
-T(J+t\mathbf{1})=TJ+\alpha t\mathbf{1}.
-\end{align}
-\end{lemma}
-Note that Lemmas~\ref{maxnorm}--\ref{shift} also hold for the Bellman operator $H$ defined for the action values in Definition~\ref{bellactval}.\par
+Though in these results, we make use of the Bellman operator $T$, the results also hold for $T_u$ and $H$ as well.
+%Note that Lemmas~\ref{maxnorm}--\ref{shift} also hold for the Bellman operator $H$ defined for the action values in Definition~\ref{bellactval}.\par
+
 Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}.

### 2015-06-14 constsamp.tex
s.t. abbreviation corrected
Refinement of constraint sampling result

@@
 \min_{r\in \N}\, &c^\top \Phi r\\
-\text{s.t}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \mb (s,a) \in \I\,,
+\text{s.t.}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \mb (s,a) \in \I\,,
 \end{split}
@@
 \min_{r\in \N}\, &c^\top \Phi r\\
-\text{s.t}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
+\text{s.t.}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
 \end{split}
@@
 and a probability distribution $c$ over the states
-we define probability distributions $\mu_{u,c}$, $\mu_{u,\c,\psi}$ and constant $\theta_{u,c,\psi}$ as 
+we define probability distributions $\mu_{u,c}$, $\mu_{u,c,\psi}$ and constant $\theta_{u,c,\psi}$ as 
 \begin{align}
@@
 \mu_{u,c,\psi}(s,a)&\eqdef (d \, \mu_u^\top \psi)^{-1} \, \mu_{u}(s) \psi(s),\nn\qquad s\in \S,a\in  \A\,,\\
-\theta_{u,c,\psi} &\eqdef\mfrac{(1+\beta_{\psi})}{2} \, \mfrac{\mu_{u,c}^\top \,\psi}{c^\top J^*}\, \sup_{r\in \N}||J^*-\Phi r||_{\mn}.
+\theta_{u,c,\psi} &\eqdef\mfrac{(1+\beta_{\psi})}{2} \, \mfrac{\mu_{u,c}^\top \,\psi}{\norm{J^*}_{1,c}}\, \sup_{r\in \N}||J^*-\Phi r||_{\mn}.
 \end{align}
 %\end{definition}
+Note that in the definition of $\theta_{u,c,\psi}$ the \emph{supremum} 
+of the error of approximating $J^*$ by the LFA over $\N$ appears.
+De Farias and Van Roy show through an example how this term can still be reasonable controlled  \cite{CS}.
+\todoc{If we avoid this, this would be great!}
+
 We now recall Theorem~$3.1$ of \cite{CS} below. \todoc{Assumptions? }

### 2015-06-14 grlp.tex
s.t. abbreviation corrected
GRLP cleaning

--- 2015-06-02 grlp.tex
@@
 \section{Generalized Reduced Linear Program}
-In this section we present the generalized reduced linear program (GRLP) which is obtained by appropriately extending the definition of the RLP.
-An important property that should carry over from the RLP is that the feasible set of the GRLP should also be a superset of the feasible set of the ALP.
-A natural way to achieve this is to replace the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP.
-Formally, we define the generalized reduced linear program (GRLP) as below:
+In this section we present the generalized reduced linear program (GRLP) which is obtained by replacing the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP.
+Formally, we define the generalized reduced linear program (GRLP) as follows:
 \begin{align}\label{grlp}
 \begin{split}
-\min_{r\in \chi}\, &c^\top \Phi r,\\
-\text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
+\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
+\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r, 
 \end{split}
 \end{align}
-where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$. \todoc{Is not $\hj\in \R^n$?
-Moreover, later often $\chi$ is not taken into account. 
-Also, the role of $\chi$ is never explained. Do we want to keep $\chi$ or maybe we should just remove it?
-Further, $\hj$ is not really well defined. We need to defined $r_c$ and then set $\hj = \Phi r_c$.
-}
-Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP.
-Constraint reduction is achieved by choosing $m<<nd$.
+where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and 
+$\N \subset \R^k$ is a set such that $\tilde{r}_c \in \N$. 
+\todoc{Changed the definition and using $\N$ that was used in the definition of RLP.}
+The role of $\N$, as in the case of RLPs, is to guarantee
+the existence of bounded solutions. \todoc{We'll be trouble with $\N$ if we start assume that it is a bounded set. See below.}
+
+The $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP.
+Constraint reduction is achieved by choosing $m\ll nd$.
 The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone.
-Also note that an RLP is trivially a GRLP as well.
-Unless specified otherwise we use $\hr$ to denote the solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
+Also note that an RLP is trivially a GRLP as well with a random matrix $W$.
+Unless specified otherwise, we use $\hr$ to denote any solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
 Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column).
 Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive.
-Also, normalizing columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP.
+Then, normalizing the columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP.
 Keeping these in mind we also assume the following throughout the rest of the paper:
 \begin{assumption}\label{wassump}
-$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m<<nd$) and each of its column sums equals $1$.
+$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m\ll nd$) and each of its column-sums equals one.
 \end{assumption}
+\begin{comment}
 The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
+\end{comment}
 \input{cartoon}
+\todoc{The picture needs to be perfected.}
 The rest of the paper develops analytically various performance bounds and our main results provide the following:
@@
 \item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
-\item an important result on constraint sampling.
+\item an important result on constraint sampling. \todoc{we should be more specific}
 \end{enumerate}
@@
 We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$.
-We first establish our results in the $L_\infty$-norm and then extend the same in a modified $L_\infty$-norm.
-The schematic in Fig.
-~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
+We first establish our results in the $L_\infty$-norm and then in a weighted $L_\infty$-norm.
+The schematic in Fig.~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
 \FloatBarrier
 \input{schematic}
+\todoc{$d_1$ and $d_2$ use different norms?}

### 2015-06-14 lubp.tex
eqdef and other minor fixes
s.t. abbreviation corrected
cleaning up LUBP section

@@
 \section{Least Upper Bound Projection}\label{sec:lubp}
+Let $e_j$ denote the $j$th basis vector in the standard Euclidean bases of $\R^n$.
 The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
 \begin{definition}\label{lubpop}
-Given $J\in \R^n$, its least upper bound projection is denoted by $\Gamma J$ and is defined as 
+Given $J\in \R^n$, $c\in \R^n$ positive-valued vector define $r_{c,J}$ to be the solution to 
+\begin{align}
+\label{lubplp}
+\begin{split}
+ \underset{r\in \N}{\min} &\,\, c^\top \Phi r\,,\\
+ \text{s.t.}& \mb \Phi r\geq  TJ\,,
+ \end{split}
+\end{align}
+where it is assumed that a (bounded) solution exists.
+Then, for $J\in \R^n$, $\Gamma J$,
+the least upper bound projection of $J$ is defined as 
 \begin{align}\label{gamdef}
-(\Gamma J)(i)\stackrel{\Delta}{=}(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n,
-\end{align}
-where $V(i)$ denotes the $i^{th}$ component of the vector $V\in \R^n$.
-Also in \eqref{gamdef}, $e_j$ is the vector with $1$ in the $j^{th}$ place and zeros elsewhere, and $r_{e_j}$ is a solution to the linear program in \eqref{lubplp} for $c=e_j$:
-\begin{align}\label{lubplp}
- r_{c,J}   \stackrel{\Delta}{=}& \underset{r\in \N}{\argmin} \mbox{ } c^\top \Phi r,\nn\\
- \text{s.t}& \mb \Phi r\geq  TJ.
+(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
 \end{align}
@@
 %Note that $r_{e_j}$ depends on $J$, but this dependence is suppressed to reduce clutter. 
-\begin{remark}
+\begin{remark}\label{lubremark}
+The following hold: 
 \begin{enumerate}
-\item The definition of LUB operator $\Gamma \colon \R^n \ra \R^n$ involves $n$ associated linear programs.
-\item Observe that $\Gamma J\geq TJ$ (follows from the fact that if $a\geq c$ and $b\geq c$, then $\min(a,b)\geq c$, where $a, b, c \in \R$).
-\item Given $\Phi$ and $J\in \R^n$, define $\F\stackrel{\Delta}{=}\{\Phi r|\Phi r\geq TJ\}$.
-Thus $\F$ is the set of all vectors in the span of $\Phi$ that upper bound $TJ$.
-By fixing $c$ in the linear program in \eqref{lubplp} we select a unique vector $\Phi r_c \in \F$.
+\item Assuming that $\N$ is polyhedral, 
+	the definition of LUB operator $\Gamma \colon \R^n \ra \R^n$ involves $n$ associated linear programs.
+\item It holds that $\Gamma J\geq TJ$ (this follows from the fact that if $a\geq c$ and $b\geq c$, then $\min(a,b)\geq c$, where $a, b, c \in \R$).
+\item Given $J\in \R^n$, define $\F_J\eqdef\{\,\Phi r\,|\,\Phi r\geq TJ, r\in \N\,\}$. 
+Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. 
+Further, since $(\Gamma J)(i) = \min\{ V(i) \,|\, V\in \F_J \}$, it also follows that $\Gamma J \le V$ for any $V\in \F_J$.
+%By fixing $c$ in the linear program in \eqref{lubplp} we select a unique vector $\Phi r_c \in \F$.
 The LUB projection operator $\Gamma$ picks $n$ vectors $\Phi r_{e_i},i=1,\ldots,n$ from the set $\F$ and $\Gamma J$ is obtained by computing their component-wise minimum.
@@
 \end{comment}
-\todoc{In fact, I would prefer the simpler definition without the $\min$ and then changing this remark.}
 \end{enumerate}
@@
 \begin{definition}\label{bestproj}
-The LUB projection of $J^*$ is denoted by $\bj=\Gamma J^*$.
+The LUB projection of $J^*$ is denoted by $\bj=\Gamma J^*$. \todoc{It is a bit strange to call this a definition. A numbered equation could be enough.}
 \end{definition}
@@
 \todoc{Poor choice of symbols: $\tv$ is the fixed point of $\Gamma$ and $\hat{V}$ will be the fixed point of $\tilde{\Gamma}$? Hmm.. Not a high priority to change it, but still..}
+In what follows, we let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_\infty$.
 \begin{lemma}\label{bestbnd}
-Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\argmin_{r\in R^k}||J^*-\Phi r||_\infty$, then 
+It holds that
 \begin{align}
-||J^*-\bj||_\infty\leq 2||J^*-\Phi r^*||_\infty.
+||J^*-\bj||_\infty\leq 2||J^*-\Phi r^*||_\infty\,.
 \end{align}
@@
 \begin{proof}
+By our earlier remark, 
+\begin{align} \label{eq:jtjgj}
+J^* = T J^* \le \Gamma J^*\,.
+\end{align}
+Define $\eps = \norm{J^* - \Phi r^*}_{\infty}$. Then, $\Phi(r^* + \eps e_1) = \Phi r^* + \eps \one \ge J^* = TJ^*$.
+Hence, $\Phi(r^* + \eps e_1) \in \F_{J^*}$ and thus
+by Remark~\ref{lubremark}, $\Phi(r^* + \eps e_1) \ge \Gamma J^*$. This, together with~\eqref{eq:jtjgj} means that
+$J^* \le \Gamma J^* \le \Phi r^* + \eps \one$ and thus
+$0 \le \Gamma J^* - J^* \le \Phi r^* - J^* + \eps \one \le 2 \eps \one$. Taking maximum over the components gives the result.
+\if0
 The result follows from the definition of $\Gamma$ in \eqref{gamdef} and the construction of $V_0$, Assumption~\ref{one}, and the fact that $\Phi r^*+||J^*-\Phi r^*||_\infty \one\geq TJ^*$.
@@
 \end{align}
+\fi
 \end{proof}
@@
 \begin{proof}
-Choose any $i\in \{1,\ldots,n\}$ and let $r_{e_i,J_1}$ and $r_{e_i,J_2}$ be solutions to the linear program in \eqref{lubplp} for $c=e_i$ with $J=J_1$ and $J=J_2$ respectively.
-Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$ and $e_i^\top \Phi r_{e_i,J_1} \geq e_i^\top \Phi r_{e_i,J_2}$, i.e., $(\Phi r_{e_i,J_1})(i)\geq (\Phi r_{e_i,J_2})(i)$.
-The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i,J})(i)$, $J\in \R^n$, and our choice of $i$ was arbitrary.
+Choose any $i\in \{1,\ldots,n\}$. 
+Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$.
+Hence, $\F_{J_1} \subset \F_{J_2}$ and thus $(\Gamma J_1)(i) \ge (\Gamma J_2)(i)$. 
+Since $i$ was arbitrary, the result follows.
 \end{proof}
 \begin{lemma}\label{lpsol}
-Let $A\in \R^{u\times v}$, $b,c\in R^u$, $x_0 \in R^v$ and $b_0=Ax_0$. Then
+Let $A\in \R^{u\times v}$, $b,c\in \R^u$ and $b_0=Ax_0$ for 
+some $x_0 \in \R^v$, $\N \subset \R^v$. Then
 \begin{align}
-\min\{c^\top Ax:Ax\geq b+b_0\} =\min\{c^\top Ax:Ax\geq b\}+c^\top b_0.
+\min\{c^\top Ax:Ax\geq b+b_0, x\in \N\} =\min\{c^\top A y:Ay \geq b, y+x_0 \in \N \}+c^\top b_0.
 \end{align}
@@
 \begin{proof}
-The claim can be shown by a simple change of variables.
+The claim follows by the change of variables $y := x-x_0$.
 \end{proof}
 \begin{lemma}\label{gshift}
-Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+t\one$, then $\Gamma J_2=\Gamma J_1+\alpha t\one$.
+Let $J\in \R^n$ and $t\in \R$ be a constant.
+Then, $\Gamma (J+t\one) = \Gamma J + \alpha t \one$ provided that $r\in \N$ holds if and only $r+s e_1\in \N$ holds for any $s\in \R$.
 \end{lemma}
 \begin{proof}
-Consider the $i^{th}$ linear programs associated with $\Gamma J_1$ and $\Gamma J_2$.
-The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ and $x_0=\alpha t e_i$.
+Consider the $i^{th}$ linear programs associated with $\Gamma J$ and $\Gamma (J+ t\one)$. 
+The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ 
+and $x_0=\alpha t e_1$, noting that by our assumption on $\N$,
+$\{ y\,: \, \Phi y \geq TJ, y + \alpha t e_1\in \N \}
+= \{ y\,: \, \Phi y \geq TJ, y \in \N \}$. \todoc{This is where this assumption is needed.}
 \end{proof}
@@
 \begin{proof}
-Given $J_1,J_2\in \R^n,$ let $\epsilon=||J_1-J_2||_\infty$. Thus,
-\begin{align}\label{ineq}
-J_2-\epsilon\one\leq J_1\leq J_2+\epsilon \one.
-\end{align}
-From Lemmas~\ref{gmonotone} and ~\ref{gshift}, we can write
-\begin{align}\label{ineq}
-\Gamma J_2-\alpha \epsilon\one\leq \Gamma J_1\leq \Gamma J_2+\alpha \epsilon\one.
-\end{align}
+The statement follows immediately from Lemmas~\ref{gmonotone} and~\ref{gshift}, and \cref{maxnorm}.
 \end{proof}
+\if0
 \begin{corollary}
@@
 \end{corollary}
+\fi
+Define $\tv$ to be the unique fixed point of $\Gamma$.
 \begin{lemma}\label{gfp}
- $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, obeys $\tv\geq T\tv$.
+The vector $\tv$ obeys $\tv\geq T\tv$.
 \end{lemma}
 \begin{proof}
+Let $1\le i \le n$. We have $\tv(i) = (\Gamma \tv)(i) = (\Phi r_{e_i,\tv})(i) \ge (T\tv)(i)$.
+\if0
 Consider the $i^{th}$ linear program associated with $\Gamma \tv$.
@@
 The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=(\Phi r_{e_i,V})(i)$.
+\fi
 \end{proof}
+Recall that $\tj$ denotes the solution to the ALP in \eqref{alp}.
 \begin{lemma}\label{relation1}
- $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey the relation $\tj\geq\tv\geq J^*$.
+Assume that $\N$ is such that if $r_i$ is
+the solution to the ALP in \eqref{alp} for $c=e_i$ then $r_i\in \N$, $1\le i \le n$.
+% $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey 
+Then, the relation $\tj\geq\tv\geq J^*$ holds.
 \end{lemma}
@@
 Since $\tv\geq T\tv$ it follows that $\tv\geq J^*$. 
-Let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively.
-Now consider the iterative scheme in \eqref{pvi} with $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$.
-It is clear from the definition of $V_0$ that $\tj(i)\geq\Phi r_i(i)\geq V_0(i)$, $i=1,\ldots,n$.
-Also from the monotone property of $T$, we have
-\begin{align}\label{lineq}
-\Phi r_i&\geq V_0,\nn\\
-T\Phi r_i&\geq T V_0,\nn
-\end{align}
+%Let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively. 
+Define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. 
+It is clear from the definition of $V_0$ that $\tj(i), \Phi r_j(i) \geq\Phi r_i(i)\geq V_0(i)$, $1\le i,j \le n$. 
+Also from the monotone property of $T$, we have $T\Phi r_j\geq T V_0$,
 hence we also have,
-$\Phi r_i\geq T\Phi r_i \geq T V_0$, 
+$\Phi r_j\geq T\Phi r_j \geq T V_0$, 
 and so by taking component-wise minimum,
@@
 
-From the first three inequalities in \eqref{lineq}, $\Phi r_i\geq T \Phi r_i\geq T V_0$, $i=1,\dots, n$ and hence $V_0\geq TV_0$.
-Since $V_1=\Gamma V_0$, from the definition of $\Gamma$ in \eqref{gamdef} we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}$, $n\geq 0$.
-So it follows that $\tj\geq V_0\geq V_1\ldots\geq \tv$.
+Now let $V_{n+1} = \Gamma V_n$, $n=0,1,\dots$. Then, $V_1(i) = (\Gamma V_0)(i) = \min\{ V(i) \,:\, V\in \F_{V_0} \}
+\le \min\{ V(i) \,:\, V\ge V_0, V = \Phi r, r\in \N \} \le \min\{ V(i)\,:\, V \ge V_0, V = \Phi r_j, 1\le j \le n \} = V_0(i)$,
+where in the last step we used that $r_1,\dots,r_n \in \N$.
+Hence, $V_1 \le V_0$. Using~\cref{gmonotone}, we then get $V_{n+1}\le V_n$ for $n\ge 0$ and thus 
+$\tj\geq V_0\geq V_1\ldots\geq \tv \geq J^*$.
 \end{proof}

### 2015-06-14 lp.tex
LUB cleanup

@@
 
-The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplpshort} with $\Phi \in \R^{n\times k}$ and the new variables $r\in \R^k$.
+The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplpshort} with $\Phi \in \R^{n\times k}$ and introducing 
+the new variables $r\in \R^k$. 
 By substitution, this leads to
@@
 \end{align}
-Unless specified otherwise we use $\tr$ to denote any solution\todoc{instead of saying the solution} to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. 
+Unless specified otherwise we use $\tr$ to denote any solution 
+to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. 
 The extra constraint added that $J$ lies in the (column) span of $\Phi$ could lead to an infeasible LP.
@@
 \end{assumption}
+Under this assumption \eqref{alp} is thus feasible and since \eqref{alp} is obtained by adding an extra constraint to the LP \eqref{mdplpshort}, the solutions to  \eqref{alp} are bounded and $\tj$ is uniquely defined.
 

### 2015-06-14 lubp.tex
LUB cleanup

@@
 Let $e_j$ denote the $j$th basis vector in the standard Euclidean bases of $\R^n$.
+We make the following assumption on $\N$:
+\begin{assumption}
+\label{ass:n}
+The set $\N$ satisfies the following conditions:
+\begin{enumerate}[(i)]
+\item \label{ass:n1}
+For any $t\in \R$, $t e_1 + \N \eqdef \{ r + t e_1 \,:\, r\in \N \} = \N$, i.e., 
+$\N$ is invariant to shifts by vectors of the form $t e_1$.
+\item \label{ass:n2}
+For $2\le k \le n$, $\sup_{r\in \N} | e_k^\top r | <+\infty$.
+\item \label{ass:n3}
+For each $1\le i \le n$, there exists a solution $r_i\in \R^k$ to the ALP \eqref{alp} with $c = e_i$ such that
+$r_i\in \N$.
+\end{enumerate}
+\end{assumption}
 The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
 \begin{definition}\label{lubpop}
-Given $J\in \R^n$, $c\in \R^n$ positive-valued vector define $r_{c,J}$ to be the solution to 
+Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to 
 \begin{align}
@@
 \begin{split}
- \underset{r\in \N}{\min} &\,\, c^\top \Phi r\,,\\
- \text{s.t.}& \mb \Phi r\geq  TJ\,,
+ \underset{r\in \R^k}{\min} &\,\, c^\top \Phi r\,,\\
+ \text{s.t.}& \mb \Phi r\geq  TJ\,, \qquad r\in \N\,.
  \end{split}
 \end{align}
-where it is assumed that a (bounded) solution exists.
 Then, for $J\in \R^n$, $\Gamma J$,
@@
 \begin{enumerate}
+\item Thanks to \cref{ass:n} \eqref{ass:n1} and \eqref{ass:n2}, 
+for arbitrary $J$ and arbitrary \emph{nonnegative valued} $c$,
+ $\Phi r_{c,J}$ is uniquely defined.
+Indeed, although $r_{c,J}$ might not be unique, but $\Phi r$ where $r$ belongs to the feasible
+ region underlying \eqref{lubplp}, is bounded from below, hence  $\Phi r_{c,J}$ is uniquely defined.
+It also follows that $\Gamma$ is well-defined.
 \item Assuming that $\N$ is polyhedral, 
@@
 \item It holds that $\Gamma J\geq TJ$ (this follows from the fact that if $a\geq c$ and $b\geq c$, then $\min(a,b)\geq c$, where $a, b, c \in \R$).
-\item Given $J\in \R^n$, define $\F_J\eqdef\{\,\Phi r\,|\,\Phi r\geq TJ, r\in \N\,\}$. 
+\item Given $J\in \R^n$, define 
+\begin{align*}
+\F_J\eqdef\{\,\Phi r\,|\,\Phi r\geq TJ, r\in \N\,\}\,.
+\end{align*}
 Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. 
-Further, since $(\Gamma J)(i) = \min\{ V(i) \,|\, V\in \F_J \}$, it also follows that $\Gamma J \le V$ for any $V\in \F_J$.
+Further, since $(\Gamma J)(i) = \min\{ V(i) \,|\, V\in \F_J \}$, it also follows that $\Gamma J \le V$ holds for any $V\in \F_J$.
 %By fixing $c$ in the linear program in \eqref{lubplp} we select a unique vector $\Phi r_c \in \F$.
@@
 \end{remark}
-\begin{definition}\label{bestproj}
-The LUB projection of $J^*$ is denoted by $\bj=\Gamma J^*$. \todoc{It is a bit strange to call this a definition. A numbered equation could be enough.}
-\end{definition}
+%\begin{definition}\label{bestproj}
+%\end{definition}
 We now characterize the LUB projection operator $\Gamma$ in the following lemmas. 
-As mentioned earlier, the error analysis depends on two $\max$-norm contraction operators the first of which is $\Gamma$.
+%As mentioned earlier, the error analysis depends on two $\max$-norm contraction operators the first of which is $\Gamma$.
 The important result of this section is Theorem~\ref{fxpres} and it relates the fixed point $\tv$ of $\Gamma$ to $J^*$.
-\todoc{Poor choice of symbols: $\tv$ is the fixed point of $\Gamma$ and $\hat{V}$ will be the fixed point of $\tilde{\Gamma}$? Hmm.. Not a high priority to change it, but still..}
-In what follows, we let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_\infty$.
+In what follows, we let $r^*\in \R^k$, $\bj\in \R^n$ be defined by
+\begin{align*}
+r^* & \eqdef \argmin_{r\in R^k}||J^*-\Phi r||_\infty\,\\
+\bj & \eqdef \Gamma J^*\,.
+\end{align*}
+If $r^*$ is non-unique, one may choose any minimizer.
+We will now show that $\Gamma$ is a contraction and that its fixed point is close to $J^*$ as long as $\bj$ is closed to $J^*$.
+The following lemma shows that this latter always holds as long as $\Phi$ is well-chosen:
 \begin{lemma}\label{bestbnd}
@@
 
+We now show that $\Gamma$ is a contraction. 
+By \cref{maxnorm}, it suffices to show that $\Gamma$ is monotone and linear along $[\one]$-rays.
+We start with monotonicity.
 \begin{lemma}\label{gmonotone}
@@
 Let $A\in \R^{u\times v}$, $b,c\in \R^u$ and $b_0=Ax_0$ for 
-some $x_0 \in \R^v$, $\N \subset \R^v$. Then
+some $x_0 \in \R^v$, $\N \subset \R^v$ such that $\N =x_0+ \N$. Then
 \begin{align}
-\min\{c^\top Ax:Ax\geq b+b_0, x\in \N\} =\min\{c^\top A y:Ay \geq b, y+x_0 \in \N \}+c^\top b_0.
+\min\{c^\top Ax:Ax\geq b+b_0, x\in \N\} =\min\{c^\top A y:Ay \geq b, y \in \N \}+c^\top b_0.
 \end{align}
@@
 Let $J\in \R^n$ and $t\in \R$ be a constant.
-Then, $\Gamma (J+t\one) = \Gamma J + \alpha t \one$ provided that $r\in \N$ holds if and only $r+s e_1\in \N$ holds for any $s\in \R$.
+Then, $\Gamma (J+t\one) = \Gamma J + \alpha t \one$.
 \end{lemma}
@@
 The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ 
-and $x_0=\alpha t e_1$, noting that by our assumption on $\N$,
-$\{ y\,: \, \Phi y \geq TJ, y + \alpha t e_1\in \N \}
-= \{ y\,: \, \Phi y \geq TJ, y \in \N \}$. \todoc{This is where this assumption is needed.}
+and $x_0=\alpha t e_1$, noting that by our assumption on $\N$, $\N = \N + \alpha t e_1$.
 \end{proof}
@@
 \fi
-Define $\tv$ to be the unique fixed point of $\Gamma$.
+Define $\tv$ denote the unique fixed point of $\Gamma$.
+\todoc{Poor choice of symbols: $\tv$ is the fixed point of $\Gamma$ and $\hat{V}$ will be the fixed point of $\tilde{\Gamma}$? Hmm.. Not a high priority to change it, but still..}
 \begin{lemma}\label{gfp}
@@
 \begin{proof}
-Let $1\le i \le n$. We have $\tv(i) = (\Gamma \tv)(i) = (\Phi r_{e_i,\tv})(i) \ge (T\tv)(i)$.
+From the definitions we have $\tv(i) = (\Gamma \tv)(i) = (\Phi r_{e_i,\tv})(i) \ge (T\tv)(i)$, $1\le i \le n$.
 \if0
@@
 Recall that $\tj$ denotes the solution to the ALP in \eqref{alp}.
+The fixed point of $\Gamma$ is sandwiched between $J^*$ and $\tj$:
 \begin{lemma}\label{relation1}
-Assume that $\N$ is such that if $r_i$ is
-the solution to the ALP in \eqref{alp} for $c=e_i$ then $r_i\in \N$, $1\le i \le n$.
+%Assume that $\N$ is such that if $r_i$ is
+%the solution to the ALP in \eqref{alp} for $c=e_i$ then $r_i\in \N$, $1\le i \le n$.
 % $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey 
-Then, the relation $\tj\geq\tv\geq J^*$ holds.
+The relation $\tj\geq\tv\geq J^*$ holds.
 \end{lemma}
@@
 Since $\tv\geq T\tv$ it follows that $\tv\geq J^*$. 
-%Let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively. 
+Let $r_1, r_2,\ldots, r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively
+such that $r_1,\dots,r_n\in \N$. It is possible to find such solutions thanks to \cref{ass:n} \eqref{ass:n3}.
 Define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. 
@@
 where in the last step we used that $r_1,\dots,r_n \in \N$.
-Hence, $V_1 \le V_0$. Using~\cref{gmonotone}, we then get $V_{n+1}\le V_n$ for $n\ge 0$ and thus 
+Hence, $V_1 \le V_0$. Using the monotone property of $\Gamma$ (i.e., \cref{gmonotone})
+we then get $V_{n+1}\le V_n$ for $n\ge 0$ and thus 
 $\tj\geq V_0\geq V_1\ldots\geq \tv \geq J^*$.

### 2015-06-14 mdp.tex
LUB cleanup

@@
 \end{lemma}
+Operators that satisfy \eqref{eq:shift} are said to be \emph{linear along $[\one]$-rays}.
 From these result, it immediately follows that $T$ is a contraction in the $L_\infty$-norm through the following lemma:

### 2015-06-14 alubp.tex
Refining the meaning of DP, making the intro more precise
ALUBP cleaned

@@
 We define an approximate least upper bound (ALUB) projection operator which has a structure similar to the GRLP and is an approximation to the LUB operator.
+Recall that $W\in \R^{nd\times m}$ is the matrix in \eqref{grlp} which is assumed to satisfy Assumption~\ref{wassump}.
 \begin{definition}\label{alubpop}
-Given $J\in \R^n$, its approximate least upper bound (ALUB) projection is denoted by $\hg J$ and is defined as 
+Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}'$ to be the solution to 
+\begin{align}\label{alubplp}
+ \underset{r\in \R^k}{\min}& \,\mb c^\top \Phi r\,,\nn\\
+ \text{s.t.}& \,\,\, W^\top E \Phi r\geq W^\top HJ\,,\qquad r \in \N\,.
+\end{align}
+Then, for $J\in \R^n$, $\hg J$, the approximate least upper bound (ALUB) projection of $J$ is defined as 
 \begin{align}\label{tgamdef}
-(\hg J)(i)\stackrel{\Delta}{=}(\Phi r_{e_i,J})(i), \mb i=1,\ldots,n,
-\end{align}
-where $r_{e_j}$ is a solution to the linear program in \eqref{alubplp} for $c=e_j$, and $e_j$ is the same as in Definition~\ref{lubpop}.
-\begin{align}\label{alubplp}
-r_{c,J}\stackrel{\Delta}{=} & \underset{r\in \N}{\argmin}\mb c^\top \Phi r,\nn\\
-& \text{s.t.}\,\,\, W^\top E \Phi r\geq W^\top HJ,\,\, W \in \R^{nd\times m}_+ .
+(\hg J)(i)\eqdef(\Phi \har_{e_i,J})(i), \mb i=1,\ldots,n\,.
 \end{align}
 \end{definition}
-Note that $W$ in \eqref{alubplp} is the same matrix that is used in \eqref{grlp} and satisfies Assumption~\ref{wassump}.
+\noindent 
+Note that under our assumptions on $\N$, $\hg$ is well-defined.
+We now show that $\hg$ satisfies the monotone property and is linear along $[\one]$-rays with a factor smaller than one and hence it will follow that it is a contraction.
 \begin{lemma}\label{tgmonotone}
-For $J_1, J_2\in \R^n$ such that $J_1\geq J_2$, we have $\hg J_1\geq \hg J_2$.
+For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
 \end{lemma}
 \begin{proof}
-The proof follows from Assumptions~\ref{wassump} and ~\ref{one} using arguments along the lines of Lemma~\ref{gmonotone}.
+By \cref{wassump}, $W^\top H: \R^n \to \R^m$ is monotone.
+The proof then follows along the lines of Lemma~\ref{gmonotone}.
 \end{proof}
 \begin{lemma}\label{tgshift}
-Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+t\one$, then $\hg J_2=\hg J_1+\alpha t\one$.
+Let $J\in \R^n$ and $t\in \R$ be a constant. Then $\hg (J+t\one)=\hg J+\alpha t\one$.
 \end{lemma}
 \begin{proof}
-The proof follows from Assumption~\ref{wassump} and ~\ref{one}, as well as Lemma~\ref{lpsol} using arguments along the lines of Lemma~\ref{gshift}.
-In particular, consider the $i^{th}$ linear program corresponding to $\hg J_1$ and $\hg J_2$.
-Now, the result follows by letting $A=W^\top E \Phi$, $b=W^\top H J$, $c=e_i$, $b_0=\alpha t \mathbf{1}$, $x_0=\alpha t e_i$.
+The statement follows from Assumptions \ref{one}, \ref{wassump} and \ref{ass:n}, 
+as well as Lemma~\ref{lpsol} using arguments along the lines of Lemma~\ref{gshift}. 
+In particular, consider the $i^{th}$ linear program corresponding to $\hg J$ and $\hg (J+t\one)$. 
+Now, the result follows by letting $A=W^\top E \Phi$, $b=W^\top H J$, 
+$c=e_i$, $b_0=\alpha t \mathbf{1}$, 
+$x_0=\alpha t e_1$,
+noting that thanks to
+\cref{one} and \ref{wassump}, $A x_0 = b_0$ and that thanks to
+\cref{ass:n} \eqref{ass:n1}, $\N = \N + \alpha t e_1$.
 \end{proof}
+From these results, by~\cref{maxnorm} it immediately follows that $\hg$ is an $\alpha$-contraction with respect to the $\max$-norm:
 \begin{theorem}\label{tgmaxcontra}
-The operator $\hg \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$ and the following iterative scheme based on the ALUB projection operator $\hg$, see \eqref{apvi}, converges to a unique fixed point $\hv$.
+The operator $\hg \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$.
+\if0
+ and the following iterative scheme based on the ALUB projection operator $\hg$, see \eqref{apvi}, converges to a unique fixed point $\hv$.
 \begin{align}\label{apvi}
@@
 \end{align}
+\fi
 \end{theorem}
 \begin{proof}
-Follows along similar lines as the proof of Theorem~\ref{gmaxcontra}.
+As noted, this is immediate from \cref{tgmonotone,tgshift} and \cref{maxnorm}.
+%Follows along similar lines as the proof of Theorem~\ref{gmaxcontra}.
 \end{proof}
+In what follows we denote by $\hv$ the unique fixed point of $\hg$:
+\begin{align*}
+\hv = \hg \hv\,.
+\end{align*}
+Recall that $\hj$ denotes the solution $\hj$ of the GRLP \eqref{grlp}. 
+The vector $\hj$ dominates the vector $\hv$:
 \begin{lemma}\label{relation2}
-The unique fixed point $\hv$ of the iteration in \eqref{apvi} and the solution $\hj$ of the GRLP \eqref{grlp} obey $\hj\geq\hv$.
+The vectors $\hv,\hj$ obey $\hj\geq\hv$.
 \end{lemma}
@@
 \todoc[inline]{I lost why this was needed.
-I think the proof would be much easier to understand if we introduced $r_{c,J} = \argmin_{r} \{ c^\top \Phi r \,|\, W^\top E \Phi r \ge W^\top H J\}$.
+I think the proof would be much easier to understand if we introduced $r_{c,J} = \argmin_{r} \{ c^\top \Phi r \,:\, W^\top E \Phi r \ge W^\top H J\}$.
 We could start by saying we need $V_1\le V_0 \le \hj$ because then Lemma~\ref{tgmonotone} will give the desired result.
@@
 \end{proof}
+The next result bounds the distance between $J^*$ and $\hv$ in terms of the distance of $\bj = \Gamma J^*$ and $J^*$, and that between $\bj$ and $\hg J^*$.
 \begin{theorem}\label{mt1}
-Let $\hv$ be the fixed point of the iterative scheme in \eqref{apvi} and let $\bj$ be the best possible LUB approximation of $J^*$ as in Definition~\ref{bestproj}. Then,
+We have
 \begin{align}
-||J^*-\hv||_\infty\leq \frac{||J^*-\bj||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
+||J^*-\hv||_\infty\leq \frac{||J^*-\Gamma J^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
 \end{align}
@@
 \begin{proof}
-Let $\epsilon=||J^*-\bj||_\infty$, and $\{V_n\},n\geq 0$ be the iterates of the scheme in \eqref{apvi} with $V_0=\hg J^*$, then
-\todoc{Can the proof be simplified similarly to that of Theorem~\ref{fxpres}? Not a high priority.}
-\begin{align}
-||J^*-\hg J^*||_\infty&\leq||J^*-\Gamma J^*||_\infty+||\Gamma J^*-\hg J^*||_\infty\nn\\
-&= \epsilon+\beta,
-\end{align}
-where $\beta=||\Gamma J^*-\hg J^*||_\infty$. Now
+By the triangle inequality,
 \begin{align}
@@
 %&\leq (\epsilon+\beta)+\alpha(\epsilon+\beta)+\ldots\nn\\
-%&=\frac{\epsilon+\beta}{1-\alpha}.
+%&=\frac{\epsilon+\beta}{1-\alpha}
 \end{align}
+and so by reordering and another triangle inequality,
+\begin{align*}
+\norm{J^*-\hv}_{\infty} \le \frac{\norm{ J^*-\hg J^*}_{\infty}}{1-\alpha}
+\le \frac{\norm{ J^*-\Gamma J^*}_{\infty}+\norm{\Gamma J^* - \hg J^*}_{\infty}}{1-\alpha}\,.
+\end{align*}
 \end{proof}
+\noindent Combining this result with \cref{bestbnd} gives the following corollary:
 \begin{corollary}\label{cmt1}
-Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\argmin_{r\in \R^k}||J^*-\Phi r||_\infty$, then
+%Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\eqdef\argmin_{r\in \R^k}||J^*-\Phi r||_\infty$, then
+We have
 \begin{align}
@@
 \end{corollary}
-\begin{proof}
-The result is obtained by using Lemma~\ref{bestbnd} to replace the term $||J^*-\bj||_\infty$ in Theorem~\ref{mt1}.
-\end{proof}
+%\begin{proof}
+%The result is obtained by using Lemma~\ref{bestbnd} to replace the term $||J^*-\bj||_\infty$ in Theorem~\ref{mt1}.
+%\end{proof}

### 2015-06-14 lubp.tex
ALUBP cleaned

@@
 \item \label{ass:n2}
-For $2\le k \le n$, $\sup_{r\in \N} | e_k^\top r | <+\infty$.
+For $2\le i \le k$, $\sup_{r\in \N} | e_i^\top r | <+\infty$.
 \item \label{ass:n3}
@@
 \end{assumption}
+Recalling that the first column vector of $\Phi$ is $\one$, \eqref{ass:n1} implies that $\{\Phi r \,:\,r\in \N \}$ is invariant to shifts by constants, a property that will prove to be useful.
+Part~\eqref{ass:n2} is required to guarantee that solutions to the LPs we define below are bounded.
+To satisfy \eqref{ass:n2} and \eqref{ass:n3} simultaneously, it is enough to select $\N$ to be contained in 
+$\{ r = (r_1,\dots,r_k)^\top \in \R^k \,:\, \max_{2\le i \le k} |r_i| \le r_{\max} \}$ with $r_{\max}>0$ sufficiently large.
+\todoc{Can we calculate an a priori bound on how $r_{\max}$ should be? It is a major weakness if we cannot
+suggest a way to define $\N$.}
+
 The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
@@
 \begin{align*}
-\F_J\eqdef\{\,\Phi r\,|\,\Phi r\geq TJ, r\in \N\,\}\,.
+\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\}\,.
 \end{align*}
 Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. 
-Further, since $(\Gamma J)(i) = \min\{ V(i) \,|\, V\in \F_J \}$, it also follows that $\Gamma J \le V$ holds for any $V\in \F_J$.
+Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $\Gamma J \le V$ holds for any $V\in \F_J$.
 %By fixing $c$ in the linear program in \eqref{lubplp} we select a unique vector $\Phi r_c \in \F$.
@@
 We now show that $\Gamma$ is a contraction. 
-By \cref{maxnorm}, it suffices to show that $\Gamma$ is monotone and linear along $[\one]$-rays.
+By \cref{maxnorm}, it suffices to show that $\Gamma$ is monotone and linear along $[\one]$-rays with a factor smaller than one.
 We start with monotonicity.
 \begin{lemma}\label{gmonotone}
-For $J_1, J_2\in \R^n$ such that $J_1\geq J_2$, we have $\Gamma J_1\geq \Gamma J_2$.
+For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\Gamma J_1\leq \Gamma J_2$.
 \end{lemma}
@@
 Choose any $i\in \{1,\ldots,n\}$. 
-Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$.
-Hence, $\F_{J_1} \subset \F_{J_2}$ and thus $(\Gamma J_1)(i) \ge (\Gamma J_2)(i)$. 
+Since $J_1\leq J_2$, we have $TJ_1\leq TJ_2$.
+Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\Gamma J_1)(i) \le (\Gamma J_2)(i)$. 
 Since $i$ was arbitrary, the result follows.
@@
 The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ 
-and $x_0=\alpha t e_1$, noting that by our assumption on $\N$, $\N = \N + \alpha t e_1$.
+and $x_0=\alpha t e_1$, noting that thanks to
+\cref{one}, $A x_0 = b_0$ and that thanks to
+\cref{ass:n} \eqref{ass:n1}, $\N = \N + \alpha t e_1$.
 \end{proof}

### 2015-06-14 alubp.tex
LUBP, ALUBP further minor improvements

@@
 The proof follows in a similar manner as the proof of Lemma~\ref{relation1}.
-To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively.
-Fix some other $c\in [0,1]^n$, $\sum_i c(i)=1$.
-Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$.\par
-We need to show $V_1\le V_0 \le \hj$ and then the desired result follows from Lemma~\ref{tgmonotone}.
-Since $(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $1\leq i,j\leq n$ we have $V_0(i)  = (\Phi r_i)(i)$.
-Also, since $\hj(i) \ge (\Phi r_i)(i),1\leq i \leq n$ it follows that $\hj\geq V_0$.
-Now, for showing that $V_1 \le V_0$ holds, fix any $i$.
-We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi r_{e_i,V_0})(i) \leq V_0(i)$.
-By the definition of $r_{e_i,V_0}$ we know that $(\Phi r_{e_i,V_0})(i) \le (\Phi r)(i)$
-holds for any $r$ such that $W^\top E \Phi r \ge W^\top H V_0$.
-Thus, it suffices to show that $r_i$ satisfies this latter inequality, i.e., $W^\top E \Phi r_i \ge W^\top H V_0$.
-For this, it clearly sufficient if $\Phi r_i \ge V_0$.
+To elaborate, let $ r_1,  r_2,\ldots, r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$, respectively,
+and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.
+
+It suffices to show $V_1\eqdef \hg V_0 \le V_0 \le \hj$ since then the desired result follows
+by defining $V_{n+1} = \hg V_n$, $n\ge 1$, noting that by \cref{tgmonotone}, $V_{n+1}\le V_{n}$ and by  \cref{tgmaxcontra}, $V_n \to \hv$.
+
+Since $(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $1\leq i,j\leq n$ we have $V_0(i)  = (\Phi r_i)(i)$. Also, since $\hj(i) \ge (\Phi r_i)(i),1\leq i \leq n$ it follows that $\hj\geq V_0$. 
+Now,  fix any $i$. 
+We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi \har_{e_i,V_0})(i) \leq V_0(i)$. 
+By the definition of $\har_{e_i,V_0}$ we know that $(\Phi \har_{e_i,V_0})(i) \le (\Phi r)(i)$
+holds for any $r\in \N$ such that $W^\top E \Phi r \ge W^\top H V_0$. 
+Since by \cref{ass:n} \eqref{ass:n4}, $r_i \in \N$, 
+ it suffices to show that $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H V_0$. 
+ By definition, $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H \Phi r_i$.
+ Hence, by the monotone property of $H$ and thanks to
+  \cref{wassump} it is sufficient if $\Phi r_i \ge V_0$.
 This however directly follows from the definition of $V_0$.
-\begin{comment}
-It is clear from the definition of $V_0$ that $\hj(i),(\Phi r_j)(i)\geq(\Phi r_i)(i)$, $i=1,\ldots,n$.
-In particular, it follows that $V_0(i) =( \Phi r_i)(i)$ and so
-$\Phi r_i \geq V_0$.
-From the monotone property of $T$ (viz. $H$) we have 
-$H\Phi r_i\geq H V_0$ and also, by minimizing component-wise
-$E\Phi r_i\geq H\Phi r_i\geq HV_0$. Thus,
-$E V_0\geq H V_0$. 
-\todoc[inline]{I lost why this was needed.
-I think the proof would be much easier to understand if we introduced $r_{c,J} = \argmin_{r} \{ c^\top \Phi r \,:\, W^\top E \Phi r \ge W^\top H J\}$.
-We could start by saying we need $V_1\le V_0 \le \hj$ because then Lemma~\ref{tgmonotone} will give the desired result.
-Next, $V_0\le \hj$ holds because on the one hand, $\hj(i) \ge (\Phi r_i)(i)$ for any $i$, while on the other hand,
-$(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $i,j$, hence $V_0(i)  = (\Phi r_i)(i)$. 
-Now, for showing that $V_1 \le V_0$ holds, fix any $i$.
-We need to show that $(\hg V_0)(i) = \min_j (\Phi r_{e_j,V_0})(i) = (\Phi r_{e_i,V_0})(i)$ is less than $V_0(i)$.
-By the definition of $r_{e_j,V_0}$ we know that $(\Phi r_{e_i,V_0})(i) \le (\Phi r)(i)$
-holds for any $r$ such that $W^\top E \Phi r \ge W^\top H V_0$. Thus, it suffices to show that $r_i$ satisfies this latter inequality,
-i.e., $W^\top E \Phi r_i \ge W^\top H V_0$. For this, it clearly sufficient if $\Phi r_i \ge V_0$. This however directly follows 
-from the definition of $V_0$.
-}
-Since $V_1=\hg V_0$, from the definition of $\hg$ in \eqref{gamdef} and the construction of $V_0$, we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb n\geq 0$.
-So it follows that $\hj\geq V_0\geq V_1\ldots\geq \hv$.
-\end{comment}
 \end{proof}
-The next result bounds the distance between $J^*$ and $\hv$ in terms of the distance of $\bj = \Gamma J^*$ and $J^*$, and that between $\bj$ and $\hg J^*$.
+The next result bounds the distance between $J^*$ and $\hv$ in terms of the distance of $\Gamma J^*$ and $J^*$, and that between $\Gamma J^*$ and $\hg J^*$.
 \begin{theorem}\label{mt1}

### 2015-06-14 lubp.tex
LUBP, ALUBP further minor improvements

@@
 $r_i\in \N$.
+\item \label{ass:n4}
+For each $1\le i \le n$, there exists a solution $r_i\in \R^k$ to the GRLP \eqref{grlp} with $c = e_i$ such that
+$r_i\in \N$.
 \end{enumerate}
@@
 Part~\eqref{ass:n2} is required to guarantee that solutions to the LPs we define below are bounded.
-To satisfy \eqref{ass:n2} and \eqref{ass:n3} simultaneously, it is enough to select $\N$ to be contained in 
+To satisfy \eqref{ass:n2}, \eqref{ass:n3} and \eqref{ass:n4} 
+simultaneously, it is enough to select $\N$ to be contained in 
 $\{ r = (r_1,\dots,r_k)^\top \in \R^k \,:\, \max_{2\le i \le k} |r_i| \le r_{\max} \}$ with $r_{\max}>0$ sufficiently large.
@@
 Define $\tv$ denote the unique fixed point of $\Gamma$.
-\todoc{Poor choice of symbols: $\tv$ is the fixed point of $\Gamma$ and $\hat{V}$ will be the fixed point of $\tilde{\Gamma}$? Hmm.. Not a high priority to change it, but still..}
+\todoc{I am mildly unhappy with denoting the fixed point of $\Gamma$ by $\tv$, but much happier with denoting
+the fixed point of $\hg$ by $\hv$. So this is progress:)}
 \begin{lemma}\label{gfp}
@@
 Also from the monotone property of $T$, we have $T\Phi r_j\geq T V_0$,
-hence we also have,
+hence, by the definition of $r_j$ we also have,
 $\Phi r_j\geq T\Phi r_j \geq T V_0$, 

### 2015-06-14 strel.tex
Mostly streamlining the text in the alp section
s.t. abbreviation corrected
LUBP, ALUBP further minor improvements

@@
 \begin{lemma}\label{srw}
-$\hat{r} \in \R^k$ is a solution to GRLP in \eqref{grlp} iff it solves the following program:
+The vector
+$\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
 \begin{align}\label{grlpeqprog}
 \begin{split}
-\min_{r\in \chi}\, &||\Phi r-\hv||_{1,c}\\
-\text{s.t}\mb & W^\top \Phi r\geq W^\top T \Phi r.
+\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
+\text{s.t.}\mb &\, W^\top \Phi r\geq W^\top T \Phi r\,, \qquad r\in \N\,.
 \end{split}
@@
 The result follows from \eqref{mt2eq1} and Corollary~\ref{cmt1}.
-\end{proof}\\
-\textbf{Prediction Error bound in the $L_\infty$-norm}\\
+\end{proof}
+
+\paragraph{Prediction Error bound in the $L_\infty$-norm.}
 \begin{corollary}\label{cmt2}

### 2015-06-14 strel.tex
polishing

@@
 \begin{lemma}\label{srw}
-The vector
+A vector
 $\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
@@
 \min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
-\text{s.t.}\mb &\, W^\top \Phi r\geq W^\top T \Phi r\,, \qquad r\in \N\,.
+\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r\,, \qquad r\in \N\,.
 \end{split}
@@
 \begin{proof}
-We know from Lemma~\ref{relation2} that $\hj\geq\hv$, and thus minimizing 
+We know from Lemma~\ref{relation2} that $\hj = \Phi \hr \geq\hv$, and thus
+the solutions to \eqref{grlp} do not change if we add the constraint $\Phi r \ge \hv$.
+Now, under this constraint, minimizing $c^\top \Phi r$ is the same as
+ minimizing 
 \begin{align*}
-||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv
+||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.
 \end{align*} 
-is the same as minimizing $c^\top \Phi r$.
 \end{proof}
 \begin{theorem}\label{mt2}
-Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP.
+%Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP.
 Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
+It holds that
 \begin{align}
@@
 \begin{proof}
-Let $\gamma=||J^*-\Phi r^*||_\infty$, then  it is easy to see that
-\begin{align}
-||J^*-T\Phi r^*||_\infty&=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma,\mb\text{and}\nn\\
-||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma.
+Let $\gamma=||J^*-\Phi r^*||_\infty$. Then, since $T$ is an $\alpha$-contraction in the $\max$-norm,
+$||J^*-T\Phi r^*||_\infty=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma$ and hence by the triangle inequality,
+\begin{align}\label{eq:tphir}
+||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma\,.
 \end{align}
-From Assumption~\ref{one} there exists $r'= r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP.
-\todoc{Why not just state that let $r' = r^* + \frac{(1+\alpha)\gamma}{1-\alpha} e_1$?}
-Now
-\begin{align}
-||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty\nn\\&\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
-\label{mt2eq1}
-\end{align}
-Since $r'$ is also feasible for GRLP in \eqref{grlp} we have
+Let $r'= r^*+t e_1$ with $t>0$ to be chosen later.
+Then, from \cref{one},
+$T\Phi r' = T(\Phi r^* + t \one) = T \Phi r^* + \alpha t \one \le \Phi r^* + (\alpha t+ (1+\alpha) \gamma) \one$,
+ where the inequality follows from~\eqref{eq:tphir}.
+ Choosing $t$ so that $t = \alpha t+ (1+\alpha) \gamma$, or $t = \frac{(1+\alpha)\gamma}{1-\alpha}$, we get
+ that $T\Phi r' \le \Phi r'$. Hence, $r'$ is feasible to the ALP \eqref{alp} and 
+since, thanks to \cref{wassump}, 
+any feasible solution to \eqref{alp} is also a feasible solution to the GRLP  \eqref{grlp},
+$r'$ is also feasible to \eqref{grlp}. Thus, 
 \begin{align}
@@
 &\leq||\Phi r'-\hv||_\infty\mb & (\text{since $c$ is a distribution})\nn\\
-&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,.\nn
+&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty\,. & (\text{triangle inequality}) \label{mt2eq0}
 \end{align}
-The result follows from \eqref{mt2eq1} and Corollary~\ref{cmt1}.
+Now, by another triangle inequality,
+\begin{align}
+||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty
+\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
+\label{mt2eq1}
+\end{align}
+The result follows by combining this bound with \eqref{mt2eq0} and Corollary~\ref{cmt1}.
 \end{proof}
 
-\paragraph{Prediction Error bound in the $L_\infty$-norm.}
-\begin{corollary}\label{cmt2}
-Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then \todoc{Where is the effect of $\chi$?}
+\begin{corollary}[Prediction error bound]
+\label{cmt2}
+%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then \todoc{Where is the effect of $\chi$?}
+We have
 \begin{align}\label{finalbnd}
-||J^*-\hj||_{1,c}\leq\frac{6 ||J^*-\Phi r^*||_\infty+2||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
+||J^*-\hj||_{1,c}\leq\frac{6 ||J^*-\Phi r^*||_\infty+2||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}\,.
 \end{align}
@@
 \begin{proof}
-\begin{align}
-||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
-&\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}\nn
-\end{align}
+We have
+$
+||J^*-\hj||_{1,c}\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}
+\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}
+$.
 The result now follows from Corollary~\ref{cmt1} and Theorem~\ref{mt2}.
 \end{proof}
-The results presented in Corollary~\ref{cmt2} is in the $L_\infty$-norm. In the next section, we use of Lyapunov functions to provide an improved bound in a modified $L_\infty$-norm.
+The results presented in Corollary~\ref{cmt2} is in the $L_\infty$-norm. In the next section, we make use of Lyapunov functions to provide an improved bound in the weighted $L_\infty$-norm.

### 2015-06-15 improv.tex
weighted norm section update

@@
 %!TEX root =  autocontgrlp.tex
-\section{Improved Bounds}\label{sec:improv}
-In this section, we present improved error bounds by making use of Lyapunov functions. 
+\section{Bounds using weighted norms}\label{sec:improv}
+In this section, we present error bounds by making use of Lyapunov functions and weighted norms.
+For the purpose of this section, we define $r^*$ to be 
+\begin{align*}
+r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}\,.
+\end{align*}
+where $\psi$ is a Lyapunov function as in \cref{lyap}.
+We also replace \cref{ass:n} \eqref{ass:n1} by the following assumption,
+which is assumed to hold in the rest of this section:
+\begin{assumption}\label{ass:n4}
+The set $\N$ is such that $\N = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ 
+\todoc{Is not this a little problematic? In particular, this seems to contradict \cref{ass:n} \eqref{ass:n2}.
+How can we guarantee that $\Gamma$, $\hg$ are well-defined?
+}
+is the vector such that $\Phi r_0 = \psi$.
+\end{assumption}
 \begin{lemma}\label{bestbndmn}
-Let $r^*\in \R^k$ be defined as $r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}$, then 
+We have
 \begin{align}
-||J^*-\bj||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.
+||J^*-\Gamma J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.
 \end{align}
@@
 \begin{proof}
-The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\mn} \psi\geq TJ^*$.
+The proof parallels that of \cref{bestbnd}.
+%By \cref{lyap}, there exists $r_0 \in \R^k$ such that $\psi = \Phi r_0$.
+Define $\eps = \norm{J^* - \Phi r^*}_{\mn}$ so that
+$|J^*(i) - (\Phi r^*)(i) | \le \eps \psi (i)$, $1 \le i \le n$.
+Then, $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$.
+From this point the proof follows the same steps as those in \cref{bestbnd}
+with the obvious modifications.
+%The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\mn} \psi\geq TJ^*$.
 \end{proof}
 
-Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.
-\begin{lemma}\label{gshiftmn}
-Let $J_1\in \R^n$ and $k\in \R$ be a constant. If $J_2=J_1+k\psi$, then $\Gamma J_2\leq \Gamma J_1+\beta_{\psi} k\psi$.
+Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm, we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.
+The generalization of  \cref{maxnorm} for the weighted $L_{\infty}$ norm is as follows:
+\begin{lemma}\label{maxnormmn}
+Assume that $\Gamma: \R^n \to \R^n$ is monotone and 
+that there exists some $\beta\in [0,1)$ such that for any $J\in \R^n$ and $t>0$,
+\begin{align}
+\label{eq:shiftmn}
+\Gamma( J + t \psi) \le \Gamma J + \beta t \psi\,.
+\end{align} 
+for any $J\in \R^n$ and $t\ge 0$.
+Then $\Gamma$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
 \end{lemma}
 \begin{proof}
-The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
+The proof mimics that of  \cref{maxnorm}:
+First, we show that for any $t\ge 0$,  $J\in \R^n$,
+$\Gamma( J - t \psi) \ge \Gamma J - \beta t \psi$ also holds.
+To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $\Gamma J \le \Gamma J' + \beta t \psi$. Reordering this inequality gives the result.
+Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \R^n$ are arbitrary.
+Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
+By the monotonicity of $\Gamma$,
+$\Gamma(J_2 - \eps \psi) \le \Gamma J_1 \le \Gamma(J_2 + \eps \psi)$. 
+Using~\eqref{eq:shiftmn}, we get 
+$\Gamma J_2 - \beta \eps \psi \le \Gamma J_1 \le \Gamma J_2 + \beta \eps \psi$, i.e., $-\beta \eps \psi \le \Gamma J_1 - \Gamma J_2 \le \beta \eps \psi$, from which the result follows.
 \end{proof}
+Let us note in passing that from this result and~\eqref{eq:linpsi} it immediately follows that $T$ is an $\norm{\cdot}_{\mn}$-contraction with factor $\beta_{\psi}$.
+Returning to $\Gamma$,
+since we already now that $\Gamma$ is monotone (cf. \cref{gmonotone}), it remains to see that it satisfies \eqref{eq:shiftmn}:
+\begin{lemma}\label{gshiftmn}
+The operator $\Gamma$ satisfies \eqref{eq:shiftmn} with $\beta = \beta_\psi$.
+%For any $J\in \R^n$, $t\in \R_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.
+\end{lemma}
+\begin{proof}
+The proof of the first part parallels that of \cref{gshift}:
+%Consider the $i^{th}$ linear programs associated with $\Gamma J$ and $\Gamma (J+ t\one)$. 
+By definition, for $1\le i \le n$,
+$(\Gamma (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, \Phi r \ge T(J+t\psi), r\in \N \}$.
+By \cref{eq:psilin}, as $t>0$, $T(J+t\psi) \le TJ + t \beta \psi$. Thus,
+$(\Gamma (J+t\psi) )(i) \le 
+ \min\{ e_i^\top \Phi r \,:\, \Phi r \ge TJ+t\beta \psi, r\in \N \}$.
+Now, using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$,
+ $b_0=\beta t \psi$ 
+and $x_0=t \beta r_0$, the statement follows
+as thanks to \cref{lyap}, $A x_0 = b_0$ and thanks to
+\cref{ass:n4}, $\N = \N + \alpha t r_0$.
+%The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
+\end{proof}
+From this result and \cref{maxnormmn}, we immediately get that $\Gamma$ is a contraction in $\norm{\cdot}_{\mn}$:
 \begin{theorem}\label{gmaxcontramn}
-The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in weighted $L_\infty$ with factor $\beta_{\psi}$.
+The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
 \end{theorem}
+\if0
 \begin{proof}
@@
 \end{proof}
-\begin{corollary}\label{hgmaxcontramn}
-$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
-\end{corollary}
+\fi
+In a similar way, one can also show that $\hg$ is also a contraction:
+\begin{theorem}\label{hgmaxcontramn}
+The operator $\hg:\R^n\to\R^n$  is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
+%$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
+\end{theorem}
 \begin{proof}
-Follows from arguments similar to Theorem~\ref{gmaxcontramn}.
+We already know that $\hg$ is monotone. That $\hg$ satisfies~\cref{eq:shiftmn}
+with $\beta = \beta_{\psi}$ follows similarly to the argument used in  \cref{tgshift}
+with modifications similar to those introduced in the proof of \cref{gshiftmn}.
+Then, \cref{gmaxcontramn} gives the desired result.
 \end{proof}
@@
 \begin{proof}
-The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\mn}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
+The proof follows from \cref{gmaxcontramn}, \cref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\mn}$ in the arguments presented in 
+Sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to \cref{cmt1}.
 \end{proof}
 
-We now recall Lemma~$4.5$ of \cite{ALP}. \todoc{You had 4.3 here, but in the official journal version this seems to be Lemma 5 in Section 4.}
+We now recall Lemma~$5$ from Section 4.2 of \cite{ALP}. 
+For this result, recall that $r_\in \R^k$ is the vector such that $\psi = \Phi r_0$ by assumption.
 \begin{lemma}\label{restate}
-Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ , $r \in \R^k$ be an arbitrary vector and let $r'$ be such that
+%Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ ,
+For  $r \in \R^k$ arbitrary vector, let $r'$ be
 \begin{align}
-\Phi r'=\Phi r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, \psi.
+ r'= r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0.
 \end{align}
@@
 \end{lemma}
+Recall that $\hv$ is the fixed point of $\hg$ and $\hj=\Phi \hr$ is the solution to the GRLP
+\eqref{grlp}. 
 \begin{theorem}\label{mt2mn}
-Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP.
-Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\mn}$ be the error due to ALUB projection and let $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\mn}$, then
+We have
 \begin{align}
@@
 \begin{proof}
-Let $\gamma=||J^*-\Phi r^*||_{\mn}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
-\begin{align}
-||\Phi r'-J^*||_{\mn}&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
-&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
-&=\frac{2}{1-\beta_\psi}\gamma.\nn
-\end{align}
+Let $\gamma=||J^*-\Phi r^*||_{\mn}$. 
+Then, by choosing $r'$ as in Lemma~\ref{restate} we have
+\begin{align*}
+||\Phi r'-J^*||_{\mn}&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn
+=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn
+=\frac{2}{1-\beta_\psi}\gamma.\nn
+\end{align*}
 Since $r'$ is also feasible for the GRLP in \eqref{grlp} we have
 \begin{align}
-||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\
-&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
-&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
-&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).
+||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn
+=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
+&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn
+\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).
 \end{align}
-The result follows from Corollary~\ref{cmt1}.\\
-\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
+The result follows from \cref{cmt1mn}.
+%\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
 \end{proof}
-\begin{theorem}\label{cmt2mn}
-Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
+\begin{theorem}[Prediction error bound in $\norm{\cdot}_{\mn}$]
+\label{cmt2mn}
+%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
+It holds that
 \begin{align}\label{finalbndmn}
@@
 \begin{proof}
+We have
 \begin{align}
-||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
-&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
+||J^*-\hj||_{1,c}
+&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn
+\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
 \end{align}

### 2015-06-15 lp.tex
weighted norm section update

@@
 $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
-and is present in the column span of the feature matrix $\Phi$.
+and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$.
 \end{assumption}
@@
 In what follows we will always assume that Assumptions \ref{probdist}--\ref{lyap} hold. 
+When \cref{lyap} holds, it follows that for any $J\in \R^n$, $t>0$, $s\in S$,
+\begin{align*}
+(T(J+ t \psi))(s) &= 
+\max_{a} g_a(s) + \alpha \sum_{s'} p_a(s,s') J(s') + t \alpha  \sum_{s'} p_a(s,s') \psi(s') \\
+& \le 
+\max_{a} g_a(s) + \alpha \sum_{s'} p_a(s,s') J(s') + t \beta_{\psi} \psi(s) \\
+& = (T J)(s) + \beta_{\psi}\,t\,  \psi(s),
+\end{align*}
+or, in short,
+\begin{align}
+\label{eq:psilin}
+T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,\, \quad (J\in \R^n,\, t>0)\,.
+\end{align}
 

### 2015-06-15 polbnd.tex
weighted norm section update

@@
 %!TEX root =  autocontgrlp.tex
-\textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\
+%\textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\
 We now bound the performance of the greedy policy $\hu$.
-\begin{theorem}\label{polthe}
-Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function. Let $r^*$ be as in Theorem~\ref{mt2mn}, then
+\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\mn}$]
+\label{polthe}
+Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
+% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
+Then,
 \begin{align}\label{polthebnd}
-||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(6 ||J^*-\Phi r^*||_{\mn}
+%||J_{\hu}-\hj||_{1,c}
+\norm{J^* - J_{\hu}}_{1,c}
+&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2\, \big(6 ||J^*-\Phi r^*||_{\mn}
 %\nn\\&
@@
 \begin{proof}
+By the triangle inequality,
+\begin{align*}
+||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\,.
+\end{align*}
+Let us now bound the second term on the right-hand side.
+Since $\hu$ is greedy w.r.t. $\hj$, it holds that $T_{\hu} \hj = T \hj$.
+Also, $T_{\hu} J_{\hu} = J_{\hu}$.
+Hence, $J_{\hu} - \hj = T_{\hu} J_{\hu} - T_{\hu} \hj + T \hj - \hj
+=\alpha P_{\hu} (J_{\hu}- \hj) + T\hj - \hj$.
+Hence,
 \begin{align}\label{polderv}
@@
 &\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
-&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
+%&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
 &\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
@@
 \end{align}
-where in the second inequality, for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. Now
+where in the second inequality, we use Jensen's inequality and $|T\hj - \hj|$ stands for the 
+vector whose $i$th component is $|(T\hj)(i) - \hj(i)|$ and the last inequality follows
+since $T$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta_{\psi}$, as we noted it earlier.
+%componentwise  $(I-\alpha P_{\hu})^{-1}$ is a positive operator for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. 
+Hence,
 \begin{align}
-||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
+||J^*-J_{\hu}||_{1,c}
+%&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
 &\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
@@
 \end{align}
-The result now follows by substituting the value of $||J^*- \hj||_{\mn}$ from Corollary~\ref{cmt2mn}.
+The result now follows by substituting the bound on $||J^*- \hj||_{\mn}$ from \cref{cmt2mn}.
 \end{proof}
 \begin{note}
-By letting $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}+||J^*-\hg J^*||_{\mn}$ (inequality follows from Lemma~\ref{bestbndmn}), we can also modifiy the bounds in \eqref{finalbnd} and \eqref{polthe} as
+By bounding $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}+||J^*-\hg J^*||_{\mn}$ 
+(the inequality follows from \cref{bestbndmn}), 
+we can loosen the bounds in \cref{cmt2mn} and \cref{polthe} to
 \begin{align}
-\label{loose1}||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
+\label{loose1}
+||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
 %\nn\\&
 +2||J^*-\hg J^*||_{\mn}).\\
-\label{loose2}||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(10 ||J^*-\Phi r^*||_{\mn}
+\label{loose2}
+||J^* - J_{\hu}||_{1,c}&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2 \,\big(10 ||J^*-\Phi r^*||_{\mn}
 %\nn\\&
@@
 Here the term $||J^*-\hg J^*||$ in \eqref{loose1} and \eqref{loose2} captures the error due to the use of both $\Phi$ and $W$.
-Though, \eqref{loose1} and \eqref{loose2} might be loser bounds than \eqref{finalbndmn} and \eqref{polthebnd} respectively, the aim here is to capture the error due to function approximation as well as constraint reduction in a single term.
+Though, \eqref{loose1} and \eqref{loose2} might be loser bounds than \eqref{finalbndmn} and \eqref{polthebnd} respectively, the advantage of this bound is that it captures the error due to function approximation as well as constraint reduction in a direct manner.
 \end{note}

### 2016-07-08 constsampshort.tex
Chandru's shortened version

--- 2015-06-13 constsamp.tex
@@
 \begin{align}\label{rlp}
-\begin{split}
-\min_{r\in \N}\, &c^\top \Phi r\\
-\text{s.t}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \mb (s,a) \in \I\,,
-\end{split}
+\min_{r\in \N}\, &c^\top \Phi r\nn\\
+\text{s.t.}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \nn\\
+&\forall (s,a) \in \I.
 \end{align}
-where $\I$ is the index set containing $m$ sampled state-action pairs and
-the extra constraint set $\N\subset \R^k$ is introduced to guarantee a bounded feasible set (hence, bounded solution).
-It is assumed that $\N$ is compact and $\tr\in \N$. \todoc{How can one arrange for this in general?}
-The index set $\I$ naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
+where $\I$ is the index set containing $m$ sampled state-action pairs and the extra constraint set $\N$ is introduced to guarantee a bounded solution.
+Note that apart from $r\in \N$ the feasible set of the RLP is a superset of the feasible set of the ALP.
+\begin{comment}
+The index set $\I$ in \eqref{rlp} naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
 \begin{definition}\label{csampmat}
@@
 \min_{r\in \N}\, &c^\top \Phi r\\
-\text{s.t}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
+\text{s.t.}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r\,.
 \end{split}
 \end{align}
-Note that apart from $r\in \N$ the feasible set of the RLP is a superset of the feasible set of the ALP.
-
-The RLP based on constraint sampling has been found to perform well empirically in application domains ranging from controlled queuing networks (see section $6.2$ of \cite{ALP} and section $7$ of \cite{SALP}) to Tetris (see \cite{CST} and section $6$ of \cite{SALP}).
-However, the theoretical guarantees for the RLP are available only under a restricted setting \cite{CS}.
-We present the main result of \cite{CS} on constraint sampling, and to that end define the following quantities:
-%\begin{definition}\label{sampdist}
-Given a policy $u$, a Lyapunov function $\psi$ in the column span of $\Phi$
-and a probability distribution $c$ over the states
-we define probability distributions $\mu_{u,c}$, $\mu_{u,\c,\psi}$ and constant $\theta_{u,c,\psi}$ as 
-\begin{align}
-\mu_{u,c}^\top& \eqdef (1-\alpha)c^\top (I-\alpha P_u)^{-1},\nn\\
-\mu_{u,c,\psi}(s,a)&\eqdef (d \, \mu_u^\top \psi)^{-1} \, \mu_{u}(s) \psi(s),\nn\qquad s\in \S,a\in  \A\,,\\
-\theta_{u,c,\psi} &\eqdef\mfrac{(1+\beta_{\psi})}{2} \, \mfrac{\mu_{u,c}^\top \,\psi}{c^\top J^*}\, \sup_{r\in \N}||J^*-\Phi r||_{\mn}.
-\end{align}
-%\end{definition}
-We now recall Theorem~$3.1$ of \cite{CS} below. \todoc{Assumptions? }
-\begin{theorem}\label{csresult}
-Let $\epsilon$ and $\delta$ be scalars in $(0,1)$,
-$\theta = \theta_{u^*,c,\psi}$ where $u^*$ is an optimal policy.
-Let $\I$ be an index set obtained by sampling $m$ state-action pairs 
-	independently according to the distribution $\mu_{u^*,c,\psi}$,
-	\todoc{Their Lyapunov function definition is slightly different. Which one is the real one needed by this result?}
-	where%
-	\footnote{Note that the cardinality of $\I$ might be smaller than $m$.}
-\begin{align}
-m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\left(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\right).
-\end{align}
-Let $\tilde{r}$ be an optimal	solution of the ALP and let $\hat{r}$ be the solution of the corresponding RLP. 
-Then, with probability at least $1-\delta$, we have
-\begin{align}
-||J^*-\Phi \hat{r}||_{1,c}\leq ||J^*-\Phi \tilde{r}||_{1,c}+\epsilon||J^*||_{1,c}.
-\end{align}
-\end{theorem}
-\noindent \textbf{Motivation for our work:}
-As noted by the authors of \cite{CS}, this result is best viewed as a
-	theoretical illustration of the potential of constraint sampling:
-	sampling from $\mu_{u^*,c,\psi}$ will more often than not be infeasible in practice
-	as this distribution is dependent on the optimal policy $u^*$.
-However, as mentioned before, the RLP has performed reasonably well 
-	even when the sampling distribution is not $\mu_{u^*,\psi}$. 
-Thus there is a gap between the theoretical understanding of the RLP 
-	and its practical efficacy which merits our attention. 
-The gap also indicates that the RLP might be a special case 
-	of a generalized constraint reduction scheme with provable performance guarantees. 
-Understanding such a generalized method would result in an ALP based ADP technique 
-	that would have theoretical performance guarantees while being practically useful. 
-In particular, we wish to answer the following open questions.
-\begin{itemize}
-\item  As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?
-\item Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
-\end{itemize}
-In this paper, we address both of the questions above.
+The error bounds for the RLP can be found in \cite{CS} and the RLP has been shown to perform well in experiments \cite{ALP,CS,CST} in various domains such as Tetris and in network of queues.
+An alternative to constraint sampling is to introduce function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}.
+While such an approach has been applied in practice, there are no known theoretical guarantess for function approximation of the dual variables.\par
+In the next section, we present the generalized reduced linear program (GRLP) which is the main object of study in this paper.
+\end{comment}

### 2016-07-08 errana.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Error Analysis}\label{sec:errana}
We now define the two projection operators which are central to our error analysis. The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
\begin{definition}\label{lubpop}
Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to 
\begin{align}
\label{lubplp}
\begin{split}
 \underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,,\\
 \text{s.t.}& \mb \Phi r\geq  TJ.
 \end{split}
\end{align}
Then, for $J\in \R^n$, $\Gamma J$,
the least upper bound projection of $J$ is defined as 
\begin{align}\label{gamdef}
(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
\end{align}
\end{definition}
\begin{remark}\label{ubrem}
To understand the meaning of $\Gamma$ (and $\hg$) define 
\begin{align}\label{ubclass}
\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
\end{align}
where $J\in \R^n$. Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
\end{remark}
The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
\begin{definition}\label{alubpop}
Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}$ to be the solution to 
\begin{align}\label{alubplp}
 \underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,,\nn\\
 \text{s.t.}& \,\,\, W^\top E \Phi r\geq W^\top HJ.
\end{align}
Further, define $\hg J$  as 
\begin{align}\label{tgamdef}
(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,.
\end{align}
\end{definition}
\begin{lemma}\label{lpsol}
Let $A\in \R^{u\times v}$, $b,c\in \R^u$ and $b_0=Ax_0$ for 
some $x_0 \in \R^v$, $\N' \subset \R^v$ such that $\N' =x_0+ \N'$. Then
\begin{align}
&\min\{c^\top Ax:Ax\geq b+b_0, x\in \N'\} \nn\\
&=\min\{c^\top A y:Ay \geq b, y \in \N' \}+c^\top b_0.
\end{align}
\end{lemma}
\begin{proof}
The claim follows by the change of variables $y := x-x_0$.
\end{proof}
\noindent 
%Note that under our assumptions on $\N$, $\hg$ is well-defined.
%\begin{align*}
%r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}\,.
%\end{align*}
%where $\psi$ is a Lyapunov function as in \cref{lyap}.
\begin{lemma}\label{bestbndmn}
We have
\begin{align}
||J^*-\Gamma J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.
\end{align}
\end{lemma}
\begin{proof}
Define $\eps = \norm{J^* - \Phi r^*}_{\mn}$ so that
$ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$. Then from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$. From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$. The result follows by noting that $2\eps\psi\geq \Phi r^*+\eps\psi -J^*\geq \Gamma J^*-J^*\geq 0$.
\end{proof}
\begin{lemma}\label{tgmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
\end{lemma}
\begin{proof}
Given $J\in \R^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$. Choose any $i\in \{1, \ldots, n\}$. Since $J_1\leq J_2$, from \cref{monotone} and \cref{grlpassmp}-\eqref{wassump} it follows that $W^\top H J_1\leq W^\top H J_2$. Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.  Since $i$ was arbitrary, the result follows. 
\end{proof}
\begin{lemma}\label{maxnormmn}
Assume that $\hg: \R^n \to \R^n$ is monotone and 
that there exists some $\beta\in [0,1)$ such that for any $J\in \R^n$ and $t>0$,
\begin{align}
\label{eq:shiftmn}
\hg( J + t \psi) \le \hg J + \beta t \psi,
\end{align} 
for any $J\in \R^n$ and $t\ge 0$.
Then $\hg$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
\end{lemma}
\begin{proof}
First, we show that for any $t\ge 0$,  $J\in \R^n$,
$\hg( J - t \psi) \ge \hg J - \beta t \psi$ also holds.
To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $\hg J \le \hg J' + \beta t \psi$. Reordering this inequality gives the result.
Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \R^n$ are arbitrary.
Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
By the monotonicity of $\hg$,
$\hg(J_2 - \eps \psi) \le \hg J_1 \le \hg(J_2 + \eps \psi)$. 
Using~\eqref{eq:shiftmn}, we get 
$\hg J_2 - \beta \eps \psi \le \hg J_1 \le \hg J_2 + \beta \eps \psi$, i.e., $-\beta \eps \psi \le \hg J_1 - \hg J_2 \le \beta \eps \psi$, from which the result follows.
\end{proof}
\begin{corollary}\label{tmaxnormmn}
$T$ is a $\norm{\cdot}_{\mn}$-contraction with factor $\beta_{\psi}$.
\end{corollary}
%Returning to $\hg$, since we already now that $\hg$ is monotone (cf. \cref{gmonotone}), it remains to see that it satisfies \eqref{eq:shiftmn}:
\begin{lemma}\label{gshiftmn}
The operator $\hg$ satisfies \eqref{eq:shiftmn} with $\beta = \beta_\psi$.
%For any $J\in \R^n$, $t\in \R_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.
\end{lemma}
\begin{proof}
By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N' \}$.
By \eqref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta_\psi \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi \psi)$. Thus,
$(\hg (J+t\psi) )(i) \le 
 \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
Now, using Lemma~\ref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $c=e_i$, $b_0=t\beta_\psi \psi$ 
and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
%The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
\end{proof}
%From this result and \cref{maxnormmn}, we immediately get that $\Gamma$ is a contraction in $\norm{\cdot}_{\mn}$:
\begin{comment}
\begin{theorem}\label{gmaxcontramn}
The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
\end{theorem}
\end{comment}
%In a similar way, one can also show that $\hg$ is also a contraction:
\begin{theorem}\label{hgmaxcontramn}
The operator $\hg:\R^n\to\R^n$  is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
%$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
\end{theorem}
\begin{proof}
Follows from \cref{maxnormmn} and \cref{gshiftmn}.
\begin{comment}
We already know that $\hg$ is monotone. That $\hg$ satisfies~\cref{eq:shiftmn}
with $\beta = \beta_{\psi}$ follows similarly to the argument used in  \cref{tgshift}
with modifications similar to those introduced in the proof of \cref{gshiftmn}.
Then, \cref{gmaxcontramn} gives the desired result.
\end{comment}
\end{proof}
In what follows we denote by $\hv$ the unique fixed point of $\hg$ i.e., $\hv = \hg \hv\,$. 
We now show that the vector $\hj$ dominates the vector $\hv$:
\begin{lemma}\label{relation1}
The vectors $\hv,\hj$ obey $\hj\geq\hv$.
\end{lemma}
\begin{proof}
Let $ r_1,  r_2,\ldots, r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$, respectively,
and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.

It suffices to show that $V_1\eqdef \hg V_0 \le V_0 \le \hj$ since then the desired result follows
by defining $V_{n+1} = \hg V_n$, $n\ge 1$, noting that by \cref{tgmonotone}, $V_{n+1}\le V_{n}$ and by  \cref{tmaxnormmn}, $V_n \to \hv$.

Since $(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $1\leq i,j\leq n$ we have $V_0(i)  = (\Phi r_i)(i)$. Also, since $\hj(i) \ge (\Phi r_i)(i),1\leq i \leq n$ it follows that $\hj\geq V_0$. 
Now,  fix any $i$. 
We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi r'_{e_i,V_0})(i) \leq V_0(i)$. 
By the definition of $r'_{e_i,V_0}$ we know that $(\Phi r'_{e_i,V_0})(i) \le (\Phi r)(i)$
holds for any $r\in \N$ such that $W^\top E \Phi r \ge W^\top H V_0$. 
Now it suffices to show that $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H V_0$. 
By definition, $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H \Phi r_i$.
Hence, by the monotone property of $H$ and \cref{grlpassmp}-\eqref{wassump} it is sufficient if $\Phi r_i \ge V_0$.
This however directly follows from the definition of $V_0$.
\end{proof}
\begin{lemma}\label{relation2}
The vectors $\hv,\tj$ obey $\tj\geq\hv$.
\end{lemma}
\begin{proof}
%The proof follows in a similar manner as the proof of \Cref{relation1}. To elaborate, 
Let $ r_1,  r_2,\ldots, r_n$ be solutions to the ALP in \eqref{alp} (with an additional constraint that the solution be restricted to $\N$) for $c=e_1, e_2,\ldots,e_n$, respectively,
and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 
follows in the same manner as the proof of \cref{relation1}.
\end{proof}
\begin{lemma}\label{srw}
A vector
$\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\begin{split}
\min_{r\in \N}\, &||\Phi r-\hv||_{1,c}\\
\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r.
\end{split}
\end{align}
\end{lemma}
\begin{proof}
We know from Lemma~\ref{relation2} that $\hj = \Phi \hr \geq\hv$, and thus
the solutions to \eqref{grlp} do not change if we add the constraint $\Phi r \ge \hv$.
Now, under this constraint, minimizing $c^\top \Phi r$ is the same as minimizing 
\begin{align*}
||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.
\end{align*} 
\end{proof}
\begin{lemma}\label{srwalp}
A vector
$\tr \in \R^k$ is a solution to ALP \eqref{alp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\begin{split}
\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
\text{s.t.}\mb &\, \Phi r\geq  T \Phi r.
\end{split}
\end{align}
\end{lemma}
\begin{proof}
We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$, and the rest of the arguments follow in the same manner as proof for \cref{srw}.
\end{proof}
\begin{lemma}\label{cmt1mn}
We have
\begin{align}
||J^*-\hv||_{\mn}&\leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}&\nn\\+||\Gamma J^*-\hg J^*||_{\mn}\big).
\end{align}
\end{lemma}
\begin{proof}
Recall that $\hg \hv=\hv$. By the triangle inequality,
\begin{align*}
&||J^*-\hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+||\hg J^*-\hg \hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+\beta_\psi || J^*- \hv||_\mn,
\end{align*}
and so by reordering and with another triangle inequality,
\begin{align}\label{jhv}
&\norm{J^*-\hv}_{\mn} \nn\\&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\nn\\
&\le \frac{\norm{ J^*-\Gamma J^*}_{\mn}+\norm{\Gamma J^* - \hg J^*}_{\mn}}{1-\beta_\psi}\,.
\end{align}
The proof follows by applying \cref{bestbndmn} on \eqref{jhv}.
\end{proof}
We now recall Lemma~$5$ from Section 4.2 of \cite{ALP}. 
For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$ by assumption.
\begin{lemma}\label{restate}
%Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ ,
For  $r \in \R^k$ arbitrary vector, let $r'$ be
\begin{align}
 r'= r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0.
\end{align}
Then $r'$ is feasible for the ALP in \eqref{alp}.
\end{lemma}
Recall that $\hv$ is the fixed point of $\hg$ and $\hj=\Phi \hr$ is the solution to the GRLP
\eqref{grlp}. 
\begin{theorem}\label{mt2mn}
We have
\begin{align}
||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn\\
&+||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_{\mn}$. 
Then, by choosing $r'$ as in Lemma~\ref{restate} we have
\begin{align}\label{part}
&||\Phi r'-J^*||_{\mn}\nn\\&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.
\end{align}
%We know that $\tr \in \N$ by \cref{grlpassmp}-\eqref{nassmp} and 
$r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. Then from \cref{srwalp} it follows that
%As a result, from \cref{srw} it follows that
\begin{align}
&||\hj-\hv||_{1,c}\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\
&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).
\end{align}
The result follows from \cref{cmt1mn} and \eqref{part}.
%\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
\end{proof}
\begin{theorem}[Prediction error bound in $\norm{\cdot}_{\mn}$]
\label{cmt2mn}
%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
It holds that
\begin{align}\label{finalbndmn}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\nn\\
&+2||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
We have
\begin{align}
&||J^*-\hj||_{1,c}\nn\\
&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
\end{align}
The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
\end{proof}
We now bound the performance of the greedy policy $\hu$.
\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\mn}$]
\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
Then,
\begin{align}\label{polthebnd}
%||J_{\hu}-\hj||_{1,c}
\norm{J^* - J_{\hu}}_{1,c}
&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2\, \big(6 ||J^*-\Phi r^*||_{\mn}
\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}\big).
\end{align}
\end{theorem}
\begin{proof}
By the triangle inequality,
\begin{align*}
||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\,.
\end{align*}
Let us now bound the second term on the right-hand side.
Since $\hu$ is greedy w.r.t. $\hj$, it holds that $T_{\hu} \hj = T \hj$.
Also, $T_{\hu} J_{\hu} = J_{\hu}$.
Hence, $J_{\hu} - \hj = T_{\hu} J_{\hu} - T_{\hu} \hj + T \hj - \hj
=\alpha P_{\hu} (J_{\hu}- \hj) + T\hj - \hj$.
Hence,
\begin{align}\label{polderv}
&||J_{\hu}-\hj||_{1,c}\nn\\&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
&\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
&\leq c^\top (I-\alpha P_{\hu})^{-1} \psi ||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
%&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})||J^*- \hj||_{\mn},
\end{align}
where in the second inequality, we use Jensen's inequality and $|T\hj - \hj|$ stands for the 
vector whose $i$th component is $|(T\hj)(i) - \hj(i)|$. Further, the last inequality follows
since $T$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta_{\psi}$ as noted earlier.
%componentwise  $(I-\alpha P_{\hu})^{-1}$ is a positive operator for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. 
Hence,
\begin{align}
&||J^*-J_{\hu}||_{1,c}\nn\\
%&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
&=\frac{2c^\top \psi}{1-\beta_{\psi}}||J^*- \hj||_{\mn}.
\end{align}
The result now follows by substituting the bound on $||J^*- \hj||_{\mn}$ from \cref{cmt2mn}.
\end{proof}
\begin{comment}
\begin{note}
By bounding $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}+||J^*-\hg J^*||_{\mn}$ 
(the inequality follows from \cref{bestbndmn}), 
we can loosen the bounds in \cref{cmt2mn} and \cref{polthe} to
\begin{align}
\label{loose1}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
\nn\\&
+2||J^*-\hg J^*||_{\mn}).\\
\label{loose2}
||J^* - J_{\hu}||_{1,c}&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2 \,\big(10 ||J^*-\Phi r^*||_{\mn}
\nn\\&
+2||J^*-\hg J^*||_{\mn}\big).
\end{align}
Here the term $||J^*-\hg J^*||$ in \eqref{loose1} and \eqref{loose2} captures the error due to the use of both $\Phi$ and $W$. Though, \eqref{loose1} and \eqref{loose2} might be loser bounds than \eqref{finalbndmn} and \eqref{polthebnd} respectively, the advantage of this bound is that it captures the error due to function approximation as well as constraint reduction in a direct manner.
\end{note}
\end{comment}

### 2016-07-08 grlp.tex
polishing
Chandru's shortened version

@@
 \section{Generalized Reduced Linear Program}
-In this section we present the generalized reduced linear program (GRLP) which is obtained by replacing the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP.
-Formally, we define the generalized reduced linear program (GRLP) as follows:
+\begin{assumption}\label{grlpassmp}
+\begin{enumerate}[(i)]
+\item \label{probdist} $c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0 \mb \forall i$ and $\sum_{i=1}^n c(i)=1$.
+\item  \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
+\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
+and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$. 
+\item \label{nassmp} $\N\subset \R^k$ is compact and $\tr \in \N\subset\R^k$.
+\item \label{wassump} $W \in \R^{nd\times m}_+$ is a full rank $nd\times m$ matrix (where $m\ll nd$), with all non-negative entries such that each of its column-sums equals one.
+\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
+\end{enumerate}
+\end{assumption}
+When \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$, $t>0$, $s\in S$,
+\begin{align}
+\label{eq:psilin}
+T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,\, \quad (J\in \R^n,\, t>0)\,.
+\end{align}
+The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$.
+By substitution, this leads to
+\begin{align}\label{alp}
+\begin{split}
+\min_{r\in \R^k}\, &c^\top \Phi r\\
+\text{s.t.}\mb &\Phi r\geq T \Phi r,
+\end{split}
+\end{align}
+where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}.
+Unless specified otherwise we use $\tr$ to denote any solution to the ALP, $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
+The Generalized Reduced Linear Program is given as:
 \begin{align}\label{grlp}
@@
 \end{align}
-where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and 
-$\N \subset \R^k$ is a set such that $\tilde{r}_c \in \N$. 
-\todoc{Changed the definition and using $\N$ that was used in the definition of RLP.}
-The role of $\N$, as in the case of RLPs, is to guarantee
-the existence of bounded solutions. \todoc{We'll be trouble with $\N$ if we start assume that it is a bounded set. See below.}
-
-The $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP.
-Constraint reduction is achieved by choosing $m\ll nd$.
-The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone.
-Also note that an RLP is trivially a GRLP as well with a random matrix $W$.
-Unless specified otherwise, we use $\hr$ to denote any solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
-Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column).
-Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive.
-Then, normalizing the columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP.
-Keeping these in mind we also assume the following throughout the rest of the paper:
-\begin{assumption}\label{wassump}
-$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m\ll nd$) and each of its column-sums equals one.
-\end{assumption}
-\begin{comment}
-The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.
-\end{comment}
-\input{cartoon}
-\todoc{The picture needs to be perfected.}
-The rest of the paper develops analytically various performance bounds and our main results provide the following:
-\begin{enumerate}
-\item A bound for $||J^*-\hj||$, the error between the approximate value function $\hj$ as computed by the GRLP and the optimal value function $J^*$;
-\item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
-\item an important result on constraint sampling. \todoc{we should be more specific}
-\end{enumerate}
-We achieve the above via two novel $\max$-norm contraction operators namely the least upper bound (LUB) projection operator (denoted by $\Gamma$) and the approximate least upper bound (ALUB) projection operator (denoted by $\hat{\Gamma}$).
-We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$.
-We first establish our results in the $L_\infty$-norm and then in a weighted $L_\infty$-norm.
-The schematic in Fig.~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
-\FloatBarrier
-\input{schematic}
-\todoc{$d_1$ and $d_2$ use different norms?}
+where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional constraint set to ensure the boundedness of the solution.
+In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.

### 2016-07-08 intro.tex
Chandru's shortened version

--- 2015-06-05 intro.tex
@@
-%!TEX root =  autocontgrlp.tex
-\section{Introduction}\label{intro}
-Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs).
-A policy $u$, is a mapping from state space to action space and it specifies the action selection mechanism.
-The problem of \emph{control} requires coming up with good policies and for which one needs to \emph{predict} the behavior of individual policies.
-The problem of \emph{prediction} deals with computing the value-function $J_u$(a mapping from state space to reals\footnote{Also known as reward/cost-to-go function.}) which specifies the value of each state under a given policy $u$.
-\todoc{How is the MDP given?
-If it is given as a list of values, just reading the values may take too much time.
-Or we assume sparsity?
-Or we assume that one can query the next state distribution at any state-action?
-These yield to different models.
-We should specify which one we work with (presumably the sparse is the easiest).
-}Ideally, we are be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$.
-The Bellman equation (BE) relates these quantities and in particular $u^*$ can be obtained as a `greedy/one-step look ahead' policy by substituting $J^*$ in the BE.
-Conventional solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming can compute exact values of $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation.
-By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems.
-However, in the case of MDPs with large number of states, computing $u^*$ and $J^*$ using the exact methods is infeasible.
-\todoc{Do we have a source to cite here?
-What does it mean to solve an MDP anyways?
-Find an optimal policy?
-Find a near-optimal policy?
-I think the story is that knowing the optimal value function helps, but I have not seen any claim that it is \emph{necessary} to compute it to find.}
-
-\emph{Approximate dynamic programming} (ADP) \cite{dpchapter,powell} refers to a gamut of approximate solution methods to MDPs with large number of states.
-Value-function-only\footnote{Since this paper is concerned with results related to the approximate linear programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods compute an approximate value function and use it to obtain a one-step look ahead policy by making use of BE.
-In order to reduce the computational effort, the approximate value function is restricted to a chosen parametrized class of functions.
-The most widely used parametrization to approximate the value function is the \emph{linear function approximator} (LFA).
-Methods employing LFA approximate the value function as $\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learned.
-Computational advantage (in terms of the number of unknowns) is achieved by choosing fewer number of basis functions compared to the number of states.
-Once the set of basis function is chosen, the way to compute $r^*$ varies across the different ADP methods.\todoc{I don't understand why one should care about  approximating $J^*$ at all.}
-
-A host of value-function-based ADP methods solve the \emph{projected Bellman equation} (PBE) which is obtained by including the least squares projection operator in the BE so as to project quantities onto the lower dimensional subspace.
-A limitation of using the least squares projection operator is that it reduces the prediction error $L_2$-norm and cannot ensure policy improvement which requires prediction error to be minimum in the $L_\infty$-norm.
-Due to this norm mismatch, policy improvement cannot be guaranteed and \emph{policy-chattering} (policy-oscillations) can occur in practice \cite{dpchapter}.
-As a result, the performance loss is difficult to control and existing result that control this loss are proven under restrictive conditions \cite{anszemu:mlj07,FaMuSz10}.
-
-The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy $\tilde{u}$.
-Since ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, there is no issue of policy-chattering.
-The ALP formulation also provides theoretical performance guarantees, i.e., the prediction error $||J^*-\tilde{J}||$ and the control error\footnote{loss in performance due to the sub-optimal policy} $||J^*-J_{\tilde{u}}||$ can be bounded.
-This makes ALP an attractive method since it addresses both the prediction and control problems by providing the error bounds.
-However, an important shortcoming of ALP is that the number of constraints are of the order of the state space, making the vanilla version of ALP intractable.
-
-One proposal in the literature to overcome this hurdle is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP).
-The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} in various domains such as Tetris and in network of queues.
-However, the theoretical results are available only for a specific RLP formulated under idealized conditions \cite{CS}.
-Thus, there is a gap in the theoretical understanding of RLP and constraint reduction/approximation.
-Our aim in this paper is to fill this gap by providing theoretical guarantees which will make the RLP a complete ADP method that addresses both the prediction and the control problems.
-
-In particular, in this paper we develop a novel theoretical framework to study a generalized constraint reduction technique namely \emph{generalized reduced linear program} (GRLP) and present its error analysis.
+\section{Introduction}
+Markov decision processes (MDPs) is an important mathematical framework to study optimal sequential decision making problems that arise in science and engineering.
+Solving an MDP involves computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states.
+MDPs with small number of states can be solved easily by conventional solution methods such as value / policy iteration or linear programming (LP) \cite{BertB}.
+Dynamic programming is at the heart of all the conventional solution methods for MDPs.\par
+A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$.
+Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$.
+The most widely used method for approximation is the linear function approximation (LFA), i.e., let $\tilde{J}=\Phi r^*$, where $\Phi$ is a feature matrix and $r^*$ is a learnt weight vector.
+Dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states and this makes computing $\tilde{J}$ easier.\par
+The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation.
+A critical shortcoming of the ALP is that the number of constraints are of the order of the size of the state space, making the vanilla version of the ALP intractable.
+A way out is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP).
+The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}.
+An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach useful in practice, however, without any theoretical guarantees bounding the loss in performance resulting from such an approximation.\par
+In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints obtained as positive linear combinations of the original constraints of the ALP.
 The salient aspects of our contribution are listed below:
 \begin{enumerate}
-\item \textbf{Framework:}
-
-We generalize RLPs to define GRLPs. A GRLP has a small number of constraints which are obtained as positive linear combinations of the original constraints of the ALP. 
-The GRLP serves as a framework to analyze error due to constraint reduction and linear constraint approximation.
-\item \textbf{Error Analysis:}
-	\begin{itemize}
-		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$. 
-		\item We show a bound of the form $||J^*-\hat{J}||\leq c_1+c_2$, 
-		where the term $c_1$ is the error inherent to the ALP formulation itself, 
-		while the term $c_2$ is the additional error introduced due to the constraint approximation.  
-		\item We derive a greedy policy $\hu$ by making use of $\hj$ and bound the loss $||J^*-J_{\hu}||$. 
-		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a modified $L_\infty$-norm.
-		\item Our analysis is based on two novel $\max$-norm contraction operators called the least upper bound (LUB) projection operator and the approximate least upper bound projection operator (ALUB).
+		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction erorr $||J^*-\hj||$ (\Cref{cmt2mn}). 
+		\item We also bound the performance loss due to the one-step greedy policy $\hu$ (greedy with respect to $\hj$) given by $||J^*-J_{\hu}||$ (Theorem~\ref{polthe}).
+		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{with probability one}.
 This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
-\end{itemize}
-\item \textbf{Significant Results:}
-	\begin{itemize}
-		\item We provide error bounds for both prediction and control errors, i.e., bound the terms $||J^*-\hj||$ and $||J^*-J_{\hu}||$ in a modified $L_\infty$-norm.
-Thus, the GRLP is a complete ADP method with performance guarantees for both the prediction as well as control problems.
-The modified $L_\infty$-norm allows us to choose the quality of approximation across various states.
-This makes our result an important addition to the theory of ALP \cite{ALP,CS,CST,SALP}.
-		\item The structure of the error terms also reveals an important result that it is not always necessary to sample using the stationary distribution of the optimal policy.
-This throws additional light on constraint sampling by providing a better explanation for its empirical success even in those cases when sampling distributions other than the stationary distribution of the optimal policy was used.
 		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints.
-This means that constraint reduction is not only limited to sampling but also can be extended to include linear combinations of constraints.
-	\end{itemize}
-\item We also discuss the implication of our results in the context of reinforcement learning and also present a numerical example illustrating the theory developed.
-A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.
+		\item We demonstrate via an example in controlled queues that the experiments conform to the theory developed.
 \end{enumerate}

### 2016-07-08 lpshort.tex
Chandru's shortened version

--- 2015-06-15 lp.tex
@@
 \section{Approximate Linear Programming}
-The LP formulation in \eqref{mdplp} can be represented in short as,
-\begin{align}
-\begin{split}
-\label{mdplpshort}
-\min_{J\in \R^n}\, &c^\top J\\
-\text{s.t.}\mb &J\geq T J,
-\end{split}
-\end{align}
-or 
-%\text{ or }\nn\\
-\begin{align}
-\begin{split}
-\label{shortalter}
-\min_{J\in \R^n} \,&c^\top J\\
-\text{s.t.}\mb &EJ\geq H J,
-\end{split}
-\end{align}
-where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $E$ is an $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
-Note that \eqref{mdplpshort} and \eqref{shortalter} are identical programs and differ only in notation.
-We use notation of type \eqref{mdplpshort} whenever we prefer brevity and we use notation \eqref{shortalter} in some definitions and proofs for the sake of clarity.
-Recall that the vector $c\in \R^n$ must have positive entries to guarantee that the unique solution to the above LP is the optimal value function.
-By convention, we will also assume that $c$ is also normalized:
-\begin{assumption}\label{probdist}
-$c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0$ and $\sum_{i=1}^n c(i)=1$.
-\todoc{I am pretty sure the positivity is needed.}
-\end{assumption}
-
+\begin{comment}
 The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplpshort} with $\Phi \in \R^{n\times k}$ and introducing 
@@
 to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. 
-The extra constraint added that $J$ lies in the (column) span of $\Phi$ could lead to an infeasible LP.
-An easy way to prevent this is if the vector $\one$ whose components are all equal to one is in the span of $\Phi$.
-Indeed, by \cref{shift}, for any $t\in \R$, $T (t\one ) =  \alpha t \one+T \zero \le \alpha t \one + \max_{s,a} g_a(s)$, hence $t\one \ge \alpha t \one+T\zero $ happens as soon as
-$t\ge \frac{1}{1-\alpha}\max_{s,a} g_a(s)$. 
-This leads to the following assumption:
-\begin{assumption}\label{one}
-The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
-In other words, the constant function is part of the basis.
+\end{comment}
+For any function $\chi\colon S\ra \R_+$, define the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as
+\begin{align*}
+\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}\,.
+\end{align*}
+\begin{definition}
+A function $\chi:S\to\R_+$ is said to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ 
+	if $\beta_{\chi}<1$.
+\end{definition}
+The error bound will be given in terms of a Lyapunov function $\psi$ for $P$ that is in the column span of $\Phi$:
+\begin{assumption}\label{lyap}
+$\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
+and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$.
 \end{assumption}
-Under this assumption \eqref{alp} is thus feasible and since \eqref{alp} is obtained by adding an extra constraint to the LP \eqref{mdplpshort}, the solutions to  \eqref{alp} are bounded and $\tj$ is uniquely defined.
-
+It is straightforward to check that the vector $\one$ when viewed as an $S \to \R_+$ function 
+is a Lyapunov function. Further, by \cref{one}, $\one$ is trivially present in the column span of $\Phi$, 
+hence, \cref{lyap} is not limiting.
+In what follows we will always assume that Assumptions \ref{probdist}--\ref{lyap} hold. 
+When \cref{lyap} holds, it follows that for any $J\in \R^n$, $t>0$, $s\in S$,
+\begin{align*}
+(T(J+ t \psi))(s) &= 
+\max_{a} g_a(s) + \alpha \sum_{s'} p_a(s,s') J(s') + t \alpha  \sum_{s'} p_a(s,s') \psi(s') \\
+& \le 
+\max_{a} g_a(s) + \alpha \sum_{s'} p_a(s,s') J(s') + t \beta_{\psi} \psi(s) \\
+& = (T J)(s) + \beta_{\psi}\,t\,  \psi(s),
+\end{align*}
+or, in short,
+\begin{align}
+\label{eq:psilin}
+T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,\, \quad (J\in \R^n,\, t>0)\,.
+\end{align}
+%Under this assumption \eqref{alp} is thus feasible and since \eqref{alp} is obtained by adding an extra constraint to the LP \eqref{mdplpshort}, the solutions to  \eqref{alp} are bounded and $\tj$ is uniquely defined.
+\begin{comment}
 We will now recall two results due to de Farias and Van Roy 
@@
 \todoc{Column generation, Dantzig-Wolf decomposition?}
+\end{comment}

### 2016-07-08 mdp.tex
Chandru's shortened version

--- 2015-06-13 mdp.tex
@@
 \section{Markov Decision Processes (MDPs)}
-In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
-An MDP is a $4$-tuple $\langle S,A,P,g\rangle$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function.
 We consider MDPs with large but finite number of states.
-We also assume that the number of actions is finite.
-Without the loss of generality, we set  $S=\{1,2,\ldots,n\}$  and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. 
-The probability transition kernel $P= (p_a)_{a\in A}$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$.
-We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
-By a policy, we mean a sequence $\pi=\{\pi_0,\ldots,\pi_n,\ldots\}$ of functions $\pi_n, n\geq 0$ 
-	that describe the manner in which an action is picked in a given state at time $n$. 
-In the most general case, $\pi_n$ maps $(S \times A)^n \times S$, i.e., 
-	histories $h_n =(s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$ 
-	of state-action sequences of length $2n+1$, to a distribution over the actions. 
-We denote the class of policies by $\Pi$. 
-The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$ is denoted by $J_\pi(s)$ and is defined by \todoc{Explain the meaning of $\eqdef$.}
+Thus $S=\{1,2,\ldots,n\}$ for some large $n$ is the state space, and the action set is given by $A=\{1,2,\ldots,d\}$.
+For simplicity, we assume that all actions are feasible in all states.
+The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$.
+We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\par
+A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.}(SDP) or simply a policy is a map $u\colon S\ra A$ which specifies the action selection mechanism.
+Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
 \begin{align}
-J_\pi(s) \eqdef
-	\E\left[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)\,\Large|\,\pi\right]\,,\nn
+J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n)\mbox{ }\forall n\geq 0],\nn
 \end{align}
-	where $a_{n} \sim \pi_n(\,\cdot\,|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$, $s_{n+1} \sim p_{a_n}(s_n,\cdot)$ 
-	and $\alpha \in (0,1)$ is a given discount factor. 
-Here $J_\pi(s)$ is known as the value of the state $s$ under the policy $\pi$, and $J_\pi:S\to \R$ is 
- %the vector quantity $J_\pi\eqdef(J_\pi(s))_{s\in S}\in R^n$ is 
- called the value-function corresponding to the policy $\pi$. 
- The optimal value function $J^*:S\to \R$ is defined as $J^*(s) \eqdef
- \sup_{\pi\in\Pi} J_\pi(s)$, $s\in S$.
- %\underset{\pi \in \Pi}{\sup}\, J_\pi(s)$, $s\in S$.
-
-A stationary deterministic policy (SDP) is one where $\pi_n\equiv u$ for all $n\geq 0$ for some $u\colon S \ra A$
-in the sense that $\pi_n(a|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$ is one for $a = u(s_n)$ and is zero elsewhere.
-By abuse of notation we denote such an SDP by $u$ itself instead of $\pi$. 
-In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}, i.e., there exists an SDP $u^*$ such that $J_{u^*}(s)=J^*(s),\forall s\in S$. 
-In this paper, we restrict our focus to the class $U$ of SDPs. 
-%	and without loss of generality 
-%	we assume that there exists a unique SDP $u^*$ that is optimal.  
-	\todoc{Do we need uniqueness? I got rid of it.}
-%Under a stationary policy $u$ (or $\pi$), 
-%	the MDP is a Markov chain and we denote its probability transition kernel 
-%	by $P_u=(p_{u(s)}(s,s'),s,s'=1,\ldots,n)$ (or $P_\pi=(p_{\pi(s)}(s,s'),s,s'=1,\ldots,n)$, 
-%	where $p_{\pi(s)}(s,s')=\sum_{a\in A}\pi(s,a)p_a(s,s')$ and $\pi(s)=(\pi(s,a), a\in A)$).
-Under a stationary deterministic policy $u$, 
-	the MDP gives rise to a Markov chain with state space $S$,
-whose  transition probability kernel we will denote
-	by $P_u=(p_{u(s)}(s,s'),s,s'=1,\ldots,n)$.  \todoc{I don't think we need stationary \emph{stochastic} policies anywhere.}
-
-Given an MDP, our aim is to find the optimal value function $J^*$ and an optimal policy SDP $u^*$. 
-Any optimal policy $u^*$ and the value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
+where $\alpha \in (0,1)$ is a given discount factor.
+Here $J_u(s)$ is known as the value of the state $s$ under SDP $u$, and the vector quantity $J_u\eqdef(J_u(s), \forall s\in S)\in R^n$ is called the value function corresponding to the SDP $u$.
+The \emph{optimal policy} $u^*$ is obtained as $u^*(s)\eqdef\arg\max_{u\in U}J_u(s)$\footnote{An optimal (SDP) $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{BertB}.}, where $U$ is the class of all SDPs.
+The \emph{optimal value function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.\par
+Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
 \begin{subequations}\label{bell}
@@
 \label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
-\label{bellpol}u^*(s)&\in \argmax_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
+\label{bellpol}u^*(s)&= \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
 \end{align}
 \end{subequations}
-If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}.
-
-For convenience, in what follows we identify $\R^n$ with $\R^{S}$:
-Any vector $J\in \R^n$ is viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
-We now define some operators acting on $\R^n$ (equivalently, on $\R^S$) that will be useful later.
-The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
+Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.\par
+For convenience, in what follows we allow any vector $J\in \R^n$ to be viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
+We now define some operators acting on $\R^n$ (equivalently on $\R^S$) that will be useful later.
+%The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
 \begin{definition}
-The Bellman operator $T: \R^n \to \R^n$ is defined by 
-\begin{align}
-(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big)\,,  \qquad s\in S\,,J\in \R^n\,.
-\end{align}
-\end{definition}
-Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
-\begin{definition}
-The Bellman operator $T_u:\R^n \to \R^n$  restricted to an SDP $u$ is defined by
-\begin{align}
-(T_uJ)(s)=g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\,,  \qquad s\in S\,,J\in \R^n\,.
-\end{align}
-\end{definition}
-Given $J \in \R^n$, $TJ$ is the `one-step' greedy value function. It is also useful to define the notion of a one-step greedy policy as below:
-\begin{definition}
-A policy $\tilde{u}$ is said to be greedy with respect to $\tilde{J}$ if
-\begin{align}\label{subpol}
-\tilde{u}(s)\in \underset{a \in A}{\argmax} \, \big(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')\big)\,.
-\end{align}
-\end{definition}
-We also define the Bellman operator $H$ for action values  \cite{BertB}: 
-\begin{definition}\label{bellactval}
-Let $H: \R^n \to \R^{nd}$ be defined as follows: For $J\in \R^n$,
-\begin{align}
-HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd}, \text{ where}\nn\\
-(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A.
-\end{align}
+Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$, 
+define
+\begin{enumerate}[(i)]
+\item The Bellman operator $T\colon \R^n \ra \R^n$ as $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
+$
+\item \label{bellactval} The Bellman operator (of action values) $H: \R^n \to \R^{nd}$ for state-action values as $HJ=[ H_1 J,\cdots,H_d J]^\top\in \R^{nd},$ where $(H_a J)(s)= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s')$.
+\item The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ 
+and 
+the weighted $L_\infty$-norms  $\norm{\cdot}_{\infty,\rho}$ as $
+||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|, 
+||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
+\item The discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
+\item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
+\item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
+\item The greedy policy with respect to the value function $\tj$ as \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
+\end{enumerate}
 \end{definition}
 We now state without proof the most important properties of the Bellman operator.
-Though in these results, we make use of the Bellman operator $T$, the results also trivially hold for $T_u$ as well.
-
-%\subsection{Properties of $T$}
+The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
+First, we introduce some extra notation:
+For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
+We use $\one \in \R^n$ to denote a vector with all entries $1$.
+The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
+\begin{lemma}\label{monotone}
+$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
+\end{lemma}
+\begin{lemma}\label{shift}
+Given $J\in \R^n$ and $t \in \R$, we have
+\begin{align}\label{eq:shift}
+T(J+t\one)=TJ+\alpha t\one.
+\end{align}
+\end{lemma}
 \begin{lemma}\label{maxnorm}
-$T$ is a $\max$-norm contraction operator with contraction factor $\alpha$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
-\todoc{Introduce $\norm{\cdot}_{\infty}$. Should we have a notation/symbols section?}
+If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{eq:shift} then 
+$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
 \begin{align}
@@
 \end{lemma}
-For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
-The Bellman operator $T$ exhibits two more important properties presented in the following lemmas (see \cite{BertB} for proofs):
-\begin{lemma}\label{monotone}
-$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
-Further, if $J\in \R^n$ is such that $J\geq TJ$ then $J\geq J^*$.
-\end{lemma}
-\begin{lemma}\label{shift}
-Given $J\in \R^n$, $t \in \R$ and $\mathbf{1} \in \R^n$, a vector with all entries $1$, we have
-\begin{align}
-T(J+t\mathbf{1})=TJ+\alpha t\mathbf{1}.
+\begin{corollary}
+If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
+\end{corollary}
+Though in \cref{monotone,shift,maxnorm}, we make use of the Bellman operator $T$, the results also hold for $H$ as well.
+\subsection{Linear Programming Formulation}
+The optimal value function $J^*$ can be obtained by solving the following linear program:
+\begin{align}\label{mdplp}
+\min_{J\in \R^n}\, &c^\top J\\
+\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\nn\\
+&\forall s \in S, a \in A,
 \end{align}
-\end{lemma}
-Note that Lemmas~\ref{maxnorm}--\ref{shift} also hold for the Bellman operator $H$ defined for the action values in Definition~\ref{bellactval}.\par
-Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}.
-The problem of \emph{control} deals with coming up with a good (and if possible an optimal) policy.
-Often, in order to solve the problem of \emph{control}, one needs to solve the problem of \emph{prediction}, which deals with computing the value function $J_u$ of the policy $u$.
-The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain an optimal policy $u^*$.
-Thus, the Bellman equation is at the heart of the solution methods to MDPs.
-Any solution method to MDP is said to be complete only if it satisfactorily (with provable performance guarantees) addresses both the prediction and the control problems.
-\todoc{Why insist on prediction?}
-
-The basic solution methods namely value iteration, policy iteration and linear programming (LP) \cite{BertB} solve both the control and prediction problems.
-Of the three basic methods, in this paper, we focus on the LP formulation given by
-\begin{align}\label{mdplp}
-\begin{split}
-\min_{J\in \R^n}\, &c^\top J\\
-\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \qquad s\in S, a \in A,
-\end{split}
-\end{align}
-where $c\in \R^n$ is any vector whose components are all positive.
-\todoc{I changed this from nonnegative to positive.} 
-One can show that $J^*$ is the solution to the linear program given by \eqref{mdplp} \cite{BertB}. 
-Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.
-
-While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are intractable in the case of MDPs with a large number of states.
+where $c$ is a probability distribution such that $c(s)>0, \forall s \in S$ and $\sum_{s\in S}c(s)=1$.\par
+When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}.
+A practical solution is to resort to function approximation.
+The most widely used is the linear function approximation wherein the exact value function is approximated by a function that is obtained as a linear combination of a set of pre-selected basis functions.

### 2016-07-08 mdpshort.tex
Chandru's shortened version

--- 2016-07-08 mdp.tex
@@
-%!TEX root =  autocontgrlp.tex
-\section{Markov Decision Processes (MDPs)}
-We consider MDPs with large but finite number of states.
-Thus $S=\{1,2,\ldots,n\}$ for some large $n$ is the state space, and the action set is given by $A=\{1,2,\ldots,d\}$.
+\section{Introduction}
+Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs).
+We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$.
 For simplicity, we assume that all actions are feasible in all states.
@@
 We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\par
-A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.}(SDP) or simply a policy is a map $u\colon S\ra A$ which specifies the action selection mechanism.
+A stationary deterministic policy\footnote{For the scope of this paper, it is suffices to restrict our attention to stationary deterministic policies}(SDP) or simply a policy is a map $u\colon S\ra A$ which specifies the action selection mechanism.
 Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
@@
 where $\alpha \in (0,1)$ is a given discount factor.
-Here $J_u(s)$ is known as the value of the state $s$ under SDP $u$, and the vector quantity $J_u\eqdef(J_u(s), \forall s\in S)\in R^n$ is called the value function corresponding to the SDP $u$.
-The \emph{optimal policy} $u^*$ is obtained as $u^*(s)\eqdef\arg\max_{u\in U}J_u(s)$\footnote{An optimal (SDP) $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{BertB}.}, where $U$ is the class of all SDPs.
-The \emph{optimal value function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.\par
-Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
+Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s), \forall s\in S)\in R^n$ is called the value-function corresponding to the SDP $u$.
+The \emph{optimal policy} $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}, where $U$ is the class of all SDPs.
+The \emph{optimal value-function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.\par
+Any optimal policy $u^*$ and the value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
 \begin{subequations}\label{bell}
@@
 \end{subequations}
-Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.\par
-For convenience, in what follows we allow any vector $J\in \R^n$ to be viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
-We now define some operators acting on $\R^n$ (equivalently on $\R^S$) that will be useful later.
-%The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
+If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.
+The optimal value function $J^*$ can be obtained by solving the following linear program :
+\begin{align}\label{mdplp}
+\min_{J\in \R^n}\, &c^\top J\\
+\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\nn\\
+&\forall s \in S, a \in A,
+\end{align}
+where $c$ is a probability distribution such that $c(s)>0, \forall s \in S$ and $\sum_{s\in S}c(s)=1$.
+\begin{comment}
+The LP formulation in \eqref{mdplp} can also be represented in short by either of the below linear programs (which are idential but differ in notation),\begin{minipage}{.5\columnwidth}
+\begin{align}\label{mdplpshort}
+\begin{split}
+\min_{J\in \R^n}\, &c^\top J\\
+\text{s.t.}\mb &J\geq T J,
+\end{split}
+\end{align}
+\end{minipage}%
+\begin{minipage}{.5\columnwidth}
+\begin{align}
+\begin{split}
+\min_{J\in \R^n}\, &c^\top J\\
+\text{s.t.}\mb &EJ\geq H J,
+\end{split}
+\end{align}
+\end{minipage}\\
+\end{comment}
+We now define certain important quantities which will used in the rest of the paper.
 \begin{definition}
@@
 \item The discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
-\item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
+\item Function $\chi:S\to\R_+$ to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
 \item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
-\item The greedy policy with respect to the value function $\tj$ as \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
+\item The greedy policy with respect to the value function $\tj$ as \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big)\end{align*}
 \end{enumerate}
 \end{definition}
-We now state without proof the most important properties of the Bellman operator.
-The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
-First, we introduce some extra notation:
-For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
-We use $\one \in \R^n$ to denote a vector with all entries $1$.
-The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
-\begin{lemma}\label{monotone}
-$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
-\end{lemma}
-\begin{lemma}\label{shift}
-Given $J\in \R^n$ and $t \in \R$, we have
-\begin{align}\label{eq:shift}
-T(J+t\one)=TJ+\alpha t\one.
-\end{align}
-\end{lemma}
-\begin{lemma}\label{maxnorm}
-If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{eq:shift} then 
-$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
-\begin{align}
-||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
-\end{align}
-\end{lemma}
-\begin{lemma}\label{uniquesol} 
-$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
-\end{lemma}
-\begin{corollary}
-If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
-\end{corollary}
-Though in \cref{monotone,shift,maxnorm}, we make use of the Bellman operator $T$, the results also hold for $H$ as well.
-\subsection{Linear Programming Formulation}
-The optimal value function $J^*$ can be obtained by solving the following linear program:
-\begin{align}\label{mdplp}
-\min_{J\in \R^n}\, &c^\top J\\
-\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\nn\\
-&\forall s \in S, a \in A,
-\end{align}
-where $c$ is a probability distribution such that $c(s)>0, \forall s \in S$ and $\sum_{s\in S}c(s)=1$.\par
-When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}.
+When the MDP has a large number of states it is difficult to solve for $J^*$, using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration, policy iteration \cite{BertB}.
 A practical solution is to resort to function approximation.

### 2016-07-08 num.tex
Chandru's shortened version

--- 2015-06-05 resdisc.tex
@@
-%!TEX root =  autocontgrlp.tex
-\section{Discussion}
-In this section we discuss the implications and insights provided by the results presented in Theorems~\ref{cmt2mn} and ~\ref{polthe}.
-\subsection{On Error Terms}
-\begin{itemize}
-\item The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
-\begin{enumerate}
-\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$,
-\item $||\Gamma J^*-\hg J^*||_{\mn}$.
-\end{enumerate}
-The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
-This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\\
-The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.
-\item Unlike the result in \cite{CS} which holds only for a specific RLP formulated under ideal assumptions, our bounds hold for any GRLP and as a result for any given RLP.
-Another interesting feature of our result is that it holds with probability $1$.
-\item A salient feature of the ALP formulation is the use of Lyapunov functions to control/shape the error across the states based on their relative importance.
-Since the error bounds are in a modified $L_\infty$-norm, the GRLP framework retains this salient feature of the ALP.
-\end{itemize}
-The fact that both the prediction and control problems can be addressed by the GRLP makes it a complete ADP method, and by addressing the constraint approximation, the GRLP framework is an important addition to the theory of ALP.
-\subsection{On Constraint Reduction and Approximation}
-We claim the following based on the error bounds that we derived for the GRLP.\\
-{Claim $1$)} It is not always necessary to sample constraints according to the stationary distribution of the optimal policy.\\
-{Claim $2$)} Constraint approximation is not only restricted to constraint sampling but also can be extended to include linear approximation of the constraints.\\
-The following result (Theorem~\ref{st}) supports Claim~$1$ in the above.\\
-\textbf{Main Result~$3$: On Constraint Sampling}\\
-The error term $\etmn$ gives new insights into constraint sampling. 
-\begin{theorem}\label{st}
-Let $s\in S$ be a state whose constraint was sampled. Then
-\begin{align}\label{sampexp}
-|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
-\end{align}
-\end{theorem}
-\begin{proof}
-Let $r_{e_s}$ and $\hat{r}_{e_s}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$.
-It is easy to note that $r_{e_s}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s})(s)\geq (\Phi \hat{r}_{e_s})(s)$.
-However, since all the constraints with respect to state $s$ have been sampled we know that $(\Phi \hat{r}_{e_s})(s)\geq J^*$.
-The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.
-\end{proof}\\
-The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
-This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
-The modified $L_\infty$ norm in \eqref{finalbnd} comes to our rescue to control the error due to those states that are not sampled.
-Thus the sampling distribution need not be the stationary distribution of the optimal policy as long as it samples the \emph{important} states, an observation that might theoretically explain the empirical successes of the RLP \cite{ALP,CST,SALP}.\\
-To understand the implication of Claim~$2$ we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
-\begin{align}\label{lag}
-\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
-\end{align}
-The insight that the GRLP is a linear function approximation of the constraints (i.e., the Lagrangian multipliers) can be obtained by noting that $ Wq\approx \lambda$ in \eqref{lag2}.
-Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
-Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
-One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under the optimal policy $u^*$, i.e.,
-\begin{align}
-\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
-				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
-			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
-\end{align}
-where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy.
-Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.\\
-\subsection{Numerical Illustration}
-We take up an example in the domain of controlled queues from \cite{ALP} for which the ALP has been known to work well.
-For this domain, we make use of our results and observations to select various useful $W$ matrices and present their performance.\\
-The queuing system consists of $n=10^4$ states and $d=4$ actions.
-We chose $n=10^4$ because it was possible to solve both the GRLP and the exact LP (the latter with significant effort) so as to enumerate the approximation errors.
-We hasten to mention that while we could run the GRLP for queuing systems with $n>10^4$ without much computational overhead, solving the exact LP was not possible for $n>10^4$ as a result of which the approximation error could not be computed.\\
-\textbf{Queuing Model:}
+\section{Numerical Illustration}
+In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $\et$ indicates the quality of the constraint approximation.
 The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}.
@@
 The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue.
-The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$.\\
-\textbf{Choice of $\Phi:$} We make use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
-This takes care of the term $||J^*-\Phi r^*||_\infty$ in \eqref{finalbnd}.
-\\
-\textbf{Selection of $W$:} For our experiments, we choose two contenders for the $W$-matrix and compare them with the ideal sampling matrix $W_i$ (\cite{CS}) and random positive matrix $W_r$.
-Our choices of the $W$ matrix are as below.\\
-{$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$.
-This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states.\\
+The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$.
+We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
+For our experiments, we chose two contenders for the $W$-matrix and compared them with random positive matrix $W_r$.
+Our choices of the $W$ matrix were: {$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$.
+This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states.
 {$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$.
@@
 \begin{align}\label{wdes}
-W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
+W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t.}\mb \nn\\&j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
 &=0,\mb\text{otherwise}.
@@
 The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.
+Note that computing $\et$ was hard in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate.
+Accordingly, we chose a smaller system $Q_S$ with $n=10$, $d=2$, $k=2$, $m=5$, $q(1)=0.2$, $q(2)=0.4$, $p=0.2$ and $\alpha=0.98$.
+Note that a better performance of $W_a$ and $W_c$ is in agreement with a lower value of $\et$.
 \FloatBarrier
@@
 \begin{center}
-%\resizebox{\columnwidth}{!}{
+\resizebox{\columnwidth}{!}{
 \begin{tabular}{|c|c|c|c|c|}\hline
@@
 $||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
+$\et$ & $0$&	$39$& $24$& $214$ \\\hline
 \end{tabular}
+}
 \end{center}
-%}
 \caption{Shows values of Error Terms for $Q_L$.}
@@
 \end{table}
-
+\begin{comment}
+\subsection{Computational Complexity}
+It is known that the complexity of the linear program is polynomial in the length of its entries, i.e., the number of constraints times the number of variables \cite{karmarkar,adler}. 
+In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states.
+Thus, the complexity of obtaining the exact solution grows at a rate which is at least quadratic in the number of states.
+The entries of the GRLP on the other hand are of the order of $m\times k$, \todoc{$\times d$?} where the constants $m$ and $k$ are chosen to be much smaller than the number of states.
+We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, the ALP with took about $0.7$ seconds, while computing the exact solution took about $20$ minutes.
+\todoc{Sorry for the many questions, but did you also run ALP ($k=4$) with no constraint aggregation?}
+ Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the original constraints of the ALP without additional computational overhead.
 \FloatBarrier
@@
 \end{table}
-Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
-\subsection{Computational Complexity}
-It is known that the complexity of the linear program \cite{karmarkar,adler} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables.
-In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states.
-Thus, the complexity of obtaining the exact solution grows at a rate which is at least quadratic in the number of states.
-The entries of the GRLP on the other hand are of the order of $m\times k$, \todoc{$\times d$?} where the constants $m$ and $k$ are chosen to be much smaller than the number of states.
-We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, the ALP with took about $0.7$ seconds, while computing the exact solution took about $20$ minutes.
-\todoc{Sorry for the many questions, but did you also run ALP ($k=4$) with no constraint aggregation?}
- Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the original constraints of the ALP without additional computational overhead.
+\end{comment}
+
+%Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
+\begin{comment}
 \subsection{Reinforcement Learning}
@@
 Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.
+\end{comment}

### 2016-07-08 resdisc.tex
s.t. abbreviation corrected
Chandru's shortened version

--- 2015-06-01 resdisc.tex
@@
 \section{Discussion}
-In this section we discuss the implications and insights provided by the results presented in Theorems~\ref{cmt2mn} and ~\ref{polthe}.
-\subsection{On Error Terms}
-\begin{itemize}
-\item The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
+The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
 \begin{enumerate}
@@
 The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
-This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\\
+This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
 The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.
-\item Unlike the result in \cite{CS} which holds only for a specific RLP formulated under ideal assumptions, our bounds hold for any GRLP and as a result for any given RLP.
-Another interesting feature of our result is that it holds with probability $1$.
-\item A salient feature of the ALP formulation is the use of Lyapunov functions to control/shape the error across the states based on their relative importance.
-Since the error bounds are in a modified $L_\infty$-norm, the GRLP framework retains this salient feature of the ALP.
-\end{itemize}
-The fact that both the prediction and control problems can be addressed by the GRLP makes it a complete ADP method, and by addressing the constraint approximation, the GRLP framework is an important addition to the theory of ALP.
-\subsection{On Constraint Reduction and Approximation}
-We claim the following based on the error bounds that we derived for the GRLP.\\
-{Claim $1$)} It is not always necessary to sample constraints according to the stationary distribution of the optimal policy.\\
-{Claim $2$)} Constraint approximation is not only restricted to constraint sampling but also can be extended to include linear approximation of the constraints.\\
-The following result (Theorem~\ref{st}) supports Claim~$1$ in the above.\\
-\textbf{Main Result~$3$: On Constraint Sampling}\\
-The error term $\etmn$ gives new insights into constraint sampling. 
+It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators.
+As a consequence, our result holds with probability $1$, unlike prior results on constraint sampling \cite{CS} that hold only with high probability.
+The error term $\etmn$ gives new insights into constraint selection.
 \begin{theorem}\label{st}
-Let $s\in S$ be a state whose constraint was sampled. Then
+Let $s\in S$ be a state whose constraint was selected. Then
 \begin{align}\label{sampexp}
@@
 \begin{proof}
-Let $r_{e_s}$ and $\hat{r}_{e_s}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$.
-It is easy to note that $r_{e_s}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s})(s)\geq (\Phi \hat{r}_{e_s})(s)$.
-However, since all the constraints with respect to state $s$ have been sampled we know that $(\Phi \hat{r}_{e_s})(s)\geq J^*$.
-The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.
-\end{proof}\\
+Let $r_{e_s,J^*}$ and ${r}'_{e_s,J^*}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$.
+It is easy to note that $r_{e_s,J^*}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s,J^*})(s)\geq (\Phi {r}'_{e_s,J^*})(s)$.
+However, since the constraints with respect to state $s$ have been sampled we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*$.
+The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s,J^*})(s)$ and $\hg J^*(s)=(\Phi {r}_{e_s,J^*})(s)$.
+\end{proof}
 The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
 This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
-The modified $L_\infty$ norm in \eqref{finalbnd} comes to our rescue to control the error due to those states that are not sampled.
-Thus the sampling distribution need not be the stationary distribution of the optimal policy as long as it samples the \emph{important} states, an observation that might theoretically explain the empirical successes of the RLP \cite{ALP,CST,SALP}.\\
-To understand the implication of Claim~$2$ we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
+The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.\par
+The GRLP has linear function approximation in both the primal and dual variables of the LP formulation.
+To understand this, we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e.,
 \begin{align}\label{lag}
@@
 \end{align}
-The insight that the GRLP is a linear function approximation of the constraints (i.e., the Lagrangian multipliers) can be obtained by noting that $ Wq\approx \lambda$ in \eqref{lag2}.
+Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approxmation of the Lagrange multipliers.
 Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
@@
 where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy.
-Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.\\
-\subsection{Numerical Illustration}
-We take up an example in the domain of controlled queues from \cite{ALP} for which the ALP has been known to work well.
-For this domain, we make use of our results and observations to select various useful $W$ matrices and present their performance.\\
-The queuing system consists of $n=10^4$ states and $d=4$ actions.
-We chose $n=10^4$ because it was possible to solve both the GRLP and the exact LP (the latter with significant effort) so as to enumerate the approximation errors.
-We hasten to mention that while we could run the GRLP for queuing systems with $n>10^4$ without much computational overhead, solving the exact LP was not possible for $n>10^4$ as a result of which the approximation error could not be computed.\\
-\textbf{Queuing Model:}
-The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}.
-We consider a single queue with arrivals and departures.
-The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue.
-The action set $A=\{1,\ldots,d\}$ is related to the service rates.
-We let $s_t$ denote the state at time $t$.
-The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$.
-For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$.
-The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue.
-The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$.\\
-\textbf{Choice of $\Phi:$} We make use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
-This takes care of the term $||J^*-\Phi r^*||_\infty$ in \eqref{finalbnd}.
-\\
-\textbf{Selection of $W$:} For our experiments, we choose two contenders for the $W$-matrix and compare them with the ideal sampling matrix $W_i$ (\cite{CS}) and random positive matrix $W_r$.
-Our choices of the $W$ matrix are as below.\\
-{$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$.
-This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states.\\
-{$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$.
-Our choice of the $W_a$ matrix to correspond to aggregation of near by states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
-The aggregation matrix $W_a$ is defined as below: for all $ i=1,\ldots,m$,
-\begin{align}\label{wdes}
-W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
-&=0,\mb\text{otherwise}.
-\end{align}
-We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$.
-We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$.
-We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively.
-The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.
-\FloatBarrier
-\begin{table}[H]
-\begin{center}
-%\resizebox{\columnwidth}{!}{
-\begin{tabular}{|c|c|c|c|c|}\hline
-Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
-$||J^*-\hj||_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
-$||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
-\end{tabular}
-\end{center}
-%}
-\caption{Shows values of Error Terms for $Q_L$.}
-\label{pref}
-\end{table}
-
-\FloatBarrier
-\begin{table}[H]
-%\resizebox{\columnwidth}{!}{
-\begin{center}
-\begin{tabular}{|c|c|c|c|}\hline
-Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
-$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
-$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
-\end{tabular}
-\end{center}
-%}
-\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
-$.}
-\label{pref}
-\end{table}
-Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
-\subsection{Computational Complexity}
-It is known that the complexity of the linear program \cite{karmarkar,adler} is polynomial in the length of its entries, i.e., the number of constraints times the number of variables.
-In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states.
-Thus, the complexity of obtaining the exact solution grows at a rate which is at least quadratic in the number of states.
-The entries of the GRLP on the other hand are of the order of $m\times k$, \todoc{$\times d$?} where the constants $m$ and $k$ are chosen to be much smaller than the number of states.
-We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, while computing the exact solution took about $20$ minutes.
-\todoc{Sorry for the many questions, but did you also run ALP ($k=4$) with no constraint aggregation?}
- Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the original constraints of the ALP without additional computational overhead.
-\subsection{Reinforcement Learning}
-Reinforcement Learning (RL) algorithms are useful in scenarios where the system is available in the form of a simulator or only samples can be obtained via direct interaction.
-In particular, in the RL setting, the model parameters $g$ and $P$ are not known explicitly and the underlying MDP needs to be solved by using sample trajectories.
-In short, RL algorithms are sample trajectory based solution schemes for solving MDPs whose model information is not known.
-RL methods learn by filtering out the noisy sample via stochastic approximation and they also employ function approximation in order to handle MDPs with large number of states.
-Most RL algorithms are sample trajectory based extensions of ADP methods.\\
-The RL extension of the ALP formulation has been applied to the optimal stopping problem in \cite{ALP-Bor}.
-Function approximation is employed to approximate the square root of the Lagrange multipliers.
-However, since the approximation is not linear, convergence of the resulting RL algorithm cannot be guaranteed.
-Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.
+Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.

### 2016-07-08 single/abstract.tex
Chandru's shortened version

--- 2015-05-27 abstract.tex
@@
+%\begin{comment}
 \begin{abstract}
@@
 \end{abstract}
+%\end{comment}
+\begin{comment}
+\begin{abstract}
+The approximate linear programming (ALP) method and its variants have been widely applied to various Markov Decision Processes (MDPs) with large number of states.
+An attractive feature of the ALP is that it has fewer number of variables compared to the number of states of the MDP and it offers sound theoretical guarantees.
+Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead.
+Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.
+\end{abstract}
+\end{comment}
+\begin{comment}
+\begin{abstract}
+The approximate linear programming (ALP) method and its variants have been widely applied to various Markov Decision Processes (MDPs) with large number of states.
+A serious limitation of the ALP is that it has intractable number of constraints.
+A practical solution is to sample a tractable number constraints of the ALP to formulate a reduced linear program (ALP).
+In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP.
+The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP.
+Unlike prior results on constraint sampling which hold only with high probability, our analysis holds with probability one and is based on a novel contraction operator.
+%In addition to handling linear approximation of the constraints
+%We discuss the implication of our results in the contexts of ADP and reinforcement learning.
+\end{abstract}
+\end{comment}
 \begin{keywords}{

### 2016-07-08 single/autocontgrlp.tex
Chandru's shortened version

\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
%\documentclass[12pt,twocolumn]{IEEEtran}
\usepackage{times}
\input{pack.tex}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\title{A Generalized Reduced Linear Program for Markov Decision Processes}
\author{Chandrashekar Lakshminarayanan and Shalabh Bhatnagar\\Department of Computer Science and Automation\\ Indian Institute of Science\\ Bangalore-560012\\\{chandrul,shalabh\}@csa.iisc.ernet.in\\ and \\
Csaba Szepesv\'{a}ri\\Department of Computing Science\\University of Alberta\\Edmonton, Alberta\\Canada T6G 2E8\\  csaba.szepesvari@ualberta.ca }

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
%\nipsfinalcopy % Uncomment for camera-ready version
\begin{document}
\maketitle
\input{abstract}
%\input{intro}
\input{introshort}
\input{mdpshort}
\input{lp}
%\input{constsamp}
\input{grlp}
\input{errana}
%\input{lubp}
%\input{alubp}
%\input{strel}
\input{improv}
\input{polbnd}
\input{resdisc}
\input{num}
\input{concl}
%\input{example}
%\input{discussion}
\bibliographystyle{plain}
\bibliography{ref.bib}
\newpage
\onecolumn
%\input{appendix}
\end{document}

### 2016-07-08 single/concl.tex
Chandru's shortened version

--- 2015-05-27 concl.tex
@@
 \section{Conclusion}
-The approximate linear programming (ALP) is an approximate dynamic programming method that addresses the prediction and control problems successfully.
+The approximate linear programming (ALP) is a widely employed method to handle MDPs with large number of states.
 However, an important shortcoming of the ALP is that it has large number of constraints, which is tackled in practice by sampling a tractable number of constraints from the ALP to formulate and solve a reduced linear program (RLP).
-Though RLP has been found to work well empirically in various domains ranging from queues to Tetris games, performance guarantees are available only in the case of a specific RLP formulated under idealized assumptions.
-Thus there has been a gap in the theory of constraint reduction.\\
+The RLP has been found to work well empirically in various domains ranging from queues to Tetris games, and performance guarantees are for a specific RLP formulated under idealized assumptions.
+Alternatively, function approximation in the dual variables of the ALP has been another approach that has been employed in literature \cite{ALP-Bor,dolgov} to address the issue of large number of constraints.
+However \cite{ALP-Bor,dolgov} do not provide theoretical characterization for the function approximation of the dual variables.\par
 In this paper, we introduced a novel framework based on the generalized reduced linear program formulation to study constraint reduction.

### 2016-07-08 single/constsamp.tex
Chandru's shortened version

--- 2015-06-14 constsamp.tex
@@
 \begin{align}\label{rlp}
-\begin{split}
-\min_{r\in \N}\, &c^\top \Phi r\\
-\text{s.t.}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \mb (s,a) \in \I\,,
-\end{split}
+\min_{r\in \N}\, &c^\top \Phi r\nn\\
+\text{s.t.}\mb &(\Phi r)(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')(\Phi r)(s'), \nn\\
+&\forall (s,a) \in \I.
 \end{align}
-where $\I$ is the index set containing $m$ sampled state-action pairs and
-the extra constraint set $\N\subset \R^k$ is introduced to guarantee a bounded feasible set (hence, bounded solution).
-It is assumed that $\N$ is compact and $\tr\in \N$. \todoc{How can one arrange for this in general?}
-The index set $\I$ naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
+where $\I$ is the index set containing $m$ sampled state-action pairs and the extra constraint set $\N$ is introduced to guarantee a bounded solution. Further we assume that the following holds:
+\begin{assumption}\label{nassump}
+$\N \subset \R^k$ is compact and $\tr \in \N$.
+\end{assumption}
+The index set $\I$ in \eqref{rlp} naturally gives rise to the definition of an $nd\times m$ constraint sampling matrix $\M$:
 \begin{definition}\label{csampmat}
@@
 \end{align}
-Let $\tilde{r}$ be an optimal	solution of the ALP and let $\hat{r}$ be the solution of the corresponding RLP. 
+Let $\tilde{r}_c$ be an optimal	solution of the ALP and let $\hat{r}_c$ be the solution of the corresponding RLP. 
+Assume that $\tilde{r}_c\in \N$.
 Then, with probability at least $1-\delta$, we have
 \begin{align}
-||J^*-\Phi \hat{r}||_{1,c}\leq ||J^*-\Phi \tilde{r}||_{1,c}+\epsilon||J^*||_{1,c}.
+||J^*-\Phi \hat{r}_c||_{1,c}\leq ||J^*-\Phi \tilde{r}_c||_{1,c}+\epsilon||J^*||_{1,c}.
 \end{align}

### 2016-07-08 single/errana.tex
Chandru's shortened version

--- 2016-07-08 errana.tex
@@
 \section{Error Analysis}\label{sec:errana}
-We now define the two projection operators which are central to our error analysis. The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
+The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
 \begin{definition}\label{lubpop}
@@
 \end{definition}
-\begin{remark}\label{ubrem}
-To understand the meaning of $\Gamma$ (and $\hg$) define 
-\begin{align}\label{ubclass}
-\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
-\end{align}
-where $J\in \R^n$.
-Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$.
-Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
-\end{remark}
 The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
@@
 \end{align}
-Further, define $\hg J$  as 
+Then, for $J\in \R^n$ define $\hg J$  as 
 \begin{align}\label{tgamdef}
@@
 \end{definition}
+\begin{assumption}\label{ass:n4}
+The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$ and $\N$ is as in \eqref{grlp} satisfying \cref{nassmp}.
+\end{assumption}
 \begin{lemma}\label{lpsol}
@@
 Define $\eps = \norm{J^* - \Phi r^*}_{\mn}$ so that
-$ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$.
-Then from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$.
-From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$.
+$ J^*-\Phi r^* \le \eps \psi$.
+Then from \cref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$.
+From the definition of $\Gamma$ in \eqref{gamdef} we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$.
 The result follows by noting that $2\eps\psi\geq \Phi r^*+\eps\psi -J^*\geq \Gamma J^*-J^*\geq 0$.
@@
 \begin{proof}
-Given $J\in \R^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$.
-Choose any $i\in \{1, \ldots, n\}$.
-Since $J_1\leq J_2$, from \cref{monotone} and \cref{grlpassmp}-\eqref{wassump} it follows that $W^\top H J_1\leq W^\top H J_2$.
+Given $J\in \R^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N\,\}\,$.
+Choose any $i\in \{1,\ldots,n\}$.
+Since $J_1\leq J_2$, from \cref{wassump} it follows that $W^\top H J_1\leq W^\top H J_2$.
 Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.
@@
 \end{proof}
+
+%Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm, we first show that $\Gamma$ is also a contraction map in the weighted $L_\infty$ norm.
+%The generalization of  \cref{maxnorm} for the weighted $L_{\infty}$ norm is as follows:
 \begin{lemma}\label{maxnormmn}
@@
 \label{eq:shiftmn}
-\hg( J + t \psi) \le \hg J + \beta t \psi,
+\hg( J + t \psi) \le \hg J + \beta t \psi\,.
 \end{align} 
@@
 \begin{corollary}\label{tmaxnormmn}
-$T$ is a $\norm{\cdot}_{\mn}$-contraction with factor $\beta_{\psi}$.
+Let us note in passing that from this result and~\eqref{eq:psilin} it immediately follows that $T$ is an $\norm{\cdot}_{\mn}$-contraction with factor $\beta_{\psi}$.
 \end{corollary}
@@
 \begin{proof}
-By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N' \}$.
-By \eqref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta_\psi \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi \psi)$. Thus,
+By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N \}$.
+By \cref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta \psi)$. Thus,
 $(\hg (J+t\psi) )(i) \le 
- \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
-Now, using Lemma~\ref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $c=e_i$, $b_0=t\beta_\psi \psi$ 
-and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
+ \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N \}$.
+Now, using Lemma~\ref{lpsol} with $A=W^\top E \Phi$, $b=TJ$, $c=e_i$, $b_0=\beta t \psi$ 
+and $x_0=t \beta r_0$, the statement follows
+as thanks to \cref{lyap}, $A x_0 = b_0$ and thanks to
+\cref{ass:n4}, $\N = \N + \alpha t r_0$.
 %The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
@@
 \end{proof}
-In what follows we denote by $\hv$ the unique fixed point of $\hg$ i.e., $\hv = \hg \hv\,$. 
-We now show that the vector $\hj$ dominates the vector $\hv$:
-\begin{lemma}\label{relation1}
+In what follows we denote by $\hv$ the unique fixed point of $\hg$ i.e., $\hv = \hg \hv\,$. We now show that the vector $\hj$ dominates the vector $\hv$:
+\begin{lemma}\label{relation2}
 The vectors $\hv,\hj$ obey $\hj\geq\hv$.
@@
 \begin{proof}
+%The proof follows in a similar manner as the proof of \Cref{relation1}. To elaborate, 
 Let $ r_1,  r_2,\ldots, r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$, respectively,
@@
 
-It suffices to show that $V_1\eqdef \hg V_0 \le V_0 \le \hj$ since then the desired result follows
+It suffices to show $V_1\eqdef \hg V_0 \le V_0 \le \hj$ since then the desired result follows
 by defining $V_{n+1} = \hg V_n$, $n\ge 1$, noting that by \cref{tgmonotone}, $V_{n+1}\le V_{n}$ and by  \cref{tmaxnormmn}, $V_n \to \hv$.
@@
 Now,  fix any $i$. 
-We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi r'_{e_i,V_0})(i) \leq V_0(i)$. 
-By the definition of $r'_{e_i,V_0}$ we know that $(\Phi r'_{e_i,V_0})(i) \le (\Phi r)(i)$
+We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi \har_{e_i,V_0})(i) \leq V_0(i)$. 
+By the definition of $\har_{e_i,V_0}$ we know that $(\Phi \har_{e_i,V_0})(i) \le (\Phi r)(i)$
 holds for any $r\in \N$ such that $W^\top E \Phi r \ge W^\top H V_0$. 
@@
 By definition, $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H \Phi r_i$.
-Hence, by the monotone property of $H$ and \cref{grlpassmp}-\eqref{wassump} it is sufficient if $\Phi r_i \ge V_0$.
+Hence, by the monotone property of $H$ and \cref{wassump} it is sufficient if $\Phi r_i \ge V_0$.
 This however directly follows from the definition of $V_0$.
 \end{proof}
-\begin{lemma}\label{relation2}
-The vectors $\hv,\tj$ obey $\tj\geq\hv$.
-\end{lemma}
-\begin{proof}
-%The proof follows in a similar manner as the proof of \Cref{relation1}. To elaborate, 
-Let $ r_1,  r_2,\ldots, r_n$ be solutions to the ALP in \eqref{alp} (with an additional constraint that the solution be restricted to $\N$) for $c=e_1, e_2,\ldots,e_n$, respectively,
-and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 
-follows in the same manner as the proof of \cref{relation1}.
-\end{proof}
+%The following lemmas relate the fixed point $\hv$ of $\hg$ to the solution $\hj$ of the GRLP in \eqref{grlp}.
 \begin{lemma}\label{srw}
@@
 \begin{split}
-\min_{r\in \N}\, &||\Phi r-\hv||_{1,c}\\
-\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r.
+\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
+\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r\,, \qquad r\in \N\,.
 \end{split}
@@
 \end{proof}
-\begin{lemma}\label{srwalp}
-A vector
-$\tr \in \R^k$ is a solution to ALP \eqref{alp} iff it solves the following program:
-\begin{align}\label{grlpeqprog}
-\begin{split}
-\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
-\text{s.t.}\mb &\, \Phi r\geq  T \Phi r.
-\end{split}
+\begin{lemma}\label{cmt1mn}
+We have
+\begin{align}
+||J^*-\hv||_{\mn}\leq \frac{2||J^*-\Phi r^*||_{\mn}+||\Gamma J^*-\hg J^*||_{\mn}}{1-\beta_{\psi}}.
 \end{align}
@@
 \begin{proof}
-We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$, and the rest of the arguments follow in the same manner as proof for \cref{srw}.
-\end{proof}
-\begin{lemma}\label{cmt1mn}
-We have
-\begin{align}
-||J^*-\hv||_{\mn}&\leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}&\nn\\+||\Gamma J^*-\hg J^*||_{\mn}\big).
-\end{align}
-\end{lemma}
-\begin{proof}
-Recall that $\hg \hv=\hv$. By the triangle inequality,
+By the triangle inequality,
 \begin{align*}
-&||J^*-\hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+||\hg J^*-\hg \hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+\beta_\psi || J^*- \hv||_\mn,
+&||J^*-\hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+||\hg J^*-\hg \hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+\beta_\psi || J^*- \hv||_\mn
 \end{align*}
-and so by reordering and with another triangle inequality,
+and so by reordering and another triangle inequality,
 \begin{align}\label{jhv}
-&\norm{J^*-\hv}_{\mn} \nn\\&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\nn\\
+&\norm{J^*-\hv}_{\mn} \\&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\\
 &\le \frac{\norm{ J^*-\Gamma J^*}_{\mn}+\norm{\Gamma J^* - \hg J^*}_{\mn}}{1-\beta_\psi}\,.
 \end{align}
-The proof follows by applying \cref{bestbndmn} on \eqref{jhv}.
+The proof is complete by using \cref{bestbndmn} in \eqref{jhv}.
 \end{proof}
 We now recall Lemma~$5$ from Section 4.2 of \cite{ALP}. 
-For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$ by assumption.
+For this result, recall that $r_\in \R^k$ is the vector such that $\psi = \Phi r_0$ by assumption.
 \begin{lemma}\label{restate}
@@
 Then, by choosing $r'$ as in Lemma~\ref{restate} we have
-\begin{align}\label{part}
-&||\Phi r'-J^*||_{\mn}\nn\\&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
+\begin{align*}
+&||\Phi r'-J^*||_{\mn}\\&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
 &=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
-&=\frac{2}{1-\beta_\psi}\gamma.
-\end{align}
-%We know that $\tr \in \N$ by \cref{grlpassmp}-\eqref{nassmp} and 
-$r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. Then from \cref{srwalp} it follows that
-%As a result, from \cref{srw} it follows that
+&=\frac{2}{1-\beta_\psi}\gamma.\nn
+\end{align*}
+Since $r'$ is also feasible for the GRLP in \eqref{grlp} we have
 \begin{align}
-&||\hj-\hv||_{1,c}\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\
+&||\hj-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\
 &=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
@@
 \end{align}
-The result follows from \cref{cmt1mn} and \eqref{part}.
+The result follows from \cref{cmt1mn}.
 %\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
@@
 \end{proof}
-We now bound the performance of the greedy policy $\hu$.
-\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\mn}$]
-\label{polthe}
-Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
-% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
-Then,
-\begin{align}\label{polthebnd}
-%||J_{\hu}-\hj||_{1,c}
-\norm{J^* - J_{\hu}}_{1,c}
-&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2\, \big(6 ||J^*-\Phi r^*||_{\mn}
-\nn\\&
-+2||\Gamma J^*-\hg J^*||_{\mn}\big).
-\end{align}
-\end{theorem}
-\begin{proof}
-By the triangle inequality,
-\begin{align*}
-||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\,.
-\end{align*}
-Let us now bound the second term on the right-hand side.
-Since $\hu$ is greedy w.r.t. $\hj$, it holds that $T_{\hu} \hj = T \hj$.
-Also, $T_{\hu} J_{\hu} = J_{\hu}$.
-Hence, $J_{\hu} - \hj = T_{\hu} J_{\hu} - T_{\hu} \hj + T \hj - \hj
-=\alpha P_{\hu} (J_{\hu}- \hj) + T\hj - \hj$.
-Hence,
-\begin{align}\label{polderv}
-&||J_{\hu}-\hj||_{1,c}\nn\\&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
-&\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
-&\leq c^\top (I-\alpha P_{\hu})^{-1} \psi ||T\hj-\hj||_{\mn}\nn\\
-&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
-%&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
-&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
-&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})||J^*- \hj||_{\mn},
-\end{align}
-where in the second inequality, we use Jensen's inequality and $|T\hj - \hj|$ stands for the 
-vector whose $i$th component is $|(T\hj)(i) - \hj(i)|$. Further, the last inequality follows
-since $T$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta_{\psi}$ as noted earlier.
-%componentwise  $(I-\alpha P_{\hu})^{-1}$ is a positive operator for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. 
-Hence,
-\begin{align}
-&||J^*-J_{\hu}||_{1,c}\nn\\
-%&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
-&\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
-&=\frac{2c^\top \psi}{1-\beta_{\psi}}||J^*- \hj||_{\mn}.
-\end{align}
-The result now follows by substituting the bound on $||J^*- \hj||_{\mn}$ from \cref{cmt2mn}.
-\end{proof}
-\begin{comment}
-\begin{note}
-By bounding $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}+||J^*-\hg J^*||_{\mn}$ 
-(the inequality follows from \cref{bestbndmn}), 
-we can loosen the bounds in \cref{cmt2mn} and \cref{polthe} to
-\begin{align}
-\label{loose1}
-||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
-\nn\\&
-+2||J^*-\hg J^*||_{\mn}).\\
-\label{loose2}
-||J^* - J_{\hu}||_{1,c}&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2 \,\big(10 ||J^*-\Phi r^*||_{\mn}
-\nn\\&
-+2||J^*-\hg J^*||_{\mn}\big).
-\end{align}
-Here the term $||J^*-\hg J^*||$ in \eqref{loose1} and \eqref{loose2} captures the error due to the use of both $\Phi$ and $W$.
-Though, \eqref{loose1} and \eqref{loose2} might be loser bounds than \eqref{finalbndmn} and \eqref{polthebnd} respectively, the advantage of this bound is that it captures the error due to function approximation as well as constraint reduction in a direct manner.
-\end{note}
-\end{comment}

### 2016-07-08 single/grlp.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}
\end{align}
where $\N$ is an additional constraint set (see \Cref{nassmp}) to ensure the boundedness of the solution. We denote the solution to the GRLP by $\hr$ and the approximate value functions are denoted by $\hj=\Phi \hr$. 
\begin{assumption}\label{nassmp}
$\N\subset \R^k$ is compact and $\tr \in \N\subset\R^k$.
\end{assumption}
In what follows, we build the analytical framework to characterize the performance of the GRLP and then discuss the implications of our results.
\begin{comment}
Further we assume the following to ensure the boundedness of the solution to the GRLP.
\begin{assumption}\label{mainassmp}
\begin{enumerate}[(i)]
\item \label{probdist} $c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0$ and $\sum_{i=1}^n c(i)=1$.
\item  \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
\item \label{wassump} $W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m\ll nd$) and each of its column-sums equals one.
\item \label{nassmp} $\tr \in \N\subset\R^k$.
\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$. 
\end{enumerate}
\end{assumption}

Here \Cref{mainassmp} \eqref{probdist}-\eqref{one} are carry overs from \cite{ALP}. \Cref{mainassmp} \eqref{wassump} means that the constraints of the GRLP are obtained as positive linear combinations of the original constraints of the ALP. By setting $\N=\R^k$ (\Cref{mainassmp}-\eqref{nassmp} is trivially satified), $m=nd$ and $W=I_{nd\times nd}$ in \eqref{grlp} we recover the ALP as considered in \cite{ALP}. Similarly, RLP in \cite{CS} can be recovered from \eqref{grlp} by choosing an appropriate $W$ (whose $m$ column correspond to the $m$ sampled constraints and each column has a $1$ corresponding to constraint to be sampled with other entries as $0$). It is straightforward to check that the vector $\one$ when viewed as an $S \to \R_+$ function 
is a Lyapunov function. Further, by \cref{one}, $\one$ is trivially present in the column span of $\Phi$, hence, \cref{lyap} is not limiting.
\begin{lemma}
When \cref{lyap} holds, it follows that for any $J\in \R^n$, $t>0$, $s\in S$, \begin{align}\label{eq:psilin}T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,\, \quad (J\in \R^n,\, t>0)\,.
\end{align}
\end{lemma}
\begin{proof}
\begin{align*}
&(T(J+ t \psi))(s) = 
\max_{a} g_a(s) + \alpha \sum_{s'} p_a(s,s') J(s') \\&+ t \alpha  \sum_{s'} p_a(s,s') \psi(s') \\
& \le 
\max_{a} g_a(s) + \alpha \sum_{s'} p_a(s,s') J(s') + t \beta_{\psi} \psi(s) \\
& = (T J)(s) + \beta_{\psi}\,t\,  \psi(s).
\end{align*}
\end{proof}
\end{comment}

### 2016-07-08 single/intro.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Introduction}\label{intro}
Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs), where the problem is to find a policy $u$, mapping states to actions, so as to maximize long term expected cumulated discounted reward. 
The problem of \emph{control} requires coming up with good policies.
% and for which one needs to \emph{predict} the behavior of individual policies. 
	\todoc{I removed the second part of the sentence; it seemed that it was not adding anything.}
The problem of \emph{prediction} deals with computing the value-function $J_u$ 
	(a mapping from the state space to the set of reals%
	\footnote{Also known as reward/cost-to-go function.}), 
	which gives the value of each state under a given policy $u$. 
\todoc{How is the MDP given? If it is given as a list of values, just reading the values may take too much time.
Or we assume sparsity? Or we assume that one can query the next state distribution at any state-action? These yield to different models. We should specify which one we work with (presumably the sparse is the easiest).
}
\todoc{Why do we discuss control and prediction?}
The optimal value function $J^*$ collects the highest values achievable in each state.
A policy $u^*$ is optimal if it achieves the optimal value in each state, i.e., if $J^* = J_{u^*}$.
A key observation that goes back to Bellman is that $J^*$ is the solution of a nonlinear fixed point equation,
	known as the Bellman equation (BE),
	and that an optimal policy can be obtained via the knowledge of $J^*$ through this fixed point equation.
Dynamic programming based solution methods for MDPs \cite{BertB},
	such as value iteration, policy iteration and linear programming,
	hence compute $J^*$ to then obtain an optimal policy.
%Ideally, we would be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$. 
%Under reasonable conditions, the optimal value function is known to be the fixed point of the (so-called) Bellman equation (BE),
%in which case $u^*$ can be obtained as a `greedy/one-step look ahead' policy by substituting $J^*$ in the BE. 
%``Exact'' solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming 
%compute $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation. 
By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems. 
\todoc{So is the prediction problem to predict $J_{u^*}$?}
However, in the case of MDPs with large number of states, computing $u^*$ and $J^*$ using 
	these exact methods is infeasible.

\emph{Approximate dynamic programming} (ADP) \cite{dpchapter,powell} 
	refers to a gamut of approximate solution methods to MDPs with large number of states
	that build on dynamic programming.
The key idea in value-function-only%
\footnote{
		Since this paper is concerned with results related to the approximate linear programming formulation we do not 
		discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} 
	(or \emph{critic-only}) ADP methods is to employ a parametrized class of functions
	to approximate the optimal value function.
Linear parameterization is the most common.
Methods employing such a \emph{linear function approximator} (LFA) 
	approximate the value function as $\Phi r^*$, 
	where $\Phi$ is a feature matrix whose columns are the basis functions 
	and $r^*$ is a weight vector to be learned. 
A representational advantage (in terms of the number of unknowns) 
	is achieved by choosing fewer number of basis functions compared to the number of states. 
Once the set of basis function is chosen, 
	the way to compute $r^*$ varies across the different ADP methods.

Building on policy iteration, a host of value-function-based ADP methods solve 
	the \emph{projected Bellman equation} (PBE) 
	which is obtained by including the least squares projection operator in the BE 
	so as to project the value function onto the lower dimensional subspace. 
A limitation of using the least squares projection operator is that 
	it minimizes the $L_2$-norm distance to the chosen subspace of linearly parameterized functions 
	and cannot in general ensure monotonous policy improvement 
	which requires the distance to be minimum in the $L_\infty$-norm. 
Due to this norm mismatch, in the lack of monotonous policy improvement 
	\emph{policy-chattering} (policy-oscillations) can occur \cite{dpchapter}. 
The performance loss can still be controlled \cite{FaMuSz10}, 
	though only at the price of posing extra, limiting assumptions on the MDP. 
	\todoc{How about value-iteration based methods? The paragraph
	should/could capture both of these..}

The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} host of methods 
	also employs LFA. 
However, ALP solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, 
	based on which a one-step greedy policy $\tilde{u}$ is then computed as an approximation to $u^*$. 
Since ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, 
	there is no issue of policy-chattering. 
The ALP formulation also provides theoretical performance guarantees, 
	i.e., the prediction error $||J^*-\tilde{J}||$ and the control error%
	\footnote{That is, the loss in performance due to the sub-optimal policy} 
	$||J^*-J_{\tilde{u}}||$ can be bounded. 
This makes ALP an attractive method since it addresses both the prediction 
	and control problems by providing the error bounds. 
However, a critical shortcoming of ALP is 
	that the number of constraints are of the order of the state space, 
	making, in the lack of extra structure, 
	\todoc{I added this as sometimes one can solve linear programs with exponentially many constraints in polynomial time.}
	the vanilla version of ALP intractable.

One proposal in the literature to overcome this hurdle is 
	to employ a procedure known as constraint sampling, 
	wherein a subset of the original constraints of the ALP 
	are sampled to formulate a \emph{reduced linear program} (RLP). 
The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} 
	in various domains such as Tetris and in network of queues. 
However, theoretical results are available only for a specific RLP 
	formulated under idealized conditions \cite{CS}. 
Thus, there is a gap in the theoretical understanding of RLP 
	and constraint reduction/approximation. 
Our aim in this paper is to fill this gap by providing theoretical guarantees 
	which will make the RLP a complete ADP method that addresses 
	both the prediction and the control problems.

In particular, in this paper we develop a novel theoretical framework 
	to study a generalized constraint reduction technique 
	namely \emph{generalized reduced linear program} (GRLP) and present its error analysis. 
	The salient aspects of our contribution are listed below:
%
\begin{enumerate}
\item \textbf{Framework:}

We generalize RLPs to define GRLPs. A GRLP has a small number of constraints which are obtained as positive linear combinations of the original constraints of the ALP. 
The GRLP serves as a framework to analyze error due to constraint reduction and linear constraint approximation.
\todoc{Give theorem numbers?}
\item \textbf{Error Analysis:}
	\begin{itemize}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$. 
		\item We show a bound of the form $||J^*-\hat{J}||\leq c_1+c_2$, 
		where the term $c_1$ is the error inherent to the ALP formulation itself, 
		while the term $c_2$ is the additional error introduced due to the constraint approximation.  
		\item We also bound the loss $||J^*-J_{\hu}||$ of the one-step greedy policy $\hu$ based on $\hj$.
		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a weighted $L_\infty$-norm.
		\item Our analysis is based on two novel $\max$-norm contraction operators called the least upper bound (LUB) projection operator and the approximate least upper bound projection operator (ALUB). This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
\end{itemize}
\item \textbf{Significant Results:}
	\begin{itemize}
		\item We provide error bounds for both prediction and control errors, i.e., bound the terms $||J^*-\hj||$ and $||J^*-J_{\hu}||$ in a weighted $L_\infty$-norm. Thus, the GRLP is a complete ADP method with performance guarantees for both the prediction as well as control problems. The weighted $L_\infty$-norm allows us to choose the quality of approximation across various states. This makes our result an important addition to the theory of ALP \cite{ALP,CS,CST,SALP}.
		\item The structure of the error terms also reveals that it is not always necessary to sample using the stationary distribution of the optimal policy. This throws additional light on constraint sampling by providing a better explanation for its empirical success in the more practical situations when sampling distributions other than the stationary distribution of the optimal policy was used. 
		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints. This means that constraint reduction is not only limited to sampling but also can be extended to include linear combinations of constraints.
	\end{itemize}
\item We also discuss the implication of our results in the context of reinforcement learning and also present a numerical example illustrating the theory developed. A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.
\end{enumerate}

### 2016-07-08 single/introshort.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Introduction}\label{intro}
\begin{comment}
Markov decision processes (MDPs) is an important mathematical framework to study optimal sequential decision making problems that arise in science and engineering. Solving an MDP involves computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states. MDPs with small number of states can be solved easily by conventional solution methods such as value/ policy iteration or linear programming (LP) \cite{BertB}. However, it is difficult to compute  $J^*$ exactly when there are a large number of states. A practical way to tackle the curse is to empoly function approximation, i.e., to choose an approximate value function $\tilde{J}$ instead of $J^*$ from a paramterized function class. Linear function approximation is the most common, wherein, the value function is approximated as $J^*\approx \tj=\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learned. A representational advantage (in terms of the number of unknowns) is achieved by choosing fewer number of basis functions compared to the number of states. Once approximate value function $\tilde{J}$ is known, a sub-optimal policy $\tilde{u}$ which is greedy with respect to $\tilde{J}$ can be computed.  The quality of approximation depends on the quantity $||J^*-\tilde{J}||$. 
\end{comment}
Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs), where the problem is to find a policy $u$, mapping states to actions, so as to maximize long term expected cumulated discounted reward. A given policy $u$ is associated with a value function $J_u$ (a mapping from the state space to the set of reals\footnote{Also known as reward/cost-to-go function.}), which gives the value of each state under a given policy $u$. The optimal value function $J^*$ collects the highest values achievable in each state. A policy $u^*$ is optimal if it achieves the optimal value in each state, i.e., if $J^* = J_{u^*}$. Conventional solution methods for Markov Decision Processes (MDPs) such as value iteration, policy iteration and linear programming formulation compute the optimal value function and the optimal policy. However, computing the exact quantities for each and every state is hard when there are a large number of states.\par
A practical way to address the issue of large number of states is function approximation, wherein, the idea is to choose a function belonging to a parameterized family as an approximation to the exact value function. Linear function approximation is the most common, wherein, the value function is approximated as $J^*\approx \tj=\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learned. A representational advantage (in terms of the number of unknowns) is achieved by choosing fewer number of basis functions compared to the number of states. Once approximate value function $\tilde{J}$ is known, a sub-optimal policy $\tilde{u}$ which is greedy with respect to $\tilde{J}$ can be computed.\par
The \emph{approximate linear programming} (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} host of methods introduce linear function approximation in the linear programming formulation. 
%The ALP method outputs an approximate value function $\tj$ and a sub-optimal policy $\tu$ which is obtained as a greedy policy with respect to $\tj$. The approximation error $||J^*-\tilde{J}||$ and the loss in performance $||J^*-J_{\tilde{u}}||$ can be bounded \cite{ALP}. 
A critical shortcoming of ALP is that the number of constraints are of the order of the state space, making, in the lack of extra structure, the vanilla version of ALP intractable. One proposal in the literature to overcome this hurdle is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP). The perfromance analysis of the RLP can be found in \cite{CS}. The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} 
in various domains such as Tetris and in network of queues. 
%However, theoretical results are available only for a specific RLP 	formulated under idealized conditions \cite{CS}. 
An alternative approach to handle the constraints is employ function approximation in the dual variables of the ALP \cite{ALP-Bor}. However, \cite{ALP-Bor} does not provide theoretical guarntees for the loss in performance due to such an approximation.\par 
The success of the RLP \cite{CS,CST}and the idea of approximating the dual variables \cite{ALP-Bor}, naturally leads us to the question understanding linear function approximation of the constraints. To this end, in this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP. 
The salient aspects of our contribution are listed below:
\begin{enumerate}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ (\Cref{cmt2mn}). 
		\item We also bound (Theorem~\ref{polthe}) the loss $||J^*-J_{\hu}||$ of the one-step greedy policy $\hu$ based on $\hj$.
%		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a weighted $L_\infty$-norm.
		\item Our analysis is based on a novel $\max$-norm contraction operator  and our results hold with probability one. This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
		\item The structure of the error terms also reveals that it is not always necessary to sample using the stationary distribution of the optimal policy.
		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints.
\end{enumerate}

### 2016-07-08 single/lp.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Approximate Linear Programming}
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$. By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\
\text{s.t.}\mb &\Phi r\geq T \Phi r,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}. Unless specified otherwise we use $\tr$ to denote any solution to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. 
Further we assume the following to ensure the boundedness of the various linear programs (\cref{mdplp,alp,grlp} ) presented in this paper.
\begin{assumption}\label{mainassmp}
\begin{enumerate}[(i)]
\item \label{probdist} $c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0$ and $\sum_{i=1}^n c(i)=1$.
\item  \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
\item \label{wassump} $W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m\ll nd$) and each of its column-sums equals one.
\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$. 
%\item \label{nassmp} $\tr \in \N\subset\R^k$.
\end{enumerate}
\end{assumption}

It is straightforward to check that the vector $\one$ when viewed as an $S \to \R_+$ function 
is a Lyapunov function. 
Further, by \cref{one}, $\one$ is trivially present in the column span of $\Phi$, 
hence, \cref{lyap} is not limiting.
In what follows we will always assume that Assumptions \ref{probdist}--\ref{lyap} hold. 
When \cref{lyap} holds, it follows that for any $J\in \R^n$, $t>0$, $s\in S$,
\begin{align*}
(T(J+ t \psi))(s) &= 
\max_{a} g_a(s) + \alpha \sum_{s'} p_a(s,s') J(s') \\&+ t \alpha  \sum_{s'} p_a(s,s') \psi(s') \\
& \le 
\max_{a} g_a(s) + \alpha \sum_{s'} p_a(s,s') J(s') \\&+ t \beta_{\psi} \psi(s) \\
& = (T J)(s) + \beta_{\psi}\,t\,  \psi(s),
\end{align*}
or, in short,
\begin{align}
\label{eq:psilin}
T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,\, \quad (J\in \R^n,\, t>0)\,.
\end{align}
We will now recall two results due to de Farias and Van Roy that bound the error due to the introduction of the extra constraint in the ALP.
\begin{theorem}[Theorem~$4.2$ of \cite{ALP}]
\label{restateval}
Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$.
% $\psi$ be as in \cref{lyap} 
%and $c$ be a distribution as in \eqref{probdist}. 
Then, it holds that
\begin{align*}
||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}\,.
\end{align*}
\end{theorem}
The next result  the loss in performance of a policy that is greedy w.r.t. $J_{\tu}$:
\begin{theorem}[Theorem~$3.1$ of \cite{ALP}]
\label{restatepol}
Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP. Then,
\begin{align*}
||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'}\,,
\end{align*}
where $c'=(1-\alpha)c^\top(I-\alpha P_{\tu})^{-1}$.
\end{theorem}
Theorems~\ref{restateval} and ~\ref{restatepol} together imply that the ALP addresses both the control and prediction problems. Please refer to \cite{ALP} for a more detailed treatment of the ALP.\\
Note that the ALP is a linear program in $k$ ($\ll n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables. Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
\todoc{Column generation, Dantzig-Wolf decomposition?}
One proposal in the literature to overcome this hurdle is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP). The perfromance analysis of the RLP can be found in \cite{CS}. The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} 
in various domains such as Tetris and in network of queues. 
%However, theoretical results are available only for a specific RLP 	formulated under idealized conditions \cite{CS}. 
An alternative approach to handle the constraints is employ function approximation in the dual variables of the ALP \cite{ALP-Bor}. However, \cite{ALP-Bor} does not provide theoretical guarntees for the loss in performance due to such an approximation.\par

### 2016-07-08 single/lubp.tex
Chandru's shortened version

--- 2015-06-14 lubp.tex
@@
 \section{Least Upper Bound Projection}\label{sec:lubp}
+\begin{comment}
 Let $e_j$ denote the $j$th basis vector in the standard Euclidean bases of $\R^n$.
@@
 suggest a way to define $\N$.}
-
+\end{comment}
 The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
@@
 \begin{split}
- \underset{r\in \R^k}{\min} &\,\, c^\top \Phi r\,,\\
- \text{s.t.}& \mb \Phi r\geq  TJ\,, \qquad r\in \N\,.
+ \underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,,\\
+ \text{s.t.}& \mb \Phi r\geq  TJ.
  \end{split}
@@
 \end{definition}
+\begin{definition}\label{alubpop}
+Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}'$ to be the solution to 
+\begin{align}\label{alubplp}
+ \underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,,\nn\\
+ \text{s.t.}& \,\,\, W^\top E \Phi r\geq W^\top HJ.
+\end{align}
+Then, for $J\in \R^n$, $\hg J$, the approximate least upper bound (ALUB) projection of $J$ is defined as 
+\begin{align}\label{tgamdef}
+(\hg J)(i)\eqdef(\Phi \har_{e_i,J})(i), \mb i=1,\ldots,n\,.
+\end{align}
+\end{definition}
+\begin{comment}
 %Note that $r_{e_j}$ depends on $J$, but this dependence is suppressed to reduce clutter. 
@@
 \item Even though $\Gamma J$ does not belong to the span of $\Phi$, $\Gamma J$ collates the various best upper bounds that can be obtained via the linear program in \eqref{lubplp}.
-\begin{comment}
 \item The LUB operator $\Gamma$ in \eqref{gamdef} bears close similarity to the ALP in \eqref{alp}.
 In fact, it is not hard to observe that $(\Gamma J)(i) = (\Phi r_{e_i})(i)$ for any $1\le i \le n$; the reason $\Gamma$ is defined the way it is so that this resembles to \eqref{alp} will be clear. 
-\end{comment}
 \end{enumerate}
 \end{remark}
+\end{comment}
 %\begin{definition}\label{bestproj}
 %\end{definition}
+\begin{comment}
 We now characterize the LUB projection operator $\Gamma$ in the following lemmas. 
@@
 \end{proof}
+\end{comment}
 
+\begin{comment}
 We now show that $\Gamma$ is a contraction. 
@@
 \input{perfbnds}
+\end{comment}

### 2016-07-08 single/mdp.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Markov Decision Processes (MDPs)}
In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
An MDP is a $4$-tuple $\langle S,A,P,g\rangle$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g:S\times A \to \R$ is the reward function. We consider MDPs with large but finite number of states. We also assume that the number of actions is finite.
Without the loss of generality, we set  $S=\{1,2,\ldots,n\}$  and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. 
The probability transition kernel $P= (p_a)_{a\in A}$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. 
We also denote the reward $g(s,a)$ obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
By a policy, we mean a sequence $\pi=\{\pi_0,\ldots,\pi_n,\ldots\}$ of functions $\pi_n, n\geq 0$ 
	that describe which action is to be picked in a given state at time $n$. 
In the most general case, $\pi_n$ maps $(S \times A)^n \times S$, i.e., 
	histories $h_n =(s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$ 
	of state-action sequences of length $2n+1$, to a distribution over the actions. 
Let $\Pi$ stand for the set of policies. 
The infinite horizon discounted reward corresponding to state $s$ under a policy $\pi$,
	or, in short, the value of $\pi$ in state $s$
	is denoted by $J_\pi(s)$ and is defined by \todoc{Explain the meaning of $\eqdef$.}
\begin{align}
J_\pi(s) \eqdef
	\E\left[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)\,\Large|\,\pi\right]\,,\nn
\end{align}
	where $a_{n} \sim \pi_n(\,\cdot\,|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$, $s_{n+1} \sim p_{a_n}(s_n,\cdot)$ 
	and $\alpha \in (0,1)$ is the so-called discount factor. 
The resulting function $J_\pi:S\to \R$ is called the value function of policy $\pi$.	
 The optimal value function $J^*:S\to \R$ is defined as $J^*(s) \eqdef
 \sup_{\pi\in\Pi} J_\pi(s)$, $s\in S$.
 %\underset{\pi \in \Pi}{\sup}\, J_\pi(s)$, $s\in S$.

A stationary deterministic policy (SDP) is one where $\pi_n\equiv u$ for all $n\geq 0$ for some $u\colon S \ra A$
in the sense that $\pi_n(a|s_0,a_0,\dots,s_{n-1},a_{n-1},s_n)$ is one for $a = u(s_n)$ and is zero elsewhere.
By abuse of notation we denote such an SDP by $u$ itself instead of $\pi$. 
In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}, i.e., there exists an SDP $u^*$ such that $J_{u^*}(s)=J^*(s),\forall s\in S$. 
In this paper, we restrict our focus to the class $U$ of SDPs. 
%	and without loss of generality 
%	we assume that there exists a unique SDP $u^*$ that is optimal.  
	\todoc{Do we need uniqueness? I got rid of it.}
%Under a stationary policy $u$ (or $\pi$), 
%	the MDP is a Markov chain and we denote its probability transition kernel 
%	by $P_u=(p_{u(s)}(s,s'),s,s'=1,\ldots,n)$ (or $P_\pi=(p_{\pi(s)}(s,s'),s,s'=1,\ldots,n)$, 
%	where $p_{\pi(s)}(s,s')=\sum_{a\in A}\pi(s,a)p_a(s,s')$ and $\pi(s)=(\pi(s,a), a\in A)$).
Under a stationary deterministic policy $u$, 
	the MDP gives rise to a Markov chain with state space $S$,
whose  transition probability kernel we will denote
	by $P_u=(p_{u(s)}(s,s'),s,s'=1,\ldots,n)$.  \todoc{I don't think we need stationary \emph{stochastic} policies anywhere.}

Given an MDP, our aim is to find the optimal value function $J^*$ and an optimal policy SDP $u^*$. 
Any optimal policy $u^*$ and the value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
\label{bellpol}u^*(s)&\in \argmax_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
\end{align}
\end{subequations}
If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}.

For convenience, in what follows we identify $\R^n$ with $\R^{S}$:
Any vector $J\in \R^n$ is viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
We now define some operators acting on $\R^n$ (equivalently, on $\R^S$) that will be useful later.
The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
\begin{definition}
The Bellman operator $T: \R^n \to \R^n$ is defined by 
\begin{align}
(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big)\,,  \qquad s\in S\,,J\in \R^n\,.
\end{align}
\end{definition}
Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
\begin{definition}
The Bellman operator $T_u:\R^n \to \R^n$  restricted to an SDP $u$ is defined by
\begin{align}
(T_uJ)(s)=g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\,,  \qquad s\in S\,,J\in \R^n\,.
\end{align}
\end{definition}
Given $J \in \R^n$, $TJ$ is the `one-step' greedy value function. It is also useful to define the notion of a one-step greedy policy as below:
\begin{definition}
A policy $\tilde{u}$ is said to be greedy with respect to $\tilde{J}$ if
\begin{align}\label{subpol}
\tilde{u}(s)\in \underset{a \in A}{\argmax} \, \big(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')\big)\,.
\end{align}
\end{definition}
We also define the Bellman operator $H$ for action values  \cite{BertB}: 
\begin{definition}\label{bellactval}
Let $H: \R^n \to \R^{nd}$ be defined as follows: For $J\in \R^n$,
\begin{align}
HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd}, \text{ where}\nn\\
(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \qquad s\in S, a\in A.
\end{align}
\end{definition}
We now state without proof the most important properties of the Bellman operator.
The proofs are immediate from the definitions, but can also be found in \cite{BertB}.

%\subsection{Properties of $T$}
First, we introduce some extra notation:
For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
We use $\one \in \R^n$ to denote a vector with all entries $1$.
The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
\begin{lemma}\label{monotone}
$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
Further, if $J\in \R^n$ is such that $J\geq TJ$ then $J\geq J^*$. \todoc{Should we move this second part out?}
\end{lemma}
\begin{lemma}\label{shift}
Given $J\in \R^n$ and $t \in \R$, we have
\begin{align}\label{eq:shift}
T(J+t\one)=TJ+\alpha t\one.
\end{align}
\end{lemma}
Operators that satisfy \eqref{eq:shift} are said to be \emph{linear along $[\one]$-rays with factor $\alpha$}.
From these result, it immediately follows that $T$ is a contraction in the $L_\infty$-norm through the following lemma:
\begin{lemma}\label{maxnorm}
If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{eq:shift} then 
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
\begin{align}
||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
\end{align}
\end{lemma}
\begin{proof}
The proof is given as we will need this lemma later.
Let $\eps = \norm{J_1 - J_2}_\infty$. Then $J_2 - \eps \one \le J_1 \le J_2 + \eps \one$. By the monotonicity of $T$,
$T(J_2 - \eps \one) \le T J_1 \le T(J_2 + \eps \one)$. Using~\eqref{eq:shift}, we get 
$TJ_2 - \alpha \eps \one \le T J_1 \le TJ_2 + \alpha \eps \one$, i.e., $-\alpha \eps \one \le T J_1 - T J_2 \le \alpha \eps \one$, from which the result follows.
\end{proof}
Through Banach's fixed point theorem, from \cref{maxnorm} we get the following lemma:
\begin{lemma}\label{uniquesol} 
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{lemma}
Though in these results, we make use of the Bellman operator $T$, the results also hold for $T_u$ and $H$ as well.
%Note that Lemmas~\ref{maxnorm}--\ref{shift} also hold for the Bellman operator $H$ defined for the action values in Definition~\ref{bellactval}.\par

Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}. The problem of \emph{control} deals with coming up with a good (and if possible an optimal) policy. Often, in order to solve the problem of \emph{control}, one needs to solve the problem of \emph{prediction}, which deals with computing the value function $J_u$ of the policy $u$. The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain an optimal policy $u^*$. Thus, the Bellman equation is at the heart of the solution methods to MDPs. Any solution method to MDP is said to be complete only if it satisfactorily (with provable performance guarantees) addresses both the prediction and the control problems. 
\todoc{Why insist on prediction?}

The basic solution methods namely value iteration, policy iteration and linear programming (LP) \cite{BertB} solve both the control and prediction problems. Of the three basic methods, in this paper, we focus on the LP formulation given by
\begin{align}\label{mdplp}
\begin{split}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \qquad s\in S, a \in A,
\end{split}
\end{align}
where $c\in \R^n$ is any vector whose components are all positive.
\todoc{I changed this from nonnegative to positive.} 
One can show that $J^*$ is the solution to the linear program given by \eqref{mdplp} \cite{BertB}. 
Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.

While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are intractable in the case of MDPs with a large number of states.

### 2016-07-08 single/mdpshort.tex
Chandru's shortened version

--- 2016-07-08 mdpshort.tex
@@
-\section{Introduction}
-Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs).
+\section{Markov Decision Processes (MDPs)}
+%In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
+%Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs), where the problem is to find a policy $u$, mapping states to actions, so as to maximize long term expected cumulated discounted reward.
+A given policy $u$ is associated with a value function $J_u$ (a mapping from the state space to the set of reals\footnote{Also known as reward/cost-to-go function.}), which gives the value of each state under a given policy $u$.
+The optimal value function $J^*$ collects the highest values achievable in each state.
+A policy $u^*$ is optimal if it achieves the optimal value in each state, i.e., if $J^* = J_{u^*}$.
+In this section, briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
 We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$.
@@
 The \emph{optimal policy} $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}, where $U$ is the class of all SDPs.
-The \emph{optimal value-function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.\par
-Any optimal policy $u^*$ and the value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
-\begin{subequations}\label{bell}
-\begin{align}
-\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
-\label{bellpol}u^*(s)&= \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
-\end{align}
-\end{subequations}
-If $J^*$ is computed first, then $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.
-The optimal value function $J^*$ can be obtained by solving the following linear program :
+The \emph{optimal value-function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.The optimal value function $J^*$ can be obtained by solving the following linear program :
 \begin{align}\label{mdplp}
 \min_{J\in \R^n}\, &c^\top J\\
-\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\nn\\
-&\forall s \in S, a \in A,
+\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), s\in S, a \in A.\nn
 \end{align}
-where $c$ is a probability distribution such that $c(s)>0, \forall s \in S$ and $\sum_{s\in S}c(s)=1$.
+and the optimal policy can be obtained as 
+\begin{align}
+u^*(s)=\arg\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)
+\end{align}
 \begin{comment}
@@
 \end{comment}
-We now define certain important quantities which will used in the rest of the paper.
+We now define certain important quantities which will used in the rest of the discussion.
 \begin{definition}
@@
 \item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
-\item The greedy policy with respect to the value function $\tj$ as \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big)\end{align*}
 \end{enumerate}
 \end{definition}
-When the MDP has a large number of states it is difficult to solve for $J^*$, using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration, policy iteration \cite{BertB}.
-A practical solution is to resort to function approximation.
-The most widely used is the linear function approximation wherein the exact value function is approximated by a function that is obtained as a linear combination of a set of pre-selected basis functions.
+When the MDP has a large number of states it is difficult to solve for $J^*$, using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration, policy iteration \cite{BertB}).

### 2016-07-08 single/num.tex
Chandru's shortened version

--- 2016-07-08 num.tex
@@
 \section{Numerical Illustration}
-In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $\et$ indicates the quality of the constraint approximation.
+In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $||J^*-\Gamma J^* ||_\infty$ indicates the quality of the constraint approximation.
 The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}.
@@
 We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
-For our experiments, we chose two contenders for the $W$-matrix and compared them with random positive matrix $W_r$.
-Our choices of the $W$ matrix were: {$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$.
+For our experiments, we choose two contenders for the $W$-matrix and compare them with random positive matrix $W_r$.
+Our choices of the $W$ matrix are as below.{$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$.
 This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states.
@@
 \begin{align}\label{wdes}
-W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t.}\mb \nn\\&j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
+W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t.}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
 &=0,\mb\text{otherwise}.
@@
 The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.
-Note that computing $\et$ was hard in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate.
-Accordingly, we chose a smaller system $Q_S$ with $n=10$, $d=2$, $k=2$, $m=5$, $q(1)=0.2$, $q(2)=0.4$, $p=0.2$ and $\alpha=0.98$.
-Note that a better performance of $W_a$ and $W_c$ is in agreement with a lower value of $\et$.
 \FloatBarrier
@@
 \begin{center}
-\resizebox{\columnwidth}{!}{
+%\resizebox{\columnwidth}{!}{
 \begin{tabular}{|c|c|c|c|c|}\hline
@@
 $||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
-$\et$ & $0$&	$39$& $24$& $214$ \\\hline
+$||\Gamma J^*-\hg J^*||_\infty$ & $0$&	$39$& $24$& $214$ \\\hline
 \end{tabular}
-}
 \end{center}
+%}
 \caption{Shows values of Error Terms for $Q_L$.}
@@
 \end{table}
-\begin{comment}
 \subsection{Computational Complexity}
@@
  Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the original constraints of the ALP without additional computational overhead.
+
+\begin{comment}
 \FloatBarrier

### 2016-07-08 single/polbnd.tex
Chandru's shortened version

--- 2016-07-08 errana.tex
@@
 %!TEX root =  autocontgrlp.tex
-\section{Error Analysis}\label{sec:errana}
-We now define the two projection operators which are central to our error analysis. The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
-\begin{definition}\label{lubpop}
-Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to 
-\begin{align}
-\label{lubplp}
-\begin{split}
- \underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,,\\
- \text{s.t.}& \mb \Phi r\geq  TJ.
- \end{split}
-\end{align}
-Then, for $J\in \R^n$, $\Gamma J$,
-the least upper bound projection of $J$ is defined as 
-\begin{align}\label{gamdef}
-(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
-\end{align}
-\end{definition}
-\begin{remark}\label{ubrem}
-To understand the meaning of $\Gamma$ (and $\hg$) define 
-\begin{align}\label{ubclass}
-\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
-\end{align}
-where $J\in \R^n$.
-Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$.
-Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
-\end{remark}
-The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
-\begin{definition}\label{alubpop}
-Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}$ to be the solution to 
-\begin{align}\label{alubplp}
- \underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,,\nn\\
- \text{s.t.}& \,\,\, W^\top E \Phi r\geq W^\top HJ.
-\end{align}
-Further, define $\hg J$  as 
-\begin{align}\label{tgamdef}
-(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,.
-\end{align}
-\end{definition}
-\begin{lemma}\label{lpsol}
-Let $A\in \R^{u\times v}$, $b,c\in \R^u$ and $b_0=Ax_0$ for 
-some $x_0 \in \R^v$, $\N' \subset \R^v$ such that $\N' =x_0+ \N'$. Then
-\begin{align}
-&\min\{c^\top Ax:Ax\geq b+b_0, x\in \N'\} \nn\\
-&=\min\{c^\top A y:Ay \geq b, y \in \N' \}+c^\top b_0.
-\end{align}
-\end{lemma}
-\begin{proof}
-The claim follows by the change of variables $y := x-x_0$.
-\end{proof}
-\noindent 
-%Note that under our assumptions on $\N$, $\hg$ is well-defined.
-%\begin{align*}
-%r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}\,.
-%\end{align*}
-%where $\psi$ is a Lyapunov function as in \cref{lyap}.
-\begin{lemma}\label{bestbndmn}
-We have
-\begin{align}
-||J^*-\Gamma J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.
-\end{align}
-\end{lemma}
-\begin{proof}
-Define $\eps = \norm{J^* - \Phi r^*}_{\mn}$ so that
-$ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$.
-Then from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$.
-From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$.
-The result follows by noting that $2\eps\psi\geq \Phi r^*+\eps\psi -J^*\geq \Gamma J^*-J^*\geq 0$.
-\end{proof}
-\begin{lemma}\label{tgmonotone}
-For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
-\end{lemma}
-\begin{proof}
-Given $J\in \R^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$.
-Choose any $i\in \{1, \ldots, n\}$.
-Since $J_1\leq J_2$, from \cref{monotone} and \cref{grlpassmp}-\eqref{wassump} it follows that $W^\top H J_1\leq W^\top H J_2$.
-Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.
-Since $i$ was arbitrary, the result follows.
-\end{proof}
-\begin{lemma}\label{maxnormmn}
-Assume that $\hg: \R^n \to \R^n$ is monotone and 
-that there exists some $\beta\in [0,1)$ such that for any $J\in \R^n$ and $t>0$,
-\begin{align}
-\label{eq:shiftmn}
-\hg( J + t \psi) \le \hg J + \beta t \psi,
-\end{align} 
-for any $J\in \R^n$ and $t\ge 0$.
-Then $\hg$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
-\end{lemma}
-\begin{proof}
-First, we show that for any $t\ge 0$,  $J\in \R^n$,
-$\hg( J - t \psi) \ge \hg J - \beta t \psi$ also holds.
-To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $\hg J \le \hg J' + \beta t \psi$. Reordering this inequality gives the result.
-Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \R^n$ are arbitrary.
-Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
-By the monotonicity of $\hg$,
-$\hg(J_2 - \eps \psi) \le \hg J_1 \le \hg(J_2 + \eps \psi)$. 
-Using~\eqref{eq:shiftmn}, we get 
-$\hg J_2 - \beta \eps \psi \le \hg J_1 \le \hg J_2 + \beta \eps \psi$, i.e., $-\beta \eps \psi \le \hg J_1 - \hg J_2 \le \beta \eps \psi$, from which the result follows.
-\end{proof}
-\begin{corollary}\label{tmaxnormmn}
-$T$ is a $\norm{\cdot}_{\mn}$-contraction with factor $\beta_{\psi}$.
-\end{corollary}
-%Returning to $\hg$, since we already now that $\hg$ is monotone (cf. \cref{gmonotone}), it remains to see that it satisfies \eqref{eq:shiftmn}:
-\begin{lemma}\label{gshiftmn}
-The operator $\hg$ satisfies \eqref{eq:shiftmn} with $\beta = \beta_\psi$.
-%For any $J\in \R^n$, $t\in \R_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.
-\end{lemma}
-\begin{proof}
-By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N' \}$.
-By \eqref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta_\psi \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi \psi)$. Thus,
-$(\hg (J+t\psi) )(i) \le 
- \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
-Now, using Lemma~\ref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $c=e_i$, $b_0=t\beta_\psi \psi$ 
-and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
-%The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
-\end{proof}
-%From this result and \cref{maxnormmn}, we immediately get that $\Gamma$ is a contraction in $\norm{\cdot}_{\mn}$:
-\begin{comment}
-\begin{theorem}\label{gmaxcontramn}
-The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
-\end{theorem}
-\end{comment}
-%In a similar way, one can also show that $\hg$ is also a contraction:
-\begin{theorem}\label{hgmaxcontramn}
-The operator $\hg:\R^n\to\R^n$  is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
-%$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
-\end{theorem}
-\begin{proof}
-Follows from \cref{maxnormmn} and \cref{gshiftmn}.
-\begin{comment}
-We already know that $\hg$ is monotone. That $\hg$ satisfies~\cref{eq:shiftmn}
-with $\beta = \beta_{\psi}$ follows similarly to the argument used in  \cref{tgshift}
-with modifications similar to those introduced in the proof of \cref{gshiftmn}.
-Then, \cref{gmaxcontramn} gives the desired result.
-\end{comment}
-\end{proof}
-In what follows we denote by $\hv$ the unique fixed point of $\hg$ i.e., $\hv = \hg \hv\,$. 
-We now show that the vector $\hj$ dominates the vector $\hv$:
-\begin{lemma}\label{relation1}
-The vectors $\hv,\hj$ obey $\hj\geq\hv$.
-\end{lemma}
-\begin{proof}
-Let $ r_1,  r_2,\ldots, r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$, respectively,
-and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.
-
-It suffices to show that $V_1\eqdef \hg V_0 \le V_0 \le \hj$ since then the desired result follows
-by defining $V_{n+1} = \hg V_n$, $n\ge 1$, noting that by \cref{tgmonotone}, $V_{n+1}\le V_{n}$ and by  \cref{tmaxnormmn}, $V_n \to \hv$.
-
-Since $(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $1\leq i,j\leq n$ we have $V_0(i)  = (\Phi r_i)(i)$. Also, since $\hj(i) \ge (\Phi r_i)(i),1\leq i \leq n$ it follows that $\hj\geq V_0$. 
-Now,  fix any $i$. 
-We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi r'_{e_i,V_0})(i) \leq V_0(i)$. 
-By the definition of $r'_{e_i,V_0}$ we know that $(\Phi r'_{e_i,V_0})(i) \le (\Phi r)(i)$
-holds for any $r\in \N$ such that $W^\top E \Phi r \ge W^\top H V_0$. 
-Now it suffices to show that $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H V_0$. 
-By definition, $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H \Phi r_i$.
-Hence, by the monotone property of $H$ and \cref{grlpassmp}-\eqref{wassump} it is sufficient if $\Phi r_i \ge V_0$.
-This however directly follows from the definition of $V_0$.
-\end{proof}
-\begin{lemma}\label{relation2}
-The vectors $\hv,\tj$ obey $\tj\geq\hv$.
-\end{lemma}
-\begin{proof}
-%The proof follows in a similar manner as the proof of \Cref{relation1}. To elaborate, 
-Let $ r_1,  r_2,\ldots, r_n$ be solutions to the ALP in \eqref{alp} (with an additional constraint that the solution be restricted to $\N$) for $c=e_1, e_2,\ldots,e_n$, respectively,
-and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 
-follows in the same manner as the proof of \cref{relation1}.
-\end{proof}
-\begin{lemma}\label{srw}
-A vector
-$\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
-\begin{align}\label{grlpeqprog}
-\begin{split}
-\min_{r\in \N}\, &||\Phi r-\hv||_{1,c}\\
-\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r.
-\end{split}
-\end{align}
-\end{lemma}
-\begin{proof}
-We know from Lemma~\ref{relation2} that $\hj = \Phi \hr \geq\hv$, and thus
-the solutions to \eqref{grlp} do not change if we add the constraint $\Phi r \ge \hv$.
-Now, under this constraint, minimizing $c^\top \Phi r$ is the same as minimizing 
-\begin{align*}
-||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.
-\end{align*} 
-\end{proof}
-\begin{lemma}\label{srwalp}
-A vector
-$\tr \in \R^k$ is a solution to ALP \eqref{alp} iff it solves the following program:
-\begin{align}\label{grlpeqprog}
-\begin{split}
-\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
-\text{s.t.}\mb &\, \Phi r\geq  T \Phi r.
-\end{split}
-\end{align}
-\end{lemma}
-\begin{proof}
-We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$, and the rest of the arguments follow in the same manner as proof for \cref{srw}.
-\end{proof}
-\begin{lemma}\label{cmt1mn}
-We have
-\begin{align}
-||J^*-\hv||_{\mn}&\leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}&\nn\\+||\Gamma J^*-\hg J^*||_{\mn}\big).
-\end{align}
-\end{lemma}
-\begin{proof}
-Recall that $\hg \hv=\hv$. By the triangle inequality,
-\begin{align*}
-&||J^*-\hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+||\hg J^*-\hg \hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+\beta_\psi || J^*- \hv||_\mn,
-\end{align*}
-and so by reordering and with another triangle inequality,
-\begin{align}\label{jhv}
-&\norm{J^*-\hv}_{\mn} \nn\\&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\nn\\
-&\le \frac{\norm{ J^*-\Gamma J^*}_{\mn}+\norm{\Gamma J^* - \hg J^*}_{\mn}}{1-\beta_\psi}\,.
-\end{align}
-The proof follows by applying \cref{bestbndmn} on \eqref{jhv}.
-\end{proof}
-We now recall Lemma~$5$ from Section 4.2 of \cite{ALP}. 
-For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$ by assumption.
-\begin{lemma}\label{restate}
-%Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ ,
-For  $r \in \R^k$ arbitrary vector, let $r'$ be
-\begin{align}
- r'= r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0.
-\end{align}
-Then $r'$ is feasible for the ALP in \eqref{alp}.
-\end{lemma}
-Recall that $\hv$ is the fixed point of $\hg$ and $\hj=\Phi \hr$ is the solution to the GRLP
-\eqref{grlp}. 
-\begin{theorem}\label{mt2mn}
-We have
-\begin{align}
-||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn\\
-&+||\Gamma J^*-\hg J^*||_{\mn}).
-\end{align}
-\end{theorem}
-\begin{proof}
-Let $\gamma=||J^*-\Phi r^*||_{\mn}$. 
-Then, by choosing $r'$ as in Lemma~\ref{restate} we have
-\begin{align}\label{part}
-&||\Phi r'-J^*||_{\mn}\nn\\&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
-&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
-&=\frac{2}{1-\beta_\psi}\gamma.
-\end{align}
-%We know that $\tr \in \N$ by \cref{grlpassmp}-\eqref{nassmp} and 
-$r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. Then from \cref{srwalp} it follows that
-%As a result, from \cref{srw} it follows that
-\begin{align}
-&||\hj-\hv||_{1,c}\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\
-&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
-&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
-&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).
-\end{align}
-The result follows from \cref{cmt1mn} and \eqref{part}.
-%\textbf{Main Result~$1$: Prediction Error bound in weighted $L_\infty$-norm}
-\end{proof}
-\begin{theorem}[Prediction error bound in $\norm{\cdot}_{\mn}$]
-\label{cmt2mn}
-%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
-It holds that
-\begin{align}\label{finalbndmn}
-||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\nn\\
-&+2||\Gamma J^*-\hg J^*||_{\mn}).
-\end{align}
-\end{theorem}
-\begin{proof}
-We have
-\begin{align}
-&||J^*-\hj||_{1,c}\nn\\
-&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
-&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
-\end{align}
-The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
-\end{proof}
+%\textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\
 We now bound the performance of the greedy policy $\hu$.
@@
 \begin{align}\label{polderv}
-&||J_{\hu}-\hj||_{1,c}\nn\\&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
+||J_{\hu}-\hj||_{1,c}&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
 &\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
@@
 where in the second inequality, we use Jensen's inequality and $|T\hj - \hj|$ stands for the 
-vector whose $i$th component is $|(T\hj)(i) - \hj(i)|$. Further, the last inequality follows
-since $T$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta_{\psi}$ as noted earlier.
+vector whose $i$th component is $|(T\hj)(i) - \hj(i)|$ and the last inequality follows
+since $T$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta_{\psi}$, as we noted it earlier.
 %componentwise  $(I-\alpha P_{\hu})^{-1}$ is a positive operator for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. 
@@
 \end{proof}
-\begin{comment}
+%\begin{comment}
 \begin{note}
@@
 \end{note}
-\end{comment}
+%\end{comment}
+%The following result (Theorem~\ref{st}) supports Claim~$1$ in the above.\\
+The error term $\etmn$ gives new insights into constraint sampling. 
+\begin{theorem}[ On Constraint Sampling]\label{st}
+Let $s\in S$ be a state whose constraint was sampled. Then
+\begin{align}\label{sampexp}
+|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
+\end{align}
+\end{theorem}
+\begin{proof}
+Let $r_{e_s}$ and $\hat{r}_{e_s}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$.
+It is easy to note that $r_{e_s}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s})(s)\geq (\Phi \hat{r}_{e_s})(s)$.
+However, since all the constraints with respect to state $s$ have been sampled we know that $(\Phi \hat{r}_{e_s})(s)\geq J^*$.
+The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.
+\end{proof}

### 2016-07-08 single/resdisc.tex
Chandru's shortened version

%!TEX root =  autocontgrlp.tex
\section{Discussion}
In this section we discuss the implications and insights provided by the results presented in Theorems~\ref{cmt2mn} and ~\ref{polthe}.
\subsection{On Error Terms}
\begin{itemize}
\item The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
\begin{enumerate}
\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$,
\item $||\Gamma J^*-\hg J^*||_{\mn}$.
\end{enumerate}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\\
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.
\item Unlike the result in \cite{CS} which holds only for a specific RLP formulated under ideal assumptions, our bounds hold for any GRLP and as a result for any given RLP. Another interesting feature of our result is that it holds with probability $1$. 
\item A salient feature of the ALP formulation is the use of Lyapunov functions to control/shape the error across the states based on their relative importance. Since the error bounds are in a modified $L_\infty$-norm, the GRLP framework retains this salient feature of the ALP.
\end{itemize}
The fact that both the prediction and control problems can be addressed by the GRLP makes it a complete ADP method, and by addressing the constraint approximation, the GRLP framework is an important addition to the theory of ALP.
\subsection{On Constraint Reduction and Approximation}
We claim the following based on the error bounds that we derived for the GRLP.\\
{Claim $1$)} It is not always necessary to sample constraints according to the stationary distribution of the optimal policy.\\
{Claim $2$)} Constraint approximation is not only restricted to constraint sampling but also can be extended to include linear approximation of the constraints.\\
The following result (Theorem~\ref{st}) supports Claim~$1$ in the above.\\
\textbf{Main Result~$3$: On Constraint Sampling}\\
The error term $\etmn$ gives new insights into constraint sampling. 
\begin{theorem}\label{st}
Let $s\in S$ be a state whose constraint was sampled. Then
\begin{align}\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align}
\end{theorem}
\begin{proof}
Let $r_{e_s}$ and $\hat{r}_{e_s}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s})(s)\geq (\Phi \hat{r}_{e_s})(s)$. However, since all the constraints with respect to state $s$ have been sampled we know that $(\Phi \hat{r}_{e_s})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.
\end{proof}
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled. Thus the sampling distribution need not be the stationary distribution of the optimal policy as long as it samples the \emph{important} states, an observation that might theoretically explain the empirical successes of the RLP \cite{ALP,CST,SALP}.

To understand the implication of Claim~$2$ we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
\begin{align}\label{lag}
\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
\end{align}
The insight that the GRLP is a linear function approximation of the constraints (i.e., the Lagrangian multipliers) can be obtained by noting that $ Wq\approx \lambda$ in \eqref{lag2}. Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$). Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under the optimal policy $u^*$, i.e., 
\begin{align}
\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
\end{align}
where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.\\
\subsection{Reinforcement Learning}
Reinforcement Learning (RL) algorithms are useful in scenarios where the system is available in the form of a simulator or only samples can be obtained via direct interaction. In particular, in the RL setting, the model parameters $g$ and $P$ are not known explicitly and the underlying MDP needs to be solved by using sample trajectories. In short, RL algorithms are sample trajectory based solution schemes for solving MDPs whose model information is not known. RL methods learn by filtering out the noisy sample via stochastic approximation and they also employ function approximation in order to handle MDPs with large number of states. Most RL algorithms are sample trajectory based extensions of ADP methods.\\
The RL extension of the ALP formulation has been applied to the optimal stopping problem in \cite{ALP-Bor}. Function approximation is employed to approximate the square root of the Lagrange multipliers. However, since the approximation is not linear, convergence of the resulting RL algorithm cannot be guaranteed. Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.

### 2016-07-08 single/strel.tex
Chandru's shortened version

--- 2015-06-14 strel.tex
@@
 %!TEX root =  autocontgrlp.tex
-\section{A simple bound}
+\section{A worst-case bound}
 The following lemmas relate the fixed point $\hv$ of $\hg$ to the solution $\hj$ of the GRLP in \eqref{grlp}.
@@
 \end{align}
-The result follows by combining this bound with \eqref{mt2eq0} and Corollary~\ref{cmt1}.
+The result follows by combining this bound with \eqref{mt2eq0} and \cref{cmt1}.
 \end{proof}
@@
 $.
-The result now follows from Corollary~\ref{cmt1} and Theorem~\ref{mt2}.
+The result now follows from \cref{cmt1} and \cref{mt2}.
 \end{proof}
-The results presented in Corollary~\ref{cmt2} is in the $L_\infty$-norm. In the next section, we make use of Lyapunov functions to provide an improved bound in the weighted $L_\infty$-norm.
+When no constraints are removed, $\Gamma = \hg$.
+In this case, \eqref{finalbnd} can be compared to the bound in \cref{restateval} instantiated with $\psi = \one$, in which case the right-hand side of \eqref{finalbnd}
+becomes $\frac{2\norm{J^* - \Phi r^*}_{\infty}}{1-\alpha}$, i.e., the bound  \eqref{finalbnd} is a off by a factor three 
+only from that in \cref{restateval}.
+We view this as a small price paid to be paid for the increased generality of \eqref{finalbnd}.
+In terms of the price of removing constraints,
+the result shows that there is effectively no price to be paid for removing constraints as long as
+those constraints that are binding in the definition of $\Gamma J^*(i)$, $1\le i \le n$ are kept: 
+a rather intuitive result.
+\todoc{I am still trying to understand whether it is good or bad that the result is independent of $\N$.
+}
+
+Just like in the case of RLPs, it is possible to tighten the bounds by using weighted $\max$-norms. 
+This is the subject of the next section.

### 2016-07-08 single/autocontgrlp_flattened.tex
Still Chandru's version

\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
%\documentclass[12pt,onecolumn]{IEEEtran}
\usepackage{times}
\usepackage{hyperref}
\input{pack.tex}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\title{A Generalized Reduced Linear Program for Markov Decision Processes}
\author{Chandrashekar Lakshminarayanan and Shalabh Bhatnagar\\Department of Computer Science and Automation\\ Indian Institute of Science\\ Bangalore-560012\\\{chandrul,shalabh\}@csa.iisc.ernet.in\\ and \\
Csaba Szepesv\'{a}ri\\Department of Computing Science\\University of Alberta\\Edmonton, Alberta\\Canada T6G 2E8\\  szepesva@cs.ualberta.csa }

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
%\nipsfinalcopy % Uncomment for camera-ready version
\begin{document}
\maketitle
\begin{abstract}
The term Approximate Dynamic Programming (ADP) refers to a gamut of approximate solution methods for MDPs with large number of states. Though various ADP algorithms are known till date, very few of them successfully address both the prediction and the control problems. Approximate Linear Programming (ALP) is an ADP method that offers sound theoretical guarantees and solves both the prediction and the control problems. Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead. Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.\\
In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP. Central to our framework are two $\max$-norm contraction operators. Our result also theoretically justifies linear approximation of constraints. We discuss the implication of our results in the contexts of ADP and reinforcement learning.
\end{abstract}
\begin{keywords}{
Approximate Dynamic Programming (ADP), Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), Generalized Reduced Linear Program (GRLP), Constraint Sampling, Reinforcement Learning.}
\end{keywords}

\section{Introduction}\label{intro}
Optimal sequential decision making problems occurring in science, engineering and economics can be cast in the framework of Markov Decision Processes (MDPs). A policy $u$, is a mapping from state space to action space and it specifies the action selection mechanism. The problem of \emph{control} requires coming up with good policies and for which one needs to \emph{predict} the behavior of individual policies. The problem of \emph{prediction} deals with computing the value-function $J_u$\footnote{Also known as reward/cost-to-go function.} (a mapping from state space to reals) which specifies the value of each state under a given policy $u$. In order to solve an MDP it is necessary to solve the problem of prediction as well as the problem of control.\\
Given an MDP, ideally, we would be interested in computing the optimal value function $J^*$ and the optimal policy $u^*$. The Bellman equation (BE) relates these quantities. Conventional solution methods for MDPs \cite{BertB} such as value iteration, policy iteration and linear programming can compute exact values of $J^*$ and $u^*$ by either directly or indirectly solving the Bellman equation. By computing $J^*$ and $u^*$, the conventional methods address both the prediction and control problems. However, due to the curse-of-dimensionality, the size of the state space grows exponentially in the number of state variables and as a consequence most MDPs arising from practical applications have a large number of states. It is hence difficult to compute the exact values of $u^*$ and $J^*$ for MDPs with large number of states and the usage of conventional methods to solving MDPs is limited.\\
Approximate Dynamic Programming (ADP) \cite{dpchapter,powell} refers to a gamut of approximate solution methods to MDPs with large number of states. In order to reduce the computational effort, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy and restricting their search space to the chosen parameterized class. Thus, instead of computing exact values of $u^*$ and $J^*$, ADP methods only compute an approximate value function $\tilde{J}$ and a sub-optimal policy $\tilde{u}$. The quality of the ADP method is measured by the error $||J^*-\tilde{J}||$, in approximating the value function and the loss in performance due to the sub-optimal policy $||J^*-J_{\tilde{u}}||$, measured with respect to the optimal policy. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in the problem of finding a useful policy. In the context of ADP, the prediction and control problems are said to be addressed when the errors $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$ can be bounded so that the loss in performance due to the approximation can be quantified.\\
Value-function-only\footnote{Since this paper is concerned with results related to the Approximate Linear Programming formulation we do not discuss other classes of ADP methods such as \emph{actor-only} and \emph{actor-critic} methods.} (or \emph{critic-only}) ADP methods approximate the value function and use it to obtain a one-step look ahead policy by making use of the Bellman equation. Most widely used parameterization to approximate the value function is the linear function approximator (LFA). Methods employing LFA approximate the value function as $J_u\approx\Phi r^*$, where $\Phi$ is a feature matrix whose columns are the basis functions and $r^*$ is a weight vector to be learnt. Dimensionality reduction is achieved by choosing fewer number of basis functions compared to the number of states.\\
A host of value-function-based ADP methods solve the Projected Bellman equation (PBE) which is obtained by including the least squares projection operator in the BE so as to project quantities onto the lower dimensional subspace. A limitation of using the least squares projection operator is that it reduces the prediction error $L_2$-norm and cannot ensure policy improvement which requires prediction error to be minimum in the $L_\infty$-norm. Due to this norm mismatch, policy improvement cannot be guaranteed and \emph{policy-chattering} (policy-oscillations) can occur in practice \cite{dpchapter}. Thus the fundamental issue with the PBE based methods is that they fail to address the control problem.\\
The approximate linear programming (ALP) \cite{ALP,CS,SALP,ALP-Bor,gkp,fs,npalp} formulation also employs LFA, however, solves a linear program to compute $J^*\approx\tilde{J}=\Phi r^*$, and computes a one-step greedy policy. Since the ALP computes an approximation to $J^*$ and outputs only a single policy $\tilde{u}$, there is no issue of \emph{policy-chattering}. The ALP formulation also provides theoretical performance guarantees, i.e., both error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$ can be bounded. This makes the ALP an attractive method since it addresses both the prediction and control problems. However, an important shortcoming of the ALP is that the number of constraints are of the order of the state space. Due to the curse, the number of constraints can be large for practical MDPs and is a limitation.\\
In practice, the issue of large number of constraints in the ALP has been tackled by a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a reduced linear program (RLP). The RLP has been shown to perform well in experiments \cite{ALP,CS,CST} in various domains such as Tetris and in network of queues. However, the theoretical results \cite{CS} are available only for a specific RLP formulated under idealized conditions. Thus, there is a gap in the theoretical understanding of RLP and constraint reduction/approximation. Our aim in this paper is to provide theoretical guarantees which will make the RLP a complete ADP method that addresses both the prediction and the control problems.\\
In this paper, we develop a novel theoretical framework to study a generalized constraint reduction technique namely generalized reduced linear program (GRLP) and present its error analysis. The salient aspects of our contribution are listed below:
\begin{enumerate}
\item \textbf{Framework:}\\ We generalize the RLP to define the GRLP. The GRLP has a small number of constraints which are obtained as positive linear combinations of the original constraints of the ALP. The GRLP serves as a framework to analyze error due to constraint reduction and linear constraint approximation.
\item \textbf{Error Analysis:}
	\begin{itemize}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$. 
		\item We show that $||J^*-\hat{J}||\leq (c_1+c_2)$, where $c_1>0$, $c_2>0$ are constants. While the term $c_1$ is error inherent to the ALP formulation itself, the term $c_2$ is the additional error introduced due to constraint approximation.  
		\item We derive a greedy policy $\hu$ by making use of $\hj$ and bound the term $||J^*-J_{\hu}||$. 
		\item Akin to the error analysis in \cite{ALP,CS,SALP} our bounds are also in terms of a modified $L_\infty$-norm.
		\item Our analysis is based on two novel $\max$-norm contraction operators called the least upper bound (LUB) projection operator and the approximate least upper bound projection operator (ALUB). This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
\end{itemize}
\item \textbf{Significant Results:}
	\begin{itemize}
		\item We provide error bounds for both prediction and control errors, i.e., bound the terms $||J^*-\hj||$ and $||J^*-J_{\hu}||$ in a modified $L_\infty$-norm. Thus, the GRLP is a complete ADP method with performance guarantees for both the prediction as well as control problems. The modified $L_\infty$-norm allows us to choose the quality of approximation across various states. This makes our result an important addition to the theory of ALP \cite{ALP,CS,CST,SALP}.
		\item The structure of the error terms also reveals an important result that it is not always necessary to sample using the stationary distribution of the optimal policy. This throws additional light on constraint sampling by providing a better explanation for its empirical success even in those cases when sampling distributions other than the stationary distribution of the optimal policy was used. 
		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints. This means that constraint reduction is not only limited to sampling but also can be extended to include linear combinations of constraints.
	\end{itemize}
\item We also discuss the implication of our results in the context of reinforcement learning and also present a numerical example illustrating the theory developed. A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.
\end{enumerate}

\section{Markov Decision Processes (MDPs)}
In this section, we briefly discuss the basics of Markov Decision Processes (MDPs) (the reader is referred to \cite{BertB,Puter} for a detailed treatment).\\
An MDP is a $4$-tuple $<S,A,P,g>$, where $S$ is the state space, $A$ is the action space, $P$ is the probability transition kernel and $g$ is the reward function. We consider MDPs with large but finite number of states, i.e., $S=\{1,2,\ldots,n\}$ for some large $n$, and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\\
A policy $\mu$ specifies the action selection mechanism, and is described by the sequence $\mu=\{u_1,u_2,\ldots,u_n,\ldots\}$, where $u_n\colon S \ra A, \mbox{ }\forall n \geq 0$. A stationary deterministic policy (SDP) is one where $u_n\equiv u, \mbox{ }\forall n\geq 0$ for some $u\colon S \ra A$. By abuse of notation we denote the SDP by $u$ itself instead of $\mu$. In the setting that we consider, one can find an SDP that is optimal \cite{BertB,Puter}. In this paper, we restrict our focus to the class $U$ of SDPs.  Under an SDP $u$, the MDP is a Markov chain with probability transition kernel $P_u$.\\
Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
\begin{align}
J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n)\mbox{ }\forall n\geq 0],\nn
\end{align}
where $\alpha \in (0,1)$ is a given discount factor. Here $J_u(s)$ is known as the value of the state $s$ under the SDP $u$, and the vector quantity $J_u\stackrel{\Delta}{=}(J_u(s), \forall s\in S)^\top\in R^n$ is called the value-function corresponding to the SDP $u$.\\
The optimal policy $u^*$ is obtained as $u^*(s)\stackrel{\Delta}{=}\arg\max_{u\in U}J_u(s)$\footnote{Such $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{Puter}.}. The optimal value-function $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$. Given an MDP, our aim is to find the optimal value function $J^*$ and the optimal policy $u^*$. The optimal policy and value function obey the Bellman equation (BE) as under: $\forall s \in S$,
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
\label{bellpol}u^*(s)&=\arg\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big).
\end{align}
\end{subequations}
Typically $J^*$ is computed first and $u^*$ is obtained by substituting $J^*$ in \eqref{bellpol}. The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
\begin{definition}
\begin{align}
(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big), 
\end{align}
where $J\in \R^n$. Similarly one can define the Bellman operator restricted to an SDP $u$ as follows:
\begin{align}
(T_uJ)(s)=\big(g_{u(s)}(s)+\alpha \sum_{s'} p_{u(s)}(s,s')J(s')\big).
\end{align}
\end{definition}
Given $J \in \R^n$, $TJ$ is the `one-step' greedy value function. It is also useful to define the notion of a one-step greedy policy as below:
\begin{definition}
A policy $\tilde{u}$ is said to be greedy with respect to $\tilde{J}$ if
\begin{align}\label{subpol}
\tilde{u}(s)=\underset{a \in A}{\arg\max}(g_a(s)+\alpha\sum_{s'} p_a(s,s')\tilde{J}(s')).
\end{align}
\end{definition}
\begin{definition}
We also define the $Q$-Bellman operator \cite{BertB} $H$. Given any $J\in \R^n$ we have,

\begin{align}
HJ&=\left[ {\begin{array}{c} H_1 J  \\ \vdots \\ H_d J\end{array}} \right]\in \R^{nd},\mbox{where}\nn\\
(H_a J)(s)&= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s'), \forall s\in S, a\in A,
\end{align}
\end{definition}
 We now state without proof the important properties related to the Bellman operator. Though in these results, we make use of the Bellman operator $T$, the results also trivially hold for $T_u$ as well.
\subsection{Properties of $T$}
\begin{lemma}\label{maxnorm}
$T$ is a $\max$-norm contraction operator, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
\begin{align}
||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
\end{align}
\end{lemma}
\begin{corollary}\label{uniquesol}
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{corollary}
The Bellman operator $T$ exhibits two more important properties presented in the following lemmas (see \cite{BertB} for proofs):
\begin{lemma}\label{monotone}
$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_2\geq J_1$, we have $T J_2\geq T J_1$. Further, if $J\in \R^n$ is such that $J\geq TJ$, it follows that $J\geq J^*$.
\end{lemma}
\begin{lemma}\label{shift}
Given $J\in \R^n$, $t \in \R$ and $\mathbf{1} \in \R^n$, a vector with all entries $1$, we have
\begin{align}
T(J+t\mathbf{1})=TJ+\alpha t\mathbf{1}.
\end{align}
\end{lemma}
Note that Lemmas~\ref{maxnorm}-\ref{shift} also hold for the $Q$-Bellman operator $H$.
Solving an MDP involves handling two sub-problems namely the problem of \emph{control} and the problem of \emph{prediction}. The problem of \emph{control} deals with coming up with a good (and if possible the optimal) policy. Often, in order to solve the problem of \emph{control}, one needs to solve the problem of \emph{prediction}, which deals with computing the value function $J_u$ of the policy $u$. The fact that the two problems are related is reflected in the Bellman equation in \eqref{bell}, where $J^*$ from \eqref{bellval} is used in \eqref{bellpol} to obtain the optimal policy $u^*$. Thus, the Bellman equation is at the heart of the solution methods to MDPs. Any solution method to MDP is said to be complete only if it satisfactorily (with provable performance guarantees) addresses both the prediction and the control problems. \\
The basic solution methods namely value iteration, policy iteration and linear programming (LP) formulation \cite{BertB} solve both the control and prediction problems. Of the three basic methods, in this paper, we are interested in the LP formulation given by
\small
\begin{align}\label{mdplp}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall s\in S, a \in A,
\end{align}
\normalsize
where $c\in \R^n_+$ is any vector whose components are all non-negative. One can show that $J^*$ is the solution to the LP formulation \eqref{mdplp} \cite{BertB}. 
Also, of the three methods, value iteration and LP formulation are value function based methods, i.e., they compute $J^*$ directly and then $u^*$ is obtained by plugging $J^*$ in \eqref{bellpol}.\\
While the basic methods (i.e., VI, PI and LP) can be used to compute exact values $J^*$ and $u^*$ for MDPs with a small number of states, they are computationally expensive in the case of MDPs with a large number of states.
\section{Approximate Dynamic Programming}
\emph{Curse-of-Dimensionality} is a term used to denote the fact that the number of states grows exponentially in the number of state variables. Most MDPs arising in practical applications suffer from the curse, i.e., have large number of states and it is difficult to compute $J^*/J_u\in \R^n$ exactly in such scenarios. Approximate dynamic programming (ADP) \cite{lspi,lspe,ALP,wang2014approximate} methods compute an approximate value function $\tilde{J}$ instead of $J^*/J_u$. In order to tackle the curse, ADP methods resort to dimensionality reduction by parameterizing the value function and/or the policy. Value-function based ADP methods form an important subclass of ADP methods whose brief overview is given below.
\subsection{Value-Function based ADP}
In the value-function based ADP schemes a parameterized family is chosen and the approximate value-function $\tilde{J}$ is picked from the chosen parameterized class.
Once the approximate value function $\tilde{J}$ is computed, a sub-optimal policy $\tilde{u}$ can be obtained as the one-step greedy policy with respect to $\tilde{J}$ by making use of \eqref{subpol}.
The following lemma characterizes the degree of sub-optimality of the greedy policy $\tilde{u}$.
\begin{lemma}\label{subopt}
Let $\tilde{J}$ be the approximate value function and $\tilde{u}$ be as in \eqref{subpol}, then 
\begin{align}
||J^*-J_{\tilde{u}}||_\infty \leq \frac{2}{1-\alpha}||J^*-\tilde{J}||_\infty.
\end{align}
\end{lemma}
The quality of any ADP method depends on the approximation guarantees it offers for the quantities $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$, where $||\cdot||$ is an appropriate norm. The term  $||J^*-\tilde{J}||$ denotes the error in prediction and $||J^*-J_{\tu}||$ denotes the loss in performance resulting from the sub-optimal policy $\tu$ with respect to the optimal policy $u^*$. Of the two error terms, $||J^*-J_{\tu}||$ is more important because ultimately we are interested in coming up with a useful policy. In the context of ADP methods, the control and prediction problems are said to be addressed when the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tu}||$ are bounded by ``small'' constants.\\
\subsection{Linear Function Approximation}
The most widely used parameterized class to approximate the value-function is the linear function approximator (LFA). Under LFA, the value-function is approximated as $\tilde{J}=\Phi r^*$, with $\Phi=[\phi_1|\ldots|\phi_k]$ being an $n\times k$ feature matrix and $r^*$ is the parameter to be learnt.\\
There are two important approaches to value function approximation. Both the approaches start out with a basic solution method and appropriately introduce function approximation in it. The two approaches are:
\begin{enumerate}
\item The Projected Bellman Equation (PBE) which combines the BE and the linear least squares projection operator to project high dimensional quantities onto the subspace of the LFA.
\item The approximate linear programming formulation which introduces the LFA in the linear programming formulation. 
\end{enumerate}
A host of ADP methods are based on the PBE and have been found to be useful in practice. The main application of the PBE is for approximate policy evaluation, i.e., to compute $\tilde{J}_u$, an approximation to the value function $J_u$ of policy $u$. Due to the mismatch in the norms, i.e, the linear least squares projection operator based on the $L_2$-norm and the $L_\infty$-norm of the Bellman operator $T$, one cannot use the PBE to obtain a direct approximation to $J^*$. Thus in order to solve the problem of control, $\tilde{J}_u$ is used to compute a one-step greedy policy. However, again due to the mismatch in the norms, i.e., $L_2$-norm of the linear least squares projection and the $L_\infty$ norm required for policy improvement (Lemma~\ref{subopt}), the one-step greedy policy need not necessarily be an improvement. This leads to a phenomenon called \emph{policy-chattering} \cite{dpchapter} where looping within of bad policies can occur. Further, such policy-chattering can be demonstrated in simple examples as well \cite{dpchapter}. Thus, though the approximate value function obtained by solving the PBE offers guarantees for prediction it does not offer any guarantees for the control problem, a significant shortcoming of the PBE based methods.\\
The ALP formulation \cite{ALP} on the other hand does not suffer from issues such as policy-chattering, for the simple reason that it computes $\tilde{J}$ which is an approximation to $J^*$ and a one-step greedy policy $\tilde{u}$ obtained using $\tilde{J}$. In short, since there is only one policy that the ALP outputs there is no question of policy-chattering. Further, the ALP offers performance guarantees for both the error terms $||J^*-\tilde{J}||$ and $||J^*-J_{\tilde{u}}||$. Though the ALP is a complete method addressing both the control and prediction problems, it nevertheless suffers from an important limitation in the form of large number of constraints (as large as the size of the state space). This limitation has been addressed in literature by sampling only a fewer tractable constraints to formulate a reduced linear program (RLP). The RLP has been shown to perform well in practice \cite{ALP,CS,CST}, but theoretical performance guarantees \cite{CS} are available for a specific RLP obtained under idealized assumptions. In this paper, by providing a sound theoretical analysis of the RLP, we aim to show that RLP is a complete method that addresses both the prediction and the control problems.
We achieve this by developing and presenting a comprehensive theoretical framework to understand the constraint reduction/approximation procedure.\\
In the next section, we discuss the approximate linear programming (ALP) formulation, the basic results and present prior results in literature as well as motivate the problem that we address in this paper.

\section{Approximate Linear Programming}
The LP formulation in \eqref{mdplp} can be represented in short as,
\begin{align}\label{mdplpshort}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J\geq T J,\\
\textbf{or}\nn\\
\label{shortalter}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &EJ\geq H J,\\
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $E$ is an $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other. Note that \eqref{mdplpshort} and \eqref{shortalter} are identical programs and differ only in notation. We use notation of type \eqref{mdplpshort} whenever we prefer brevity and we use notation \eqref{shortalter} in some definitions and proof for the sake of clarity.
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by letting $J=\Phi r$ in \eqref{mdplpshort} and is given as
\begin{align}\label{alp}
\min_{r\in \R^k} &c^\top \Phi r\nn\\
\text{s.t}\mb &\Phi r\geq T \Phi r.
\end{align}
Unless specified otherwise we use $\tr$ to denote the solution to the ALP and $\tj=\Phi \tr$ to denote the corresponding approximate value function. We now state the assumptions and definitions used for the rest of the paper.
\begin{assumption}\label{one}
The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. In other words, the constant function is part of the basis.
\end{assumption}
\begin{assumption}\label{probdist}
$c=(c(i),i=1,\ldots,n)\in \R^n$ is a probability distribution, i.e., $c(i)\geq 0$ and $\sum_{i=1}^n c(i)=1$.
\end{assumption}
\begin{definition}
Given a function $\chi\colon S\ra \R^+$ we define the quantity $\beta_{\chi}$ as
\begin{align}
\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}.
\end{align}
\end{definition}
\begin{definition}
The function $\chi$ is then said to be a \emph{Lyapunov} function if $\beta_{\chi}<1$.
\end{definition}
\begin{assumption}\label{lyap}
$\psi\colon S \ra \R^+$ is a Lyapunov function and is present in the column span of the feature matrix $\Phi$.
\end{assumption}
It is straightforward to check that the function $\one$ is a Lyapunov function and trivially is present in the column span of $\Phi$. 
\begin{definition}\label{modlone}
The modified $L_1$-norm is defined as
\begin{align}
||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|,
\end{align}
where $c$ obeys Assumption~\ref{probdist}.
\end{definition}
\begin{definition}\label{modnorm}
The modified $L_\infty$-norm is defined as follows:
\begin{align}
||J||_{\infty,\rho}=\max_{s \in S} \rho(s) |J(s)|,
\end{align}
where $\rho \colon \S \ra \R^+$, $J\in \R^n$.
\end{definition}
In Definition~\ref{modnorm}, the use of the weighting function $\rho$ allows us to measure the error taking into account the relative importance of the various states. A lower value of $\rho(s)$ means that the state $s$ is less important and vice-versa.\\
We recall below Theorem~$4.2$ of \cite{ALP} which bounds the error in the approximate value function.
\begin{theorem}\label{restateval}
Let $\tr$ be the solution to the ALP in \eqref{alp}, $\tilde{J}_c=\Phi \tilde{r}_c$, $\psi$ be a Lyapunov function and $c$ be a distribution as in \eqref{probdist}, then 
\begin{align}
||J^*-\tj||_{1,c}\leq \frac{2c^\top \psi}{1-\beta_{\psi}}\min_{r}||J^*-\Phi r||_{\mn}.
\end{align}
\end{theorem}
We now recall Theorem~$3.1$ of \cite{ALP} that characterizes the loss in performance of the greedy policy.
\begin{theorem}\label{restatepol}
Let $\tilde{u}$ be the greedy policy with respect to the solution $\tj$ of the ALP, then 
\begin{align}
||J^*-J_{\tu}||_{1,c}\leq \frac{1}{1-\alpha}||J^*-\tj||_{1,c'},
\end{align}
where $c'=(1-\alpha)c^\top(I-\alpha P_{\tu})^{-1}$.
\end{theorem}
Theorems~\ref{restateval} and ~\ref{restatepol} together imply that the ALP addresses both the control and prediction problems. Please refer to \cite{ALP} for a more detailed treatment of the ALP.\\
Note that the ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplpshort} which has $n$ variables. Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.

\section{Constraint sampling}
The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP. While the objective function of the RLP is the same as that of the ALP, the RLP has only $m<<nd$ constraints sampled from the original ALP according to a given probability distribution. The reduced linear program is then given by
\small
\begin{align}\label{rlp}
\min_{J\in \R^n} &c^\top J\nn\\
\text{s.t}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'), \mb\forall (s,a) \in \I,
\end{align}
\normalsize
where $\I$ is the index set containing the $m$ sampled state-action pairs. Using the index set $\I$ we define an $nd\times m$ matrix $\M$, called the constraint sampling matrix as below.
\begin{definition}\label{csampmat}
Let $\I=\{(s_1,a_1),\ldots,(s_m,a_m)\}$ be the sampled state-action pairs and let $q_i\stackrel{\Delta}{=}s_i+(a_i-1)\times n,\forall i=1,\ldots,m$. Then the constraint sampling matrix associated with the index set $\I$ is given by
\begin{align}
\M(i,j)&=1, \mb\text{if}\mb q_i=j\nn\\
&=0, \mb\text{otherwise}.
\end{align}
\end{definition}
The RLP can then be represented in short as
\begin{align}\label{rlpshort}
\min_{r\in \N} &c^\top \Phi r\nn\\
\text{s.t}\mb & \M^\top E \Phi r \geq \M^\top H \Phi r,
\end{align}
where $\M$ is a constraint sampling matrix as in Definition~\ref{csampmat} and $\N\subset \R^k$ is a bounded set such that $\tr \in \N$. Note that the feasible set of the RLP is a superset of the feasible set of the ALP.\\
The RLP based on constraint sampling has been found to perform well empirically in application domains ranging from controlled queuing networks (see section $6.2$ of \cite{ALP} and section $7$ of \cite{SALP}) to Tetris (see \cite{CST} and section $6$ of \cite{SALP}). However, the theoretical guarantees for the RLP are available only under a restricted setting \cite{CS}. We present the main result of \cite{CS} on constraint sampling, and to that end define the following:
\begin{definition}\label{sampdist}
Given a policy $u$ and Lyapunov function $\psi$ in the column span of $\Phi$, we define probability distributions $\mu_u$, $\mu_{u,\psi}$ and constant $\theta$ as 
\begin{align}
\mu^\top&\stackrel{\Delta}{=}(1-\alpha)c^\top (I-\alpha P_u)^{-1},\nn\\
\mu_{u,\psi}(s,a)&\stackrel{\Delta}{=}\frac{\mu_{u}(s) \psi(s)}{\mu_u^\top \psi d},\nn\\
\theta&\stackrel{\Delta}{=}\frac{(1+\beta_{\psi})}{2}\frac{\mu_{u^*}^\top \psi}{c^\top J^*}\sup_{r\in \N}||J^*-\Phi r||_{\mn}.
\end{align}
\end{definition}
We now recall Theorem~$3.1$ of \cite{CS} below.
\begin{theorem}\label{csresult}
Let $\epsilon$ and $\delta$ be scalars in $(0,1)$. Let $u^*$ be the optimal policy and $\I$ an index set containing the $m$ state-action pairs sampled independently according to the distribution $\psi_{u^*,\psi}$, for some Lyapunov function $\psi$, where
\begin{align}
m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln\frac{2}{\delta}\big).
\end{align}
Let $\tilde{r}$ be an optimal	solution of the ALP and let $\hat{r}$ be the solution of the corresponding RLP, then with probability at least $1-\delta$, we have
\begin{align}
||J^*-\Phi \hat{r}||_{1,c}\leq ||J^*-\Phi \tilde{r}||_{1,c}+\epsilon||J^*||_{1,c}.
\end{align}
\end{theorem}
\textbf{Motivation for our work:}\\
The result in Theorem~\ref{csresult} has a significant limitation in that the sampling distribution $\mu_{u^*,\psi}$ requires the knowledge of $u^*$. The optimal policy $u^*$ might not be available in practice and hence it would not be possible to even formulate the specific RLP for which the bound in Theorem~\ref{csresult} applies. However, as mentioned before, the RLP has performed reasonably well even when the sampling distribution is not $\mu_{u^*,\psi}$. Thus there is a gap between the theoretical understanding of the RLP and its practical efficacy which merits our attention. The gap also indicates that the RLP might be a special case of a generalized constraint reduction scheme with provable performance guarantees. Understanding such a generalized method would result in an ALP based ADP techinque that would have theoretical performance guarantees while being practically useful. In particular, we wish to answer the following open questions.
\begin{itemize}
\item  As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?
\item Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
\end{itemize}
In this paper, we address both of the questions above.

\section{Generalized Reduced Linear Program}
In this section we present the generalized reduced linear program (GRLP) which is obtained by appropriately extending the definition of the RLP. An important property that should carry over from the RLP is that the feasible set of the GRLP should also be a superset of the feasible set of the ALP. A natural way to achieve this is to replace the set of sampled constraints in the RLP by a set of constraints which are obtained as linear combinations of the original constraints of the ALP. Formally, we define the generalized reduced linear program (GRLP) as below:
\begin{align}\label{grlp}
\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb & W^\top E\Phi r\geq W^\top H \Phi r, 
\end{align}
where $W \in \R_+^{nd\times m}$ is an $nd\times m$ matrix with all nonnegative entries and $\chi \subset \R^k$ is any bounded set such that $\hj \in \chi$. Thus the $i^{th}$ ($1\leq i\leq m$) constraint of the GRLP is a positive linear combination of the original constraints of the ALP. Constraint reduction is achieved by choosing $m<<nd$. The key difference between the RLP in \eqref{rlpshort} and the GRLP in \eqref{grlp} despite their similar structure is that while $\M$ is a matrix of only zeros and ones, $W$ is a matrix of positive entries alone. Also note that an RLP is trivially a GRLP as well. Unless specified otherwise we use $\hr$ to denote the solution to the GRLP in \eqref{grlp}, $\hj=\Phi \hr$, to denote the corresponding approximate value function and $\hu$ to denote the greedy policy with respect to $\hj$.\par
Note that we want to avoid certain uninteresting and trivial cases of $W$ matrix such as $W=0$ or an entire column of $W$ being zero (which means no constraint is generated with respect to that column). Thus it is intuitive to demand that every column of $W$ should be non-negative and have at least one entry which is strictly positive. Also, normalizing columns of $W$ so that they sum to $1$ does not make any difference to the constraints of the RLP. Keeping these in mind we also assume the following throughout the rest of the paper:
\begin{assumption}\label{wassump}
$W \in \R^{nd\times m}_+$ is a full rank $nd\times m$  matrix (where $m<<nd$) and each of its column sums equals $1$.
\end{assumption}
The above assumption is just a technical condition that eliminates uninteresting choices such as $W=0$ or cases when certain columns of $W$ have all zeros, which implies that the corresponding column generates no constraint.

\begin{figure}[h!]
\centering
%\resizebox{columnwidth}{2cm}{
\begin{tikzpicture}[domain=-10:7.7,scale=0.6,font=\small,axis/.style={very thick, ->, >=stealth'}]
%\draw[line,thick,->] (-1,-0.625)--(4,-0.625);
%\draw[line,thick,->] (0,-1)--(0,4);
%\draw[line,thick,-](-0.2,-0.6)--(1,3);
\draw[line,thick,-](0.5,3.5)--(1,1);
\draw[line,thick,-](1,1)--(3,1.5);
\draw[line,thick,-](3,1.5)--(4,2.1);
\node[](one) at (2,2.3){\text{$J\geq TJ$}};
\node[rotate=-45](seven) at (-0.5,2.3){\text{\tiny $W^\top J\geq W^\top TJ$}};
\node[](two) at (-0.3,-0.5){\text{$\Phi r$}};
\node[](three) at (0.7,0.7){\text{$J^*$}};
%\draw[line,thick,-](0,0)--(4,2.5);
 \draw [ultra thick, draw=white, fill=gray, opacity=0.5]
       (0.5,3.5)--(1,1)--(3,1.5)--(4,2.1) -- cycle;
\draw[line,thick,-](-1,-0.625)--(3,1.8750);
 \fill (1,1)  circle[radius=2pt];
 \fill (2,1.25)  circle[radius=2pt];
 \fill (0.5,0.3125)  circle[radius=2pt];
\draw[line,dashed,-](-1,0.1)--(6,1);
\draw[line,dashed,-](-1,0.1)--(-2,5);
 \draw [ultra thick, draw=white, fill=gray, opacity=0.2]
       (-1,0.1)--(6,1)--(-2,5) -- cycle;
\node[] (four) at (2,0.8){\text{$\tilde{J}_c$}};
\node[] (six) at (0.5,-0.1){\text{$\hat{J}_c$}};
\end{tikzpicture}
%}
\caption{The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints. The main contribution of the paper is to bound $||J^*-\hat{J}_c||$.}
\label{cartoon}
\end{figure}

The rest of the paper develops analytically various performance bounds and our main results provide the following:
\begin{enumerate}
\item A bound for $||J^*-\hj||$, the error between the approximate value function $\hj$ as computed by the GRLP and the optimal value function $J^*$;
\item a bound for $||J^*-J_{\hu}||$, the loss in performance due to the greedy policy $\hu$ measured with respect to the optimal policy; and
\item an important result on constraint sampling.
\end{enumerate}
We achieve the above via two novel $\max$-norm contraction operators namely the least upper bound (LUB) projection operator (denoted by $\Gamma$) and the approximate least upper bound (ALUB) projection operator (denoted by $\hat{\Gamma}$). We bound the error due to constraint approximation by analyzing the fixed points of the operators $\Gamma$ and $\hg$. We first establish our results in the $L_\infty$-norm and then extend the same in a modified $L_\infty$-norm. The schematic in Fig. ~\ref{schematic} provides a pictorial representation of what shall follow in the next three sections.
\FloatBarrier
\begin{figure}[h!]
\centering
%\resizebox{columnwidth}{}{
\begin{tikzpicture}[domain=0:7.7,scale=0.8,font=\small,axis/.style={very thick, ->, >=stealth'}]
\draw [line,thick,-] (0,-1)--(0,4.7);
\draw [line,thick,-] (0,4.7)--(12.5,4.7);
\draw [line,thick,-] (12.5,4.7)--(12.5,-1);
\draw [line,thick,-] (0,-1)--(12.5,-1);
\node[](one) at (1.5,0.5) {$\tj$};
\node[](four) at (2.5,0.5) {$\geq$};
\node[](two) at (5,0.5) {$\tv$};
\node[](three) at (10,0.5) {$J^*$};
\node[](five) at (7.5,0.5) {$\geq$};
\node[](six) at (10,3.7) {$\hj$};
\node[](seven) at (5,3.7) {$\hv$};
\node[](eight) at (7.5,3.7) {$\leq$};
\node[](nine) at(1.5,0){\text{Solution }};
\node[](twenty) at(1.5,-0.5	){\text{to ALP }};
\node[](ten) at(5,0){\text{Fixed point of }$\Gamma$};
\node[](eleven) at(10,0){\text{Optimal Value Function }};
\node[](twelve)at (10,4.2){\text{Solution to GRLP}};
\node[](thirteen)at (5,4.2){\text{Fixed point of }$\hg$};
\draw [line,thick,<->] (5,3.2)--(9.8,0.9);
\draw [line,thick,<->] (5,3.2)--(9.8,3.2);
\draw [line,thick,<->] (9.8,3.2)--(9.8,0.9);
\node[](fourteen)at (6,2.2){$d_1$};
\node[](fifteen)at (6.5,2.9){$d_2$};
\node[](sixteen)at (11.2,2.2){$d\leq d_1+d_2$};
\node[](eighteen)at (11,1.6){\text{Corollary~\ref{cmt2}}};
\node[](seventeen)at (8,2.9){\text{(Theorem~\ref{mt2}})};
\node[](fourteen)at (6,1.8){\text{(Theorem~\ref{mt1})}};
\node[](fourteen)at (6,1.3){\text{(\& Corollary~\ref{cmt1})}};
%\node[rotate=-25](fourteen)at (7.5,1.5){\text{(Theorem~\ref{mt1})}};
%\node[draw, circle](two) at (5.5,1) {$s_{n+1}=s'$};
%\draw[->, =>latex](one) edge[bend left=42.5](two);
%\node [above=1.1cm]at (2.8,1.2) {${p_{a_n}(s,s')}$};
%\node [right] at(0,0){$g_{a_n}(s_n)$};
\end{tikzpicture}
%}
\caption{A schematic of the error analysis. Here $d=||J^*-\hj||_{1,c}.$}
\label{schematic}
\end{figure}

\section{Least Upper Bound Projection}\label{sec:lubp}
The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined as below:
\begin{definition}\label{lubpop}
Given $J\in \R^n$, its least upper bound projection is denoted by $\Gamma J$ and is defined as 
\begin{align}\label{gamdef}
(\Gamma J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb \forall i=1,\ldots,n,
\end{align}
where $V(i)$ denotes the $i^{th}$ component of the vector $V\in \R^n$. Also in \eqref{gamdef}, $e_j$ is the vector with $1$ in the $j^{th}$ place and zeros elsewhere, and $r_{e_j}$ is a solution to the linear program in \eqref{lubplp} for $c=e_j$.
\begin{align}\label{lubplp}
r_c\stackrel{\Delta}{=}\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb &\Phi r\geq  TJ.
\end{align}
\end{definition}
\vspace{-10pt}
\begin{remark}
\mb\\
\vspace{-10pt}
\begin{enumerate}
\item The definition of LUB operator $\Gamma \colon \R^n \ra \R^n$ involves $n$ associated linear programs.
\item Observe that $\Gamma J\geq TJ$ (follows from the fact that if $a\geq c$ and $b\geq c$, then $\min(a,b)\geq c$, where $a, b, c \in \R$).
\item Given $\Phi$ and $J\in \R^n$, define $\F\stackrel{\Delta}{=}\{\Phi r|\Phi r\geq TJ\}$. Thus $\F$ is the set of all vectors in the span of $\Phi$ that upper bound $TJ$. By fixing $c$ in the linear program in \eqref{lubplp} we select a unique vector $\Phi r_c \in \F$. The LUB projection operator $\Gamma$ picks $n$ vectors $\Phi r_{e_i},i=1,\ldots,n$ from the set $\F$ and $\Gamma J$ is obtained by computing their component-wise minimum.
\item Even though $\Gamma J$ does not belong to the span of $\Phi$, $\Gamma J$ collates the various best upper bounds that can be obtained via the linear program in \eqref{lubplp}.
\item The LUB operator $\Gamma$ in \eqref{gamdef} bears close similarity to the ALP in \eqref{alp}.
\end{enumerate}
\end{remark}
\begin{definition}\label{bestproj}
The LUB projection of $J^*$ is denoted by $\bj=\Gamma J^*$.
\end{definition}
We now characterize the LUB projection operator $\Gamma$ in the following lemmas (all the proofs are presented in the Appendix). As mentioned earlier, the error analysis depends on two $\max$-norm contraction operators the first of which is $\Gamma$. The important result of this section is Theorem~\ref{fxpres} and it relates the fixed point $\tilde{V}$ of $\Gamma$ to $J^*$.
\begin{lemma}\label{bestbnd}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_\infty$, then 
\begin{align}
||J^*-\bj||_\infty\leq 2||J^*-\Phi r^*||_\infty.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef} and the construction of $V_0$, Assumption~\ref{one}, and the fact that $\Phi r^*+||J^*-\Phi r^*||_\infty \one\geq TJ^*$. To see this, note that
\begin{align}
&\Gamma J^*=\hj \geq J^*,\nn\\
&\Phi r^* +||J^*-\Phi r^*||_\infty\geq TJ^*= J^*.\nn\\
&\text{Thus,}\nn\\
&\Phi r^* +||J^*-\Phi r^*||_\infty\geq \Gamma J^*\geq TJ^*.
\end{align}
\end{proof}

\begin{lemma}\label{gmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\geq J_2$, we have $\Gamma J_1\geq \Gamma J_2$.
\end{lemma}
\begin{proof}
Choose any $i\in \{1,\ldots,n\}$ and let $r^1_{e_i}$ and $r^2_{e_i}$ be solutions to the linear program in \eqref{lubplp} for $c=e_i$ with $J=J_1$ and $J=J_2$ respectively. Since $J_1\geq J_2$, we have $TJ_1\geq TJ_2$ and $e_i^\top \Phi r^1_{e_i} \geq e_i^\top \Phi r^2_{e_i}$, i.e., $(\Phi r^1_{e_i})(i)\geq (\Phi r^2_{e_i})(i)$. The result follows from the fact that $(\Gamma J)(i)=(\Phi r_{e_i})(i),\mb\forall J\in \R^n$, and our choice of $i$ was arbitrary.
\end{proof}
\begin{lemma}\label{lpsol}
Let $A\in \R^{u\times v}$, $b,c\in R^u$, $x_0 \in R^v$ and $b_0=Ax_0$. Then
\begin{align}
\min\{c^\top Ax:Ax\geq b+b_0\} =\min\{c^\top Ax:Ax\geq b\}+c^\top b_0.
\end{align}
\end{lemma}
\begin{proof}
The claim can be shown by a simple change of variables.
\end{proof}
\begin{lemma}\label{gshift}
Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+k\one$, then $\Gamma J_2=\Gamma J_1+\alpha t\one$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear programs associated with $\Gamma J_1$ and $\Gamma J_2$. The result follows by using Lemma~\ref{lpsol} with $A=\Phi$, $b=TJ$, $c=e_i$, $b_0=\alpha t\mathbf{1}$ and $x_0=\alpha t e_i$.
\end{proof}
\begin{theorem}\label{gmaxcontra}
The operator $\Gamma  \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n,$ let $\epsilon=||J_1-J_2||_\infty$. Thus,
\begin{align}\label{ineq}
J_2-\epsilon\one\leq J_1\leq J_2+\epsilon \one.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshift}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\alpha \epsilon\one\leq \Gamma J_1\leq \Gamma J_2+\alpha \epsilon\one.
\end{align}
\end{proof}
\begin{corollary}
The iterative scheme in \eqref{pvi} based on the LUB projection operator $\Gamma$ in \eqref{gamdef} converges to a unique fixed point $\tv$.
\begin{align}\label{pvi}
V_{n+1}&=\Gamma V_n,\mb \forall n\geq 0.
\end{align}
\end{corollary}
\begin{lemma}\label{gfp}
 $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, obeys $\tv\geq T\tv$.
\end{lemma}
\begin{proof}
Consider the $i^{th}$ linear program associated with $\Gamma \tv$. We know that $\Phi r_{e_i}\geq T \tv,\mb \forall i=1,\ldots, n$. The result follows from noting that $\tv$ is the unique fixed point of $\Gamma $ and that $\tv(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_{e_j})(i)$.
\end{proof}
\begin{lemma}\label{relation1}
 $\tv$, the unique fixed point of the iterative scheme \eqref{pvi}, and the solution $\tj$ to the ALP in \eqref{alp}, obey the relation $\tj\geq\tv\geq J^*$.
\end{lemma}
\begin{proof}
Since $\tv\geq T\tv$ it follows that $\tv\geq J^*$. Let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the ALP in \eqref{alp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{pvi} with $V_0(i)=\underset{j=1,\ldots, n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\tj(i)\geq\Phi r_i(i)\geq V_0(i),\mb \forall i=1,\ldots,n$. Also from the monotone property of $T$, we have 
\begin{align}\label{lineq}
\Phi r_i&\geq V_0,\nn\\
T\Phi r_i&\geq T V_0,\mbox{we also have}\nn\\
\Phi r_i\geq T\Phi r_i&\geq T V_0,\mb\text{by taking component-wise minimum},\nn\\
V_0&\geq T V_0.
\end{align}
From the first three inequalitites in \eqref{lineq}, $\Phi r_i\geq T \Phi r_i\geq T V_0, \mb\forall i=1\to n$ and hence $V_0\geq TV_0$. Since $V_1=\Gamma V_0$, from the definition of $\Gamma$ in \eqref{gamdef} we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb\forall n\geq 0$. So it follows that $\tj\geq V_0\geq V_1\ldots\geq \tv$.
\end{proof}
\begin{theorem}\label{fxpres}
Let $\tv$ be the fixed point of the iterative scheme in \eqref{pvi} and let $\bj$ be the best possible projection of $J^*$ as in Definition~\ref{bestproj}, then
\begin{align}
||J^*-\tv||_\infty\leq \frac{1}{1-\alpha}||J^*-\bj||_\infty.
\end{align}
\end{theorem}
\begin{proof}
Let $\epsilon=||J^*-\bj||_\infty$, and $\{V_n\},n\geq 0$ be the iterates of the scheme in \eqref{pvi} with $V_0=\bj$, then
\begin{align}
||J^*-\tv||_\infty&\leq ||J^*-V_0+V_0-V_1+V_1\ldots-\tv||_\infty\nn\\
&\leq ||J^*-V_0||_\infty+||V_0-V_1||_\infty+\ldots\nn
\end{align}
Since $||V_1-V_0||_\infty=||\Gamma \bj-\Gamma J^*||_\infty\leq\alpha||\bj-J^*||_\infty$, from Theorem~\ref{gmaxcontra},
\begin{align}
||J^*-\tv||_\infty&\leq \epsilon+\alpha\epsilon+\alpha^2\epsilon+\ldots\nn\\
&=\frac{\epsilon}{1-\alpha}.
\end{align}
\end{proof}

\section{Approximate Least Upper Bound Projection}\label{sec:alubp}
We define an approximate least upper bound (ALUB) projection operator which has a structure similar to the GRLP and is an approximation to the LUB operator.
\begin{definition}\label{alubpop}
Given $J\in \R^n$, its approximate least upper bound (ALUB) projection is denoted by $\hg J$ and is defined as 
\begin{align}\label{tgamdef}
(\hg J)(i)\stackrel{\Delta}{=}\underset{j=1,\ldots,k}{\min} (\Phi r_{e_j})(i), \mb \forall i=1,\ldots,n,
\end{align}
where $r_{e_j}$ is a solution to the linear program in \eqref{alubplp} for $c=e_j$, and $e_j$ is the same as in Definition~\ref{lubpop}.
\begin{align}\label{alubplp}
r_c\stackrel{\Delta}{=}\min_{r\in \chi} &c^\top \Phi r,\nn\\
\text{s.t}\mb &W^\top E \Phi r\geq W^\top HJ, W \in \R^{nd\times m}_+ .
\end{align}
\end{definition}
Note that $W$ in \eqref{alubplp} is the same matrix that is used in \eqref{grlp} and satisfies Assumption~\ref{wassump}.
\begin{lemma}\label{tgmonotone}
For $J_1, J_2\in \R^n$ such that $J_1\geq J_2$, we have $\hg J_1\geq \hg J_2$.
\end{lemma}
\begin{proof}
The proof follows from Assumptions~\ref{wassump} and ~\ref{one} using arguments along the lines of Lemma~\ref{gmonotone}.
\end{proof}
\begin{lemma}\label{tgshift}
Let $J_1\in \R^n$ and $t\in \R$ be a constant. If $J_2=J_1+t\one$, then $\hg J_2=\hg J_1+\alpha t\one$.
\end{lemma}
\begin{proof}
The proof follows from Assumption~\ref{wassump} and ~\ref{one}, as well as Lemma~\ref{lpsol} using arguments along the lines of Lemma~\ref{gshift}. In particular, consider the $i^{th}$ linear program corresponding to $\hg J_1$ and $\hg J_2$. Now, the result follows by letting $A=W^\top E \Phi$, $b=W^\top H J$, $c=e_i$, $b_0=\alpha t \mathbf{1}$, $x_0=\alpha t e_i$.
\end{proof}
\begin{theorem}\label{tgmaxcontra}
The operator $\hg \colon \R^n\ra \R^n$ obeys the $\max$-norm contraction property with factor $\alpha$ and the following iterative scheme based on the ALUB projection operator $\hg$, see \eqref{apvi}, converges to a unique fixed point $\hv$.
\begin{align}\label{apvi}
V_{n+1}&=\hg V_n,\mb\forall n\geq 0.
\end{align}
\end{theorem}
\begin{proof}
Follows along similar lines as the proof of Theorem~\ref{gmaxcontra}.
\end{proof}
\begin{lemma}\label{relation2}
The unique fixed point $\hv$ of the iteration in \eqref{apvi} and the solution $\hj$ of the GRLP obey $\hj\geq\hv$.
\end{lemma}
\begin{proof}
Follows in a similar manner as the proof of Lemma~\ref{relation1}. To elaborate, let $\Phi r_1, \Phi r_2,\ldots,\Phi r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$ respectively. Now consider the iterative scheme in \eqref{apvi} with $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$. It is clear from the definition of $V_0$ that $\hj(i)\geq\Phi r_i(i)\geq V_0(i), \mb \forall i=1,\ldots,n$. Also from the monotone property of $T$ we have 
\begin{align}
\Phi r_i&\geq V_0,\nn\\
H\Phi r_i&\geq H V_0,\mbox{we also have}\nn\\
E\Phi r_i\geq H\Phi r_i&\geq HV_0,\mb\text{by taking component-wise minimum},\nn\\
E V_0\geq H V_0.
\end{align}
Since $V_1=\hg V_0$, from the definition of $\hg$ in \eqref{gamdef} and the construction of $V_0$, we have $V_0\geq V_1$, and recursively $V_{n}\geq V_{n+1}, \mb\forall n\geq 0$. So it follows that $\hj\geq V_0\geq V_1\ldots\geq \hv$.
\end{proof}
\begin{theorem}\label{mt1}
Let $\hv$ be the fixed point of the iterative scheme in \eqref{apvi} and let $\bj$ be the best possible approximation of $J^*$ as in Definition~\ref{bestproj}, then
\begin{align}
||J^*-\hv||_\infty\leq \frac{||J^*-\bj||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{theorem}
\begin{proof}
Let $\epsilon=||J^*-\bj||_\infty$, and $\{V_n\},n\geq 0$ be the iterates of the scheme in \eqref{apvi} with $V_0=\hg J^*$, then
\begin{align}
||J^*-\hg J^*||_\infty&\leq||J^*-\Gamma J^*||_\infty+||\Gamma J^*-\hg J^*||_\infty\nn\\\vspace{10pt}
&= \epsilon+\beta,
\end{align}
where $\beta=||\Gamma J^*-\hg J^*||_\infty$. Now
\begin{align}
||J^*-\hv||_\infty&\leq ||J^*-V_0+V_0-V_1+V_1\ldots-\hv||_\infty\nn\\
&\leq ||J^*-V_0||_\infty+||V_0-V_1||_\infty+||V_1-V_2||_\infty+\ldots\nn\\
&=||J^*-V_0||_\infty+||\hg J^*-\hg V_0||_\infty+\ldots\nn\\\vspace{10pt}
&\leq (\epsilon+\beta)+\alpha(\epsilon+\beta)+\ldots\nn\\
&=\frac{\epsilon+\beta}{1-\alpha}.
\end{align}
\end{proof}

\begin{corollary}\label{cmt1}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_\infty$, then
\begin{align}
||J^*-\hv||_\infty\leq \frac{2||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{corollary}
\begin{proof}
The result is obtained by using Lemma~\ref{bestbnd} to replace the term $||J^*-\bj||_\infty$ in Theorem~\ref{mt1}.
\end{proof}

\section{A simple bound}
The following lemmas relate the fixed point $\hv$ of $\hg$ to the solution $\hj$ of the GRLP in \eqref{grlp}.
\begin{lemma}\label{srw}
$\hat{r} \in \R^k$ is a solution to GRLP in \eqref{grlp} iff it solves the following program:
\begin{align}\label{grlpeqprog}
\min_{r\in \chi} &||\Phi r-\hv||_{1,c}\nn\\
\text{s.t}\mb & W^\top \Phi r\geq W^\top T \Phi r.
\end{align}
\end{lemma}
\begin{proof}
We know from Lemma~\ref{relation2} that $\hj\geq\hv$, and thus minimizing $||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv$, is the same as minimizing $c^\top \Phi r$.
\end{proof}
\begin{theorem}\label{mt2}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_\infty$ be the error due to ALUB projection and let $r^*\stackrel{\Delta}{=}\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_\infty$, then
\begin{align}
||\hj-\hv||_{1,c}\leq\frac{4||J^*-\Phi r^*||_\infty+||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_\infty$, then  it is easy to see that
\begin{align}
||J^*-T\Phi r^*||_\infty&=||TJ^*-T\Phi r^*||_\infty\leq\alpha\gamma,\mb\text{and}\nn\\\vspace{10pt}
||T\Phi r^*-\Phi r^*||_\infty&\leq(1+\alpha)\gamma.
\end{align}
From Assumption~\ref{one} there exists $r'\in \R^k$ such that $\Phi r'=\Phi r^*+\frac{(1+\alpha)\gamma}{1-\alpha}\one$ and $r'$ is feasible to the ALP. Now
\begin{align}
||\Phi r'-J^*||_\infty&\leq ||\Phi r^* -J^*||_\infty+||\Phi r'-\Phi r^*||_\infty\nn\\&\leq \gamma+\frac{(1+\alpha)\gamma}{1-\alpha}=\frac{2\gamma}{1-\alpha}.
\end{align}
Since $r'$ is also feasible for GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\\vspace{10pt}
&\leq||\Phi r'-\hv||_\infty\mb\text{(Since $c$ is a distribution)}\nn\\
&\leq||\Phi r'-J^*||_\infty+||J^*-\hv||_\infty.\nn
\end{align}
The result follows from Corollary~\ref{cmt1}.
\end{proof}\\
\textbf{Prediction Error bound in the $L_\infty$-norm}\\
\begin{corollary}\label{cmt2}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2}, then
\begin{align}\label{finalbnd}
||J^*-\hj||_{1,c}\leq\frac{6 ||J^*-\Phi r^*||_\infty+2||\Gamma J^*-\hg J^*||_\infty}{1-\alpha}.
\end{align}
\end{corollary}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\\vspace{10pt}
&\leq||J^*-\hv||_\infty+||\hv-\hj||_{1,c}\nn
\end{align}
The result now follows from Corollary~\ref{cmt1} and Theorem~\ref{mt2}.
\end{proof}
The results presented in Corollary~\ref{cmt2} is in the $L_\infty$-norm. In the next section, we use of Lyapunov functions to provide an improved bound in a modified $L_\infty$-norm.

\section{Improved Bounds}\label{sec:improv}
In this section, we present improved error bounds by making use of Lyapunov functions. 
\begin{lemma}\label{bestbndmn}
Let $r^*\in \R^k$ be defined as $r^*\stackrel{\Delta}{=}\arg\min_{r\in R^k}||J^*-\Phi r||_{\infty,1/\psi}$, then 
\begin{align}
||J^*-\bj||_{\infty,1/\psi}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}.
\end{align}
\end{lemma}
\begin{proof}
The result follows from the definition of $\Gamma$ in \eqref{gamdef}, Assumption~\ref{lyap} and the fact that $\Phi r^*+||J^*-\Phi r^*||_{\infty,1/\psi} \psi\geq TJ^*$.
\end{proof}

Since most of our analysis in sections~\ref{sec:lubp} and ~\ref{sec:alubp} depended on showing that $\Gamma$ is a contraction map in the $L_\infty$ norm we first show that $\Gamma$ is also a contraction map in the modified $L_\infty$ norm.
\begin{lemma}\label{gshiftmn}
Let $J_1\in \R^n$ and $k\in \R$ be a constant. If $J_2=J_1+k\psi$, then $\Gamma J_2\leq \Gamma J_1+\beta_{\psi} k\psi$.
\end{lemma}
\begin{proof}
The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
\end{proof}
\begin{theorem}\label{gmaxcontramn}
The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in modified $L_\infty$ with factor $\beta_{\psi}$.
\end{theorem}
\begin{proof}
Given $J_1,J_2\in \R^n$ let $\epsilon=||J_1-J_2||_{\infty,1/\psi}$. Thus
\begin{align}\label{ineq}
J_2-\epsilon\psi\leq J_1\leq J_2+\epsilon \psi.
\end{align}
From Lemmas~\ref{gmonotone} and ~\ref{gshiftmn}, we can write
\begin{align}\label{ineq}
\Gamma J_2-\beta_{\psi} \epsilon\psi\leq \Gamma J_1\leq \Gamma J_2+\beta_{\psi} \epsilon\psi.
\end{align}
Thus
\begin{align}
||\Gamma J_1-\Gamma J_2||_{\infty,1/\psi}\leq \beta_{\psi} ||J_1-J_2||_{\infty,1/\psi}.
\end{align}
\end{proof}
\begin{corollary}\label{hgmaxcontramn}
$\hg$ is also a contraction map in the modified $L_\infty$ norm.
\end{corollary}
\begin{proof}
Follows from arguments similar to Theorem~\ref{gmaxcontramn}.
\end{proof}
\begin{lemma}\label{cmt1mn}
Let $\hv$, $\bj$ be as in Theorem~\ref{mt1} and let $r^*\stackrel{\Delta}{=}\arg\min_{r\in \R^k}||J^*-\Phi r||_{\infty,1/\psi}$ then
\begin{align}
||J^*-\hv||_{\infty,1/\psi}\leq \frac{2||J^*-\Phi r^*||_{\infty,1/\psi}+||\Gamma J^*-\hg J^*||_{\infty,1/\psi}}{1-\beta_{\psi}}.
\end{align}
\end{lemma}
\begin{proof}
The proof follows from Lemma~\ref{gmaxcontramn}, Corollary~\ref{hgmaxcontramn} and by replacing the $||\cdot||_\infty$ norm by $||\cdot||_{\infty,1/\psi}$ in the arguments presented in sections~\ref{sec:lubp} and ~\ref{sec:alubp} leading to Corollary~\ref{cmt1}.
\end{proof}\\
We now recall Lemma~$4.3$ of \cite{ALP}.
\begin{lemma}\label{restate}
Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ , $r \in \R^k$ be an arbitrary vector and let $r'$ be such that
\begin{align}
\Phi r'=\Phi r+||J^*-\Phi r||_{\mn}(\frac{1+\beta_{\psi}}{1-\beta_{\psi}})\psi.
\end{align}
Then $r'$ is feasible for the ALP in \eqref{alp}.
\end{lemma}
\begin{theorem}\label{mt2mn}
Let $\hv$ be the solution to the iterative scheme in \eqref{apvi} and let $\hj=\Phi \hr$ be the solution to the GRLP. Let $\bj$ be the best possible approximation to $J^*$ as in Definition~\ref{bestproj}, and $||\Gamma J^* -\hg J^*||_{\infty,1/\psi}$ be the error due to ALUB projection and let $r^*\stackrel{\Delta}{=}\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\infty,1/\psi}$, then
\begin{align}
||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}
%\nn\\&
+||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
Let $\gamma=||J^*-\Phi r^*||_{\infty,1/\psi}$, then by choosing $r'$ as in Lemma~\ref{restate} we have
\begin{align}
||\Phi r'-J^*||_{\mn}&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
&=\frac{2}{1-\beta_\psi}\gamma.\nn
\end{align}
Since $r'$ is also feasible for the GRLP in \eqref{grlp} we have
\begin{align}
||\hj-\hv||_{1,c}&\leq||\Phi r'-\hv||_{1,c}\nn\\
&=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
&\leq c^\top \psi ||\Phi r'-\hv||_{\infty,1/\psi}\nn\\
&\leq c^\top \psi (||\Phi r'-J^*||_{\infty,1/\psi}+||J^*-\hv||_{\infty,1/\psi}).
\end{align}
The result follows from Corollary~\ref{cmt1}.\\
\textbf{Main Result~$1$: Prediction Error bound in modified $L_\infty$-norm}
\end{proof}
\begin{theorem}\label{cmt2mn}
Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{finalbndmn}
||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}
||J^*-\hj||_{1,c}&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
\end{align}
The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
\end{proof}\\

\textbf{Main Result $2$: Control Error bound in modified $L_\infty$-norm}\\
We now bound the performance of the greedy policy $\hu$.
\begin{theorem}\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function. Let $r^*$ be as in Theorem~\ref{mt2mn}, then
\begin{align}\label{polthebnd}
||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(6 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||\Gamma J^*-\hg J^*||_{\mn}\big).
\end{align}
\end{theorem}
\begin{proof}
\begin{align}\label{polderv}
||J_{\hu}-\hj||_{1,c}&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
&\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
&\leq c^\top (I-\alpha P_{\hu})^{-1} \psi ||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})||J^*- \hj||_{\mn},
\end{align}
where in the second inequality, for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. Now
\begin{align}
||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
&\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
&=\frac{2c^\top \psi}{1-\beta_{\psi}}||J^*- \hj||_{\mn}.
\end{align}
The result now follows by substituting the value of $||J^*- \hj||_{\mn}$ from Corollary~\ref{cmt2mn}.
\end{proof}
\begin{note}
By letting $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\infty,1/\psi}+||J^*-\hg J^*||_{\mn}$ (inequality follows from Lemma~\ref{bestbndmn}), we can also modifiy the bounds in \eqref{finalbnd} and \eqref{polthe} as
\begin{align}
\label{loose1}||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||J^*-\hg J^*||_{\mn}).\\
\label{loose2}||J_{\hu}-\hj||_{1,c}&\leq 2\big(\frac{c^\top \psi}{1-\beta_{\psi}}\big)^2 \big(10 ||J^*-\Phi r^*||_{\mn}
%\nn\\&
+2||J^*-\hg J^*||_{\mn}\big).
\end{align}
Here the term $||J^*-\hg J^*||$ in \eqref{loose1} and \eqref{loose2} captures the error due to the use of both $\Phi$ and $W$. Though, \eqref{loose1} and \eqref{loose2} might be loser bounds than \eqref{finalbndmn} and \eqref{polthebnd} respectively, the aim here is to capture the error due to function approximation as well as constraint reduction in a single term.
\end{note}

\section{Discussion}
In this section we discuss the implications and insights provided by the results presented in Theorems~\ref{cmt2mn} and ~\ref{polthe}.
\subsection{On Error Terms}
\begin{itemize}
\item The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
\begin{enumerate}
\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$,
\item $||\Gamma J^*-\hg J^*||_{\mn}$.
\end{enumerate}
The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\\
The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy. It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.
\item Unlike the result in \cite{CS} which holds only for a specific RLP formulated under ideal assumptions, our bounds hold for any GRLP and as a result for any given RLP. Another interesting feature of our result is that it holds with probability $1$. 
\item A salient feature of the ALP formulation is the use of Lyapunov functions to control/shape the error across the states based on their relative importance. Since the error bounds are in a modified $L_\infty$-norm, the GRLP framework retains this salient feature of the ALP.
\end{itemize}
The fact that both the prediction and control problems can be addressed by the GRLP makes it a complete ADP method, and by addressing the constraint approximation, the GRLP framework is an important addition to the theory of ALP.
\subsection{On Constraint Reduction and Approximation}
We claim the following based on the error bounds that we derived for the GRLP.\\
{Claim $1$)} It is not always necessary to sample constraints according to the stationary distribution of the optimal policy.\\
{Claim $2$)} Constraint approximation is not only restricted to constraint sampling but also can be extended to include linear approximation of the constraints.\\
The following result (Theorem~\ref{st}) supports Claim~$1$ in the above.\\
\textbf{Main Result~$3$: On Constraint Sampling}\\
The error term $\etmn$ gives new insights into constraint sampling. 
\begin{theorem}\label{st}
Let $s\in S$ be a state whose constraint was sampled. Then
\begin{align}\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align}
\end{theorem}
\begin{proof}
Let $r_{e_s}$ and $\hat{r}_{e_s}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$. It is easy to note that $r_{e_s}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s})(s)\geq (\Phi \hat{r}_{e_s})(s)$. However, since all the constraints with respect to state $s$ have been sampled we know that $(\Phi \hat{r}_{e_s})(s)\geq J^*$. The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s})(s)$ and $\hg J^*(s)=(\Phi \hat{r}_{e_s})(s)$.
\end{proof}\\
The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well. The modified $L_\infty$ norm in \eqref{finalbnd} comes to our rescue to control the error due to those states that are not sampled. Thus the sampling distribution need not be the stationary distribution of the optimal policy as long as it samples the \emph{important} states, an observation that might theoretically explain the empirical successes of the RLP \cite{ALP,CST,SALP}.\\
To understand the implication of Claim~$2$ we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
\begin{align}\label{lag}
\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
\end{align}
The insight that the GRLP is a linear function approximation of the constraints (i.e., the Lagrangian multipliers) can be obtained by noting that $ Wq\approx \lambda$ in \eqref{lag2}. Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$). Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under the optimal policy $u^*$, i.e., 
\begin{align}
\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
			\lambda^*(s,a)&=0, \forall a \neq u^*(s),\nn
\end{align}
where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy. Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.\\
\subsection{Numerical Illustration}
We take up an example in the domain of controlled queues from \cite{ALP} for which the ALP has been known to work well. For this domain, we make use of our results and observations to select various useful $W$ matrices and present their performance.\\
The queuing system consists of $n=10^4$ states and $d=4$ actions. We chose $n=10^4$ because it was possible to solve both the GRLP and the exact LP (the latter with significant effort) so as to enumerate the approximation errors. We hasten to mention that while we could run the GRLP for queuing systems with $n>10^4$ without much computational overhead, solving the exact LP was not possible for $n>10^4$ as a result of which the approximation error could not be computed.\\
\textbf{Queuing Model:}
The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}. We consider a single queue with arrivals and departures. The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue. The action set $A=\{1,\ldots,d\}$ is related to the service rates. We let $s_t$ denote the state at time $t$. The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$. For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by 	$s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$.
The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue. The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$.\\
\textbf{Choice of $\Phi:$} We make use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}. This takes care of the term $||J^*-\Phi r^*||_\infty$ in \eqref{finalbnd}. \\
\textbf{Selection of $W$:} For our experiments, we choose two contenders for the $W$-matrix and compare them with the ideal sampling matrix $W_i$ (\cite{CS}) and random positive matrix $W_r$. Our choices of the $W$ matrix are as below.\\
{$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$. This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states.\\
{$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$. Our choice of the $W_a$ matrix to correspond to aggregation of near by states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
The aggregation matrix $W_a$ is defined as below: $\forall i=1,\ldots,m$,
\begin{align}\label{wdes}
W_a(i,j)&=1, \mb\forall j\mb\text{s.t}\mb j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
&=0,\mb\text{otherwise}.
\end{align}
We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$. We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$. We set $c(s)=(1-\zeta) \zeta^s, \mb\forall s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively. The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$. Also note that a better performance of $W_a$ and $W_c$ in the larger system $Q_L$ tallies with a lower value of $\et$ in the smaller system $Q_S$.
\FloatBarrier
\begin{table}[H]
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|c|}\hline
Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
$||J^*-\hj||_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
$||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
\end{tabular}
%}
\caption{Shows values of Error Terms for $Q_L$.}
\label{pref}
\end{table}

\FloatBarrier
\begin{table}[H]
%\resizebox{\columnwidth}{!}{
\begin{tabular}{|c|c|c|c|}\hline
Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
\end{tabular}
%}
\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
$.}
\label{pref}
\end{table}
Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
\subsection{Reinforcement Learning}
Reinforcement Learning (RL) algorithms are useful in scenarios where the system is available in the form of a simulator or only samples can be obtained via direct interaction. In particular, in the RL setting, the model parameters $g$ and $P$ are not known explicitly and the underlying MDP needs to be solved by using sample trajectories. In short, RL algorithms are sample trajectory based solution schemes for solving MDPs whose model information is not known. RL methods learn by filtering out the noisy sample via stochastic approximation and they also employ function approximation in order to handle MDPs with large number of states. Most RL algorithms are sample trajectory based extensions of ADP methods.\\
The RL extension of the ALP formulation has been applied to the optimal stopping problem in \cite{ALP-Bor}. Function approximation is employed to approximate the square root of the Lagrange multipliers. However, since the approximation is not linear, convergence of the resulting RL algorithm cannot be guaranteed. Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.

\section{Conclusion}
The approximate linear programming (ALP) is an approximate dynamic programming method that addresses the prediction and control problems successfully. However, an important shortcoming of the ALP is that it has large number of constraints, which is tackled in practice by sampling a tractable number of constraints from the ALP to formulate and solve a reduced linear program (RLP). Though RLP has been found to work well empirically in various domains ranging from queues to Tetris games, performance guarantees are available only in the case of a specific RLP formulated under idealized assumptions. Thus there has been a gap in the theory of constraint reduction.\\
In this paper, we introduced a novel framework based on the generalized reduced linear program formulation to study constraint reduction. The constraints of the GRLP were obtained as positive linear combinations of the original ALP. We provided an error bound that relates the optimal value function to the solution of the GRLP. Our error bound contained two terms, one inherent to the ALP formulation and the other due to constraint reduction. We also made qualitative and quantitative observations about the nature of the error term that arose due to constraint reduction. Our analysis also revealed the fact that it is not always necessary to sample according to the stationary distribution of the optimal policy and, in fact, potentially several different constraint sampling/approximation strategies might work. In particular, we also theoretically justified linear function approximation of the constraints. We also discussed the results and provided a numerical example in the domain of controlled queues. To conclude, we observe that by providing a novel theoretical framework to study constraint approximation, this paper provides important results that add to the theory of ALP.

\bibliographystyle{plain}
\bibliography{ref.bib}
\newpage
\onecolumn
\end{document}

### 2016-07-08 abstract.tex
some reordering and copyediting

@@
+\begin{comment}
 \begin{abstract}
@@
 \end{abstract}
+\end{comment}
+\begin{comment}
+\begin{abstract}
+The approximate linear programming (ALP) method and its variants have been widely applied to various Markov Decision Processes (MDPs) with large number of states.
+An attractive feature of the ALP is that it has fewer number of variables compared to the number of states of the MDP and it offers sound theoretical guarantees.
+Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead.
+Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.
+\end{abstract}
+\end{comment}
+%\begin{comment}
+\begin{abstract}
+The approximate linear program (ALP) and its variants have been widely applied to Markov Decision Processes (MDPs) with large number of states.
+A serious limitation of the ALP is that it has intractable number of constraints, as a result of which constraint approximation is of interest.
+In this paper, we define a generalized reduced linear program (GRLP) that has a tractable number of constraints obtained as positive linear combinations of the original constraints of the ALP.
+The main contribution of this paper is a novel theoretical framework developed to obtain error bounds for any given GRLP.
+By providing a detailed error analysis for the GRLP, we justify linear approximation of the dual variables.
+Unlike prior results on constraint sampling which hold only with high probability, our analysis holds with probability one and is based on a novel contraction operator.
+%We discuss the implication of our results in the contexts of ADP and reinforcement learning.
+\end{abstract}
+%\end{comment}
 \begin{keywords}{

### 2016-07-08 grlp.tex
some reordering and copyediting

@@
 \section{Generalized Reduced Linear Program}
+The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$.
+By substitution, this leads to
+\begin{align}\label{alp}
+\begin{split}
+\min_{r\in \R^k}\, &c^\top \Phi r\\
+\text{s.t.}\mb &\Phi r\geq T \Phi r,
+\end{split}
+\end{align}
+where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}.
+Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
+The Generalized Reduced Linear Program is given as:
+\begin{align}\label{grlp}
+\begin{split}
+\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
+\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
+\end{split}
+\end{align}
+where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution.
+In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.
+
+For brevity, we introduce our assumptions, whose meaning will be explained later.
 \begin{assumption}\label{grlpassmp}
@@
 \end{assumption}
-When \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$, $t>0$, $s\in S$,
+We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$ and $t>0$,
 \begin{align}
 \label{eq:psilin}
-T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,\, \quad (J\in \R^n,\, t>0)\,.
+T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,. %\,\, \quad (J\in \R^n,\, t>0)\,.
 \end{align}
-The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$.
-By substitution, this leads to
-\begin{align}\label{alp}
-\begin{split}
-\min_{r\in \R^k}\, &c^\top \Phi r\\
-\text{s.t.}\mb &\Phi r\geq T \Phi r,
-\end{split}
+
+The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation. 
+To understand this, we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
+\begin{align}\label{lag}
+\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
 \end{align}
-where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}.
-Unless specified otherwise we use $\tr$ to denote any solution to the ALP, $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
-The Generalized Reduced Linear Program is given as:
-\begin{align}\label{grlp}
-\begin{split}
-\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
-\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
-\end{split}
+Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers.
+Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
+Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
+One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e.,
+\begin{align}
+\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
+				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
+			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
 \end{align}
-where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional constraint set to ensure the boundedness of the solution.
-In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.
+where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$).
+Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.

### 2016-07-08 intro.tex
some reordering and copyediting

@@
+%!TEX root =  autocontgrlp.tex
 \section{Introduction}
-Markov decision processes (MDPs) is an important mathematical framework to study optimal sequential decision making problems that arise in science and engineering.
-Solving an MDP involves computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states.
-MDPs with small number of states can be solved easily by conventional solution methods such as value / policy iteration or linear programming (LP) \cite{BertB}.
-Dynamic programming is at the heart of all the conventional solution methods for MDPs.\par
+Markov decision processes (MDPs) is a powerful mathematical framework to study optimal sequential decision making problems that arise in science and engineering.
+The so-called dynamic programming methods find an optimal policy by computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states.
+MDPs with small number of states can be solved easily by conventional solution methods such as value-, or policy-iteration, or linear programming (LP) \cite{BertB}.
+
 A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$.
-Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$.
-The most widely used method for approximation is the linear function approximation (LFA), i.e., let $\tilde{J}=\Phi r^*$, where $\Phi$ is a feature matrix and $r^*$ is a learnt weight vector.
-Dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states and this makes computing $\tilde{J}$ easier.\par
+Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm.
+The most widely used method for approximation is the linear function approximation (LFA), i.e., let $\tilde{J}=\Phi r^*$, where $\Phi$ is a feature matrix and $r^*$ is a weight vector to be computed.
+Dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, making it possible to work with large MDPs where even storing one value per state would be impossible in the computer's main memory.
+
 The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation.
 A critical shortcoming of the ALP is that the number of constraints are of the order of the size of the state space, making the vanilla version of the ALP intractable.
-A way out is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP).
+A way out is to employ choose a subset of constraints random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP).
 The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}.
-An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach useful in practice, however, without any theoretical guarantees bounding the loss in performance resulting from such an approximation.\par
+An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was empirically found to be useful.
+However, to this date, there exist no theoretical guarantees bounding the loss in performance resulting from such an approximation.
+
 In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints obtained as positive linear combinations of the original constraints of the ALP.
@@
 \begin{enumerate}
-		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction erorr $||J^*-\hj||$ (\Cref{cmt2mn}). 
-		\item We also bound the performance loss due to the one-step greedy policy $\hu$ (greedy with respect to $\hj$) given by $||J^*-J_{\hu}||$ (Theorem~\ref{polthe}).
-		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{with probability one}.
-This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
-		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints.
-		\item We demonstrate via an example in controlled queues that the experiments conform to the theory developed.
+		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}). 
+		\item We also bound the performance loss due to using the one-step greedy policy $\hu$ (greedy with respect to $\hj$) as a function of $||J^*-J_{\hu}||$ (Theorem~\ref{polthe}).
+		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
+		\item Our results on the GRLP are the first to theoretically justify linear function approximation of Langrangian (dual) variables underlying the constraints.
+		\item A numerical example in controlled queues is provided to illustrate the theory.
 \end{enumerate}

### 2016-07-08 mdp.tex
some reordering and copyediting

@@
 \section{Markov Decision Processes (MDPs)}
-We consider MDPs with large but finite number of states.
-Thus $S=\{1,2,\ldots,n\}$ for some large $n$ is the state space, and the action set is given by $A=\{1,2,\ldots,d\}$.
+We consider MDPs with a finite state space $S=\{1,2,\ldots,n\}$ and finite action space $A=\{1,2,\ldots,d\}$, where the sentiment is that $n$ is large.
 For simplicity, we assume that all actions are feasible in all states.
-The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$.
-We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\par
-A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.}(SDP) or simply a policy is a map $u\colon S\ra A$ which specifies the action selection mechanism.
-Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
+The probability transition kernel $P$ collects the probabilities $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$ for all possible $s,s'\in S$ and $a\in A$.
+We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
+
+A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP) or simply a policy is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
+Given an SDP $u$, the expected total discounted reward corresponding to starting at state $s$ and then choosing actions as dictated by $u$ for the states encountered is denoted by $J_u(s)$ and is defined by
 \begin{align}
@@
 \end{align}
-where $\alpha \in (0,1)$ is a given discount factor.
-Here $J_u(s)$ is known as the value of the state $s$ under SDP $u$, and the vector quantity $J_u\eqdef(J_u(s), \forall s\in S)\in R^n$ is called the value function corresponding to the SDP $u$.
-The \emph{optimal policy} $u^*$ is obtained as $u^*(s)\eqdef\arg\max_{u\in U}J_u(s)$\footnote{An optimal (SDP) $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{BertB}.}, where $U$ is the class of all SDPs.
-The \emph{optimal value function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.\par
+where $\alpha \in (0,1)$ is the so-called discount factor and $s_{n+1} \sim p_{a_n}(s_n,\cdot)$, $n\ge 0$. 
+Here $J_u(s)$ is known as the value of the state $s$ under SDP $u$, and $J_u$ (as a map from $S$ to the reals)
+is known as the value function corresponding to the SDP $u$.
+The \emph{optimal policy} $u^*$ is one that in each state $s\in S$ achieves the best possible total expected discounted reward from that state.
+That is, $J^{u^*})(s) = J^*(s) \eqdef \max_{u\in U} J_u(s)$.\footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.}, where $U$ is the set of all SDPs and $J^*$ is coined the \emph{optimal value function}.
+
 Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
@@
 \end{subequations}
-Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.\par
-For convenience, in what follows we allow any vector $J\in \R^n$ to be viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
-We now define some operators acting on $\R^n$ (equivalently on $\R^S$) that will be useful later.
+Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.
+
+For convenience, in what follows we identify elements of $\R^n$ with $\R^S$ in the natural way.
+In particular, we can thus treat $J_u$ and $J^*$ as vectors in $\R^n$.
+Similarly we identify $\R^{nd}$ with $\R^{S\times A}$.
+We now give some definitions that will be useful later.
 %The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
@@
 \item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
-\item The greedy policy with respect to the value function $\tj$ as \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
+\item A policy $\tu$ is said to be greedy with respect to some function $\tj:S \to \R$ if \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
 \end{enumerate}
@@
 \end{corollary}
-Though in \cref{monotone,shift,maxnorm}, we make use of the Bellman operator $T$, the results also hold for $H$ as well.
-\subsection{Linear Programming Formulation}
-The optimal value function $J^*$ can be obtained by solving the following linear program:
+Though  \cref{monotone,shift,maxnorm} are stated for the Bellman operator $T$, the results also hold for $H$ as well.
+
+\subsection{The Linear Programming Formulation}
+As it is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
 \begin{align}\label{mdplp}
@@
 \end{align}
-where $c$ is a probability distribution such that $c(s)>0, \forall s \in S$ and $\sum_{s\in S}c(s)=1$.\par
+where $c$ is \emph{any} function such that $c(s)>0, \forall s \in S$.
+Without loss of generality, we may and will assume in what follows that $\sum_{s\in S}c(s)=1$, i.e., $c$ is a probability distribution over $S$.
+
 When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}.

### 2016-07-08 resdisc.tex
some reordering and copyediting

@@
 This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
-The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.\par
-The GRLP has linear function approximation in both the primal and dual variables of the LP formulation.
-To understand this, we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e.,
-\begin{align}\label{lag}
-\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
-\end{align}
-Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approxmation of the Lagrange multipliers.
-Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
-Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
-One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under the optimal policy $u^*$, i.e.,
-\begin{align}
-\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
-				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
-			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
-\end{align}
-where $P_{u^*}$ is the probability transition matrix with respect to the optimal policy.
-Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.
+The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.

### 2016-07-08 errana.tex
First cut

@@
 \section{Error Analysis}\label{sec:errana}
-We now define the two projection operators which are central to our error analysis. The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
+We now define two projection operators which are central to our error analysis:
+%The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
 \begin{definition}\label{lubpop}
@@
 Then, for $J\in \R^n$, $\Gamma J$,
-the least upper bound projection of $J$ is defined as 
+the \emph{ least upper bound projection} of $J$ is defined as 
 \begin{align}\label{gamdef}
@@
 where $J\in \R^n$. 
-Thus $\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$.
-Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
+Disregarding the constraint $r\in \N$, 
+$\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
 \end{remark}
-The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
+%The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
+The definition of the second operator is as follows:
 \begin{definition}\label{alubpop}
@@
 \end{align}
-Further, define $\hg J$  as 
+Then, the \emph{approximate least upper bound (ALUB) projection operator}
+$\hg \colon \R^n \ra \R^n$ is defined as 
 \begin{align}\label{tgamdef}
-(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,.
+(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,, J\in \R^n\,.
 \end{align}
@@
 \end{proof}
-In what follows we denote by $\hv$ the unique fixed point of $\hg$ i.e., $\hv = \hg \hv\,$. 
+In what follows we denote by $\hv$ the unique fixed point of $\hg$, i.e., $\hv = \hg \hv\,$. 
 We now show that the vector $\hj$ dominates the vector $\hv$:
@@
 \begin{proof}
-Let $ r_1,  r_2,\ldots, r_n$ be solutions to the GRLP in \eqref{grlp} for $c=e_1, e_2,\ldots,e_n$, respectively,
+For $i\in \{1,\dots,n\}$, $c=e_i$ let $r_i$ be a solution to the GRLP in \eqref{grlp}
 and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.
@@
 \begin{proof}
-We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$, and the rest of the arguments follow in the same manner as proof for \cref{srw}.
+We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$.
+The rest of the argument follows in the same manner as the proof for \cref{srw}.
 \end{proof}
@@
 \begin{align}
-||J^*-\hv||_{\mn}&\leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}&\nn\\+||\Gamma J^*-\hg J^*||_{\mn}\big).
+||J^*-\hv||_{\mn}
+& \leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}
+\nn\\
+& {}\qquad \qquad+||\Gamma J^*-\hg J^*||_{\mn}\big).
 \end{align}
@@
 \begin{align*}
-&||J^*-\hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+||\hg J^*-\hg \hv||_\mn\\&\leq ||J^*-\hg J^*||_\mn+\beta_\psi || J^*- \hv||_\mn,
+||J^*-\hv||_{\mn}
+& \leq ||J^*-\hg J^*||_{\mn}+||\hg J^*-\hg \hv||_{\mn}\\
+&\leq ||J^*-\hg J^*||_{\mn}+\beta_\psi || J^*- \hv||_{\mn},
 \end{align*}
@@
 \begin{align}\label{jhv}
-&\norm{J^*-\hv}_{\mn} \nn\\&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\nn\\
+\norm{J^*-\hv}_{\mn} \nn
+&\le \frac{\norm{ J^*-\hg J^*}_{\mn}}{1-\beta_\psi}\nn\\
 &\le \frac{\norm{ J^*-\Gamma J^*}_{\mn}+\norm{\Gamma J^* - \hg J^*}_{\mn}}{1-\beta_\psi}\,.
@@
 We now recall Lemma~$5$ from Section 4.2 of \cite{ALP}. 
-For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$ by assumption.
+For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$.
 \begin{lemma}\label{restate}
 %Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ ,
-For  $r \in \R^k$ arbitrary vector, let $r'$ be
+For  $r \in \R^k$ arbitrary, let $r'$ be
 \begin{align}
@@
 \begin{align}
-||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn\\
-&+||\Gamma J^*-\hg J^*||_{\mn}).
+||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn
++||\Gamma J^*-\hg J^*||_{\mn}).
 \end{align}
@@
 Then, by choosing $r'$ as in Lemma~\ref{restate} we have
-\begin{align}\label{part}
-&||\Phi r'-J^*||_{\mn}\nn\\&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
-&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma\nn\\
-&=\frac{2}{1-\beta_\psi}\gamma.
+\begin{align}
+||\Phi r'-J^*||_{\mn}\nn
+&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
+&=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma
+	=\frac{2}{1-\beta_\psi}\gamma.
+\label{part}
 \end{align}
 %We know that $\tr \in \N$ by \cref{grlpassmp}-\eqref{nassmp} and 
-$r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. Then from \cref{srwalp} it follows that
+Now, $r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. 
+Then from \cref{srwalp} it follows that
 %As a result, from \cref{srw} it follows that
 \begin{align}
-&||\hj-\hv||_{1,c}\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\
+||\hj-\hv||_{1,c}
+&\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\
 &=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
 &\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
-&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).
+&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).\nn
 \end{align}
@@
 \begin{align}\label{finalbndmn}
-||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\nn\\
+\begin{split}
+||J^*-\hj||_{1,c}
+&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\\
 &+2||\Gamma J^*-\hg J^*||_{\mn}).
+\end{split}
 \end{align}
@@
 \begin{align}
-&||J^*-\hj||_{1,c}\nn\\
+||J^*-\hj||_{1,c}\nn
 &\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
@@
 \begin{align}\label{polderv}
-&||J_{\hu}-\hj||_{1,c}\nn\\&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
+||J_{\hu}-\hj||_{1,c}\nn
+&=||(I-\alpha P_{\hu})^{-1}(T\hj-\hj)||_{1,c}\nn\\
 &\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
-&\leq c^\top (I-\alpha P_{\hu})^{-1} \psi ||T\hj-\hj||_{\mn}\nn\\
+&\leq c^\top (I-\alpha P_{\hu})^{-1} \,\psi\, ||T\hj-\hj||_{\mn}\nn\\
 &\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\

### 2016-07-08 grlp.tex
First cut

@@
 \section{Generalized Reduced Linear Program}
-The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$.
+The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by ntroducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$.
 By substitution, this leads to
@@
 where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution.
+\todoc{So what is our advice on how to select $\N$?}
 In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.

### 2016-07-08 num.tex
First cut

@@
+%!TEX root =  autocontgrlp.tex
 \section{Numerical Illustration}
-In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $\et$ indicates the quality of the constraint approximation.
+In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $\et$ indicates \todoc{right word?}
+ the quality of the constraint approximation.
 The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}.

### 2016-07-08 resdisc.tex
First cut

@@
 \section{Discussion}
-The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors namely
+The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors, namely
 \begin{enumerate}
-\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$,
+\item $\min_{r\in \R^k} ||J^*-\Phi r||_{\mn}$, and
 \item $||\Gamma J^*-\hg J^*||_{\mn}$.
@@
 The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators.
-As a consequence, our result holds with probability $1$, unlike prior results on constraint sampling \cite{CS} that hold only with high probability.
-The error term $\etmn$ gives new insights into constraint selection.
+It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators and is completely deterministic, unlike prior results on constraint sampling \cite{CS} which are probabilistic.The error term $\etmn$ gives new insights into constraint selection:
 \begin{theorem}\label{st}
-Let $s\in S$ be a state whose constraint was selected. Then
+Let $s\in S$ be a state whose constraint is selected in $W$. \todoc{Try to rephrase this..}
+Then
 \begin{align}\label{sampexp}
@@
 \end{proof}
-The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
+The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling \todoc{??} is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
 This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
 The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.
+\todoc{??}

### 2016-07-16 appendix.tex
describing N and fixing a bug

\begin{appendix}
\textbf{On choice of $\N$:}\\
Let $g_{\min}=\underset{a,s}{\min}g_a(s)$, $g_{\max}=\underset{a,s}{\max}g_a(s)$ and define $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\mn}$. Now $\frac{g_{\min}}{1-\alpha}\leq J^* \leq \frac{g_{\max}}{1-\alpha}$ and since $\mathbf{1}$ is in the basis, we have $||J^*-\Phi r^*||_{\mn}\leq \frac{g_{\max}-g_{\min}}{1-\alpha}$ (making use of the fact that for any sensible choice of Lyapunov function $||J^*-\Phi r^*||_{\mn}\leq ||J^*-\Phi r^*||_{\infty}$). Further, in our arguments, we have made the implicit assumption that $r'= r^*+||J^*-\Phi r^*||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0 \in \N$. This implicit assumption will continue to hold when $\N\eqdef\{\r| a\leq \Phi r\leq b\}$, where $a=\frac{g_{\min}}{1-\alpha}$ and $b=\frac{g_{\max}}{1-\alpha}+\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\frac{g_{\max}-g_{\min}}{1-\alpha}$.
\end{appendix}

### 2016-07-16 errana.tex
describing N and fixing a bug

@@
 \norm{J^* - J_{\hu}}_{1,c}
-&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2\, \big(6 ||J^*-\Phi r^*||_{\mn}
+&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\mn}
 \nn\\&
-+2||\Gamma J^*-\hg J^*||_{\mn}\big).
++||\Gamma J^*-\hg J^*||_{\mn}+||\hj-\hg\hj||_{\mn}\big).
 \end{align}
@@
 \end{align}
-The result now follows by substituting the bound on $||J^*- \hj||_{\mn}$ from \cref{cmt2mn}.
+Now in a manner similar to \cref{cmt2mn} we have
+\begin{align}
+||J^*- \hj||_{\mn}&\leq ||J^*- \hv||_{\mn}+||\hv -\hj||_{\mn}\nn
+\end{align}
+The result now follows by substituting the bound on $||J^*- \hv||_{\mn}$ from \cref{cmt1mn} and the fact that $||\hv-\hj||_{\mn}\leq \frac{1}{1-\beta_{\psi}}||\hj-\hg\hj||$.
 \end{proof}

### 2016-07-22 grlp.tex
changes up to discussion

--- 2016-07-08 grlp.tex
@@
 \section{Generalized Reduced Linear Program}
-The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$.
+The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
 By substitution, this leads to
@@
 \begin{split}
-\min_{r\in \R^k}\, &c^\top \Phi r\\
-\text{s.t.}\mb &\Phi r\geq T \Phi r,
+\min_{r\in \R^k}\, &c^\top \Phi r\,\,\,
+\text{s.t.}\mb \Phi r\geq T \Phi r,
 \end{split}
@@
 where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}.
-Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
+Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy w.r.t.
+$\tj$.
 The Generalized Reduced Linear Program is given as:
@@
 \begin{split}
-\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
-\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
+\underset{r\in \N}{\min}\, &\, c^\top \Phi r\,\,\,\,
+\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
 \end{split}
 \end{align}
-where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution.
-In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.
+where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution.%
+\footnote{The appendix explains how $\N$ can be chosen.}
+In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.
 
-For brevity, we introduce our assumptions, whose meaning will be explained later.
+We assume that the following hold in the rest of the paper:
 \begin{assumption}\label{grlpassmp}
@@
 The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation. 
-To understand this, we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
+To understand this, we need to look at the Lagrangian of the ALP and GRLP in 
+\eqref{lag} and \eqref{lag2} respectively, i.e., 
 \begin{align}\label{lag}
@@
 \end{align}
-Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers.
-Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
-Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
-One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e.,
+Thus, when $Wq = \lambda$, i.e., when $W$ is a set of basis functions that allow
+a low dimensional linear representation of the dual variables $\lambda$,
+the two problems are the same.
+%Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers. 
+Hence, while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
+%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. 
+To get a sense of how $W$ should be chosen, recall that
+the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e., 
 \begin{align}
@@
 \end{align}
-where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$).
+where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$) \cite{dolgov}.
 Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.

### 2016-07-22 intro.tex
changes up to discussion

@@
 \section{Introduction}
-Markov decision processes (MDPs) is a powerful mathematical framework to study optimal sequential decision making problems that arise in science and engineering.
+Markov decision processes (MDPs) are a powerful mathematical framework to study optimal sequential decision making problems  arising in science and engineering.
 The so-called dynamic programming methods find an optimal policy by computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states.
-MDPs with small number of states can be solved easily by conventional solution methods such as value-, or policy-iteration, or linear programming (LP) \cite{BertB}.
+MDPs with small number of states can be solved easily by conventional dynamic programming techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB}.
 
+In this paper we consider the problem of using dynamic programming with MDPs with large state spaces.
 A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$.
-Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm.
-The most widely used method for approximation is the linear function approximation (LFA), i.e., let $\tilde{J}=\Phi r^*$, where $\Phi$ is a feature matrix and $r^*$ is a weight vector to be computed.
-Dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, making it possible to work with large MDPs where even storing one value per state would be impossible in the computer's main memory.
+%Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm.
+Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation.
+Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.
 
 The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation.
-A critical shortcoming of the ALP is that the number of constraints are of the order of the size of the state space, making the vanilla version of the ALP intractable.
-A way out is to employ choose a subset of constraints random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP).
+A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable.
+A way out is to choose a subset of constraints at random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP).
 The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}.
-An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was empirically found to be useful.
+An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was also found useful in experiments.
 However, to this date, there exist no theoretical guarantees bounding the loss in performance resulting from such an approximation.
 
-In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints obtained as positive linear combinations of the original constraints of the ALP.
+In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
 The salient aspects of our contribution are listed below:
@@
 		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}). 
-		\item We also bound the performance loss due to using the one-step greedy policy $\hu$ (greedy with respect to $\hj$) as a function of $||J^*-J_{\hu}||$ (Theorem~\ref{polthe}).
+		\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).
 		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
-		\item Our results on the GRLP are the first to theoretically justify linear function approximation of Langrangian (dual) variables underlying the constraints.
+		\item Our results on the GRLP are the first to theoretically analyze the use of linear function approximation of Langrangian (dual) variables underlying the constraints.
 		\item A numerical example in controlled queues is provided to illustrate the theory.

### 2016-07-22 mdp.tex
changes up to discussion

@@
 
-A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP) or simply a policy is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
-Given an SDP $u$, the expected total discounted reward corresponding to starting at state $s$ and then choosing actions as dictated by $u$ for the states encountered is denoted by $J_u(s)$ and is defined by
+A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
+Given an SDP $u$, the expected total discounted reward corresponding to starting at state $s$, while choosing actions as dictated by $u$ for the states encountered, is
 \begin{align}
@@
 where $\alpha \in (0,1)$ is the so-called discount factor and $s_{n+1} \sim p_{a_n}(s_n,\cdot)$, $n\ge 0$. 
-Here $J_u(s)$ is known as the value of the state $s$ under SDP $u$, and $J_u$ (as a map from $S$ to the reals)
-is known as the value function corresponding to the SDP $u$.
+We call $J_u(s)$ the value of state $s$ under SDP $u$, while $J_u$ (as a map from $S$ to the reals)
+is called the value function underlying policy $u$.
 The \emph{optimal policy} $u^*$ is one that in each state $s\in S$ achieves the best possible total expected discounted reward from that state.
-That is, $J^{u^*})(s) = J^*(s) \eqdef \max_{u\in U} J_u(s)$.\footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.}, where $U$ is the set of all SDPs and $J^*$ is coined the \emph{optimal value function}.
+That is, $J^{u^*}(s) = J^*(s) \eqdef \max_{u\in U} J_u(s)$
+where $U$ is the set of all SDPs and $J^*$ is coined the \emph{optimal value function}.%
+\footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.},
 
@@
 \end{subequations}
-Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.
+Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}
+for each state relatively cheaply (e.g., having the ability to sample from the next-state distribution at
+a given state-action pair).
+Thus computing the value function is at the heart of most solution methods to MDP.
 
-For convenience, in what follows we identify elements of $\R^n$ with $\R^S$ in the natural way.
-In particular, we can thus treat $J_u$ and $J^*$ as vectors in $\R^n$.
+The value functions $J^u$ or $J^*$ are elements of $\R^S$.
+In what follows it will be useful for us to treat these as $n$-dimensional vectors, i.e., elements of $\R^n$, effectively identifying $\R^S$ with $\R^S$ in the natural way.
 Similarly we identify $\R^{nd}$ with $\R^{S\times A}$.
-We now give some definitions that will be useful later.
+The following definitions will be useful later:
 %The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
@@
 \item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
-\item A policy $\tu$ is said to be greedy with respect to some function $\tj:S \to \R$ if \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
+\item A policy $\tu$ is said to be greedy with respect to (w.r.t.) $\tj\in \R^n$ if for any $s\in S$,
+%some function $\tj:S \to \R$ 
+\begin{align*}\tu(s)\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
 \end{enumerate}
 \end{definition}
-We now state without proof the most important properties of the Bellman operator.
+We now state without proof the most important properties of the Bellman operator(s).
 The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
@@
 If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{eq:shift} then 
-$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
+$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \R^n$,
 \begin{align}
@@
 \begin{align}\label{mdplp}
-\min_{J\in \R^n}\, &c^\top J\\
-\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\nn\\
-&\forall s \in S, a \in A,
+\min_{J\in \R^n}\, &c^\top J\,\,\text{s.t.}\\
+%\mb
+ J(s)&\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
+\forall (s,a)\in S\times A,
 \end{align}
-where $c$ is \emph{any} function such that $c(s)>0, \forall s \in S$.
+where $c$ is \emph{any} vector of $\R^n$ such that $c(s)>0, \forall s \in S$.
 Without loss of generality, we may and will assume in what follows that $\sum_{s\in S}c(s)=1$, i.e., $c$ is a probability distribution over $S$.
@@
 A practical solution is to resort to function approximation.
-The most widely used is the linear function approximation wherein the exact value function is approximated by a function that is obtained as a linear combination of a set of pre-selected basis functions.
+Linear function approximation, wherein the solution is searched in the subspace spanned by a set of pre-selected basis functions, is an attractive choice.

### 2016-07-22 num.tex
experiments etc

@@
 \section{Numerical Illustration}
-In this section, we show via an example in the domain of controlled queues \cite{ALP}  that the error term $\et$ indicates \todoc{right word?}
+In this section, we show via an example in the domain of controlled queues that the error term $\et$ indicates \todoc{right word?}
  the quality of the constraint approximation.
@@
 We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
-For our experiments, we chose two contenders for the $W$-matrix and compared them with random positive matrix $W_r$.
+For our experiments, we chose two contenders for the $W$-matrix and compared them with random positive matrices $W_r$.
 Our choices of the $W$ matrix were: {$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$.
@@
 {$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$.
-Our choice of the $W_a$ matrix to correspond to aggregation of near by states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
+Our choice of the $W_a$ matrix to correspond to aggregation of nearby states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
 The aggregation matrix $W_a$ is defined as below: for all $ i=1,\ldots,m$,
@@
 We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$.
-We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$.
+We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$, where $W_i$ is the ideal
+(and intractable) sampler of \citep{CS}. \todoc{Right??}
 We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively.

### 2016-07-22 resdisc.tex
experiments etc

@@
 The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities, our analysis is based on contraction operators and is completely deterministic, unlike prior results on constraint sampling \cite{CS} which are probabilistic.The error term $\etmn$ gives new insights into constraint selection:
+It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
+In particular, the error term $\etmn$ gives new insights into constraint selection:
 \begin{theorem}\label{st}
-Let $s\in S$ be a state whose constraint is selected in $W$. \todoc{Try to rephrase this..}
+Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$, 
+$W_{s'a,i}=\delta_{s=s'}$. 
 Then
@@
 It is easy to note that $r_{e_s,J^*}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s,J^*})(s)\geq (\Phi {r}'_{e_s,J^*})(s)$.
-However, since the constraints with respect to state $s$ have been sampled we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*$.
+However, since the constraints with respect to state $s$ have been chosen we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*(s)$.
 The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s,J^*})(s)$ and $\hg J^*(s)=(\Phi {r}_{e_s,J^*})(s)$.
 \end{proof}
-The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint sampling \todoc{??} is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
+The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
 This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
-The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not sampled.
-\todoc{??}
+The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.

### 2016-07-22 abstract.tex
abstract

@@
+%!TEX root =  autocontgrlp.tex
 \begin{comment}
@@
 By providing a detailed error analysis for the GRLP, we justify linear approximation of the dual variables.
-Unlike prior results on constraint sampling which hold only with high probability, our analysis holds with probability one and is based on a novel contraction operator.
+Unlike prior probabilistic results on constraint sampling, our analysis is deterministic and is based on a novel contraction operator.
 %We discuss the implication of our results in the contexts of ADP and reinforcement learning.

### 2016-07-22 num.tex
abstract

@@
 \section{Numerical Illustration}
-In this section, we show via an example in the domain of controlled queues that the error term $\et$ indicates \todoc{right word?}
- the quality of the constraint approximation.
+In this section, we show via an example in the domain of controlled queues that the error term $\et$ indeed correlates with
+ the error induced by the constraint approximation.
 The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}.

### 2016-11-27 errana.tex
changes up to discussion
revised

@@
 \section{Error Analysis}\label{sec:errana}
-We now define two projection operators which are central to our error analysis:
-%The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
-\begin{definition}\label{lubpop}
-Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to 
+\subsection{Premilinary results from MDP}
+We now state without proof the most important properties of the Bellman operator(s).
+The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
+\begin{comment}
+First, we introduce some extra notation:
+For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
+We use $\one \in \R^n$ to denote a vector with all entries $1$.
+The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
+\end{comment}
+\begin{lemma}\label{tprop}
+\begin{enumerate}[(i)]
+\item \label{monotone}$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$.
+\item \label{shift}
+Given $J\in \R^n$ and $t \in \R$, we have $T(J+t\one)=TJ+\alpha t\one$.
+\item \label{maxnorm}
+If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{shift} then
+$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \R^n$,
+$
+||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
+$
+\item \label{uniquesol}
+$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
+\end{enumerate}
+\end{lemma}
+\begin{corollary}
+If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
+\end{corollary}
+Though \cref{tprop} are stated for the Bellman operator $T$, the results also hold for $H$ as well.
+\subsection{Analysis using Lyapunov Functions}
+\begin{definition}
+Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$, define
+\begin{enumerate}[(i)]
+\item The discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
+\item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
+\end{enumerate}
+\end{definition}
+\begin{assumption}\label{grlpassmp}
+\begin{enumerate}[(i)]
+%\item \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$.
+\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
+and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$.
+\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
+\end{enumerate}
+\end{assumption}
+The error bounds for the ALP in \cite{ALP} are expressed in terms of $\frac{1}{1-\beta_{\psi}}$.
+A smaller $\beta_{\psi}$ loosely implies `stability' of the the underlying MDP,  with smaller values representative of higher stability.
+Prior works in ALP literature \cite{ALP,SALP,CS} make use of Lyapunov function based analysis to obtain error bounds that exploit the structure of the underlying MDP.
+In particular, the prior bounds suggests that the ALP is likely to generate good approximations when the underlying MDP is stable.
+We also adopt a similar approach by stating our results using Lyapunov function based arguments.
+
+We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$ and $t>0$,
 \begin{align}
-\label{lubplp}
-\begin{split}
- \underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,,\\
- \text{s.t.}& \mb \Phi r\geq  TJ.
- \end{split}
+\label{eq:psilin}
+T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,. %\,\, \quad (J\in \R^n,\, t>0)\,.
 \end{align}
-Then, for $J\in \R^n$, $\Gamma J$,
-the \emph{ least upper bound projection} of $J$ is defined as 
-\begin{align}\label{gamdef}
-(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
-\end{align}
-\end{definition}
-\begin{remark}\label{ubrem}
-To understand the meaning of $\Gamma$ (and $\hg$) define 
-\begin{align}\label{ubclass}
-\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
-\end{align}
-where $J\in \R^n$. 
-Disregarding the constraint $r\in \N$, 
-$\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
-\end{remark}
-%The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
-The definition of the second operator is as follows:
-\begin{definition}\label{alubpop}
-Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}$ to be the solution to 
-\begin{align}\label{alubplp}
- \underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,,\nn\\
- \text{s.t.}& \,\,\, W^\top E \Phi r\geq W^\top HJ.
-\end{align}
-Then, the \emph{approximate least upper bound (ALUB) projection operator}
-$\hg \colon \R^n \ra \R^n$ is defined as 
-\begin{align}\label{tgamdef}
-(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,, J\in \R^n\,.
-\end{align}
-\end{definition}
+%\input{schematic}
+The next lemma is elementary, but will prove to be useful:
 \begin{lemma}\label{lpsol}
-Let $A\in \R^{u\times v}$, $b,c\in \R^u$ and $b_0=Ax_0$ for 
+Let $A\in \R^{u\times v}$, $b\in \R^u,d\in \R^v$ and $b_0=Ax_0$ for
 some $x_0 \in \R^v$, $\N' \subset \R^v$ such that $\N' =x_0+ \N'$. Then
 \begin{align}
-&\min\{c^\top Ax:Ax\geq b+b_0, x\in \N'\} \nn\\
-&=\min\{c^\top A y:Ay \geq b, y \in \N' \}+c^\top b_0.
+&\min\{d^\top x:Ax\geq b+b_0, x\in \N'\} \nn\\
+&=\min\{d^\top y:Ay \geq b, y \in \N' \}+d^\top x_0.
 \end{align}
@@
 \begin{lemma}\label{bestbndmn}
-We have
+Let $r^*\eqdef\underset{r\in \R^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$, then
 \begin{align}
@@
  \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
-Now, using Lemma~\ref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $c=e_i$, $b_0=t\beta_\psi \psi$ 
+Now, using Lemma~\ref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=e_i\Phi$, $b_0=t\beta_\psi \psi$
 and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
@@
 \begin{proof}
-Follows from \cref{maxnormmn} and \cref{gshiftmn}.
+Follows from \cref{maxnormmn,gshiftmn}.
 \begin{comment}
@@
 In what follows we denote by $\hv$ the unique fixed point of $\hg$, i.e., $\hv = \hg \hv\,$. 
-We now show that the vector $\hj$ dominates the vector $\hv$:
+We now show that vector $\hj$ dominates $\hv$:
 \begin{lemma}\label{relation1}
@@
 Hence, by the monotone property of $H$ and \cref{grlpassmp}-\eqref{wassump} it is sufficient if $\Phi r_i \ge V_0$.
-This however directly follows from the definition of $V_0$.
+This however follows from the definition of $V_0$.
 \end{proof}
@@
 \begin{split}
-\min_{r\in \N}\, &||\Phi r-\hv||_{1,c}\\
-\text{s.t.}\mb &\, W^\top E \Phi r\geq W^\top H \Phi r.
+\min_{r\in \N}\, &||\Phi r-\hv||_{1,c}\,\mb
+\text{s.t.}\mb \, W^\top E \Phi r\geq W^\top H \Phi r.
 \end{split}
@@
 \begin{split}
-\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\\
-\text{s.t.}\mb &\, \Phi r\geq  T \Phi r.
+\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\,\mb
+\text{s.t.}\mb \, \Phi r\geq  T \Phi r.
 \end{split}
@@
 \end{align}
-The result now follows by substituting the bound on $||J^*- \hv||_{\mn}$ from \cref{cmt1mn} and the fact that $||\hv-\hj||_{\mn}\leq \frac{1}{1-\beta_{\psi}}||\hj-\hg\hj||$.
+The result now follows by substituting the bound on $||J^*- \hv||_{\mn}$ from \cref{cmt1mn} and the fact that $||\hv-\hj||_{\mn}\leq \frac{1}{1-\beta_{\psi}}||\hj-\hg\hj||_{\mn}$.
 \end{proof}

### 2016-11-27 grlp.tex
revised

@@
 %!TEX root =  autocontgrlp.tex
-\section{Generalized Reduced Linear Program}
+\section{Approximate Linear Programming: Successes and Challanges}
+When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}.
+A practical solution is to resort to function approximation.
+Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$.
 The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
@@
 \end{align}
-where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}.
+where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $\Phi$ is a feature matrix whose first column is $\one$.
 Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy w.r.t.
 $\tj$.
+The following is a preliminary error bound for the ALP from \cite{ALP}:
+\begin{theorem}[Error Bound for ALP]
+\begin{align*}
+||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty
+\end{align*}
+\end{theorem}
+%For a more detailed treatment of the ALP and sophisticated bounds, the reader is referred to \cite{ALP}.
+%\subsection{Approximating the Constraints}
+The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
+Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
+Most works in literature make use of the underlying structure of the problem to cleverly reduce the number of constraints of the ALP.
+A good example is \cite{gkp}, wherein the structure in factored linear functions is exploited.
+The use of basis function also helps constraint reduction in \cite{Mor-Kum}.
+In \cite{ALP-Bor}, the constraints are approximated indirectly by approximating the square of the Lagrange multipliers.
+In \cite{petrik} the transitional error is reduced ignoring the representational and sampling errors.\par
+The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP.
+While the objective of the RLP is same as that of the ALP, the RLP has only $m<<nd$ constraints \emph{sampled} from the original $nd$ constraints of the ALP.
+The following is a preliminary error bound for the RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
+\begin{theorem}[Error Bound for RLP]
+If $\tilde{r}_{RLP}$ is a solution to the RLP, then
+\begin{align*}
+||J^*-\Phi\tilde{r}_{RLP}||_{1,c}\leq ||J^*-\Phi\tilde{r}||_{1,c}+\epsilon ||J^*||_{1,c}
+\end{align*}
+\end{theorem}
+%A major gap in the theoretical analysis is that the error bounds are known for only a specific RLP formulated using idealized assumptions, i.e., under knowledge of $u^*$.
+However, the RLP has be found to do well empirically in domains such as Tetris \cite{CST} and controlled queues \cite{CS}.
+\subsection{Open Questions}
+Interestingly, the RLP has nevertheless been found to do well empirically in domain such as Tetris \cite{CST} and controlled queues \cite{CS} even when the constraints were sampled using distribution other than the ideal distribution.
+This fact indicates a gap in the theoretical analysis and points to the need for a more elaborate theory that addresses the issue of constraint approximation.
+In this paper, we answer the following questions related to constraint reduction in ALP that have so far remained open.
+\\
+$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
+$\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
+In this paper, we address both of the questions above.
+\section{Generalized Reduced Linear Program}
 The Generalized Reduced Linear Program is given as:
@@
 \begin{split}
-\underset{r\in \N}{\min}\, &\, c^\top \Phi r\,\,\,\,
-\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
+&\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
+&\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
 \end{split}
 \end{align}
-where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution.%
+where we assume that $W \in \R^{nd\times m}_+$ is a matrix with all positive entries, $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution and $\tr \in \N$.
 \footnote{The appendix explains how $\N$ can be chosen.}
-In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.
-
-We assume that the following hold in the rest of the paper:
-\begin{assumption}\label{grlpassmp}
-\begin{enumerate}[(i)]
-\item \label{probdist} $c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0 \mb \forall i$ and $\sum_{i=1}^n c(i)=1$.
-\item  \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
-\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
-and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$. 
-\item \label{nassmp} $\N\subset \R^k$ is compact and $\tr \in \N\subset\R^k$.
-\item \label{wassump} $W \in \R^{nd\times m}_+$ is a full rank $nd\times m$ matrix (where $m\ll nd$), with all non-negative entries such that each of its column-sums equals one.
-\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
-\end{enumerate}
-\end{assumption}
-We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$ and $t>0$,
-\begin{align}
-\label{eq:psilin}
-T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,. %\,\, \quad (J\in \R^n,\, t>0)\,.
-\end{align}
-
+In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.\par
 The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation. 
@@
 Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.
+\subsection{Novel Projection Operators}
+We now define two projection operators which are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
+%The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
+\begin{definition}\label{lubpop}
+Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to
+\begin{align}
+\label{lubplp}
+\begin{split}
+\underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,\mb
+\text{s.t.} \mb \Phi r\geq  TJ.
+\end{split}
+\end{align}
+Then, for $J\in \R^n$, $\Gamma J$,
+the \emph{ least upper bound projection} of $J$ is defined as
+\begin{align}\label{gamdef}
+(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
+\end{align}
+\end{definition}
+
+%The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
+The definition of the second operator is as follows:
+\begin{definition}\label{alubpop}
+Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}$ to be the solution to
+\begin{align}\label{alubplp}
+\underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,\mb
+\text{s.t.} \,\,\, W^\top E \Phi r\geq W^\top HJ.
+\end{align}
+Then, the \emph{approximate least upper bound (ALUB) projection operator}
+$\hg \colon \R^n \ra \R^n$ is defined as
+\begin{align}\label{tgamdef}
+(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,, J\in \R^n\,.
+\end{align}
+\end{definition}
+\begin{remark}\label{ubrem}
+To understand the meaning of $\Gamma$ (and $\hg$) define
+\begin{align}\label{ubclass}
+\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
+\end{align}
+where $J\in \R^n$.
+Disregarding the constraint $r\in \N$,
+$\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
+\end{remark}
+
+%\input{cartoon}
+\subsection{Error Bounds}
+\begin{theorem}[Error Bound for GRLP]
+\label{cmt2mn}
+%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
+It holds that
+\begin{align*}%\label{finalbndmn}
+\begin{split}
+||J^*-\hj||_{1,c}
+\leq\frac{1}{1-\alpha}(6 ||J^*-\Phi r^*||_{\infty}
++2||\Gamma J^*-\hg J^*||_{\infty}).
+\end{split}
+\end{align*}
+\end{theorem}
+\begin{comment}
+\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
+\label{polthe}
+Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
+% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
+Then,
+\begin{align}\label{polthebnd}
+%||J_{\hu}-\hj||_{1,c}
+\norm{J^* - J_{\hu}}_{1,c}
+&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\infty}
+\nn\\&
++||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big).
+\end{align}
+\end{theorem}
+\end{comment}
+\begin{theorem}[Constraint Sampling]\label{st}
+Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
+$W_{s'a,i}=\delta_{s=s'}$.
+Then
+\begin{align*}%\label{sampexp}
+|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
+\end{align*}
+\end{theorem}
+The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
+This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
+The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
+It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
+In particular, the error term $\parallel\Gamma J^*-\tg J^* \parallel$ gives new insights into constraint selection. 
+The result of Theorem~\ref{st} is that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
+This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
+The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.
+\begin{comment}
+\subsection{Comparison with ADP methods}
+A host of the ADP methods such as \cite{lspi,lspe,lstd,Tsit} are based on solving the projected Bellman equation (PBE).
+The PBE based methods have been empirically successful and also have theoretical guarantees for the approximate value function.
+However, a significant shortcoming is that they suffer from the issue of \emph{policy-chattering} (see section~$6.4.3$ of \cite{BertB}), i.e., the sequence of policies might oscillate within a set of bad policies.
+A salient feature of the ALP based methods is that they find only one approximate value function $\tj$ and one sub-optimal policy derived as a greedy policy with respect to $\tj$.
+As a result there is no such issue of policy-chattering for the ALP based methods.
+By providing the error bounds for the GRLP, our paper provides the much required theoretical support for the RLP.
+Our GRLP framework closes the long-standing gap in the literature of providing a theoretical framework to bound the error due to constraint reduction in ALP based schemes.\\
+
+\FloatBarrier
+\begin{table}[H]
+\resizebox{\columnwidth}{!}{
+\begin{tabular}{|c|c|c|}\hline
+ADP Method	&Empirical	&Theoretical\\\hline
+Projected Bellman &\ding{51}    &\ding{53}-Policy Chattering\\
+Equation	&	&\\\hline
+ALP		&\ding{53}-Large number of Constraints &\ding{51}\\\hline
+RLP		&\ding{51} &\ding{53}-  Only under\\
+&&ideal assumptions\\\hline
+\end{tabular}
+}
+\end{table}
+\end{comment}

### 2016-11-27 mdp.tex
revised

@@
 %!TEX root =  autocontgrlp.tex
-\section{Markov Decision Processes (MDPs)}
+\section{Markov Decision Processes (MDPs) and Linear Programming}
 We consider MDPs with a finite state space $S=\{1,2,\ldots,n\}$ and finite action space $A=\{1,2,\ldots,d\}$, where the sentiment is that $n$ is large.
@@
 We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
-
 A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
@@
 \footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.}, 
-
 Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$,
@@
 a given state-action pair).
-Thus computing the value function is at the heart of most solution methods to MDP.
-
+Thus computing the value function is at the heart of most solution methods to MDP.\par
+%\subsection{Linear Programming}
+As it is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
+\begin{align}\label{mdplp}
+\begin{split}
+\min_{J\in \R^n}\, &c^\top J\,\,\text{s.t.}\\
+%\mb
+J(s)&\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
+\forall (s,a)\in S\times A,
+\end{split}
+\end{align}
+where $c$ is \emph{any} vector of $\R^n$ such that $c(s)>0, \forall s \in S$.
+Without loss of generality, we may and will assume in what follows that $\sum_{s\in S}c(s)=1$, i.e., $c$ is a probability distribution over $S$.\par
+%\subsection{Notation}
 The value functions $J^u$ or $J^*$ are elements of $\R^S$.
@@
 %The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
-\begin{definition}
+\begin{definition}Define
+\begin{comment}
 Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$,
 define
+\end{comment}
 \begin{enumerate}[(i)]
@@
 \item \label{bellactval} The Bellman operator (of action values) $H: \R^n \to \R^{nd}$ for state-action values as $HJ=[ H_1 J,\cdots,H_d J]^\top\in \R^{nd},$ where $(H_a J)(s)= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s')$.
-\item The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ 
-and 
-the weighted $L_\infty$-norms  $\norm{\cdot}_{\infty,\rho}$ as $
-||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|, 
+\begin{comment}
+\item
 ||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
@@
 \item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
+\end{comment}
 \item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
-\item A policy $\tu$ is said to be greedy with respect to (w.r.t.) $\tj\in \R^n$ if for any $s\in S$,
+\item A policy $u_J$ is said to be greedy with respect to (w.r.t.) $J\in \R^n$ if for any $s\in S$,
 %some function $\tj:S \to \R$
-\begin{align*}\tu(s)\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
+\begin{align*}u_J(s)\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J(s')\big).\end{align*}
+\item The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ with respect to a probability distribution $c$ as $
+||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|$.
+\item The (un)weighted $L_\infty$-norms $\norm{\cdot}_{1,\infty}$
+and $\norm{\cdot}_{\infty,\rho}$, $\parallel J\parallel_{\infty}=\max_{s\in S}|J(s)|$ and $||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
+\item $J_1\leq J_2$, when $J_1(s)\leq J_2(s),~\forall s\in S$.
+\item $\one\in \R^n$ to be the vector whose all coordinates are $1$.
 \end{enumerate}
 \end{definition}
-We now state without proof the most important properties of the Bellman operator(s).
-The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
-First, we introduce some extra notation:
-For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
-We use $\one \in \R^n$ to denote a vector with all entries $1$.
-The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
-\begin{lemma}\label{monotone}
-$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
-\end{lemma}
-\begin{lemma}\label{shift}
-Given $J\in \R^n$ and $t \in \R$, we have
-\begin{align}\label{eq:shift}
-T(J+t\one)=TJ+\alpha t\one.
-\end{align}
-\end{lemma}
-\begin{lemma}\label{maxnorm}
-If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{eq:shift} then 
-$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \R^n$,
-\begin{align}
-||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
-\end{align}
-\end{lemma}
-\begin{lemma}\label{uniquesol} 
-$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
-\end{lemma}
-\begin{corollary}
-If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
-\end{corollary}
-Though  \cref{monotone,shift,maxnorm} are stated for the Bellman operator $T$, the results also hold for $H$ as well.
-
-\subsection{The Linear Programming Formulation}
-As it is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
-\begin{align}\label{mdplp}
-\min_{J\in \R^n}\, &c^\top J\,\,\text{s.t.}\\
-%\mb
- J(s)&\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
-\forall (s,a)\in S\times A,
-\end{align}
-where $c$ is \emph{any} vector of $\R^n$ such that $c(s)>0, \forall s \in S$.
-Without loss of generality, we may and will assume in what follows that $\sum_{s\in S}c(s)=1$, i.e., $c$ is a probability distribution over $S$.
-
-When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}.
-A practical solution is to resort to function approximation.
-Linear function approximation, wherein the solution is searched in the subspace spanned by a set of pre-selected basis functions, is an attractive choice.

### 2016-11-27 resdisc.tex
revised

@@
 %!TEX root =  autocontgrlp.tex
-\section{Discussion}
+\subsection{Discussion}
+\begin{comment}
 The error bounds in the main results (Theorems~\ref{cmt2mn} and \ref{polthe}) contain two factors, namely
@@
 \end{theorem}
+\end{comment}
 \begin{proof}
@@
 \end{proof}
+\begin{comment}
 The expression in \eqref{sampexp} in Theorem~\ref{st} says that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
@@
 The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.
+\end{comment}

### 2017-01-31 grlp.tex
changed intro

@@
 %!TEX root =  autocontgrlp.tex
+\begin{comment}
 \section{Approximate Linear Programming: Successes and Challanges}
@@
 In this paper, we address both of the questions above.
-\section{Generalized Reduced Linear Program}
+\end{comment}
+\section{Main Results}
+\begin{comment}
 The Generalized Reduced Linear Program is given as:
@@
 In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.\par
-The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation. 
-To understand this, we need to look at the Lagrangian of the ALP and GRLP in 
-\eqref{lag} and \eqref{lag2} respectively, i.e., 
-\begin{align}\label{lag}
-\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
-\end{align}
-Thus, when $Wq = \lambda$, i.e., when $W$ is a set of basis functions that allow
-a low dimensional linear representation of the dual variables $\lambda$,
-the two problems are the same.
-%Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers. 
-Hence, while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
-%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. 
-To get a sense of how $W$ should be chosen, recall that
-the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e., 
-\begin{align}
-\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
-				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
-			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
-\end{align}
-where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$) \cite{dolgov}.
-Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.
-\subsection{Novel Projection Operators}
+\end{comment}
+%\subsection{Novel Projection Operators}
 We now define two projection operators which are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
@@
 \end{theorem}
+The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
+This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.
+The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
+It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
 \begin{comment}
@@
 \end{theorem}
-The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
-This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
-The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
-In particular, the error term $\parallel\Gamma J^*-\tg J^* \parallel$ gives new insights into constraint selection. 
-The result of Theorem~\ref{st} is that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
+\begin{comment}
+An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
+In particular, the error term $\etmn$ gives new insights into constraint selection:
+The result of Theorem~\ref{st} is that
+\end{comment}
+The additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
 This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
-The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.
-\begin{comment}
-\subsection{Comparison with ADP methods}
-A host of the ADP methods such as \cite{lspi,lspe,lstd,Tsit} are based on solving the projected Bellman equation (PBE).
-The PBE based methods have been empirically successful and also have theoretical guarantees for the approximate value function.
-However, a significant shortcoming is that they suffer from the issue of \emph{policy-chattering} (see section~$6.4.3$ of \cite{BertB}), i.e., the sequence of policies might oscillate within a set of bad policies.
-A salient feature of the ALP based methods is that they find only one approximate value function $\tj$ and one sub-optimal policy derived as a greedy policy with respect to $\tj$.
-As a result there is no such issue of policy-chattering for the ALP based methods.
-By providing the error bounds for the GRLP, our paper provides the much required theoretical support for the RLP.
-Our GRLP framework closes the long-standing gap in the literature of providing a theoretical framework to bound the error due to constraint reduction in ALP based schemes.\\
-
-\FloatBarrier
-\begin{table}[H]
-\resizebox{\columnwidth}{!}{
-\begin{tabular}{|c|c|c|}\hline
-ADP Method	&Empirical	&Theoretical\\\hline
-Projected Bellman &\ding{51}    &\ding{53}-Policy Chattering\\
-Equation	&	&\\\hline
-ALP		&\ding{53}-Large number of Constraints &\ding{51}\\\hline
-RLP		&\ding{51} &\ding{53}-  Only under\\
-&&ideal assumptions\\\hline
-\end{tabular}
-}
-\end{table}
-\end{comment}
+%The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.

### 2017-01-31 intro.tex
submitted_version
revised
changed intro

@@
 Markov decision processes (MDPs) are a powerful mathematical framework to study optimal sequential decision making problems  arising in science and engineering.
-The so-called dynamic programming methods find an optimal policy by computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states.
-MDPs with small number of states can be solved easily by conventional dynamic programming techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB}.
+In an MDP, the configuration of the system is described by the state variables (or simply the state) and the system evolves in a stochastic manner which depends on the action made.
+The set of all states is denoted by $S$, the state space and the set of all actions is denoted by $A$, the action space.
+%An instance of an MDP is a controlled queue setting, where there is a cost associated with the number of customers in the queue, and the aim is to control the service level depending on the number of %customers so as to achieve a minimum cumulative cost.
+In more general terms, given any MDP,
+We are interested in computing what is known as the optimal policy $u^*$ (a map from $S$ to $A$).
+The so-called dynamic programming (DP) methods first compute what is known as the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states, and use it to compute $u^*$.
+When the number of state is small conventional DP techniques, such as value-, or policy-iteration, or linear programming (LP) can be used to compute $J^*$ and $u^*$\cite{BertB}.\par
+As the number of states is grows, it becomes increasingly difficult to compute the exact values of $J^*$ and $u^*$.
+A practical solution then is to compute an approximate value function $\tilde{J}$ instead of $J^*$.
+Approximate dynamic programming (ADP) methods combine an approximation architecture to represent $\tj$ and a conventional DP method to compute $\tj$.
+Eventually, ADP methods output a sub-optimal policy $\tu$ using the $\tj$ they compute.
+%Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm.\par
+Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation.
+Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.\par
+It is natural to expect that approximations lead to errors and it is important to quantify the errors.
+For a given ADP method, theoretical performance analysis analytically bounding the error terms $||J^*-\tilde{J}||$  and $\norm{J^*-J_{\tu}}$ which denote the error in approximating the value function, and performance loss due to following policy $\tu$ (here $J_{\tu}$ is the value of $\tu$) respectively.
+Further, in most cases the error terms reveal some structure that can offer insights and act as guide to the designer of the ADP method (for example the choice of $\Phi$).
+\par
 
-In this paper we consider the problem of using dynamic programming with MDPs with large state spaces.
-A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$.
-%Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm.
-Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation.
-Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.
+%While many ADP methods use LFA, not all of them are successful.
+For instance, ADP methods that use linear least squares projection are known to exhibit `policy oscillations' \cite{dpchapter}, i.e., %output a repeating sequence of bad sub-optimal policies.
+%Such an analysis is important to establish that the error is always bounded.
+%Further, in most cases the error terms reveal some structure that can offer insights and act as guide to the designer of the ADP method (for example the choice of $\Phi$). \par
 
-The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation.
+The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants combine LFA and the LP approach. Theoretical performance analysis of the ALP can be found in \cite{ALP}.
+%and a salient feature is that it does not suffer from issues such as `policy oscillations'\footnote{ADP methods that use linear least squares projection are known to exhibit `policy oscillations' %\cite{BertB}, i.e., output a repeating sequence of bad sub-optimal policies.
+Since our focus in this paper is the ALP formulation, we refrain from a detailed presentation of the other methods.}
+
 A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable.
-A way out is to choose a subset of constraints at random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP).
-The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}.
-An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was also found useful in experiments.
-However, to this date, there exist no theoretical guarantees bounding the loss in performance resulting from such an approximation.
-
-In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
+Two approaches have been found empircally successful in addressing the issue of large number of constraints in the ALP.
+In the first approach, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear program} (RLP).
+The performance analysis of the RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions.
+The second approach involves employing function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}.
+However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach.\par
+Our motivation stems from the fact that ALP with tractable number of constraints will result in a full dimeniosnality free ADP method.
+However, constraint reduction in the ALP is an extra source of error (in addition to the error due to LFA), which has not been theoretically well understood.
+The focus of this paper is to fill this gap in theory by deriving performance bounds for constraint reduction in the ALP formulation.
 The salient aspects of our contribution are listed below:
 \begin{enumerate}
+\item We define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
+The GRLP amounts to linear function approximation of the dual variables, and the RLP is a special case of GRLP.
 		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}). 
@@
 		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
+%Our analysis also makes use of arguments based on \emph{Lyanpunov} function, an approach much similar to prior works in ALP literature \cite{ALP,SALP}.
 \item Our results on the GRLP are the first to theoretically analyze the use of linear function approximation of Langrangian (dual) variables underlying the constraints.
@@
 \end{enumerate}
+%ALP with tractable number of constraints would result in  a full dimensionality free ADP method, without issues such as policy oscillations.
+A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.

### 2017-01-31 prob.tex
changed intro

\section{Problem Setup}
We now present the linear programming (LP), approximate linear programming (ALP) and the generalized reduced approximate linear programming (GRLP) respectively. In what follows, $c>0\in \R^n$ is a probability distribution.
It is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
\begin{align}\label{mdplp}
\begin{split}
\min_{J\in \R^n}\, &c^\top J\,\,\text{s.t.}\\
%\mb
J(s)&\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
\forall (s,a)\in S\times A,
\end{split}
\end{align}
\begin{comment}
When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy ite
ration \cite{BertB}. A practical solution is to resort to function approximation. Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$.\par
\end{comment}
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\,\,\,
\text{s.t.}\mb \Phi r\geq T \Phi r,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $\Phi$ is a feature matrix whose first column is $\one$.
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
&\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
&\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}
\end{align}
Unless specified otherwise we use $\hr$/$\tr$ to denote an arbitrary solution to the GRLP/ALP. In similar spirit, and we let $\hj=\Phi \hr$/$\tj=\Phi \tr$ to denote the corresponding value functions and $\hu$/$\tu$ to denote the greedy policy w.r.t. $\hj$/$\tj$.\par
\textbf{Remarks:}
\begin{enumerate}
\item When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}. A practical solution is to resort to function approximation. Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$. For $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
\item $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints. $\N$ is a compact set such that $\tr \in \N$. This additional constraint set ensures the boundedness of the solution. For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as the ALP.
\end{enumerate}
\FloatBarrier
\input{cartoon}
\Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively. The erorr in the ALP solution has already been studied in \cite{ALP}. Our objective is to study the extra source of error due to constriant approximation.
\begin{comment}
In addition, we answer the following questions related to constraint reduction in ALP that have so far remained open. \\
$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
$\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
In this paper, we address both of the questions above.
\end{comment}

### 2017-01-31 rel.tex
changed intro

--- 2016-11-27 grlp.tex
@@
-%!TEX root =  autocontgrlp.tex
-\section{Approximate Linear Programming: Successes and Challanges}
-When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}.
-A practical solution is to resort to function approximation.
-Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$.
-The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
-By substitution, this leads to
-\begin{align}\label{alp}
-\begin{split}
-\min_{r\in \R^k}\, &c^\top \Phi r\,\,\,
-\text{s.t.}\mb \Phi r\geq T \Phi r,
-\end{split}
-\end{align}
-where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $\Phi$ is a feature matrix whose first column is $\one$.
-Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy w.r.t.
-$\tj$.
+\section{Related Work}
 The following is a preliminary error bound for the ALP from \cite{ALP}:
@@
 Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
+
 Most works in literature make use of the underlying structure of the problem to cleverly reduce the number of constraints of the ALP.
@@
 In this paper, we address both of the questions above.
-\section{Generalized Reduced Linear Program}
-The Generalized Reduced Linear Program is given as:
-\begin{align}\label{grlp}
-\begin{split}
-&\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
-&\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
-\end{split}
-\end{align}
-where we assume that $W \in \R^{nd\times m}_+$ is a matrix with all positive entries, $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution and $\tr \in \N$.
-\footnote{The appendix explains how $\N$ can be chosen.}
-In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.\par
+\subsection{Primal-Dual Approximation}
 The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation.
@@
 Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.
-\subsection{Novel Projection Operators}
-We now define two projection operators which are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
-%The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
-\begin{definition}\label{lubpop}
-Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to
-\begin{align}
-\label{lubplp}
-\begin{split}
-\underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,\mb
-\text{s.t.} \mb \Phi r\geq  TJ.
-\end{split}
-\end{align}
-Then, for $J\in \R^n$, $\Gamma J$,
-the \emph{ least upper bound projection} of $J$ is defined as
-\begin{align}\label{gamdef}
-(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
-\end{align}
-\end{definition}
 
-%The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
-The definition of the second operator is as follows:
-\begin{definition}\label{alubpop}
-Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}$ to be the solution to
-\begin{align}\label{alubplp}
-\underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,\mb
-\text{s.t.} \,\,\, W^\top E \Phi r\geq W^\top HJ.
-\end{align}
-Then, the \emph{approximate least upper bound (ALUB) projection operator}
-$\hg \colon \R^n \ra \R^n$ is defined as
-\begin{align}\label{tgamdef}
-(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,, J\in \R^n\,.
-\end{align}
-\end{definition}
-\begin{remark}\label{ubrem}
-To understand the meaning of $\Gamma$ (and $\hg$) define
-\begin{align}\label{ubclass}
-\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
-\end{align}
-where $J\in \R^n$.
-Disregarding the constraint $r\in \N$,
-$\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
-\end{remark}
-
-%\input{cartoon}
-\subsection{Error Bounds}
-\begin{theorem}[Error Bound for GRLP]
-\label{cmt2mn}
-%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
-It holds that
-\begin{align*}%\label{finalbndmn}
-\begin{split}
-||J^*-\hj||_{1,c}
-\leq\frac{1}{1-\alpha}(6 ||J^*-\Phi r^*||_{\infty}
-+2||\Gamma J^*-\hg J^*||_{\infty}).
-\end{split}
-\end{align*}
-\end{theorem}
-\begin{comment}
-\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
-\label{polthe}
-Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
-% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
-Then,
-\begin{align}\label{polthebnd}
-%||J_{\hu}-\hj||_{1,c}
-\norm{J^* - J_{\hu}}_{1,c}
-&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\infty}
-\nn\\&
-+||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big).
-\end{align}
-\end{theorem}
-\end{comment}
-\begin{theorem}[Constraint Sampling]\label{st}
-Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
-$W_{s'a,i}=\delta_{s=s'}$.
-Then
-\begin{align*}%\label{sampexp}
-|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
-\end{align*}
-\end{theorem}
-The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
-This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.\par
-The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
-In particular, the error term $\parallel\Gamma J^*-\tg J^* \parallel$ gives new insights into constraint selection. 
-The result of Theorem~\ref{st} is that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
-This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
-The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.
 \begin{comment}

### 2017-01-31 grlp.tex
rearranged

@@
 \begin{theorem}[Error Bound for GRLP]
-\label{cmt2mn}
+\label{cmt2}
 %Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
 It holds that
-\begin{align*}%\label{finalbndmn}
+\begin{align}\label{finalbnd}
 \begin{split}
@@
 \end{split}
-\end{align*}
+\end{align}
 \end{theorem}
-The first factor is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
-This term is inherent to the ALP formulation and it appears in the bounds provided by \cite{ALP}.
-The second factor is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
 \begin{comment}
@@
 \end{comment}
-The additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
-This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
 %The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.

### 2017-01-31 rel.tex
rearranged

@@
-\section{Related Work}
-The following is a preliminary error bound for the ALP from \cite{ALP}:
-\begin{theorem}[Error Bound for ALP]
+\subsection{Comparison With Related Work}
+In order to interpret the resutls in \Cref{cmt2} and \Cref{st}, we now dicuss relevant prior work.
+We begin by re-stating a preliminary\footnote{The improved error bounds in \cite{ALP} as well as in \Cref{sec:improv} of this paper are in a weighted $L_\infty$ norm and are based on Lyapunov analysis.} error bounds for the ALP from \cite{ALP}:
+\begin{theorem}[Error Bound for ALP]\label{alpvanilla}
 \begin{align*}
@@
 \end{theorem}
-%For a more detailed treatment of the ALP and sophisticated bounds, the reader is referred to \cite{ALP}.
-%\subsection{Approximating the Constraints}
+\begin{comment}
+
 The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
@@
 In \cite{petrik} the transitional error is reduced ignoring the representational and sampling errors.\par
-The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP.
+\end{comment}
+%The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP.
 While the objective of the RLP is same as that of the ALP, the RLP has only $m<<nd$ constraints \emph{sampled} from the original $nd$ constraints of the ALP.
-The following is a preliminary error bound for the RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
-\begin{theorem}[Error Bound for RLP]
+%The following is a preliminary error bound for the RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
+\begin{theorem}[Error Bound for RLP]\label{rlpt}
 If $\tilde{r}_{RLP}$ is a solution to the RLP, then
@@
 \end{theorem}
-%A major gap in the theoretical analysis is that the error bounds are known for only a specific RLP formulated using idealized assumptions, i.e., under knowledge of $u^*$.
-However, the RLP has be found to do well empirically in domains such as Tetris \cite{CST} and controlled queues \cite{CS}.
+\textbf{Remarks:}
+The first factor in the right hand side of \eqref{finalbnd} in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
+This term is inherent to the ALP formulation as shown in \Cref{alpvanilla}.
+The second factor in the right hand sie of \eqref{finalbnd} is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
+It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
+It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$ and \Cref{cmt2} does not have these limitations.
+In addition, from \Cref{st}, we know that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
+This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
+\begin{comment}
 \subsection{Open Questions}
@@
 In this paper, we address both of the questions above.
+\end{comment}
 \subsection{Primal-Dual Approximation}

### 2017-02-04 abstract.tex
fresh changes

--- 2015-05-27 abstract.tex
@@
 \begin{abstract}
-The term Approximate Dynamic Programming (ADP) refers to a gamut of approximate solution methods for MDPs with large number of states.
-Though various ADP algorithms are known till date, very few of them successfully address both the prediction and the control problems.
-Approximate Linear Programming (ALP) is an ADP method that offers sound theoretical guarantees and solves both the prediction and the control problems.
-Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead.
-Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.\\
-In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP.
-The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP.
-Central to our framework are two $\max$-norm contraction operators.
-Our result also theoretically justifies linear approximation of constraints.
-We discuss the implication of our results in the contexts of ADP and reinforcement learning.
+Approximate linear programming (ALP) and its variants have been widely applied to Markov Decision Processes (MDPs) with a large number of states.
+A serious limitation of ALP is that it has an intractable number of constraints, as a result of which constraint approximations are of interest.
+In this paper, we define a generalized reduced linear program (GRLP) that has a tractable number of constraints, which are obtained as positive linear combinations of the original constraints of the ALP.
+The main contribution of this paper is a novel theoretical framework developed to obtain error bounds for any given GRLP.
+By providing a detailed error analysis for the GRLP, we justify linear approximation of the dual variables.
+Unlike prior results on constraint sampling, our analysis is deterministic and is based on a novel contraction operator.
 \end{abstract}

### 2017-02-04 adp.tex
fresh changes

@@
 %!TEX root =  autocontgrlp.tex
-\section{Approximate Dynamic Programming}
+\section{Approximate Dynamic Programming: Objectives and Methods}
+\FloatBarrier
+\begin{table}[H]
+\resizebox{\columnwidth}{!}{
+\begin{tabular}{|c|c|c|}\hline
+ADP Method	&Empirical	&Theoretical\\\hline
+Projected Bellman &\ding{51}    &\ding{53}-Policy Chattering\\
+Equation	&	&\\\hline
+ALP		&\ding{53}-Large number of Constraints &\ding{51}\\\hline
+RLP		&\ding{51} &\ding{53}-  Only under\\
+&&ideal assumptions\\\hline
+\end{tabular}
+}
+\end{table}
+
+\begin{comment}
 In practical problems, often the states are best described as multi-dimensional tuples.
@@
 In the next section, we discuss the approximate linear programming (ALP) formulation, the basic results and present prior results in literature as well as motivate the problem that we address in this paper.
+\end{comment}

### 2017-02-04 errana.tex
fresh changes

@@
 %!TEX root =  autocontgrlp.tex
-\section{Error Analysis}\label{sec:errana}
-\subsection{Premilinary results from MDP}
+\section{Error Analysis}\label{sec:improv}
+\subsection{Properties of the Bellman Operator}
 We now state without proof the most important properties of the Bellman operator(s).
@@
 \end{corollary}
-Though \cref{tprop} are stated for the Bellman operator $T$, the results also hold for $H$ as well.
+Though \cref{tprop} are stated for the Bellman operator $T$, the results also hold for $H$ as well.\par
+We now present the analysis to derive the improved bounds where the idea is to show that the novel projection operators ($\Gamma/\hg$) are contraction maps.
+To this end, we go through steps similar to \Cref{tprop}-\eqref{monotone},~\eqref{shift} and ~\eqref{maxnorm}.
+Much the results that ensue are based on `Lyapunov' analysis where the idea is to replace the constant function $\one$ by a certain Lyapunov function (see \Cref{def:lyap}) and the $\norm{\cdot}_{\infty}$ by a weighted max-norm (see \Cref{notations}-\eqref{norms}).
 \subsection{Analysis using Lyapunov Functions}
-\begin{definition}
+\begin{definition}\label{def:lyap}
 Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$, define
@@
 \item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
+\item \label{wassmp} $W \in \R^{nd\times m}_+$ is a matrix with all positive entries.
 \end{enumerate}
@@
 We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$ and $t>0$,
-\begin{align}
-\label{eq:psilin}
-T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,. %\,\, \quad (J\in \R^n,\, t>0)\,.
+\begin{align}\label{eq:psilin}
+\begin{split}
+T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi,\\
+H(J+ t \psi ) \le HJ + E \beta_{\psi}\,t\,  \psi\,.
+\end{split}
 \end{align}
@@
 Choose any $i\in \{1, \ldots, n\}$.
-Since $J_1\leq J_2$, from \cref{monotone} and \cref{grlpassmp}-\eqref{wassump} it follows that $W^\top H J_1\leq W^\top H J_2$.
+Since $J_1\leq J_2$, from \Cref{tprop}-\eqref{monotone} and \cref{grlpassmp}-\eqref{wassmp} it follows that $W^\top H J_1\leq W^\top H J_2$.
 Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.
@@
 \label{eq:shiftmn}
-\hg( J + t \psi) \le \hg J + \beta t \psi,
+\hg( J + t \psi) \le \hg J + \beta t \psi.
 \end{align} 
-for any $J\in \R^n$ and $t\ge 0$.
 Then $\hg$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
@@
  \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
-Now, using Lemma~\ref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=e_i\Phi$, $b_0=t\beta_\psi \psi$
+Now, using \Cref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=e_i\Phi$, $b_0=t\beta_\psi \psi$
 and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
-%The result follows in a similar manner as the proofs for Lemmas~\ref{gshift} and ~\ref{tgshift} by using the result in Lemma~\ref{lpsol}.
 \end{proof}
@@
 By definition, $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H \Phi r_i$.
-Hence, by the monotone property of $H$ and \cref{grlpassmp}-\eqref{wassump} it is sufficient if $\Phi r_i \ge V_0$.
+Hence, by the monotone property of $H$ and \cref{grlpassmp}-\eqref{wassmp} it is sufficient if $\Phi r_i \ge V_0$.
 This however follows from the definition of $V_0$.
@@
 \begin{proof}
-We know from Lemma~\ref{relation2} that $\hj = \Phi \hr \geq\hv$, and thus
+We know from \Cref{relation1} that $\hj = \Phi \hr \geq\hv$, and thus
 the solutions to \eqref{grlp} do not change if we add the constraint $\Phi r \ge \hv$.
@@
 \begin{proof}
-We know from Lemma~\ref{relation2} that $\tj = \Phi \tr \geq\hv$.
+We know from \Cref{relation2} that $\tj = \Phi \tr \geq\hv$.
 The rest of the argument follows in the same manner as the proof for \cref{srw}.
@@
 Let $\gamma=||J^*-\Phi r^*||_{\mn}$. 
-Then, by choosing $r'$ as in Lemma~\ref{restate} we have
+Then, by choosing $r'$ as in \Cref{restate} we have
 \begin{align}
@@
 %We know that $\tr \in \N$ by \cref{grlpassmp}-\eqref{nassmp} and 
-Now, $r'$ is feasible for the ALP in \eqref{grlp} by \cref{restate}. 
+Now, $r'$ is feasible for the ALP in \eqref{alp} by \cref{restate}.
 Then from \cref{srwalp} it follows that
@@
 \end{align}
-The result now follows from Lemma~\ref{cmt1mn} and Theorem~\ref{mt2mn}.
+The result now follows from \Cref{cmt1mn} and \Cref{mt2mn}.
 \end{proof}
@@
 \end{comment}
+\begin{theorem}[Constraint Sampling]
+Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
+$W_{s'a,i}=\delta_{s=s'}$.
+Then
+$
+|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
+$
+\end{theorem}
+
+\begin{proof}
+Let $r_{e_s,J^*}$ and ${r}'_{e_s,J^*}$ be solutions to the linear programs in \eqref{lubplp} and \eqref{alubplp} respectively for $c=e_s$ and $J=J^*$.
+It is easy to note that $r_{e_s,J^*}$ is feasible for the linear program in \eqref{alubplp} for $c=e_s$ and $J^*$, and hence it follows that $(\Phi r_{e_s,J^*})(s)\geq (\Phi {r}'_{e_s,J^*})(s)$.
+However, since the constraints with respect to state $s$ have been chosen we know that $(\Phi {r}'_{e_s,J^*})(s)\geq J^*(s)$.
+The proof follows from noting that $(\Gamma J^*)(s)=(\Phi r_{e_s,J^*})(s)$ and $\hg J^*(s)=(\Phi {r}_{e_s,J^*})(s)$.
+\end{proof}

### 2017-02-04 grlp.tex
fresh changes

@@
 \begin{comment}
-\section{Approximate Linear Programming: Successes and Challanges}
+\section{Approximate Linear Programming: Successes and Challenges}
 When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}.
@@
 \end{align*}
+
 \end{theorem}
@@
 \begin{theorem}[Error Bound for RLP]
-If $\tilde{r}_{RLP}$ is a solution to the RLP, then
+Let $\mu_{u^*}\eqdef(1-\alpha)c^\top (I-\alpha P_{u^*})^{-1}$ be a probability distribution (of discounted number of visits) over the states $S$.
+Define $\psi_{u^*}$ to be the distribution amongst state-action pairs such that $\psi(s,a)\eqdef \frac{\mu_{u^*}}{d}$ and define $\theta\eqdef=\frac{1+\alpha}{2 c^\top J^*}\underset_{r\in \N}{\sup}\parallelJ^*-\Phi r \parallel_\infty$.
+Then for a given $\epsilon>0$ and $\delta>0$ it holds that
 \begin{align*}
@@
 \end{align*}
+for all $m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln \frac{2}{\delta}\big)$.
 \end{theorem}
@@
 \end{comment}
-\section{Main Results}
-\begin{comment}
+\section{Generalized Reduced Linear Programming}\label{sec:grlp}
 The Generalized Reduced Linear Program is given as:
@@
 \end{align}
-where we assume that $W \in \R^{nd\times m}_+$ is a matrix with all positive entries, $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution and $\tr \in \N$.
-\footnote{The appendix explains how $\N$ can be chosen.}
-In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.\par
-\end{comment}
-%\subsection{Novel Projection Operators}
+where we assume that $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints.
+The RLP \eqref{rlp} can be recovered as a special case of the GRLP \eqref{grlp} by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$.
+The $\N$ in the RLP \eqref{rlp} is retained in the GRLP \eqref{grlp} as well.
+For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as the ALP.
+We denote an arbitrary solution to the GRLP by $\hr$, and the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t.
+$\hj$.\par
+The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation.
+To understand this, we need to look at the Lagrangian of the ALP and GRLP in
+\eqref{lag} and \eqref{lag2} respectively, i.e.,
+\begin{align}\label{lag}
+\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
+\end{align}
+Thus, when $Wq = \lambda$, i.e., when $W$ is a set of basis functions that allow
+a low dimensional linear representation of the dual variables $\lambda$,
+the two problems are the same.
+%Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers.
+Hence, while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
+%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
+To get a sense of how $W$ should be chosen, recall that
+the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e.,
+\begin{align}
+\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
+&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
+\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
+\end{align}
+where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$) \cite{dolgov}.
+Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.
+\FloatBarrier
+\input{cartoon}
+\Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively.
+The error in the ALP solution has already been studied in \cite{ALP}.
+Our objective is to study the extra source of error due to constraint approximation.
 We now define two projection operators which are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
+\section{Main Results}
+In this section we present the main results of this paper in \Cref{cmt2} (we state improved bounds in \Cref{sec:improv}).
+Our bounds are expressed in terms of two novel contractions operators which we define in \Cref{lubpop,alubpop}.
 %The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
@@
 \end{definition}
-
-%The approximate least upper bound (ALUB) projection operator $\hg \colon \R^n \ra \R^n$ is defined as below:
 The definition of the second operator is as follows:
@@
 \end{remark}
-
-%\input{cartoon}
 \subsection{Error Bounds}
@@
 \label{cmt2}
-%Let $\hj$, $\hv$, $r^*$ and $J^*$ be as in Theorem~\ref{mt2mn}, then
-It holds that
-\begin{align}\label{finalbnd}
-\begin{split}
-||J^*-\hj||_{1,c}
-\leq\frac{1}{1-\alpha}(6 ||J^*-\Phi r^*||_{\infty}
-+2||\Gamma J^*-\hg J^*||_{\infty}).
-\end{split}
-\end{align}
+Let $\one\in\R^k$ be in the column span of $\Phi$, then it holds that
+\begin{enumerate}
+\item The prediction error is bound as\\
+$||J^*-\hj||_{1,c}
+\leq\frac{1}{1-\alpha}(6~\us{\min}{r\in \R^k}||J^*-\Phi r||_{\infty}
++2||\Gamma J^*-\hg J^*||_{\infty})$.
+\item The control error is bound as\\
+$\norm{J^* - J_{\hu}}_{1,c}
+\leq 2\left(\frac{1}{(1-\alpha)^2}\right)\, \big( 2~\us{\min}{r\in \R^k} ||J^*-\Phi r||_{\infty}
++||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big)$.
+\end{enumerate}
 \end{theorem}
+\textbf{On Prediction Error:}The first factor in the right hand side of the prediction error in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
+This term is inherent to the ALP formulation as shown in \Cref{alpvanilla}.
+The second factor in the right hand side of the prediction error is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
+It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
+\textbf{On Control Error:} The first two terms are quite similar to those in the bound for prediction error.
+The third term occurs due to the fact that $\Phi \geq T\Phi r$ that holds in the case of ALP does not hold in the case of GRLP.\par
 \begin{comment}
@@
 \end{theorem}
-\begin{comment}
-An interesting feature is that unlike prior work on constraint sampling based on concentration inequalities (e.g.,  \cite{CS}), our analysis is based on contraction operators and is completely deterministic.
-In particular, the error term $\etmn$ gives new insights into constraint selection:
-The result of Theorem~\ref{st} is that
-\end{comment}
-%The modified $L_\infty$ norm in \eqref{finalbndmn} comes to our rescue to control the error due to those states that are not chosen.
+It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$ and \Cref{cmt2} does not have these limitations.
+In addition, from \Cref{st}, we know that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
+This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.

### 2017-02-04 intro.tex
fresh changes

@@
 %!TEX root =  autocontgrlp.tex
+\section{Introduction}
+The  framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems arising in science and engineering.
+By casting a given decision problem as an MDP, the goal then is to find an optimal policy ($u^*$) which is the best decision rule.
+The so-called dynamic programming (DP) methods find an optimal policy by computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states.
+The value function $J^*$ stands for the cumulative return of making decisions according to $u^*$.
+Conventional DP  techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB} can compute the exact value of $J^*$.
+However, a shortcoming of these conventional methods is that their computational overhead grows with the number of states, a practical hindrance when the MDP has a large number of states.\par
+In this paper we consider the problem of using dynamic programming with MDPs with large state spaces.
+A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$, and a sub-optimal policy $\tu$ can be obtained using $\tj$.
+The sub-optimal policy can then be used to make the decision and results in a cumulative return given by $J_{\tu}$.
+The idea here is forsake optimality to gain computational tractability.
+The success depends on the quality of approximation, i.e., on the quantities $||J^*-\tilde{J}||$ and $\norm{J^*-J_{\tu}}$ ($\norm{\cdot}$ is an appropriate norm) known as prediction error and the control error respectively.\par
+Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation.
+Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.\par
+The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation.
+A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable.
+A way out is to choose a subset of constraints at random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP).
+The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}.
+An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was also found useful in experiments.
+However, to this date, there exist no theoretical guarantees bounding the loss in performance resulting from such an approximation.
+In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
+The salient aspects of our contribution are listed below:
+\begin{enumerate}
+\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}).
+\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).
+\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
+\item Our analysis also makes use of arguments based on \emph{Lyapunov} function, an approach much similar to prior works in ALP literature \cite{ALP,SALP}.
+\item Our results on the GRLP are the first to theoretically analyze the use of linear function approximation of Lagrangian (dual) variables underlying the constraints.
+\item A numerical example in controlled queues is provided to illustrate the theory.
+\end{enumerate}
+A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.
+\begin{comment}
 \section{Introduction}
@@
 In more general terms, given any MDP,
-We are interested in computing what is known as the optimal policy $u^*$ (a map from $S$ to $A$).
-The so-called dynamic programming (DP) methods first compute what is known as the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states, and use it to compute $u^*$.
+An optimal policy $u^*$ is a map from $S$ to $A$ that results in the best cumulative reward that can be obtained by starting from any state.
+The rewards for the various The so-called dynamic programming (DP) methods first compute what is known as the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states, and use it to compute $u^*$.
 When the number of state is small conventional DP techniques, such as value-, or policy-iteration, or linear programming (LP) can be used to compute $J^*$ and $u^*$\cite{BertB}.\par
-As the number of states is grows, it becomes increasingly difficult to compute the exact values of $J^*$ and $u^*$.
+Curse-of-dimensionality  refers to the fact that the number of states grows exponentially in the number of state variables. Many practical systems such as controlled queues, inventory control etc are
+afflicted by the curse, i.e., have large number of states.
+In such scenarios, it becomes increasingly difficult to compute the exact values of $J^*$ and $u^*$ because the DP methods are based on computations involving as many (or even more) number of variables as the number of states.
 A practical solution then is to compute an approximate value function $\tilde{J}$ instead of $J^*$.
@@
 %Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm.\par
-Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation.
-Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.\par
+Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi \tr$ where $\Phi \in \R^{|S|\times k}$ is a so-called feature matrix and $\tr*\in \R^k$ is a weight vector (to be computed), is the most widely used method of approximation.
+Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states ($k<<|S|$), holding the promise of being able to work with MDPs regardless of the number of states.\par
 It is natural to expect that approximations lead to errors and it is important to quantify the errors.
@@
 \par
-
 %While many ADP methods use LFA, not all of them are successful.
@@
 
-The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants combine LFA and the LP approach. Theoretical performance analysis of the ALP can be found in \cite{ALP}.
+The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce LFA in the linear programming formulation to dynamic programming.
+Theoretical performance analysis of the ALP can be found in \cite{ALP}.
 %and a salient feature is that it does not suffer from issues such as `policy oscillations'\footnote{ADP methods that use linear least squares projection are known to exhibit `policy oscillations' %\cite{BertB}, i.e., output a repeating sequence of bad sub-optimal policies.
 Since our focus in this paper is the ALP formulation, we refrain from a detailed presentation of the other methods.}
-
-A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable.
-Two approaches have been found empircally successful in addressing the issue of large number of constraints in the ALP.
-In the first approach, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear program} (RLP).
+The number of variables of the ALP is only $k$, a critical shortcoming of the ALP is that the number of constraints are of the order of the size of the state space, making it intractable.
+Two approaches have been found empirically successful \cite{CS,dolgov,ALP-Bor} in addressing the issue of large number of constraints in the ALP.
+In the first approach \cite{CS}, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear programming} (RLP) problem.
 The performance analysis of the RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions.
@@
 However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach.\par
+
 Our motivation stems from the fact that ALP with tractable number of constraints will result in a full dimeniosnality free ADP method.
@@
 \begin{enumerate}
-\item We define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
+\item We define a generalized reduced linear programming (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
 The GRLP amounts to linear function approximation of the dual variables, and the RLP is a special case of GRLP.
-		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}). 
+\item We develop a novel analytical machinery to bound the prediction error $\norm{J^*-\hj}$ where $hj$ is the solution to the GRLP.
 		\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).
 		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
-%Our analysis also makes use of arguments based on \emph{Lyanpunov} function, an approach much similar to prior works in ALP literature \cite{ALP,SALP}.
-\item Our results on the GRLP are the first to theoretically analyze the use of linear function approximation of Langrangian (dual) variables underlying the constraints.
+%Our analysis also makes use of arguments based on \emph{Lyapunov} functions, an approach much similar to prior works in the ALP literature \cite{ALP,SALP}.
+\item Our results on GRLP are the first to theoretically analyze the use of linear function approximation of Lagrangian (dual) variables underlying the constraints.
 \item A numerical example in controlled queues is provided to illustrate the theory.
@@
 %ALP with tractable number of constraints would result in  a full dimensionality free ADP method, without issues such as policy oscillations.
-A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.
+A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}. The rest of the paper is organized as follows:
+\end{comment}

### 2017-02-04 intro_bkp.tex
fresh changes

%!TEX root =  autocontgrlp.tex
\section{Introduction}
Markov decision processes (MDPs) are a powerful mathematical framework to study optimal sequential decision making problems arising in science and engineering. Typically, the configuration of the underlying environment is known as the state and in decisions are chosen from a set of actions. Given an MDP, the objective is to compute a useful \emph{policy} $u$ (we defer a more formal definition to later) which is specifies the action selection mechanism, i.e., maps each and every state of the system to a corresponding action. The effectiveness of a policy $u$ is indicated by a corresponding value function $J_u$, a vector whose dimension is the number of states. The so-called dynamic programming methods find an optimal (best) policy $u^*$ by computing the optimal \emph{value-function} ($J^*$). MDPs with small number of states can be solved easily by conventional dynamic programming techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB}.\par

The paradigm of approximate dynamic programming (ADP) deals with the problem of using dynamic programming with MDPs with large state spaces. In practice, ADP methods handle the issue of large number of states by computing an approximate value function $\tilde{J}$ instead of $J^*$.
Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation. Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.
\todoch{Mention objectives}
Given a fixed LFA (i.e., a fixed $\Phi$), ADP methods vary in the manner in which they compute $\tilde{J}=\Phi r^*$. The so called projected Bellman equation (PBE) based methods compute $r^*$ by solving a fixed point equation. However, a downside to the PBE based methods is that they exhibit divergent behavior leading to a oscillatory policy behaviour \cite{BertB}. The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation. The vanilla ALP method computes an approximate value function $\tilde{J}$ and an approximate policy $u$. A salient feature that the ALP methods enjoy over the PBE based methods is that they do not suffer from the issue of policy oscillation. In addition, the ALP method has good performance guarantees i.e., the error terms $\parallel J^*-\tj\parallel$ (error in approximating value function) and $\parallel J^*-J_{\tilde{u}}\parallel$ (loss in perfromance i.e., the sub-optimality of $\tilde{u}$ as opposed to $u^*$).\par
\todoch{Mention all the works including Malek's and the open problem we wish to address}
\todoch{Add the table with tick and cross and the cartoon}
A critical shortcoming of the vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable. Typically, a way out is to choose a subset of constraints at random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP). The performance analysis of the RLP under idealized assumptions (of the knowledge of the optimal policy) can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}. An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was also found useful in experiments. However, to this date, there exist no theoretical guarantees bounding the loss in performance resulting from such an approximation. The dual ALP formulation has been studied in \cite{abbasi}, however without addressing the limitation posed by the large number of constraints.\par
\todoch{Mention Motivation and Challanges}
\todoch{Use of Lyanpunov analysis}
In this paper, we focus on constraint approximation, an aspect of the ALP which has not been well understood in the literature. In particular, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
The salient aspects of our contribution are listed below:
\begin{enumerate}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}). 
		\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).
		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
\item Our analysis also makes use of arguments based on \emph{Lyanpunov} function, an approach much similar to prior works in ALP literature \cite{ALP,SALP}.
		\item Our results on the GRLP are the first to theoretically analyze the use of linear function approximation of Langrangian (dual) variables underlying the constraints.
		\item A numerical example in controlled queues is provided to illustrate the theory.
\end{enumerate}
A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.

### 2017-02-04 mdp.tex
fresh changes

@@
 %!TEX root =  autocontgrlp.tex
-\section{Markov Decision Processes (MDPs) and Linear Programming}
-We consider MDPs with a finite state space $S=\{1,2,\ldots,n\}$ and finite action space $A=\{1,2,\ldots,d\}$, where the sentiment is that $n$ is large.
+\section{Background: Markov Decision Processes (MDPs)}
+The framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems in stochastic environments.
+In this section, we present a brief overview of the MDP framework, introducing the notions of policy, value function and optimality (please refer to \cite{BertB} for a detailed presentation on MDP).\par
+\textbf{Model:} We consider an MDP with a finite state space given by $S=\{1,2,\ldots,n\}$ and a finite action space given by $A=\{1,2,\ldots,d\}$ (where the sentiment is that $n$ is large).
 For simplicity, we assume that all actions are feasible in all states.
 The probability transition kernel $P$ collects the probabilities $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$ for all possible $s,s'\in S$ and $a\in A$.
-We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
-A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
-Given an SDP $u$, the expected total discounted reward corresponding to starting at state $s$, while choosing actions as dictated by $u$ for the states encountered, is
+We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\par
+\textbf{Policy:} A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
+Under an SDP, an MDP is a Markov chain whose probability transition matrix is denoted by $P_u$.\par
+\textbf{Value Function:} Given an SDP $u$, the expected total discounted reward corresponding to starting at a state $s\in S$ at $t=0$, while choosing actions as dictated by $u$ for the states encountered in the future (i.e., $t>0$), is
 \begin{align}
-J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n)\mbox{ }\forall n\geq 0],\nn
+J_u(s)\stackrel{\Delta}{=}\E[\sum_{t=0}^\infty \alpha^t g_{a_t}(s_t)|s_0=s,a_t=u(s_t)\mbox{ }\forall t\geq 0],\nn
 \end{align}
-where $\alpha \in (0,1)$ is the so-called discount factor and $s_{n+1} \sim p_{a_n}(s_n,\cdot)$, $n\ge 0$. 
+where $\alpha \in (0,1)$ is the so-called discount factor and $s_{t+1} \sim p_{a_t}(s_t,\cdot)$, $t\ge 0$.
 We call $J_u(s)$ the value of state $s$ under SDP $u$, while $J_u$ (as a map from $S$ to the reals)
 is called the value function underlying policy $u$.
-The \emph{optimal policy} $u^*$ is one that in each state $s\in S$ achieves the best possible total expected discounted reward from that state.
-That is, $J^{u^*}(s) = J^*(s) \eqdef \max_{u\in U} J_u(s)$
-where $U$ is the set of all SDPs and $J^*$ is coined the \emph{optimal value function}.%
-\footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.}, 
-Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$,
+The value functions $J_u$ is an elements of $\R^S$.
+In what follows it will be useful for us to treat it as an $n$-dimensional vector, i.e., an element of $\R^n$, effectively identifying $\R^S$ with $\R^n$ in the natural way.
+Similarly we identify $\R^{nd}$ with $\R^{S\times A}$, where $d=|A|$.\par
+\textbf{Optimality and the Bellman Equation:} The \emph{optimal policy} $u^*$ is one that in each state $s\in S$ achieves the best possible total expected discounted reward from that state.
+That is, $J_{u^*}(s) = J^*(s) \eqdef \us{\max}{u\in U} J_u(s)$
+where $U$ is the set of all SDPs and $J^*$ is coined the \emph{optimal value function}.
+\footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.}
+Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE) which states that for all $ s \in S$,
 \begin{subequations}\label{bell}
 \begin{align}
-\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
-\label{bellpol}u^*(s)&= \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
+\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),~\text{and}\\
+\label{bellpol}u^*(s)&= \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),\,.
 \end{align}
 \end{subequations}
-Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}
-for each state relatively cheaply (e.g., having the ability to sample from the next-state distribution at
-a given state-action pair).
-Thus computing the value function is at the heart of most solution methods to MDP.\par
-%\subsection{Linear Programming}
-As it is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
-\begin{align}\label{mdplp}
-\begin{split}
-\min_{J\in \R^n}\, &c^\top J\,\,\text{s.t.}\\
-%\mb
-J(s)&\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
-\forall (s,a)\in S\times A,
-\end{split}
-\end{align}
-where $c$ is \emph{any} vector of $\R^n$ such that $c(s)>0, \forall s \in S$.
-Without loss of generality, we may and will assume in what follows that $\sum_{s\in S}c(s)=1$, i.e., $c$ is a probability distribution over $S$.\par
-%\subsection{Notation}
-The value functions $J^u$ or $J^*$ are elements of $\R^S$.
-In what follows it will be useful for us to treat these as $n$-dimensional vectors, i.e., elements of $\R^n$, effectively identifying $\R^S$ with $\R^S$ in the natural way.
-Similarly we identify $\R^{nd}$ with $\R^{S\times A}$.
-The following definitions will be useful later:
-%The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
-\begin{definition}Define
+where ties in \eqref{bellpol} are resolved arbitrarily.\par
+We now present some definition which will be useful later:
+\begin{definition}\label{notations}
 \begin{comment}
@@
 \begin{enumerate}[(i)]
-\item The Bellman operator $T\colon \R^n \ra \R^n$ as $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
+\item The Bellman operator $T\colon \R^n \ra \R^n$ is given by $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
 $
-\item \label{bellactval} The Bellman operator (of action values) $H: \R^n \to \R^{nd}$ for state-action values as $HJ=[ H_1 J,\cdots,H_d J]^\top\in \R^{nd},$ where $(H_a J)(s)= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s')$.
-\begin{comment}
-\item
-||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
-\item The discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
-\item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
-\end{comment}
-\item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
-\item A policy $u_J$ is said to be greedy with respect to (w.r.t.) $J\in \R^n$ if for any $s\in S$,
+\item \label{bellactval} The Bellman operator (of action values) $H: \R^n \to \R^{nd}$ for state-action values is given by $HJ=[ H_1 J,\cdots,H_d J]^\top\in \R^{nd},$ where $(H_a J)(s)= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s')$.
+\item\label{emat} The $nd\times n$ matrix $E$ is given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
+\item\label{greedy} A policy $u_J$ is said to be greedy with respect to (w.r.t.) $J\in \R^n$ if for any $s\in S$,
 %some function $\tj:S \to \R$
-\begin{align*}u_J(s)\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J(s')\big).\end{align*}
-\item The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ with respect to a probability distribution $c$ as $
+\begin{align*} u_J(s)\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S} p_a(s,s')J(s')\big).\end{align*}
+\item\label{norms} The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ with respect to a probability distribution $c$ is given by $
 ||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|$.
@@
 and $\norm{\cdot}_{\infty,\rho}$, $\parallel J\parallel_{\infty}=\max_{s\in S}|J(s)|$ and $||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
-\item $J_1\leq J_2$, when $J_1(s)\leq J_2(s),~\forall s\in S$.
-\item $\one\in \R^n$ to be the vector whose all coordinates are $1$.
+\item For $J_1, J_2\in \R^n$ we write $J_1\leq J_2$ when $J_1(s)\leq J_2(s),~\forall s\in S$.
+\item We define $\one\in \R^n$ to be the vector whose coordinates are all equal to $1$.
 \end{enumerate}
 \end{definition}
+We would like to point out that from \Cref{notations}, it follows that for any $J\in \R^n$ the condition $J\geq TJ$ can be rephrased as $EJ\geq HJ$.
+\subsection{Dynamic Programming: Objective and Methods}
+Once a given sequential decision making is cast in the MDP framework, it remains for us to still compute the optimal policy $u^*$.
+The idea behind Dynamic Programming (DP) methods is to use the BE \eqref{bellval} to first compute $J^*$, and then a near-optimal action $u^*$ can be obtained via \eqref{bellpol}
+for each state relatively cheaply even for large state-spaces (e.g., having the ability to sample from the next-state distribution at
+a given state-action pair).
+Thus computing $J^*$ is at the heart DP methods \cite{BertB} such as value-, or policy-iteration and linear programming (LP) \eqref{mdplp} which can be used in practice when the MDP has a tractable number of states.
+However, when the MDP has a large number of states, using DP methods to obtain $J^*$ is tedious, since they involve computations in variables that are of the order of the number of states.\par
+Approximate dynamic programming (ADP) methods are based on DP methods, but employ (value) function approximation to ease the computational overhead encountered in MDPs with a large number of states.
+In particular, linear function approximation (LFA) has been used widely, wherein, $J^*$ is approximated by $J^*\approx\tj =\Phi \tr$, where $\Phi$ is an $n\times k$ feature matrix and $\tr\in \R^n$ is a weight vector (to be computed).
+Thus the solution is searched in the subspace spanned by the column vectors of $\Phi$.
+The linear representation helps in two ways.
+Firstly, given any state $s$, its approximate value can be recovered as $\tj(s)=\phi(s) \tr$ (where $\phi(s)$ is the $s^{th}$ row of $\Phi$).
+Secondly, a greedy policy $\tilde{u}=u_{\tj}$ (see \Cref{notations}-\eqref{greedy}) can be found using the approximate value function.
+Note that all computations are $O(k)$ which is independent of the number of states.\par
+It is natural to expect that approximations lead to errors and it is important to quantify the errors.
+For a given ADP method, theoretical performance analysis involves  bounding the error terms $||J^*-\tilde{J}||$  and $\norm{J^*-J_{\tu}}$ which denote the error in approximating the value function, and performance loss due to following policy $\tu$ respectively (where $\norm{\cdot}$ is an appropriate norm).
+Further, in most cases the error terms reveal some structure that can offer insights and act as guide to the designer of the ADP method (for example the choice of $\Phi$).
+The focus of this paper is to present the error analysis for generalized reduced linear programming (GRLP), a new ADP formulation which we introduce in \Cref{sec:grlp}.

### 2017-02-04 prob.tex
fresh changes

@@
-\section{Problem Setup}
-We now present the linear programming (LP), approximate linear programming (ALP) and the generalized reduced approximate linear programming (GRLP) respectively.
-In what follows, $c>0\in \R^n$ is a probability distribution.
-It is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
+\section{Linear Programming for MDP}
+In this section, we review relevant results \cite{BertB,ALP,CS} in the linear programming approach to MDPs.
+Throughout the rest of the paper, we let $c>0\in \R^n$ to denote a probability distribution over the state space S.\par
+\begin{comment}
+%first present linear programming (LP), approximate linear programming (ALP) and reduced linear programming (RLP) respectively.
+The LP is an exact method in that it computes $J^*$ and the other two methods (ALP and RLP) are approximate methods that are based on introducing LFA in LP.
+We then discuss prior literature that have analyzed the approximation errors in ALP and RLP.
+Finally, we present the open question that we wish to understand in this paper.
+\end{comment}
+\textbf{Linear Programming (LP)}: It is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
 \begin{align}\label{mdplp}
+&\text{LP:~}\min_{J\in \R^n}\,c^\top J\,\,\\
+%\mb
+&J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
+\forall (s,a)\in S\times A,\nn
+\end{align}
+\textbf{Approximate Linear Programming (ALP)} is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
+By substitution, this leads to
+\begin{flalign}\label{alp}
 \begin{split}
-\min_{J\in \R^n}\, &c^\top J\,\,\text{s.t.}\\
+\text{ALP:}& \min_{r\in \R^k}\, c^\top \Phi r\\
+& \Phi r\geq T \Phi r,
+\end{split}
+\end{flalign}
+where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}.
+Note that, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
+In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}.\par
+A detailed theoretical analysis of ALP can be found in \cite{ALP}.
+However, we restate (from \cite{ALP}) a useful preliminary\footnote{The improved error bounds in \cite{ALP} as well as in \Cref{sec:improv} of this paper are in a weighted $L_\infty$ norm (see \Cref{notations}-\eqref{norms}).} performance bound for ALP as follows:
+\begin{theorem}[Error Bound for ALP]\label{alpvanilla}
+Let $\one\in \R^k$ belong to the column span of $\Phi$ and let $\mu_u\eqdef (1-\alpha)c^\top\top(I-\alpha P_u)^{-1}$ be a probability distribution over $S$ induced by a policy $u$.
+Then it follows that
+\begin{enumerate}
+\item\label{alppe} The prediction error is bounded as $||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty$.
+\item\label{alpce} The control error is bounded as $||J^*-J_{\tu}||_{1,c}\leq \frac{2}{1-\alpha}||J^*-\tj||_{1,\mu_{\tu}}$.
+\end{enumerate}
+\end{theorem}
+The gist of \Cref{alpvanilla}-\eqref{alppe} is that the prediction error $||J^*-\tj||_{1,c}$ of ALP is worse utmost by a constant factor than the best possible error that can be achieved using the span of $\Phi$.
+Further from \Cref{alpvanilla}-\eqref{alpce} the control error is worse utmost by a constant factor than the prediction error.\par
+\textbf{Reduced Linear Programming (RLP)} is formulated by retaining only $m$ out of the $nd$ ($m<<nd$) constraints of ALP.
+RLP is easier to solve compared to ALP due to the reduced number of constraints.
+\begin{align}\label{rlp}
+\begin{split}
+&\text{RLP:~}\underset{r\in \N\subset R^k}{\min}\, c^\top \Phi r\,\,\\
 %\mb
-J(s)&\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
-\forall (s,a)\in S\times A,
+&\Phi r (s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')\Phi r(s'),\,\,
+\forall (s,a)\in \I,
 \end{split}
 \end{align}
+where $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$ and $\N$\footnote{The appendix explains how $\N$ can be chosen analytically.} is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}.
+We denote an arbitrary solution to the RLP by $\tr_{RLP}$.\par
+We now state a useful result from \cite{CS} that characterizes the performance analysis RLP as follows:
+\begin{theorem}[Error Bound for RLP]\label{rlpt}
+Let $\mu_{u^*}\eqdef(1-\alpha)c^\top (I-\alpha P_{u^*})^{-1}$ be a probability distribution (of discounted number of visits) over the states $S$.
+Define $\psi_{u^*}$ to be the distribution over the state-action pairs such that $\psi(s,a)\eqdef \frac{\mu_{u^*}}{d}$ and define $\theta\eqdef\frac{1+\alpha}{2 c^\top J^*}\underset{r\in \N}{\sup}\parallel J^*-\Phi r \parallel_\infty$.
+Then for a given $\epsilon>0$ and $\delta>0$ it holds with probability greater than $1-\delta$ that
+\begin{align*}
+||J^*-\Phi\tilde{r}_{RLP}||_{1,c}\leq ||J^*-\Phi\tilde{r}||_{1,c}+\epsilon ||J^*||_{1,c}
+\end{align*}
+for all $m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln \frac{2}{\delta}\big)$.
+\end{theorem}
+The gist of \Cref{rlpt} is that when `sufficient' number of samples are retained using a specialized distribution ($\psi_{u^*}$), then with high probability, the prediction error of RLP and ALP differ only by a small factor (i.e., $\epsilon\norm{J^*}_{1,c}$).\par
+A major weakness of \Cref{rlpt} is that it holds only for RLP formulated using $\psi_{u^*}$ which is impractical since $u^*$ is unknown in general.
+However, empirical studies \cite{ALP,CS,CST} have shown that RLP formulated with other sampling distributions do perform well in experiments.
+In this context, another interesting approach is linear approximation of the dual variables \cite{dolgov}, which also is known to work in experiments but without any theoretical guarantees.
+These fact hint to the fact that the theoretical understanding of RLP and constraint sampling/approximation needs to be improved.
+Further, such theoretical understanding will justify that ALP with constraint reduction is a fully dimensionality free method in that the problem variables as well as constraints are independent of the number of states of the MDP.
 \begin{comment}
-When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy ite
-ration \cite{BertB}.
-A practical solution is to resort to function approximation.
-Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$.\par
-\end{comment}
-The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
-By substitution, this leads to
-\begin{align}\label{alp}
-\begin{split}
-\min_{r\in \R^k}\, &c^\top \Phi r\,\,\,
-\text{s.t.}\mb \Phi r\geq T \Phi r,
-\end{split}
-\end{align}
-where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $\Phi$ is a feature matrix whose first column is $\one$.
 The Generalized Reduced Linear Program is given as:
@@
 \begin{split}
-&\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
-&\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
+&\text{GRLP:~}\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
+&  \,W^\top E\Phi r\geq W^\top H \Phi r.
 \end{split}
 \end{align}
-Unless specified otherwise we use $\hr$/$\tr$ to denote an arbitrary solution to the GRLP/ALP.
-In similar spirit, and we let $\hj=\Phi \hr$/$\tj=\Phi \tr$ to denote the corresponding value functions and $\hu$/$\tu$ to denote the greedy policy w.r.t.
-$\hj$/$\tj$.\par
-\textbf{Remarks:}
+\end{comment}
+\begin{comment}
 \begin{enumerate}
-\item When the MDP has a large number of states, it is difficult to solve for $J^*$ using either the linear program \eqref{mdplp} or other full state representation methods such as value iteration or policy iteration \cite{BertB}.
-A practical solution is to resort to function approximation.
-Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$.
-For $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
-\item $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints.
-$\N$ is a compact set such that $\tr \in \N$.
-This additional constraint set ensures the boundedness of the solution.
+
+\item In \eqref{mdplp}, \eqref{alp}, \eqref{rlp} and \eqref{grlp} $c>0 \in \R^n$ is a probability distribution.
+\item The ALP \eqref{alp} is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
+Note that in \eqref{alp}, $Phi r\geq T\Phi r$ is a shortcut to denote the $S\times A$ constraints.
+Also, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
+We denote an arbitrary solution to the ALP by $\tr\in \R^k$.\par
+\item The RLP \eqref{rlp} was first introduced in \cite{CS}.
+The RLP \eqref{rlp} has the same objective function as the ALP \eqref{rlp}.
+The construction of the RLP needs three parameters to be specified namely, the number of samples $m$, the sampling distribution $\psi$ and the constraint set $\N$.
+In particular, $\psi=\psi(u^*)$ i.e., the sampling distribution
+In the RLP in \eqref{rlp}, $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$.
+The samples are generated using a distribution $\psi$ (see a restatement of the results in \cite{CS} summarized in \Cref{}).
+$\N$ is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}.
+We denote an arbitrary solution to the RLP by $\tr_{RLP}$.
+It is important to note that the RLP \eqref{rlp} is a random linear program, in the sense that it depends on the $m$ samples obtained from $\psi$.
+\item In the GRLP in \eqref{grlp}, $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints.
+The RLP \eqref{rlp} can be recovered as a special case of the GRLP \cite{grlp} by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$.
+The $\N$ in the RLP \eqref{rlp} is retained in the GRLP \eqref{grlp} as well.
 For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as the ALP.
+We denote an arbitrary solution to the GRLP by $\hr$.
 \end{enumerate}
+In what follows, unless specified otherwise we use let $\hj=\Phi \hr$/$\tj=\Phi \tr$ to denote the corresponding value functions and $\hu$/$\tu$ to denote the greedy policy w.r.t. $\hj$/$\tj$.\par
 \FloatBarrier
@@
 \Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively.
-The erorr in the ALP solution has already been studied in \cite{ALP}.
-Our objective is to study the extra source of error due to constriant approximation.
+The error in the ALP solution has already been studied in \cite{ALP}.
+Our objective is to study the extra source of error due to constraint approximation.
+\end{comment}
 \begin{comment}

### 2017-02-04 rel.tex
fresh changes

@@
-\subsection{Comparison With Related Work}
-In order to interpret the resutls in \Cref{cmt2} and \Cref{st}, we now dicuss relevant prior work.
+\begin{comment}
+In order to interpret the results in \Cref{cmt2} and \Cref{st}, we now discuss relevant prior work.
 We begin by re-stating a preliminary\footnote{The improved error bounds in \cite{ALP} as well as in \Cref{sec:improv} of this paper are in a weighted $L_\infty$ norm and are based on Lyapunov analysis.} error bounds for the ALP from \cite{ALP}:
@@
 \end{theorem}
-\begin{comment}
-
 The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
@@
 In \cite{petrik} the transitional error is reduced ignoring the representational and sampling errors.\par
-\end{comment}
+
 %The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP.
@@
 \begin{theorem}[Error Bound for RLP]\label{rlpt}
-If $\tilde{r}_{RLP}$ is a solution to the RLP, then
+Let $\mu_{u^*}\eqdef(1-\alpha)c^\top (I-\alpha P_{u^*})^{-1}$ be a probability distribution (of discounted number of visits) over the states $S$.
+Define $\psi_{u^*}$ to be the distribution over the state-action pairs such that $\psi(s,a)\eqdef \frac{\mu_{u^*}}{d}$ and define $\theta\eqdef\frac{1+\alpha}{2 c^\top J^*}\underset{r\in \N}{\sup}\parallel J^*-\Phi r \parallel_\infty$.
+Then for a given $\epsilon>0$ and $\delta>0$ it holds with probability greater than $1-\delta$ that
 \begin{align*}
@@
 \end{align*}
+for all $m\geq \frac{16d\theta}{(1-\alpha)\epsilon}\big(k\ln\frac{48d\theta}{(1-\alpha)\epsilon}+\ln \frac{2}{\delta}\big)$.
 \end{theorem}
-\textbf{Remarks:}
-The first factor in the right hand side of \eqref{finalbnd} in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
-This term is inherent to the ALP formulation as shown in \Cref{alpvanilla}.
-The second factor in the right hand sie of \eqref{finalbnd} is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
-It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$ and \Cref{cmt2} does not have these limitations.
-In addition, from \Cref{st}, we know that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
-This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
+\end{comment}
 \begin{comment}
@@
 \end{comment}
-\subsection{Primal-Dual Approximation}
-The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation.
-To understand this, we need to look at the Lagrangian of the ALP and GRLP in
-\eqref{lag} and \eqref{lag2} respectively, i.e.,
-\begin{align}\label{lag}
-\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
-\end{align}
-Thus, when $Wq = \lambda$, i.e., when $W$ is a set of basis functions that allow
-a low dimensional linear representation of the dual variables $\lambda$,
-the two problems are the same.
-%Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers.
-Hence, while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
-%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
-To get a sense of how $W$ should be chosen, recall that
-the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e.,
-\begin{align}
-\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
-&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
-\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
-\end{align}
-where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$) \cite{dolgov}.
-Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.
-
 \begin{comment}

### 2017-02-27 errana.tex
addressed the comments by Csaba

@@
 \end{comment}
-\begin{lemma}\label{tprop}
+\begin{lemma}\label{tprop} The following hold:
 \begin{enumerate}[(i)]
@@
 $
-||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
+\norm{TJ_1-TJ_2}_\infty\leq \alpha \norm{J_1-J_2}_\infty.
 $
@@
 \begin{definition}\label{def:lyap}
-Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$, define
-\begin{enumerate}[(i)]
-\item The discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
-\item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
-\end{enumerate}
+Let $c,\rho,\chi:S \to \R_+$ be positive-valued functions. Then for $J\in \R^n$, $a\in A$ and $s\in S$, define
+the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
+The function $\chi:S\to\R_+$ is a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
 \end{definition}
@@
 \end{assumption}
-The error bounds for the ALP in \cite{ALP} are expressed in terms of $\frac{1}{1-\beta_{\psi}}$.
+The authors of \cite{ALP} express the error bounds in terms of $\frac{1}{1-\beta_{\psi}}$.
 A smaller $\beta_{\psi}$ loosely implies `stability' of the the underlying MDP,  with smaller values representative of higher stability.
-Prior works in ALP literature \cite{ALP,SALP,CS} make use of Lyapunov function based analysis to obtain error bounds that exploit the structure of the underlying MDP.
+Prior works in ALP literature \cite{ALP,SALP,CS} make use of Lyapunov functions based analysis to obtain error bounds that exploit the structure of the underlying MDP.
 In particular, the prior bounds suggests that the ALP is likely to generate good approximations when the underlying MDP is stable.
@@
 %\begin{align*}
-%r^*\eqdef\argmin_{r\in R^k}||J^*-\Phi r||_{\mn}\,.
+%r^*\eqdef\argmin_{r\in R^k}\norm{J^*-\Phi r}_{\mn}\,.
 %\end{align*}
@@
 \begin{lemma}\label{bestbndmn}
-Let $r^*\eqdef\underset{r\in \R^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$, then
+Let $r^*\eqdef\underset{r\in \R^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$. Then,
 \begin{align}
-||J^*-\Gamma J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}.
+\norm{J^*-\Gamma J^*}_{\mn}\leq 2 \norm{J^*-\Phi r^*}_{\mn}.
 \end{align}
@@
 $ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$.
-Then from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$.
+Then, from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$.
 From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$.
@@
 \begin{split}
-\min_{r\in \N}\, &||\Phi r-\hv||_{1,c}\,\mb
+\min_{r\in \N}\, &\norm{\Phi r-\hv}_{1,c}\,\mb
 \text{s.t.}\mb \, W^\top E \Phi r\geq W^\top H \Phi r.
@@
 \begin{align*}
-||\Phi r-\hv||_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.
+\norm{\Phi r-\hv}_{1,c}=\sum_{i=1}^n c(i) |(\Phi r)(i)-\hv(i)|=c^\top \Phi r-c^\top \hv\,.
 \end{align*} 
@@
 \begin{split}
-\min_{r\in \R^k}\, &||\Phi r-\hv||_{1,c}\,\mb
+\min_{r\in \R^k}\, &\norm{\Phi r-\hv}_{1,c}\,\mb
 \text{s.t.}\mb \, \Phi r\geq  T \Phi r.
@@
 \begin{align}
-||J^*-\hv||_{\mn}
-& \leq \frac{1}{{1-\beta_{\psi}}}\big(2||J^*-\Phi r^*||_{\mn}
+\norm{J^*-\hv}_{\mn}
+& \leq \frac{1}{{1-\beta_{\psi}}}\big(2\norm{J^*-\Phi r^*}_{\mn}
 \nn\\
-& {}\qquad \qquad+||\Gamma J^*-\hg J^*||_{\mn}\big).
+& {}\qquad \qquad+\norm{\Gamma J^*-\hg J^*}_{\mn}\big).
 \end{align}
@@
 \begin{align*}
-||J^*-\hv||_{\mn}
-& \leq ||J^*-\hg J^*||_{\mn}+||\hg J^*-\hg \hv||_{\mn}\\
-&\leq ||J^*-\hg J^*||_{\mn}+\beta_\psi || J^*- \hv||_{\mn},
+\norm{J^*-\hv}_{\mn}
+& \leq \norm{J^*-\hg J^*}_{\mn}+\norm{\hg J^*-\hg \hv}_{\mn}\\
+&\leq \norm{J^*-\hg J^*}_{\mn}+\beta_\psi \norm{ J^*- \hv}_{\mn},
 \end{align*}
@@
 \begin{align}
- r'= r+||J^*-\Phi r||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0.
+r'= r+\norm{J^*-\Phi r}_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0.
 \end{align}
@@
 \begin{align}
-||\hj-\hv||_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4||J^*-\Phi r^*||_{\mn}\nn
-+||\Gamma J^*-\hg J^*||_{\mn}).
+\norm{\hj-\hv}_{1,c}&\leq \frac{c^\top \psi}{1-\beta_\psi}(4\norm{J^*-\Phi r^*}_{\mn}\nn
++\norm{\Gamma J^*-\hg J^*}_{\mn}).
 \end{align}
@@
 \begin{proof}
-Let $\gamma=||J^*-\Phi r^*||_{\mn}$. 
+Let $\gamma=\norm{J^*-\Phi r^*}_{\mn}$.
 Then, by choosing $r'$ as in \Cref{restate} we have
 \begin{align}
-||\Phi r'-J^*||_{\mn}\nn
-&\leq ||\Phi r^*-J^*||_{\mn}+||\Phi r'-\Phi r^*||_{\mn}\nn\\
+\norm{\Phi r'-J^*}_{\mn}\nn
+&\leq \norm{\Phi r^*-J^*}_{\mn}+\norm{\Phi r'-\Phi r^*}_{\mn}\nn\\
 &=\gamma+\frac{1+\beta_\psi}{1-\beta_\psi}\gamma
@@
 \begin{align}
-||\hj-\hv||_{1,c}
-&\leq||\Phi \tr-\hv||_{1,c}\leq||\Phi r'-\hv||_{1,c}\nn\\
+\norm{\hj-\hv}_{1,c}
+&\leq\norm{\Phi \tr-\hv}_{1,c}\leq\norm{\Phi r'-\hv}_{1,c}\nn\\
 &=\sum_{s\in S}c(s)\psi(s)\frac{|\Phi r'(s)-\hv(s)|}{\psi(s)}\nn\\
-&\leq c^\top \psi ||\Phi r'-\hv||_{\mn}\nn\\
-&\leq c^\top \psi (||\Phi r'-J^*||_{\mn}+||J^*-\hv||_{\mn}).\nn
+&\leq c^\top \psi \norm{\Phi r'-\hv}_{\mn}\nn\\
+&\leq c^\top \psi (\norm{\Phi r'-J^*}_{\mn}+\norm{J^*-\hv}_{\mn}).\nn
 \end{align}
@@
 \begin{split}
-||J^*-\hj||_{1,c}
-&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 ||J^*-\Phi r^*||_{\mn}\\
-&+2||\Gamma J^*-\hg J^*||_{\mn}).
+\norm{J^*-\hj}_{1,c}
+&\leq\frac{c^\top\psi}{1-\beta_\psi}(6 \norm{J^*-\Phi r^*}_{\mn}\\
+&+2\norm{\Gamma J^*-\hg J^*}_{\mn}).
 \end{split}
@@
 \begin{align}
-||J^*-\hj||_{1,c}\nn
-&\leq||J^*-\hv||_{1,c}+||\hv-\hj||_{1,c}\nn\\
-&\leq c^\top \psi ||J^*-\hv||_{\mn}+||\hv-\hj||_{1,c}.\nn
+\norm{J^*-\hj}_{1,c}\nn
+&\leq\norm{J^*-\hv}_{1,c}+\norm{\hv-\hj}_{1,c}\nn\\
+&\leq c^\top \psi \norm{J^*-\hv}_{\mn}+\norm{\hv-\hj}_{1,c}.\nn
 \end{align}
@@
 \begin{align}\label{polthebnd}
-%||J_{\hu}-\hj||_{1,c}
 \norm{J^* - J_{\hu}}_{1,c}
-&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\mn}
+&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2\norm{J^*-\Phi r^*}_{\mn}
 \nn\\&
-+||\Gamma J^*-\hg J^*||_{\mn}+||\hj-\hg\hj||_{\mn}\big).
++\norm{\Gamma J^*-\hg J^*}_{\mn}+\norm{\hj-\hg\hj}_{\mn}\big).
 \end{align}
@@
 \begin{align*}
-||J^*-J_{\hu}||_{1,c}&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\,.
+\norm{J^*-J_{\hu}}_{1,c}&\leq \norm{J^*-\hj}_{1,c}+\norm{J_{\hu}-\hj}_{1,c}\,.
 \end{align*}
@@
 &\leq c^\top(I-\alpha P_{\hu})^{-1}|T\hj-\hj|\nn\\
-&\leq c^\top (I-\alpha P_{\hu})^{-1} \,\psi\, ||T\hj-\hj||_{\mn}\nn\\
-&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-\hj||_{\mn}\nn\\
-%&\leq \frac{c^\top \psi}{1-\beta_{\psi}}||T\hj-TJ^* +J^*- \hj||_{\mn}\nn\\
-&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(||T\hj-TJ^*||_{\mn} +||J^*- \hj||_{\mn})\nn\\
-&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})||J^*- \hj||_{\mn},
+&\leq c^\top (I-\alpha P_{\hu})^{-1} \,\psi\, \norm{T\hj-\hj}_{\mn}\nn\\
+&\leq \frac{c^\top \psi}{1-\beta_{\psi}}\norm{T\hj-\hj}_{\mn}\nn\\
+%&\leq \frac{c^\top \psi}{1-\beta_{\psi}}\norm{T\hj-TJ^* +J^*- \hj}_{\mn}\nn\\
+&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(\norm{T\hj-TJ^*}_{\mn} +\norm{J^*- \hj}_{\mn})\nn\\
+&\leq \frac{c^\top \psi}{1-\beta_{\psi}}(1+\beta_{\psi})\norm{J^*- \hj}_{\mn},
 \end{align}
@@
 \begin{align}
-&||J^*-J_{\hu}||_{1,c}\nn\\
-%&\leq ||J^*-\hj||_{1,c}+||J_{\hu}-\hj||_{1,c}\nn\\
-&\leq c^\top \psi ||J^*-\hj||_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}||J^*- \hj||_{\mn}\nn\\
-&=\frac{2c^\top \psi}{1-\beta_{\psi}}||J^*- \hj||_{\mn}.
+&\norm{J^*-J_{\hu}}_{1,c}\nn\\
+%&\leq \norm{J^*-\hj}_{1,c}+\norm{J_{\hu}-\hj}_{1,c}\nn\\
+&\leq c^\top \psi \norm{J^*-\hj}_{\mn}+c^\top \psi\frac{1+\beta_\psi}{1-\beta_\psi}\norm{J^*- \hj}_{\mn}\nn\\
+&=\frac{2c^\top \psi}{1-\beta_{\psi}}\norm{J^*- \hj}_{\mn}.
 \end{align}
@@
 \begin{align}
-||J^*- \hj||_{\mn}&\leq ||J^*- \hv||_{\mn}+||\hv -\hj||_{\mn}\nn
+\norm{J^*- \hj}_{\mn}&\leq \norm{J^*- \hv}_{\mn}+\norm{\hv -\hj}_{\mn}\nn
 \end{align}
-The result now follows by substituting the bound on $||J^*- \hv||_{\mn}$ from \cref{cmt1mn} and the fact that $||\hv-\hj||_{\mn}\leq \frac{1}{1-\beta_{\psi}}||\hj-\hg\hj||_{\mn}$.
+The result now follows by substituting the bound on $\norm{J^*- \hv}_{\mn}$ from \cref{cmt1mn} and the fact that $\norm{\hv-\hj}_{\mn}\leq \frac{1}{1-\beta_{\psi}}\norm{\hj-\hg\hj}_{\mn}$.
 \end{proof}
@@
 \begin{note}
-By bounding $\etmn=||\Gamma J^*-J^*+J^*-\hg J^*||_{\mn}\leq 2||J^*-\Phi r^*||_{\mn}+||J^*-\hg J^*||_{\mn}$ 
+By bounding $\etmn=\norm{\Gamma J^*-J^*+J^*-\hg J^*}_{\mn}\leq 2\norm{J^*-\Phi r^*}_{\mn}+\norm{J^*-\hg J^*}_{\mn}$
 (the inequality follows from \cref{bestbndmn}), 
@@
 \label{loose1}
-||J^*-\hj||_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 ||J^*-\Phi r^*||_{\mn}
+\norm{J^*-\hj}_{1,c}&\leq\frac{c^\top\psi}{1-\beta_\psi}(10 \norm{J^*-\Phi r^*}_{\mn}
 \nn\\&
-+2||J^*-\hg J^*||_{\mn}).\\
++2\norm{J^*-\hg J^*}_{\mn}).\\
 \label{loose2}
-||J^* - J_{\hu}||_{1,c}&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2 \,\big(10 ||J^*-\Phi r^*||_{\mn}
+\norm{J^* - J_{\hu}}_{1,c}&\leq 2\left(\frac{c^\top \psi}{1-\beta_{\psi}}\right)^2 \,\big(10 \norm{J^*-\Phi r^*}_{\mn}
 \nn\\&
-+2||J^*-\hg J^*||_{\mn}\big).
++2\norm{J^*-\hg J^*}_{\mn}\big).
 \end{align}

### 2017-02-27 intro.tex
addressed the comments by Csaba

@@
 The  framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems arising in science and engineering.
-By casting a given decision problem as an MDP, the goal then is to find an optimal policy ($u^*$) which is the best decision rule.
-The so-called dynamic programming (DP) methods find an optimal policy by computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states.
-The value function $J^*$ stands for the cumulative return of making decisions according to $u^*$.
-Conventional DP  techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB} can compute the exact value of $J^*$.
+At any decision instance, an action is made which yeilds an immediate reward and the system moves to the next state in a stochastic manner such that the next state depends only on the current state and the action chosen.
+The set of all states, the state space, is denoted by $S$, and the set of all actions, the action space, is denoted by $A$.
+Formally, a decision rule is called a policy $u$, ($u\colon S\ra A$) and has an associated value function $J_u$\footnote{Without loss of generality value function $J_u$ can be thought of as a vector in $\R^{|S|}$.}, ($J_u(s)\colon S\ra \R$) which specifies the expected cumulative reward obtained by following the policy $u$ starting from each state.\par
+The so-called dynamic programming (DP) compute the optimal value function $J^*$ first and then obtain an optimal policy $u^*$ using $J^*$.
+Conventional DP  techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB} can compute the exact value of $J^*$ (and $u^*$).
 However, a shortcoming of these conventional methods is that their computational overhead grows with the number of states, a practical hindrance when the MDP has a large number of states.\par
 In this paper we consider the problem of using dynamic programming with MDPs with large state spaces.
-A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$, and a sub-optimal policy $\tu$ can be obtained using $\tj$.
+A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$, and a sub-optimal policy $\tu$ can be obtained using $\tj$\footnote{It is computationally cheap to obtain such a $\tu$ from $tj$ or $u^*$ from $J^*$}.
 The sub-optimal policy can then be used to make the decision and results in a cumulative return given by $J_{\tu}$.
 The idea here is forsake optimality to gain computational tractability.
-The success depends on the quality of approximation, i.e., on the quantities $||J^*-\tilde{J}||$ and $\norm{J^*-J_{\tu}}$ ($\norm{\cdot}$ is an appropriate norm) known as prediction error and the control error respectively.\par
+The success then depends on the quality of approximation, i.e., on the quantities $\norm{J^*-\tilde{J}}$ and $\norm{J^*-J_{\tu}}$ ($\norm{\cdot}$ is an appropriate norm) known as prediction error and the control error respectively.\par
 Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation.
@@
 \begin{enumerate}
-\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}).
-\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).
+\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $\norm{J^*-\hj}$ (\Cref{cmt2mn}).
+\item We also bound the performance loss due to using the policy $\hu$ that is obtained using $\hj$ (Theorem~\ref{polthe}).
 \item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
@@
 \end{enumerate}
-A short and preliminary version of this paper without the theoretical analysis is available in \cite{aaaipaper}.
+A short and preliminary version of this paper without the theoretical analysis can be found in \cite{aaaipaper}.
 \begin{comment}
@@
 Markov decision processes (MDPs) are a powerful mathematical framework to study optimal sequential decision making problems  arising in science and engineering.
-In an MDP, the configuration of the system is described by the state variables (or simply the state) and the system evolves in a stochastic manner which depends on the action made.
-The set of all states is denoted by $S$, the state space and the set of all actions is denoted by $A$, the action space.
+In an MDP, the configuration of the system, the state, evolves in a stochastic manner in a way that the next state depends only on the last state and the action chosen.
+The set of all states, the state space, is denoted by $S$, and the set of all actions, the action space, is denoted by $A$.
 %An instance of an MDP is a controlled queue setting, where there is a cost associated with the number of customers in the queue, and the aim is to control the service level depending on the number of %customers so as to achieve a minimum cumulative cost.

### 2017-02-27 prob.tex
addressed the comments by Csaba

@@
 In this section, we review relevant results \cite{BertB,ALP,CS} in the linear programming approach to MDPs.
-Throughout the rest of the paper, we let $c>0\in \R^n$ to denote a probability distribution over the state space S.\par
+Throughout the rest of the paper, we let $c\in (0,1)^n$ to denote a probability distribution with strictly positive components.
 \begin{comment}
@@
 \end{comment}
-\textbf{Linear Programming (LP)}: It is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
+\textbf{Linear Programming (LP)}: As it is well known \cite{manne}, the optimal value function $J^*$ can be obtained by solving the following linear program:
 \begin{align}\label{mdplp}
@@
 &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\,\,
-\forall (s,a)\in S\times A,\nn
+\forall (s,a)\in S\times A.\nn
 \end{align}
@@
 \text{ALP:}& \min_{r\in \R^k}\, c^\top \Phi r\\
-& \Phi r\geq T \Phi r,
+& E\Phi r\geq H \Phi r,
 \end{split}
 \end{flalign}
-where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}.
+where $E\Phi r\geq H \Phi r$ is a shorthand for the $nd$ constraints in \eqref{mdplp} which uses the definition of $H$ from \Cref{notations}-\eqref{bellactval}.
+Alternatively, we also use the notation $\Phi r \geq T\Phi r$, instead of $E\Phi r\geq H \Phi r$ using the definition of $T$ from \Cref{notations}-\eqref{bellopval}.
 Note that, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
@@
 \begin{enumerate}
-\item\label{alppe} The prediction error is bounded as $||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty$.
-\item\label{alpce} The control error is bounded as $||J^*-J_{\tu}||_{1,c}\leq \frac{2}{1-\alpha}||J^*-\tj||_{1,\mu_{\tu}}$.
+\item\label{alppe} The prediction error is bounded as $\norm{J^*-\tj}_{1,c}\leq \frac{2}{1-\alpha}\min_{r}\norm{J^*-\Phi r}_\infty$.
+\item\label{alpce} The control error is bounded as $\norm{J^*-J_{\tu}}_{1,c}\leq \frac{2}{1-\alpha}\norm{J^*-\tj}_{1,\mu_{\tu}}$.
 \end{enumerate}
 \end{theorem}
-The gist of \Cref{alpvanilla}-\eqref{alppe} is that the prediction error $||J^*-\tj||_{1,c}$ of ALP is worse utmost by a constant factor than the best possible error that can be achieved using the span of $\Phi$.
+The gist of \Cref{alpvanilla}-\eqref{alppe} is that the prediction error $\norm{J^*-\tj}_{1,c}$ of ALP is worse utmost by a constant factor than the best possible error that can be achieved using the span of $\Phi$.
 Further from \Cref{alpvanilla}-\eqref{alpce} the control error is worse utmost by a constant factor than the prediction error.\par
@@
 \begin{align*}
-||J^*-\Phi\tilde{r}_{RLP}||_{1,c}\leq ||J^*-\Phi\tilde{r}||_{1,c}+\epsilon ||J^*||_{1,c}
+\norm{J^*-\Phi\tilde{r}_{RLP}}_{1,c}\leq \norm{J^*-\Phi\tilde{r}}_{1,c}+\epsilon \norm{J^*}_{1,c}
 \end{align*}

### 2017-02-28 num.tex
submitted_version
addressed comments by Csaba

@@
 The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$.
-We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
+We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work reasonably well for this domain \cite{ALP}.
 For our experiments, we chose two contenders for the $W$-matrix and compared them with random positive matrices $W_r$.
@@
 Our choice of the $W_a$ matrix to correspond to aggregation of nearby states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
-The aggregation matrix $W_a$ is defined as below: for all $ i=1,\ldots,m$,
+The aggregation matrix $W_a$ is defined as follows: for all $ i=1,\ldots,m$,
 \begin{align}\label{wdes}
@@
 We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$, where $W_i$ is the ideal
-(and intractable) sampler of \citep{CS}. \todoc{Right??}
+(and intractable) sampler of \citep{CS}.
 We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively.
-The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.
+The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is close to that of the ideal sampler $W_i$.
 Note that computing $\et$ was hard in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate.
@@
 \resizebox{\columnwidth}{!}{
-\begin{tabular}{|c|c|c|c|c|}\hline
-Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
-$||J^*-\hj||_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
-$||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
-$\et$ & $0$&	$39$& $24$& $214$ \\\hline
+\begin{tabular}{|c|c|c|c|c|c|}\hline
+Queuing System&Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
+$Q_L$& $\norm{J^*-\hj}_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
+$Q_L$& $\norm{J^*-\hj}_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
+$Q_s$& $\et$ & $0$&	$39$& $24$& $214$ \\\hline
 \end{tabular}
@@
 Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
-$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
-$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
+$\norm{J_{\hu}}_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
+$\norm{J_{\hu}}_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
 \end{tabular}
@@
 %}
-\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
+\caption{Shows performance metrics for $Q_L$.
+Here $\norm{J^*}_{1,c}=-439.26$ for $\zeta=0.9$ and $\norm{J^*}_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
 $.}

### 2017-02-28 grlp.tex
further changes

@@
 \begin{align*}
-||J^*-\tj||_{1,c}\leq \frac{2}{1-\alpha}\min_{r}||J^*-\Phi r||_\infty
+\norm{J^*-\tj}_{1,c}\leq \frac{2}{1-\alpha}\min_{r}\norm{J^*-\Phi r}_\infty
 \end{align*}
-
 \end{theorem}
@@
 where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$) \cite{dolgov}.
-Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.
+Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for constructing the $W$ matrix.
 \FloatBarrier
-\input{cartoon}
+%\input{cartoon}
+\begin{figure}
+\includegraphics[scale=0.7]{cartoon_grlp.pdf}
+\end{figure}
 \Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively.
@@
 Our objective is to study the extra source of error due to constraint approximation.
-We now define two projection operators which are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
+We now define two projection operators that are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
 \section{Main Results}
@@
 \end{align}
-Then, for $J\in \R^n$, $\Gamma J$,
-the \emph{ least upper bound projection} of $J$ is defined as
+For $J\in \R^n$, $\Gamma J$, the \emph{least upper} (LU) projection of $J$ is defined as
 \begin{align}\label{gamdef}
@@
 \end{align}
-Then, the \emph{approximate least upper bound (ALUB) projection operator}
+The \emph{approximate least upper} (ALU) projection operator
 $\hg \colon \R^n \ra \R^n$ is defined as
@@
 Disregarding the constraint $r\in \N$,
-$\F_J$ contains vectors in the span of $\Phi$ that upper bound $TJ$. Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
+$\F_J$ contains all vectors in the span of $\Phi$ that upper bound $TJ$.
+Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
+Also $\Gamma J\geq T J$.
 \end{remark}
@@
 \item The prediction error is bound as\\
-$||J^*-\hj||_{1,c}
-\leq\frac{1}{1-\alpha}(6~\us{\min}{r\in \R^k}||J^*-\Phi r||_{\infty}
-+2||\Gamma J^*-\hg J^*||_{\infty})$.
+$\norm{J^*-\hj}_{1,c}
+\leq\frac{1}{1-\alpha}(6~\us{\min}{r\in \R^k}\norm{J^*-\Phi r}_{\infty}
++2\norm{\Gamma J^*-\hg J^*}_{\infty})$.
 \item The control error is bound as\\
 $\norm{J^* - J_{\hu}}_{1,c}
-\leq 2\left(\frac{1}{(1-\alpha)^2}\right)\, \big( 2~\us{\min}{r\in \R^k} ||J^*-\Phi r||_{\infty}
-+||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big)$.
+\leq 2\left(\frac{1}{(1-\alpha)^2}\right)\, \big( 2~\us{\min}{r\in \R^k} \norm{J^*-\Phi r}_{\infty}
++\norm{\Gamma J^*-\hg J^*}_{\infty}+\norm{\hj-\hg\hj}_{\infty}\big)$.
 \end{enumerate}
 \end{theorem}
-\textbf{On Prediction Error:}The first factor in the right hand side of the prediction error in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
-This term is inherent to the ALP formulation as shown in \Cref{alpvanilla}.
-The second factor in the right hand side of the prediction error is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.
-It makes intuitive sense since given that $\Phi$ approximates $J^*$, it is enough for $W$ to depend on $\Phi$ and $T$ without any additional requirements.\par
+\textbf{On Prediction Error:} The first factor in the right hand side of the prediction error in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
+This term is an carry over of the upper bound in ALP formulation as shown in \Cref{alpvanilla}.
+The second factor in the right hand side of the prediction error is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.\par
 \textbf{On Control Error:} The first two terms are quite similar to those in the bound for prediction error.
@@
 \begin{align}\label{polthebnd}
-%||J_{\hu}-\hj||_{1,c}
 \norm{J^* - J_{\hu}}_{1,c}
-&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2||J^*-\Phi r^*||_{\infty}
+&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2\norm{J^*-\Phi r^*}_{\infty}
 \nn\\&
-+||\Gamma J^*-\hg J^*||_{\infty}+||\hj-\hg\hj||_{\infty}\big).
++norm{\Gamma J^*-\hg J^*}_{\infty}+\norm{\hj-\hg\hj}_{\infty}\big).
 \end{align}
@@
 \end{comment}
-\begin{theorem}[Constraint Sampling]\label{st}
-Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
+\begin{corollary}[Constraint Sampling]\label{st}
+$W\in \{0,1\}^{nd\times m}$Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
 $W_{s'a,i}=\delta_{s=s'}$.
@@
 \end{align*}
-\end{theorem}
-It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$ and \Cref{cmt2} does not have these limitations.
-In addition, from \Cref{st}, we know that the additional error $|\Gamma J^*(s) -\hg J^*(s)|$ due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
-This means that for the RLP to perform well it is enough to retain those states for which the linear function approximation via $\Phi$ is known to perform well.
+\end{corollary}
+It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$, while \Cref{cmt2} does not have these limitations.
+In addition, the error $|\Gamma J^*(s) -\hg J^*(s)|$ (in \Cref{st} ) due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
+This means that for the RLP to perform well it is important to retain the constraints corresponding to those states for which the linear function approximation via $\Phi$ is known to perform well.

### 2017-02-28 intro.tex
further changes

@@
 Formally, a decision rule is called a policy $u$, ($u\colon S\ra A$) and has an associated value function $J_u$\footnote{Without loss of generality value function $J_u$ can be thought of as a vector in $\R^{|S|}$.}, ($J_u(s)\colon S\ra \R$) which specifies the expected cumulative reward obtained by following the policy $u$ starting from each state.\par
-The so-called dynamic programming (DP) compute the optimal value function $J^*$ first and then obtain an optimal policy $u^*$ using $J^*$.
+The so-called dynamic programming (DP) methods \cite{BertB} compute the optimal value function $J^*$ first and then obtain an optimal policy $u^*$ using $J^*$\footnote{Obtaining $u^*$ from $J^*$ is computationally cheap}.
 Conventional DP  techniques, such as value-, or policy-iteration, or linear programming (LP) \cite{BertB} can compute the exact value of $J^*$ (and $u^*$).
@@
 In this paper we consider the problem of using dynamic programming with MDPs with large state spaces.
-A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$, and a sub-optimal policy $\tu$ can be obtained using $\tj$\footnote{It is computationally cheap to obtain such a $\tu$ from $tj$ or $u^*$ from $J^*$}.
+A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$, and a sub-optimal policy $\tu$ can be obtained using $\tj$\footnote{It is computationally cheap to obtain such a $\tu$ from $\tj$ or $u^*$ from $J^*$}.
 The sub-optimal policy can then be used to make the decision and results in a cumulative return given by $J_{\tu}$.
@@
 Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation.
-Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.\par
+Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.
+Note that the matrix $\Phi$ is implicit in these methods: the full matrix is neither stored nor computed, but only its rows are accessed as needed.\par
 The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation.
-A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable.
+A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable in MDPs with large number of states.
 A way out is to choose a subset of constraints at random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP).
@@
 An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was also found useful in experiments.
-However, to this date, there exist no theoretical guarantees bounding the loss in performance resulting from such an approximation.
+However, to this date, there exist no theoretical guarantees for this approach.\par
 In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
@@
 %Further, in most cases the error terms reveal some structure that can offer insights and act as guide to the designer of the ADP method (for example the choice of $\Phi$). \par
-
 The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce LFA in the linear programming formulation to dynamic programming.
@@
 However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach.\par
-
 Our motivation stems from the fact that ALP with tractable number of constraints will result in a full dimeniosnality free ADP method.

### 2017-02-28 mdp.tex
addressed the comments by Csaba
further changes

@@
 \label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),~\text{and}\\
-\label{bellpol}u^*(s)&= \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),\,.
+\label{bellpol}u^*(s)&\in \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S}p_a(s,s')J^*(s')\big),\,.
 \end{align}
@@
 where ties in \eqref{bellpol} are resolved arbitrarily.\par
-We now present some definition which will be useful later:
+For the subsequent sections, the following definitions will be useful later:
 \begin{definition}\label{notations}
@@
 \begin{enumerate}[(i)]
-\item The Bellman operator $T\colon \R^n \ra \R^n$ is given by $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
+\item\label{bellopval} The Bellman operator $T\colon \R^n \ra \R^n$ is given by $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
 $
@@
 %some function $\tj:S \to \R$
-\begin{align*} u_J(s)\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S} p_a(s,s')J(s')\big).\end{align*}
+\begin{align*} u_J(s)\in\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \us{\sum}{s'\in S} p_a(s,s')J(s')\big).\end{align*}
 \item\label{norms} The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ with respect to a probability distribution $c$ is given by $
-||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|$.
+\norm{J}_{1,c}=\sum_{s \in S} c(s)|J(s)|$.
 \item The (un)weighted $L_\infty$-norms $\norm{\cdot}_{1,\infty}$
-and $\norm{\cdot}_{\infty,\rho}$, $\parallel J\parallel_{\infty}=\max_{s\in S}|J(s)|$ and $||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
+and $\norm{\cdot}_{\infty,\rho}$, $\norm{J}_{\infty}=\max_{s\in S}|J(s)|$ and $\norm{J}_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
 \item For $J_1, J_2\in \R^n$ we write $J_1\leq J_2$ when $J_1(s)\leq J_2(s),~\forall s\in S$.
@@
 We would like to point out that from \Cref{notations}, it follows that for any $J\in \R^n$ the condition $J\geq TJ$ can be rephrased as $EJ\geq HJ$.
+\begin{comment}
 \subsection{Dynamic Programming: Objective and Methods}
@@
 The focus of this paper is to present the error analysis for generalized reduced linear programming (GRLP), a new ADP formulation which we introduce in \Cref{sec:grlp}.
+\end{comment}

### 2017-02-28 num.tex
further changes

@@
 The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is close to that of the ideal sampler $W_i$.
-Note that computing $\et$ was hard in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate.
+Note that computing $\et$ was expensive in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate.
 Accordingly, we chose a smaller system $Q_S$ with $n=10$, $d=2$, $k=2$, $m=5$, $q(1)=0.2$, $q(2)=0.4$, $p=0.2$ and $\alpha=0.98$.

### 2017-02-28 prob.tex
further changes

@@
-\section{Linear Programming for MDP}
+\section{Exact and Approximate Linear Programming for MDP}
 In this section, we review relevant results \cite{BertB,ALP,CS} in the linear programming approach to MDPs.
-Throughout the rest of the paper, we let $c\in (0,1)^n$ to denote a probability distribution with strictly positive components.
+Throughout the rest of the paper, we let $c\in (0,1)^n$ to denote a probability distribution with strictly positive components.\\
 \begin{comment}
@@
 \end{align}
-\textbf{Approximate Linear Programming (ALP)} is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
-By substitution, this leads to
+Once $J^*$ is obtained from \eqref{mdplp}, an optimal policy $u^*$ can then be obtained via \eqref{bellpol} for each state relatively cheaply even for large state-spaces.
+However, notice that \eqref{mdplp} is a linear program in $n$ variables with $nd$ constraints.
+As a result, when $n$ is large it is computationally expensive to solve \eqref{mdplp}, a fact that motivated the need to look at the approximate linear programming (ALP) formulation which computes an approximate value function $\tj$.\\
+\textbf{Approximate Linear Programming (ALP)} is obtained by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}. By substitution, this leads to
 \begin{flalign}\label{alp}
@@
 where $E\Phi r\geq H \Phi r$ is a shorthand for the $nd$ constraints in \eqref{mdplp} which uses the definition of $H$ from \Cref{notations}-\eqref{bellactval}.
-Alternatively, we also use the notation $\Phi r \geq T\Phi r$, instead of $E\Phi r\geq H \Phi r$ using the definition of $T$ from \Cref{notations}-\eqref{bellopval}.
+ALP introduces what is known as linear function approximation in the LP, i.e., the value function computed by ALP can be given by $\tj=\Phi \tr$ for an appropriate $\tr\in \R^k$.
+ALP is a linear program in $k$ ($<<n$) variables and hence is computationally easier to handle in practice than LP.
 Note that, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
-In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}.\par
+In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ (the greedy policy with respect to $\tj$, see \Cref{notations}-\eqref{greedy}) where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}.
+Further, when convenient, we also use the notation $\Phi r \geq T\Phi r$, instead of $E\Phi r\geq H \Phi r$ in \eqref{alp} using the definition of $T$ from \Cref{notations}-\eqref{bellopval}.\\
+\textbf{Error Analysis of ALP:} ALP is an approximate method as opposed to LP.
+Thus, it is important for us to characterize the approximation error.
+In the context of ALP for MDPs, we care about two error terms namely the \emph{prediction error} $\norm{\tj-J^*}$, that captures the error in the approximate value function $\tj$ and the \emph{control error} $\norm{J_{\tu}-J^*}$, that is the loss in performance when a sub-optimal policy $\tu$ is used instead of an optimal policy $u^*$ (note that here $\norm{\cdot}$ is an appropriate norm).\par
 A detailed theoretical analysis of ALP can be found in \cite{ALP}.
@@
 \begin{theorem}[Error Bound for ALP]\label{alpvanilla}
-Let $\one\in \R^k$ belong to the column span of $\Phi$ and let $\mu_u\eqdef (1-\alpha)c^\top\top(I-\alpha P_u)^{-1}$ be a probability distribution over $S$ induced by a policy $u$.
-Then it follows that
+Let $\one\in \R^k$ belong to the column span of $\Phi$ and let $\mu_u\eqdef (1-\alpha)c^\top(I-\alpha P_u)^{-1}$ be a probability distribution over $S$ induced by a policy $u$. Then it follows that
 \begin{enumerate}
-\item\label{alppe} The prediction error is bounded as $\norm{J^*-\tj}_{1,c}\leq \frac{2}{1-\alpha}\min_{r}\norm{J^*-\Phi r}_\infty$.
-\item\label{alpce} The control error is bounded as $\norm{J^*-J_{\tu}}_{1,c}\leq \frac{2}{1-\alpha}\norm{J^*-\tj}_{1,\mu_{\tu}}$.
+\item\label{alppe} $\norm{J^*-\tj}_{1,c}\leq \frac{2}{1-\alpha}\min_{r}\norm{J^*-\Phi r}_\infty$.
+\item\label{alpce} $\norm{J^*-J_{\tu}}_{1,c}\leq \frac{2}{1-\alpha}\norm{J^*-\tj}_{1,\mu_{\tu}}$.
 \end{enumerate}
@@
 The gist of \Cref{alpvanilla}-\eqref{alppe} is that the prediction error $\norm{J^*-\tj}_{1,c}$ of ALP is worse utmost by a constant factor than the best possible error that can be achieved using the span of $\Phi$.
-Further from \Cref{alpvanilla}-\eqref{alpce} the control error is worse utmost by a constant factor than the prediction error.\par
+Further from \Cref{alpvanilla}-\eqref{alpce} the control error is worse utmost by a constant factor than the prediction error.\\
+\textbf{Issues with ALP}: While ALP has only $k$ variables, it has $nd$ constraints.
+Two approaches have been found empirically successful \cite{CS,dolgov,ALP-Bor} in addressing the issue of large number of constraints in the ALP.
+In the first approach \cite{CS}, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear programming} (RLP) problem.
+The performance analysis of the RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions.
+The second approach involves employing function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}.
+However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach.
+We now dicuss RLP and its error analysis.\\
 \textbf{Reduced Linear Programming (RLP)} is formulated by retaining only $m$ out of the $nd$ ($m<<nd$) constraints of ALP.
@@
 where $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$ and $\N$\footnote{The appendix explains how $\N$ can be chosen analytically.} is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}.
-We denote an arbitrary solution to the RLP by $\tr_{RLP}$.\par
-We now state a useful result from \cite{CS} that characterizes the performance analysis RLP as follows:
+We denote an arbitrary solution to the RLP by $\tr_{RLP}$.\\
+\textbf{Error Analysis of RLP:} We now state a useful result from \cite{CS} that characterizes the performance analysis RLP as follows:
 \begin{theorem}[Error Bound for RLP]\label{rlpt}
@@
 \end{theorem}
-The gist of \Cref{rlpt} is that when `sufficient' number of samples are retained using a specialized distribution ($\psi_{u^*}$), then with high probability, the prediction error of RLP and ALP differ only by a small factor (i.e., $\epsilon\norm{J^*}_{1,c}$).\par
-A major weakness of \Cref{rlpt} is that it holds only for RLP formulated using $\psi_{u^*}$ which is impractical since $u^*$ is unknown in general.
+The gist of \Cref{rlpt} is that when `sufficient' number of samples are retained using a specialized distribution ($\psi_{u^*}$), then with high probability, the prediction error of RLP and ALP differ only by a small factor (i.e., $\epsilon\norm{J^*}_{1,c}$).\\
+\textbf{Limitations of Error Analysis for RLP:} A major weakness of \Cref{rlpt} is that it holds only for RLP formulated using $\psi_{u^*}$ which is impractical since $u^*$ is unknown in general.
 However, empirical studies \cite{ALP,CS,CST} have shown that RLP formulated with other sampling distributions do perform well in experiments.

### 2017-03-01 appendix.tex
further re-arragement

@@
 \textbf{On choice of $\N$:}\\
-Let $g_{\min}=\underset{a,s}{\min}g_a(s)$, $g_{\max}=\underset{a,s}{\max}g_a(s)$ and define $r^*\eqdef\underset{r\in \R^k}{\arg\min}||J^*-\Phi r||_{\mn}$.
-Now $\frac{g_{\min}}{1-\alpha}\leq J^* \leq \frac{g_{\max}}{1-\alpha}$ and since $\mathbf{1}$ is in the basis, we have $||J^*-\Phi r^*||_{\mn}\leq \frac{g_{\max}-g_{\min}}{1-\alpha}$ (making use of the fact that for any sensible choice of Lyapunov function $||J^*-\Phi r^*||_{\mn}\leq ||J^*-\Phi r^*||_{\infty}$).
-Further, in our arguments, we have made the implicit assumption that $r'= r^*+||J^*-\Phi r^*||_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0 \in \N$.
-This implicit assumption will continue to hold when $\N\eqdef\{\r| a\leq \Phi r\leq b\}$, where $a=\frac{g_{\min}}{1-\alpha}$ and $b=\frac{g_{\max}}{1-\alpha}+\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\frac{g_{\max}-g_{\min}}{1-\alpha}$.
+It is desirable to get rid of the assumption that $\tr\in \N$ without affecting our arguments.
+Note that the set $\N$ is not used in ALP \eqref{alp} and the feasible set of ALP can be specified as the set $\S\eqdef\{r\in \R^k| \Phi r \geq T\Phi r\}$.
+Further, the only property about $\S$ that we used in our argument (\Cref{restate}) was that $r'= r^*+\norm{J^*-\Phi r^*}_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0 \in \S$.
+Thus, so long as $\N$ contains $r'$ it is not necessary for it to contain $\tr$.\par
+Let $g_{\min}=\underset{a,s}{\min}g_a(s)$, $g_{\max}=\underset{a,s}{\max}g_a(s)$ and define $r^*\eqdef\underset{r\in \R^k}{\arg\min}\norm{J^*-\Phi r}_{\mn}$.
+Now $\frac{g_{\min}}{1-\alpha}\leq J^* \leq \frac{g_{\max}}{1-\alpha}$ and since $\mathbf{1}$ is in the basis, we have $\norm{J^*-\Phi r^*}_{\mn}\leq \frac{g_{\max}-g_{\min}}{1-\alpha}$ (making use of the fact that for any sensible choice of Lyapunov function $\norm{J^*-\Phi r^*}_{\mn}\leq \norm{J^*-\Phi r^*}_{\infty}$).
+The fact that $r'\in \N$ can then be ensured when $\N\eqdef\{\r| a\leq \Phi r\leq b\}$, where $a=\frac{g_{\min}}{1-\alpha}$ and $b=\frac{g_{\max}}{1-\alpha}+\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\frac{g_{\max}-g_{\min}}{1-\alpha}$.
 \end{appendix}

### 2017-03-01 errana.tex
addressed comments by Csaba
further re-arragement

@@
 Prior works in ALP literature \cite{ALP,SALP,CS} make use of Lyapunov functions based analysis to obtain error bounds that exploit the structure of the underlying MDP.
-In particular, the prior bounds suggests that the ALP is likely to generate good approximations when the underlying MDP is stable.
+In particular, the prior bounds suggests that ALP is likely to generate good approximations when the underlying MDP is stable.
 We also adopt a similar approach by stating our results using Lyapunov function based arguments.
@@
 \begin{proof}
-For $i\in \{1,\dots,n\}$, $c=e_i$ let $r_i$ be a solution to the GRLP in \eqref{grlp}
+For $i\in \{1,\dots,n\}$, $c=e_i$ let $r_i$ be a solution to GRLP in \eqref{grlp}
 and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.
@@
 %The proof follows in a similar manner as the proof of \Cref{relation1}. To elaborate, 
-Let $ r_1,  r_2,\ldots, r_n$ be solutions to the ALP in \eqref{alp} (with an additional constraint that the solution be restricted to $\N$) for $c=e_1, e_2,\ldots,e_n$, respectively,
+Let $ r_1,  r_2,\ldots, r_n$ be solutions to ALP in \eqref{alp} (with an additional constraint that the solution be restricted to $\N$) for $c=e_1, e_2,\ldots,e_n$, respectively,
 and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 
@@
 \end{align}
-The proof follows by applying \cref{bestbndmn} on \eqref{jhv}.
+The proof follows by combining this and \cref{bestbndmn}.
 \end{proof}
@@
 \end{align}
-Then $r'$ is feasible for the ALP in \eqref{alp}.
+Then $r'$ is feasible for ALP in \eqref{alp}.
 \end{lemma}
-Recall that $\hv$ is the fixed point of $\hg$ and $\hj=\Phi \hr$ is the solution to the GRLP
+Recall that $\hv$ is the fixed point of $\hg$ and $\hj=\Phi \hr$ is the solution to GRLP
 \eqref{grlp}. 
@@
 %We know that $\tr \in \N$ by \cref{grlpassmp}-\eqref{nassmp} and 
-Now, $r'$ is feasible for the ALP in \eqref{alp} by \cref{restate}.
+Now, $r'$ is feasible for ALP in \eqref{alp} by \cref{restate}.
 Then from \cref{srwalp} it follows that
@@
 \end{proof}
-\begin{theorem}[Prediction error bound in $\norm{\cdot}_{\mn}$]
+\begin{theorem}[Prediction error bound]
 \label{cmt2mn}
@@
 We now bound the performance of the greedy policy $\hu$.
-\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\mn}$]
+\begin{theorem}[Control Error Bound]
 \label{polthe}
-Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
+Let $\hu$ be the greedy policy with respect to the solution $\hj$ of GRLP and $J_{\hu}$ be its value function.
 % Let $r^*$ be as in Theorem~\ref{mt2mn}, then

### 2017-03-01 grlp.tex
further re-arragement

@@
 where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp} and $\Phi$ is a feature matrix whose first column is $\one$.
-Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy w.r.t.
+Unless specified otherwise we use $\tr$ to denote an arbitrary solution to ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy w.r.t.
 $\tj$.
-The following is a preliminary error bound for the ALP from \cite{ALP}:
+The following is a preliminary error bound for ALP from \cite{ALP}:
 \begin{theorem}[Error Bound for ALP]
@@
 \end{theorem}
-%For a more detailed treatment of the ALP and sophisticated bounds, the reader is referred to \cite{ALP}.
+%For a more detailed treatment of ALP and sophisticated bounds, the reader is referred to \cite{ALP}.
 %\subsection{Approximating the Constraints}
 The ALP is a linear program in $k$ ($<<n$) variables as opposed to the LP in \eqref{mdplp} which has $n$ variables.
-Nevertheless, the ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
-Most works in literature make use of the underlying structure of the problem to cleverly reduce the number of constraints of the ALP.
+Nevertheless, ALP has $nd$ constraints (same as the LP) which is an issue when $n$ is large and calls for constraint approximation/reduction techniques.
+Most works in literature make use of the underlying structure of the problem to cleverly reduce the number of constraints of ALP.
 A good example is \cite{gkp}, wherein the structure in factored linear functions is exploited.
@@
 In \cite{petrik} the transitional error is reduced ignoring the representational and sampling errors.\par
-The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of the ALP.
-While the objective of the RLP is same as that of the ALP, the RLP has only $m<<nd$ constraints \emph{sampled} from the original $nd$ constraints of the ALP.
-The following is a preliminary error bound for the RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
+The most important work in the direction of constraint reduction is constraint sampling \cite{CS} wherein a reduced linear program (RLP) is solved instead of ALP.
+While the objective of RLP is same as that of ALP, RLP has only $m<<nd$ constraints \emph{sampled} from the original $nd$ constraints of ALP.
+The following is a preliminary error bound for RLP from \cite{CS} holds for a special sampling distribution which is dependent on the optimal policy $u^*$ (see \cite{CS} for a detailed presentation):
 \begin{theorem}[Error Bound for RLP]
@@
 %A major gap in the theoretical analysis is that the error bounds are known for only a specific RLP formulated using idealized assumptions, i.e., under knowledge of $u^*$.
-However, the RLP has be found to do well empirically in domains such as Tetris \cite{CST} and controlled queues \cite{CS}.
+However, RLP has be found to do well empirically in domains such as Tetris \cite{CST} and controlled queues \cite{CS}.
 \subsection{Open Questions}
-Interestingly, the RLP has nevertheless been found to do well empirically in domain such as Tetris \cite{CST} and controlled queues \cite{CS} even when the constraints were sampled using distribution other than the ideal distribution.
+Interestingly, RLP has nevertheless been found to do well empirically in domain such as Tetris \cite{CST} and controlled queues \cite{CS} even when the constraints were sampled using distribution other than the ideal distribution.
 This fact indicates a gap in the theoretical analysis and points to the need for a more elaborate theory that addresses the issue of constraint approximation.
@@
 \\
-$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
+$\bullet$ As a natural generalization of RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of ALP?\\
 $\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?
@@
 where we assume that $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints.
-The RLP \eqref{rlp} can be recovered as a special case of the GRLP \eqref{grlp} by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$.
-The $\N$ in the RLP \eqref{rlp} is retained in the GRLP \eqref{grlp} as well.
-For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as the ALP.
-We denote an arbitrary solution to the GRLP by $\hr$, and the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t.
-$\hj$.\par
-The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation.
-To understand this, we need to look at the Lagrangian of the ALP and GRLP in
+We denote an arbitrary solution to GRLP by $\hr$, and the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t.
+$\hj$.\\
+\textbf{RLP as a special case:} Recovering RLP \eqref{rlp} as a special case of GRLP \eqref{grlp} can be accomplished by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$.
+The $\N$ in RLP \eqref{rlp} is retained in GRLP \eqref{grlp} as well.
+For $m=nd$ and $W=I_{nd\times nd}$, GRLP is same as ALP.\\
+\textbf{Linear function approximation in Primal and Dual Variables:} Let us look at the Lagrangian of ALP and GRLP in
 \eqref{lag} and \eqref{lag2} respectively, i.e.,
@@
 %Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers.
-Hence, while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
+Hence, while ALP employs LFA in its objective function (i.e., use of $\Phi r$), GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
 %Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
@@
 \includegraphics[scale=0.7]{cartoon_grlp.pdf}
+\caption{
+%\normalsize
+The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints.
+The main contribution of the paper is to bound $\norm{J^*-\hat{J}_c}$.}
+\label{cartoon}
 \end{figure}
-\Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively.
-The error in the ALP solution has already been studied in \cite{ALP}.
+\Cref{cartoon} shows the solutions to the LP, ALP and GRLP respectively.
+The error in ALP solution has already been studied in \cite{ALP}.
 Our objective is to study the extra source of error due to constraint approximation.
-We now define two projection operators that are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
 \section{Main Results}
@@
 Our bounds are expressed in terms of two novel contractions operators which we define in \Cref{lubpop,alubpop}.
+We now define two projection operators that are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
 %The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
@@
 \begin{align}\label{ubclass}
-\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N\,\},
+\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N'\,\},
 \end{align}
 where $J\in \R^n$.
-Disregarding the constraint $r\in \N$,
+Disregarding the constraint $r\in \N'$,
 $\F_J$ contains all vectors in the span of $\Phi$ that upper bound $TJ$.
 Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
-Also $\Gamma J\geq T J$.
+Also $\Gamma J\geq T J$.\par
+The operators $\Gamma$ and $\hg$ are closely related to ALP \eqref{alp} and GRLP \eqref{grlp} respectively and are only analytical tools that we will need to express our bounds and need not be computed in practice.
+It turns out that the novel operators ($\Gamma$ and $\hg$) are contraction maps (see \Cref{hgmaxcontramn}), a fact that is a key to our results (\Cref{cmt2mn,polthe}).
+Though we are concerned about the behaviour of $\Gamma$ and $\hg$ on the candidate value functions in the constraint set $\N$, we want them to make sense for any arbitrary $J\in \R^n$.
+In order to be accomplish the same, we define $\N'$ in \Cref{lubplp,alubplp} to be `$\N$ plus its translations by $\one$', so as to patch $\N$ via translations and make the neighbourhood of any arbitrary $J\in \R^n$, `look' like $\N$.
 \end{remark}
@@
 \label{polthe}
-Let $\hu$ be the greedy policy with respect to the solution $\hj$ of the GRLP and $J_{\hu}$ be its value function.
+Let $\hu$ be the greedy policy with respect to the solution $\hj$ of GRLP and $J_{\hu}$ be its value function.
 % Let $r^*$ be as in Theorem~\ref{mt2mn}, then
@@
 In addition, the error $|\Gamma J^*(s) -\hg J^*(s)|$ (in \Cref{st} ) due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
-This means that for the RLP to perform well it is important to retain the constraints corresponding to those states for which the linear function approximation via $\Phi$ is known to perform well.
+This means that for RLP to perform well it is important to retain the constraints corresponding to those states for which the linear function approximation via $\Phi$ is known to perform well.

### 2017-03-01 intro.tex
further re-arragement

@@
 The  framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems arising in science and engineering.
-At any decision instance, an action is made which yeilds an immediate reward and the system moves to the next state in a stochastic manner such that the next state depends only on the current state and the action chosen.
+At any decision instance, an action is made which yields an immediate reward and the system moves to the next state in a stochastic manner such that the next state depends only on the current state and the action chosen.
 The set of all states, the state space, is denoted by $S$, and the set of all actions, the action space, is denoted by $A$.
@@
 However, a shortcoming of these conventional methods is that their computational overhead grows with the number of states, a practical hindrance when the MDP has a large number of states.\par
-In this paper we consider the problem of using dynamic programming with MDPs with large state spaces.
-A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$, and a sub-optimal policy $\tu$ can be obtained using $\tj$\footnote{It is computationally cheap to obtain such a $\tu$ from $\tj$ or $u^*$ from $J^*$}.
+This paper is related to LP based techniques for MDPs with large state spaces.
+One way to handle the large number of states is to restrict the value function to the sub-space spanned by the columns of an $n\times k$ feature matrix $\Phi$\footnote{This is known as linear function approximation (LFA) where in the value function is approximated by $\Phi \tr$, for some $\tr\in \R^k$.
+The idea of LFA is not restricted to LP based approach and is also widely used in other approximate dynamic programming methods \cite{dpchapter}, which are not discussed in this paper.}.
+This sub-space restriction can be accommodated in the LP formulation and results in the approximate linear programming (ALP) formulation \cite{ALP,CS,SALP,ALP-Bor}.
+ALP computes an approximate value function $\tj=\Phi \tr$ and a sub-optimal policy $\tu$ can be obtained using $\tj$\footnote{It is computationally cheap to obtain such a $\tu$ from $\tj$ or $u^*$ from $J^*$}.
 The sub-optimal policy can then be used to make the decision and results in a cumulative return given by $J_{\tu}$.
-The idea here is forsake optimality to gain computational tractability.
-The success then depends on the quality of approximation, i.e., on the quantities $\norm{J^*-\tilde{J}}$ and $\norm{J^*-J_{\tu}}$ ($\norm{\cdot}$ is an appropriate norm) known as prediction error and the control error respectively.\par
-Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi r^*$ where $\Phi$ is a so-called feature matrix and $r^*$ is a weight vector to be computed, is the most widely used method of approximation.
-Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, holding the promise of being able to work with MDPs regardless of the number of states.
-Note that the matrix $\Phi$ is implicit in these methods: the full matrix is neither stored nor computed, but only its rows are accessed as needed.\par
-The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation.
-A critical shortcoming of vanilla ALP is that the number of constraints are of the order of the size of the state space, making this vanilla version intractable in MDPs with large number of states.
-A way out is to choose a subset of constraints at random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP).
-The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}.
-An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was also found useful in experiments.
+The performance of ALP was studied in \cite{ALP} in terms of the quantities $\norm{J^*-\tilde{J}}$ and $\norm{J^*-J_{\tu}}$ ($\norm{\cdot}$ is an appropriate norm) known as prediction error and the control error respectively.
+Here, prediction error is the error in the approximate value function $\tj$ and the control error is the loss in performance due to the sub-optimal policy $\tu$.\par
+%The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation.
+A critical shortcoming of ALP is that the number of constraints are of the order of the size of the state space, making it intractable in MDPs with large number of states.
+A way out of this shortcoming is to choose a subset of constraints at random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP).
+The performance analysis of RLP can be found in \cite{CS} and RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}.
+An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of ALP \cite{ALP-Bor,dolgov}, an approach that was also found useful in experiments.
 However, to this date, there exist no theoretical guarantees for this approach.\par
-In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
+In this paper, we generalize RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
 The salient aspects of our contribution are listed below:
 \begin{enumerate}
-\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $\norm{J^*-\hj}$ (\Cref{cmt2mn}).
+\item We develop novel analytical machinery to relate $\hat{J}$, the solution to GRLP, and the optimal value function $J^*$ by bounding the prediction error $\norm{J^*-\hj}$ (\Cref{cmt2mn}).
 \item We also bound the performance loss due to using the policy $\hu$ that is obtained using $\hj$ (Theorem~\ref{polthe}).
@@
 \item Our analysis also makes use of arguments based on \emph{Lyapunov} function, an approach much similar to prior works in ALP literature \cite{ALP,SALP}.
-\item Our results on the GRLP are the first to theoretically analyze the use of linear function approximation of Lagrangian (dual) variables underlying the constraints.
+\item Our results on GRLP are the first to theoretically analyze the use of linear function approximation of Lagrangian (dual) variables underlying the constraints.
 \item A numerical example in controlled queues is provided to illustrate the theory.
@@
 The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce LFA in the linear programming formulation to dynamic programming.
-Theoretical performance analysis of the ALP can be found in \cite{ALP}.
+Theoretical performance analysis of  ALP can be found in \cite{ALP}.
 %and a salient feature is that it does not suffer from issues such as `policy oscillations'\footnote{ADP methods that use linear least squares projection are known to exhibit `policy oscillations' %\cite{BertB}, i.e., output a repeating sequence of bad sub-optimal policies.
-Since our focus in this paper is the ALP formulation, we refrain from a detailed presentation of the other methods.}
-The number of variables of the ALP is only $k$, a critical shortcoming of the ALP is that the number of constraints are of the order of the size of the state space, making it intractable.
-Two approaches have been found empirically successful \cite{CS,dolgov,ALP-Bor} in addressing the issue of large number of constraints in the ALP.
+Since our focus in this paper is ALP formulation, we refrain from a detailed presentation of the other methods.}
+The number of variables of ALP is only $k$, a critical shortcoming of ALP is that the number of constraints are of the order of the size of the state space, making it intractable.
+Two approaches have been found empirically successful \cite{CS,dolgov,ALP-Bor} in addressing the issue of large number of constraints in ALP.
 In the first approach \cite{CS}, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear programming} (RLP) problem.
-The performance analysis of the RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions.
-The second approach involves employing function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}.
+The performance analysis of RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions.
+The second approach involves employing function approximation in the dual variables of ALP \cite{ALP-Bor,dolgov}.
 However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach.\par
 Our motivation stems from the fact that ALP with tractable number of constraints will result in a full dimeniosnality free ADP method.
-However, constraint reduction in the ALP is an extra source of error (in addition to the error due to LFA), which has not been theoretically well understood.
-The focus of this paper is to fill this gap in theory by deriving performance bounds for constraint reduction in the ALP formulation.
+However, constraint reduction in ALP is an extra source of error (in addition to the error due to LFA), which has not been theoretically well understood.
+The focus of this paper is to fill this gap in theory by deriving performance bounds for constraint reduction in ALP formulation.
 The salient aspects of our contribution are listed below:
@@
 \item We define a generalized reduced linear programming (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints.
-The GRLP amounts to linear function approximation of the dual variables, and the RLP is a special case of GRLP.
-\item We develop a novel analytical machinery to bound the prediction error $\norm{J^*-\hj}$ where $hj$ is the solution to the GRLP.
+The GRLP amounts to linear function approximation of the dual variables, and RLP is a special case of GRLP.
+\item We develop a novel analytical machinery to bound the prediction error $\norm{J^*-\hj}$ where $hj$ is the solution to GRLP.
 		\item We also bound the performance loss due to using the policy $\hu$ that is one-step greedy with respect to $\hj$ (Theorem~\ref{polthe}).
 		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
-%Our analysis also makes use of arguments based on \emph{Lyapunov} functions, an approach much similar to prior works in the ALP literature \cite{ALP,SALP}.
+%Our analysis also makes use of arguments based on \emph{Lyapunov} functions, an approach much similar to prior works in ALP literature \cite{ALP,SALP}.
 \item Our results on GRLP are the first to theoretically analyze the use of linear function approximation of Lagrangian (dual) variables underlying the constraints.

### 2017-03-01 prob.tex
further re-arragement

@@
 ALP is a linear program in $k$ ($<<n$) variables and hence is computationally easier to handle in practice than LP.
-Note that, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
+Note that, for $k=n$ and $\Phi=I_{n\times n}$, ALP is same as the LP.
 In what follows, we use the notation $\tj=\Phi \tr$ and $\tu=u_{\tj}$ (the greedy policy with respect to $\tj$, see \Cref{notations}-\eqref{greedy}) where $\tr\in\R^k$ denotes an arbitrary solution to ALP in \eqref{alp}.
@@
 \textbf{Issues with ALP}: While ALP has only $k$ variables, it has $nd$ constraints.
-Two approaches have been found empirically successful \cite{CS,dolgov,ALP-Bor} in addressing the issue of large number of constraints in the ALP.
+Two approaches have been found empirically successful \cite{CS,dolgov,ALP-Bor} in addressing the issue of large number of constraints in ALP.
 In the first approach \cite{CS}, a random subset of constraints is chosen (dropping the rest), thereby formulating a \emph{reduced linear programming} (RLP) problem.
-The performance analysis of the RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions.
-The second approach involves employing function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}.
+The performance analysis of RLP can be found in \cite{CS}, however, the bounds hold only in high probability under idealized assumptions.
+The second approach involves employing function approximation in the dual variables of ALP \cite{ALP-Bor,dolgov}.
 However, to this date, there exist no theoretical guarantees bounding the loss in performance due to this approach.
@@
 \end{align}
-where $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$ and $\N$\footnote{The appendix explains how $\N$ can be chosen analytically.} is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}.
-We denote an arbitrary solution to the RLP by $\tr_{RLP}$.\\
+where $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$ and $\N$\footnote{The appendix explains how $\N$ can be chosen analytically.} is a compact set such that $\tr \in \N$, and it ensures boundedness of RLP \eqref{alp}.
+We denote an arbitrary solution to RLP by $\tr_{RLP}$.\\
 \textbf{Error Analysis of RLP:} We now state a useful result from \cite{CS} that characterizes the performance analysis RLP as follows:
@@
 Note that in \eqref{alp}, $Phi r\geq T\Phi r$ is a shortcut to denote the $S\times A$ constraints.
-Also, for $k=n$ and $\Phi=I_{n\times n}$, the ALP is same as the LP.
-We denote an arbitrary solution to the ALP by $\tr\in \R^k$.\par
+Also, for $k=n$ and $\Phi=I_{n\times n}$, ALP is same as the LP.
+We denote an arbitrary solution to ALP by $\tr\in \R^k$.\par
 \item The RLP \eqref{rlp} was first introduced in \cite{CS}.
-The RLP \eqref{rlp} has the same objective function as the ALP \eqref{rlp}.
-The construction of the RLP needs three parameters to be specified namely, the number of samples $m$, the sampling distribution $\psi$ and the constraint set $\N$.
+The RLP \eqref{rlp} has the same objective function as ALP \eqref{rlp}.
+The construction of RLP needs three parameters to be specified namely, the number of samples $m$, the sampling distribution $\psi$ and the constraint set $\N$.
 In particular, $\psi=\psi(u^*)$ i.e., the sampling distribution
-In the RLP in \eqref{rlp}, $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$.
+In RLP in \eqref{rlp}, $\I\subset S \times A$ is the index set of sampled constraints, i.e., $|\I|=m$.
 The samples are generated using a distribution $\psi$ (see a restatement of the results in \cite{CS} summarized in \Cref{}).
-$\N$ is a compact set such that $\tr \in \N$, and it ensures boundedness of the RLP \eqref{alp}.
-We denote an arbitrary solution to the RLP by $\tr_{RLP}$.
-It is important to note that the RLP \eqref{rlp} is a random linear program, in the sense that it depends on the $m$ samples obtained from $\psi$.
+$\N$ is a compact set such that $\tr \in \N$, and it ensures boundedness of RLP \eqref{alp}.
+We denote an arbitrary solution to RLP by $\tr_{RLP}$.
+It is important to note that RLP \eqref{rlp} is a random linear program, in the sense that it depends on the $m$ samples obtained from $\psi$.
 \item In the GRLP in \eqref{grlp}, $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints.
 The RLP \eqref{rlp} can be recovered as a special case of the GRLP \cite{grlp} by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$.
-The $\N$ in the RLP \eqref{rlp} is retained in the GRLP \eqref{grlp} as well.
-For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as the ALP.
+The $\N$ in RLP \eqref{rlp} is retained in the GRLP \eqref{grlp} as well.
+For $m=nd$ and $W=I_{nd\times nd}$, the GRLP is same as ALP.
 We denote an arbitrary solution to the GRLP by $\hr$.
@@
 \Cref{cartoon} which shows the solutions to the LP, ALP and GRLP respectively.
-The error in the ALP solution has already been studied in \cite{ALP}.
+The error in ALP solution has already been studied in \cite{ALP}.
 Our objective is to study the extra source of error due to constraint approximation.
@@
 In addition, we answer the following questions related to constraint reduction in ALP that have so far remained open. \\
-$\bullet$ As a natural generalization of the RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of the ALP?\\
+$\bullet$ As a natural generalization of RLP, what happens if we define a generalized reduced linear program (GRLP) whose constraints are positive linear combinations of the original constraints of ALP?\\
 $\bullet$ Unlike \cite{CS} which provides error bounds for a specific RLP formulated using an idealized sampling distribution, is it possible to provide error bounds for any GRLP (and hence any RLP)?

### 2017-03-01 ResponseToReview114203Of16-1082v1.tex
adding the review directory

\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
%\documentclass[12pt,twocolumn]{IEEEtran}
%\documentclass[twocolumn]{IEEEtran}
\usepackage{times}
\input{pack}
%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\title{ Response to comments by Reviewer1}
\author{Chandrashekar Lakshminarayanan$^\star$, Shalabh Bhatnagar$^\star$,
 and Csaba Szepesvari$^\dagger$\thanks{$^\star$Department of Computer
Science and Automation, Indian Institute of Science, Bangalore 560012.
E-mail: $\{$chandrul, shalabh$\}$@csa.iisc.ernet.in}
\thanks{$^\dagger$Department of Computing Science, University of Alberta,
Edmonton, Alberta, Canada T6G 2E8. E-mail: csaba.szepesvari@ualberta.ca}}
% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}
\begin{document}
\maketitle
In what follows, we present the reviewer's comment in \emph{italized} fonts and our repsonse to them in normal fonts.
\begin{enumerate}
\item \emph{
The authors have developed a deterministic way to handle LP for MDP and
also new analytic tools for error analysis. Though this article
introduces novel contributions to the field but the writing is a bit
clumsy. Explanations of the lemmas and definitions are missing (as
marked later). The authors don't provide intuition for most of the
assumptions. Since the authors have additional space, more details
should be provided.
Some of the terms in the definitions like discounted maximal inflations
are never used directly and no reasoning behind the use of Lyapunov
stability (which is a good and important part of the technique here) is
given anywhere. For a contribution of this kind such an explanation is
at least expected. So it's better if the authors give some
explanations, elongate it a bit and make it readable to someone who
isn't expert of both control and MDP, otherwise it is a very good piece
of work.
Few detailed comments are attached.
}
\textbf{Response:} We have restructured our paper and added the explanations as suggested.
\end{enumerate}

%\input{appendix}
\end{document}

### 2017-03-01 grlp.tex
adding the review directory

@@
 It turns out that the novel operators ($\Gamma$ and $\hg$) are contraction maps (see \Cref{hgmaxcontramn}), a fact that is a key to our results (\Cref{cmt2mn,polthe}).
-Though we are concerned about the behaviour of $\Gamma$ and $\hg$ on the candidate value functions in the constraint set $\N$, we want them to make sense for any arbitrary $J\in \R^n$.
-In order to be accomplish the same, we define $\N'$ in \Cref{lubplp,alubplp} to be `$\N$ plus its translations by $\one$', so as to patch $\N$ via translations and make the neighbourhood of any arbitrary $J\in \R^n$, `look' like $\N$.
+At the outset we are interested in the candidate value functions in the constraint set $\N$ and want to study them using $\Gamma$ and $\hg$.
+However since the basis $\Phi$ contains $\one$ we make it helps our analysis to define the set $\N'$ in \Cref{lubplp,alubplp} to be `$\N$ plus its translations by $\one$'.
 \end{remark}
-\subsection{Error Bounds}
+%\subsection{Error Bounds}
 \begin{theorem}[Error Bound for GRLP]

### 2017-03-01 prob.tex
adding the review directory

@@
 Further, when convenient, we also use the notation $\Phi r \geq T\Phi r$, instead of $E\Phi r\geq H \Phi r$ in \eqref{alp} using the definition of $T$ from \Cref{notations}-\eqref{bellopval}.\\
-\textbf{Error Analysis of ALP:} ALP is an approximate method as opposed to LP.
-Thus, it is important for us to characterize the approximation error.
-In the context of ALP for MDPs, we care about two error terms namely the \emph{prediction error} $\norm{\tj-J^*}$, that captures the error in the approximate value function $\tj$ and the \emph{control error} $\norm{J_{\tu}-J^*}$, that is the loss in performance when a sub-optimal policy $\tu$ is used instead of an optimal policy $u^*$ (note that here $\norm{\cdot}$ is an appropriate norm).\par
+\textbf{Error Analysis of ALP:} %ALP is an approximate method as opposed to LP. Thus, it is important for us to characterize the approximation error. In the context of ALP for MDPs,
+We care about two error terms namely the \emph{prediction error} $\norm{\tj-J^*}$, that captures the error in the approximate value function $\tj$ and the \emph{control error} $\norm{J_{\tu}-J^*}$, that is the loss in performance when a sub-optimal policy $\tu$ is used instead of an optimal policy $u^*$ (note that here $\norm{\cdot}$ is an appropriate norm).\par
 A detailed theoretical analysis of ALP can be found in \cite{ALP}.

### 2017-03-20 intro.tex
intro

@@
 \section{Introduction}
+Markov decision processes (MDPs) have proved to be an indispensable model for sequential decision making under uncertainty with applications in networking, traffic control, robotics, operations research, business, finance, artificial intelligence, health-care and more (see, e.g., \cite{BauRie:11,Puter,FeiSh02:MDPHandbook,Abuetal15:MDPWireless,White93:Apps,QiWu07,SiBu10:MDPinAI}).
+The main objective in planning with MDPs is to compute actions of a policy that maximizes cumulated reward over time.
+While this can be done in time that scales polynomially with the number of states and actions using various algorithms
+\cite{BlonTsi:00Complexity}, in most practical applications, 
+the MDPs are described using a ``succinct'' representation and the number of states (and sometimes actions) then scale exponentially with the size of the representation.
+For specific such MDPs various hardness results show that the
+goal of computing near-optimal policies is impractical.
+One approach then is to change the goal to the more modest goal of efficiently computing actions of a policy that 
+is nearly as good as the best policy in a given restricted policy class.
+The choice of the policy class, within some limits, is left to the user. 
+Stronger methods give more flexibility to the user in choosing the policy class.
+
+%One promising class of methods is built on the idea of
+
 The  framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems arising in science and engineering.

### 2017-03-20 mdp.tex
intro

@@
 The framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems in stochastic environments.
-In this section, we present a brief overview of the MDP framework, introducing the notions of policy, value function and optimality (please refer to \cite{BertB} for a detailed presentation on MDP).\par
+In this section, we present a brief overview of the MDP framework, introducing the notions of policy, value function and optimality (please refer to \cite{BertB} for a detailed presentation on MDP).
+
 \textbf{Model:} We consider an MDP with a finite state space given by $S=\{1,2,\ldots,n\}$ and a finite action space given by $A=\{1,2,\ldots,d\}$ (where the sentiment is that $n$ is large).
@@
 The probability transition kernel $P$ collects the probabilities $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$ for all possible $s,s'\in S$ and $a\in A$.
-We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\par
+We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
+
 \textbf{Policy:} A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
-Under an SDP, an MDP is a Markov chain whose probability transition matrix is denoted by $P_u$.\par
+Under an SDP, an MDP is a Markov chain whose probability transition matrix is denoted by $P_u$.
+
 \textbf{Value Function:} Given an SDP $u$, the expected total discounted reward corresponding to starting at a state $s\in S$ at $t=0$, while choosing actions as dictated by $u$ for the states encountered in the future (i.e., $t>0$), is
@@
 In what follows it will be useful for us to treat it as an $n$-dimensional vector, i.e., an element of $\R^n$, effectively identifying $\R^S$ with $\R^n$ in the natural way.
-Similarly we identify $\R^{nd}$ with $\R^{S\times A}$, where $d=|A|$.\par
+Similarly we identify $\R^{nd}$ with $\R^{S\times A}$, where $d=|A|$.
+
 \textbf{Optimality and the Bellman Equation:} The \emph{optimal policy} $u^*$ is one that in each state $s\in S$ achieves the best possible total expected discounted reward from that state.
@@
 \end{subequations}
-where ties in \eqref{bellpol} are resolved arbitrarily.\par
+where ties in \eqref{bellpol} are resolved arbitrarily.
+
 For the subsequent sections, the following definitions will be useful later:
@@
 Thus computing $J^*$ is at the heart DP methods \cite{BertB} such as value-, or policy-iteration and linear programming (LP) \eqref{mdplp} which can be used in practice when the MDP has a tractable number of states.
-However, when the MDP has a large number of states, using DP methods to obtain $J^*$ is tedious, since they involve computations in variables that are of the order of the number of states.\par
+However, when the MDP has a large number of states, using DP methods to obtain $J^*$ is tedious, since they involve computations in variables that are of the order of the number of states.
+
 Approximate dynamic programming (ADP) methods are based on DP methods, but employ (value) function approximation to ease the computational overhead encountered in MDPs with a large number of states.
@@
 Secondly, a greedy policy $\tilde{u}=u_{\tj}$ (see \Cref{notations}-\eqref{greedy}) can be found using the approximate value function.
-Note that all computations are $O(k)$ which is independent of the number of states.\par
+Note that all computations are $O(k)$ which is independent of the number of states.
+
 It is natural to expect that approximations lead to errors and it is important to quantify the errors.

### 2017-03-20 talk-abstract.tex
intro

Title: Towards a rigorous approach to approximate computations in huge-scale Markovian decision processes
Based on joint with Chandrashekar Lakshminarayanan and Shalabh Bhatnagar.

In this talk, without assuming any background beyond familiarity with basic probability and 
linear algebra, I will describe exciting new results on the computation of near-optimal policies in 
huge-scale Markovian decision processes (MDPs) via the so-called approximate linear programming methodology.
In a nutshell, the new results provide meaningful upper bounds on the quality of the computed policies
as a function of the linear basis functions chosen by the algorithm designer, while avoiding unrealistic assumptions
which have effectively become the norm in prior results. 
As opposed to previous work that relied on worst-case reasoning over randomly sampled constraints,
in this work the analysis is done using an operator-theoretic approach.
I will finish by discussing the remaining main open problems, connections to alternative approaches,
as well as potential extensions.
Markov decision processes lie at the hear of many reinforcement learning algorithms and have found
numerous applications across many engineering and scientific problems. 
----
Sequential decision making under uncertainty is a common element of numerous important scientific and engineering problems.
These problems are often phrased as Markov decision processes
Many important scientific and engineering problems involve sequential decision making under uncertainty.
----
MDPs are often used to model the dilemma of an agent who is trying to control its stochastic environment,
has widespread applications in science and engineering and is at the heart of formulating reinforcement learning problems.
Markovian decision processes merge Markov chains with elements of control:
The controlling agent observe a state, chooses an action, which results in a stochastic Markov transition 
to a next state while incurring some reward. The goal is to maximize the total expected discount reward.
While many problems can be modeled as MDPs, the number of states in these MDPs is more often than not is
at a scale so that only sublinear computations in the number of states are feasible. 
A common methodology uses compact representations based on linear function approximation.
The question then becomes how to interact with an oracle that gives a local, state-based access to the MDP
to efficiently compute a near-optimal policy.
----

to

Since Bellman it has been widely recognized that value-functions, mapping states of the process to reals, representing
the "value" of being in a given state, lie at the heart

A common computation model assumes state-based oracle access to the MDP
The algorithms that compute actions of a near-optimal "policy" can obtain averages of any selec

tend to have a state  where the number of states is intractably large,
A key problem is to compute given a large-scale model
Without assuming background knowledge on MDPs and reinforcement learning,

in this talk 
describe exciting new results on using approximate linear programming

building on linear programming

A common element of numerous important scientific and engineering problems is that

MDPs math model to capture seq. dec. making.
A discounted MDP is composed of states, actions, next-state distributions for each state-action pair, a reward
for each state-action pair and a discount factor in the (0,1) open interval.
An agent in an MDP, knowing which state it is at,
takes an action to arrive stochastically at some next state while incurring some reward.
An optimal behavior is one that maximizes the total expected discounted reward from any state.
The computational question is

The goal is to compute a policy, a map from states to actions, that maximizes from each state the total
expected discounted reward over time.
At a high level one is given finitely many Markov transition matrices, each matrix corresponding to one action.
The matrices capture stochastic transitions under the effect of an action.

If MDPs are the math model, how do we compute good
Core

What is the problem?
Computation of near-optimal policies in large scale MDPs.
State-based oracle access to large scale MDP, features for capturing the optimal value function.

Why should we care?

What's left?
Is this even asking the right question? Search in policy space vs. value space (direct vs. indirect).

This is a non-adaptive method.
Would adaptive methods work better?

Linear vs. nonlinear.

Applications of the LP approach to ADP range from scheduling in queueing networks (Morrison and Kumar., 1999; Veatch, 2005; Moallemi et al., 2008), revenue management (Adelman, 2007; Farias and Van Roy, 2007; Zhang and Adelman, 2008), portfolio management (Han, 2005), inventory problems (Adelman, 2004; Adelman and Klabjan, 2009), and algorithms for solving stochastic games (Farias et al., 2008) among others.

Approximate linear programming (ALP) and its variants have been widely applied to Markov Decision Processes (MDPs) with a large number of states. A serious limitation of ALP is that it has an intractable number of constraints, as a result of which constraint approximations are of interest. In this paper, we define a generalized reduced linear program (GRLP) that has a tractable number of constraints, which are obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is a novel theoretical framework developed to obtain error bounds for any given GRLP. By providing a detailed error analysis for the GRLP, we justify usage of a linear architecture for approximating the dual variables. Unlike prior results on constraint sampling, our analysis is deterministic and is based on a novel contraction operator.
\end{abstract}
\begin{keywords}{
Approximate Dynamic Programming (ADP), Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), Generalized Reduced Linear Program (GRLP), Constraint Sampling, Reinforcement Learning.}
\end{keywords}

### 2017-03-20 intro.tex
new ref

@@
 \section{Introduction}
-Markov decision processes (MDPs) have proved to be an indispensable model for sequential decision making under uncertainty with applications in networking, traffic control, robotics, operations research, business, finance, artificial intelligence, health-care and more (see, e.g., \cite{BauRie:11,Puter,FeiSh02:MDPHandbook,Abuetal15:MDPWireless,White93:Apps,QiWu07,SiBu10:MDPinAI}).
+Markov decision processes (MDPs) have proved to be an indispensable model for sequential decision making under uncertainty with applications in networking, traffic control, robotics, operations research, business, finance, artificial intelligence, health-care and more (see, e.g., \cite{BauRie:11,Puter,FeiSh02:MDPHandbook,Abuetal15:MDPWireless,White93:Apps,QiWu07,SiBu10:MDPinAI,BouDi17:MDPPractice}).
 The main objective in planning with MDPs is to compute actions of a policy that maximizes cumulated reward over time.

### 2017-03-20 intro.tex
intro finalized

--- 2017-03-01 intro.tex
@@
 \section{Introduction}
+Markov decision processes (MDPs) have proved to be an indispensable model for sequential decision making under uncertainty with applications in networking, traffic control, robotics, operations research, business, finance, artificial intelligence, health-care and more (see, e.g., \cite{
+White93:Apps,
+rust96:book,
+FeiSh02:MDPHandbook,
+QiWu07,
+SiBu10:MDPinAI,
+BauRie:11,Puter,
+LeLiu12:RLBook,
+Abuetal15:MDPWireless,
+BouDi17:MDPPractice}).
+In this paper we adopt the framework of discrete-time, discounted MDPs when
+a controller steers the stochastically evolving state of a system while receiving 
+rewards that depends on the states visited and actions chosen.
+The goal is to choose the actions so as to maximize the \emph{return}, defined as the total discounted expected reward.
+A controller that uses past state information is called a \emph{policy}.
+An \emph{optimal policy} is one that maximizes the value no matter where the process is started from \cite{Puter}.
+In this paper we consider planning problems where the goal is to calculate actions of policies that give rise to high values
+ and give new error bounds on the quality of solutions obtained by solving linear programs of tractable size. 
+To explain the contributions in more details, we start by describing the computational challenges involved in planning.
+
+The main objective of \emph{planning} is to compute actions of an optimal policy while interacting with an MDP model. 
+In finite state-action MDPs,
+assuming access to individual transition probabilities and rewards along transitions, 
+various algorithms are available to perform this computation in time and space that scales polynomially with the number of states and actions.
+However, in most practical applications, the MDP is compactly represented
+and if it is not infinite, the number of states scale \emph{exponentially} with the \emph{size of the representation} of the MDP.
+%an effect that is known as \emph{Bellman's curse of dimensionality}.
+If planners are allowed to perform some fixed amount of calculations for each state encountered,
+it is possible to use sampling to make the per-state calculation-cost 
+independent of the size of the state space \cite{rust96:randomization,szepesvari2001,kearns2002sparse}.
+Nevertheless, the resulting methods are still quite limited. 
+In fact, various hardness results show that computing actions of (near-) optimal policies is intractable in various senses
+and in various compactly represented MDPs \cite{BlonTsi:00Complexity}.
+Given these negative results, 
+it is customary to adopt the \emph{modest goal of efficiently computing actions of a policy that 
+is nearly as good as the best policy in a given restricted policy class}.
+Here, within some restrictions (see below), the policy class can be chosen by the user.
+The more flexibility the user is given in this choice, the stronger a planning method is.
+
+A popular approach along these lines, which goes back to \citet{SchSei85}, 
+relies on considering linear approximations to the \emph{optimal value function}:
+The idea is that, similarly to linear regression, a fixed sequence of basis functions are combined
+linearly. The user's task is to use a priori knowledge of the MDP 
+to choose the basis functions so that 
+a good approximation to the optimal value function will exist in the linear space spanned by the basis functions.
+The idea then is to design some algorithm to find the coefficients of the basis functions that gives a a good approximation, 
+while keeping computation cost in check.
+Finding a good approximation is sufficient, since at the expense of an extra $O(1/\epsilon^2)$ randomized computation, 
+a uniform $O(\epsilon)$-approximation 
+to the optimal value function can be used to calculate an action of an $O(\epsilon)$-optimal policy at any given state
+(e.g., follow the ideas in \cite{szepesvari2001,kearns2002sparse}; see also Theorem 3.7 of \citet{Kall17}).
+Since the number of coefficients can be much smaller than the number of states, the algorithms that search
+for the coefficients have the potential to run efficiently regardless of the number of states.
+
+Following \citet{SchSei85}, most of the literature considers
+algorithms that are obtained from restricting exact planning methods to search 
+in the span of the fixed basis functions when performing computations.
+In this paper we consider the so-called \emph{approximate linear programming} (ALP) approach, which
+was heavily studied during the last two decades 
+\cite[e.g.,][]{
+schuurmans,
+gkp,
+ALP,
+CS,
+kveton2004heuristic,
+petrik,
+SALP,
+fs,
+npalp,
+BhatFaMo12:SALPNP,
+abbasi}.
+The basic idea here is to combine a linear program whose solution is the optimal value function (and thus the number of optimization variables in it scales with the number of states) with a linear constraint that restricts the optimization variables to lie in the subspace spanned by the basis functions.
+As already noted by \citet{SchSei85}, the new LP can still be kept feasible by just adding one special basis function, while by substituting the ``value function candidates'' with their linear expansions, the number of optimization variables becomes the number of basis functions.
+As shown by \citet{ALP}, the solution to the resulting LP is within a constant factor of the best approximation to the optimal value function within the span of the chosen bases.
+However, since the number of constraints in the LP is still proportional to the number of states, it is not obvious whether a solution to the resulting LP can be found in time independent of the number of states (other computations can be done in time independent of the number of states, e.g., using sampling, at the price of a controlled increase of the error, e.g., Theorem 6 of \citep{petrik}).
+
+Most of the literature is thus devoted to designing methods to select a tractable subset of the constraints while keeping the approximation guarantees, as well as keeping computations tractable. 
+For example, \citet{schuurmans} and \citet{gkp} propose constraint generation in a setting 
+where the MDP has additional structure (i.e., factorized transition structure) 
+that is then exploited in the constraint generation method.
+A more general approach due to \citet{CS} 
+is to choose a random subset of the constraints 
+by choosing states to be included at random from a distribution that reflects the ``importance'' of states.
+While constraint generation is powerful when applicable,
+it is not known how solution quality degrades with the budget on the constraints generated.
+For constraint sampling,  \citet{CS} prove a bound on the suboptimality, but this bound applies only 
+in the unrealistic scenario when the constraints are sampled from an \emph{idealized} distribution,
+which is related to the stationary distribution of an optimal policy. 
+While it is possible to extend this result
+to any sampling distribution, the bound then scales with the mismatch between the sampling and the idealized
+distributions, which, in general, will be uncontrolled. 
+Another weakness of the bound is related to that when constraints are dropped, the linear program may become
+unbounded. To prevent this, \citet{CS}  propose adding an extra constraint on the optimization variables.
+The bound they obtain, however, scales with the \emph{worst approximation error} over this constraint set.
+While in a specific example it is shown that this error can be controlled, no general results are derived in this direction.
+Later works, such as that of
+\citet{SALP,BhatFaMo12:SALPNP},  repeat the analysis of \citet{CS}
+in combinations with other ideas. However, no existing work that we know of addresses the above weaknesses of the result of \citet{CS}.
+
+Our main contribution is a new suboptimality bound for the case when the constraint system is replaced with a smaller, 
+linearly projected constraint system. We also propose a specific way of adding the extra constraint to keep the resulting LP bounded.
+Rather than relying on combinatorial arguments (such as those at the heart of \citet{CS}), our argument uses previously unexploited geometric structure of the linear programs underlying MDPs.
+As a result our bound avoids distribution-mismatch terms and we also remove the scaling with worst approximation error.
+A specific outcome of our general result is the realization that it is beneficial to select states so that the ``feature vectors'' of all states when scaled with a fixed constant factor are included in the conic hull of the ``feature vectors'' underlying the selected states.
+This suggests to choose the basis functions so that this property can be satisfied by selecting only a few states.
+As we will argue, this property holds for several popular choices of basis functions.
+A preliminary version of this paper without the theoretical analysis and without the geometric arguments was published in a short conference communication \cite{aaaipaper}.
+
+\if0
+
 The  framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems arising in science and engineering.
@@
 \end{comment}
+\fi

### 2017-03-21 grlp.tex
LP edits

@@
 \end{comment}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Generalized Reduced Linear Programming}\label{sec:grlp}
-The Generalized Reduced Linear Program is given as:
+\todoc{How about the cleaner ``Linear projected approximate linear programming''}
+In this section we introduce the computational model used and the optimization problem
+that is the main object of our study.
+As discussed in the introduction, we are interested in methods that compute a good approximation to the optimal value function.
+As noted earlier, at the expense of a modest additional cost, knowing an $O(\epsilon)$ approximation to $J^*$ at a few states suffices to compute actions of an $O(\epsilon)$-optimal policy.
+We will take a more general view, and we will consider calculating good approximations to $J^*$ with respect to a weighted $1$-norm, where the weights $c$ form a probability distribution over $\S$.
+Recall that the weighted $1$-norm $\norm{J}_{1,c}$ of a vector $J\in \R^S$ is defined as $\norm{J}_{1,c}  = \sum_s c(s) |J(s)|$.
+Note that here and in what follows we identify elements of $\R^\S$ (functions, mapping $\S = \{1,\dots,S\}$ to the reals) with elements of $\R^S$ in the obvious way.
+This allows us to write e.g.
+$c^\top J$, which denotes $\sum_s c(s) J(s)$.
+
+To introduce the optimization problem we study first recall that 
+the optimal value function $J^*$ is the solution of the fixed point equation $TJ^* = J^*$. 
+It follows from the definition of $T$ that $J^* = \max_u T_u J^* \ge T_u J^*$ for any $u$, 
+where $\ge$ is the componentwise partial ordering of vectors. 
+With some abuse of notation, we also introduce $T_a$ to denote $T_u$ where $u(s) = a$ for any $s\in \S$. 
+It follows that $J^* \ge T_a J^*$ for any $a\in \A$ and also that $T = \max_a T_a$, where again the maximization is componentwise.
+We call a vector $J$ that satisfies $J \ge T_a J$ for any $a\in A$ \emph{superharmonic}. Note that this is a set of linear inequalities. 
+By our note on $T$ and $(T_a)_a$, these inequalities can also be written compactly as $J \ge T J$.
+\if0
+Since $T$ is monotone (i.e., for any $J_1\le J_2$ it holds that $TJ_1 \le T J_2$) and can be seen to be an $\alpha$-contraction with respect to the maximum norm, if $J$ is superharmonic then $J \ge T J \ge T^2 J \ge \dots \ge J^*$, where the last inequality follows since $T$ is an $\alpha$-contraction and hence $T^n J \to J^*$ in the maximum norm, and hence also componentwise.
+Thus, $J^*$ is the ``smallest'' superharmonic function. It follows than that 
+for any $c\in \R_+^S \doteq [0,\infty)^S$ and any superharmonic $J$, $c^\top J^*\le c^\top J$ and since $J^*$ is also superharmonic, $\min \{ c^\top J\,:\, J \ge T J \} = c^\top J^*$ and if $c$ is positive-valued then the minimizer of $c^\top J$ amongst all superharminoc functions is $J^*$.
+\fi
+It is not hard to show then that $J^*$ is the smallest superharminoc function (i.e., for any $J$ superharmonic, $J\ge J^*$).
+It also follows that for any  $c\in \R_{++}^S \doteq (0,\infty)^S$, the unique solution to the linear program $\min\{ c^\top J \,:\, J \ge T J \} =\min \{ c^\top J\,:\, J \ge T_a J, a\in \A \} $ is $J^*$.
+
+Now, let $\phi_1,\ldots,\phi_k : \S \to \R$ be $k$ basis functions. 
+\todoc{I think we should use $d$ to denote the number of basis functions. Or at least $n$. Low priority.} 
+The \emph{Approximate Linear Program} (ALP) of \citet{SchSei85} 
+is obtained by adding the linear constraints $J = \sum_{i=1}^k r_i \phi_i$ to the above linear program.
+Eliminating $J$ then gives $\min\{ \sum_i r_i c^\top \phi_i \,:\, \sum_i r_i \phi_i \ge g_a + \alpha \sum_i r_i P_a \phi_i, a\in \A, r = (r_i)\in \R^k \}$.
+As noted by \citet{SchSei85}, the linear program is feasible as long as $\one$, defined as the vector with all components being identically equal to one, is in the span of $\{\phi_1,\dots,\phi_k\}$. 
+\emph{For the purpose of computations, it is assumed that the values $c^\top \phi_i$, $i=1,\dots, k$ and the values $(P_a \phi_i)(s)$ and $g_a(s)$ can be accessed in constant time.} 
+This assumption can be relaxed to assuming that one can access $g_a(s)$ and $\phi_i(s)$ for any $(s,a)$ in constant time, as well as to that one can efficiently sample from $c$, from $P_a(s,\cdot)$ for any $(s,a)$ pair,
+but the details of this are the beyond the scope of the present work.
+As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi r$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$ where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm.
+
+While evaluating the objective and checking a single constraint for constraint violations can be done in constant time, 
+since the number of constraints in the ALP is equal to the number of state-action pairs, the ALP is still intractable in general.
+To reduce the number of constraints, we propose to relax the constraints by considering a linear projection of them with 
+positive linear coefficients.
+Since the resulting program may become unbounded, it is necessary to introduce an additional constraint $r\in \N$, where $\N$ will be chosen to be large enough so as not to exclude ``good solutions'', while constraining enough so as to prevent unbounded solutions.
+\todoc{I still don't get whether we need or not $\N$.
+Under the conic constraints, do we need it or not?
+I mean when $r$ hits the boundary of $\N$ I have the feeling that we get a very bad solution and it would not then matter much whether $\N$ is even there or not.}
+This leads to what we call the Generalized Reduced Linear Program: \todoc{Again, Linearly Projected ALP, or ALP with Linear Constraint Projection, or with Linear Constrain Relaxation?} \todoc{I stopped here, need to sleep.
+The idea in this section is to just explain how the computation is done.
+In the next section I would just give the main result.
+In the next section I would give the proof.
+Rather than the present lemma, lemma, lemma..
+organization it is probably better to organize the proof in a top-down.
+Starting to do the proof, required results can be stated as claims/lemmas.
+But maybe some of the lemmas can be saved (I have a specific plan, just saying, if you want to do something with this).}
 \begin{align}\label{grlp}

### 2017-03-21 intro.tex
LP edits

@@
 it is customary to adopt the \emph{modest goal of efficiently computing actions of a policy that 
-is nearly as good as the best policy in a given restricted policy class}.
+is nearly as good as the best policy \todoc{This is too ambitious still. Need to tweak.}
+in a given restricted policy class}.
 Here, within some restrictions (see below), the policy class can be chosen by the user.
@@
 Most of the literature is thus devoted to designing methods to select a tractable subset of the constraints while keeping the approximation guarantees, as well as keeping computations tractable. 
-For example, \citet{schuurmans} and \citet{gkp} propose constraint generation in a setting 
-where the MDP has additional structure (i.e., factorized transition structure) 
-that is then exploited in the constraint generation method.
-A more general approach due to \citet{CS} 
+Since a linear objective is optimized by a point on the boundary of the feasible region, 
+knowing the optimizer would be sufficient to eliminate all but 
+as many constraints as the number of optimization variables.
+The question is how to find a superset of these, or an approximating set, without incurring much computational overhead.
+\citet{schuurmans} and \citet{gkp} propose constraint generation in a setting 
+where the MDP has additional structure (i.e., factorized transition structure).
+This additional structure is then exploited in designing constraint generation methods which are able to efficiently generate
+violated constraints. A more general approach due to \citet{CS} 
 is to choose a random subset of the constraints 
 by choosing states to be included at random from a distribution that reflects the ``importance'' of states.
-While constraint generation is powerful when applicable,
-it is not known how solution quality degrades with the budget on the constraints generated.
+While constraint generation can be powerful,
+it is not known how solution quality degrades with the budget on the constraints generated
+(\citeauthor{gkp} note that the number of constraints generated can be at most exponential in a fundamental quantity,
+the induced width of a so-called cost-network, which may be large and is in general hard to control).
 For constraint sampling,  \citet{CS} prove a bound on the suboptimality, but this bound applies only 

### 2017-03-21 mdp.tex
LP edits

@@
 %!TEX root =  autocontgrlp.tex
-\section{Background: Markov Decision Processes (MDPs)}
-The framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems in stochastic environments.
+\section{Background} %: Markov Decision Processes (MDPs)}
+%The framework of Markov decision processes (MDPs) is useful to mathematically cast optimal sequential decision making problems in stochastic environments.
 In this section, we present a brief overview of the MDP framework, introducing the notions of policy, value function and optimality (please refer to \cite{BertB} for a detailed presentation on MDP).
+The purpose of this section is to introduce the necessary background before we can present the problem studied and the main results.
 
-\textbf{Model:} We consider an MDP with a finite state space given by $S=\{1,2,\ldots,n\}$ and a finite action space given by $A=\{1,2,\ldots,d\}$ (where the sentiment is that $n$ is large).
-For simplicity, we assume that all actions are feasible in all states.
-The probability transition kernel $P$ collects the probabilities $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$ for all possible $s,s'\in S$ and $a\in A$.
+We shall consider finite state-action space, discounted total expected reward MDPs.
+We note in passing that the assumption that number of states is finite is mainly made for convenience and at the expense of a more technical presentation could be lifted.
+We will comment later on the assumption concerning the number of actions.
+Let the set of states, or state space be $\S = \{1,2,\dots,S\}$ and let the set of actions be $\A = \{1,2,\dots,A\}$.
+\todoc{$\S$ is for state space, $S$ for number of states, $\A$, $A$, similarly.
+Thus, $S=n$, $A=d$.}
+For simplicity, we assume that all actions are admissible in all states. 
+Given a choice of an action $a\in \A$ in a state $s\in \S$, the controller incurs a reward (or gain) of $g_a(s)\in [0,1]$ 
+and the state moves to a next state $s'\in \S$ with probability $p_{a}(s,s')$. 
+A \emph{policy} $u$ is a mapping from states to actions.\footnote{For the scope of this paper, it suffices to restrict our attention to such policies as opposed to considering history dependent policies.
+See Chapter 3, and specifically Corollary 3.3 of \cite{Kall17}.}
+When a policy is followed, the state sequence evolves as a Markov chain with transition probabilities given by $P_u$ matrix whose $(s,s')$th entry is $P_{u(s)}(s,s')$.
+Along the way the rewards generated from $g_u$ defined by $g_u(s) \defeq g_{u(s)}(s)$.
+The \emph{value} of following a policy from a starting state $s$ is denoted by $J_u(s)$ and is defined as 
+the expected total reward discounted reward. Thus,
+%The probability transition kernel $P$ collects the probabilities $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$ for all possible $s,s'\in S$ and $a\in A$.
 We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.
 
-\textbf{Policy:} A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
+%\textbf{Policy:} A stationary deterministic policy(SDP), or simply a policy, is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
 Under an SDP, an MDP is a Markov chain whose probability transition matrix is denoted by $P_u$.
 
-\textbf{Value Function:} Given an SDP $u$, the expected total discounted reward corresponding to starting at a state $s\in S$ at $t=0$, while choosing actions as dictated by $u$ for the states encountered in the future (i.e., $t>0$), is
+%\textbf{Value Function:} Given an SDP $u$, the expected total discounted reward corresponding to starting at a state $s\in S$ at $t=0$, while choosing actions as dictated by $u$ for the states encountered in the future (i.e., $t>0$), is
 \begin{align}
-J_u(s)\stackrel{\Delta}{=}\E[\sum_{t=0}^\infty \alpha^t g_{a_t}(s_t)|s_0=s,a_t=u(s_t)\mbox{ }\forall t\geq 0],\nn
+%J_u(s)\stackrel{\Delta}{=}\E[\sum_{t=0}^\infty \alpha^t g_{a_t}(s_t)|s_0=s,a_t=u(s_t)\mbox{ }\forall t\geq 0],\nn
+J_u(s)\defeq \sum_{t=0}^\infty \alpha^t (P_u^t g_u)(s)\,,\nn
+%\E[\sum_{t=0}^\infty \alpha^t g_{a_t}(s_t)|s_0=s,a_t=u(s_t)\mbox{ }\forall t\geq 0],\nn
 \end{align}
-where $\alpha \in (0,1)$ is the so-called discount factor and $s_{t+1} \sim p_{a_t}(s_t,\cdot)$, $t\ge 0$.
-We call $J_u(s)$ the value of state $s$ under SDP $u$, while $J_u$ (as a map from $S$ to the reals)
-is called the value function underlying policy $u$.
+where  $\alpha \in (0,1)$ is the so-called discount factor. % and $s_{t+1} \sim p_{a_t}(s_t,\cdot)$, $t\ge 0$.
+We call $J_u$ the \emph{value function} of policy $u$.
+The value function of a policy satisfies the fixed-point equation $J_u = T_u J_u$ where the affine-linear operator $T_u$ is defined by $T_u J = g_u + \alpha P_u J$.
+An \emph{optimal policy}, is one that maximizes the value simultaneously for all initial states.
+The \emph{optimal value function} $J^*$ is defined by $J^*(s) = \max_u J_u(s)$ and is known to be the solution of the fixed-point equation $J^* = T J^*$ where the operator $T$ is defined by $(TJ)(s) = \max_u (T_u J)(s)$, $s\in \S$, i.e., the maximization is component-wise.
+Optimal policies exist and in fact any policy $u$ such that the equation $T_u J^* = T J^*$ holds is optimal (e.g., Corollary 3.3 of \cite{Kall17}).
+A policy $u$ is said to be \emph{greedy} with respect to (w.r.t.) $J$ if $T_u J = T J^*$.
+Thus, any policy that is greedy w.r.t.
+$J^*$ is optimal.
+
+\if0
 The value functions $J_u$ is an elements of $\R^S$.
@@
 where ties in \eqref{bellpol} are resolved arbitrarily.
-
 For the subsequent sections, the following definitions will be useful later:

### 2017-03-21 cone.tex
cone file added

\begin{theorem}
Let $\phi(s)$^\footnote{Here $\phi(s)$ is the $s^{th}$ row of the feature matrix $\Phi$} be the feature of the $s^{th}$ state. Let $i$ be a state whose constraints have not been retained and let $\{J}$ denote the set of states whose constraints have been retained. Further, let $\phi(i)\in \R^k$ lie in the linear span of vectors $\phi(j)\in \R^k,\forall j\in \J$, then
\begin{align}
(\Gamma J^*-\hg J^*)(i) \leq (\Gamma J^*-J^*)(i)+J^*(i)-\underset{j\in \J}{\sum} |\gamma_j| J^*(j)+ \underset{j\in \J}(|\gamma_j|-\gamma_j) B,
\end{align}
where $\gamma_j$ are the co-efficients of the linear span and $B\eqdef \underset{\underset{s\in S}{r\in \N}}{\max}(\Phi r) (s)$
\end{theorem}
\begin{proof}
Let $r^s_{\Gamma}$ and $r^s_{\hg}$ be such that $(\Phi r^s_{\Gamma})(s)=(\Gamma J^*)(s)$ and $(\Phi r^s_{\hg})(s)=(\hg J^*)(s)$
\begin{algin}
(\Gamma J^*-\hg J^*)(i) &=\phi(i) r^s_{\Gamma}- \phi(i) r^s_{\Gamma}
&=\phi(i) r^i_{\Gamma}- \underset{j\in \J}(|\gamma_j|+\gamma_j -|\gamma_j|)\phi(j) r^i_{\hg}
\leq \phi(i) r^i_{\Gamma}- \underset{j\in \J}|\gamma_j| J^*(j) + \underset{j\in \J} (|\gamma_j|-\gamma_j)B
= \phi(i) r^i_{\Gamma}- J^*(i)+ J^*(i) -\underset{j\in \J}|\gamma_j| J^*(j) + \underset{j\in \J} (|\gamma_j|-\gamma_j)B
\end{align}
\end{proof}

### 2017-03-22 cone.tex
integrating cone constraint

@@
+%!TEX root =  autocontgrlp.tex
 \begin{theorem}
-Let $\phi(s)$^\footnote{Here $\phi(s)$ is the $s^{th}$ row of the feature matrix $\Phi$} be the feature of the $s^{th}$ state.
-Let $i$ be a state whose constraints have not been retained and let $\{J}$ denote the set of states whose constraints have been retained.
+Let $\phi(s)$%
+\footnote{Here $\phi(s)$ is the $s^{th}$ row of the feature matrix $\Phi$} be the feature of the $s^{th}$ state.
+Let $i$ be a state whose constraints have not been retained and let $\{J\}$ denote the set of states whose constraints have been retained.
 Further, let $\phi(i)\in \R^k$ lie in the linear span of vectors $\phi(j)\in \R^k,\forall j\in \J$, then
-\begin{align}
-(\Gamma J^*-\hg J^*)(i) \leq (\Gamma J^*-J^*)(i)+J^*(i)-\underset{j\in \J}{\sum} |\gamma_j| J^*(j)+ \underset{j\in \J}(|\gamma_j|-\gamma_j) B,
-\end{align}
+\begin{align*}
+\MoveEqLeft (\Gamma J^*-\hg J^*)(i)
+ \leq 
+(\Gamma J^*-J^*)(i) \\
+& {}+J^*(i)-\underset{j\in \J}{\sum} |\gamma_j| J^*(j)
++ \underset{j\in \J}(|\gamma_j|-\gamma_j) B,
+\end{align*}
 where $\gamma_j$ are the co-efficients of the linear span and $B\eqdef \underset{\underset{s\in S}{r\in \N}}{\max}(\Phi r) (s)$
@@
 Let $r^s_{\Gamma}$ and $r^s_{\hg}$ be such that $(\Phi r^s_{\Gamma})(s)=(\Gamma J^*)(s)$ and $(\Phi r^s_{\hg})(s)=(\hg J^*)(s)$
-\begin{algin}
-(\Gamma J^*-\hg J^*)(i) &=\phi(i) r^s_{\Gamma}- \phi(i) r^s_{\Gamma}
-&=\phi(i) r^i_{\Gamma}- \underset{j\in \J}(|\gamma_j|+\gamma_j -|\gamma_j|)\phi(j) r^i_{\hg}
-\leq \phi(i) r^i_{\Gamma}- \underset{j\in \J}|\gamma_j| J^*(j) + \underset{j\in \J} (|\gamma_j|-\gamma_j)B
-= \phi(i) r^i_{\Gamma}- J^*(i)+ J^*(i) -\underset{j\in \J}|\gamma_j| J^*(j) + \underset{j\in \J} (|\gamma_j|-\gamma_j)B
-\end{align}
+\begin{align*}
+\MoveEqLeft (\Gamma J^*-\hg J^*)(i) 
+=\phi(i) r^s_{\Gamma}- \phi(i) r^s_{\Gamma}\\
+&=\phi(i) r^i_{\Gamma}- \underset{j\in \J}(|\gamma_j|+\gamma_j -|\gamma_j|)\phi(j) r^i_{\hg}\\
+&\leq \phi(i) r^i_{\Gamma}- \underset{j\in \J}|\gamma_j| J^*(j) + \underset{j\in \J} (|\gamma_j|-\gamma_j)B\\
+&= \phi(i) r^i_{\Gamma}- J^*(i)+ J^*(i) -\underset{j\in \J}|\gamma_j| J^*(j) \\
+& \quad + \underset{j\in \J} (|\gamma_j|-\gamma_j)B\,.
+\end{align*}
 \end{proof}

### 2017-03-22 grlp.tex
integrating cone constraint

@@
 but the details of this are the beyond the scope of the present work.
-As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi r$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$ where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm.
+As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi r$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$ where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm and $\Phi \in \R^{S\times k}$ is the matrix formed by $(\phi_1,\dots,\phi_k)$.
 

### 2017-03-22 grlp.tex
Relaxed program text

--- 2017-03-21 grlp.tex
@@
 but the details of this are the beyond the scope of the present work.
-As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi r$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$ where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm.
+As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi \ralp$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$, where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm and $\Phi \in \R^{S\times k}$ is the matrix formed by $(\phi_1,\dots,\phi_k)$.
+That the error of approximating $J^*$ with $\Jalp$ is $O(\epsilon)$ is significant: The user can focus on finding a good basis, leaving the search for the ``right'' coefficients to a linear program solver.
 
-While evaluating the objective and checking a single constraint for constraint violations can be done in constant time, 
-since the number of constraints in the ALP is equal to the number of state-action pairs, the ALP is still intractable in general.
-To reduce the number of constraints, we propose to relax the constraints by considering a linear projection of them with 
-positive linear coefficients.
+While the solving the ALP can be significantly cheaper than solving the LP underlying the MDP
+and thus it can be advantageous for moderate-scale MDPs,
+ \todoc{Give the big-Oh costs!} the number of constraints in the ALP is $SA$, 
+ hence the ALP is still infeasible for huge-scale MDPs. 
+%While evaluating the objective and checking a single constraint for constraint violations can be done in constant time, 
+%since the number of constraints in the ALP is equal to the number of state-action pairs, 
+%the ALP is still intractable in general.
+To reduce the number of constraints, we consider a relaxation of ALP 
+where the constraints are replaced with positive linear 
+combinations of them. 
+Recalling that the constraints took the form $J \ge g_a + \alpha P_a J$ (with $J = \Phi r$),
+choosing $m$ to be target number of constraints, for $1\le i \le m$, the $i$th new constraint is given by
+$\sum_a w_{i,a}^\top J \ge \sum_a w_{i,a}^\top(g_a + \alpha P_a J)$, 
+where the choice of $m$ and that of the vectors $w_{i,a}\in [0,\infty)^S$ is left to the user.
+Note that this results in a linear program with $k$ variables and $m$ constraints, which can be written as
+\begin{align}\label{grlp}
+\begin{split}
+&\underset{r\in \R^k}{\min}\, \, c^\top \Phi r\\
+&\text{s.t.}\mb  \,\sum_a W_a^\top \Phi r\geq \sum_a W_a^\top (g_a + \alpha P_a) \Phi r\,,
+\end{split}
+\end{align}
+where $W_a = (w_{1,a},\dots,w_{m,a}) \in [0,\infty)^{S \times m}$. 
+\todoc{Do we need that $(w_{i,a}^\top)_i$ defines a probability distribution?}
+Note that the $(i,j)$th entry of the $m\times k$ constraint matrix of the resulting LP is
+$\sum_a  w_{i,a}^\top  \phi_j - \alpha \sum_a w_{i,a}^\top P_a \phi_j$ and assuming that $(w_{i,a})_{a}$ has $p$ nonzero
+elements, this can be calculated in $O( p )$ time, making the total cost of obtaining the constraint matrix to be $O(mkp)$ regardless the value of $S$ and $A$.
+\todoc{Somewhere discuss that the cost of obtaining a policy will depend on $A$.
+We can also discuss how $A$ could be folded into states.}
+
+We will call the LP in \eqref{grlp} the \emph{linearly relaxed approximate linear program (LRALP)}.
+\todoc{Replace GRLP everywhere with LRALP.} Note that the LRALP may be unbounded.
+While unboundedness could be prevented by adding an extra constraint of the form $r\in \N$ for a ``sufficiently large'' and ``simple'' bounded polytope $\N \subset \R^k$ which can be chosen based on the knowledge of $\alpha$ alone.
+However, we see little value in this and thus stick to the above simple form.%
+\footnote{
+Note though that $\N$ would need to be chosen based on very little information,
+hence it would in general be chosen to provide an extremely loose constraint to avoid
+the accidental elimination of potentially good solutions. 
+Hence, on the occasion when the LP without the extra $r\in \N$ constraint is unbounded,
+the solution found when $r\in \N$ is added would lie on the boundary of $\N$, which
+makes one expect the error of the resulting solution to be rather large.
+}
+
 Since the resulting program may become unbounded,  it is necessary to introduce an additional constraint $r\in \N$, where $\N$ will be chosen to be large enough so as not to exclude ``good solutions'', while constraining enough so as to prevent unbounded solutions.
-\todoc{I still don't get whether we need or not $\N$.
-Under the conic constraints, do we need it or not?
-I mean when $r$ hits the boundary of $\N$ I have the feeling that we get a very bad solution and it would not then matter much whether $\N$ is even there or not.}
 This leads to what we call the Generalized Reduced Linear Program: \todoc{Again, Linearly Projected ALP, or ALP with Linear Constraint Projection, or with Linear Constrain Relaxation?} \todoc{I stopped here, need to sleep.

### 2017-03-23 grlp.tex
up to main results

@@
 $\sum_a w_{i,a}^\top J \ge \sum_a w_{i,a}^\top(g_a + \alpha P_a J)$, 
-where the choice of $m$ and that of the vectors $w_{i,a}\in [0,\infty)^S$ is left to the user.
+where the choice of $m$ and that of the vectors $w_{i,a}\in \R_+^S$ is left to the user.
 Note that this results in a linear program with $k$ variables and $m$ constraints, which can be written as
@@
 \end{align}
-where $W_a = (w_{1,a},\dots,w_{m,a}) \in [0,\infty)^{S \times m}$. 
+where $W_a = (w_{1,a},\dots,w_{m,a}) \in \R_+^{S \times m}$. 
 \todoc{Do we need that $(w_{i,a}^\top)_i$ defines a probability distribution?}
@@
 
-We will call the LP in \eqref{grlp} the \emph{linearly relaxed approximate linear program (LRALP)}.
-\todoc{Replace GRLP everywhere with LRALP.} Note that the LRALP may be unbounded.
-While unboundedness could be prevented by adding an extra constraint of the form $r\in \N$ for a ``sufficiently large'' and ``simple'' bounded polytope $\N \subset \R^k$ which can be chosen based on the knowledge of $\alpha$ alone.
-However, we see little value in this and thus stick to the above simple form.%
+We will call the LP in \eqref{grlp} the \emph{linearly relaxed approximate linear program (LRALP)}. \todoc{Replace GRLP everywhere with LRALP.} Any LP obtained using 
+any constraint selection/generation process can be represented by choosing an appropriate binary-valued matrix
+$W^\top = (W_1^\top,\dots,W_A^\top)\in \R_+^{m\times SA}$. In particular, when the constraints are selected
+in a random process as suggested by \citet{CS}, the matrix $W$ would be a random, binary-valued matrix.
+
+Note that the LRALP may be unbounded. 
+Unboundedness could be avoided by adding an extra constraint of the form $r\in \N$ to the LRALP,
+for a properly chosen polyhedron $\N \subset \R^k$.%
 \footnote{
-Note though that $\N$ would need to be chosen based on very little information,
-hence it would in general be chosen to provide an extremely loose constraint to avoid
-the accidental elimination of potentially good solutions. 
-Hence, on the occasion when the LP without the extra $r\in \N$ constraint is unbounded,
+In particular, to obtain their theoretical result, \citet{CS} need the assumption that the set $\N$ 
+is bounded and that it contains $\ralp$. In fact, 
+the error bound derived by \citeauthor{CS} depends on the \emph{worst} 
+error of approximating $J^*$ with $\Phi r$ when
+$r$ ranges over $\N$. Hence, if $\N$ is unbounded, their bound is vacuous. In the context of a particular application, 
+\citet{CS} demonstrate that $\N$ can be chosen properly to control this term. 
+However, no general construction is presented to choose $\N$.}
+However, it seems to us that it is downright misleading to think that guaranteeing a bounded solution 
+will also lead to reasonable solutions.
+Thus we will stick to the above simple form, forcing a discussion of how $W$ should be chosen to get meaningful results.%
+\footnote{
+The only question is whether there is some value in adding constraints beyond choosing $W$ properly.
+Our position is that the set $\N$ would most likely be chosen based on very little and general information;
+the useful knowledge is in choosing $W$, not in some general set $\N$. 
+Since randomization does not guarantee bounded solutions, \citet{ALP} needs to use $\N$, which incorporates
+all the knowledge which makes the LP bounded. Since 
+$\N$
+or we could incorporate the choice into $W$.
+On the occasion when the LP without the extra $r\in \N$ constraint would be unbounded,
 the solution found when $r\in \N$ is added would lie on the boundary of $\N$, which
@@
 
-Since the resulting program may become unbounded,  it is necessary to introduce an additional constraint $r\in \N$, where $\N$ will be chosen to be large enough so as not to exclude ``good solutions'', while constraining enough so as to prevent unbounded solutions.
-This leads to what we call the Generalized Reduced Linear Program: \todoc{Again, Linearly Projected ALP, or ALP with Linear Constraint Projection, or with Linear Constrain Relaxation?} \todoc{I stopped here, need to sleep.
-The idea in this section is to just explain how the computation is done.
-In the next section I would just give the main result.
-In the next section I would give the proof.
-Rather than the present lemma, lemma, lemma..
-organization it is probably better to organize the proof in a top-down.
-Starting to do the proof, required results can be stated as claims/lemmas.
-But maybe some of the lemmas can be saved (I have a specific plan, just saying, if you want to do something with this).}
-\begin{align}\label{grlp}
-\begin{split}
-&\underset{r\in \N\subset R^k}{\min}\, \, c^\top \Phi r\,\,\,\,\\
-&\text{s.t.}\mb  \,W^\top E\Phi r\geq W^\top H \Phi r,
-\end{split}
-\end{align}
-where we assume that $W \in \R^{nd\times m}_+$ is a matrix with all positive entries which specifies the linear combination of constraints.
-We denote an arbitrary solution to GRLP by $\hr$, and the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t.
-$\hj$.\\
-\textbf{RLP as a special case:} Recovering RLP \eqref{rlp} as a special case of GRLP \eqref{grlp} can be accomplished by setting $W$ to the matrix with the $i^{th}$ column having $1$ corresponding to the constraint that was sampled (implicitly assuming that there is a natural ordering of the $nd$ constraints) and all the other entries as $0$.
-The $\N$ in RLP \eqref{rlp} is retained in GRLP \eqref{grlp} as well.
-For $m=nd$ and $W=I_{nd\times nd}$, GRLP is same as ALP.\\
+Further insight into the choice of $W$ can be gained by
+considering the Langrangians of the ALP and LRALP.
+To write both LP's in a similar form let us introduce $E = (I_{S\times S},\dots,I_{S\times S})^\top$, where $I_{S\times S}$ is the $S\times S$ identity matrix.
+Further, let $H:\R^S \times \R^{SA}$ be the operator defined by $(HJ)^\top = ( (T_1 J)^\top, \dots, (T_A J)^\top )$.
+Note that $H$ is a linear operator.
+Then, the ALP can be written as $\min\{ c^\top \Phi r \,|\, E \Phi r \ge H \Phi r \}$, while LRALP takes the form
+$\min\{ c^\top \Phi r \,|\, W^\top E \Phi r \ge W^\top H \Phi r \}$. 
+Hence, their Langrangians are $\mathcal{L}_{\alp}(r,\lambda) = c^\top \Phi r+\lambda^\top (H\Phi r-E\Phi r)$
+$\mathcal{L}_{\lralp}(r,q) = c^\top \Phi r+q^\top W^\top (H\Phi r-E\Phi r)$. Thus, we can view $W q$ as a ``linear approximation''
+to the dual variable $\lambda \in \R_+^{SA}$. 
+This suggests that perhaps $W$ should be chosen such that it approximates well the optimal dual variable.
+If $\Phi$ spans $\R^{S}$, the optimal dual variable $\lambda^*$ is known to be the discounted occupancy measure underlying the optimal policy (Theorem 3.18, \cite{Kall}), suggesting that the role of $W$ is very similar to the role of $\Phi$ excepts that the subspace spanned by the columns of $W$ should ideally be close to $\lambda^*$.
+
+We denote an arbitrary solution to GRLP by $\hr$, and the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.\\
+\if0
 \textbf{Linear function approximation in Primal and Dual Variables:} Let us look at the Lagrangian of ALP and GRLP in
@@
 Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for constructing the $W$ matrix.
-\FloatBarrier
-%\input{cartoon}
-\begin{figure}
-\includegraphics[scale=0.7]{cartoon_grlp.pdf}
-\caption{
-%\normalsize
-The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints.
-The main contribution of the paper is to bound $\norm{J^*-\hat{J}_c}$.}
-\label{cartoon}
-\end{figure}
-\Cref{cartoon} shows the solutions to the LP, ALP and GRLP respectively.
-The error in ALP solution has already been studied in \cite{ALP}.
-Our objective is to study the extra source of error due to constraint approximation.
-\section{Main Results}
-In this section we present the main results of this paper in \Cref{cmt2} (we state improved bounds in \Cref{sec:improv}).
-Our bounds are expressed in terms of two novel contractions operators which we define in \Cref{lubpop,alubpop}.
-We now define two projection operators that are central to our error analysis and in them we assume that the set $\N'\subset \R^k$ is such that $\N' = \N + t \one$ for any $t\in \R$.
-%The least upper bound (LUB) projection operator $\Gamma \colon \R^n \ra\R^n$ is defined below, see \eqref{gamdef}.
-\begin{definition}\label{lubpop}
-Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r_{c,J}$ to be the solution to
-\begin{align}
-\label{lubplp}
-\begin{split}
-\underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,\mb
-\text{s.t.} \mb \Phi r\geq  TJ.
-\end{split}
-\end{align}
-For $J\in \R^n$, $\Gamma J$, the \emph{least upper} (LU) projection of $J$ is defined as
-\begin{align}\label{gamdef}
-(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
-\end{align}
-\end{definition}
-The definition of the second operator is as follows:
-\begin{definition}\label{alubpop}
-Given $J\in \R^n$ and the nonnegative valued vector $c\in \R^n_+$, define $r'_{c,J}$ to be the solution to
-\begin{align}\label{alubplp}
-\underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,\mb
-\text{s.t.} \,\,\, W^\top E \Phi r\geq W^\top HJ.
-\end{align}
-The \emph{approximate least upper} (ALU) projection operator
-$\hg \colon \R^n \ra \R^n$ is defined as
-\begin{align}\label{tgamdef}
-(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,, J\in \R^n\,.
-\end{align}
-\end{definition}
-\begin{remark}\label{ubrem}
-To understand the meaning of $\Gamma$ (and $\hg$) define
-\begin{align}\label{ubclass}
-\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N'\,\},
-\end{align}
-where $J\in \R^n$.
-Disregarding the constraint $r\in \N'$,
-$\F_J$ contains all vectors in the span of $\Phi$ that upper bound $TJ$.
-Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
-Also $\Gamma J\geq T J$.\par
-The operators $\Gamma$ and $\hg$ are closely related to ALP \eqref{alp} and GRLP \eqref{grlp} respectively and are only analytical tools that we will need to express our bounds and need not be computed in practice.
-It turns out that the novel operators ($\Gamma$ and $\hg$) are contraction maps (see \Cref{hgmaxcontramn}), a fact that is a key to our results (\Cref{cmt2mn,polthe}).
-At the outset we are interested in the candidate value functions in the constraint set $\N$ and want to study them using $\Gamma$ and $\hg$.
-However since the basis $\Phi$ contains $\one$ we make it helps our analysis to define the set $\N'$ in \Cref{lubplp,alubplp} to be `$\N$ plus its translations by $\one$'.
-\end{remark}
-%\subsection{Error Bounds}
-\begin{theorem}[Error Bound for GRLP]
-\label{cmt2}
-Let $\one\in\R^k$ be in the column span of $\Phi$, then it holds that
-\begin{enumerate}
-\item The prediction error is bound as\\
-$\norm{J^*-\hj}_{1,c}
-\leq\frac{1}{1-\alpha}(6~\us{\min}{r\in \R^k}\norm{J^*-\Phi r}_{\infty}
-+2\norm{\Gamma J^*-\hg J^*}_{\infty})$.
-\item The control error is bound as\\
-$\norm{J^* - J_{\hu}}_{1,c}
-\leq 2\left(\frac{1}{(1-\alpha)^2}\right)\, \big( 2~\us{\min}{r\in \R^k} \norm{J^*-\Phi r}_{\infty}
-+\norm{\Gamma J^*-\hg J^*}_{\infty}+\norm{\hj-\hg\hj}_{\infty}\big)$.
-\end{enumerate}
-\end{theorem}
-\textbf{On Prediction Error:} The first factor in the right hand side of the prediction error in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$.
-This term is an carry over of the upper bound in ALP formulation as shown in \Cref{alpvanilla}.
-The second factor in the right hand side of the prediction error is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.\par
-\textbf{On Control Error:} The first two terms are quite similar to those in the bound for prediction error.
-The third term occurs due to the fact that $\Phi \geq T\Phi r$ that holds in the case of ALP does not hold in the case of GRLP.\par
-\begin{comment}
-\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
-\label{polthe}
-Let $\hu$ be the greedy policy with respect to the solution $\hj$ of GRLP and $J_{\hu}$ be its value function.
-% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
-Then,
-\begin{align}\label{polthebnd}
-\norm{J^* - J_{\hu}}_{1,c}
-&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2\norm{J^*-\Phi r^*}_{\infty}
-\nn\\&
-+norm{\Gamma J^*-\hg J^*}_{\infty}+\norm{\hj-\hg\hj}_{\infty}\big).
-\end{align}
-\end{theorem}
-\end{comment}
-\begin{corollary}[Constraint Sampling]\label{st}
-$W\in \{0,1\}^{nd\times m}$Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
-$W_{s'a,i}=\delta_{s=s'}$.
-Then
-\begin{align*}%\label{sampexp}
-|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
-\end{align*}
-\end{corollary}
-It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$, while \Cref{cmt2} does not have these limitations.
-In addition, the error $|\Gamma J^*(s) -\hg J^*(s)|$ (in \Cref{st} ) due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation.
-This means that for RLP to perform well it is important to retain the constraints corresponding to those states for which the linear function approximation via $\Phi$ is known to perform well.
+\fi

### 2017-03-23 appendix.tex
adding the review directory
towards main result

@@
 \begin{appendix}
-\textbf{On choice of $\N$:}\\
+\textbf{On choice of $\N$:}
 It is desirable to get rid of the assumption that $\tr\in \N$ without affecting our arguments.
-Note that the set $\N$ is not used in ALP \eqref{alp} and the feasible set of ALP can be specified as the set $\S\eqdef\{r\in \R^k| \Phi r \geq T\Phi r\}$.
+Note that the set $\N$ is not used in ALP \eqref{alp} and the feasible set of ALP can be specified as the set $\S\eqdef\{r\in \Re^k| \Phi r \geq T\Phi r\}$.
 Further, the only property about $\S$ that we used in our argument (\Cref{restate}) was that $r'= r^*+\norm{J^*-\Phi r^*}_{\mn} \left(\frac{1+\beta_{\psi}}{1-\beta_{\psi}}\right)\, r_0 \in \S$.
 Thus, so long as $\N$ contains $r'$ it is not necessary for it to contain $\tr$.\par
-Let $g_{\min}=\underset{a,s}{\min}g_a(s)$, $g_{\max}=\underset{a,s}{\max}g_a(s)$ and define $r^*\eqdef\underset{r\in \R^k}{\arg\min}\norm{J^*-\Phi r}_{\mn}$.
+Let $g_{\min}=\underset{a,s}{\min}g_a(s)$, $g_{\max}=\underset{a,s}{\max}g_a(s)$ and define $r^*\eqdef\underset{r\in \Re^k}{\arg\min}\norm{J^*-\Phi r}_{\mn}$.
 Now $\frac{g_{\min}}{1-\alpha}\leq J^* \leq \frac{g_{\max}}{1-\alpha}$ and since $\mathbf{1}$ is in the basis, we have $\norm{J^*-\Phi r^*}_{\mn}\leq \frac{g_{\max}-g_{\min}}{1-\alpha}$ (making use of the fact that for any sensible choice of Lyapunov function $\norm{J^*-\Phi r^*}_{\mn}\leq \norm{J^*-\Phi r^*}_{\infty}$).

### 2017-03-23 errana.tex
adding the review directory
towards main result

@@
 First, we introduce some extra notation:
-For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
-We use $\one \in \R^n$ to denote a vector with all entries $1$.
+For $J_1,J_2\in \Re^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
+We use $\one \in \Re^n$ to denote a vector with all entries $1$.
 The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
@@
 \begin{enumerate}[(i)]
-\item \label{monotone}$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$.
+\item \label{monotone}$T$ is a monotone map, i.e., given $J_1,J_2 \in \Re^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$.
 \item \label{shift}
-Given $J\in \R^n$ and $t \in \R$, we have $T(J+t\one)=TJ+\alpha t\one$.
+Given $J\in \Re^n$ and $t \in \Re$, we have $T(J+t\one)=TJ+\alpha t\one$.
 \item \label{maxnorm}
-If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{shift} then
-$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \R^n$,
+If $T: \Re^n \to \Re^n$ is any operator that is monotonous and satisfies~\eqref{shift} then
+$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \Re^n$,
 $
@@
 \begin{corollary}
-If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
+If $J\in \Re^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
 \end{corollary}
@@
 \begin{definition}\label{def:lyap}
-Let $c,\rho,\chi:S \to \R_+$ be positive-valued functions. Then for $J\in \R^n$, $a\in A$ and $s\in S$, define
+Let $c,\rho,\chi:S \to \Re_+$ be positive-valued functions. Then for $J\in \Re^n$, $a\in A$ and $s\in S$, define
 the discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
-The function $\chi:S\to\R_+$ is a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
+The function $\chi:S\to\Re_+$ is a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
 \end{definition}
@@
 \begin{enumerate}[(i)]
-%\item \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$.
-\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
-and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$.
-\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
-\item \label{wassmp} $W \in \R^{nd\times m}_+$ is a matrix with all positive entries.
+%\item \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \Re^n$.
+\item \label{lyap} $\psi\colon S \ra \Re_+$ is a Lyapunov function for $P$
+and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \Re^k$, $\Phi r_0 = \psi$.
+\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \Re$, where $r_0\in \Re^k$ such that $\Phi r_0 = \psi$.
+\item \label{wassmp} $W \in \Re^{nd\times m}_+$ is a matrix with all positive entries.
 \end{enumerate}
@@
 
-We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$ and $t>0$,
+We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \Re^n$ and $t>0$,
 \begin{align}\label{eq:psilin}
@@
 \begin{lemma}\label{lpsol}
-Let $A\in \R^{u\times v}$, $b\in \R^u,d\in \R^v$ and $b_0=Ax_0$ for
-some $x_0 \in \R^v$, $\N' \subset \R^v$ such that $\N' =x_0+ \N'$. Then
+Let $A\in \Re^{u\times v}$, $b\in \Re^u,d\in \Re^v$ and $b_0=Ax_0$ for
+some $x_0 \in \Re^v$, $\N' \subset \Re^v$ such that $\N' =x_0+ \N'$. Then
 \begin{align}
@@
 \begin{lemma}\label{bestbndmn}
-Let $r^*\eqdef\underset{r\in \R^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$. Then,
+Let $r^*\eqdef\underset{r\in \Re^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$. Then,
 \begin{align}
@@
 \begin{lemma}\label{tgmonotone}
-For $J_1, J_2\in \R^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
+For $J_1, J_2\in \Re^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
 \end{lemma}
 \begin{proof}
-Given $J\in \R^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$.
+Given $J\in \Re^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$.
 Choose any $i\in \{1, \ldots, n\}$.
@@
 \begin{lemma}\label{maxnormmn}
-Assume that $\hg: \R^n \to \R^n$ is monotone and 
-that there exists some $\beta\in [0,1)$ such that for any $J\in \R^n$ and $t>0$,
+Assume that $\hg: \Re^n \to \Re^n$ is monotone and 
+that there exists some $\beta\in [0,1)$ such that for any $J\in \Re^n$ and $t>0$,
 \begin{align}
@@
 \begin{proof}
-First, we show that for any $t\ge 0$,  $J\in \R^n$,
+First, we show that for any $t\ge 0$,  $J\in \Re^n$,
 $\hg( J - t \psi) \ge \hg J - \beta t \psi$ also holds.
 To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $\hg J \le \hg J' + \beta t \psi$. Reordering this inequality gives the result.
-Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \R^n$ are arbitrary.
+Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \Re^n$ are arbitrary.
 Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
@@
 The operator $\hg$ satisfies \eqref{eq:shiftmn} with $\beta = \beta_\psi$.
-%For any $J\in \R^n$, $t\in \R_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.
+%For any $J\in \Re^n$, $t\in \Re_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.
 \end{lemma}
@@
 \begin{theorem}\label{gmaxcontramn}
-The operator $\Gamma  \colon \R^n\ra \R^n$ is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
+The operator $\Gamma  \colon \Re^n\ra \Re^n$ is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
 \end{theorem}
@@
 \begin{theorem}\label{hgmaxcontramn}
-The operator $\hg:\R^n\to\R^n$  is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
+The operator $\hg:\Re^n\to\Re^n$  is a contraction operator in $\norm{\cdot}_{\mn}$ with factor $\beta_{\psi}$.
 %$\hg$ is also a contraction map in the weighted $L_\infty$ norm.
@@
 For $i\in \{1,\dots,n\}$, $c=e_i$ let $r_i$ be a solution to GRLP in \eqref{grlp}
-and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.
+and define $V_0\in \Re^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.
 
@@
 Let $ r_1,  r_2,\ldots, r_n$ be solutions to ALP in \eqref{alp} (with an additional constraint that the solution be restricted to $\N$) for $c=e_1, e_2,\ldots,e_n$, respectively,
-and define $V_0\in \R^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 
+and define $V_0\in \Re^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$. The rest of the proof 
 follows in the same manner as the proof of \cref{relation1}.
@@
 A vector
-$\hat{r} \in \R^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
+$\hat{r} \in \Re^k$ is a solution to GRLP \eqref{grlp} iff it solves the following program:
 \begin{align}\label{grlpeqprog}
@@
 A vector
-$\tr \in \R^k$ is a solution to ALP \eqref{alp} iff it solves the following program:
+$\tr \in \Re^k$ is a solution to ALP \eqref{alp} iff it solves the following program:
 \begin{align}\label{grlpeqprog}
 \begin{split}
-\min_{r\in \R^k}\, &\norm{\Phi r-\hv}_{1,c}\,\mb
+\min_{r\in \Re^k}\, &\norm{\Phi r-\hv}_{1,c}\,\mb
 \text{s.t.}\mb \, \Phi r\geq  T \Phi r.
@@
 and so by reordering and with another triangle inequality,
-\begin{align}\label{jhv}
+\begin{align*}%\label{jhv}
 \norm{J^*-\hv}_{\mn} \nn
@@
 &\le \frac{\norm{ J^*-\Gamma J^*}_{\mn}+\norm{\Gamma J^* - \hg J^*}_{\mn}}{1-\beta_\psi}\,.
-\end{align}
+\end{align*}
 The proof follows by combining this and \cref{bestbndmn}.
@@
 We now recall Lemma~$5$ from Section 4.2 of \cite{ALP}. 
-For this result, recall that $r_0 \in \R^k$ is the vector such that $\psi = \Phi r_0$.
+For this result, recall that $r_0 \in \Re^k$ is the vector such that $\psi = \Phi r_0$.
 \begin{lemma}\label{restate}
 %Let $\psi$ be a Lyapunov function that belongs to the column span of $\Phi$ ,
-For  $r \in \R^k$ arbitrary, let $r'$ be
+For  $r \in \Re^k$ arbitrary, let $r'$ be
 \begin{align}
@@
 since $T$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta_{\psi}$ as noted earlier.
-%componentwise  $(I-\alpha P_{\hu})^{-1}$ is a positive operator for $x=(x_1,\ldots,x_n)^\top\in \R^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \R^n$. 
+%componentwise  $(I-\alpha P_{\hu})^{-1}$ is a positive operator for $x=(x_1,\ldots,x_n)^\top\in \Re^n$, $|x|=(|x_1|,\ldots,|x_n|)^\top\in \Re^n$. 
 Hence,

### 2017-03-23 grlp.tex
towards main result

@@
 Linear function approximation, wherein the solution is searched in the subspace spanned by the column vectors of a given feature matrix $\Phi$.
-The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \R^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ \citep{SchSei85}.
+The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by introducing the new variables $r\in \Re^k$ and adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \Re^{n\times k}$ \citep{SchSei85}.
 By substitution, this leads to
@@
 \begin{split}
-\min_{r\in \R^k}\, &c^\top \Phi r\,\,\,
+\min_{r\in \Re^k}\, &c^\top \Phi r\,\,\,
 \text{s.t.}\mb \Phi r\geq T \Phi r,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Generalized Reduced Linear Programming}\label{sec:grlp}
-\todoc{How about the cleaner ``Linear projected approximate linear programming''}
-In this section we introduce the computational model used and the optimization problem
-that is the main object of our study.
+\section{The Linearly Relaxed ALP}\label{sec:grlp}
+In this section we introduce the computational model used and the ``Linearly Relaxed Approximate Linear Program''
+a relaxation of the ALP.
+
 As discussed in the introduction, we are interested in methods that compute a good approximation to the optimal value function.
@@
 We will take a more general view, and we will consider calculating good approximations to $J^*$ with respect to a weighted $1$-norm, where the weights $c$ form a probability distribution over $\S$.
-Recall that the weighted $1$-norm $\norm{J}_{1,c}$ of a vector $J\in \R^S$ is defined as $\norm{J}_{1,c}  = \sum_s c(s) |J(s)|$.
-Note that here and in what follows we identify elements of $\R^\S$ (functions, mapping $\S = \{1,\dots,S\}$ to the reals) with elements of $\R^S$ in the obvious way.
+Recall that the weighted $1$-norm $\norm{J}_{1,c}$ of a vector $J\in \Re^S$ is defined as $\norm{J}_{1,c}  = \sum_s c(s) |J(s)|$.
+Note that here and in what follows we identify elements of $\Re^\S$ (functions, mapping $\S = \{1,\dots,S\}$ to the reals) with elements of $\Re^S$ in the obvious way.
 This allows us to write e.g.
@@
 Thus, $J^*$ is the ``smallest'' superharmonic function. It follows than that 
-for any $c\in \R_+^S \doteq [0,\infty)^S$ and any superharmonic $J$, $c^\top J^*\le c^\top J$ and since $J^*$ is also superharmonic, $\min \{ c^\top J\,:\, J \ge T J \} = c^\top J^*$ and if $c$ is positive-valued then the minimizer of $c^\top J$ amongst all superharminoc functions is $J^*$.
+for any $c\in \Re_+^S \doteq [0,\infty)^S$ and any superharmonic $J$, $c^\top J^*\le c^\top J$ and since $J^*$ is also superharmonic, $\min \{ c^\top J\,:\, J \ge T J \} = c^\top J^*$ and if $c$ is positive-valued then the minimizer of $c^\top J$ amongst all superharminoc functions is $J^*$.
 \fi
 It is not hard to show then that $J^*$ is the smallest superharminoc function (i.e., for any $J$ superharmonic, $J\ge J^*$).
-It also follows that for any  $c\in \R_{++}^S \doteq (0,\infty)^S$, the unique solution to the linear program $\min\{ c^\top J \,:\, J \ge T J \} =\min \{ c^\top J\,:\, J \ge T_a J, a\in \A \} $ is $J^*$.
+It also follows that for any  $c\in \Re_{++}^S \doteq (0,\infty)^S$, the unique solution to the linear program $\min\{ c^\top J \,:\, J \ge T J \} =\min \{ c^\top J\,:\, J \ge T_a J, a\in \A \} $ is $J^*$.
 
-Now, let $\phi_1,\ldots,\phi_k : \S \to \R$ be $k$ basis functions. 
+Now, let $\phi_1,\ldots,\phi_k : \S \to \Re$ be $k$ basis functions. 
 \todoc{I think we should use $d$ to denote the number of basis functions. Or at least $n$. Low priority.} 
@@
 is obtained by adding the linear constraints $J = \sum_{i=1}^k r_i \phi_i$ to the above linear program.
-Eliminating $J$ then gives $\min\{ \sum_i r_i c^\top \phi_i \,:\, \sum_i r_i \phi_i \ge g_a + \alpha \sum_i r_i P_a \phi_i, a\in \A, r = (r_i)\in \R^k \}$.
+Eliminating $J$ then gives $\min\{ \sum_i r_i c^\top \phi_i \,:\, \sum_i r_i \phi_i \ge g_a + \alpha \sum_i r_i P_a \phi_i, a\in \A, r = (r_i)\in \Re^k \}$.
 As noted by \citet{SchSei85}, the linear program is feasible as long as $\one$, defined as the vector with all components being identically equal to one, is in the span of $\{\phi_1,\dots,\phi_k\}$. 
@@
 but the details of this are the beyond the scope of the present work.
-As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi \ralp$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$, where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm and $\Phi \in \R^{S\times k}$ is the matrix formed by $(\phi_1,\dots,\phi_k)$.
+As shown by \citet{ALP}, if $\ralp$ denotes the solution to the above ALP then for $\Jalp \doteq \sum_i \ralp(i) \phi_i \doteq \Phi \ralp$ it holds that $\norm{\Jalp - J^*}_{1,c} \le \frac{2 \epsilon}{1-\alpha}$, where $\epsilon = \inf_r \norm{ J^* - \Phi r }_\infty$ is the error of approximating the optimal value with the span of the basis functions $\phi_1,\dots,\phi_k$ and $\norm{J}_\infty = \max_s |J(s)|$ is the maximum norm and $\Phi \in \Re^{S\times k}$ is the matrix formed by $(\phi_1,\dots,\phi_k)$.
 That the error of approximating $J^*$ with $\Jalp$ is $O(\epsilon)$ is significant: The user can focus on finding a good basis, leaving the search for the ``right'' coefficients to a linear program solver.
@@
 $\sum_a w_{i,a}^\top J \ge \sum_a w_{i,a}^\top(g_a + \alpha P_a J)$, 
-where the choice of $m$ and that of the vectors $w_{i,a}\in \R_+^S$ is left to the user.
+where the choice of $m$ and that of the vectors $w_{i,a}\in \Re_+^S$ is left to the user.
 Note that this results in a linear program with $k$ variables and $m$ constraints, which can be written as
@@
 \begin{split}
-&\underset{r\in \R^k}{\min}\, \, c^\top \Phi r\\
+&\underset{r\in \Re^k}{\min}\, \, c^\top \Phi r\\
 &\text{s.t.}\mb  \,\sum_a W_a^\top \Phi r\geq \sum_a W_a^\top (g_a + \alpha P_a) \Phi r\,,
@@
 \end{align}
-where $W_a = (w_{1,a},\dots,w_{m,a}) \in \R_+^{S \times m}$. 
+where $W_a = (w_{1,a},\dots,w_{m,a}) \in \Re_+^{S \times m}$. 
 \todoc{Do we need that $(w_{i,a}^\top)_i$ defines a probability distribution?}
@@
 any constraint selection/generation process can be represented by choosing an appropriate binary-valued matrix
-$W^\top = (W_1^\top,\dots,W_A^\top)\in \R_+^{m\times SA}$. In particular, when the constraints are selected
+$W^\top = (W_1^\top,\dots,W_A^\top)\in \Re_+^{m\times SA}$. In particular, when the constraints are selected
 in a random process as suggested by \citet{CS}, the matrix $W$ would be a random, binary-valued matrix.
@@
 Unboundedness could be avoided by adding an extra constraint of the form $r\in \N$ to the LRALP,
-for a properly chosen polyhedron $\N \subset \R^k$.%
+for a properly chosen polyhedron $\N \subset \Re^k$.%
 \footnote{
@@
 To write both LP's in a similar form let us introduce $E = (I_{S\times S},\dots,I_{S\times S})^\top$, where $I_{S\times S}$ is the $S\times S$ identity matrix.
-Further, let $H:\R^S \times \R^{SA}$ be the operator defined by $(HJ)^\top = ( (T_1 J)^\top, \dots, (T_A J)^\top )$.
-Note that $H$ is a linear operator.
+Further, let $H:\Re^S \to \Re^{SA}$ be the operator defined by $(HJ)^\top = ( (T_1 J)^\top, \dots, (T_A J)^\top )$.
+Note that $H$ is a linear operator, which we call the \emph{linear Bellman operator}.
 Then, the ALP can be written as $\min\{ c^\top \Phi r \,|\, E \Phi r \ge H \Phi r \}$, while LRALP takes the form  
@@
 $\mathcal{L}_{\lralp}(r,q) = c^\top \Phi r+q^\top W^\top (H\Phi r-E\Phi r)$. Thus, we can view $W q$ as a ``linear approximation''
-to the dual variable $\lambda \in \R_+^{SA}$. 
+to the dual variable $\lambda \in \Re_+^{SA}$. 
 This suggests that perhaps $W$ should be chosen such that it approximates well the optimal dual variable.
-If $\Phi$ spans $\R^{S}$, the optimal dual variable $\lambda^*$ is known to be the discounted occupancy measure underlying the optimal policy (Theorem 3.18, \cite{Kall}), suggesting that the role of $W$ is very similar to the role of $\Phi$ excepts that the subspace spanned by the columns of $W$ should ideally be close to $\lambda^*$.
+If $\Phi$ spans $\Re^{S}$, the optimal dual variable $\lambda^*$ is known to be the discounted occupancy measure underlying the optimal policy (Theorem 3.18, \cite{Kall17}), suggesting that the role of $W$ is very similar to the role of $\Phi$ excepts that the subspace spanned by the columns of $W$ should ideally be close to $\lambda^*$.
 
-We denote an arbitrary solution to GRLP by $\hr$, and the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.\\
 \if0
@@
 Hence, while ALP employs LFA in its objective function (i.e., use of $\Phi r$), GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$).
-%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$.
+%Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \Re^{nd}, r\in \Re^m$.
 To get a sense of how $W$ should be chosen, recall that

### 2017-03-23 intro.tex
towards main result

@@
 it is customary to adopt the \emph{modest goal of efficiently computing actions of a policy that 
-is nearly as good as the best policy \todoc{This is too ambitious still. Need to tweak.}
-in a given restricted policy class}.
+is nearly as good as a policy chosen by a suitable (computationally unbounded, and well-informed) oracle
+from a given restricted policy class}. \todoc{Is this better now? We should probably elaborate on the oracle idea space permitting.}
 Here, within some restrictions (see below), the policy class can be chosen by the user.
@@
 The set of all states, the state space, is denoted by $S$, and the set of all actions, the action space, is denoted by $A$.
-Formally, a decision rule is called a policy $u$, ($u\colon S\ra A$) and has an associated value function $J_u$\footnote{Without loss of generality value function $J_u$ can be thought of as a vector in $\R^{|S|}$.}, ($J_u(s)\colon S\ra \R$) which specifies the expected cumulative reward obtained by following the policy $u$ starting from each state.\par
+Formally, a decision rule is called a policy $u$, ($u\colon S\ra A$) and has an associated value function $J_u$\footnote{Without loss of generality value function $J_u$ can be thought of as a vector in $\Re^{|S|}$.}, ($J_u(s)\colon S\ra \Re$) which specifies the expected cumulative reward obtained by following the policy $u$ starting from each state.\par
 The so-called dynamic programming (DP) methods \cite{BertB} compute the optimal value function $J^*$ first and then obtain an optimal policy $u^*$ using $J^*$\footnote{Obtaining $u^*$ from $J^*$ is computationally cheap}.
@@
 This paper is related to LP based techniques for MDPs with large state spaces.
-One way to handle the large number of states is to restrict the value function to the sub-space spanned by the columns of an $n\times k$ feature matrix $\Phi$\footnote{This is known as linear function approximation (LFA) where in the value function is approximated by $\Phi \tr$, for some $\tr\in \R^k$.
+One way to handle the large number of states is to restrict the value function to the sub-space spanned by the columns of an $n\times k$ feature matrix $\Phi$\footnote{This is known as linear function approximation (LFA) where in the value function is approximated by $\Phi \tr$, for some $\tr\in \Re^k$.
 The idea of LFA is not restricted to LP based approach and is also widely used in other approximate dynamic programming methods \cite{dpchapter}, which are not discussed in this paper.}.
@@
 %Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm.\par
-Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi \tr$ where $\Phi \in \R^{|S|\times k}$ is a so-called feature matrix and $\tr*\in \R^k$ is a weight vector (to be computed), is the most widely used method of approximation.
+Linear function approximation (LFA), i.e., letting $\tilde{J}=\Phi \tr$ where $\Phi \in \Re^{|S|\times k}$ is a so-called feature matrix and $\tr*\in \Re^k$ is a weight vector (to be computed), is the most widely used method of approximation.
 Here, dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states ($k<<|S|$), holding the promise of being able to work with MDPs regardless of the number of states.\par

### 2017-03-23 errana.tex
main result section

@@
 %!TEX root =  autocontgrlp.tex
-\section{Error Analysis}\label{sec:improv}
+\section{Proofs}\label{sec:improv}
+
+In this section we present the main results of this paper in \Cref{cmt2} (we state improved bounds in \Cref{sec:improv}).
+Our bounds are expressed in terms of two novel contractions operators which we define in \Cref{lubpop,alubpop}.
+We now define two projection operators that are central to our error analysis and in them we assume that the set $\N'\subset \Re^k$ is such that $\N' = \N + t \one$ for any $t\in \Re$.
+%The least upper bound (LUB) projection operator $\Gamma \colon \Re^n \ra\Re^n$ is defined below, see \eqref{gamdef}.
+\begin{definition}\label{lubpop}
+Given $J\in \Re^n$ and the nonnegative valued vector $c\in \Re^n_+$, define $r_{c,J}$ to be the solution to
+\begin{align}
+\label{lubplp}
+\begin{split}
+\underset{r\in \N'}{\min} &\,\, c^\top \Phi r\,\mb
+\text{s.t.} \mb \Phi r\geq  TJ.
+\end{split}
+\end{align}
+For $J\in \Re^n$, $\Gamma J$, the \emph{least upper} (LU) projection of $J$ is defined as
+\begin{align}\label{gamdef}
+(\Gamma J)(i)\eqdef(\Phi r_{e_i,J})(i),\quad i=1,\ldots,n\,.
+\end{align}
+\end{definition}
+The definition of the second operator is as follows:
+\begin{definition}\label{alubpop}
+Given $J\in \Re^n$ and the nonnegative valued vector $c\in \Re^n_+$, define $r'_{c,J}$ to be the solution to
+\begin{align}\label{alubplp}
+\underset{r\in \N'}{\min}& \,\mb c^\top \Phi r\,\mb
+\text{s.t.} \,\,\, W^\top E \Phi r\geq W^\top HJ.
+\end{align}
+The \emph{approximate least upper} (ALU) projection operator
+$\hg \colon \Re^n \ra \Re^n$ is defined as
+\begin{align}\label{tgamdef}
+(\hg J)(i)\eqdef(\Phi r'_{e_i,J})(i), \mb i=1,\ldots,n\,, J\in \Re^n\,.
+\end{align}
+\end{definition}
+\begin{remark}\label{ubrem}
+To understand the meaning of $\Gamma$ (and $\hg$) define
+\begin{align}\label{ubclass}
+\F_J\eqdef\{\,\Phi r\,:\,\Phi r\geq TJ, r\in \N'\,\},
+\end{align}
+where $J\in \Re^n$.
+Disregarding the constraint $r\in \N'$,
+$\F_J$ contains all vectors in the span of $\Phi$ that upper bound $TJ$.
+Further, since $(\Gamma J)(i) = \min\{ V(i) \,:\, V\in \F_J \}$, it also follows that $ V\ge \Gamma J $ holds for any $V\in \F_J$.
+Also $\Gamma J\geq T J$.\par
+The operators $\Gamma$ and $\hg$ are closely related to ALP \eqref{alp} and GRLP \eqref{grlp} respectively and are only analytical tools that we will need to express our bounds and need not be computed in practice.
+It turns out that the novel operators ($\Gamma$ and $\hg$) are contraction maps (see \Cref{hgmaxcontramn}), a fact that is a key to our results (\Cref{cmt2mn,polthe}).
+At the outset we are interested in the candidate value functions in the constraint set $\N$ and want to study them using $\Gamma$ and $\hg$.
+However since the basis $\Phi$ contains $\one$ we make it helps our analysis to define the set $\N'$ in \Cref{lubplp,alubplp} to be `$\N$ plus its translations by $\one$'.
+\end{remark}
+
 \subsection{Properties of the Bellman Operator}
@@
 Much the results that ensue are based on `Lyapunov' analysis where the idea is to replace the constant function $\one$ by a certain Lyapunov function (see \Cref{def:lyap}) and the $\norm{\cdot}_{\infty}$ by a weighted max-norm (see \Cref{notations}-\eqref{norms}).
+
 \subsection{Analysis using Lyapunov Functions}

### 2017-03-23 results.tex
results sections added

%!TEX root =  autocontgrlp.tex
\section{Main Results}
%We denote an arbitrary solution to GRLP by $\hr$, and the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy w.r.t. $\hj$.\\

The purpose of this section is to present our main results.
\newcommand{\Jalpo}{J^*_{\alp}}
\newcommand{\Jlro}{J^*_{\lralp}}
\newcommand{\Jlr}{J_{\lralp}}
Let $\Jlr$ be a solution to the LRALP given by \eqref{grlp}. When multiple solutions exist, we can choose any of them.
For the result, we assume that the LRALP is not unbounded, and hence a solution exist. In fact, we will assume something much stronger. The discussion of why our assumptions are reasonable and how to ensure that they hold is postponed to after the presentation of our results.
Our main results bounds the error $\norm{J^* - \Jlr}_{1,c}$.

The bound is given in terms of the approximation error of $J^*$ with the basis functions $\Phi= (\phi_1,\dots,\phi_k)$, as well as the deviation between two functions, $\Jalpo,\Jlro: \S \to \Re$, which we define next. In particular,
\begin{align*}
\Jalpo(s) & = \min\{ r^\top\phi(s) \,|\, \Phi r \ge J^*, \, r\in \Re^k \}\,,\\
\Jlro(s)    & = \min\{ r^\top\phi(s) \,|\, W^\top E \Phi r \ge W^\top E J^*, \, r\in \Re^k \}\,,
\end{align*}
where $s\in \S$. Recall that $E: \Re^S \to \Re^{SA}$ is defined so that $(E J)^\top = (J^\top, \dots, J^\top)$, i.e., $E$ stacks its argument $A$-fold. Hence, $W^\top E = \sum_a W_a^\top$. Our strong assumption is that $\Jlro$ is finite-valued. Note that $\Jalpo\ge J^*$ reflects the error due to using the basis functions $(\phi_j)_j$, and the magnitude of the deviation $\Jlro-\Jalpo$ reflects the error introduced due to the relaxed constraint system. \todoc{I commented out the figure. We can discuss whether we want to include it.}
%The function $\Jalpo$ is an upper approximation to $J^*$

Following \citet{ALP,CS}, 
in the result the magnitude of the error $\Jlro-\Jalpo$ and also that of the error
of approximating $J^*$ with the subspace spanned by $\Phi$, 
will be measured in terms of a \emph{weighted maximum norm}, 
$\norm{J}_{\infty,\psi} = \max_{s\in \S} |J(s)|/\psi(s)$, 
where $\psi: \S \to \Re_{++}$ is a positive-valued weighting function.%
\footnote{As opposed to \citet{ALP} and others, our definition uses division and not multiplication with the weights.
We choose this form for mathematical convenience:
With this definition, nice duality results hold between weighted $1$-norms and weighted maximum norms.
}
As also stressed by \citeauthor{ALP}, 
the appropriate choice of $\psi$ is crucial for MDPs with huge state-spaces:
The problem is that if the range of values of $|J^*(s)|$ in different parts of the state space
differ in orders of magnitude, it is not meaningful to expect to control the error of approximating it uniformly.
By choosing the weighting function to reflect the magnitude of $J^*$, controlling the weighted maximum norm
is achieved by controlling relative errors, which may be much easier to ensure than controlling meaningfully small
absolute errors.

Just like \citet{ALP}, we will also require that $\psi$ is a \emph{stochastic Lyapunov-function} for the MDP.  In particular, we require that the $\alpha$-discounted stability coefficient
\begin{align*}
\beta_\psi \doteq \alpha  \max_{a} \norm{P_a \psi}_{\infty,\psi}
\end{align*}
is strictly less than one.
This can be seen to imply that $H: (\Re^S,\norm{\cdot}_{\infty,\psi}) \to (\Re^{SA}, \norm{\cdot}_{\infty,\psi})$ is a contraction,
where for $J = (J_1^\top,\dots,J_A^\top)^\top \in \Re^{SA}$ we let $\norm{J}_{\infty,\psi} = \max_a\norm{J}_{\infty,\psi}$.
That $H$ is a contraction will play a crucial role in our results.
Note that the condition $\beta_\psi<1$ is closely related to the condition that for any policy $u$, 
$P_u \psi \le \psi$, which can be viewed as a stability condition on the MDP 
and which appeared in a slightly altered form in studying the stability of MDPs with infinite 
state spaces \citep[e.g.,][]{chemey99a}.
Note that one can always choose $\psi = \one$: $\beta_\one = \alpha<1$. 
With this, we are ready to state our main result:

\if0
\FloatBarrier
%\input{cartoon}
\begin{figure}
\includegraphics[scale=0.7]{cartoon_grlp.pdf}
\caption{
%\normalsize
The outer lightly shaded region corresponds to GRLP constraints and the inner dark shaded region corresponds to the original constraints. The main contribution of the paper is to bound $\norm{J^*-\hat{J}_c}$.}
\label{cartoon}
\end{figure}
\Cref{cartoon} shows the solutions to the LP, ALP and GRLP respectively. The error in ALP solution has already been studied in \cite{ALP}. Our objective is to study the extra source of error due to constraint approximation.
\fi

%\subsection{Error Bounds}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{theorem}[Error Bound for LRALP]
\label{cmt2}
Assume that $c\in \Re_+^S$ is such that $1^\top c = 1$ and that $W \in \Re_+^{SA\times m}$ is nonnegative valued.
Let $\psi\in \Re_+^S$ be in the column span of $\Phi$ and assume that the $\alpha$-discounted stability coefficient of $\psi$ is $\beta_\psi<1$. 
Let $\eps = \inf_{r\in \Re^k}\norm{J^*-\Phi r}_{\infty,\psi}$ 
be the error of approximation $J^*$ using the basis functions in $\Phi$.
Then,
\begin{align*}
\norm{J^*-\hj}_{1,c} \leq 
 \frac{2}{1-\beta_\psi} \left(
	3 \eps
     +\norm{\Jalpo-\Jlro}_{\infty,\psi}\right)\,.
\end{align*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\if0
\item The control error is bound as\\
$\norm{J^* - J_{\hu}}_{1,c}
\leq 2\left(\frac{1}{(1-\alpha)^2}\right)\, \big( 2~\us{\min}{r\in \Re^k} \norm{J^*-\Phi r}_{\infty}
+\norm{\Gamma J^*-\hg J^*}_{\infty}+\norm{\hj-\hg\hj}_{\infty}\big)$.
\end{enumerate}
\fi
\end{theorem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Note that the result implicitly assumes that $\hj$ exists, because if $\hj$ does not exist then $\Jlro$ is necessarily unbounded, making the last error term infinite. To ensure that $\psi$ is in the span of $\Phi$, after choosing $\psi$, one can add $\psi$ as one of the basis functions. Alternatively, the bound can also be interpreted to hold for any $\psi$ in the span of $\Phi$ with $\beta_\psi<1$.

As noted earlier, \citet{ALP} prove a similar error bound for $\Jalp$, the solution of the ALP.
In particular, their Theorem 3 states that  under identical assumptions as in our result,
$\norm{J^* - \Jalp}_{1,c} \le \frac{2 c^\top \psi \epsilon}{1-\beta_\psi}$ for $\epsilon$ defined as above
 (the result we cited previously is a simplified form of this bound).
\todoc{Strange that we don't have $c^\top \psi$!?}
The larger coefficient of $\epsilon$ is probably an artifact of our analysis. 
Note that when $W$ does not reduce the constraints, 
our bound is only a constant factor larger than this previous result.
The extra term $\norm{\Jalpo-\Jlro}_{\infty,\psi}$ can be seen as the price paid for relaxing the constraints.

\if0
\textbf{On Prediction Error:} The first factor in the right hand side of the prediction error in \Cref{cmt2} is related to the best possible approximation that can be achieved with the chosen feature matrix $\Phi$. This term is an carry over of the upper bound in ALP formulation as shown in \Cref{alpvanilla}. The second factor in the right hand side of the prediction error is related to constraint approximation and is completely defined in terms of $\Phi$, $W$ and $T$, and does not require knowledge of stationary distribution of the optimal policy.\par
\textbf{On Control Error:} The first two terms are quite similar to those in the bound for prediction error. The third term occurs due to the fact that $\Phi \geq T\Phi r$ that holds in the case of ALP does not hold in the case of GRLP.\par
\begin{comment}
\begin{theorem}[Control Error Bound in $\norm{\cdot}_{\infty}$]
\label{polthe}
Let $\hu$ be the greedy policy with respect to the solution $\hj$ of GRLP and $J_{\hu}$ be its value function.
% Let $r^*$ be as in Theorem~\ref{mt2mn}, then
Then,
\begin{align}\label{polthebnd}
\norm{J^* - J_{\hu}}_{1,c}
&\leq 2\left(\frac{c^\top \psi}{(1-\beta_{\psi})^2}\right)\, \big( 2\norm{J^*-\Phi r^*}_{\infty}
\nn\\&
+norm{\Gamma J^*-\hg J^*}_{\infty}+\norm{\hj-\hg\hj}_{\infty}\big).
\end{align}
\end{theorem}
\end{comment}
\begin{corollary}[Constraint Sampling]\label{st}
$W\in \{0,1\}^{nd\times m}$Let $s\in S$ be a state whose constraint is selected by $W$ (i.e., for some $i$ and all $(s',a)\in S\times A$,
$W_{s'a,i}=\delta_{s=s'}$.
Then
\begin{align*}%\label{sampexp}
|\Gamma J^*(s)-\hg J^*(s)|<|\Gamma J^*(s)-J^*(s)|.
\end{align*}
\end{corollary}
It is important to note that \Cref{rlpt} holds only in high probability and is valid only under idealized assumption of knowing the optimal policy $u^*$, while \Cref{cmt2} does not have these limitations.
In addition, the error $|\Gamma J^*(s) -\hg J^*(s)|$ (in \Cref{st} ) due to constraint approximation is less than the original projection error $|\Gamma J^*(s)-J^*(s)|$ due to function approximation. This means that for RLP to perform well it is important to retain the constraints corresponding to those states for which the linear function approximation via $\Phi$ is known to perform well.
\fi

### 2017-03-23 num.tex
num section updated

--- 2016-07-22 num.tex
@@
 \section{Numerical Illustration}
-In this section, we show via an example in the domain of controlled queues that the error term $\et$ indeed correlates with
- the error induced by the constraint approximation.
-The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}.
+In this section, we show via an example in the domain of controlled queues to show that the consequences of \Cref{conetheorm} (the \emph{cone} condition) derived based on the geometric intuition (please refer \cite{aaaipaper} for preliminary experiments in this domain).
+
+\textbf{Queuing System Model:} The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}.
 We consider a single queue with arrivals and departures.
@@
 The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue.
-The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s+60q(a)^3)$.
-We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work well for this domain \cite{ALP}.
-For our experiments, we chose two contenders for the $W$-matrix and compared them with random positive matrices $W_r$.
-Our choices of the $W$ matrix were: {$\mathbf{(i)}$} $W_c$- matrix that corresponds to sampling according to $c$.
-This is justified by the insights obtained from Theorem~\ref{st} on the error term $\et$, i.e., the idea of selecting the important states.
-{$\mathbf{(ii)}$} $W_a$ state-aggregation matrix, a heuristic derived using the fact that $\lambda^*$ is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$.
-Our choice of the $W_a$ matrix to correspond to aggregation of nearby states is motivated by the observation that $P^n$ captures $n^{th}$ hop connectivity/neighborhood information.
-The aggregation matrix $W_a$ is defined as below: for all $ i=1,\ldots,m$,
-\begin{align}\label{wdes}
-W_a(i,j)&=1, \mb\text{for all } j\mb\text{s.t.}\mb \nn\\&j=(i-1)\times\frac{n}{m}+k+(l-1)\times n, \nn\\&\mb\quad\quad k=1,\ldots,\frac{n}{m}, l=1,\ldots,d,\nn\\
-&=0,\mb\text{otherwise}.
-\end{align}
-We ran our experiments on a moderately large queuing system denoted by $Q_L$ with $n=10^4$ and $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=0.98$.
-We chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors) and we chose $W_a$ \eqref{wdes}, $W_c$, $W_i$ and $W_r$ with $m=50$, where $W_i$ is the ideal
-(and intractable) sampler of \citep{CS}. \todoc{Right??}
-We set $c(s)=(1-\zeta) \zeta^s$, where $s=1,\ldots,9999$, with $\zeta=0.9$ and $\zeta=0.999$ respectively.
-The results in Table~\ref{pref} show that the performance exhibited by $W_a$ and $W_c$ is better by several orders of magnitude over `random' in the case of the large system $Q_L$ and is closer to the ideal sampler $W_i$.
-Note that computing $\et$ was hard in the case of large $n=10^4$ and since $\et$ is completely dependent on the structure of $\Phi$, $T$ and $W$ we instead computed the same for $n=10$ and used it as a surrogate.
-Accordingly, we chose a smaller system $Q_S$ with $n=10$, $d=2$, $k=2$, $m=5$, $q(1)=0.2$, $q(2)=0.4$, $p=0.2$ and $\alpha=0.98$.
-Note that a better performance of $W_a$ and $W_c$ is in agreement with a lower value of $\et$.
-\FloatBarrier
-\begin{table}[H]
-\begin{center}
-\resizebox{\columnwidth}{!}{
-\begin{tabular}{|c|c|c|c|c|}\hline
-Error Terms&	$W_i$&	$W_c$& $W_a$& $W_r$ \\\hline
-$||J^*-\hj||_{1,c}$ for $\zeta=0.9$& $32$&	$32$& $220$& $5.04\times 10^4$ \\\hline
-$||J^*-\hj||_{1,c}$ for $\zeta=0.999$& $110$&	$180.5608$& $82$& $1.25\times 10^7$ \\\hline
-$\et$ & $0$&	$39$& $24$& $214$ \\\hline
-\end{tabular}
-}
-\end{center}
-\caption{Shows values of Error Terms for $Q_L$.}
-\label{pref}
-\end{table}
-\begin{comment}
-\subsection{Computational Complexity}
-It is known that the complexity of the linear program is polynomial in the length of its entries, i.e., the number of constraints times the number of variables \cite{karmarkar,adler}. 
-In the case of exact LP, both the number of variable as well as the number of constraints are of the order of the number of states.
-Thus, the complexity of obtaining the exact solution grows at a rate which is at least quadratic in the number of states.
-The entries of the GRLP on the other hand are of the order of $m\times k$, \todoc{$\times d$?} where the constants $m$ and $k$ are chosen to be much smaller than the number of states.
-We made use of the \textbf{SoPlex} solver \href{http://soplex.zib.de/} and observed that solving the GRLPs (for $m=50$, $k=4$, $d=4$) took a time of only about $0.03$ seconds or lesser, the ALP with took about $0.7$ seconds, while computing the exact solution took about $20$ minutes.
-\todoc{Sorry for the many questions, but did you also run ALP ($k=4$) with no constraint aggregation?}
- Also, it is important to note the sparsity of the $W$ matrix in the case of state aggregation helps in formulating the constraints of the GRLP from the original constraints of the ALP without additional computational overhead.
-\FloatBarrier
-\begin{table}[H]
-%\resizebox{\columnwidth}{!}{
-\begin{center}
-\begin{tabular}{|c|c|c|c|}\hline
-Performance Metric&	$W_i$&	$W_c$& $W_a$ \\\hline
-$||J_{\hu}||_{1,c}$ for $\zeta=0.9$& $-441.25$&	$-450.59$& $-446.49$ \\\hline
-$||J_{\hu}||_{1,c}$ for $\zeta=0.999$& $-2.0611e+04$&	$-2.0611e+04$& $-2.0612e+04$ \\\hline
-\end{tabular}
-\end{center}
-%}
-\caption{Shows performance metrics for $Q_L$. Here $||J^*||_{1,c}=-439.26$ for $\zeta=0.9$ and $||J^*||_{1,c}=-2.0603e+04$ for $\zeta=0.999$   and a random policy yields a total reward of $-1.2661e+03
-$.}
-\label{pref}
-\end{table}
-\end{comment}
-
-%Empirical evidence for the performance of RLP with various sampling distributions can also be found in \cite{CST,CS}.
-\begin{comment}
-\subsection{Reinforcement Learning}
-Reinforcement Learning (RL) algorithms are useful in scenarios where the system is available in the form of a simulator or only samples can be obtained via direct interaction.
-In particular, in the RL setting, the model parameters $g$ and $P$ are not known explicitly and the underlying MDP needs to be solved by using sample trajectories.
-In short, RL algorithms are sample trajectory based solution schemes for solving MDPs whose model information is not known.
-RL methods learn by filtering out the noisy sample via stochastic approximation and they also employ function approximation in order to handle MDPs with large number of states.
-Most RL algorithms are sample trajectory based extensions of ADP methods.\\
-The RL extension of the ALP formulation has been applied to the optimal stopping problem in \cite{ALP-Bor}.
-Function approximation is employed to approximate the square root of the Lagrange multipliers.
-However, since the approximation is not linear, convergence of the resulting RL algorithm cannot be guaranteed.
-Our results theoretically justify linear function approximation of the Lagrange multipliers, an immediate implication of which is that the RL extension of the ALP can be guaranteed to converge if the updates in \cite{ALP-Bor} use LFA for the Lagrange multipliers instead of a non-linear approximator.
-\end{comment}
+The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s/n+q(a)^3)$.\par
+\textbf{Parameter Settings:} We ran our experiments $n=1000$, $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=1-\frac{1}{n}$.
+The moderate size of $n=1000$ enabled us to compute the exact the exact value of $J^*$ (it was however expensive).
+We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work reasonably well for this domain \cite{ALP}, and chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors).\\
+\textbf{Experimental Methodology:} We compare two different sampling strategies $(i)$ based on the \emph{cone} conditions, and $(ii)$ based on constraint sampling.
+The two strategies are compared via  \emph{lookahead} policies, wherein, the action at state $s$ is obtained by computing the approximate value functions of the next states.
+The details are as follows:
+$Case (i):$ Except for the corner states i.e., $s=1$ and $s=999$, each state $1<s<n-1$ has two next states namely $s'=s-1$ and $s'=s+1$.
+We formulate two separate LRALPs (or just one LRALP for $s=1$ and $s=n-1$) for next states.
+When formulating the LRALP for state $s'$, we let $c=e_{s'}$ and choose the constraint corresponding to state $s'$ to ensure the cone condition.
+We choose $5$ more constraints corresponding to states $1,200,400,600,800,999$ (uniformly spaced across the state space) and compute $\hat{J}_{e_s'}$.
+The lookahead policy is formulated as $u(s)=\underset{\arg\min}{a\in A}(g_a(s)+\underset{s'\in S}{\sum}p_a(s,s')\hat{J}_{e_s'}$.\\
+$Case (ii):$ In a manner similar to $Case (i)$, here too we formulate two separate RLPs for next states.
+When formulating the RLP for state $s'$, we first let $c_{s'}(i)=(1-\alpha)(\alpha)^{|s'-i|}$ and normalize $c$ and sample $m=6$ constraints using $c$ and compute $\hat{J}_{c_s'}$.
+The lookahead policy is formulated as $u(s)=\underset{\arg\min}{a\in A}(g_a(s)+\underset{s'\in S}{\sum}p_a(s,s')\hat{J}_{c_s'}$.

### 2017-03-23 errana.tex
conic stuff

@@
 \end{proof}
+
+\if0
 We now bound the performance of the greedy policy $\hu$.
@@
 \end{proof}
+\fi

### 2017-03-23 results.tex
fixed main theorem
conic stuff

@@
 \newcommand{\Jalpo}{J^*_{\alp}}
-\newcommand{\Jlro}{J^*_{\lralp}}
-\newcommand{\Jlr}{J_{\lralp}}
-Let $\Jlr$ be a solution to the LRALP given by \eqref{grlp}. When multiple solutions exist, we can choose any of them.
+\newcommand{\Jlro}{J^*_{\lralpshort}}
+\newcommand{\Jlr}{J_{\lralpshort}}
+\newcommand{\rlr}{r_{\lralpshort}}
+Let $\rlr$ be a solution to the LRALP given by \eqref{grlp}
+and let $\Jlr = \Phi \rlr$. When multiple solutions exist, we can choose any of them.
 For the result, we assume that the LRALP is not unbounded, and hence a solution exist.
@@
 \norm{J^*-\hj}_{1,c} \leq 
- \frac{2}{1-\beta_\psi} \left(
+ \frac{2 c^\top \psi}{1-\beta_\psi} \left(
 	3 \eps
@@
  (the result we cited previously is a simplified form of this bound).
-\todoc{Strange that we don't have $c^\top \psi$!?}
 The larger coefficient of $\epsilon$ is probably an artifact of our analysis. 
@@
 The extra term $\norm{\Jalpo-\Jlro}_{\infty,\psi}$ can be seen as the price paid for relaxing the constraints.
+
+From linear programming theory, it follows that primal boundedness is equivalent to dual feasibility. 
+Since the dual of $\min\{c^\top x\,:\, Ax \ge b \}$ is 
+$\max\{ y^\top b\,:\, y \ge 0, c = A^\top y\}$, we get
+that a necessary and sufficient condition for $\Jlro$ 
+to be finite-valued is that for any $s\in \S$, $\phi(s)$ lies in the conic span of $U = \Phi^\top E^\top W$.
+%(Note that the boundedness of LRALP only requires that $\Phi^\top c$ lies in the conic span of $U$.)
+When $W$ is such that its constituents $W_1,\dots,W_A$ are all identical, 
+the conic span of $U$ is equal to the conic span of $\Phi^\top W_1$. 
+It is particularly instructive 
+to consider the case when the common matrix $W_a = (w_{1,a},\dots,w_{m,a})$ ``selects'' the $m$ states,
+i.e., when $\{w_{1,a},\dots,w_{m,a}\}= \{ e_{s}\,:\, s\in \S_0 \}$ for some $\S_0\subset \S$, $|\S_0|\le m$.
+In this case the condition that $\phi(s)$ lies in the conic span of $U$ is equivalent to that $\phi(s)$ lies in the conic
+span of $\{\phi(s')\,:\, s'\in \S_0\}$. 
+Thus, to ensure boundedness, 
+the chosen states should be selected to ``conicly cover'' $\phi(\S)\doteq \{\phi(s)\,:\,s\in \S\}$.
+
+\todoc[inline]{TODO: 
+Finish error bound (see theorem below).
+Discuss how this can be done with common choices of basis functions.
+State aggregation.
+Separable choices.
+Also, this conic cover is a bit stringent.
+}
+
+\begin{theorem}
+Let $\phi(s)$%
+\footnote{Here $\phi(s)$ is the $s^{th}$ row of the feature matrix $\Phi$} be the feature of the $s^{th}$ state.
+Let $i$ be a state whose constraints have not been retained and let $\{J\}$ denote the set of states whose constraints have been retained.
+Further, let $\phi(i)\in \Re^k$ lie in the linear span of vectors $\phi(j)\in \Re^k,\forall j\in \J$, then
+\begin{align*}
+\MoveEqLeft (\Gamma J^*-\hg J^*)(i)
+ \leq 
+(\Gamma J^*-J^*)(i) \\
+& {}+J^*(i)-\underset{j\in \J}{\sum} |\gamma_j| J^*(j)
++ \underset{j\in \J}{\sum}(|\gamma_j|-\gamma_j) B,
+\end{align*}
+where $\gamma_j$ are the co-efficients of the linear span and $B\eqdef \underset{\underset{s\in S}{r\in \N}}{\max}(\Phi r) (s)$
+\end{theorem}
+\begin{proof}
+Let $r^s_{\Gamma}$ and $r^s_{\hg}$ be such that $(\Phi r^s_{\Gamma})(s)=(\Gamma J^*)(s)$ and $(\Phi r^s_{\hg})(s)=(\hg J^*)(s)$
+\begin{align*}
+\MoveEqLeft (\Gamma J^*-\hg J^*)(i) 
+=\phi(i) r^s_{\Gamma}- \phi(i) r^s_{\Gamma}\\
+&=\phi(i) r^i_{\Gamma}- \underset{j\in \J}{\sum} (|\gamma_j|+\gamma_j -|\gamma_j|)\phi(j) r^i_{\hg}\\
+&\leq \phi(i) r^i_{\Gamma}- \underset{j\in \J}{\sum} |\gamma_j| J^*(j) + \underset{j\in \J} {\sum} (|\gamma_j|-\gamma_j)B\\
+&= \phi(i) r^i_{\Gamma}- J^*(i)+ J^*(i) -\underset{j\in \J}{\sum} |\gamma_j| J^*(j) \\
+& \quad + \underset{j\in \J}{\sum} (|\gamma_j|-\gamma_j)B\,.
+\end{align*}
+\end{proof}
+
+Note that the bound of \cite{CS} and our bound can be seen as largely complementary. 
+Recall that \citeauthor{CS} consider adding an extra constraint $r\in \N$, while they propose to select all $A$ constraints
+from the ALP corresponding to $m$ states chosen at random from some distribution $\mu$. 
+Then, with high probability,
+they show that, provided that $\ralp \in \N$,
+ the extra price paid for relaxing the constraints of the ALP is $O( \rho \epsilon_{\N} k/m)$,
+ where $\rho = \max_{s} \frac{\mu^*(s)}{\mu(s)}$, $\mu^* = (1-\alpha)c^\top (I-\alpha P_{u^*})^{-1}$, $u^*$ is an optimal policy,
+and $\epsilon_{\N} = \sup_{r\in \N} \norm{J^*-\Phi r}_{\infty,\psi}$.%
+\footnote{The paper presents the results for $\mu = \mu^*$ giving $\rho=1$, but the analysis easily extends to the general case.}
+The bound is nontrivial when $m\ge \rho \epsilon_{\N} k$.
+In general, it may be hard to control $\rho$, or even $\epsilon_{\N}$ while ensuring that $\ralp \in \N$.
 

### 2017-03-23 lralp_exp/Qsystem.m
experiment folder

@@ -1,0 +1,52 @@
+clear all;
+close all;
+addpath ~/proj/MDPtoolbox
+a=1e-1*2;
+b=5;
+N=1000;
+discount=1-1/N;
+epsilon=0.1;
+p=0.2;
+q=[0.2 0.4 0.6 0.8];
+d=length(q);
+
+for i=2:N-1
+	for j=1:d
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-((i/N)^2+q(j)^3);
+	end;
+end;
+
+for j=1:d
+g(N,j)=-((N/N)^2+(q(j))^3);
+end;
+
+for j=1:d
+g(1,j)=-((1/N)+(q(j))^3);
+end;
+
+g=g;
+
+for i=1:d
+P(1,1,i)=1-p;
+P(1,2,i)=p;
+P(N,N,i)=1-q(i);
+P(N,N-1,i)=q(i);
+end;
+
+
+%[V_LP,dum, policy, cpu_time,lambda] = mdp_LP(P, g, discount,eye(N),eye(N*d),ones(N,1));
+%[V_LP,dum, policy,] = mdp_LP(P, g, discount,eye(N),eye(N*d),ones(N,1));
+[V_PI, policy, iter, cpu_time] = mdp_policy_iteration(P, g, discount);
+V_LP=V_PI;
+
+P_pol=zeros(N,N);
+g_pol=zeros(N,1);
+for i=1:N
+P_pol(i,:)=P(i,:,policy(i));
+g_pol(i)=g(i,policy(i));
+end;
+V=inv(eye(N)-discount*P_pol)*g_pol;
+

### 2017-03-23 lralp_exp/bell.m

@@ -1,0 +1,9 @@
+function [TV]=bell(P,g,discount,V);
+
+for i=1:size(P,1)
+	for a=1:size(P,3)
+		Q(a)=g(i,a)+discount*P(i,:,a)*V;
+	end;
+TV(i)=max(Q);
+end;
+TV=TV';

### 2017-03-23 lralp_exp/conepol.m

@@ -1,0 +1,34 @@
+function [policy_RLP]=conepol(P,g,discount,Phi,c)
+N=size(P,1);
+policy_RLP=ones(N,1);
+q=[0.2 0.4 0.6 0.8];
+A=4;
+Q=zeros(A,1);
+for s=2:N-1
+m=5;
+W=zeros(m+1,N*A);
+	fact=N/m;
+
+	for i=1:m-1
+	ind=(i-1)*fact+1;
+	W(i,ind)=1;
+	end;
+  W(m,N)=1;
+  W(m+1,s-1)=1;
+
+	for i=2:A
+	W(:,(i-1)*N+1:i*N)=W(:,1:N);
+	end;
+c_local=zeros(N,1);
+c_local(s-1)=1;
+[V_RLPp,r_RLP,policy_RLP]=mdp_LP(P,g,discount,Phi,W,c_local);
+  W(m+1,s-1)=0;
+    W(m+1,s+1)=1;
+    c_local(s-1)=0;
+    c_local(s+1)=1;
+[V_RLPn,r_RLP,policy_RLP]=mdp_LP(P,g,discount,Phi,W,c_local);
+	for a=1:A
+		Q(a)=g(s,a)+discount*P(s,s-1,a)*V_RLPp(s-1)+discount*P(s,s+1,a)*V_RLPn(s+1);
+	end;
+	policy_RLP(s)=min(find(Q==max(Q)));
+end;

### 2017-03-23 lralp_exp/constprint.m

@@ -1,0 +1,117 @@
+a=1e-1*2;
+b=5;
+N=10;
+discount=0.9;
+epsilon=0.1;
+p=1/2-epsilon/2;
+q=[1/4 1/2+epsilon/2];
+
+
+for i=2:N-1
+	for j=1:2
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-(a*i*i+b*j);
+	end;
+end;
+g(N,1)=-(a*N*N+b*1);
+g(N,2)=-(a*N*N+b*2);
+g(1,1)=-(a*1*1+b*1);
+g(1,2)=-(a*1*1+b*2);
+g=g*1e-1/(1-discount);
+
+fptr=fopen('constraints.tex','w');
+fprintf(fptr,'\\begin{tikzpicture}\n');
+fprintf(fptr,'\\begin{axis}[xmax=10,xmin=-20,ymax=5,ymin=-10]\n')
+%fprintf(fptr,'\\begin{axis}\n')
+%fprintf(fptr,'\\draw[->] (-3,0) -- (4.2,0) node[right] {$x$};\n');
+%fprintf(fptr,'\\draw[->] (0,-3) -- (0,4.2) node[above] {$y$};\n');
+
+for x=2:N-1
+	c='red';
+	for j=1:2
+		fprintf(fptr,'\\addplot[scale=1.0,domain=-5:5,smooth,variable=\\y,%s]  plot ({',c);
+%		fprintf(fptr,'%f+%f*(\\y-1)+%f*\\y+%f*(\\y+1)-%f*\\y',(a*x+b*q(j)),discount*q(j),discount*(1-q(j)-p),discount*p,x);
+		fprintf(fptr,'%f+%f*\\y',g(x,j),discount/(1-discount)*(q(j)*fun(x-1)+(1-q(j)-p)*fun(x)+p*fun(x+1)) -fun(x)/(1-discount));
+		fprintf(fptr,'},{\\y});\n');
+		c='black';
+	end;
+
+end;
+
+
+
+
+fprintf(fptr,'\\addplot[scale=1.0,domain=-5:5,smooth,variable=\\y,red]  plot ({',c);
+fprintf(fptr,'%f+%f*\\y',g(1,1) ,discount/(1-discount)*((1-p)*fun(1)+p*fun(1+1)) -fun(1)/(1-discount));
+fprintf(fptr,'},{\\y});\n');
+
+
[…]

### 2017-03-23 lralp_exp/fun.m

@@ -1,0 +1,2 @@
+function [r]=fun(x)
+r=x-1;

### 2017-03-23 lralp_exp/gam.m

@@ -1,0 +1,10 @@
+function [GV]=gam(V,Phi);
+
+for i=1:length(V)
+e=zeros(length(V),1);
+e(i)=1;
+f=e'*Phi;
+[r(:,i)]=glpk(f',-Phi,-V,-150*ones(size(Phi,2),1),150*ones(size(Phi,2),1), repmat(["U"],size(Phi,1),1),repmat(["C"],size(Phi,2),1),1);
+end;
+
+GV=min((Phi*r)')';

### 2017-03-23 lralp_exp/gamt.m

@@ -1,0 +1,24 @@
+function [GV,r]=gamt(V,Phi,W);
+
+d=length(V)/size(Phi,1);
+
+k=1;
+%for i=1:length(Phi)
+%	for j=1:d
+%		A(k,:)=Phi(i,:);
+%		k=k+1;
+%	end;
+%end;
+A=[];
+for a=1:d
+A=[A;Phi];
+end;
+
+for i=1:size(Phi,1)
+e=zeros(size(Phi,1),1);
+e(i)=1;
+f=e'*Phi;
+
+[r(:,i)]=glpk(f',-W*A,-W*V,-150*ones(size(Phi,2),1),150*ones(size(Phi,2),1), repmat(["U"],size(W*A,1),1),repmat(["C"],size((f))),1);
+end;
+GV=min((Phi*r)')';

### 2017-03-23 lralp_exp/genconst.m

@@ -1,0 +1,134 @@
+clear all;
+addpath ~/proj/MDPtoolbox
+a=1e-1*2;
+b=5;
+N=10;
+discount=0.98;
+epsilon=0.1;
+p=0.2;
+q=[0.2 0.4];
+d=length(q);
+for i=2:N-1
+	for j=1:d
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-((i-1)+60*q(j)^3);
+	end;
+end;
+
+for j=1:d
+g(N,j)=-(N-1+60*q(j)^3);
+end;
+
+for j=1:d
+g(1,j)=-(0+60*q(j)^3);
+end;
+
+for i=1:d
+P(1,1,i)=1-p;
+P(1,2,i)=p;
+P(N,N,i)=1-q(i);
+P(N,N-1,i)=q(i);
+end;
+
+g=g/(1-discount);
+
+fptr=fopen('queue.tex','w');
+fprintf(fptr,'\\begin{tikzpicture}\n');
+fprintf(fptr,'\\begin{axis}\n')
+
+x=1;
+	c='red';
+	for j=1:d
+		fprintf(fptr,'\\addplot[domain=-100:100,smooth,variable=\\y,%s]  plot ({',c);
+		fprintf(fptr,'%f+%f*\\y',g(x,j),discount/(1-discount)*((1-p)*fun(x)+p*fun(x+1))-fun(x)/(1-discount));
+		fprintf(fptr,'},{\\y});\n');
+		c='black';
+	end;
+
+
+for x=2:N-1
+	c='red';
+	for j=1:d
+		fprintf(fptr,'\\addplot[domain=-60:60,smooth,variable=\\y,%s]  plot ({',c);
+		fprintf(fptr,'%f+%f*\\y',g(x,j),discount/(1-discount)*(q(j)*fun(x-1)+(1-q(j)-p)*fun(x)+p*fun(x+1)) -fun(x)/(1-discount));
+		fprintf(fptr,'},{\\y});\n');
+		c='black';
+	end;
+
+end;
+
+
+x=N;
+	c='red';
+	for j=1:d
+		fprintf(fptr,'\\addplot[domain=-60:60,smooth,variable=\\y,%s]  plot ({',c);
[…]

### 2017-03-23 lralp_exp/generateW.m

@@ -1,0 +1,1 @@
+function [W,c_local]=generateW(m,N,A,discount,s)

	fact=N*A/m;
	W=zeros(m+1,N*A);
	for i=1:m
	 W(i,(i-1)*fact+1:i*fact)=1;
	end;
c_local=zeros(N,1);
	W=zeros(m+1,N*A);
	fact=N/m;
		for i=1:N
		c_local(i)=(1-discount)*discount^(abs(s-i));
		end;
    c_local=c_local/sum(c_local);
	for i=1:m
	%W(i,(i-1)*fact+1:i*fact)=1;
	ind=(i-1)*fact+1;
	ind=lot(c_local,1);
	W(i,ind)=1;
	end;
	W(m+1,s)=1;
	%c1(N)=1;
	for i=2:A
	W(:,(i-1)*N+1:i*N)=W(:,1:N);
	end;

  

### 2017-03-23 lralp_exp/large.m

@@ -1,0 +1,61 @@
+clear all;
+
+addpath ~/proj/MDPtoolbox
+N=1000;
+d=10;
+k=2;
+discount=0.9;
+[P,R]=mdp_example_rand(N,d);
+PR=mdp_computePR(P,R);
+g=PR*100;
+
+[V_LP,dum, policy, cpu_time,lambda] = mdp_LP(P, g, discount,eye(N),eye(N*d),ones(N,1));
+
+P_pol=zeros(N,N);
+g_pol=zeros(N,1);
+for i=1:N
+P_pol(i,:)=P(i,:,policy(i));
+g_pol(i)=g(i,policy(i));
+end;
+V=inv(eye(N)-discount*P_pol)*g_pol;
+
+Phi=round(rand(N,k));
+Phi(:,1)=ones(N,1);
+
+%for i=1:N
+%	for j=1:k
+%	Phi(i,j)=i^j;
+%	end;
+%end;
+
+
+[V_ALP,r_ALP,policy_ALP,cpu_time,lambda_ALP]=mdp_LP(P,g,discount,Phi,eye(N*d),ones(N,1));
+
+
+P_pol_alp=zeros(N,N);
+g_pol_alp=zeros(N,1);
+for i=1:N
+P_pol_alp(i,:)=P(i,:,policy_ALP(i));
+g_pol_alp(i)=g(i,policy_ALP(i));
+end;
+
+V_pol_alp=inv(eye(N)-discount*P_pol_alp)*g_pol_alp;
+
+m=50;
+W=round(rand(m,N*d));
+
+[V_RLP,r_RLP,policy_RLP,cpu_time,lambda_RLP]=mdp_LP(P,g,discount,Phi,W,ones(N,1));
+
+
+P_pol_rlp=zeros(N,N);
+g_pol_rlp=zeros(N,1);
+for i=1:N
+P_pol_rlp(i,:)=P(i,:,policy_RLP(i));
+g_pol_rlp(i)=g(i,policy_RLP(i));
+end;
+
+V_pol_rlp=inv(eye(N)-discount*P_pol_rlp)*g_pol_rlp;
+
+
+
+[sum(V_LP) sum(V_pol_alp) sum(V_pol_rlp)]

### 2017-03-23 lralp_exp/lookahead.m

@@ -1,0 +1,113 @@
+clear all;
+close all;
+addpath ~/proj/MDPtoolbox
+a=1e-1*2;
+b=5;
+N=1000;
+discount=1-1/N;
+epsilon=0.1;
+p=0.2;
+q=[0.2 0.4 0.6 0.8];
+d=length(q);
+
+for i=2:N-1
+	for j=1:d
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-((i/N)^2+q(j)^3);
+	end;
+end;
+
+for j=1:d
+g(N,j)=-((N/N)^2+(q(j))^3);
+end;
+
+for j=1:d
+g(1,j)=-((1/N)+(q(j))^3);
+end;
+
+g=g;
+
+for i=1:d
+P(1,1,i)=1-p;
+P(1,2,i)=p;
+P(N,N,i)=1-q(i);
+P(N,N-1,i)=q(i);
+end;
+
+
+%[V_LP,dum, policy, cpu_time,lambda] = mdp_LP(P, g, discount,eye(N),eye(N*d),ones(N,1));
+%[V_LP,dum, policy,] = mdp_LP(P, g, discount,eye(N),eye(N*d),ones(N,1));
+[V_PI, policy, iter, cpu_time] = mdp_policy_iteration(P, g, discount);
+V_LP=V_PI;
+
+P_pol=zeros(N,N);
+g_pol=zeros(N,1);
+for i=1:N
+P_pol(i,:)=P(i,:,policy(i));
+g_pol(i)=g(i,policy(i));
+end;
+V=inv(eye(N)-discount*P_pol)*g_pol;
+
+
+
+
+c=ones(N,1);
+c1=zeros(N,1);
+zeta=discount;
+for i=1:N
+Phi(i,2)=i;
+Phi(i,1)=1;
+Phi(i,3)=i*i;
+Phi(i,4)=i^3;
+c(i)=(1-zeta)*zeta^(i);
+end;
+c=c/sum(c);
+
+
+
+
+
+policy_CS=rlppol(P,g,discount,Phi,c);
+
+policy_cone=conepol(P,g,discount,Phi,c);
+
+
+P_pol_CS=zeros(N,N);
+g_pol_CS=zeros(N,1);
+for i=1:N
+P_pol_CS(i,:)=P(i,:,policy_CS(i));
+g_pol_CS(i)=g(i,policy_CS(i));
+end;
+
[…]

### 2017-03-23 lralp_exp/lot.m

@@ -1,0 +1,9 @@
+function [vec]=lot(A,num);
+B=cumsum(A);
+x=rand(1,num);
+	for i=1:num
+	vec(i)=min(find(B>x(i)));
+	end;
+
+
+

### 2017-03-23 lralp_exp/mdp_LP.m

@@ -1,0 +1,103 @@
+function [V,r, policy] = mdp_LP(P, R, discount,Phi,W,f)
+% mdp_LP    Resolution of discounted MDP with linear programming
+% Arguments --------------------------------------------------------------
+% Let S = number of states, A = number of actions
+%   P(SxSxA) = transition matrix 
+%              P could be an array with 3 dimensions or 
+%              a cell array (1xA), each cell containing a matrix (SxS) possibly sparse
+%   R(SxSxA) or (SxA) = reward matrix
+%              R could be an array with 3 dimensions (SxSxA) or 
+%              a cell array (1xA), each cell containing a sparse matrix (SxS) or
+%              a 2D array(SxA) possibly sparse  
+%   discount = discount rate, in ]0; 1[
+% Evaluation -------------------------------------------------------------
+%   V(S)   = optimal values
+%   policy(S) = optimal policy
+%   cpu_time = used CPU time
+
+% MDPtoolbox: Markov Decision Processes Toolbox
+% Copyright (C) 2009  INRA
+% Redistribution and use in source and binary forms, with or without modification, 
+% are permitted provided that the following conditions are met:
+%    * Redistributions of source code must retain the above copyright notice, 
+%      this list of conditions and the following disclaimer.
+%    * Redistributions in binary form must reproduce the above copyright notice, 
+%      this list of conditions and the following disclaimer in the documentation 
+%      and/or other materials provided with the distribution.
+%    * Neither the name of the <ORGANIZATION> nor the names of its contributors 
+%      may be used to endorse or promote products derived from this software 
+%      without specific prior written permission.
+% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" AND 
+% ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED 
[…]

### 2017-03-23 lralp_exp/mdp_policy_iteration.m

@@ -1,0 +1,125 @@
+function [V, policy, iter, cpu_time] = mdp_policy_iteration(P, R, discount, policy0, max_iter, eval_type)
+
+
+% mdp_policy_iteration  Resolution of discounted MDP 
+%                       with policy iteration algorithm
+% Arguments ---------------------------------------------------------------
+% Let S = number of states, A = number of actions
+%   P(SxSxA) = transition matrix 
+%              P could be an array with 3 dimensions or 
+%              a cell array (1xA), each cell containing a matrix (SxS) possibly sparse
+%   R(SxSxA) or (SxA) = reward matrix
+%              R could be an array with 3 dimensions (SxSxA) or 
+%              a cell array (1xA), each cell containing a sparse matrix (SxS) or
+%              a 2D array(SxA) possibly sparse  
+%   discount = discount rate, in ]0, 1[
+%   policy0(S) = starting policy, optional 
+%   max_iter = maximum number of iteration to be done, upper than 0, 
+%              optional (default 1000)
+%   eval_type = type of function used to evaluate policy: 
+%              0 for mdp_eval_policy_matrix, else mdp_eval_policy_iterative
+%              optional (default 0)
+% Evaluation --------------------------------------------------------------
+%   V(S)   = value function 
+%   policy(S) = optimal policy
+%   iter     = number of done iterations
+%   cpu_time = used CPU time
+%--------------------------------------------------------------------------
+% In verbose mode, at each iteration, displays the number 
+% of differents actions between policy n-1 and n
+
+% MDPtoolbox: Markov Decision Processes Toolbox
+% Copyright (C) 2009  INRA
+% Redistribution and use in source and binary forms, with or without modification, 
+% are permitted provided that the following conditions are met:
+%    * Redistributions of source code must retain the above copyright notice, 
+%      this list of conditions and the following disclaimer.
+%    * Redistributions in binary form must reproduce the above copyright notice, 
+%      this list of conditions and the following disclaimer in the documentation 
+%      and/or other materials provided with the distribution.
[…]

### 2017-03-23 lralp_exp/plt.m

@@ -1,0 +1,67 @@
+fptr=fopen('V','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-V(i));
+end;
+fclose(fptr);
+
+
+fptr=fopen('V_pol_alp','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-V_pol_alp(i));
+end;
+fclose(fptr);
+
+fptr=fopen('V_pol_rlp','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-V_pol_rlp(i));
+end;
+fclose(fptr);
+
+fptr=fopen('V_alp','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-V_ALP(i));
+end;
+fclose(fptr);
+
+fptr=fopen('V_rlp','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-V_RLP(i));
+end;
+fclose(fptr);
+
+fptr=fopen('V_g','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-V_g(i));
+end;
+fclose(fptr);
+
+fptr=fopen('V_t','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-V_t(i));
+end;
+fclose(fptr);
+
+
+fptr=fopen('gj','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-gj(i));
+end;
+fclose(fptr);
+
+
+fptr=fopen('ghj','w');
+for i=1:N
+fprintf(fptr,'%f\t%f\n',i,-ghj(i));
+end;
+fclose(fptr);
+
+
+fptr=fopen('r_ALP','w');
+fprintf(fptr,'%f\t%f\n',r_ALP(1),r_ALP(2));
+fclose(fptr);
+
+
+fptr=fopen('r_RLP','w');
+fprintf(fptr,'%f\t%f\n',r_RLP(1),r_RLP(2));
+fclose(fptr);
+

### 2017-03-23 lralp_exp/plts.m

@@ -1,0 +1,1 @@
+fptr=fopen('V_LP','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_LP(i));
end;

fclose(fptr);
fptr=fopen('V_pol_CS','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_pol_CS(i));
end;
fclose(fptr);

fptr=fopen('V_pol_cone','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_pol_cone(i));
end;
fclose(fptr);


fptr=fopen('policy','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy(i));
end;
fclose(fptr);

fptr=fopen('policy_CS','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy_CS(i));
end;
fclose(fptr);

fptr=fopen('policy_cone','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy_cone(i));
end;
fclose(fptr);

### 2017-03-23 lralp_exp/qbell.m

@@ -1,0 +1,9 @@
+function [TV]=qbell(P,g,discount,V);
+k=1;
+for a=1:size(P,3)
+	for i=1:size(P,1)
+		TV(k)=g(i,a)+discount*P(i,:,a)*V;
+		k=k+1;
+	end;
+end;
+TV=TV';

### 2017-03-23 lralp_exp/queue.m

@@ -1,0 +1,137 @@
+clear all;
+close all;
+addpath ~/proj/MDPtoolbox
+a=1e-1*2;
+b=5;
+N=1000;
+discount=1-1/N;
+epsilon=0.1;
+p=0.2;
+q=[0.2 0.4 0.6 0.8];
+d=length(q);
+
+for i=2:N-1
+	for j=1:d
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-((i/N)^2+q(j)^3);
+	end;
+end;
+
+for j=1:d
+g(N,j)=-((N/N)^2+(q(j))^3);
+end;
+
+for j=1:d
+g(1,j)=-((1/N)+(q(j))^3);
+end;
+
+g=g;
+
+for i=1:d
+P(1,1,i)=1-p;
+P(1,2,i)=p;
+P(N,N,i)=1-q(i);
+P(N,N-1,i)=q(i);
+end;
+
+
+%[V_LP,dum, policy, cpu_time,lambda] = mdp_LP(P, g, discount,eye(N),eye(N*d),ones(N,1));
+%[V_LP,dum, policy,] = mdp_LP(P, g, discount,eye(N),eye(N*d),ones(N,1));
+[V_PI, policy, iter, cpu_time] = mdp_policy_iteration(P, g, discount);
+V_LP=V_PI;
+
+P_pol=zeros(N,N);
+g_pol=zeros(N,1);
+for i=1:N
+P_pol(i,:)=P(i,:,policy(i));
+g_pol(i)=g(i,policy(i));
+end;
+V=inv(eye(N)-discount*P_pol)*g_pol;
+
+
+
+
+c=ones(N,1);
+c1=zeros(N,1);
+zeta=discount;
+for i=1:N
+Phi(i,2)=i;
+Phi(i,1)=1;
+Phi(i,3)=i*i;
+Phi(i,4)=i^3;
+c(i)=(1-zeta)*zeta^(i);
+end;
+c=c/sum(c);
+[V_ALP,r_ALP,policy_ALP]=mdp_LP(P,g,discount,Phi,eye(N*d),c);
+
+
+m=5;
+
+fact=N*d/m;
+W=zeros(m,N*d);
+fact=N/m;
+
+for i=1:m
+%W(i,(i-1)*fact+1:i*fact)=1;
+ind=(i-1)*fact+1;
+ind=lot(c,1);
[…]

### 2017-03-23 lralp_exp/rlppol.m

@@ -1,0 +1,17 @@
+function [policy_RLP]=rlppol(P,g,discount,Phi,c)
+N=size(P,1);
+policy_RLP=ones(N,1);
+q=[0.2 0.4 0.6 0.8];
+A=4;
+Q=zeros(A,1);
+for s=2:N-1
+m=5;
+[W,c_local]=generateW(m,N,A,discount,s-1);
+[V_RLPp,r_RLP,policy_RLP]=mdp_LP(P,g,discount,Phi,W,c_local);
+[W,c_local]=generateW(m,N,A,discount,s+1);
+[V_RLPn,r_RLP,policy_RLP]=mdp_LP(P,g,discount,Phi,W,c_local);
+	for a=1:A
+		Q(a)=g(s,a)+discount*P(s,s-1,a)*V_RLPp(s-1)+discount*P(s,s+1,a)*V_RLPn(s+1);
+	end;
+	policy_RLP(s)=min(find(Q==max(Q)));
+end;

### 2017-03-23 lralp_exp/smallqueue.m

@@ -1,0 +1,98 @@
+clear all;
+addpath ~/proj/MDPtoolbox
+
+a=1e-1*2;
+b=5;
+N=10;
+discount=0.98;
+epsilon=0.1;
+p=0.2;
+q=[0.2 0.4];
+d=length(q);
+for i=2:N-1
+	for j=1:d
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-(i-1+60*q(j)^3);
+	end;
+end;
+
+for j=1:d
+g(N,j)=-(N-1+60*q(j)^3);
+end;
+
+for j=1:d
+g(1,j)=-(0+60*q(j)^3);
+end;
+
+for i=1:d
+P(1,1,i)=1-p;
+P(1,2,i)=p;
+P(N,N,i)=1-q(i);
+P(N,N-1,i)=q(i);
+end;
+[V_PI, policy, iter] = mdp_policy_iteration(P, g, discount);
+V_LP=V_PI;
+
+P_pol=zeros(N,N);
+g_pol=zeros(N,1);
+for i=1:N
+P_pol(i,:)=P(i,:,policy(i));
+g_pol(i)=g(i,policy(i));
+end;
+V=inv(eye(N)-discount*P_pol)*g_pol;
+
+
+for i=1:N
+Phi(i,2)=i-1;
+Phi(i,1)=1;
+end;
+[V_ALP,r_ALP,policy_ALP]=mdp_LP(P,g,discount,Phi,eye(N*d),ones(N,1));
+
+m=5;
+W=zeros(m,N*d);
+fact=N/m;
+for i=1:m
+W(i,(i-1)*fact+1:i*fact)=1;
+end;
+for i=2:d
+W(:,(i-1)*N+1:i*N)=W(:,1:N);
+end;
+
+%W=rand(size(W));
+
+gj=gam(V_LP,Phi);
+Hj=qbell(P,g,discount,V_LP);
+ghj=gamt(Hj,Phi,W);
+
+
+[V_RLP,r_RLP,policy_RLP]=mdp_LP(P,g,discount,Phi,W,ones(N,1));
+
+
+
+
+
+
+
+P_pol_alp=zeros(N,N);
+g_pol_alp=zeros(N,1);
+for i=1:N
+P_pol_alp(i,:)=P(i,:,policy_ALP(i));
[…]

### 2017-03-23 lralp_exp/smallqueuec.m

@@ -1,0 +1,117 @@
+clear all;
+addpath ~/proj/MDPtoolbox
+
+a=1e-1*2;
+b=5;
+N=10;
+discount=0.98;
+epsilon=0.1;
+p=0.2;
+q=[0.2 0.4];
+d=length(q);
+for i=2:N-1
+	for j=1:d
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-(i-1+60*q(j)^3);
+	end;
+end;
+
+for j=1:d
+g(N,j)=-(N-1+60*q(j)^3);
+end;
+
+for j=1:d
+g(1,j)=-(0+60*q(j)^3);
+end;
+
+for i=1:d
+P(1,1,i)=1-p;
+P(1,2,i)=p;
+P(N,N,i)=1-q(i);
+P(N,N-1,i)=q(i);
+end;
+[V_PI, policy, iter] = mdp_policy_iteration(P, g, discount);
+V_LP=V_PI;
+
+P_pol=zeros(N,N);
+g_pol=zeros(N,1);
+for i=1:N
+P_pol(i,:)=P(i,:,policy(i));
+g_pol(i)=g(i,policy(i));
+end;
+V=inv(eye(N)-discount*P_pol)*g_pol;
+
+
+for i=1:N
+Phi(i,2)=i-1;
+Phi(i,1)=1;
+end;
+[V_ALP,r_ALP,policy_ALP]=mdp_LP(P,g,discount,Phi,eye(N*d),ones(N,1));
+
+m=5;
+W=zeros(m,N*d);
+fact=N/m;
+for i=1:m
+W(i,(i-1)*fact+1:i*fact)=1;
+end;
+for i=2:d
+W(:,(i-1)*N+1:i*N)=W(:,1:N);
+end;
+
+%W=rand(size(W));
+
+gj=gam(V_LP,Phi);
+Hj=qbell(P,g,discount,V_LP);
+ghj=gamt(Hj,Phi,W);
+
+
+[V_RLP,r_RLP,policy_RLP]=mdp_LP(P,g,discount,Phi,W,ones(N,1));
+
+
+
+
+
+
+
+P_pol_alp=zeros(N,N);
+g_pol_alp=zeros(N,1);
+for i=1:N
+P_pol_alp(i,:)=P(i,:,policy_ALP(i));
[…]

### 2017-03-23 lralp_exp/smallqueueideal.m

@@ -1,0 +1,102 @@
+clear all;
+addpath ~/proj/MDPtoolbox
+
+a=1e-1*2;
+b=5;
+N=10;
+discount=0.98;
+epsilon=0.1;
+p=0.2;
+q=[0.2 0.4];
+d=length(q);
+for i=2:N-1
+	for j=1:d
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-(i-1+60*q(j)^3);
+	end;
+end;
+
+for j=1:d
+g(N,j)=-(N-1+60*q(j)^3);
+end;
+
+for j=1:d
+g(1,j)=-(0+60*q(j)^3);
+end;
+
+for i=1:d
+P(1,1,i)=1-p;
+P(1,2,i)=p;
+P(N,N,i)=1-q(i);
+P(N,N-1,i)=q(i);
+end;
+[V_PI, policy, iter] = mdp_policy_iteration(P, g, discount);
+V_LP=V_PI;
+
+P_pol=zeros(N,N);
+g_pol=zeros(N,1);
+for i=1:N
+P_pol(i,:)=P(i,:,policy(i));
+g_pol(i)=g(i,policy(i));
+end;
+V=inv(eye(N)-discount*P_pol)*g_pol;
+
+
+for i=1:N
+Phi(i,2)=i-1;
+Phi(i,1)=1;
+end;
+[V_ALP,r_ALP,policy_ALP]=mdp_LP(P,g,discount,Phi,eye(N*d),ones(N,1));
+
+for i=1:N
+P_pol=P(:,:,policy(i));
+end;
+
+d_pol=diag(P_pol^100);
+
+sstates=lot(d_pol,5);
+m=5;
+W=zeros(m,N*d);
+fact=N/m;
+for i=1:m
+W(i,sstates(i))=1;
+end;
+for i=2:d
+W(:,(i-1)*N+1:i*N)=W(:,1:N);
+end;
+
+gj=gam(V_LP,Phi);
+Hj=qbell(P,g,discount,V_LP);
+ghj=gamt(Hj,Phi,W);
+
+[V_RLP,r_RLP,policy_RLP]=mdp_LP(P,g,discount,Phi,W,ones(N,1));
+
+
+
+
+
+
+
+P_pol_alp=zeros(N,N);
+g_pol_alp=zeros(N,1);
+for i=1:N
[…]

### 2017-03-23 lralp_exp/smallqueuerand.m

@@ -1,0 +1,98 @@
+clear all;
+addpath ~/proj/MDPtoolbox
+
+a=1e-1*2;
+b=5;
+N=100;
+discount=0.98;
+epsilon=0.1;
+p=0.2;
+q=[0.2 0.4];
+d=length(q);
+for i=2:N-1
+	for j=1:d
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-(i-1+60*q(j)^3);
+	end;
+end;
+
+for j=1:d
+g(N,j)=-(N-1+60*q(j)^3);
+end;
+
+for j=1:d
+g(1,j)=-(0+60*q(j)^3);
+end;
+
+for i=1:d
+P(1,1,i)=1-p;
+P(1,2,i)=p;
+P(N,N,i)=1-q(i);
+P(N,N-1,i)=q(i);
+end;
+[V_PI, policy, iter] = mdp_policy_iteration(P, g, discount);
+V_LP=V_PI;
+
+P_pol=zeros(N,N);
+g_pol=zeros(N,1);
+for i=1:N
+P_pol(i,:)=P(i,:,policy(i));
+g_pol(i)=g(i,policy(i));
+end;
+V=inv(eye(N)-discount*P_pol)*g_pol;
+
+
+for i=1:N
+Phi(i,2)=i-1;
+Phi(i,1)=1;
+end;
+[V_ALP,r_ALP,policy_ALP]=mdp_LP(P,g,discount,Phi,eye(N*d),ones(N,1));
+
+m=20;
+W=zeros(m,N*d);
+fact=N/m;
+for i=1:m
+W(i,(i-1)*fact+1:i*fact)=1;
+end;
+for i=2:d
+W(:,(i-1)*N+1:i*N)=W(:,1:N);
+end;
+
+W=rand(size(W));
+
+gj=gam(V_LP,Phi);
+Hj=qbell(P,g,discount,V_LP);
+ghj=gamt(Hj,Phi,W);
+
+
+[V_RLP,r_RLP,policy_RLP]=mdp_LP(P,g,discount,Phi,W,ones(N,1));
+
+
+
+
+
+
+
+P_pol_alp=zeros(N,N);
+g_pol_alp=zeros(N,1);
+for i=1:N
+P_pol_alp(i,:)=P(i,:,policy_ALP(i));
[…]

### 2017-03-23 lralp_exp/sys.m

@@ -1,0 +1,127 @@
+clear all;
+
+addpath ~/proj/MDPtoolbox
+a=1e-1*2;
+b=5;
+N=10;
+d=2;
+discount=0.9;
+epsilon=0.1;
+p=1/2-epsilon/2;
+q=[1/4 1/2+epsilon/2];
+
+for i=2:N-1
+	for j=1:2
+	P(i,i-1,j)=q(j);
+	P(i,i,j)=1-q(j)-p;
+	P(i,i+1,j)=p;
+	g(i,j)=-(a*i*i+b*j);
+	end;
+end;
+g(N,1)=-(a*N*N+b*1);
+g(N,2)=-(a*N*N+b*2);
+g(1,1)=-(a*1*1+b*1);
+g(1,2)=-(a*1*1+b*2);
+P(1,1,1)=1-p;
+P(1,2,1)=p;
+P(1,1,2)=P(1,1,1);
+P(1,2,2)=P(1,2,1);
+P(N,N,1)=1-q(1);
+P(N,N-1,1)=q(1);
+P(N,N,2)=1-q(2);
+P(N,N-1,2)=q(2);
+g=g*1e-1;
+[V_LP,dum, policy, cpu_time,lambda] = mdp_LP(P, g, discount,eye(N),eye(N*d),ones(N,1));
+
+for i=1:N
+Phi(i,2)=i*i*0.1;
+Phi(i,1)=1;
+end;
+[V_ALP,r_ALP,policy_ALP,cpu_time,lambda_ALP]=mdp_LP(P,g,discount,Phi,eye(N*d),ones(N,1));
+%W(1,:)=[1 0 1 0 1 0 1 0 1 0 0 0 0 0 0 0 0 0 0 0];
+%W(2,:)=[0 0 0 0 0 0 0 0 0 0 1 0 1 0 1 0 1 0 1 0];
+%W(3,:)=[0 1 0 1 0 1 0 1 0 1 0 0 0 0 0 0 0 0 0 0];
+%W(4,:)=[0 0 0 0 0 0 0 0 0 0 0 1 0 1 0 1 0 1 0 1];
+
+%W(1,:)=[1 1 1 1 1 0 0 0 0 0 0 0 0 0 0 0 0 0 0 0];
+%W(2,:)=[0 0 0 0 0 1 1 1 1 1 0 0 0 0 0 0 0 0 0 0];
+%W(3,:)=[0 0 0 0 0 0 0 0 0 0 1 1 1 1 1 0 0 0 0 0];
[…]

### 2017-03-23 plt.tex
including plot

\FloatBarrier
\begin{figure}[htp]
\begin{minipage}{0.5\textwidth}
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{cc}
\begin{tikzpicture}[scale=1,font=\Large,]
    \begin{axis}[
        xlabel=$t$,
        ylabel=$\theta_t$,legend style={at={(0.5,-0.1)},anchor=north}
]

    \addplot[smooth] plot file {./lralp_exp/V_LP};
    \addplot[dashed] plot file {./lralp_exp/V_pol_CS};
    \addplot[dotted] plot file {./lralp_exp/V_pol_cone};
    \addlegendentry{$J^*$};
    \addlegendentry{$J_{CS}$};
    \addlegendentry{$J_{LRA}$};

\end{axis}
\end{tikzpicture}

&
\begin{tikzpicture}[scale=1,font=\Large]
    \begin{axis}[
        xlabel=$t$,
        ylabel=$\theta_t$,legend style={at={(0.5,-0.1)},anchor=north}
]

\addplot[smooth] plot file {./lralp_exp/policy};
\addplot[dashed] plot file {./lralp_exp/policy_CS};
\addplot[dotted] plot file {./lralp_exp/policy_cone};
\addlegendentry{$u^*$};
\addlegendentry{$u_{CS}$};
\addlegendentry{$u_{LRA}$};

    \end{axis}
    \end{tikzpicture}

\end{tabular}
}
\end{minipage}
\end{figure}

### 2017-03-23 results.tex
minor changes
discussion of the main result

--- 2017-03-23 results.tex
@@
 The extra term $\norm{\Jalpo-\Jlro}_{\infty,\psi}$ can be seen as the price paid for relaxing the constraints.
+
+From linear programming theory, it follows that primal boundedness is equivalent to dual feasibility. 
+Since the dual of $\min\{c^\top x\,:\, Ax \ge b \}$ is 
+$\max\{ y^\top b\,:\, y \ge 0, c = A^\top y\}$, we get
+that a necessary and sufficient condition for $\Jlro$ 
+to be finite-valued is that for any $s\in \S$, $\phi(s)$ lies in the conic span, 
+$\{ U \lambda\,:\, \lambda\in \Re_+^{SA}\}$, of (the columns) of $U = \Phi^\top E^\top W$.
+%(Note that the boundedness of LRALP only requires that $\Phi^\top c$ lies in the conic span of $U$.)
+When $W$ is such that its constituents $W_1,\dots,W_A$ are all identical, 
+the conic span of $U$ is equal to the conic span of $\Phi^\top W_1$. 
+It is particularly instructive 
+to consider the case when the common matrix $W_a = (w_{1,a},\dots,w_{m,a})$ ``selects'' the $m$ states,
+i.e., when $\{w_{1,a},\dots,w_{m,a}\}= \{ e_{s}\,:\, s\in \S_0 \}$ for some $\S_0\subset \S$, $|\S_0|\le m$,
+where $e_s\in \{0,1\}^\S$ are the $s\in \S$ vectors in the standard Euclidean basis.
+In this case, the condition that $\phi(s)$ lies in the conic span of $U$ 
+is equivalent to that $\phi(s)$ lies in the conic span of $\phi(\S_0) \doteq \{\phi(s')\,:\, s'\in \S_0\}$. 
+Thus, to ensure boundedness of $\Jlro$, 
+the chosen states should be selected to ``conicly cover'' all the vectors in $\phi(\S)\subset \Re^k$.%
+\footnote{The same implies that, under the same condition on $W$, boundedness of the LRALP 
+holds if and only if $\sum_s c(s) \phi(s)$ is in the conic span of $\phi(\S_0)$. Note that this is easy to fulfill
+if the support of $c$ has a small cardinality by add all states in the support of $c$ to $\S_0$.
+}
+\todoc{Add reference to the intro to Mausam's book.}
+
+The next theorem shows that magnitudes of the coefficients used in the conic cover control the size of 
+$\norm{\Jalpo-\Jlro}_{\infty,\psi}$. 
+For the theorem we let $\Lambda\in \Re_+^{\S\times \S_0}$ be the matrix of conic coefficients: 
+For any $s\in \S$, $\phi(s) = \sum_{s'\in \S_0} \Lambda(s,s') \phi(s')$. After the theorem we give constructions 
+for creating conic covers.
+\begin{theorem}
+Assume that $W_1 = \dots = W_A$, $\{w_{1,a}\,dots,w_{m,a}\} = \{ e_s\,:\, s\in \S_0 \}$ 
+and that $\phi(\S)$ lies in the conic span of $\phi(\S_0)$ with conic coefficients given by $\Lambda$.
+Let $\epsilon = \inf_{r}\norm{ J^* -  \Phi r }_{\infty,\psi}$.
+Then, 
+\begin{align*}
+\norm{\Jalpo-\Jlro}_{\infty,\psi}
+\le 
+\norm{\Jalpo-J^*}_{\infty,\psi} + (1+ \norm{\Lambda \psi}_{\psi,\infty}) \epsilon\,.
+\end{align*}
+\end{theorem}
+\begin{proof}
+Let $r^*$ be such that $\norm{J^* - \Phi r^*}_{\infty,\psi} = \epsilon$ (this exists by continuity) and let 
+$\delta = J^* - \Phi r^*$.
+Pick any $s\in \S$ and let $r_s = \argmin\{ r^\top \phi(s) \,:\, W^\top E \Phi r \ge W^\top E J^*,\, r\in \Re^k \}$ 
+so that $\Jlro(s) = r_s^\top \phi(s)$.
+Note that by assumption, for any $s'\in \S_0$, $\Jlro(s') = r_s^\top \phi(s') \ge J^*(s')$.
+Now, notice that by definition, $\Jlro \le \Jalpo$ (the LP defining $\Jlro$ is the relaxation of the LP defining $\Jalpo$).
+Hence,
+\begin{align*}
+0\le \Jalpo(s) - \Jlro(s) = \Jalpo(s) - J^*(s) + J^*(s) - \Jlro(s)
+\end{align*}
+and $\Jlro(s) = r_s^\top \phi(s) = r_s^\top \sum_{s'\in \S_0} \Lambda(s,s') \phi(s') = \sum_{s'\in \S_0} \Lambda(s,s') \Jlro(s')
+\ge \sum_{s'\in \S_0} \Lambda(s,s') J^*(s')$.
+Combining this with the previous inequality we get
+\begin{align*}
+0&\le 
+ \frac{\Jalpo(s) - \Jlro(s)}{\psi(s)}\\
+&\le
+\frac{\Jalpo(s)-J^*(s)}{\psi(s)} + \frac{J^*(s) - \sum_{s'\in \S_0} \Lambda(s,s') J^*(s')}{\psi(s)}\,.
+\end{align*}
+Plugging in $J^*(s) = \phi(s)^\top r^*+\delta(s)$, using again that $\phi(s) = \sum_{s'\in \S_0} \Lambda(s,s') \phi(s')$,
+and also using the triangle inequality after taking absolute values we get
+\begin{align*}
+\MoveEqLeft \frac{|J^*(s) - \sum_{s'\in \S_0} \Lambda(s,s') J^*(s')|}{\psi(s)} \\
+& \le
+  \frac{|\delta(s)|}{\psi(s)} + \frac{\sum_{s'\in \S_0} \Lambda(s,s') |\delta(s')|}{\psi(s)} \\
+& \le
+  \frac{|\delta(s)|}{\psi(s)} + \frac{1}{\psi(s)} \, \sum_{s'\in \S_0} \Lambda(s,s') \psi(s') \frac{|\delta(s')|}{\psi(s')} \\
+& \le
+  \frac{|\delta(s)|}{\psi(s)} + \norm{\delta}_{\infty,\psi} \frac{\sum_{s'\in \S_0} \Lambda(s,s') \psi(s')}{\psi(s)} \, .
+\end{align*}
+Combining this with the previous display and noting that $\norm{\delta}_{\infty,\psi} = \epsilon$ finishes the proof.
+\if0
+Putting things together, we get 
+\begin{align*}
+\norm{\Jalpo - \Jlro}_{\infty,\psi}
+\le
+\norm{\Jalpo(s)-J^*(s)}_{\infty,\psi}
++ 
+\norm{\delta}_{\infty,\psi} (1+ \norm{\Lambda \psi}_{\infty,\psi})\,,
+\end{align*}
+finishing the proof.
+\fi
+\end{proof}
+
+Given $\phi:\S \to \Re^k$, what is the minimum cardinality set $\S_0$ that 
+conicly covers $\phi(\S)$ and how to find such a set?
+Further, how to keep the magnitude of $\norm{\Lambda \psi}_{\infty,\psi}$ small?
+To control this latter quantity it seems essential to make sure $\S_0$ contains states with high $\psi$-values.
+However, if one is content with a bound that depends on $\norm{\psi}_{\infty}$, one can bound 
+$\norm{\Lambda \psi}_{\infty,\psi}$ by $\norm{\psi}_{\infty} \zeta$ where $\zeta = \max_s \sum_{s'\in \S_0} \Lambda(s,s')$,
+hence, the second term in the previous bound will be bounded by $(1+\norm{\psi}_{\infty} \zeta) \eps$.
+
+Let us now return to the problem of finding conic covers. 
+We will proceed by considering some illustrative examples. 
+As a start, consider the case when the basis functions are binary valued.
+In this case, it is sufficient and necessary to choose one state for each binary vector 
+that appears in $\phi(\S)\subset \{0,1\}^k$.
+This gives that $m_0 \doteq |\S_0|\le 2^k$ representative states will be sufficient \emph{regardless of the cardinality of $\S$}.
+Further, in this case $\zeta = 1$.
+For moderate to large $k$ (e.g., $k\gg 20$), it will quickly become infeasible to keep $2^k$ constraints.
+In this case we may need to restrict what features are considered to guarantee the conic cover condition.
+Letting $A_i = \{s\in \S\,:\, \phi_i(s)=1 \}$, if for a many pairs $i\ne j$, $A_i$ and $A_j$ do not overlap 
+then $N = |\phi(\S)|$ can be much smaller than $2^k$. 
+For example, in the commonly used state aggregation procedures 
+$A_i \cap A_j = \emptyset$ for any $i\ne j$, giving $N=k$. 
+%In this case $N=k$: It suffices to choose one representative state from each of the $A_i$ sets and add them to the constraints. 
+In the more interesting case of 
+hierarchical aggregation (when the sets $\{A_i\}$ form a nested hierarchical partitioning of $\S$), 
+we have $m_0 \le D \cdot k$ where $D$ is the depth of the hierarchy.
+
+Another favourable example is the case of separable bases.
+In this case, the states are assumed to be factored 
+and the basis functions depend only on a few factors.
+Let us consider a simple illustration.
+By abusing notation (redefining $\S$), let $\S = \S_1 \times \S_2$, 
+let there be $k=2$ basis functions and assume that $\phi_i(s) = h_i(s)$ for some $h_i:\S_i \to \Re$, $i=1,2$.
+Assume further that $0\in h_i(\S_i)$ for both $i$ and specifically let $s_{i0}$ be such that $h_i(s_{i0})=0$.
+In this case it is not hard to verify that if $\S_{i0}$ is such that $h_i(\S_i)$ is in the conic span of $h_i(\S_{i0})$ then
+$\phi(\S)$ is also in the conic span of $\S_0 \doteq \S_1 \times \{ s_{20} \} \cup \{ s_{10} \} \times \S_2$.
+The point is that $|\S_0| \le |\S_1| + |\S_2|$, which is a tolerable increase of growth.
+This example is not hard to generalize to more general, ANOVA-like basis expansions. The moral
+is that as long as their limited order of interaction (which is usually necessary for information theoretic reasons as well),
+the number of constraints may grow moderately with the number of factors (dimensionality) of the state space.
+
+In some cases, finding a conic cover with a small cardinality is not possible. 
+This can already happen in simple examples such as when $\S = \{1,\dots,S\}$ (as before) and
+$\phi( s ) = (1,s,s^2)^\top$. In this case, the only choice is $\S_0 = \S$. 
+In examples similar to this one one possibility is to quantize the range of $\phi$, which may  loose
+little on approximation quality, while it creates the opportunity 
+to construct a small cardinality conic cover.
+
+Note that the bound of \cite{CS} and our main result can be seen as largely complementary. 
+Recall that \citeauthor{CS} consider adding an extra constraint $r\in \N$, while they propose to select all $A$ constraints
+from the ALP corresponding to $m$ states chosen at random from some distribution $\mu$. 
+Then, with high probability,
+they show that, provided that $\ralp \in \N$,
+ the extra price paid for relaxing the constraints of the ALP is $O( \rho \epsilon_{\N} k/m)$,
+ where $\rho = \max_{s} \frac{\mu^*(s)}{\mu(s)}$, $\mu^* = (1-\alpha)c^\top (I-\alpha P_{u^*})^{-1}$, $u^*$ is an optimal policy,
+and $\epsilon_{\N} = \sup_{r\in \N} \norm{J^*-\Phi r}_{\infty,\psi}$.%
+\footnote{The paper presents the results for $\mu = \mu^*$ giving $\rho=1$, but the analysis easily extends to the general case.}
+The bound is nontrivial when $m\ge \rho \epsilon_{\N} k$.
+In general, it may be hard to control $\rho$, or even $\epsilon_{\N}$ while ensuring that $\ralp \in \N$.
 

### 2017-03-23 grlp.tex
added a comment

@@
  \todoc{Give the big-Oh costs!} the number of constraints in the ALP is $SA$, 
- hence the ALP is still infeasible for huge-scale MDPs. 
+hence the ALP is still infeasible for huge-scale MDPs.\todoch{Infeasible means no solution?}
 %While evaluating the objective and checking a single constraint for constraint violations can be done in constant time,

### 2017-03-24 errana.tex
in the middle

@@
 %!TEX root =  autocontgrlp.tex
-\section{Proofs}\label{sec:improv}
+\section{Proof of \cref{cmt2}}\label{sec:improv}
+In this section we present the proof of the main result, \cref{cmt2}. 
+The proof uses contraction-arguments. 
+\newcommand{\G}{\Gamma}
+We will introduce two novel contraction operators, $\G,\hg: \Re^S \to \Re^S$, that capture the distortion introduced
+by the extra constraint in ALP and the relaxation in LRALP, respectively. 
+Then we relate the solution of LRALP to the fixed point of $\hg$.
 
+Note that for the proof it suffices to consider the case when $\Jlro$ is finite-valued because otherwise the bound is vacuous.
+Also, recall that it was assumed that $\psi$ lies in the column space of $\Phi$, while $\beta_\psi$, the $\alpha$-discounted stability of $\psi$ w.r.t.
+the MDP (cf.
+\eqref{eq:betadef}) is strictly below one.
+We also assumed that the matrix $W$ is nonnegative valued, while $c$ specifies a probability distribution over $\S$: $\sum_s c(s) = 1$ and $c\in \R_+^S$.
+
+The operators $\G,\hg$ are defined as follows: For $J\in \Re^S$, $s\in \S$,
+\begin{align*}
+(\G J)(s) & = \min\{ r^\top \phi(s) \,:\, \Phi r \ge T J ,\, r\in \Re^k \}\,,\\
+(\hg J)(s) & = \min\{ r^\top \phi(s) \,:\, W^\top E \Phi r \ge W^\top E H J ,\, r\in \Re^k\}\,.
+\end{align*}
+Note that $(\G J)(s)$ mimics the definition of ALP with $c = e_s$, except that the constraint $J = \Phi r$ is dropped.
+The same holds for $\hg$ in relation to LRALP.
+Letting $\F(J) = \{ \Phi r\,:\, \Phi r \ge T J, r\in \Re^k \}$ be the \emph{common} feasible set of the LP defining $(\G J)(s)$.
+It follows that for any $V\in \F(J)$, $V \ge \Gamma J$. Further, $\Gamma J \ge T J$.
+
+Let us now recall some basic results from the theory of contraction maps.
+First, let us recall the definition of contractions. Let $\norm{\cdot}$ be a norm on $\Re^S$ and $\rho>0$.
+We say that the map $B: \Re^S \to \Re^S$ is $(\rho,\norm{\cdot})$-Lipschitz if for any $J,J'\in \Re^S$, $\norm{ BJ - BJ' } \le \rho \norm{J-J'}$.
+We say that $B$ is a \emph{$\norm{\cdot}$-contraction} with factor $\rho$
+if it is $(\rho,\norm{\cdot})$-Lipschitz and $\rho<1$. It is particularly easy to check whether a map is a contraction map with respect to a weighted maximum norm 
+if it is known to be \emph{monotone}.
+Here, $B$ is said to be monotone if for any $J\le J'$, $J,J'\in \R^S$, $BJ \le BJ'$ also holds, where $\le$ is the componentwise
+partial order between vectors. We start with the following characterization of monotone contractions with respect to weighted maximum norms: 
+\begin{lemma}
+\label{lem:maxnormmn}
+Let $B:\R^S \to \R^S$, $\psi: \S \to \R_{++}$, $\beta\in (0,1)$.
+The following are equivalent:
+\begin{enumerate}[(i)]
+\item $B$ is a monotone contraction map with contraction factor $\beta$ with respect to $\norm{\cdot}_{\psi,\infty}$.
+\label{lem:item:mc}
+\item For any $J,J'\in \R^S$, $d\ge 0$, $J \le J' + d \psi$ implies that $BJ \le BJ' + \beta d \psi$.
+\label{lem:item:iq}
+\end{enumerate}
+\end{lemma}
+%The proof, which essentially copies Lemma 3.1 of \cite{Kall17}, is given for completeness:
+\begin{proof}
+The proof is  trivial modification of the proof of Lemma 3.1 of \cite{Kall17} and is thus left as an exercise.
+\if0
+%Note first that for any $\eps\ge 0$, $-\eps \psi \le J - J' \le \eps \psi$ implies that $\norm{J-J'}_{\mn} \le \eps$.
+Introduce $\cdot$ to denote elementwise products: Thus, $(\psi \cdot J)(s) = \psi(s) J(s)$. 
+We also let $\psi^{-1}(s) = 1/\psi(s)$ and we will use the shorthand $\norm{\cdot} = \norm{\cdot}_{\mn}$.
+
+Let us first prove \eqref{lem:item:mc} $\Rightarrow $ \eqref{lem:item:iq}. 
+Thus, assume that $B$ is a monotone contraction
+map with factor $\beta$. Take any $J,J'$, $d>0$, $J \le J'+ d\psi$. 
+We have $BJ = B(J + d \psi) - B J' + B J' \le (\psi^{-1} \cdot (B(J + d \psi) - B J' ))\cdot \psi + BJ'
+\le \norm{B(J+d\psi) - BJ'} \psi + BJ' \le \beta d \norm{J-J'} \psi +  BJ'$.
+
+For the reverse direction, note that monotinicity follows by taking $d=0$.
+Now, let $\eps = \norm{J-J'}$. Then, $J \le J'+ \eps \psi$ and $J' \le J+\eps \psi$.
+By monotonicity and the assumed property of $B$ (using $d=\eps\ge 0$), 
+$-\beta \eps \psi \le BJ - BJ' \le \beta \eps \psi$, which implies
+that $\norm{BJ - BJ'} \le \beta$.
+\fi
+\end{proof}
+\begin{corollary}
+\label{maxnormmn}
+\label{cor:maxnormmn}
+If $B$ is monotone and there exists some $\beta\in [0,1)$ such that for any $J\in \Re^S$ and $d>0$,
+\begin{align}
+\label{eq:shiftmn}
+B( J + d \psi) \le B J + \beta d \psi
+\end{align} 
+then $B$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
+\end{corollary}
+\begin{proof}
+Let $J,J'\in \R^S$, $d\ge 0$ and assume that $J\le J' + d \psi$. By monotonicity $BJ \le B(J'+ d \psi)$, while
+by~\eqref{eq:shiftmn}, $B(J'+d\psi) \le BJ' + \beta d \psi$. Hence, $BJ \le BJ' + \beta d \psi$. 
+This shows that \eqref{lem:item:iq} of \cref{lem:maxnormmn} holds. Hence, by this lemma, $B$ is a contraction with factor $\beta$ with respect to $\norm{\cdot}_{\mn}$.
+\end{proof}
+\if0
+\begin{proof}
+First, we show that for any $t\ge 0$,  $J\in \Re^n$,
+$B( J - t \psi) \ge B J - \beta t \psi$ also holds.
+To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $B J \le B J' + \beta t \psi$. Reordering this inequality gives the result.
+Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \Re^n$ are arbitrary.
+Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
+By the monotonicity of $B$,
+$B(J_2 - \eps \psi) \le B J_1 \le B(J_2 + \eps \psi)$. 
+Using~\eqref{eq:shiftmn}, we get 
+$B J_2 - \beta \eps \psi \le B J_1 \le B J_2 + \beta \eps \psi$, i.e., $-\beta \eps \psi \le B J_1 - B J_2 \le \beta \eps \psi$, from which the result follows.
+\end{proof}
+\fi
+
+\if0
 In this section we present the main results of this paper in \Cref{cmt2} (we state improved bounds in \Cref{sec:improv}).
@@
 
+\fi
+
+\if0
 \subsection{Properties of the Bellman Operator}
@@
 We also adopt a similar approach by stating our results using Lyapunov function based arguments.
+\fi
 
+Let us now return to the proof of our main result. Recall that the goal is to bound 
+$\norm{J^*-\Jlr}_{1,c}$ through relating this deviations from the fixed point of $\hg$, which was promised to be a contraction.
+Let us thus now prove this.
+%\emph{Since all $1$-norms will use the same weighting $c$, we will abbreviate $\norm{\cdot}_{1,c}$ to $\norm{\cdot}_1$.
+Similarly, since all maximum norms use the same weighting $\psi$, we will abbreviate $\norm{\cdot}_{\infty,\psi}$ to $\norm{\cdot}_{\infty}$.}
+For this, it suffices to show that $\hg$ satisfies the conditions of \cref{cor:maxnormmn}.
+In fact, we will see this holds with $\beta =\beta_\psi$. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{lemma}\label{tgmonotone}\label{gshiftmn}
+The operator satisfies the conditions of \cref{cor:maxnormmn} with $\beta =\beta_\psi$, and is thus a 
+$\norm{\cdot}_{\mn}$-contraction with coefficient $\beta_\psi$. 
+%For $J_1, J_2\in \Re^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
+\end{lemma}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{proof}
+First, recall that $H$ is monotone (all 
+the $P_a$ matrices in the definition of $H$ are nonnegative valued) 
+and that it satisfies an inequality similar to \eqref{eq:shiftmn}: For any $t\ge 0$, $J\in \R^S$,
+\begin{align}\label{eq:psilin}
+\begin{split}
+%T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi,\\
+H(J+ t \psi ) \le HJ + E \beta_{\psi}\,t\,  \psi\,.
+\end{split}
+\end{align}
+
+Let us now prove that $\hg$ is monotone. 
+Given $J\in \Re^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$.
+Choose any $i\in \{1, \ldots, n\}$.
+Since $J_1\leq J_2$, from $W$ is nonnegative valued and $H$ is monotone,
+%\Cref{tprop}-\eqref{monotone} and \cref{grlpassmp}-\eqref{wassmp} 
+it follows that $W^\top H J_1\leq W^\top H J_2$. Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.  Since $i$ was arbitrary, monotonicity of $\hg$ follows.
+
+Let us now turn to proving that \eqref{eq:shiftmn} holds with $\beta =\beta_\psi$.
+By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N' \}$.
+By \eqref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta_\psi \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi \psi)$. Thus,
+$(\hg (J+t\psi) )(i) \le 
+ \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
+Now, using \Cref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=e_i\Phi$, $b_0=t\beta_\psi \psi$
+and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
+\end{proof}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Now, recall further that if $B:\R^S \to \R^S$ is a $(\beta,\norm{\cdot})$-contraction then it has a unique fixed point $J^*_B\in \R^S$ (i.e., $B J^*_B= J^*_B$). Further, for any $J\in \R^S$,
+\begin{align}
+\label{eq:csdw}
+\frac{\norm{J-J^*_B}}{1-\beta} \le \norm{ BJ - J } \le (1+\beta) \norm{J-J^*_B}\,.
+\end{align}
+That is, $\norm{BJ-J}$ is closely tied to the distance of $J$ from $J^*_B$.%
+\footnote{This is also a standard result.
+The upper bound can be obtained using a triangle inequality and exploiting that $J^*_B$ is a fixed point of $B$ which is a contraction.
+The lower bound follows by writing $J - J^*_B = (\sum_{k=0}^n B^k J - B^{k+1} J ) + B^{n+1} J - B^{n+1} J^*_B$, taking norms using the triangle inequality together with the contraction property of $B$ and finally letting $n\to \infty$.}
+We will repeatedly apply this inequality.
+
+Let $\hv$ be the fixed point $\hg$.
+Then, by the triangle inequality,
+\begin{align*}
+\norm{J^*-\Jlr}_{1,c} \le \norm{J^*-\hv}_{1,c} +\norm{\hv-\Jlr}_{1,c}\,.
+\end{align*}
+Let us first bound the second term. Recall that $\Jlr = \Phi \rlr$.
+We claim the following:
+\begin{lemma}
+aaa
+\end{lemma}
+
+\if0
 We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \Re^n$ and $t>0$,
@@
 \end{align}
+\fi
 %\input{schematic}
@@
 \end{proof}
-\begin{lemma}\label{tgmonotone}
-For $J_1, J_2\in \Re^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
-\end{lemma}
-\begin{proof}
-Given $J\in \Re^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$.
-Choose any $i\in \{1, \ldots, n\}$.
-Since $J_1\leq J_2$, from \Cref{tprop}-\eqref{monotone} and \cref{grlpassmp}-\eqref{wassmp} it follows that $W^\top H J_1\leq W^\top H J_2$.
-Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.
-Since $i$ was arbitrary, the result follows.
-\end{proof}
-\begin{lemma}\label{maxnormmn}
-Assume that $\hg: \Re^n \to \Re^n$ is monotone and 
-that there exists some $\beta\in [0,1)$ such that for any $J\in \Re^n$ and $t>0$,
-\begin{align}
-\label{eq:shiftmn}
-\hg( J + t \psi) \le \hg J + \beta t \psi.
-\end{align} 
-Then $\hg$ is a $\norm{\cdot}_{\mn}$ contraction with factor $\beta$.
-\end{lemma}
-\begin{proof}
-First, we show that for any $t\ge 0$,  $J\in \Re^n$,
-$\hg( J - t \psi) \ge \hg J - \beta t \psi$ also holds.
-To see this define $J' = J-t\psi$. Then, $J = J'+t\psi$, hence $\hg J \le \hg J' + \beta t \psi$. Reordering this inequality gives the result.
-Let $\eps = \norm{J_1 - J_2}_{\mn}$, where $J_1,J_2\in \Re^n$ are arbitrary.
-Then $J_2 - \eps \psi \le J_1 \le J_2 + \eps \psi$. 
-By the monotonicity of $\hg$,
-$\hg(J_2 - \eps \psi) \le \hg J_1 \le \hg(J_2 + \eps \psi)$. 
-Using~\eqref{eq:shiftmn}, we get 
-$\hg J_2 - \beta \eps \psi \le \hg J_1 \le \hg J_2 + \beta \eps \psi$, i.e., $-\beta \eps \psi \le \hg J_1 - \hg J_2 \le \beta \eps \psi$, from which the result follows.
-\end{proof}
+
 \begin{corollary}\label{tmaxnormmn}
@@
 %Returning to $\hg$, since we already now that $\hg$ is monotone (cf. \cref{gmonotone}), it remains to see that it satisfies \eqref{eq:shiftmn}:
-\begin{lemma}\label{gshiftmn}
-The operator $\hg$ satisfies \eqref{eq:shiftmn} with $\beta = \beta_\psi$.
-%For any $J\in \Re^n$, $t\in \Re_+$, $\Gamma (J+ t \psi ) \le \Gamma J + \beta_{\psi} t \psi$.
-\end{lemma}
-\begin{proof}
-By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N' \}$.
-By \eqref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta_\psi \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi \psi)$. Thus,
-$(\hg (J+t\psi) )(i) \le 
- \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
-Now, using \Cref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=e_i\Phi$, $b_0=t\beta_\psi \psi$
-and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
-\end{proof}
+
 %From this result and \cref{maxnormmn}, we immediately get that $\Gamma$ is a contraction in $\norm{\cdot}_{\mn}$:
@@
 In what follows we denote by $\hv$ the unique fixed point of $\hg$, i.e., $\hv = \hg \hv\,$.
+
 We now show that vector $\hj$ dominates $\hv$:

### 2017-03-24 grlp.tex
in the middle

--- 2017-03-23 grlp.tex
@@
 
-To introduce the optimization problem we study first recall that 
+To introduce the optimization problem we study, first recall that 
 the optimal value function $J^*$ is the solution of the fixed point equation $TJ^* = J^*$. 
 It follows from the definition of $T$ that $J^* = \max_u T_u J^* \ge T_u J^*$ for any $u$, 
-where $\ge$ is the componentwise partial ordering of vectors. 
+where $\ge$ is the componentwise partial ordering of vectors ($\le$ is the reverse relation).
 With some abuse of notation, we also introduce $T_a$ to denote $T_u$ where $u(s) = a$ for any $s\in \S$. 
@@
 \if0
-Since $T$ is monotone (i.e., for any $J_1\le J_2$ it holds that $TJ_1 \le T J_2$) and can be seen to be an $\alpha$-contraction with respect to the maximum norm, if $J$ is superharmonic then $J \ge T J \ge T^2 J \ge \dots \ge J^*$, where the last inequality follows since $T$ is an $\alpha$-contraction and hence $T^n J \to J^*$ in the maximum norm, and hence also componentwise.
+Since $T$ is \emph{monotone} (i.e., for any $J_1\le J_2$ it holds that $TJ_1 \le T J_2$) and can be seen to be an $\alpha$-contraction with respect to the maximum norm, if $J$ is superharmonic then $J \ge T J \ge T^2 J \ge \dots \ge J^*$, where the last inequality follows since $T$ is an $\alpha$-contraction and hence $T^n J \to J^*$ in the maximum norm, and hence also componentwise.
 Thus, $J^*$ is the ``smallest'' superharmonic function. It follows than that 

### 2017-03-24 grlp.tex
minor edits

--- 2017-03-24 grlp.tex
@@
 
-While the solving the ALP can be significantly cheaper than solving the LP underlying the MDP
+While solving the ALP can be significantly cheaper than solving the LP underlying the MDP
 and thus it can be advantageous for moderate-scale MDPs,
  \todoc{Give the big-Oh costs!} the number of constraints in the ALP is $SA$, 
- hence the ALP is still infeasible for huge-scale MDPs. 
+hence the ALP is still intractable for huge-scale MDPs.
 %While evaluating the objective and checking a single constraint for constraint violations can be done in constant time,

### 2017-03-24 errana.tex
proof finished

@@
 \newcommand{\G}{\Gamma}
-We will introduce two novel contraction operators, $\G,\hg: \Re^S \to \Re^S$, that capture the distortion introduced
+We will introduce a novel contraction operators, $\hg: \Re^S \to \Re^S$, that captures the distortion introduced
 by the extra constraint in ALP and the relaxation in LRALP, respectively. 
@@
 \eqref{eq:betadef}) is strictly below one.
+We will let $r_0\in \R^k$ be such that $\psi = \Phi r_0$.
 We also assumed that the matrix $W$ is nonnegative valued, while $c$ specifies a probability distribution over $\S$: $\sum_s c(s) = 1$ and $c\in \R_+^S$.
 
-The operators $\G,\hg$ are defined as follows: For $J\in \Re^S$, $s\in \S$,
+The operator $\hg$ are defined as follows: For $J\in \Re^S$, $s\in \S$,
 \begin{align*}
-(\G J)(s) & = \min\{ r^\top \phi(s) \,:\, \Phi r \ge T J ,\, r\in \Re^k \}\,,\\
+%(\G J)(s) & = \min\{ r^\top \phi(s) \,:\, \Phi r \ge T J ,\, r\in \Re^k \}\,,\\
 (\hg J)(s) & = \min\{ r^\top \phi(s) \,:\, W^\top E \Phi r \ge W^\top E H J ,\, r\in \Re^k\}\,.
 \end{align*}
-Note that $(\G J)(s)$ mimics the definition of ALP with $c = e_s$, except that the constraint $J = \Phi r$ is dropped.
-The same holds for $\hg$ in relation to LRALP.
-Letting $\F(J) = \{ \Phi r\,:\, \Phi r \ge T J, r\in \Re^k \}$ be the \emph{common} feasible set of the LP defining $(\G J)(s)$.
-It follows that for any $V\in \F(J)$, $V \ge \Gamma J$. Further, $\Gamma J \ge T J$.
+Note that $(\hg J)(s)$ mimics the definition of ALP with $c = e_s$, except that the constraint $J = \Phi r$ is dropped.
+%The same holds for $\hg$ in relation to LRALP.
+%Letting $\F(J) = \{ \Phi r\,:\, \Phi r \ge T J, r\in \Re^k \}$ be the \emph{common} feasible set of the LP defining $(\G J)(s)$.
+%It follows that for any $V\in \F(J)$, $V \ge \Gamma J$. Further, $\Gamma J \ge T J$.
 
@@
 \label{lem:item:mc}
-\item For any $J,J'\in \R^S$, $d\ge 0$, $J \le J' + d \psi$ implies that $BJ \le BJ' + \beta d \psi$.
+\item For any $J,J'\in \R^S$, $t\ge 0$, $J \le J' + t \psi$ implies that $BJ \le BJ' + \beta t \psi$.
 \label{lem:item:iq}
@@
 Thus, assume that $B$ is a monotone contraction
-map with factor $\beta$. Take any $J,J'$, $d>0$, $J \le J'+ d\psi$. 
-We have $BJ = B(J + d \psi) - B J' + B J' \le (\psi^{-1} \cdot (B(J + d \psi) - B J' ))\cdot \psi + BJ'
-\le \norm{B(J+d\psi) - BJ'} \psi + BJ' \le \beta d \norm{J-J'} \psi +  BJ'$.
+map with factor $\beta$. Take any $J,J'$, $t>0$, $J \le J'+ t\psi$. 
+We have $BJ = B(J + t \psi) - B J' + B J' \le (\psi^{-1} \cdot (B(J + t \psi) - B J' ))\cdot \psi + BJ'
+\le \norm{B(J+t\psi) - BJ'} \psi + BJ' \le \beta t \norm{J-J'} \psi +  BJ'$.
 
-For the reverse direction, note that monotinicity follows by taking $d=0$.
+For the reverse direction, note that monotinicity follows by taking $t=0$.
 Now, let $\eps = \norm{J-J'}$. Then, $J \le J'+ \eps \psi$ and $J' \le J+\eps \psi$.
-By monotonicity and the assumed property of $B$ (using $d=\eps\ge 0$), 
+By monotonicity and the assumed property of $B$ (using $t=\eps\ge 0$), 
 $-\beta \eps \psi \le BJ - BJ' \le \beta \eps \psi$, which implies
@@
 \label{cor:maxnormmn}
-If $B$ is monotone and there exists some $\beta\in [0,1)$ such that for any $J\in \Re^S$ and $d>0$,
+If $B$ is monotone and there exists some $\beta\in [0,1)$ such that for any $J\in \Re^S$ and $t>0$,
 \begin{align}
 \label{eq:shiftmn}
-B( J + d \psi) \le B J + \beta d \psi
+B( J + t \psi) \le B J + \beta t \psi
 \end{align} 
@@
 \begin{proof}
-Let $J,J'\in \R^S$, $d\ge 0$ and assume that $J\le J' + d \psi$. By monotonicity $BJ \le B(J'+ d \psi)$, while
-by~\eqref{eq:shiftmn}, $B(J'+d\psi) \le BJ' + \beta d \psi$. Hence, $BJ \le BJ' + \beta d \psi$. 
-This shows that \eqref{lem:item:iq} of \cref{lem:maxnormmn} holds. Hence, by this lemma, $B$ is a contraction with factor $\beta$ with respect to $\norm{\cdot}_{\mn}$.
+Let $J,J'\in \R^S$, $t\ge 0$ and assume that $J\le J' + t \psi$. By monotonicity $BJ \le B(J'+ t \psi)$, while
+by~\eqref{eq:shiftmn}, $B(J'+t\psi) \le BJ' + \beta t \psi$. Hence, $BJ \le BJ' + \beta t \psi$. 
+This shows that \eqref{lem:item:iq} of \cref{lem:maxnormmn} holds. 
+Hence, by this lemma, $B$ is a contraction with factor $\beta$ with respect to $\norm{\cdot}_{\mn}$.
 \end{proof}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{lemma}\label{tgmonotone}\label{gshiftmn}
-The operator satisfies the conditions of \cref{cor:maxnormmn} with $\beta =\beta_\psi$, and is thus a 
+\begin{proposition}\label{tgmonotone}\label{gshiftmn}
+The operator $\hg$ satisfies the conditions of \cref{cor:maxnormmn} with $\beta =\beta_\psi$, and is thus a 
 $\norm{\cdot}_{\mn}$-contraction with coefficient $\beta_\psi$. 
 %For $J_1, J_2\in \Re^n$ such that $J_1\leq J_2$, we have $\hg J_1\leq \hg J_2$.
-\end{lemma}
+\end{proposition}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{proof}
-First, recall that $H$ is monotone (all 
+First, note that (as it is well known) $H$ is monotone (all 
 the $P_a$ matrices in the definition of $H$ are nonnegative valued) 
@@
 %T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi,\\
-H(J+ t \psi ) \le HJ + E \beta_{\psi}\,t\,  \psi\,.
+H(J+ t \psi ) \le HJ + \beta_{\psi}\,t\,  E  \psi\,.
 \end{split}
 \end{align}
+This follows again because our assumption on $\psi$ implies that for any $a\in \A$, $\alpha P_a \psi \le \beta_{\psi} \psi$.
 
 Let us now prove that $\hg$ is monotone. 
-Given $J\in \Re^n$, let $\F_J\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \N'\,\}\,$.
-Choose any $i\in \{1, \ldots, n\}$.
-Since $J_1\leq J_2$, from $W$ is nonnegative valued and $H$ is monotone,
+Given $J\in \Re^S$, let $\F'(J)\eqdef\{\,\Phi r\,: W^\top E \Phi r\geq W^\top HJ, r\in \Re^k\,\}\,$. 
+Choose any $s\in \S$. Since $J_1\leq J_2$, $W$ is nonnegative valued and $H$ is monotone, 
 %\Cref{tprop}-\eqref{monotone} and \cref{grlpassmp}-\eqref{wassmp} 
-it follows that $W^\top H J_1\leq W^\top H J_2$. Hence, $\F_{J_2} \subset \F_{J_1}$ and thus $(\hg J_1)(i) \le (\hg J_2)(i)$.  Since $i$ was arbitrary, monotonicity of $\hg$ follows.
+we have $W^\top H J_1\leq W^\top H J_2$. 
+Hence, $\F_{J_2} \subset \F_{J_1}$ 
+and thus $(\hg J_1)(s) \le (\hg J_2)(s)$.  Since $s$ was arbitrary, monotonicity of $\hg$ follows.
 
 Let us now turn to proving that \eqref{eq:shiftmn} holds with $\beta =\beta_\psi$.
-By definition, for $1\le i \le n$, $(\hg (J+t\psi) )(i) = \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \N' \}$.
-By \eqref{eq:psilin}, as $t>0$, $H(J+t\psi) \le HJ + t \beta_\psi \psi$ and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi \psi)$. Thus,
-$(\hg (J+t\psi) )(i) \le 
- \min\{ e_i^\top \Phi r \,:\, W^\top E\Phi r \ge W^\top HJ+t\beta_\psi \psi), r\in \N' \}$.
-Now, using \Cref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=e_i\Phi$, $b_0=t\beta_\psi \psi$
-and $x_0=t \beta_\psi r_0$, the statement follows since $A x_0 = b_0$ (from \cref{grlpassmp}-\eqref{lyap}) and $\N' = \N' + \alpha t r_0$ (from \cref{grlpassmp}-\eqref{ass:n4}).
+By definition, for $s\in \S$, $t\ge 0$, $J\in \R^S$, 
+$(\hg (J+t\psi) )(s) = \min\{ r^\top \phi(s) \,:\, W^\top E\Phi r \ge W^\top H(J+t\psi), r\in \Re^k \}$.
+By \eqref{eq:psilin}, 
+$H(J+t\psi) \le HJ + t \beta_\psi E \psi$ 
+and hence $W^\top H(J+t\psi) \le W^\top (HJ + t \beta_\psi E \psi)$. 
+Thus,
+$(\hg (J+t\psi) )(s) \le  \min\{ r^\top \phi(s)\,:\, W^\top E\Phi r \ge W^\top (HJ+t\beta_\psi E \psi), r\in \Re^k \}$.
+
+To finish, we need the following elementary observation:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{claim}\label{lpsol}
+Let $A\in \Re^{u\times v}$, $b\in \Re^u,d\in \Re^v$ and $b_0=Ax_0$ for
+some $x_0 \in \Re^v$. % $\N' \subset \Re^v$ such that $\N' =x_0+ \N'$. 
+Then
+\begin{align*}
+\begin{split}
+\MoveEqLeft \min\{d^\top x:Ax\geq b+b_0, x\in \Re^v\} \nn\\
+&=\min\{d^\top y:Ay \geq b, y \in \Re^v \}+d^\top x_0.
+\end{split}
+\end{align*}
+\end{claim}
+\begin{proof}[Proof of \cref{lpsol}]
+The claim follows by the change of variables $y := x-x_0$.
+\end{proof}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Now, using \Cref{lpsol} with $A=W^\top E \Phi$, $b=W^\top HJ$, $d=\phi(s)$, $b_0=t\beta_\psi W^\top E \psi$
+and $x_0=t \beta_\psi r_0$,  thanks to $\Phi r_0 = \psi$ we have $A x_0 = b_0$.
+Hence the desired statement follows from the claim.
 \end{proof}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Let us now return to bounding $\norm{J^*-\Jlr}_{1,c}$.
+For $x\in \Re$, let $(x)^-$ be the negative part of $x$: $(x)^- = \max(-x,0)$. Then, $|x| = x + 2 (x)^-$. For a vector $J\in \R^S$, 
+we will write $(J)^-$ to denote the vector obtained by applying the negative part componentwise.
+We consider the decomposition
+\begin{align}
+\label{eq:maindec}
+\norm{\Jlr-J^*}_{1,c} = c^\top ( \Jlr - J^* ) + 2c^\top ( \Jlr - J^* )^-\,.
+\end{align}
+Let $\hv$ be the fixed point $\hg$. We know claim the following:
+\begin{claim}
+We have $\Jlr \ge \hv$, $c^\top \Jalp \ge c^\top \Jlr$.
+\end{claim}
+\begin{proof}
+The inequality $c^\top \Jalp \ge c^\top \Jlr$  follows immediately from the definitions of $\Jalp$ and $\Jlr$.
+
+To prove the first part let $s\in \S$,  $c=e_s$ and let $r_s$ be a solution to LRALP in \eqref{grlp}.
+For $s\in \S$, let $V_0(s)= \min_{s'\in \S} r_{s'}^\top \phi(s)$.
+
+It suffices to show that $V_1\eqdef \hg V_0 \le V_0 \le \hj$.
+Indeed, if this holds then
+$V_{n+1} = \hg V_n$, $n\ge 1$, satisfies $V_{n+1}\le V_n$ and $V_n \to \hv$ as $n\to\infty$
+since $\hg$ is a monotone contraction mapping.
+
+Since  $r_{s'}^\top \phi(s) \ge r_s^\top \phi(s)$ %$(\Phi r_{s'})(s) \ge (\Phi r_s)(s)$
+ also holds for any $s,s'\in \S$,
+we have $V_0(s)  = r_s^\top \phi(s)$. %$(\Phi r_s)(s)$. 
+Also, since $\hj(s) \ge r_s^\top \phi(s)$, % (\Phi r_s)(s)$,$s\in \S$
+it follows that $\hj\geq V_0$. 
+Now,  fix some $s\in \S$ and
+define $r'_{e_s,V_0}$ be the solution to the linear program defining $(\hg V_0)(s)$.
+We need to show that $V_1(s)=(\hg V_0)(s) = ( r'_{e_s,V_0})^\top \phi(s) \leq V_0(s)$. 
+By the definition of $r'_{e_s,V_0}$ we know that $( r'_{e_s,V_0})^\top \phi(s) \le r^\top \phi(s)$ %$(\Phi r)(s)$
+holds for any $r\in \Re^k$ such that $W^\top E \Phi r \ge W^\top H V_0$. 
+Thus, it suffices to show that $r_s$ satisfies $W^\top E \Phi r_s \ge W^\top H V_0$. 
+By definition, $r_s$ satisfies $W^\top E \Phi r_s \ge W^\top H \Phi r_s$.
+Hence, by the monotone property of $H$ and since $W$ is nonnegative valued, % and \cref{grlpassmp}-\eqref{wassmp} 
+it is sufficient if $\Phi r_s \ge V_0$.
+This however follows from the definition of $V_0$.
+\end{proof}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Thanks to the previous claim, $(\Jlr - J^*)^- \le (\hv - J^*)^-$ and $c^\top \Jlr \le c^\top \Jalp$. Hence, 
+from \eqref{eq:maindec} we get
+\begin{align*}
+%\label{eq:maindec2}
+\norm{\Jlr-J^*}_{1,c} \le c^\top\!( \Jalp - J^* ) + 2c^\top\!( \hv - J^* )^-\,.
+\end{align*}
+By Theorem 3 of \cite{ALP}, the first term is bounded by $2 \frac{c^\top \psi}{1-\beta_\psi} \epsilon$, where
+recall that $\epsilon = \inf_{r} \norm{J^* - \Phi r}_{\mn}$. Hence, it remains to bound the second term.
+
+For this, note that for any $J\in \R^S$, 
+$(J)^-\le |J|$
+and also that $\norm{J}_{1,c} \le c^\top \psi \norm{ J }_{\mn}$. Hence, we switch to bounding 
+$\norm{J^* - \hv }_{\mn}$.
+A standard contraction argument gives
+\begin{align*}
+\norm{J^* - \hv }_{\mn}
+& =   \norm{ J^* - \hg J^ + \hg J^* -\hg \hv }_{\mn} \\
+& \le \norm{ J^* - \hg J^*}_{\mn} + \norm{\hg J^* - \hv }_{\mn} \\
+& \le \norm{ J^* - \hg J^*}_{\mn} + \beta_\psi \norm{\hg J^* - \hv }_{\mn}\,.
+\end{align*}
+Reordering and using another triangle inequality we get
+\begin{align*}
+\norm{J^* - \hv }_{\mn} \le \frac{
+\norm{J^* - \Jalpo}_{\mn} + \norm{ \Jalpo - \hg J^* }_{\mn}
+}{1-\beta_\psi}\,.
+\end{align*}
+We bound the term $\norm{J^* - \Jalpo}_{\mn}$ in the following lemma:
+\begin{lemma}\label{bestbndmn}
+We have
+\begin{align}
+\norm{J^*-\Jalpo}_{\mn}\leq 2 \epsilon\,,
+\end{align}
+where recall that $\epsilon = \inf_{r\in \Re^k} \norm{ J^*-\Phi r }_{\mn}$. 
+\end{lemma}
+\begin{proof}
+Let $r^*\eqdef \argmin_{r\in \Re^k} \norm{ J^*-\Phi r }_{\mn}$. 
+First, notice that $\Jalpo \ge J^*$.
+Hence, $0\le \Jalpo - J^*$.
+Now let $r' = r^* + \epsilon r_0$. Then, 
+$\Phi r' = \Phi r^* + \epsilon \psi \ge J^*$, where the equality follows by the definition of $r_0$ and
+the inequality follows by the definition of $\epsilon$.
+Hence, $r'$ is in the feasible set of the LP defining $\Jalpo$ and thus $\Jalpo \le \Phi r'$.
+Thus, $0\le \Jalpo - J^* \le \Phi r^* - J^* + \epsilon \psi$. Dividing componentwise by $\psi$,
+taking absolute value and then taking maximum of both sides gives the result.
+\end{proof}
+The proof of the main result is finished by noting that $\hg J^* = \Jlro$ and the chaining the inequalities we derived.
+
+\if0
 Now, recall further that if $B:\R^S \to \R^S$ is a $(\beta,\norm{\cdot})$-contraction then it has a unique fixed point $J^*_B\in \R^S$ (i.e., $B J^*_B= J^*_B$). Further, for any $J\in \R^S$,
@@
 Let us first bound the second term. Recall that $\Jlr = \Phi \rlr$.
-We claim the following:
-\begin{lemma}
-aaa
-\end{lemma}
 
@@
 %\input{schematic}
-The next lemma is elementary, but will prove to be useful:
-\begin{lemma}\label{lpsol}
-Let $A\in \Re^{u\times v}$, $b\in \Re^u,d\in \Re^v$ and $b_0=Ax_0$ for
-some $x_0 \in \Re^v$, $\N' \subset \Re^v$ such that $\N' =x_0+ \N'$. Then
-\begin{align}
-&\min\{d^\top x:Ax\geq b+b_0, x\in \N'\} \nn\\
-&=\min\{d^\top y:Ay \geq b, y \in \N' \}+d^\top x_0.
-\end{align}
-\end{lemma}
-\begin{proof}
-The claim follows by the change of variables $y := x-x_0$.
-\end{proof}
+
 \noindent 
@@
 %where $\psi$ is a Lyapunov function as in \cref{lyap}.
-\begin{lemma}\label{bestbndmn}
-Let $r^*\eqdef\underset{r\in \Re^k}{\min}\parallel J^*-\Phi r\parallel_{\mn}$. Then,
-\begin{align}
-\norm{J^*-\Gamma J^*}_{\mn}\leq 2 \norm{J^*-\Phi r^*}_{\mn}.
-\end{align}
-\end{lemma}
-\begin{proof}
-Define $\eps = \norm{J^* - \Phi r^*}_{\mn}$ so that
-$ J^*-\Phi r^* \le \eps \psi$ and $\Phi r^* - J^*\le \eps \psi$.
-Then, from \cref{grlpassmp}-\eqref{ass:n4} it follows that $\Phi( r^* + \eps r_0 ) = \Phi r^* + \eps \psi \ge J^* = T J^*$.
-From the definition of $\Gamma$ in \eqref{gamdef} and \cref{ubrem}, we know that $\Phi r^*+\eps \psi \geq \Gamma J^*\geq J^*$.
-The result follows by noting that $2\eps\psi\geq \Phi r^*+\eps\psi -J^*\geq \Gamma J^*-J^*\geq 0$.
-\end{proof}
 
@@
 
-We now show that vector $\hj$ dominates $\hv$:
-\begin{lemma}\label{relation1}
-The vectors $\hv,\hj$ obey $\hj\geq\hv$.
-\end{lemma}
-\begin{proof}
-For $i\in \{1,\dots,n\}$, $c=e_i$ let $r_i$ be a solution to GRLP in \eqref{grlp}
-and define $V_0\in \Re^n$ by $V_0(i)=\underset{j=1,\ldots,n}{\min}(\Phi r_j)(i)$, $1\le i \le n$.
-
-It suffices to show that $V_1\eqdef \hg V_0 \le V_0 \le \hj$ since then the desired result follows
-by defining $V_{n+1} = \hg V_n$, $n\ge 1$, noting that by \cref{tgmonotone}, $V_{n+1}\le V_{n}$ and by  \cref{tmaxnormmn}, $V_n \to \hv$.
-
-Since $(\Phi r_j)(i) \ge (\Phi r_i)(i)$ also holds for any $1\leq i,j\leq n$ we have $V_0(i)  = (\Phi r_i)(i)$. Also, since $\hj(i) \ge (\Phi r_i)(i),1\leq i \leq n$ it follows that $\hj\geq V_0$. 
-Now,  fix any $i$. 
-We need to show that $V_1(i)=(\hg V_0)(i) = (\Phi r'_{e_i,V_0})(i) \leq V_0(i)$. 
-By the definition of $r'_{e_i,V_0}$ we know that $(\Phi r'_{e_i,V_0})(i) \le (\Phi r)(i)$
-holds for any $r\in \N$ such that $W^\top E \Phi r \ge W^\top H V_0$. 
-Now it suffices to show that $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H V_0$. 
-By definition, $r_i$ satisfies $W^\top E \Phi r_i \ge W^\top H \Phi r_i$.
-Hence, by the monotone property of $H$ and \cref{grlpassmp}-\eqref{wassmp} it is sufficient if $\Phi r_i \ge V_0$.
-This however follows from the definition of $V_0$.
-\end{proof}
 \begin{lemma}\label{relation2}
@@
 \end{proof}
-
+\fi
 \if0

### 2017-03-24 num.tex

@@
 We consider a single queue with arrivals and departures.
-The state of the system is the queue length with the state space given by $S=\{0,\ldots,n-1\}$, where $n-1$ is the buffer size of the queue.
-The action set $A=\{1,\ldots,d\}$ is related to the service rates.
+The state of the system is the queue length with the state space given by $\S=\{0,\ldots,S-1\}$, where $S-1$ is the buffer size of the queue.
+The action set $\A=\{1,\ldots,A\}$ is related to the service rates.
 We let $s_t$ denote the state at time $t$.
-The state at time $t+1$ when action $a_t \in A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$.
+The state at time $t+1$ when action $a_t \in \A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$.
 For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by $s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$.
-The service rates satisfy $0<q(1)\leq \ldots\leq q(d)<1$ with $q(d)>p$ so as to ensure `stabilizability' of the queue.
-The reward associated with the action $a \in A$ in state $s\in S$ is given by $g_a(s)=-(s/n+q(a)^3)$.\par
-\textbf{Parameter Settings:} We ran our experiments $n=1000$, $d=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=1-\frac{1}{n}$.
-The moderate size of $n=1000$ enabled us to compute the exact the exact value of $J^*$ (it was however expensive).
+The service rates satisfy $0<q(1)\leq \ldots\leq q(A)<1$ with $q(A)>p$ so as to ensure `stabilizability' of the queue.
+The reward associated with the action $a \in \A$ in state $s\in \S$ is given by $g_a(s)=-(s/n+q(a)^3)$.\par
+\textbf{Parameter Settings:} We ran our experiments $S=1000$, $A=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=1-\frac{1}{S}$.
+The moderate size of $S=1000$ enabled us to compute the exact the exact value of $J^*$ (it was however expensive).
 We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work reasonably well for this domain \cite{ALP}, and chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors).\\
@@
 The lookahead policy is formulated as $u(s)=\underset{\arg\min}{a\in A}(g_a(s)+\underset{s'\in S}{\sum}p_a(s,s')\hat{J}_{c_s'}$.
+\input{plt.tex}

### 2017-03-24 plt.tex
thickening lines

@@
 
-    \addplot[smooth] plot file {./lralp_exp/V_LP};
-    \addplot[dashed] plot file {./lralp_exp/V_pol_CS};
-    \addplot[dotted] plot file {./lralp_exp/V_pol_cone};
+    \addplot[smooth,thick] plot file {./lralp_exp/V_LP};
+    \addplot[dashed,thick] plot file {./lralp_exp/V_pol_CS};
+    \addplot[dotted,thick] plot file {./lralp_exp/V_pol_cone};
     \addlegendentry{$J^*$};

### 2017-03-24 plt.tex
edited the pats

--- 2017-03-23 plt.tex
@@
 \begin{tikzpicture}[scale=1,font=\Large,]
-    \begin{axis}[
-        xlabel=$t$,
-        ylabel=$\theta_t$,legend style={at={(0.5,-0.1)},anchor=north}
-]
-
-    \addplot[smooth] plot file {./lralp_exp/V_LP};
-    \addplot[dashed] plot file {./lralp_exp/V_pol_CS};
-    \addplot[dotted] plot file {./lralp_exp/V_pol_cone};
+    \begin{axis}[]
+    \addplot[smooth,very thick, mark=diamond, each nth point=100] plot file {./lralp_exp/V_LP};
+    \addplot[dashed,very thick, mark=+, each nth point=100] plot file {./lralp_exp/V_pol_CS};
+    \addplot[dotted,very thick,mark=square, each nth point=100] plot file {./lralp_exp/V_pol_cone};
     \addlegendentry{$J^*$};
@@
 \begin{tikzpicture}[scale=1,font=\Large]
-    \begin{axis}[
-        xlabel=$t$,
-        ylabel=$\theta_t$,legend style={at={(0.5,-0.1)},anchor=north}
-]
-
-\addplot[smooth] plot file {./lralp_exp/policy};
-\addplot[dashed] plot file {./lralp_exp/policy_CS};
-\addplot[dotted] plot file {./lralp_exp/policy_cone};
+    \begin{axis}[]
+\addplot[smooth,very thick, mark=diamond, each nth point=100] plot file {./lralp_exp/policy};
+\addplot[dashed,very thick, mark=+, each nth point=100] plot file {./lralp_exp/policy_CS};
+\addplot[dotted,very thick, mark=square, each nth point=100] plot file {./lralp_exp/policy_cone};
 \addlegendentry{$u^*$};

### 2017-03-24 lralp_exp/plts.m

@@ -1,1 +1,1 @@
-fptr=fopen('V_LP','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_LP(i));
end;

fclose(fptr);
fptr=fopen('V_pol_CS','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_pol_CS(i));
end;
fclose(fptr);

fptr=fopen('V_pol_cone','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_pol_cone(i));
end;
fclose(fptr);


fptr=fopen('policy','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy(i));
end;
fclose(fptr);

fptr=fopen('policy_CS','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy_CS(i));
end;
fclose(fptr);

fptr=fopen('policy_cone','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy_cone(i));
end;
fclose(fptr);
+fptr=fopen('V_LP','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_LP(i));
end;

fclose(fptr);
fptr=fopen('V_pol_CS','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_pol_CS(i));
end;
fclose(fptr);

fptr=fopen('V_pol_cone','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,V_pol_cone(i));
end;
fclose(fptr);


fptr=fopen('policy','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy(i));
end;
fclose(fptr);

fptr=fopen('policy_CS','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy_CS(i));
end;
fclose(fptr);

fptr=fopen('policy_cone','w');
for i=1:N
fprintf(fptr,'%e\t%e\t',i,policy_cone(i));
end;
fclose(fptr);

load('V_LP');

fptr=fopen('V_LP_samp','w');
for i=1:100:N
fprintf(fptr,'%e\t%e\t',i,V_LP(i,2));
end
fclose(fptr);

load('V_pol_CS');

fptr=fopen('V_pol_CS','w');
for i=1:100:N
fprintf(fptr,'%e\t%e\t',i,V_pol_CS(i,2));
end
fclose(fptr);
[…]

### 2017-03-24 num.tex
edited num.tex

@@
 When formulating the LRALP for state $s'$, we let $c=e_{s'}$ and choose the constraint corresponding to state $s'$ to ensure the cone condition.
-We choose $5$ more constraints corresponding to states $1,200,400,600,800,999$ (uniformly spaced across the state space) and compute $\hat{J}_{e_s'}$.
-The lookahead policy is formulated as $u(s)=\underset{\arg\min}{a\in A}(g_a(s)+\underset{s'\in S}{\sum}p_a(s,s')\hat{J}_{e_s'}$.\\
+We choose $5$ more constraints corresponding to states $1,200,400,600,800,999$ (uniformly spaced across the state space) and compute $\hat{J}_{e_{s'}}$.
+The lookahead policy is formulated as $u(s)={\argmin}_{a\in A}(g_a(s)+{\sum}_{s'\in S}p_a(s,s')\hat{J}_{e_s'}$.\\
 $Case (ii):$ In a manner similar to $Case (i)$, here too we formulate two separate RLPs for next states.
 When formulating the RLP for state $s'$, we first let $c_{s'}(i)=(1-\alpha)(\alpha)^{|s'-i|}$ and normalize $c$ and sample $m=6$ constraints using $c$ and compute $\hat{J}_{c_s'}$.
-The lookahead policy is formulated as $u(s)=\underset{\arg\min}{a\in A}(g_a(s)+\underset{s'\in S}{\sum}p_a(s,s')\hat{J}_{c_s'}$.
+The lookahead policy is formulated as $u(s)={\argmin}_{a\in A}(g_a(s)+{\sum}_{s'\in S}p_a(s,s')\hat{J}_{c_{s'}}$.
 \input{plt.tex}

### 2017-03-24 concl.tex
exp, conc

@@
+%!TEX root =  autocontgrlp.tex
 \section{Conclusion}
-The approximate linear programming (ALP) is an approximate dynamic programming method that addresses the prediction and control problems successfully.
+In this paper, we introduced and analyzed the linearly relaxed approximate linear program (LRALP) whose constraints were obtained as positive linear combination of the original constraints of the ALP.
+The main novel contribution is a theoretical result which gives a geometrically interpretable bound on the performance loss due to relaxing the constraint sets.
+Possibilities for future work include extending the results to other forms of approximate linear programming in MDPs (e.g., \citep{SALP}), designing algorithms that use the newly derived results to actively compute what constraints to select, just to mention a few.
+%By providing performance analysis for the GRLP, this paper justified linear function approximation of the dual variables of the ALP. 
+\begin{comment}
+The approximate linear program (ALP) is a widely employed method to handle MDPs with large number of states.
 However, an important shortcoming of the ALP is that it has large number of constraints, which is tackled in practice by sampling a tractable number of constraints from the ALP to formulate and solve a reduced linear program (RLP).
-Though RLP has been found to work well empirically in various domains ranging from queues to Tetris games, performance guarantees are available only in the case of a specific RLP formulated under idealized assumptions.
-Thus there has been a gap in the theory of constraint reduction.\\
-In this paper, we introduced a novel framework based on the generalized reduced linear program formulation to study constraint reduction.
+The RLP has been found to work well empirically in various domains ranging from queues to Tetris games, and performance guarantees are for a specific RLP formulated under idealized assumptions.
+Alternatively, function approximation in the dual variables of the ALP has been another approach that has been employed in literature \cite{ALP-Bor,dolgov} to address the issue of large number of constraints.
+However there was no prior theoretical characterization for the function approximation of the dual variables.\par
+In this paper, we introduced a novel framework based on the generalized reduced linear program formulation.
 The constraints of the GRLP were obtained as positive linear combinations of the original ALP.
@@
 We also made qualitative and quantitative observations about the nature of the error term that arose due to constraint reduction.
-Our analysis also revealed the fact that it is not always necessary to sample according to the stationary distribution of the optimal policy and, in fact, potentially several different constraint sampling/approximation strategies might work.
+% Our analysis also revealed the fact that it is not always necessary to sample according to the stationary distribution of the optimal policy and, in fact, potentially several different constraint sampling/approximation strategies might work.
 In particular, we also theoretically justified linear function approximation of the constraints.
@@
 To conclude, we observe that by providing a novel theoretical framework to study constraint approximation, this paper provides important results that add to the theory of ALP.
+\end{comment}

### 2017-03-24 num.tex
exp, conc

--- 2017-03-24 num.tex
@@
 \section{Numerical Illustration}
-In this section, we show via an example in the domain of controlled queues to show that the consequences of \Cref{conetheorm} (the \emph{cone} condition) derived based on the geometric intuition (please refer \cite{aaaipaper} for preliminary experiments in this domain).
+In this section, we show via an example in the domain of controlled queues the consequences of \cref{conetheorm},
+which bounded the error when the constraints are chosen based on selecting a set of representative states
+% (the \emph{cone} condition) derived based on the geometric intuition 
+ (further preliminary experimental results have been reported in \cite{aaaipaper}).
 
-\textbf{Queuing System Model:} The queuing model used here is similar to the one in Section~$5.2$ of \cite{ALP}.
+\textbf{Model:} We run the experiments in the context of a queuing model similar to the one in Section~5.2 of \cite{ALP}.
 We consider a single queue with arrivals and departures.
@@
 We let $s_t$ denote the state at time $t$.
-The state at time $t+1$ when action $a_t \in \A $ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$.
+The state at time $t+1$ when action $a_t \in \A$ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$.
 For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by $s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$.
 The service rates satisfy $0<q(1)\leq \ldots\leq q(A)<1$ with $q(A)>p$ so as to ensure `stabilizability' of the queue.
-The reward associated with the action $a \in \A$ in state $s\in \S$ is given by $g_a(s)=-(s/n+q(a)^3)$.\par
-\textbf{Parameter Settings:} We ran our experiments $S=1000$, $A=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=1-\frac{1}{S}$.
-The moderate size of $S=1000$ enabled us to compute the exact the exact value of $J^*$ (it was however expensive).
-We made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) since they are known to work reasonably well for this domain \cite{ALP}, and chose $k=4$ (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors).\\
+The reward associated with  action $a \in \A$ and state $s\in \S$ is given by $g_a(s)=-(s/n+q(a)^3)$.
+
+\textbf{Parameter Settings:} We ran our experiments for $S=1000$, $A=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=1-\frac{1}{S}$.
+The moderate size of $S=1000$ enabled us to compute the exact value of $J^*$ (the most expensive part of the computation). 
+Despite that the conic span condition cannot be met with them, as a way of testing the limits of the theory,
+we made use of polynomial features in $\Phi$ (i.e., $1,s,\ldots,s^{k-1}$) 
+since they are known to work reasonably well for this domain \cite{ALP}.
+We chose $k=4$. % (i.e., we used $1, s,s^2$ and $s^3$ as basis vectors).
+
 \textbf{Experimental Methodology:} We compare two different sampling strategies $(i)$ based on the \emph{cone} conditions, and $(ii)$ based on constraint sampling.
@@
 The details are as follows:
-$Case (i):$ Except for the corner states i.e., $s=1$ and $s=999$, each state $1<s<n-1$ has two next states namely $s'=s-1$ and $s'=s+1$.
-We formulate two separate LRALPs (or just one LRALP for $s=1$ and $s=n-1$) for next states.
-When formulating the LRALP for state $s'$, we let $c=e_{s'}$ and choose the constraint corresponding to state $s'$ to ensure the cone condition.
+\emph{Case (i)}: Except for the corner states i.e., $s=0$ and $s=999$, each state $0<s<n-1$ has two next states namely $s'=s-1$ and $s'=s+1$.
+We formulate two separate LRALPs (or just one LRALP for $s=0$ and $s=n-1$) for next states.
+When formulating the LRALP for state $s'$, we let $c=e_{s'}$ and choose the constraint corresponding to state $s'$ to ensure the cone condition to be met for LRALP.
 We choose $5$ more constraints corresponding to states $1,200,400,600,800,999$ (uniformly spaced across the state space) and compute $\hat{J}_{e_s'}$.
-The lookahead policy is formulated as $u(s)=\underset{\arg\min}{a\in A}(g_a(s)+\underset{s'\in S}{\sum}p_a(s,s')\hat{J}_{e_s'}$.\\
-$Case (ii):$ In a manner similar to $Case (i)$, here too we formulate two separate RLPs for next states.
-When formulating the RLP for state $s'$, we first let $c_{s'}(i)=(1-\alpha)(\alpha)^{|s'-i|}$ and normalize $c$ and sample $m=6$ constraints using $c$ and compute $\hat{J}_{c_s'}$.
-The lookahead policy is formulated as $u(s)=\underset{\arg\min}{a\in A}(g_a(s)+\underset{s'\in S}{\sum}p_a(s,s')\hat{J}_{c_s'}$.
+The lookahead policy is formulated as
+$u_{LRA}(s)=\argmin_{a\in A}(g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{e_s'}(s')$.
+
+\emph{Case (ii)}: In a manner similar to \emph{Case (i)}, here too we formulate two separate LRALPs for next states.
+When formulating the LRALP for state $s'$, we first let $c_{s'}(i)=(1-\alpha)(\alpha)^{|s'-i|}$ and normalize $c$ and sample $m=6$ constraints randomly using $c$ and compute $\hat{J}_{c_s'}$.
+The lookahead policy is formulated as 
+$u_{CS}(s)=\argmin_{a\in A}(g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{c_s'}(s')$.
+
+The results are shown in the figures below:
 \input{plt.tex}
+The right-hand-side figure shows the policies computed, 
+while the left-hand-side figure shows their value functions. 
+Since constraint sampling (CS) produces randomized results,
+we repeated the simulations 10 times. 
+The results in all cases were quite similar except for one ``bad case'' for CS , hence we show the plot for a typical run.
+As can be seen from the figure, choosing the constraints to (approximately) satisfy the constraint of the theoretical results
+reliably produces better results: In fact, the value functions $J^*$ and $J_{LRA}$ are mostly on the top of each other.
+While these results are only meant for illustration,
+we expect that in larger domains it becomes even more important to select the constraints appropriately.
+However, the study of this is left for future work.

### 2017-03-24 results.tex
in the middle
exp, conc

@@
 The purpose of this section is to present our main results.
-\newcommand{\Jalpo}{J^*_{\alp}}
-\newcommand{\Jlro}{J^*_{\lralpshort}}
-\newcommand{\Jlr}{J_{\lralpshort}}
-\newcommand{\rlr}{r_{\lralpshort}}
 Let $\rlr$ be a solution to the LRALP given by \eqref{grlp}
@@
 Just like \citet{ALP}, we will also require that $\psi$ is a \emph{stochastic Lyapunov-function} for the MDP.  In particular, we require that the $\alpha$-discounted stability coefficient
-\begin{align*}
+\begin{align} \label{eq:betadef}
 \beta_\psi \doteq \alpha  \max_{a} \norm{P_a \psi}_{\infty,\psi}
-\end{align*}
+\end{align}
 is strictly less than one.
@@
 \begin{theorem}
+\label{conetheorm}
 Assume that $W_1 = \dots = W_A$, $\{w_{1,a}\,dots,w_{m,a}\} = \{ e_s\,:\, s\in \S_0 \}$ 
@@
 Plugging in $J^*(s) = \phi(s)^\top r^*+\delta(s)$, using again that $\phi(s) = \sum_{s'\in \S_0} \Lambda(s,s') \phi(s')$,
-and also using the triangle inequality after taking absolute values we get
+and also using the triangle inequality after taking absolute values, we get
 \begin{align*}
@@
   \frac{|\delta(s)|}{\psi(s)} + \frac{\sum_{s'\in \S_0} \Lambda(s,s') |\delta(s')|}{\psi(s)} \\
-& \le
-  \frac{|\delta(s)|}{\psi(s)} + \frac{1}{\psi(s)} \, \sum_{s'\in \S_0} \Lambda(s,s') \psi(s') \frac{|\delta(s')|}{\psi(s')} \\
+%& \le
+%  \frac{|\delta(s)|}{\psi(s)} + \frac{1}{\psi(s)} \, \sum_{s'\in \S_0} \Lambda(s,s') \psi(s') \frac{|\delta(s')|}{\psi(s')} \\
 & \le

### 2017-03-24 num.tex
minor edits

@@
 The state at time $t+1$ when action $a_t \in \A$ is chosen is given by $s_{t+1}= s_{t}+1$ with probability $p$, $s_{t+1}= s_{t}-1$ with probability $q(a_t)$ and $s_{t+1}= s_t$, with probability $(1-p-q(a_t))$.
-For states $s_t=0$ and $s_t=n-1$, the system dynamics is given by $s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=n-1$.
+For states $s_t=0$ and $s_t=S-1$, the system dynamics is given by $s_{t+1}= s_{t}+1$ with probability $p$ when $s_t=0$ and $s_{t+1}=s_t-1$ with probability $q(a_t)$ when $s_t=S-1$.
 The service rates satisfy $0<q(1)\leq \ldots\leq q(A)<1$ with $q(A)>p$ so as to ensure `stabilizability' of the queue.
@@
 The details are as follows:
-\emph{Case (i)}: Except for the corner states i.e., $s=0$ and $s=999$, each state $0<s<n-1$ has two next states namely $s'=s-1$ and $s'=s+1$.
-We formulate two separate LRALPs (or just one LRALP for $s=0$ and $s=n-1$) for next states.
+\emph{Case (i)}: Except for the corner states i.e., $s=0$ and $s=999$, each state $0<s<S-1$ has two next states namely $s'=s-1$ and $s'=s+1$.
+We formulate two separate LRALPs (or just one LRALP for $s=0$ and $s=S-1$) for next states.
 When formulating the LRALP for state $s'$, we let $c=e_{s'}$ and choose the constraint corresponding to state $s'$ to ensure the cone condition to be met for LRALP.
-We choose $5$ more constraints corresponding to states $1,200,400,600,800,999$ (uniformly spaced across the state space) and compute $\hat{J}_{e_s'}$.
+We choose $5$ more constraints corresponding to states $1,200,400,600,800,999$ (uniformly spaced across the state space) and compute $\hat{J}_{e_{s'}}$.
 The lookahead policy is formulated as
@@
 The lookahead policy is formulated as 
-$u_{CS}(s)=\argmin_{a\in A}(g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{c_s'}(s')$.
+$u_{CS}(s)=\argmin_{a\in A}(g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{c_{s'}}(s')$.
 

### 2017-03-24 plt.tex
minor edits

@@
     \begin{axis}[]
-\addplot[smooth,very thick, mark=diamond, each nth point=100] plot file {./lralp_exp/policy};
-\addplot[dashed,very thick, mark=+, each nth point=100] plot file {./lralp_exp/policy_CS};
-\addplot[dotted,very thick, mark=square, each nth point=100] plot file {./lralp_exp/policy_cone};
+\addplot[smooth,very thick] plot file {./lralp_exp/policy};
+\addplot[dashed,very thick] plot file {./lralp_exp/policy_CS};
+\addplot[dotted,very thick] plot file {./lralp_exp/policy_cone};
 \addlegendentry{$u^*$};

### 2017-03-24 abstract.tex
addressed the comments by Csaba
intro
compressed version; down to 8 pages

@@
+%!TEX root =  autocontgrlp.tex
 \begin{abstract}
@@
 A serious limitation of ALP is that it has an intractable number of constraints, as a result of which constraint approximations are of interest.
-In this paper, we define a generalized reduced linear program (GRLP) that has a tractable number of constraints, which are obtained as positive linear combinations of the original constraints of the ALP.
-The main contribution of this paper is a novel theoretical framework developed to obtain error bounds for any given GRLP.
-By providing a detailed error analysis for the GRLP, we justify linear approximation of the dual variables.
+In this paper, we define a linearly relaxed approximation linear program (LRALP) that has a tractable number of constraints, obtained as positive linear combinations of the original constraints of the ALP.
+The main contribution is a novel performance bound for LRALP.
+%By providing a detailed error analysis for the GRLP, we justify usage of a linear architecture for approximating the dual variables.
 Unlike prior results on constraint sampling, our analysis is deterministic and is based on a novel contraction operator.
@@
 \begin{keywords}{
-Approximate Dynamic Programming (ADP), Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), Generalized Reduced Linear Program (GRLP), Constraint Sampling, Reinforcement Learning.}
+%Approximate Dynamic Programming (ADP), 
+Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), %Generalized Reduced Linear Program (GRLP), 
+%Constraint Sampling, Reinforcement Learning
+}
 \end{keywords}

### 2017-03-24 grlp.tex
compressed version; down to 8 pages

@@
 Our position is that the set $\N$ would most likely be chosen based on very little and general information;
-the useful knowledge is in choosing $W$, not in some general set $\N$. 
-Since randomization does not guarantee bounded solutions, \citet{ALP} needs to use $\N$, which incorporates
-all the knowledge which makes the LP bounded. Since 
-$\N$
-or we could incorporate the choice into $W$.
-On the occasion when the LP without the extra $r\in \N$ constraint would be unbounded,
-the solution found when $r\in \N$ is added would lie on the boundary of $\N$, which
-makes one expect the error of the resulting solution to be rather large.
+the useful knowledge is in choosing $W$, not in choosing some general set $\N$. 
+Since randomization does not guarantee bounded solutions, \citet{ALP} must use $\N$:
+In their case, $\N$ incorporates 
+all the knowledge that makes the LP bounded. 
 }

### 2017-03-24 results.tex
compressed version; down to 8 pages

@@
  \frac{2 c^\top \psi}{1-\beta_\psi} \left(
-	3 \eps
+	2.5 \eps
      +\norm{\Jalpo-\Jlro}_{\infty,\psi}\right)\,.
@@
 Hence,
-\begin{align*}
+$%\begin{align*}
 0\le \Jalpo(s) - \Jlro(s) = \Jalpo(s) - J^*(s) + J^*(s) - \Jlro(s)
-\end{align*}
+$% \end{align*}
 and $\Jlro(s) = r_s^\top \phi(s) = r_s^\top \sum_{s'\in \S_0} \Lambda(s,s') \phi(s') = \sum_{s'\in \S_0} \Lambda(s,s') \Jlro(s')
@@
 Combining this with the previous inequality we get
-\begin{align*}
-0&\le 
+$%\begin{align*}
+0\le
+%&\le 
  \frac{\Jalpo(s) - \Jlro(s)}{\psi(s)}\\
-&\le
-\frac{\Jalpo(s)-J^*(s)}{\psi(s)} + \frac{J^*(s) - \sum_{s'\in \S_0} \Lambda(s,s') J^*(s')}{\psi(s)}\,.
-\end{align*}
+ \le
+%&\le
+\frac{\Jalpo(s)-J^*(s)}{\psi(s)} + \frac{J^*(s) - \sum_{s'\in \S_0} \Lambda(s,s') J^*(s')}{\psi(s)}
+%\,.
+$. % \end{align*}
 Plugging in $J^*(s) = \phi(s)^\top r^*+\delta(s)$, using again that $\phi(s) = \sum_{s'\in \S_0} \Lambda(s,s') \phi(s')$,

### 2017-03-24 concl.tex
minor edits

@@
 The main novel contribution is a theoretical result which gives a geometrically interpretable bound on the performance loss due to relaxing the constraint sets.
-Possibilities for future work include extending the results to other forms of approximate linear programming in MDPs (e.g., \citep{SALP}), designing algorithms that use the newly derived results to actively compute what constraints to select, just to mention a few.
+Possibilities for future work include extending the results to other forms of approximate linear programming in MDPs (e.g., \citep{SALP}), exploring the idea of approximating dual variables and
+designing algorithms that use the newly derived results to actively compute what constraints to select.
 %By providing performance analysis for the GRLP, this paper justified linear function approximation of the dual variables of the ALP. 

### 2017-03-24 num.tex
minor edits

@@
 The lookahead policy is formulated as
-$u_{LRA}(s)=\argmin_{a\in A}(g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{e_s'}(s')$.
+$u_{LRA}(s)=\argmin_{a\in A} g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{e_s'}(s')$.
 
@@
 The lookahead policy is formulated as 
-$u_{CS}(s)=\argmin_{a\in A}(g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{c_{s'}}(s')$.
+$u_{CS}(s)=\argmin_{a\in A} g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{c_{s'}}(s')$.
 

### 2017-03-24 intro.tex
e.g. cite change

@@
 In this paper we consider the so-called \emph{approximate linear programming} (ALP) approach, which
-was heavily studied during the last two decades 
-\cite[e.g.,][]{
+was heavily studied during the last two decades, e.g.,
+\cite{
 schuurmans,

### 2017-03-24 grlp.tex
cleaning todos

@@
 where $W_a = (w_{1,a},\dots,w_{m,a}) \in \Re_+^{S \times m}$. 
-\todoc{Do we need that $(w_{i,a}^\top)_i$ defines a probability distribution?}
 Note that the $(i,j)$th entry of the $m\times k$ constraint matrix of the resulting LP is
@@
 
-We will call the LP in \eqref{grlp} the \emph{linearly relaxed approximate linear program (LRALP)}. \todoc{Replace GRLP everywhere with LRALP.} Any LP obtained using 
+We will call the LP in \eqref{grlp} the \emph{linearly relaxed approximate linear program (LRALP)}. 
+Any LP obtained using 
 any constraint selection/generation process can be represented by choosing an appropriate binary-valued matrix

### 2017-03-24 intro.tex
cleaning todos

@@
 is nearly as good as a policy chosen by a suitable (computationally unbounded, and well-informed) oracle
-from a given restricted policy class}. \todoc{Is this better now? We should probably elaborate on the oracle idea space permitting.}
+from a given restricted policy class}. \todoc{We should probably elaborate on the oracle idea space permitting.
+Or in the future. Btw, the situation is similar to statistical learning theory: There competing with the best choice 
+is only information theoretically possible. And competing with best choice
+in hindsight is often computationally intractable. Maybe cite information theory result for competing with the best policy in a class?}
 Here, within some restrictions (see below), the policy class can be chosen by the user.
-The more flexibility the user is given in this choice, the stronger a planning method is.
+The more flexibility the user is given in this choice, the stronger a planning method is. \todoc{Add reference to the intro to Mausam's book. But where and what can be said?}
 

### 2017-03-24 num.tex
cleaning todos

@@
 The lookahead policy is formulated as
-$u_{LRA}(s)=\argmin_{a\in A} g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{e_s'}(s')$.
+$u_{LRA}(s)=\argmin_{a\in A} g_a(s)+\sum_{s'\in S}p_a(s,s')\hat{J}_{e_{s'}}(s')$.
 
 \emph{Case (ii)}: In a manner similar to \emph{Case (i)}, here too we formulate two separate LRALPs for next states.
-When formulating the LRALP for state $s'$, we first let $c_{s'}(i)=(1-\alpha)(\alpha)^{|s'-i|}$ and normalize $c$ and sample $m=6$ constraints randomly using $c$ and compute $\hat{J}_{c_s'}$.
+When formulating the LRALP for state $s'$, we first let $c_{s'}(s)=(1-\alpha)(\alpha)^{|s'-s|}$ and normalize $c$ and sample $m=6$ constraints randomly using $c$ and compute $\hat{J}_{c_s'}$.
 The lookahead policy is formulated as 

### 2017-03-24 intro.tex
notes on literature

@@
 independent of the size of the state space \cite{rust96:randomization,szepesvari2001,kearns2002sparse}.
+\todoc{Maybe we can cite Mausam's book here as discussing a whole range of methods originating from AI
+that target this problem, although without theoretical guarantees.}
 Nevertheless, the resulting methods are still quite limited. 
@@
 Another weakness of the bound is related to that when constraints are dropped, the linear program may become
-unbounded. To prevent this, \citet{CS}  propose adding an extra constraint on the optimization variables.
+unbounded. To prevent this, \citet{CS}  propose imposing an extra constraint on the optimization variables.
 The bound they obtain, however, scales with the \emph{worst approximation error} over this constraint set.
@@
 \citet{SALP,BhatFaMo12:SALPNP},  repeat the analysis of \citet{CS}
-in combinations with other ideas. However, no existing work that we know of addresses the above weaknesses of the result of \citet{CS}.
+in combinations with other ideas.
+However, no existing work that we know of addresses the above weaknesses of the result of \citet{CS}.
+\todoc{Yasin's paper should be cited here as an interesting alternative approach.
+My notes about his paper:
+Approximation in the dual. No control for infeasibility of resulting ALP. 
+Algorithm: Stochastic gradient descent for computing near-optimal solution on Langrangian with large Langrangian coefficients.
+Directly bounding loss of policy return as compared to best policy amongst those feasible. 
+For infeasible LP, result is vacuous (the error blows up when demanding a better solution).
+No bound on best feasible policy's return.
+Strong requirements: Result depends on ability to choose a sampling distributions to control a variance term. 
+"Few predecessor state-action pairs, which can be accessed, or sparse features", mixing. 
+}
 
@@
 A preliminary version of this paper without the theoretical analysis and without the geometric arguments was published in a short conference communication \cite{aaaipaper}.
+\todoc{This could be a footnote on page 1 if space works out better that way.}
 

### 2017-03-24 autocontrol_review/response_letter.tex
response-letter-single-col-supplement

%\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
%\documentclass[12pt,twocolumn]{IEEEtran}
\documentclass[twocolumn]{IEEEtran}
\usepackage{times}

% Packages, commands --------------------------------------------------------------------
\input{pack}

% BIBLIOGRAHY -----------------------------------------------------------------------------
% Option 1: bibtex natbib
%\usepackage[numbers]{natbib}
%\usepackage[colorlinks=true,linkcolor=blue,citecolor=purple,pagebackref=true]{hyperref}
% Option 2: biblatex 
%\usepackage[backend=bibtex,style=ieee-alphabetic,natbib=true,backref=false]{biblatex}
\usepackage[backend=bibtex,style=ieee,natbib=true,backref=false]{biblatex}
\addbibresource{ref.bib}
% Adding back references to bib entries:
\DefineBibliographyStrings{english}{%
  backrefpage = {page},% originally "cited on page"
  backrefpages = {pages},% originally "cited on pages"
}
% Title, authors, etc. -------------------------------------------------------------------------

%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\title{A Linearly Relaxed Approximate Linear Program for Markov Decision Processes}
%\author{Chandrashekar Lakshminarayanan$^\star$, Shalabh Bhatnagar$^\star$,
 and Csaba Szepesvari$^\dagger$\thanks{$^\star$Department of Computer
Science and Automation, Indian Institute of Science, Bangalore 560012.
E-mail: $\{$chandrul, shalabh$\}$@csa.iisc.ernet.in}
\thanks{$^\dagger$Department of Computing Science, University of Alberta,
Edmonton, Alberta, Canada T6G 2E8. E-mail: csaba.szepesvari@ualberta.ca}}
% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

% Doc start ------------------------------------------------------------------------------------
\begin{document}
%\maketitle
Dear Editor,
            We would like to re-submit the revised version of our paper. We now list the differences between the previous and current submission.
\begin{itemize}
\item The title of the paper has been changed to ``A Linearly Relaxed Approximate Linear Program for Markov Decisions Processes''.
\item The length of current draft has been increased to 8 pages.
\item We have incorporated major revisions in the paper and restructure the presentation.
\item The length of the introduction has been increased to make the motivation clear. Proper placement with respect to existing literature has been done.
\item The main result has been stated up front alongside a discussion.
\item Streamlined formulation of the main result, with additional corollary that illustrates the utility. Added examples.
\item The proof has been simplified and restructured. The constants in the bound have been slightly improved.
\item Numerical illustration: New example has been added to illustrate the choices available when choosing constraints.
\end{itemize}
We have taken care of all the reviewer comments, except for the following comment by Reviewer~$1$.
\emph{Comment}: Explain the intuition behind stationary Markov deterministic policies being optimal.
\emph{Our Response:} Markov property buys this. Since we are limited by space constraints we have added reference to literature.
\end{itemize}
\end{document}

### 2017-03-24 supplementary/num.tex
response-letter-single-col-supplement

--- 2017-03-24 num.tex
@@
 The service rates satisfy $0<q(1)\leq \ldots\leq q(A)<1$ with $q(A)>p$ so as to ensure `stabilizability' of the queue.
-The reward associated with  action $a \in \A$ and state $s\in \S$ is given by $g_a(s)=-(s/n+q(a)^3)$.
-
+The reward associated with  action $a \in \A$ and state $s\in \S$ is given by $g_a(s)=-(s/N+q(a)^3)$ (the idea here is to penalize higher queue lengths and higher service rates).
 \textbf{Parameter Settings:} We ran our experiments for $S=1000$, $A=4$ with $q(1)=0.2$, $q(2)=0.4$, $q(3)=0.6$, $q(4)=0.8$, $p=0.4$ and $\alpha=1-\frac{1}{S}$.
@@
 When formulating the LRALP for state $s'$, we first let $c_{s'}(s)=(1-\alpha)(\alpha)^{|s'-s|}$ and normalize $c$ and sample $m=6$ constraints randomly using $c$ and compute $\hat{J}_{c_s'}$.
+Since the optimal sampling distribution is unknown, we sample from $c$ which assigns higher weights to nearby states.
 The lookahead policy is formulated as 

### 2017-03-24 supplementary/plt.tex
response-letter-single-col-supplement

--- 2017-03-24 plt.tex
@@
 \begin{tikzpicture}[scale=1,font=\Large,]
-    \begin{axis}[
-        xlabel=$t$,
-        ylabel=$\theta_t$,legend style={at={(0.5,-0.1)},anchor=north}
-]
-
-    \addplot[smooth,thick] plot file {./lralp_exp/V_LP};
-    \addplot[dashed,thick] plot file {./lralp_exp/V_pol_CS};
-    \addplot[dotted,thick] plot file {./lralp_exp/V_pol_cone};
+    \begin{axis}[]
+    \addplot[smooth,very thick, mark=diamond, each nth point=100] plot file {../lralp_exp/V_LP};
+    \addplot[dashed,very thick, mark=+, each nth point=100] plot file {../lralp_exp/V_pol_CS};
+    \addplot[dotted,very thick,mark=square, each nth point=100] plot file {../lralp_exp/V_pol_cone};
     \addlegendentry{$J^*$};
@@
 \begin{tikzpicture}[scale=1,font=\Large]
-    \begin{axis}[
-        xlabel=$t$,
-        ylabel=$\theta_t$,legend style={at={(0.5,-0.1)},anchor=north}
-]
-
-\addplot[smooth] plot file {./lralp_exp/policy};
-\addplot[dashed] plot file {./lralp_exp/policy_CS};
-\addplot[dotted] plot file {./lralp_exp/policy_cone};
+    \begin{axis}[]
+\addplot[very thick] plot file {../lralp_exp/policy};
+\addplot[dashed,very thick] plot file {../lralp_exp/policy_CS};
+\addplot[dotted,very thick] plot file {../lralp_exp/policy_cone};
 \addlegendentry{$u^*$};

### 2017-03-24 supplementary/results.tex
response-letter-single-col-supplement

--- 2017-03-24 results.tex
@@
 Note that $\Jalpo\ge J^*$ reflects the error due to using the basis functions $(\phi_j)_j$, and the magnitude of the deviation $\Jlro-\Jalpo$ reflects the error introduced due to the relaxed constraint system.
-\todoc{I commented out the figure.
-We can discuss whether we want to include it.}
 %The function $\Jalpo$ is an upper approximation to $J^*$
@@
 This can be seen to imply that $H: (\Re^S,\norm{\cdot}_{\infty,\psi}) \to (\Re^{SA}, \norm{\cdot}_{\infty,\psi})$ is a contraction,
-where for $J = (J_1^\top,\dots,J_A^\top)^\top \in \Re^{SA}$ we let $\norm{J}_{\infty,\psi} = \max_a\norm{J}_{\infty,\psi}$.
+where for $J = (J_1^\top,\dots,J_A^\top)^\top \in \Re^{SA}$ we let $\norm{J}_{\infty,\psi} = \max_a\norm{J_a}_{\infty,\psi}$.
 That $H$ is a contraction will play a crucial role in our results.
@@
 state spaces \citep[e.g.,][]{chemey99a}.
-Note that one can always choose $\psi = \one$: $\beta_\one = \alpha<1$. 
+Note that one can always choose $\psi = \one$, which gives $\beta_\one = \alpha<1$. 
 With this, we are ready to state our main result:
@@
 }
-\todoc{Add reference to the intro to Mausam's book.}
 
@@
 \label{conetheorm}
-Assume that $W_1 = \dots = W_A$, $\{w_{1,a}\,dots,w_{m,a}\} = \{ e_s\,:\, s\in \S_0 \}$ 
+Assume that $W_1 = \dots = W_A$, $\{w_{1,a},\dots,w_{m,a}\} = \{ e_s\,:\, s\in \S_0 \}$ 
 and that $\phi(\S)$ lies in the conic span of $\phi(\S_0)$ with conic coefficients given by $\Lambda$.

### 2017-03-24 autocontrol_review/response_letter.tex
response-letter

@@
-%\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
-%\documentclass[12pt,twocolumn]{IEEEtran}
-\documentclass[twocolumn]{IEEEtran}
-\usepackage{times}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Thin Formal Letter
+% LaTeX Template
+% Version 1.11 (8/12/12)
+%
+% This template has been downloaded from:
+% http://www.LaTeXTemplates.com
+%
+% Original author:
+% WikiBooks (http://en.wikibooks.org/wiki/LaTeX/Letters)
+%
+% License:
+% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% Packages, commands --------------------------------------------------------------------
-\input{pack}
+%----------------------------------------------------------------------------------------
+%	DOCUMENT CONFIGURATIONS
+%----------------------------------------------------------------------------------------
 
-% BIBLIOGRAHY -----------------------------------------------------------------------------
-% Option 1: bibtex natbib
-%\usepackage[numbers]{natbib}
-%\usepackage[colorlinks=true,linkcolor=blue,citecolor=purple,pagebackref=true]{hyperref}
-% Option 2: biblatex 
-%\usepackage[backend=bibtex,style=ieee-alphabetic,natbib=true,backref=false]{biblatex}
-\usepackage[backend=bibtex,style=ieee,natbib=true,backref=false]{biblatex}
-\addbibresource{ref.bib}
-% Adding back references to bib entries:
-\DefineBibliographyStrings{english}{%
-  backrefpage = {page},% originally "cited on page"
-  backrefpages = {pages},% originally "cited on pages"
-}
-% Title, authors, etc. -------------------------------------------------------------------------
+\documentclass{letter}
 
-%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
-\title{A Linearly Relaxed Approximate Linear Program for Markov Decision Processes}
-%\author{Chandrashekar Lakshminarayanan$^\star$, Shalabh Bhatnagar$^\star$,
- and Csaba Szepesvari$^\dagger$\thanks{$^\star$Department of Computer
-Science and Automation, Indian Institute of Science, Bangalore 560012.
-E-mail: $\{$chandrul, shalabh$\}$@csa.iisc.ernet.in}
-\thanks{$^\dagger$Department of Computing Science, University of Alberta,
-Edmonton, Alberta, Canada T6G 2E8. E-mail: csaba.szepesvari@ualberta.ca}}
-% The \author macro works with any number of authors. There are two commands
-% used to separate the names and addresses of multiple authors: \And and \AND.
-%
-% Using \And between authors leaves it to \LaTeX{} to determine where to break
-% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
-% puts 3 of 4 authors names on the first line, and the last on the second
-% line, try using \AND instead of \And before the third author name.
-\newcommand{\fix}{\marginpar{FIX}}
-\newcommand{\new}{\marginpar{NEW}}
+% Adjust margins for aesthetics
+\addtolength{\voffset}{-0.5in}
+\addtolength{\hoffset}{-0.3in}
+\addtolength{\textheight}{2cm}
 
-% Doc start ------------------------------------------------------------------------------------
+%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page
+
+%----------------------------------------------------------------------------------------
+%	YOUR NAME & ADDRESS SECTION
+%----------------------------------------------------------------------------------------
+
+\signature{Chandrashekar L} % Your name for the signature at the bottom
+
+\address{Department of Computing Science\\ University of Alberta, Edmonton, Alberta\\ Canada, T6G 2E9.} % Your address and phone number
+
+%----------------------------------------------------------------------------------------
+
 \begin{document}
-%\maketitle
-Dear Editor,
+
+%----------------------------------------------------------------------------------------
+%	ADDRESSEE SECTION
+%----------------------------------------------------------------------------------------
+
+\begin{letter}{} % Name/title of the addressee
+
+%----------------------------------------------------------------------------------------
+%	LETTER CONTENT SECTION
+%----------------------------------------------------------------------------------------
+
+\opening{\textbf{Dear Editor,}}
 We would like to re-submit the revised version of our paper. We now list the differences between the previous and current submission.
@@
 \end{itemize}
-We have taken care of all the reviewer comments, except for the following comment by Reviewer~$1$.
-\emph{Comment}: Explain the intuition behind stationary Markov deterministic policies being optimal.
-\emph{Our Response:} Markov property buys this. Since we are limited by space constraints we have added reference to literature.
-\end{itemize}
+We have taken care of all the reviewer comments, except for the following comment by Reviewer~$1$.\\
+\emph{Comment}: Explain the intuition behind stationary Markov deterministic policies being optimal.\\
+\emph{Our Response:} The fact follows from the Markov property. Since we are limited by space, we have added a reference to literature.
+
+\vspace{2\parskip} % Extra whitespace for aesthetics
+\closing{Sincerely,}
+\vspace{2\parskip} % Extra whitespace for aesthetics
+
+%----------------------------------------------------------------------------------------
+
+\end{letter}
+
 \end{document}

### 2017-03-25 errana.tex
minor typos and coefficient changed to 3 from 2.5

@@
 \newcommand{\G}{\Gamma}
-We will introduce a novel contraction operators, $\hg: \Re^S \to \Re^S$, that captures the distortion introduced
+We will introduce a novel contraction operator, $\hg: \Re^S \to \Re^S$, that captures the distortion introduced
 by the extra constraint in ALP and the relaxation in LRALP, respectively. 
@@
 \begin{proof}[Proof of \cref{lpsol}]
-The claim follows by the change of variables $y := x-x_0$.
+Set $y = x-x_0$.
 \end{proof}
@@
 \label{eq:maindec}
-\norm{\Jlr-J^*}_{1,c} = c^\top ( \Jlr - J^* ) + 2c^\top ( \Jlr - J^* )^-\,.
+\norm{\Jlr-J^*}_{1,c} = c^\top\!( \Jlr - J^* ) + 2c^\top\!( \Jlr - J^* )^-\,.
 \end{align}
@@
 We have
-\begin{align}
-\norm{J^*-\Jalpo}_{\mn}\leq 2 \epsilon\,,
-\end{align}
+$ % \begin{align}
+\norm{J^*-\Jalpo}_{\mn}\leq 2 \epsilon
+$, %\end{align}
 where recall that $\epsilon = \inf_{r\in \Re^k} \norm{ J^*-\Phi r }_{\mn}$. 

### 2017-03-31 autocontrol_review/response_letter.tex
response update
single column supplementary updated

@@
 
-\signature{Chandrashekar L} % Your name for the signature at the bottom
+\signature{Chandrashekar Lakshminarayanan} % Your name for the signature at the bottom
 
@@
 \item The length of current draft has been increased to 8 pages.
-\item We have incorporated major revisions in the paper and restructure the presentation.
+\item We have incorporated major revisions in the paper and restructured the presentation.
 \item The length of the introduction has been increased to make the motivation clear. Proper placement with respect to existing literature has been done.
-\item The main result has been stated up front alongside a discussion.
+\item The main result has been stated upfront alongside a discussion.
 \item Streamlined formulation of the main result, with additional corollary that illustrates the utility. Added examples.
-\item The proof has been simplified and restructured. The constants in the bound have been slightly improved.
+\item The proof has been simplified and restructured.
 \item Numerical illustration: New example has been added to illustrate the choices available when choosing constraints.
 \end{itemize}
-We have taken care of all the reviewer comments, except for the following comment by Reviewer~$1$.\\
+We have taken care of all the reviewer comments, except for the following comment by Reviewer~$2$.\\
 \emph{Comment}: Explain the intuition behind stationary Markov deterministic policies being optimal.\\

### 2017-03-31 supplementary/intro.tex
single column supplementary updated

--- 2017-03-24 intro.tex
@@
 a good approximation to the optimal value function will exist in the linear space spanned by the basis functions.
-The idea then is to design some algorithm to find the coefficients of the basis functions that gives a a good approximation, 
+The idea then is to design some algorithm to find the coefficients of the basis functions that gives a good approximation,
 while keeping computation cost in check.
